### 2019-05-02 Notes/Magnus/Old/Magnus_notes.tex
Added non-code files

% Notes on Magnus project
% Created 05/15/18

\documentclass[preprintnumbers,floatfix,aps,prc,preprint]{revtex4-1}

% Packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{enumerate}
\usepackage{float}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage[figuresright]{rotating}
\usepackage{hyperref} % For clickable links to sections within table of contents
\usepackage{cellspace}
\usepackage{siunitx}
\usepackage[font=small,skip=0pt]{caption}
\usepackage{color}

\newcommand{\eps}{\varepsilon}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Decoupling of bound states with the Magnus expansion and the in-medium similarity renormalization group}

\author{A.~J.~Tropiano$^{1}$,
        S.~K.~Bogner$^{2}$,
        R.~J.~Furnstahl$^{1}$,
        N.~M.~Parzuchowski$^{1}$}
\affiliation{
$^1$\mbox{Department of Physics, The Ohio State University, Columbus, OH 43210, USA}  \\
$^2$\mbox{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy,}  \\
    \mbox{Michigan State University, East Lansing, MI 48824, USA}}

\date{\today}

\begin{abstract}
Test Magnus expansion on LO NN potential at high $\Lambda$.
\end{abstract}

\maketitle

\tableofcontents

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}

Nuclear many-body calculations are complicated from the coupling of the reference state to particle/hole excitations. The in-medium similarity renormalization group (IMSRG) simplifies the problem by decoupling the reference state from excitations \cite{Hergert:2017}. This makes approximate many-body methods feasible allowing for low-energy nuclear structure calculations. The IMSRG decouples operators by applying a continuous unitary transformation $U(s)$ where $s=0 \rightarrow \infty $ is the flow parameter (sometimes $\lambda=s^{-1/4}$ is used in place of $s$). Below is an example of an evolved Hamiltonian
%
\begin{eqnarray}
\label{eq:imsrg_hamiltonian}
H(s) = U(s) H(0) U^{\dagger}(s).
\end{eqnarray}
%
where $H(0)$ corresponds to the `bare' Hamiltonian and $H(s)$ corresponds to the evolved, decoupled Hamiltonian at $s>0$. In practice, the unitary transformation $U(s)$ is not explicitly solved for; the evolved Hamiltonian is given by a differential flow equation. To see this, we take the derivative of Eq. (\ref{eq:imsrg_hamiltonian})
%
\begin{eqnarray}
\label{eq:hamiltonian_deriv1}
\frac{dH(s)}{ds} = \frac{dU(s)}{ds} H(0) U^{\dagger}(s) + U(s) H(0) \frac{dU^{\dagger}(s)}{ds}.
\end{eqnarray}
%
Rearranging Eq. (\ref{eq:imsrg_hamiltonian}) for $H(0)$ and substituting into Eq. (\ref{eq:hamiltonian_deriv1}) gives
%
\begin{eqnarray}
\label{eq:hamiltonian_deriv2}
\frac{dH(s)}{ds} = \frac{dU(s)}{ds} U^{\dagger}(s) H(s) + H(s) U(s) \frac{dU^{\dagger}(s)}{ds}.
\end{eqnarray}
%
Because $U(s)$ is unitary, we see that
%
\begin{eqnarray}
\label{eq:antihermitian_u}
\frac{d}{ds}(U(s)U^{\dagger}(s)) = \frac{d}{ds}(I) = 0 \implies \frac{dU(s)}{ds} U^{\dagger}(s) = -U(s) \frac{dU^{\dagger}(s)}{ds}.
\end{eqnarray}
%
The anti-hermitian IMSRG generator $\eta(s)$ is defined below in terms of the unitary transformation and its derivative
%
\begin{eqnarray}
\label{eq:eta}
\eta(s) \equiv \frac{dU(s)}{ds} U^{\dagger}(s) = -\eta^{\dagger}(s).
\end{eqnarray}
%
We can now write a concise flow equation for $H(s)$ in terms of the IMSRG generator $\eta(s)$
%
\begin{eqnarray}
\label{eq:imsrg_flow}
\frac{dH(s)}{ds} = [\eta(s), H(s)],
\end{eqnarray}
%
\begin{eqnarray}
\label{eq:imsrg_generator}
\eta(s) = [G, H(s)].
\end{eqnarray}
%
In the commutator definition of $\eta(s)$, we choose $G$ to specify the type of flow. (Note that $G$ is not the IMSRG generator!) For instance, to evolve the Hamiltonian to a band-diagonal form, one can set $G=H_{D}(s)$ (the diagonal of the evolving Hamiltonian, also known as the ``Wegner" generator \cite{Wegner:1994}) or $G=T_{rel}$ (the relative kinetic energy). These are the two choices utilized in this study. \\

It is possible to construct the unitary transformation explicitly by rearranging Eq. (\ref{eq:eta})
%
\begin{eqnarray}
\label{eq:unitary_trans}
\frac{dU(s)}{ds} = \eta(s) U(s).
\end{eqnarray}
%
This equation is necessary in the Magnus expansion implementation of the IMSRG where $U(s)$ is solved for directly. The Magnus implementation offers a couple significant advantages over the typical IMSRG approach when evolving operators. (Here we have shown all the IMSRG machinery  for evolving Hamiltonians, but these transformations hold for {\it any} operator.) In section II., we discuss the advantages of the Magnus implementation. For a more detailed discussion of the Magnus expansion, see \cite{Morris:2015}. \\

Nuclei with intruder states (low-lying states in valence-space) have shown poor evolution under the IMSRG. In general, evolving the Hamiltonian of such systems will distort the reference state skewing low-energy observables. It is not understood why such systems can evolve in this way or what affects the evolution. In \cite{Glazek:2008,Wendt:2011}, a similar problem was studied within the SRG framework. Here it was shown that non-physical, spurious, bound states can corrupt the low-momentum physics of evolved Hamiltonians in free-space depending on the choice of SRG generator (more details of this are given in section III.) One possibility in the IMSRG intruder state problem is that the choice of generator matters as with the spurious bound state problem. \\

From the growing usage of the Magnus expansion in IMSRG calculations, it must first be confirmed that the Magnus implementation matches the typical IMSRG approach for these difficult systems before addressing the intruder state problem. It has already been shown that the Magnus implementation converges to the IMSRG result for many systems, but this has never been confirmed for nuclei with intruder states. To verify the Magnus expansion's validity in a difficult test case, we use the analogous SRG spurious bound state problem mentioned above.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Magnus expansion}
\label{sec:magnus}

W. Magnus proved that a solution of the form $U(s)=e^{\Omega(s)}$ exists for equations of the form (\ref{eq:unitary_trans}) where $\Omega^{\dagger}(s)=-\Omega(s)$ and $\Omega(0)=O$. The Magnus expansion yields a differential equation for $\Omega(s)$
%
\begin{eqnarray}
\label{eq:magnus_omega}
\frac{d\Omega(s)}{ds} = \sum_{k=0}^{\infty} \frac{B_k}{k!} ad_{\Omega}^{k}(\eta),
\end{eqnarray}
%
where $ad_{\Omega}^{0}(\eta)=\eta(s)$, $ad_{\Omega}^{k}(\eta)=[\Omega(s),ad_{\Omega}^{k-1}(\eta)]$, and $B_k$ are the Bernoulli numbers.
%
Mathematically-speaking, $\Omega(s)$ is usually expanded in powers of $\eta(s)$ where each term in the series is related to an integral of a nested commutator (mathematical details are given in \cite{Magnus:1954,Blanes:2009}). From a physics standpoint, it is only necessary to numerically solve Eq. (\ref{eq:magnus_omega}) and apply the transformation to the Hamiltonian (or any operator of interest)
%
\begin{eqnarray}
\label{eq:magnus_hamiltonian}
H(s) = e^{\Omega(s)} H(0) e^{-\Omega(s)}.
\end{eqnarray}
%
The Magnus implementation converges to a corresponding IMSRG transformation exactly as $k \rightarrow \infty$. In practice, the series is truncated at some $k_{max}$ as the successive terms fall off with $1/k!$. The evolved Hamiltonian, Eq. (\ref{eq:magnus_hamiltonian}), can be constructed using either the Baker-Cambell-Hausdorff (BCH) formula or numerical matrix exponentiation functions (results shown here use SciPy's expm function). Overall, the Magnus implementation shows consistency with typical IMSRG evolution. \\

The Magnus implementation becomes extremely useful with IMSRG calculations extending to further scalar and/or non-scalar observables \cite{Parzuchowski:2017}. Typically, one would need to solve several flow equations for each operator which requires a considerable amount of memory for the solution vector. However, with the Magnus expansion, $U(s)$ is given explicitly by solving for $\Omega(s)$ once from Eq. (\ref{eq:magnus_omega}) and can be applied to several operators which greatly simplifies the numerical task of evolving several operators. Another major advantage of the Magnus implementation comes from the functional form of $U(s)$. Numerically solving Eq. (\ref{eq:magnus_omega}) will introduce some error on $\Omega(s)$; however, given the exponential form of $U(s)$, the Magnus implementation guarantees a unitary transformation regardless of the error (this is easily seen by convincing yourself that $U(s)=e^{\Omega(s)+\delta \Omega}$ is still unitary no matter the size of $\delta \Omega$). Because unitary transformations preserve observables, a Magnus evolved operator will give consistent observables with the bare operator. For an IMSRG evolved operator, its observables will have some error from solving Eq. (\ref{eq:imsrg_flow}) numerically. Typically, the flow equation (\ref{eq:imsrg_flow}) is solved using a high-order ODE solver to maintain accurate results. With the Magnus implementation, one can easily solve Eq. (\ref{eq:magnus_omega}) with the first-order Euler method
%
\begin{eqnarray}
\label{eq:euler_method}
\Omega_{n+1}(s) = \Omega_{n}(s) + \frac{d\Omega(s)}{ds} ds.
\end{eqnarray}
%
This provides a modest speed-up in computational time with no loss in accuracy in the observables of the evolved operator. Thus, the Magnus expansion offers an efficient modification to IMSRG transformations while maintaining the accuracy of evolved observables and the desired decoupling.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SRG evolution at high $\Lambda$}
\label{sec:srg_high_lambda}

%
\begin{table}[H]
\caption{Bound state values for deuteron, $\epsilon_d$, and spurious, deeply bound states, $\epsilon_s^{(1)}$ and $\epsilon_s^{(2)}$, in units MeV for three cutoffs in $\Lambda$}
\label{tab:Wendt_bound_states}
\begin{ruledtabular}
\begin{tabular}{{>{\centering\arraybackslash}m{1.3in} >{\centering\arraybackslash}m{1.3in}>{\centering\arraybackslash}m{1.3in}>{\centering\arraybackslash}m{1.3in}}}
  $\Lambda \,\,\, [fm^{-1}]$ & $\epsilon_d$  [MeV] & $\epsilon_s^{(1)}$  [MeV] & $\epsilon_s^{(2)}$  [MeV] \\
  \colrule
  $4.0$ & $-2.095$ & - & - \\
  $9.0$ & $-2.001$ & $-2004.980$ & - \\
  $20.0$ & $-1.992$ & $-1669.673$ & $-34491.583$ \\
\end{tabular}
\end{ruledtabular}
\end{table}
%
In \cite{Nogga:2005} it was shown that non-local chiral nuclear interactions are cutoff dependent in the singular tensor interaction of the one-pion exchange potential (OPEP). It was argued that the cutoff dependence could be absorbed by counterterms in $S$ waves and higher partial waves, and in other partial waves, contact interactions were necessary. In the same manner, we consider an NN potential at leading order (LO) with a non-local regulator of the form
%
\begin{eqnarray}
\label{eq:non_local_reg}
f(k',k) = e^{-(k^4+k'^4)/\Lambda^4},
\end{eqnarray}
%
for both the one-pion exchange and contact force terms. In certain channels, taking the cutoff to high values can result in spurious, deeply bound states. These bound states are unphysical bound states coming from the short-ranged tensor force of the highly singular potential at short distances. In Table \ref{tab:Wendt_bound_states} the values of the deuteron bound state and spurious, deeply bound state energies are given for three cutoffs in $\Lambda$. Note that the number of spurious bound states increases as $\Lambda$ is taken to larger values. From the effective field theory (EFT) perspective, these states are outside the range of the EFT. However in \cite{Wendt:2011}, it was shown that taking high cutoffs can become problematic when SRG evolving these potentials. \\

In the SRG framework, we evolve the Hamiltonian to decouple low- and high-momenta \cite{Bogner:2007,Bogner:2010}. In Figures \ref{fig:srg_contours_Wendt_4}, \ref{fig:srg_contours_Wendt_9}, and \ref{fig:srg_contours_Wendt_20} we show an evolving potential for three cutoffs in $\Lambda$ and two choices of the SRG generator $\eta$, $G=T_{rel}$ and $G=H_D$. Note that the evolution is nearly identical in Figure \ref{fig:srg_contours_Wendt_4}. At this lower value of $\Lambda=4.0 \, fm^{-1}$, there is no significant sensitivity to the SRG generator: both evolve the potential to a band-diagonal form. However, at higher values of $\Lambda$, where deeply, spurious bound states are present, we see a qualitative difference in the evolution from $G=T_{rel}$ to $G=H_D$. \\
%
\begin{figure}[H]
  \centering
  \includegraphics[width=14cm]{srg_contours_Wendt_4}
   \hspace*{0.05\textwidth}%
  \caption{Contour of SRG evolved $V_{\lambda}(k,k')$ with $\Lambda=4.0\,fm^{-1}$, $G=T_{rel}$ (top) and $G=H_{D}$ (bottom) for several values of $\lambda$.}
  \label{fig:srg_contours_Wendt_4}
\end{figure}
%
For $G=T_{rel}$, the spurious, deeply bound state evolves to a point in which it distorts the low-momentum part of $V_{\lambda}(k,k')$. This is seen by comparing the upper left-hand block of the contours between Figures \ref{fig:srg_contours_Wendt_4}, \ref{fig:srg_contours_Wendt_9}, and \ref{fig:srg_contours_Wendt_20}. There is a noticeable difference going from $\Lambda=4.0 \, fm^{-1}$ to $\Lambda=20.0 \, fm^{-1}$, and if one were to calculate the deuteron wave function for instance, the resulting function would differ significantly from the original, unevolved wave function. Thus, the SRG generator corresponding to $G=T_{rel}$ leads to an undesirable evolution for potentials with spurious, deeply bound states. \\
%
\begin{figure}[H]
  \centering
  \includegraphics[width=14cm]{srg_contours_Wendt_9}
   \hspace*{0.05\textwidth}%
  \caption{Contour of SRG evolved $V_{\lambda}(k,k')$ with $\Lambda=9.0\,fm^{-1}$, $G=T_{rel}$ (top) and $G=H_{D}$ (bottom) for several values of $\lambda$.}
  \label{fig:srg_contours_Wendt_9}
\end{figure}
%
\begin{figure}[H]
  \centering
  \includegraphics[width=14cm]{srg_contours_Wendt_20}
   \hspace*{0.05\textwidth}%
  \caption{Contour of SRG evolved $V_{\lambda}(k,k')$ with $\Lambda=20.0\,fm^{-1}$, $G=T_{rel}$ (top) and $G=H_{D}$ (bottom) for several values of $\lambda$.}
  \label{fig:srg_contours_Wendt_20}
\end{figure}
%
With the Wegner generator, we see that the spurious, deeply bound state(s) decouple at sufficiently high momentum (meaning it does not affect the low-momentum part of the potential). Once the bound state is decoupled, the SRG evolution drives the potential to the desired band-diagonal form as before. The low-momentum part of the evolved potential is consistent between the three cutoffs unlike with $G=T_{rel}$. This is seen more clearly in Figure \ref{fig:srg_diags_offdiags_Wendt_Wegner}. Therefore, at high cutoffs, the evolution is dependent on the choice of $G$ where the Wegner generator safely evolves the potential by keeping the spurious, deeply bound state(s) outside the low-energy physics. \\
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{srg_diags_offdiags_Wendt_Wegner}
   \hspace*{0.05\textwidth}%
  \caption{Diagonal and off-diagonal matrix elements of SRG evolved $V_{\lambda}(k,k')$ with $G=H_{D}$ for $\Lambda=4.0, \, 9.0, \, 20.0\,fm^{-1}$ and several values of $\lambda$.}
  \label{fig:srg_diags_offdiags_Wendt_Wegner}
\end{figure}
%
Again, it is unusual to see a difference in the SRG evolution going from $G=T_{rel}$ to $G=H_{D}$, but the presence of spurious, deeply bound states significantly affects the SRG procedure. In practice, these potentials at high cutoffs are not very useful; however, they do offer a nice test case for the Magnus expansion given their sensitivity to SRG evolution. It is critical that the Magnus implementation matches the typical SRG approach if one is to understand the IMSRG intruder state problem using the Magnus expansion. In the following section, we compare results between the Magnus expansion and the typical SRG approach for these potentials. \\
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{srg_diags_offdiags_Wendt_Wilson}
   \hspace*{0.05\textwidth}%
  \caption{Diagonal and off-diagonal matrix elements of SRG evolved $V_{\lambda}(k,k')$ with $G=T_{rel}$ for $\Lambda=4.0, \, 9.0, \, 20.0\,fm^{-1}$ and several values of $\lambda$.}
  \label{fig:srg_diags_offdiags_Wendt_Wilson}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Magnus expansion at high $\Lambda$}
\label{sec:magnus_high_lambda}

% .....................................................................................................................................................................................................................................
\subsection{Evolved potentials}

In this subsection, we compare the evolved potentials, $V_{\lambda}(k,k')$, for the typical SRG approach and the Magnus implementation. For all figures presented in this subsection, the first-order Euler method with a fixed step-size, $ds=10^{-5}$, was used to solve Eq. (\ref{eq:magnus_omega}) in the Magnus implementation. For the most part, there is no sensitivity to the step-size, only that it has to be chosen such that ``enough" steps are taken in evolving $V_{\lambda}(k,k')$ (for instance, at $\lambda=10.0 \, fm^{-1}$ we set $ds=10^{-6}$ to get good agreement with the standard SRG approach since $ds=10^{-5}$ would only result in a total of 12 steps in $s$). However, the evolution of $V_{\lambda}(k,k')$ does depend significantly on the truncation of the Magnus series, $k_{max}$, particularly at higher cutoffs in $\Lambda$. Here $k_{max}$ represents the last term included in the Magnus series in numerically solving Eq. (\ref{eq:magnus_omega}).
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{mag_contours_Wendt_9_Wegner}
   \hspace*{0.05\textwidth}%
  \caption{Contour of evolved $V_{\lambda}(k,k')$ with $\Lambda=9.0\,fm^{-1}$ and $G=H_{D}$ for several values of $\lambda$. Each row corresponds to a different truncation in the Magnus expansion (2, 4, 6, 10, 14) with the last row being the SRG result.}
  \label{fig:mag_contours_Wendt_9_Wegner}
\end{figure}
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{mag_contours_Wendt_9_Wilson}
   \hspace*{0.05\textwidth}%
  \caption{Contour of evolved $V_{\lambda}(k,k')$ with $\Lambda=9.0\,fm^{-1}$ and $G=T_{rel}$ for several values of $\lambda$. Each row corresponds to a different truncation in the Magnus expansion (2, 4, 6, 10, 14) with the last row being the SRG result.}
  \label{fig:mag_contours_Wendt_9_Wilson}
\end{figure}
%
In Figure \ref{fig:mag_contours_Wendt_9_Wegner} we show contours of the evolving potential for $\Lambda=9.0 \, fm^{-1}$ with the Wegner generator. This figure compares the Magnus implementation at several truncations to the SRG result (bottom row). Notice the large off-diagonal values in $V_{\lambda}(k,k')$ at $\lambda=2.0 \, fm^{-1}$ for $k_{max}=2$. This illustrates the point that using the Magnus expansion with a low truncation can lead to an undesirable flow. Taking $k_{max}$ to higher values reproduces the SRG result to moderate accuracy. An important piece to notice in Figure \ref{fig:mag_contours_Wendt_9_Wegner} is that the Magnus reproduces the decoupling of the spurious, deeply bound state at all values of $k_{max}$ as in the SRG approach. At $\lambda=1.2 \, fm^{-1}$ there is a slight difference in the evolved potential near the decoupled spurious bound state, although the low-momentum block is nearly identical.
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{mag_diags_offdiags_Wendt_9_Wegner}
   \hspace*{0.05\textwidth}%
  \caption{Diagonal and off-diagonal matrix elements of evolved $V_{\lambda}(k,k')$ with $G=H_{D}$ and $\Lambda=9.0 \, fm^{-1}$ for several values of $\lambda$ and $k_{max}$ compared to the SRG result.}
  \label{fig:mag_diags_offdiags_Wendt_9_Wegner}
\end{figure}
%
Figure \ref{fig:mag_contours_Wendt_9_Wilson} shows the result for $G=T_{rel}$. Again, we see that the Magnus implementation reproduces the SRG generator sensitivity, in particular, how the spurious, deeply bound state is decoupled. This reinforces the conclusion that the Wegner generator safely evolves the potential whereas the $G=T_{rel}$ choice does not. The higher truncations in Figure \ref{fig:mag_contours_Wendt_9_Wilson} are in very good agreement with the SRG result. This can be seen more quantitatively in Figures \ref{fig:mag_diags_offdiags_Wendt_9_Wegner} and \ref{fig:mag_diags_offdiags_Wendt_9_Wilson}. These figures show the diagonal and off-diagonal elements of $V_{\lambda}(k,k')$ for several values of $k_{max}$ compared to the SRG result. We see the decoupling of the spurious bound state in the upper three panels of Figure \ref{fig:mag_diags_offdiags_Wendt_9_Wegner} where the curve dips down to large negative values at $k \approx 1.75 \, fm^{-1}$.
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{mag_diags_offdiags_Wendt_9_Wilson}
   \hspace*{0.05\textwidth}%
  \caption{Diagonal and off-diagonal matrix elements of evolved $V_{\lambda}(k,k')$ with $G=T_{rel}$ and $\Lambda=9.0 \, fm^{-1}$ for several values of $\lambda$ and $k_{max}$ compared to the SRG result.}
  \label{fig:mag_diags_offdiags_Wendt_9_Wilson}
\end{figure}
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{mag_diff_Wendt_9_Wegner}
   \hspace*{0.05\textwidth}%
  \caption{Difference in the diagonal and off-diagonal matrix elements of evolved $V_{\lambda}(k,k')$ with $G=H_D$ and $\Lambda=9.0 \, fm^{-1}$ for several values of $\lambda$ and $k_{max}$.}
  \label{fig:mag_diff_Wendt_9_Wegner}
\end{figure}
%
\newpage
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{mag_diff_Wendt_9_Wilson}
   \hspace*{0.05\textwidth}%
  \caption{Difference in the diagonal and off-diagonal matrix elements of evolved $V_{\lambda}(k,k')$ with $G=H_D$ and $\Lambda=9.0 \, fm^{-1}$ for several values of $\lambda$ and $k_{max}$.}
  \label{fig:mag_diff_Wendt_9_Wilson}
\end{figure}
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{mag_diags_offdiags_Wendt_4_Wegner}
   \hspace*{0.05\textwidth}%
  \caption{Diagonal and off-diagonal matrix elements of evolved $V_{\lambda}(k,k')$ with $G=H_{D}$ and $\Lambda=4.0 \, fm^{-1}$ for several values of $\lambda$ and $k_{max}$ compared to the SRG result.}
  \label{fig:mag_diags_offdiags_Wendt_4_Wegner}
\end{figure}
%
In Figures \ref{fig:mag_diff_Wendt_9_Wegner} and \ref{fig:mag_diff_Wendt_9_Wilson} we show the difference in the diagonal and off-diagonal matrix elements between the typical SRG evolved potential and the Magnus evolved potential. The only significant disagreement in evolution comes with the low truncation $k_{max}=2$. Taking the next term ($k_{max}=4$ since the $k=3$ term is zero from $B_3=0$) increases the agreement substantially. Finally, we check the comparison between the typical SRG approach and the Magnus implementation at the lower cutoff of $\Lambda=4.0 \, fm^{-1}$ in Figures \ref{fig:mag_diags_offdiags_Wendt_4_Wegner} and \ref{fig:mag_diags_offdiags_Wendt_4_Wilson}. At the lower cutoff, the agreement is better for even lower truncations in the Magnus series. We see consistent evolution keeping only the first couple terms in the Magnus series.
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{mag_diags_offdiags_Wendt_4_Wilson}
   \hspace*{0.05\textwidth}%
  \caption{Diagonal and off-diagonal matrix elements of evolved $V_{\lambda}(k,k')$ with $G=T_{rel}$ and $\Lambda=4.0 \, fm^{-1}$ for several values of $\lambda$ and $k_{max}$ compared to the SRG result.}
  \label{fig:mag_diags_offdiags_Wendt_4_Wilson}
\end{figure}

% .....................................................................................................................................................................................................................................
\subsection{Accuracy of observables}

The Magnus expansion guarantees a unitary transformation in evolving an operator. Thus, the evolved observables are consistent with the initial observables. Here we show some numerical results to illustrate this. In Table \ref{tab:errors} we show values for the relative error in the deuteron bound state energy and the root mean square error (RMSE) in the eigenvalues from the initial and evolved Hamiltonian. With the SRG approach, one cannot avoid compiling ODE solver error in solving the flow equations. The Magnus implementation avoids this issue; this is seen by comparing the orders of magnitude in the Table \ref{tab:errors}. We see about a $10^7$ order of magnitude difference in the relative error of $\epsilon_d$ and a $10^5$ order of magnitude difference in the RMSE going from the SRG approach to the Magnus approach.
%
\begin{table}[H]
\caption{Relative error in the deuteron bound state energy and the root mean square error in eigenvalues where $\tilde{\epsilon}$ denotes an evolved eigenvalue with SRG and Magnus evolved Hamiltonians for $\Lambda=9.0 \, fm^{-1}$ and $\lambda=1.2 \, fm^{-1}$.}
\label{tab:errors}
\begin{ruledtabular}
\begin{tabular}{{>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{2in}}}
  $  $ & $G$ & $ |\frac{\epsilon_d-\tilde{\epsilon}_d}{\epsilon_d}| $ & $\sqrt{\frac{1}{N} \, \sum_{i}^{N} (\tilde{\epsilon}_i-\epsilon_i)^2}$   [MeV] \\
  \colrule
  SRG & $ $ & $\num{2.428e-06}$ & $\num{2.856e-04}$ \\
  Magnus, $k_{max}=2$ & $H_D$ & $\num{1.040e-12}$ & $\num{6.881e-09}$ \\
  Magnus, $k_{max}=14$ & $ $ & $\num{5.727e-13}$ & $\num{6.903e-09}$ \\ \hline
  SRG & $ $ & $\num{1.325e-04}$ & $\num{1.596e-04}$ \\
  Magnus, $k_{max}=2$ & $T_{rel}$ & $\num{1.542e-11}$ & $\num{6.770e-09}$ \\
  Magnus, $k_{max}=14$ & $ $ & $\num{3.418e-12}$ & $\num{6.674e-09}$ \\
\end{tabular}
\end{ruledtabular}
\end{table}
%
In Figure \ref{fig:initial_phase_shifts} we show the phase shifts in the $^{3}S_{1}-^{3}D_{1}$ coupled channel for two cutoffs in $\Lambda$. Phase shifts should also be consistent from the bare to evolved potential from unitarity. In Figure \ref{fig:evolved_phase_shifts_diff} we show the difference in the bare ($\lambda=\infty$) and evolved ($\lambda=1.2$) phase shifts using the typical SRG approach and the Magnus expansion at two truncations. Up to $E_{lab} \sim 100 \, MeV$ the differences are very small for both methods. At higher lab energies, the difference is more sensitive to the truncation in the Magnus series. This is illustrated by the large peak at $E_{lab} \sim 100 \, MeV$ for $k_{max}=2$ and $G=H_D$ in Figure \ref{fig:evolved_phase_shifts_diff}.
%
\begin{figure}[H]
  \centering
  \includegraphics[width=10cm]{initial_phase_shifts}
   \hspace*{0.05\textwidth}%
  \caption{$^{3}S_{1}$ phase shifts for $\Lambda=4.0$ and $9.0 \, fm^{-1}$.}
  \label{fig:initial_phase_shifts}
\end{figure}
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{evolved_phase_shifts_diff}
   \hspace*{0.05\textwidth}%
  \caption{Difference in the $^{3}S_{1}$ phase shifts with $\Lambda=9.0 \, fm^{-1}$ for SRG and Magnus evolved potentials.}
  \label{fig:evolved_phase_shifts_diff}
\end{figure}

% .....................................................................................................................................................................................................................................
\subsection{RKE semi-local potentials}

The previous results used a non-local potential where both the one-pion exchange potential and contact force are regulated with Eq. (\ref{eq:non_local_reg}). One might ask how high cutoffs affect the SRG procedure for potentials that are regulated differently. This is an interesting problem in its own right, and we leave a complete analysis of this as a further study. Here we sample this problem by showing SRG and Magnus results with a semi-local LO NN potential \cite{Reinert:2018} where the regulators have the following form:
%
\begin{subequations}
\label{eq:semi_local_regulator}
\begin{eqnarray}
f_{1\pi}(q) = e^{-(q^2+M_{\pi}^2)/\Lambda^2},
\label{eq:opep_regulator} \\
%
f_{cont}(k',k) = e^{-(k^2+k'^2)/\Lambda^2},
\label{eq:contact_regulator}
\end{eqnarray}
\end{subequations}
%
where $q=|\vec{k}'-\vec{k}|$. The first function regulates the OPEP locally while the second regulates the contact force non-locally. \\

Notice that the cutoff is not consistent numerically between the two cases in the sense that functional form of the regulator controls the strength of the cutoff (i.e., $\Lambda=4.0 \, fm^{-1}$ for the non-local potential is not the same as $\Lambda=4.0 \, fm^{-1}$ for the semi-local potential). This is seen in Table \ref{tab:RKE_bound_states} by noting the presence of a spurious, deeply bound state at $\Lambda=4.0 \, fm^{-1}$. This was not the case with the non-local potential. Higher values of $\Lambda$ correspond to a stronger cutoff for the semi-local potential compared to the non-local potential. Thus, we only need to take $\Lambda \approx 4.0 \, fm^{-1}$ to produce a potential with a spurious bound state.
%
\begin{table}[H]
\caption{Bound state values for deuteron, $\epsilon_d$, and the spurious, deeply bound state, $\epsilon_s$ in units MeV for two cutoffs in $\Lambda$}
\label{tab:RKE_bound_states}
\begin{ruledtabular}
\begin{tabular}{{>{\centering\arraybackslash}m{2in} >{\centering\arraybackslash}m{2in}>{\centering\arraybackslash}m{2in}}}
  $\Lambda \,\,\, [fm^{-1}]$ & $\epsilon_d$  [MeV] & $\epsilon_s$  [MeV] \\
  \colrule
  $3.0$ & $-2.224$ & - \\
  $4.0$ & $-2.225$ & $-1311.442$ \\
\end{tabular}
\end{ruledtabular}
\end{table}
%
\begin{figure}[H]
  \centering
  \includegraphics[width=14cm]{srg_contours_RKE_3}
   \hspace*{0.05\textwidth}%
  \caption{Contour of SRG evolved $V_{\lambda}(k,k')$ with $\Lambda=3.0\,fm^{-1}$, $G=T_{rel}$ (top) and $G=H_{D}$ (bottom) for several values of $\lambda$.}
  \label{fig:srg_contours_RKE_3}
\end{figure}
%
Figures \ref{fig:srg_contours_RKE_3} and \ref{fig:srg_contours_RKE_4} show the SRG evolution of the semi-local potential. These figures reinforce the result from before, namely that the evolution is generator dependent at high cutoffs. In Figure \ref{fig:srg_contours_RKE_3} where $\Lambda=3.0 \, fm^{-1}$, we see that the choice in SRG generator is not so important as before (the analogous non-local figure is Figure \ref{fig:srg_contours_Wendt_4}). Again, both generators decouple the potential in similar fashion. But at the higher cutoff of $\Lambda=4.0 \, fm^{-1}$ where the spurious, deeply bound state is present, the $G=T_{rel}$ and $G=H_D$ differ in the same manner as with the non-local potential. The Wegner generator safely decouples the spurious bound state from the low-momentum part of the potential whereas the $G=T_{rel}$ choice keeps the spurious bound state at low-momentum. This generator behavior is independent of how the potential is regulated. One deviation from the non-local case is that the Wegner generator decouples the spurious bound state at a lower value of momentum, $k \approx 1.1 \, fm^{-1}$, compared to $k \approx 1.75 \, fm^{-1}$ for the non-local case. It is not clear what leads to where the spurious bound state is decoupled. It is also not fully understood how to compare cutoff values for potentials that are regulated differently. These questions are left as future work.
%
\begin{figure}[H]
  \centering
  \includegraphics[width=14cm]{srg_contours_RKE_4}
   \hspace*{0.05\textwidth}%
  \caption{Contour of SRG evolved $V_{\lambda}(k,k')$ with $\Lambda=4.0\,fm^{-1}$, $G=T_{rel}$ (top) and $G=H_{D}$ (bottom) for several values of $\lambda$.}
  \label{fig:srg_contours_RKE_4}
\end{figure}
%
Figures \ref{fig:mag_contours_RKE_4_Wegner} and \ref{fig:mag_contours_RKE_4_Wilson} compare Magnus evolved potentials and SRG evolved potentials for $G=H_D$ and $G=T_{rel}$ respectively. The Magnus implementation matches the SRG result at lower truncations than in the non-local case. The agreement is good for $k_{max} \gtrsim 1$ with $k_{max}=0$ being the only exception. This is seen more explicitly in Figures \ref{fig:mag_diags_offdiags_RKE_4_Wegner} and \ref{fig:mag_diags_offdiags_RKE_4_Wilson} which show the diagonal and off-diagonal elements of the evolving potential. The Magnus implementation also matches the Wegner and $T_{rel}$ spurious bound state decoupling behavior as in the non-local case. These results reinforce the idea that the Magnus implementation matches SRG transformations for even the most stringent cases which should inspire confidence for using the Magnus expansion in investigating systems with intruder states in the IMSRG context.
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{mag_contours_RKE_4_Wegner}
   \hspace*{0.05\textwidth}%
  \caption{Contour of evolved $V_{\lambda}(k,k')$ with $\Lambda=4.0\,fm^{-1}$ and $G=H_{D}$ for several values of $\lambda$. Each row corresponds to a different truncation in the Magnus expansion (0, 1, 2, 4, 6) with the last row being the SRG result.}
  \label{fig:mag_contours_RKE_4_Wegner}
\end{figure}
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{mag_contours_RKE_4_Wilson}
   \hspace*{0.05\textwidth}%
  \caption{Contour of evolved $V_{\lambda}(k,k')$ with $\Lambda=4.0\,fm^{-1}$ and $G=T_{rel}$ for several values of $\lambda$. Each row corresponds to a different truncation in the Magnus expansion (0, 1, 2, 4, 6) with the last row being the SRG result.}
  \label{fig:mag_contours_RKE_4_Wilson}
\end{figure}
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{mag_diags_offdiags_RKE_4_Wegner}
   \hspace*{0.05\textwidth}%
  \caption{Diagonal and off-diagonal matrix elements of evolved $V_{\lambda}(k,k')$ with $G=H_{D}$ and $\Lambda=4.0 \, fm^{-1}$ for several values of $\lambda$ and $k_{max}$ compared to the SRG result.}
  \label{fig:mag_diags_offdiags_RKE_4_Wegner}
\end{figure}
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{mag_diags_offdiags_RKE_4_Wilson}
   \hspace*{0.05\textwidth}%
  \caption{Diagonal and off-diagonal matrix elements of evolved $V_{\lambda}(k,k')$ with $G=T_{rel}$ and $\Lambda=4.0 \, fm^{-1}$ for several values of $\lambda$ and $k_{max}$ compared to the SRG result.}
  \label{fig:mag_diags_offdiags_RKE_4_Wilson}
\end{figure}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work in progress}
\label{sec:future}

The Magnus expansion has trouble evolving potentials at very high cutoffs $\Lambda$, $20.0 \, fm^{-1}$ for the non-local potential and $9.0 \, fm^{-1}$ for the semi-local potential. For these cutoffs the size of $\Omega(s)$ increases drastically as $s$ is taken to larger values. (Note: this is independent of the step-size $ds$.) This leads to a numerical error in evaluating $e^{\Omega(s)}$ using either SciPy's expm function or the BCH formula. For this reason, we would like to understand the validity and convergence of the Magnus expansion and how this is affected by the cutoff. For all results in this section, $G=H_D$ and the non-local potential are used unless noted otherwise. \\

In Figure \ref{fig:omega_norms_Wendt_Wegner} we show the Frobenius norm of $\Omega(s)$ for three cutoffs $\Lambda$ and two extremes in $k_{max}$. This figure illustrates the problem as stated above: the size of $\Omega$ at high cutoffs leads to errors in matrix multiplication and exponentiation. At high $s$, the norm begins to flatten with the cutoffs of $4.0$ and $9.0 \, fm^{-1}$ allowing for a full evolution to $\lambda = 1.2 \, fm^{-1}$. However, with the cutoff of $20.0 \, fm^{-1}$, the norm jumps as $s \rightarrow 10^{-4}$. Notice that $||\Omega(s)||$ is generally independent of $k_{max}$, although at $\Lambda=20.0 \, fm^{-1}$ there is more sensitivity to $k_{max}$ with the larger truncation diverging first. Large $\Omega(s)$ leads to an increasing size from the nested commutator in the series in Eq. (\ref{eq:magnus_omega}).
%
\begin{figure}[H]
  \centering
  \includegraphics[width=10cm]{omega_norms_Wendt_Wegner}
   \hspace*{0.05\textwidth}%
  \caption{Frobenius norm of $\Omega(s)$ for $\Lambda = 4.0, \, 9.0,$ and $20.0 \, fm^{-1}$ and $k_{max}=2$ and $14$ as a function of $s$.}
  \label{fig:omega_norms_Wendt_Wegner}
\end{figure}
%
The convergence of the Magnus series depends on the SRG generator $\eta(s)$. In Figure \ref{fig:eta_norms_Wendt_Wegner} we plot the Frobenius norm of $\eta(s)$ for three cutoffs $\Lambda$ and two extremes in $k_{max}$ as before. We see that $||\eta(s)||$ decreases with $s$ for $\Lambda=4.0$ and $9.0 \, fm^{-1}$ but not for $\Lambda=20.0 \, fm^{-1}$. For this last case, the size of $\eta(s)$ increases up until $\lambda \sim 10.0 \, fm^{-1}$ until an error in expm is reached (where the two curves end). Also, it is not clear what causes the spike in $||\eta(s)||$ for $\Lambda=9.0 \, fm^{-1}$ at $s \sim 10^{-1}$. Checking this more closely, the spike occurs at $\lambda \approx 2.0 \, fm^{-1}$.
%
\begin{figure}[H]
  \centering
  \includegraphics[width=10cm]{eta_norms_Wendt_Wegner}
   \hspace*{0.05\textwidth}%
  \caption{Frobenius norm of $\eta(s)$ for $\Lambda = 4.0, \, 9.0,$ and $20.0 \, fm^{-1}$ and $k_{max}=2$ and $14$ as a function of $s$.}
  \label{fig:eta_norms_Wendt_Wegner}
\end{figure}
%
\begin{table}[H]
\caption{Values of $\int_{0}^{s_{max}} ||\eta(s)|| ds$ for various values in $\Lambda$ and $k_{max}$. If the full evolution is not reached ($\lambda = 1.2 \, fm^{-1}$) because of a numerical error, then we report the last value of $\lambda$.}
\label{tab:convergence_integral}
\begin{ruledtabular}
\begin{tabular}{{>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{1.5in}}}
  $\Lambda \, [fm^{-1}]$ & $k_{max}$ & $\lambda \, [fm^{-1}]$ & $\int_{0}^{s_{max}} ||\eta(s)|| ds$ \\
  \colrule
  $4.0$ & $2$ & $1.2$ & $6.0119$ \\
  $4.0$ & $14$ & $1.2$ & $6.0195$ \\
  $9.0$ & $2$ & $1.2$ & $422.5080$ \\
  $9.0$ & $14$ & $1.2$ & $401.1647$ \\
  $20.0$ & $2$ & $9.7645$ & $43.8078$ \\
  $20.0$ & $14$ & $10.9327$ & $24.3842$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

\newpage

% .....................................................................................................................................................................................................................................
\subsection{Convergence of the Magnus expansion}

As argued in \cite{Blanes:2009}, the size of $||\eta(s)||$ controls the convergence of the Magnus series. The value $\int_{0}^{s_{max}} ||\eta(s)|| ds$ provides a measure of how the Magnus expansion convergences, and thus gives a method to evaluate the validity of the expansion. In Table \ref{tab:convergence_integral} we provide several values of $\int_{0}^{s_{max}} ||\eta(s)|| ds$ for the various cases in $\Lambda$ and $k_{max}$. This reaffirms that the Magnus series diverges at higher cutoffs in $\Lambda$. The size of $\eta(s)$ becomes too large which accounts for the increasing size of $\Omega(s)$ leading to a numerical breakdown. In Table \ref{tab:convergence_integral} we provide the last value of $\lambda$ before an error occurs (only for $\Lambda = 20.0 \, fm^{-1}$). \\

There are a couple of important things to note in understanding this issue. One, the breakdown of the Magnus implementation is independent of the ODE solver. Using a built-in Python ODE solver (such as odeint), we recover the same error as with the Euler method. This implies that the ODE error on $\Omega(s)$ is the not the cause of the problem. Two, the large size of $\Omega(s)$ leads to problems with higher truncations and adaptive truncation methods in the Magnus expansion. Again, this is because the nested commutator in Eq. (\ref{eq:magnus_omega}) begins to grow in size leading to a numerical breakdown at lower values of $s$ than with the lower truncations. \\

In \cite{Blanes:2009}, Blanes argued that the Magnus expansion is convergent in the interval $s \in [0, \, T]$ where
%
\begin{eqnarray}
\label{eq:convergence_integral}
T = max \left \{ s \geq 0 \, : \, \int_{0}^{s} ||\eta(s')|| ds' \, < r_c \right \}.
\end{eqnarray}
%
The value of $r_c$ is debated but the consensus seems to be that $r_c = \pi$ (see \cite{Blanes:2009} for details). Nevertheless, this is a useful quantity to calculate for different cases in $\Lambda$ and $k_{max}$. In Figure \ref{fig:T_values_Wendt_Wegner} we show values of $T$ for the same cases as before with $r_c = \pi$. Note that in Eq. (\ref{eq:convergence_integral}) we use the flow parameter $s$, but in Figure \ref{fig:T_values_Wendt_Wegner} $T$ is given as a $\lambda$ value. A lower $T$ value in the figure means a further evolution can be safely reached. It is not surprising then that the $T$ values increase with $\Lambda$. Note that $T$ never drops below $2 \, fm^{-1}$ for any of the cases.

\newpage

%
\begin{figure}[H]
  \centering
  \includegraphics[width=10cm]{T_values_Wendt_Wegner}
   \hspace*{0.05\textwidth}%
  \caption{$T$ in units $fm^{-1}$ for $r_c=\pi$, $\Lambda = 4.0, \, 9.0,$ and $20.0 \, fm^{-1}$, and $k_{max}=2$ and $14$.}
  \label{fig:T_values_Wendt_Wegner}
\end{figure}
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{srg_gen_with_magnus_Wendt}
   \hspace*{0.05\textwidth}%
  \caption{Contour of evolved $V_{\lambda}(k,k')$ with $\Lambda=4.0\,fm^{-1}$ (top) and $\Lambda=9.0\,fm^{-1}$ (bottom) for the typical SRG approach (left) and the Magnus approach with $\eta^{SRG}(s)$ (right). Here $\lambda = 2.8 \, fm^{-1}$, $G=H_{D}$, and $k_{max}=6$.}
  \label{fig:srg_gen_with_magnus_Wendt}
\end{figure}
%
Another way to illustrate the problem is by using the SRG $\eta(s)$ for the Magnus expansion. In an ideal situation, the Magnus implementation matches the SRG approach exactly, and the use of the SRG $\eta(s)$ would not change the evolution in the Magnus implementation. We test this by SRG evolving, saving $\eta^{SRG}(s)$, and using this generator in Eq. (\ref{eq:magnus_omega}) for the Magnus evolution. We show $V_{\lambda}(k,k')$ evolved out to $\lambda=2.8 \, fm^{-1}$ with the typical SRG approach and Magnus implementation with the SRG generator for two cutoffs in Figure \ref{fig:srg_gen_with_magnus_Wendt}. The evolved potentials are almost identical at the lower cutoff of $4.0 \, fm^{-1}$ which is expected if everything in the Magnus implementation is working correctly. However, at the larger cutoff, there is a substantial difference in the evolution. This is a confusing result given that in Figure \ref{fig:mag_contours_Wendt_9_Wegner} we see good agreement between the SRG and $k_{max}=6$ Magnus. If anything, this shows that the SRG generator is not consistent between both approaches at high cutoffs, albeit a similar flow can be reached. \\

\textcolor{red}{Try more cutoffs $\Lambda$ using Epelbaum code} (chiraln3lo.f90) \cite{Epelbaum:2005}. \textcolor{red}{Step one: reproduce Wendt files.}

% .....................................................................................................................................................................................................................................
\subsection{Reducing the matrix size with decoupling}

As mentioned before, the SRG decouples the potential as it evolves in $s$. The low-momentum part of $V_s(k,k')$ is less sensitive to the high-momentum part as it evolves. From a practical standpoint, this can simplify calculations by pairing down the size of the matrix and removing high-momentum pieces. Here we try pairing down the matrix size as the potential evolves to hopefully improve the validity of the Magnus expansion. \\

First we consider $\Lambda = 9.0 \, fm^{-1}$. The method in pairing down the size of the matrices in the Magnus implementation is as follows: if $\frac{||H_{OD}(s_{i})||}{||H_{OD}(s_{j})||} < R$ where the indices i and j represent the latest step in the Euler method and the last index in which the ratio is less than $R$ respectively, then we pair down the size of $H(s)$ sub-blocks and restart the ODE solver. We choose the value of $R$ such that the matrices are reduced in a stable manner. We test three different criteria for this method and compare to the normal result from before. In Table \ref{tab:reduced_matrix_method_table} and Figures \ref{fig:reduced_matrix_omega_norms_V9}, \ref{fig:reduced_matrix_eta_norms_V9}, and \ref{fig:reduced_matrix_mag_diff_V9} we show results for these criteria with $k_{max}=6$, $G=H_D$, and $ds=10^{-5}$.
%
\begin{table}[H]
\caption{Values of the final Hamiltonian matrix size, $N$, and $\int_{0}^{s_{max}} ||\eta(s)|| ds$ for various methods in pairing down the matrix size and values in $\lambda$. Here the cut size is the integer in which each sub-block of the Hamiltonian is reduced once the condition $\frac{||H_{OD}(s_{i})||}{||H_{OD}(s_{j})||} < R$ is met. The first three rows show the results for the original, uncut Hamiltonian.}
\label{tab:reduced_matrix_method_table}
\begin{ruledtabular}
\begin{tabular}{{>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1in}}}
  Cut size & $R$ & $\lambda \, [fm^{-1}]$ & $N$ & $\int_{0}^{s_{max}} ||\eta(s)|| ds$ \\
  \colrule
   & & $2.8$ & $240$ & $6.9327$ \\
  $0$ & $0$ & $2.0$ & $240$ & $8.6020$ \\
   & & $1.2$ & $240$ & $440.8445$ \\ \hline
   & & $2.8$ & $200$ & $6.9327$ \\
   $5$ & $0.6$ & $2.0$ & $190$ & $8.6020$ \\
   & & $1.2$ & $180$ & $326.4978$ \\ \hline
   & & $2.8$ & $180$ & $6.9327$ \\
   $10$ & $0.5$ & $2.0$ & $180$ & $8.6020$ \\
   & & $1.2$ & $160$ & $11.7170$ \\ \hline
   & & $2.8$ & $180$ & $6.9327$ \\
   $15$ & $0.4$ & $2.0$ & $180$ & $8.6020$ \\
   & & $1.2$ & $150$ & $11.7170$ \\
\end{tabular}
\end{ruledtabular}
\end{table}
%
In Figure \ref{fig:reduced_matrix_omega_norms_V9} we see that the size of the $\Omega(s)$ matrix is substantially reduced for the later two cases in pairing down the Hamiltonian. The troughs in the curve correspond to where the matrices are cut in size. We see large jumps in the original and first case matching the spike in $||\eta(s)||$ as seen in Figure \ref{fig:reduced_matrix_eta_norms_V9}. Note that this spike is absent for the later two cases which keeps the value of $\int_{0}^{s_{max}} ||\eta(s)|| ds$ relatively low in comparison. \\

In Figure \ref{fig:reduced_matrix_mag_diff_V9} we show the absolute difference in the diagonal and off-diagonal matrix elements of $V_{\lambda}(k,k')$ between the original SRG case and the Magnus, reduced matrix case. There is better agreement between the original SRG result and the reduced matrix cases than with the original Magnus result, even more so at $\lambda = 1.2 \, fm^{-1}$. This is an encouraging result as the reduced matrix method preserves the intended evolution. Lastly, we check the accuracy of the evolved eigenvalues and phase shifts with respect to the original Hamiltonian in Table \ref{tab:reduced_matrix_V9_errors}. We see that the evolved and paired down Hamiltonians keep high accuracy in the deuteron bound state energy although two orders of magnitude worse than the uncut Magnus evolution; however, there is some deviation from the uncut phase shifts seen in Figure \ref{fig:reduced_matrix_phase_shifts_V9}.
%
\begin{figure}[H]
  \centering
  \includegraphics[width=10cm]{reduced_matrix_omega_norms_V9}
   \hspace*{0.05\textwidth}%
  \caption{Frobenius norm of $\Omega(s)$ for cut sizes of $0$, $5$, $10$, and $15$ and $R=0.0$, $0.6$, $0.5$, and $0.4$. Here $\Lambda=9.0 \, fm^{-1}$, $G=H_D$, and $k_{max}=6$.}
  \label{fig:reduced_matrix_omega_norms_V9}
\end{figure}
%
\begin{figure}[H]
  \centering
  \includegraphics[width=10cm]{reduced_matrix_eta_norms_V9}
   \hspace*{0.05\textwidth}%
  \caption{Frobenius norm of $\eta(s)$ for cut sizes of $0$, $5$, $10$, and $15$ and $R=0.0$, $0.6$, $0.5$, and $0.4$. Here $\Lambda=9.0 \, fm^{-1}$, $G=H_D$, and $k_{max}=6$.}
  \label{fig:reduced_matrix_eta_norms_V9}
\end{figure}
%
\newpage
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{reduced_matrix_mag_diff_V9}
   \hspace*{0.05\textwidth}%
  \caption{Difference in the diagonal and off-diagonal matrix elements of evolved $V_{\lambda}(k,k')$ with cut sizes of $0$, $5$, $10$, and $15$ and $R=0.0$, $0.6$, $0.5$, and $0.4$. Here $\Lambda=9.0 \, fm^{-1}$, $G=H_D$, and $k_{max}=6$.}
  \label{fig:reduced_matrix_mag_diff_V9}
\end{figure}
%
\begin{figure}[H]
  \centering
  \includegraphics[width=10cm]{reduced_matrix_phase_shifts_V9}
   \hspace*{0.05\textwidth}%
  \caption{$^{3}S_{1}$ phase shifts for cut sizes of $0$, $5$, $10$, and $15$ and $R=0.0$, $0.6$, $0.5$, and $0.4$. Here $\Lambda=9.0 \, fm^{-1}$, $G=H_D$, and $k_{max}=6$.}
  \label{fig:reduced_matrix_phase_shifts_V9}
\end{figure}
%
\newpage
%
\begin{table}[H]
\caption{Relative error in the deuteron bound state energy where $\tilde{\epsilon}$ denotes an evolved eigenvalue with SRG and Magnus, reduced matrix evolved Hamiltonians for $\Lambda=9.0 \, fm^{-1}$ and $\lambda=1.2 \, fm^{-1}$.}
\label{tab:reduced_matrix_V9_errors}
\begin{ruledtabular}
\begin{tabular}{{>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1in}}}
  $ $ & Cut size & $R$ & $N$ & $ |\frac{\epsilon_d-\tilde{\epsilon}_d}{\epsilon_d}| $ \\
  \colrule
  SRG & $0$ & $0.0$ & $240$ & $\num{2.428e-06}$ \\ \hline
  Magnus & $0$ & $0.0$ & $240$ & $\num{6.104e-13}$ \\
  Magnus & $5$ & $0.6$ & $180$ & $\num{8.781e-11}$ \\
  Magnus & $10$ & $0.5$ & $160$ & $\num{7.771e-11}$ \\
  Magnus & $15$ & $0.4$ & $150$ & $\num{3.727e-11}$ \\
\end{tabular}
\end{ruledtabular}
\end{table}
%
Next we consider $\Lambda = 20.0 \, fm^{-1}$. After testing this method to allow for a full Magnus evolution to $\lambda = 1.2 \, fm^{-1}$, we set $ds=10^{-6}$ and each $R$ value $0.2$ higher from before to ensure more cuts earlier in the flow. We keep the same number of terms in the Magnus expansion $k_{max} = 6$ and $G=H_D$. Recall that at this cutoff, we cannot fully evolve the uncut Hamiltonian. This is seen in Figure \ref{fig:reduced_matrix_omega_norms_V20} where $||\Omega(s)||$ diverges before fully evolving. Thus, the $||\eta(s)||$ curve in Figure \ref{fig:reduced_matrix_eta_norms_V20} for the uncut case ends before reaching the last value of $s$. Notice that early cuts in the Hamiltonian prevent $||\Omega(s)||$ from diverging. By removing the very high-momentum pieces of the Hamiltonian, we are able to achieve a full evolution in all three reduced matrix cases.
%
\begin{figure}[H]
  \centering
  \includegraphics[width=10cm]{reduced_matrix_omega_norms_V20}
   \hspace*{0.05\textwidth}%
  \caption{Frobenius norm of $\Omega(s)$ for cut sizes of $0$, $5$, $10$, and $15$ and $R=0.0$, $0.8$, $0.7$, and $0.6$. Here $\Lambda=20.0 \, fm^{-1}$, $G=H_D$, and $k_{max}=6$.}
  \label{fig:reduced_matrix_omega_norms_V20}
\end{figure}
%
\begin{figure}[H]
  \centering
  \includegraphics[width=10cm]{reduced_matrix_eta_norms_V20}
   \hspace*{0.05\textwidth}%
  \caption{Frobenius norm of $\eta(s)$ for cut sizes of $0$, $5$, $10$, and $15$ and $R=0.0$, $0.8$, $0.7$, and $0.6$. Here $\Lambda=20.0 \, fm^{-1}$, $G=H_D$, and $k_{max}=6$.}
  \label{fig:reduced_matrix_eta_norms_V20}
\end{figure}
%
\begin{figure}[H]
  \centering
  \includegraphics[width=15cm]{reduced_matrix_mag_diff_V20}
   \hspace*{0.05\textwidth}%
  \caption{Difference in the diagonal and off-diagonal matrix elements of evolved $V_{\lambda}(k,k')$ with cut sizes of $5$, $10$, and $15$ and $R=0.8$, $0.7$, and $0.6$. Here $\Lambda=20.0 \, fm^{-1}$, $G=H_D$, and $k_{max}=6$.}
  \label{fig:reduced_matrix_mag_diff_V20}
\end{figure}
%
The agreement with the SRG evolved result shows extreme sensitivity to the method in which the Hamiltonian is reduced. In Figure \ref{fig:reduced_matrix_mag_diff_V20}, we see that the choice of $R=0.8$ with a cut size of $5$ gives the best agreement with the SRG result for the evolved potential. This is reinforced by checking the accuracy on the deuteron bound state energy (Table \ref{tab:reduced_matrix_V9_errors}) where this case also shows the best agreement with the original, un-evolved Hamiltonian. Unlike with the lower cutoff of $\Lambda = 9.0 \, fm^{-1}$, the deuteron bound state is affected significantly with the Hamiltonian being paired down early in the flow equation suggesting that we are removing information at high-momentum that is not quite decoupled from the low-momentum. The phase shifts also show more sensitivity to the larger cut size of 15 whereas cut sizes of 5 and 10 keep the deviation consistent with the results for $\Lambda = 9.0 \, fm^{-1}$.
%
\begin{table}[H]
\caption{Relative error in the deuteron bound state energy where $\tilde{\epsilon}$ denotes an evolved eigenvalue with SRG and Magnus, reduced matrix evolved Hamiltonians for $\Lambda=20.0 \, fm^{-1}$ and $\lambda=1.2 \, fm^{-1}$.}
\label{tab:reduced_matrix_V20_errors}
\begin{ruledtabular}
\begin{tabular}{{>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1in}}}
  $ $ & Cut size & $R$ & $N$ & $ |\frac{\epsilon_d-\tilde{\epsilon}_d}{\epsilon_d}| $ \\
  \colrule
  SRG & $0$ & $0.0$ & $240$ & $\num{5.869e-06}$ \\ \hline
  Magnus & $5$ & $0.8$ & $160$ & $\num{3.651e-05}$ \\
  Magnus & $10$ & $0.7$ & $160$ & $\num{3.114e-02}$ \\
  Magnus & $15$ & $0.6$ & $150$ & $\num{8.211e-01}$ \\
\end{tabular}
\end{ruledtabular}
\end{table}
%
\begin{figure}[H]
  \centering
  \includegraphics[width=10cm]{reduced_matrix_phase_shifts_V20}
   \hspace*{0.05\textwidth}%
  \caption{$^{3}S_{1}$ phase shifts for cut sizes $5$, $10$, and $15$ and $R=0.8$, $0.7$, and $0.6$. Here $\Lambda=20.0 \, fm^{-1}$, $G=H_D$, and $k_{max}=6$.}
  \label{fig:reduced_matrix_phase_shifts_V20}
\end{figure}
%
\textcolor{red}{Other ideas: Smooth cutoff on matrices. Try evolving different operators.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}

\bibitem{Hergert:2017}
H.~Hergert, S.~K.~Bogner, J.~G.~Lietz, T.~D.~Morris, S.~Novario, N.~M.~Parzuchowski, and F.~Yuan,
Lect. Notes Phys. {\bf 936}, 477 (2017).

\bibitem{Wegner:1994}
F.~Wegner,
Ann. Phys. (Leipzig) {\bf 3}, 77 (1994).

\bibitem{Morris:2015}
T.~D.~Morris, N.~M.~Parzuchowski, and S.~K.~Bogner,
Phys. Rev. C {\bf 92}, 034331 (2015).

\bibitem{Glazek:2008}
S.~D.~Glazek and R.~J.~Perry,
Phys. Rev. D {\bf 78}, 045011 (2008).

\bibitem{Wendt:2011}
K.~A.~Wendt, R.~J.~Furnstahl, and R.~J.~Perry,
Phys. Rev. C {\bf 83}, 034005 (2011).

\bibitem{Magnus:1954}
W.~Magnus,
Communications on Pure and Applied Mathematics {\bf 7}, 649 (1954).

\bibitem{Blanes:2009}
S.~Blanes, F.~Casas, J.~Oteo, and J.~Ros,
Physics Reports {\bf 470}, 151 (2009).

\bibitem{Parzuchowski:2017}
N.~M.~Parzuchowski, S.~R.~Stroberg, P.~Navr{\'a}til, H.~Hergert, and S.~K.~Bogner,
Phys. Rev. C {\bf 96}, 034324 (2017).

\bibitem{Nogga:2005}
A.~Nogga, R.~G.~E. Timmermans, and U.~van~Kolck,
Phys. Rev. C {\bf 72}, 054006 (2005).

\bibitem{Bogner:2007}
S.~K.~Bogner, R.~J.~Furnstahl, and R.~J.~Perry,
Phys. Rev. C {\bf 75}, 061001(R) (2007).

\bibitem{Bogner:2010}
S.~K.~Bogner, R.~J.~Furnstahl, and A.~Schwenk,
Prog. Part. Nucl. Phys. {\bf 65}, 94 (2010).

\bibitem{Reinert:2018}
P.~Reinert, H.~Krebs, and E.~Epelbaum,
Eur. Phys. J. A {\bf 54}, 86 (2018).

\bibitem{Epelbaum:2005}
E.~Epelbaum, W.~Gl{\"o}ckle, and U.-G.~Mei{\ss}ner,
Nucl. Phys. A {\bf 747}, 362 (2005).

\end{thebibliography}

\end{document}

### 2019-05-02 Notes/Magnus/magnus_Jan08.tex
Added non-code files

% Notes on Magnus project
% Created 01/08/19 by A.T. (tropiano.4@osu.edu)
% Update: transitioning these notes into a draft of the eventual paper

\documentclass[preprintnumbers,floatfix,aps,prc,preprint,nofootinbib]{revtex4-1}

% Packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}
\usepackage[font=small,skip=0pt]{caption} % For captions on figures and tables
\usepackage{cellspace}
\usepackage{color}
\usepackage{enumerate}
\usepackage{epsfig}
\usepackage[figuresright]{rotating}
\usepackage{float}
\usepackage{hyperref} % For clickable links to sections within table of contents
\usepackage{graphicx}
\graphicspath{{Figures/}} % Setting the graphics path
\usepackage{physics} % For bra-ket notation
\usepackage{siunitx}

\newcommand{\eps}{\varepsilon}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Exploring the Magnus expansion and the in-medium similarity renormalization group}

\author{A.~J.~Tropiano$^{1}$, S.~K.~Bogner$^{2}$, R.~J.~Furnstahl$^{1}$}

\affiliation{
$^1$\mbox{Department of Physics, The Ohio State University, Columbus, OH 43210, USA}  \\
$^2$\mbox{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy,}  \\
    \mbox{Michigan State University, East Lansing, MI 48824, USA}}

\date{\today}

\begin{abstract}
\noindent{-- Test Magnus expansion SRG implementation on LO NN potential at high $\Lambda$. (Define SRG or IMSRG acronym in abstract.)}
\\
-- High $\Lambda$ leads to spurious bound states in spin triplet channels.
\\
-- Decouple spurious bound state(s) by using two approaches within the Magnus implementation to drive the Hamiltonian to band-diagonal, unitarily equivalent form.
\\
-- One choice of generator where the deep bound state is decoupled outside low-momentum and another where it is shifted to low-momentum.
\\
-- Deep bound state corrupts low-momentum physics.
\\
-- Connection to IMSRG intruder state problem.
\\
-- Confirm unitarity of Hamiltonian by evaluation of deuteron observables.
\\
-- Lastly, study operator evolution.
\end{abstract}

\maketitle

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}

\noindent{-- In recent years \textit{ab initio} methods have made strides in nuclear structure and reactions.}
\\
-- Realistic binding energies starting from NN and 3N forces have been calculated for many medium mass nuclei using different many-body methods.
\\
-- The in-medium similarity renormalization group (IMSRG) is one such method \cite{Hergert:2015awm, Hergert:2016iju}.
\\
-- The IMSRG separates energy scales in the nuclear Hamiltonian by decoupling the reference state from excited states to band- or block-diagonal form.
\\
-- One can use the decoupled Hamiltonian to solve the many-body Sch{\"o}dinger equation extracting specific eigenvalues and eigenstates which qualifies the IMSRG as an \textit{ab initio} method.
\\

\noindent{-- The IMSRG procedure requires solving a system of nonlinear, coupled differential equations which can often be stiff necessitating a high-order ODE solver.}
\\
-- In principle, the decoupled Hamiltonian (or any operator) is unitarily equivalent but the numerical error of solving the ODE can lead to error on observable quantities.
\\
-- Furthermore, the model spaces for IMSRG calculations can be extremely large.
\\
-- Evolving several operators is often impossible due to memory restrictions in storing several operators.
\\

\noindent{-- A variant of the IMSRG that utilizes the Magnus expansion can overcome these limitations.}
\\
-- We will refer to this as the Magnus implementation or simply Magnus.
\\
-- The Magnus solves for the unitary transformation directly whereas the IMSRG applies the transformation indirectly in steps of the differential flow equation.
\\
-- From the form of the transformation, the numerical error leaves the unitarity of the evolved Hamiltonian un-affected.
\\
-- By explicitly solving for the transformation, one can evolve several operators.
\\
-- The Magnus implementation has become a standard technique in IMSRG calculations as studies have targeted observables such as radii, electromagnetic moments and transitions, etc., requiring consistently evolved operators.
\\

\noindent{-- We test the Magnus implementation on chiral non-local NN potentials in free-space for several EFT cutoffs.}
\\
-- At high cutoffs, spin triplet channels feature spurious, deeply bound states from the strong, repulsive tensor force \cite{Nogga:2005hy}.
\\
-- These bound states are features of high-momentum physics and lie outside the range of the EFT.
\\
-- However, potentials with deeply bound states have shown sensitivity to SRG transformations \cite{Glazek:2008pg, Wendt:2011qj}.
\\
-- Details of the SRG transformation can cause the spurious bound state(s) to corrupt the low-momentum physics.
\\
-- An analogous problem occurs in IMSRG calculations for systems with intruder states where the intruder state can shift to the energy scale of the reference state in valence space.
\\
-- This severely distorts low-energy properties such as the ground state wave function.
\\
-- It is not understood how the IMSRG procedure evolves intruder state systems.
\\
-- Due to the prominence of the Magnus in IMSRG, one must first understand if the Magnus approach matches the typical approach for difficult systems before investigating the intruder state problem.
\\
-- NN potentials with spurious bound states offer a good test laboratory for the Magnus implementation to better understand if the Magnus is equivalent to the SRG approach. 
\\

\noindent{-- The past decade has seen a tremendous increase in the number of chiral NN potentials.}
\\
-- Interactions can now be built up to N5LO and feature several different regularization schemes.
\\
-- A natural question is to ask whether the SRG decouples these potentials in the same way.
\\
-- There is evidence of universal, low-momentum matrix elements as seen from evolving different potentials with SRG transformations or $V_{low~k}$ \cite{Dainton:2013axa}.
\\
-- There has also been renewed interest in chiral potentials at high-cutoffs but for a locally regulated potential \cite{Tews:2018sbi}.
\\
-- Given the growing number of chiral interactions, it would be interesting to re-examine these areas from an SRG standpoint.
\\
-- However, we would like to focus on a fixed comparison of the SRG and the Magnus approach as a first test, and therefore only consider evolving non-local LO NN potentials at various cutoffs.
\\
-- We leave the other areas as topics for future studies.
\\

\noindent{-- The rest of the paper is organized as follows:}
\\
-- In Sec. \ref{sec:formalism} we review the formalism of the SRG and the Magnus implementation emphasizing the major advantages of the Magnus.
\\
-- In Sec. \ref{sec:results} we test the Magnus implementation on high-cutoff NN potentials.
\\
-- We briefly review the SRG results for the same set of bare interactions and compare Magnus to SRG results.
\\
-- With the Magnus evolved operators, we calculate several observables and explore operator evolution.
\\
-- Lastly, we summarize our results in Sec. \ref{sec:conclusion}.
\\
-- We discuss the implications for the Magnus expansion within the IMSRG.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Formalism}
\label{sec:formalism}

\noindent{\textbf{SRG formalism}}
\\
-- In this section we describe the SRG in the context of decoupling any operator.
\\
-- The SRG decouples low- and high-momentum scales by applying a continuous unitary transformation $U(s)$ where $s=0 \rightarrow \infty$ is the flow parameter.
\\
-- The `dressed' or evolved operator is given by
%
\begin{eqnarray}
  \label{eq:srg_operator}
  O(s) = U(s) O(0) U^{\dagger}(s),
\end{eqnarray}
%
where $O(0)$ corresponds to the `bare' operator.
\\
-- Because $U(s)$ is unitary, the observables of the operator are preserved.
\\
-- In practice, the unitary transformation U(s) is not explicitly solved for; the evolved operator is given by a differential flow equation which is obtained by taking the derivative of Eqn. (\ref{eq:srg_operator}),
%
\begin{eqnarray}
  \label{eq:srg_flow}
  \frac{dO(s)}{ds} = [\eta(s), O(s)],
\end{eqnarray}
%
where $\eta(s)=\frac{dU(s)}{ds} U^{\dagger}(s) = -\eta^{\dagger}(s)$ is the anti-hermitian SRG generator.
\\
-- The generator is defined as a commutator,
%
\begin{eqnarray}
  \label{eq:srg_generator}
  \eta(s) = [G, H(s)],
\end{eqnarray}
%
where $G$ specifies the type of flow or form of the decoupled operator.
\\
-- To drive the operator to band-diagonal form, set $G=H_D(s)$, the diagonal of the Hamiltonian.
\\
-- This choice was implemented by Wegner in condensed matter physics \cite{Wegner:1994ab}.
\\
-- For notational convenience, we write the Wegner choice without the $s$ dependence in the rest of the paper.
\\
-- In a similar option used in nuclear physics, $G$ is set to the relative kinetic energy, $T_{rel}$, which also drives to band-diagonal form.
\\
-- In this paper, we consider both choices.
\\
-- Generally the flow equation (\ref{eq:srg_flow}) is solved up to some finite value of $s$ with a high-order ODE solver.
\\
-- It is convenient to define $\lambda \equiv s^{-1/4}$ which roughly measures the width of the diagonal in the decoupled operator.
\\

\noindent{\textbf{Magnus expansion formalism}}
\\
-- We now consider the Magnus implementation.
\\
-- Mathematically speaking, the Magnus expansion is a method for solving an initial value problem associated with a linear ordinary differential equation (ODE).
\\
-- Formal details of the Magnus expansion are discussed in \cite{Blanes:2009ab}.
\\
-- We will introduce the Magnus expansion in the context of SRG evolving any operator.
\\
-- In an intermediate step in deriving Eqn. (\ref{eq:srg_flow}), we have a linear ODE for $U(s)$,
%
\begin{eqnarray}
  \label{eq:unitary_trans}
  \frac{dU(s)}{ds} = \eta(s) U(s).
\end{eqnarray}
%
-- Magnus showed that one can solve the following equation with a solution $U(s)=e^{\Omega(s)}$ where $\Omega(s)$ is expanded as a power series, $\sum_{n}^{\infty} \Omega_n$ (referred to as the Magnus expansion or Magnus series).
\\
-- The terms of the series are given by integral expressions involving $\eta(s)$ (again, see \cite{Blanes:2009ab, Magnus:1954zz} for details).
\\
-- For our case, we focus on the formally exact derivative of $\Omega(s)$,
%
\begin{eqnarray}
  \label{eq:magnus_omega}
  \frac{d\Omega(s)}{ds} = \sum_{k=0}^{\infty} \frac{B_k}{k!} ad_{\Omega}^{k}(\eta),
\end{eqnarray}
%
where $B_k$ are the Bernoulli numbers, $ad_{\Omega}^{0}(\eta)=\eta(s)$, and $ad_{\Omega}^{k}(\eta)=[\Omega(s),ad_{\Omega}^{k-1}(\eta)]$.
\\
-- We integrate this differential equation to find $\Omega(s)$ and evaluate the unitary transformation directly.
\\
-- Then the evolved operator can be evaluated with the BCH formula:
%
\begin{eqnarray}
  \label{eq:bch}
  O(s) = e^{\Omega(s)} O e^{-\Omega(s)} = \sum_{k=0}^{\infty} \frac{1}{k!} ad_{\Omega}^{k}(O).
\end{eqnarray}
%
-- As $k \rightarrow \infty$ in both sums in Eqns. (\ref{eq:magnus_omega}) and (\ref{eq:bch}) the Magnus transformation matches the SRG transformation.
\\
-- We investigate several truncations $k_{max}$ in Eqn. (\ref{eq:magnus_omega}) and take many terms, $k_{max} \sim 25$, in Eqn. (\ref{eq:bch}).
\\
\textcolor{red}{-- Here or earlier (for the following bullets)? Better to motivate the Magnus in the introduction or easier to explain given mathematical detail?}
\\
-- There are significant advantages in the Magnus implementation.
\\
-- In the typical approach, the numerical error associated with solving the flow equation affects the accuracy of the observables for the evolved operator.
\\
-- Therefore, one must use a high-order ODE solver in integrating the flow equation (\ref{eq:srg_flow}).
\\
-- In the Magnus implementation, unitarity is guaranteed by the form of $U(s)$; in fact, one could solve Eqn. (\ref{eq:magnus_omega}) with a simple first-order Euler step-method keeping the same observables while decoupling the operator as desired.
\\
-- This offers a decent computational speed-up by avoiding a high-order solver.
\\
-- In this paper, we demonstrate this advantage by applying the Magnus implementation using the first-order Euler step-method.
\\
-- The second major advantage involves the evolution of multiple operators.
\\
-- In many other situations, one may be interested in evolving several operators at a time.
\\
-- In the SRG procedure, we would have another set of coupled equations in Eqn. (\ref{eq:srg_flow}), drastically increasing memory usage.
\\
-- Each additional operator increases the set of equations - say $N$ equations - by another factor of $N$.
\\
-- In the Magnus, one only needs $\Omega(s)$ to consistently evolve several operators.
\\
-- We avoid the cost in memory by directly constructing $U(s)=e^{\Omega(s)}$.
\\
-- This is especially useful in IMSRG calculations where the model space can be very large.
\\
-- In the next section, we discuss results from Magnus evolved large-cutoff potentials focusing on the flow of the potential, observables, and operator evolution.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}

\noindent{\textbf{Evolution of potentials}}
\\
-- In this section, we Magnus evolve LO non-local potentials in the $^{3}S_1-^{3}D_1$ channel at cutoffs of $\Lambda=4$, $9$, and $20 \, fm^{-1}$.
\\
\textcolor{red}{-- Option: add new regularization schemes?}
\\
-- For the higher two cutoffs, the potentials have one and two spurious, deeply bound states, respectively.
\\
-- In \cite{Wendt:2011qj}, potentials at large-cutoffs were SRG evolved with $G=H_D$ and $G=T_{rel}$.
\\
-- At lower cutoffs ($\Lambda \lesssim 4 \, fm^{-1}$), potential matrix elements flowed toward a decoupled, universal form independent of $G$, that is the low-momentum matrix elements approached the same values as $\lambda \rightarrow 0$.
\\
-- However, SRG evolution differed for potentials featuring one or more spurious bound states.
\\
-- With one or more spurious bound states and $G=T_{rel}$, the SRG transformation shifted a spurious bound state toward the low-momentum block corrupting the low-energy physics (e.g., the deuteron wave function, phase shifts, etc.).
\\
-- For $G=H_D$, the SRG decoupled the spurious bound state outside the low-momentum block matching the flow to universal low-momentum form independent of the cutoff $\Lambda$.
\\
-- Similar behavior could be prevalent in IMSRG calculations where the choice in generator affects evolution of many-body Hamiltonians with intruder states as it does for these NN potentials in free-space SRG.
\\

\noindent{-- First, we compare Magnus to SRG evolution for large cutoff potentials with $G=H_D$ and $G=T_{rel}$.}
\\
-- Figures \ref{fig:magnus_contours_Wendt_Lamb9_Wegner} and \ref{fig:magnus_contours_Wendt_Lamb9_T} show potential matrix element evolution for three truncations in the sum of Eqn. \ref{eq:magnus_omega} up to three values of $\lambda$ with $\Lambda=9 \, fm^{-1}$.
\\
-- At this cutoff, the potential has one spurious bound state at about $-2000$ MeV.
\\
%	
\begin{figure}
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=10cm]{magnus_contours_Wendt_Lamb9_Wegner}
  \hspace*{0.05\textwidth}
  \caption{Contours of Magnus evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=H_{D}$ for $\lambda=2.8$ (left), $2.0$ (middle), and $1.2$ (right) $fm^{-1}$ and truncations in the Magnus $k_{max}=2$ (top), $6$ (middle), and $10$ (bottom).}
  \label{fig:magnus_contours_Wendt_Lamb9_Wegner}
\end{figure}
%
\begin{figure}
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=10cm]{magnus_contours_Wendt_Lamb9_T}
  \hspace*{0.05\textwidth}
  \caption{Contours of Magnus evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=T_{rel}$ for $\lambda=2.8$ (left), $2.0$ (middle), and $1.2$ (right) $fm^{-1}$ and truncations in the Magnus $k_{max}=2$ (top), $6$ (middle), and $10$ (bottom).}
  \label{fig:magnus_contours_Wendt_Lamb9_T}
\end{figure}
%
-- We see the same behavior with the Magnus in comparison to the SRG in \cite{Wendt:2011qj} for both generators.
\\
-- For $G=H_D$, there is a deep, blue dot in the middle of the contours at $k \approx 1.75 \, fm^{-1}$ which corresponds to the decoupled spurious bound state.
\\
-- We have checked other cutoffs and found that the evolved low-momentum matrix elements are independent of the cutoff $\Lambda$ implying a low-momentum, universal form.
\\
-- The only major difference in Magnus or SRG evolution for various cutoffs is where spurious bound state(s) are decoupled.
\\
-- This decoupling feature depends on the details of the starting interaction (i.e., the value of the bound state).
\\
%
\begin{figure}
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=14cm]{evolved_diags_Wendt_Lamb9_Wegner}
  \hspace*{0.05\textwidth}
  \caption{Diagonal (top row) and far off-diagonal (bottom row) matrix elements of evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=H_{D}$ for several values of $\lambda$ and truncations in the Magnus series $k_{max}$.}
  \label{fig:evolved_diags_Wendt_Lamb9_Wegner}
\end{figure}
%
\noindent{-- Furthermore, it is dependent on the momentum mesh on which the potential is generated.}
\\
-- At $k_{max}=2$ and $\lambda=2.0 \, fm^{-1}$, we see large, positive off-diagonal values along the momentum axes where the deep bound state is decoupled.
\\
-- Solving for $\Omega(s)$ at a low truncation leads to less desirable flow, that is, the transformation $U(s)$ is not quite the same transformation as the SRG $U(s)$.
\\
-- However, the Magnus still guarantees the unitarity of $U(s)$, and we see a consistent decoupling of the spurious bound state in each row independent of $k_{max}$.
\\
-- For $G=T_{rel}$, the spurious bound state is shifted up along the diagonal, and the low-momentum block drops to extremely negative values.
\\
-- Here, the spurious bound state corrupts the low-momentum block matching the SRG evolution of different cutoffs, thus breaking universality.
\\
%
\begin{figure}
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=14cm]{evolved_diags_Wendt_Lamb9_T}
  \hspace*{0.05\textwidth}
  \caption{Diagonal (top row) and far off-diagonal (bottom row) matrix elements of evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=T_{rel}$ for several values of $\lambda$ and truncations in the Magnus series $k_{max}$.}
  \label{fig:evolved_diags_Wendt_Lamb9_T}
\end{figure}
%
\noindent{-- Figures \ref{fig:evolved_diags_Wendt_Lamb9_Wegner} and \ref{fig:evolved_diags_Wendt_Lamb9_T} show a more quantitative depiction of the evolved potentials.}
\\
-- The black dotted line corresponds to the SRG evolved potential whereas the other lines are Magnus evolved potentials for different $k_{max}$ for diagonal and far-off diagonal matrix elements of $V_{\lambda}(k,k')$.
\\
-- It is clear in these figures that the Magnus matches the SRG at $k_{max} \gtrsim 6$.
\\
-- In Figure \ref{fig:evolved_diags_Wendt_Lamb9_Wegner} the decoupled spurious bound state is seen as the large negative drop in the curves at $k \approx 1.75 \, fm^{-1}$.
\\
\textcolor{red}{-- Unnecessary?
\\
-- From applying the Magnus in several other cases, we have seen that harder potentials cause convergence issues in the Magnus expansion due to the relative size of the SRG generator $\eta(s)$.
\\
-- To avoid convergence issues we can take a smaller step-size.
\\
-- In the previous cases (and all other cases unless specified otherwise), we take $ds=10^-5$.}
\\

\noindent{\textbf{Observables}}
\\
%
\begin{table}
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \caption{Relative error on the deuteron bound state energy and the root mean square of eigenvalues where $\tilde{\epsilon}$ denotes an eigenvalue of an SRG or Magnus evolved Hamiltonian for $\Lambda=9 \, fm^{-1}$ and $\lambda=1.2 \, fm^{-1}$.}
  \label{tab:energies}
  \begin{ruledtabular}
    \begin{tabular}{{>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{2in}}}
      $  $ & $G$ & $ |\frac{\epsilon_d-\tilde{\epsilon}_d}{\epsilon_d}| $ & $\sqrt{\frac{1}{N} \, \sum_{i}^{N} (\tilde{\epsilon}_i-\epsilon_i)^2}$   [MeV] \\
      \colrule
      SRG & $ $ & $\num{1.165e-5}$ & $\num{3.016e-4}$ \\
      Magnus, $k_{max}=2$ & $H_D$ & $\num{5.010e-10}$ & $\num{4.097e-9}$ \\
      Magnus, $k_{max}=14$ & $ $ & $\num{1.206e-11}$ & $\num{3.950e-10}$ \\ \hline
      SRG & $ $ & $\num{1.003e-4}$ & $\num{9.791e-5}$ \\
      Magnus, $k_{max}=2$ & $T_{rel}$ & $\num{7.775e-8}$ & $\num{6.376e-8}$ \\
      Magnus, $k_{max}=14$ & $ $ & $\num{7.607e-8}$ & $\num{6.359e-8}$ \\
    \end{tabular}
  \end{ruledtabular}
\end{table}
%
-- To emphasize the two major advantages of the Magnus implementation, we now consider evolved observables and operators for the remainder of the section.
\\
-- Table \ref{tab:energies} shows the relative error on the deuteron bound state energy and root mean square of all eigenvalues for several evolution cases.
\\
-- The Magnus approach preserves energies to several orders of magnitude better than the typical SRG approach.
\\
-- Again, despite the inclusion of several more terms in the sum of Eqn. \ref{eq:magnus_omega}, we see consistent errors between $k_{max}=2$ and $14$ because of the guaranteed unitarity of $U(s)=e^{\Omega(s)}$
\\
-- The errors on the Magnus energies are within the region of floating-point error whereas the SRG compounds error in solving the ODE \ref{eq:srg_flow}.
\\
-- We have also checked the phase shifts from the evolved potentials match the bare potentials in all cases for Magnus and SRG evolution.
\\ 
-- Next we show the evolved deuteron wave function for several cases.
\\
-- Figure \ref{fig:momentum_dist_Wendt_Lamb9} shows the deuteron momentum probability density, $|\phi(k)|^2$, on a semi-log scale as a function of momentum for both band-diagonal generators.
\\
-- With $G=H_D$, the evolved and un-evolved momentum distributions agree for low-momentum whereas $G=T_{rel}$ significantly distorts the distribution from the presence of the spurious bound state in the $\Lambda=9 \, fm^{-1}$ potential.
\\
-- This illustrates the advantage of the Wegner generator: the spurious bound state at high-momentum does not affect the low-momentum physics under the SRG transformation.
\\
-- In all cases of Magnus and SRG evolution, we can consistently evolve wave functions and operators to make reliable calculations of observables.
\\
-- To demonstrate this, we calculate the deuteron RMS radius and quadrupole moment with the $\Lambda=9 \, fm^{-1}$ potential using the Magnus implementation with the Wegner generator.
\\
-- The initial values of the chiral potential are $r_d = 2.022 \, fm$ and $Q_d = 0.287 \, fm^2$ compared to the experimental values $r_d^{exp} = 2.141 \, fm$ and $Q_d^{exp} = 0.286 \, fm^2$. 
\\
-- We have checked for several cases with the Magnus and found near-perfect agreement to the initial values of both observables.
\\

\noindent{\textcolor{red}{UPDATED UP TO HERE 04/03/19}}
\\
\begin{figure}
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=10cm]{momentum_dist_Wendt_Lamb9}
  \hspace*{0.05\textwidth}
  \caption{Momentum probability densities of the deuteron comparing the un-evolved wavefunction (black dotted line), SRG evolved wavefunction (blue dashed line), and two Magnus evolved wavefunctions with truncations $2$ and $14$ (green and red dash-dotted lines, respectively) where $\lambda=1.2 \, fm^{-1}$. The left panel shows evolution with $G=H_{D}$ and the right with $G=T_{rel}$. Here $\Lambda=9 \, fm^{-1}$.}
  \label{fig:momentum_dist_Wendt_Lamb9}
\end{figure}
%
\noindent{-- RMS radius and quadrupole moment of deuteron.}
\\
-- Values from initial potential ($\Lambda=9 \, fm^{-1}$):
\begin{itemize}
  \item $r_d = 2.022 \, fm$ (using momentum-space derivatives)
  \item $r_d = 2.465 \, fm$ (using Fourier transforms)
  \item $Q_d = 0.287 \, fm^2$ (using momentum-space derivatives)
\end{itemize}
-- Values from standard Magnus evolved potential ($G=H_D$, $\lambda=1.2 \, fm^{-1}$, and $k_{max}=6$):
\begin{itemize}
  \item $r_d = 2.022 \, fm$ (using momentum-space derivatives)
  \item $Q_d = 0.287 \, fm^2$ (using momentum-space derivatives)s
  \item Note: we apply $U^{\dagger}(s) U(s)$ to wave function to compute unitarily equivalent observables
\end{itemize}
-- Experimental values:
\begin{itemize}
  \item $r_d = 2.141 \, fm$
  \item $Q_d = 0.286 \, fm^2$
\end{itemize}
%
\textbf{Evolution of operators}
%
\begin{figure}[H]
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=14cm]{momentum_proj_operator_contours_q0,31_magnus_Wendt_Lamb9}
  \hspace*{0.05\textwidth}
  \caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ Magnus evolving in $\lambda$ right to left with $G=H_D$ (top) and $G=T_{rel}$ (bottom). Here $q=0.31 \, fm^{-1}$, $\Lambda=9 \, fm^{-1}$, and $k_{max}=6$.}
  \label{fig:momentum_proj_operator_contours_q0,31_magnus_Wendt_Lamb9}
\end{figure}
%
\begin{figure}[H]
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=10cm]{momentum_proj_difference_q0,31_magnus_Wendt_Lamb9}
  \hspace*{0.05\textwidth}
  \caption{Difference in evolved and bare matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ Magnus evolving to $\lambda=1.2 \, fm^{-1}$ right to with $G=H_D$ (left) and $G=T_{rel}$ (right). Here $q=0.31 \, fm^{-1}$, $\Lambda=9 \, fm^{-1}$, and $k_{max}=6$.}
  \label{fig:momentum_proj_operator_difference_q0,31_magnus_Wendt_Lamb9}
\end{figure}
%
\begin{figure}[H]
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=14cm]{momentum_proj_operator_contours_q3,04_magnus_Wendt_Lamb9}
  \hspace*{0.05\textwidth}
  \caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ Magnus evolving in $\lambda$ right to left with $G=H_D$ (top) and $G=T_{rel}$ (bottom). Here $q=3.04 \, fm^{-1}$, $\Lambda=9 \, fm^{-1}$, and $k_{max}=6$.}
  \label{fig:momentum_proj_operator_contours_q3,04_magnus_Wendt_Lamb9}
\end{figure}
%
\begin{figure}[H]
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=10cm]{momentum_proj_difference_q3,04_magnus_Wendt_Lamb9}
  \hspace*{0.05\textwidth}
  \caption{Difference in evolved and bare matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ Magnus evolving to $\lambda=1.2 \, fm^{-1}$ with $G=H_D$ (left) and $G=T_{rel}$ (right). Here $q=3.04 \, fm^{-1}$, $\Lambda=9 \, fm^{-1}$, and $k_{max}=6$.}
  \label{fig:momentum_proj_operator_difference_q3,04_magnus_Wendt_Lamb9}
\end{figure}
%
\begin{figure}[H]
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=14cm]{r2_operator_contours_magnus_Wendt_Lamb9}
  \hspace*{0.05\textwidth}
  \caption{Matrix elements of $\mel{k}{r^2}{k'}$ Magnus evolving in $\lambda$ right to left with $G=H_D$ (top) and $G=T_{rel}$ (bottom). Here $\Lambda=9 \, fm^{-1}$ and $k_{max}=6$.}
  \label{fig:r2_operator_contours_srg_Wendt_Lamb9}
\end{figure}
%
\begin{figure}[H]
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=10cm]{r2_difference_magnus_Wendt_Lamb4}
  \hspace*{0.05\textwidth}
  \caption{Difference in evolved and bare matrix elements of $\mel{k}{r^2}{k'}$ Magnus evolving to $\lambda=1.2 \, fm^{-1}$ with $G=H_D$ (left) and $G=T_{rel}$ (right). Here $\Lambda=4 \, fm^{-1}$ and $k_{max}=6$.}
  \label{fig:r2_difference_magnus_Wendt_Lamb4}
\end{figure}
%
\begin{figure}[H]
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=10cm]{r2_difference_magnus_Wendt_Lamb9}
  \hspace*{0.05\textwidth}
  \caption{Difference in evolved and bare matrix elements of $\mel{k}{r^2}{k'}$ Magnus evolving to $\lambda=1.2 \, fm^{-1}$ with $G=H_D$ (left) and $G=T_{rel}$ (right). Here $\Lambda=9 \, fm^{-1}$ and $k_{max}=6$. (Note the difference in color bar scales.)}
  \label{fig:r2_difference_magnus_Wendt_Lamb9}
\end{figure}
%
\begin{figure}[H]
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=14cm]{r2_integrand_contours_magnus_Wendt_Lamb9}
  \hspace*{0.05\textwidth}
  \caption{Integrand of $\bra{\Psi}\ket{k} \mel{k}{r^2}{k'} \bra{k'}\ket{\Psi}$ Magnus evolving the wave function in $\lambda$ right to left with $G=H_D$ (top) and $G=T_{rel}$ (bottom). Here $\Lambda=9 \, fm^{-1}$, $k_{max}=6$, and the operator $r^2$ is un-evolved.}
  \label{fig:r2_integrand_contours_srg_Wendt_Lamb9}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:conclusion}

\noindent{-- Summarize.}
\\
-- Where does the Magnus implementation differ from the SRG result?
\\
-- Connection to the IMSRG intruder state problem.
\\
-- Outlook.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{tropiano_srg}

\end{document}

### 2019-05-02 Potentials/vsrg_macos/load_save_potentials.py

@@ -115,11 +115,11 @@ def load_potential(kvnn, channel, kmax, kmid, ntot, method='initial', \
     
         if generator == 'Block-diag':
             
-            vnn_file = 'vnn_%s_kvnn_%s_%s_%s%.2f_lambda%.1f'%(channel, \
+            vnn_file = 'vnn_%s_kvnn_%s_%s_%s%.2f_lambda%.1f.out'%(channel, \
                         kvnn_string, method, generator, lambda_bd, lamb)
         else: 
             
-            vnn_file = 'vnn_%s_kvnn_%s_%s_%s_lambda%.1f'%(channel, 
+            vnn_file = 'vnn_%s_kvnn_%s_%s_%s_lambda%.1f.out'%(channel, 
                         kvnn_string, method, generator, lamb)
     
     chdir(potential_directory)
@@ -346,7 +346,7 @@ def convert2MeV(k_array, k_weights, V, coupled_channel=False):
     row,col = np.meshgrid(gp*np.sqrt(gw),gp*np.sqrt(gw))
     
     # Multiply the potential by 2/pi*row*col gives fm^-2 conversion
-    V *= 2/np.pi*row*col
+    V = V*2/np.pi*row*col
     
     # Multiply by h-bar^2 / M [MeV fm^2] to obtain MeV units
     return V*hbar_sq_over_M

### 2019-05-02 srg_wegner.py

@@ -34,6 +34,7 @@ class SRG(object):
         
         return A @ B - B @ A
 
+    # TEST THE OLD VECTOR2MATRIX FUNCTIONS HERE
     
     def vector2matrix(self, B):
         '''Takes the vector of a upper triangle matrix and returns the full 

### 2019-05-02 evolve_hamiltonian.py
Updates to SRG codes

@@ -42,6 +42,9 @@ def main(kvnn, channel, kmax, kmid, ntot, method, generator, lambda_array, \
     T0_matrix = lp.load_kinetic_energy(kvnn, channel, kmax, kmid, ntot)     
     k_array, k_weights = lp.load_momentum(kvnn, channel, kmax, kmid, ntot)
     
+    # h-bar^2 / M [MeV fm^2] for conversion of MeV to fm^-2
+    hbar_sq_over_M = 41.47
+    
     # Initialize SRG class
     if generator == 'Wegner':
         
@@ -79,9 +82,9 @@ def main(kvnn, channel, kmax, kmid, ntot, method, generator, lambda_array, \
         # Save evolved potential for each lambda value
         for lamb in lambda_array:
 
-            Hs_matrix = d[lamb]
-            # Subtract off kinetic energy
-            Vs_matrix = Hs_matrix - T0_matrix
+            Hs_matrix = d[lamb] # Units are fm^-2 here
+            # Subtract off kinetic energy (need to convert from MeV to fm^-2)
+            Vs_matrix = Hs_matrix - T0_matrix/hbar_sq_over_M
             # Save evolved potential
             lp.save_potential(k_array, k_weights, Vs_matrix, kvnn, channel, kmax, 
                               kmid, ntot, method, generator, lamb, lambda_bd)
@@ -128,4 +131,4 @@ if __name__ == '__main__':
     
     # Run evolution without saving
     #d = main(kvnn, channel, kmax, kmid, ntot, method, generator, \
-    #         lambda_array, lambda_bd, save=False)
+             #lambda_array, lambda_bd, save=False)

### 2019-05-02 srg_wegner.py

@@ -34,32 +34,82 @@ class SRG(object):
         
         return A @ B - B @ A
 
-    # TEST THE OLD VECTOR2MATRIX FUNCTIONS HERE
+
+    def matrix2vector(self, A):
+        '''Takes the top right of the matrix A (including the diagonal) and 
+        reshapes it into a vector B of dimension N*(N+1)/2.'''
     
+        # Dimension of matrix
+        N = len(A)
+        # Dimension of vectorized matrix
+        n = int(N*(N+1)/2)
+        # Initialize vectorized matrix
+        B = np.zeros(n)
+    
+        first = 0
+        last = N
+    
+        for i in range(N):
+        
+            B[first:last] = A[i][i:]
+            first = last
+            last += N-i-1
+
+        return B
+
+  
     def vector2matrix(self, B):
-        '''Takes the vector of a upper triangle matrix and returns the full 
-        matrix - i.e. the reverse of using np.triu_indices(). Use only for
-        hermitian matrices.'''
+        '''Takes the vector of a top right matrix and returns the full matrix. (USE
+        ONLY FOR HERMITIAN MATRICES.)'''
+        
+        # Dimension of the vectorized matrix
+        n = len(B)
+        # Dimension of matrix (given by solving N*(N+1)/2 = n)
+        N = int( (-1 + np.sqrt(1+8*n) ) / 2 )
+        # Initialize matrix
+        A = np.zeros((N,N))
+        
+        # Build upper half of A with diagonal
+
+        first = 0
+        last = N
+
+        for i in range(N):
+
+            A[i,i:] = B[first:last]
+            first = last
+            last += N-i-1
+
+        # Reflect upper half to lower half to build full matrix
+        # [np.transpose(A)-np.diag(np.diag(A))] is the lower half of A excluding 
+        # the diagonal
+        return A+(np.transpose(A)-np.diag(np.diag(A)))
+    
+    
+    #def vector2matrix(self, B):
+        #'''Takes the vector of a upper triangle matrix and returns the full 
+        #matrix - i.e. the reverse of using np.triu_indices(). Use only for
+        #hermitian matrices.'''
         
         # Arguments
         
         # B (NumPy array): Vectorized top right piece of a square matrix
         
         # Dimension of matrix (given by solving N*(N+1)/2 = n)
-        N = self.N
+        #N = self.N
     
         # Indices of the upper right triangle of A
[…]

### 2019-05-03 SRG_codes/srg_block_diagonal.py
Various updates
Updates to SRG codes, README file, and started operator evolution notebook and deuteron script.

@@ -1,7 +1,7 @@
 # Created 05/01/19 by A.T. (tropiano.4@osu.edu)
 
-# SRG code: Evolves Hamiltonian to band-diagonal, decoupled form with parameter 
-# s using the Wegner generator.
+# SRG code: Evolves Hamiltonian to block-diagonal, decoupled form with 
+# parameter s.
 
 
 import numpy as np
@@ -11,13 +11,19 @@ from scipy.integrate import odeint
 class SRG(object):
     
     
-    def __init__(self, H0_matrix):
-        '''Saves the initial Hamiltonian in units fm^-2 and dimension of the 
-        matrix.'''
+    def __init__(self, H0_matrix, lambda_bd, k_array, coupled_channel):
+        '''Saves the initial Hamiltonian in units fm^-2 and dimension of the
+        matrix. Also creates and saves the projection matrices for the block-
+        diagonal generator.'''
         
         # Arguments
         
         # H0_matrix (NumPy array): Hamiltonian matrix in units MeV
+        # lambda_bd (float): Lambda value for block-diagonal decoupling (e.g. 
+        # 2.00 fm^-1)
+        # k_array (NumPy array): Momentum array
+        # coupled_channel (Boolean): Value corresponding to whether the 
+        # potential is coupled channel or not
         
         # h-bar^2 / M [MeV fm^2]
         hbar_sq_over_M = 41.47
@@ -26,6 +32,25 @@ class SRG(object):
         self.H0_matrix = H0_matrix / hbar_sq_over_M
         # Save dimension of matrix
         self.N = len(H0_matrix)
+        
+        # Array of True and False
+        bool_array = k_array < lambda_bd
+        # Length of momentum array
+        n = len(k_array)
+        
+        # Build projection operators
+        # Identity matrix for k < lambda_bd
+        p = np.diag(np.ones(n)*bool_array)
+        # Opposite of p: Identity matrix for k > decouple
+        q = np.identity(n)-p
+        # Construct full matrices for coupled channel vnn if necessary
+        if coupled_channel:
+            o = np.zeros((n,n))
+            self.P = np.vstack((np.hstack((p,o)),np.hstack((o,p))))
+            self.Q = np.vstack((np.hstack((q,o)),np.hstack((o,q))))
+        else:
+            self.P = p
+            self.Q = q
 
     
     def commutator(self, A, B):
@@ -33,83 +58,57 @@ class SRG(object):
         NumPy arrays.'''
         
         return A @ B - B @ A
-
-
+    
+    
[…]

### 2019-05-03 SRG_codes/srg_kinetic_energy.py

@@ -37,30 +37,55 @@ class SRG(object):
         return A @ B - B @ A
     
     
+    def matrix2vector(self, A):
+        '''Takes the upper triangle of the matrix A (including the diagonal) 
+        and reshapes it into a vector B of dimension N*(N+1)/2.'''
+    
+        # Dimension of matrix
+        N = self.N
+        # Dimension of vectorized matrix
+        n = int(N*(N+1)/2)
+        
+        # Initialize vectorized matrix
+        B = np.zeros(n)
+    
+        a = 0
+        b = N
+    
+        for i in range(N):
+        
+            B[a:b] = A[i][i:]
+            a = b
+            b += N-i-1
+
+        return B
+
+ 
     def vector2matrix(self, B):
         '''Takes the vector of a upper triangle matrix and returns the full 
-        matrix - i.e. the reverse of using np.triu_indices(). Use only for
-        hermitian matrices.'''
-        
-        # Arguments
-        
-        # B (NumPy array): Vectorized top right piece of a square matrix
+        matrix. Use only for hermitian matrices.'''
         
         # Dimension of matrix (given by solving N*(N+1)/2 = n)
         N = self.N
     
-        # Indices of the upper right triangle of A
-        i,j = np.triu_indices(N)
-    
         # Initialize matrix
         A = np.zeros((N,N))
     
-        # Set upper right triangle
-        A[i,j] = B
-        # Using hermiticity reflect for the lower triangle
-        A[j,i] = B
-    
-        return A
+        # Build upper half of A with diagonal
+
+        a = 0
+        b = N
+
+        for i in range(N):
+
+            A[i,i:] = B[a:b]
+            a = b
+            b += N-i-1
+
+        # Reflect upper half to lower half to build full matrix
+        # [np.transpose(A)-np.diag(np.diag(A))] is the lower half of A 
+        # excluding the diagonal
+        return A+(np.transpose(A)-np.diag(np.diag(A)))
     
     
     def derivs(self, Hs_vector, s):
@@ -70,9 +95,6 @@ class SRG(object):
         
         # Hs_vector (NumPy array): Solution vector (which is a function of s)
         # s (float): SRG flow parameter
-        
-        # Dimension of matrix
-        N = self.N
         
         # Matrix of the solution vector
         Hs_matrix = self.vector2matrix(Hs_vector)
@@ -86,10 +108,10 @@ class SRG(object):
         # RHS of flow equation in matrix form
[…]

### 2019-05-03 SRG_codes/srg_wegner.py

@@ -1,29 +1,22 @@
 # Created 05/01/19 by A.T. (tropiano.4@osu.edu)
 
-# SRG code: Evolves Hamiltonian to block-diagonal, decoupled form with 
-# parameter s.
+# SRG code: Evolves Hamiltonian to band-diagonal, decoupled form with parameter 
+# s using the Wegner generator.
 
 
 import numpy as np
 from scipy.integrate import odeint
-  
+
 
 class SRG(object):
     
     
-    def __init__(self, H0_matrix, lambda_bd, k_array, coupled_channel):
-        '''Saves the initial Hamiltonian in units fm^-2 and dimension of the
-        matrix. Also creates and saves the projection matrices for the block-
-        diagonal generator.'''
+    def __init__(self, H0_matrix):
+        '''Saves the initial Hamiltonian in units fm^-2 and dimension of the matrix.'''
         
         # Arguments
         
         # H0_matrix (NumPy array): Hamiltonian matrix in units MeV
-        # lambda_bd (float): Lambda value for block-diagonal decoupling (e.g. 
-        # 2.00 fm^-1)
-        # k_array (NumPy array): Momentum array
-        # coupled_channel (Boolean): Value corresponding to whether the 
-        # potential is coupled channel or not
         
         # h-bar^2 / M [MeV fm^2]
         hbar_sq_over_M = 41.47
@@ -32,25 +25,6 @@ class SRG(object):
         self.H0_matrix = H0_matrix / hbar_sq_over_M
         # Save dimension of matrix
         self.N = len(H0_matrix)
-        
-        # Array of True and False
-        bool_array = k_array < lambda_bd
-        # Length of momentum array
-        n = len(k_array)
-        
-        # Build projection operators
-        # Identity matrix for k < lambda_bd
-        p = np.diag(np.ones(n)*bool_array)
-        # Opposite of p: Identity matrix for k > decouple
-        q = np.identity(n)-p
-        # Construct full matrices for coupled channel vnn if necessary
-        if coupled_channel:
-            o = np.zeros((n,n))
-            self.P = np.vstack((np.hstack((p,o)),np.hstack((o,p))))
-            self.Q = np.vstack((np.hstack((q,o)),np.hstack((o,q))))
-        else:
-            self.P = p
-            self.Q = q
 
     
     def commutator(self, A, B):
@@ -60,30 +34,55 @@ class SRG(object):
         return A @ B - B @ A
     
     
+    def matrix2vector(self, A):
[…]

### 2019-05-03 deuteron.py

@@ -1,0 +1,9 @@
+# Created 05/03/19 by A.T. (tropiano.4@osu.edu)
+
+# Deuteron code: Calculates observables for deuteron given an NN potential (can
+# be SRG evolved). The class contains functions that obtain the deuteron wave
+# function in either momentum- or coordinate-space, functions that calculate 
+# observable quantities, and functions that return operators in momentum-space.
+
+
+import numpy as np

### 2019-05-03 evolve_hamiltonian.py

@@ -117,10 +117,11 @@ if __name__ == '__main__':
     method = 'srg'
     #method = 'magnus'
     
-    generator = 'Wegner'
-    #generator = 'T'
+    #generator = 'Wegner'
+    generator = 'T'
     #generator = 'Block-diag'
     lambda_bd = 2.00 # This won't affect the band-diagonal generators
+    #lambda_bd = 3.00
     
     lambda_array = np.array([10.0,2.8,2.0,1.2])
     #lambda_array = np.array([10.0,2.8])

### 2019-05-20 Potentials/vsrg_macos/load_save_potentials.py
Reorganization.

@@ -17,6 +17,8 @@
 # 119     Wendt LO non-local potential at 4 fm^-1 cutoff
 # 120     Wendt LO non-local potential at 9 fm^-1 cutoff
 # 121     Wendt LO non-local potential at 20 fm^-1 cutoff
+# 222     N2LO local potential at R_0 = 1.0 fm cutoff
+# 224     N2LO local potential at R_0 = 1.2 fm cutoff
 #
 # Also saves SRG or Magnus evolved potentials in the same directory.
 

### 2019-05-20 phase_shifts.py

@@ -1,0 +1,161 @@
+# 07/11/18
+# Calculates the phase shift as a function of energy from Magnus/SRG evolved
+# potential (coupled-channel).
+# Updated 09/25/18 to manually correct +/- shifts of pi in phase shifts
+
+import numpy as np
+import numpy.linalg as LA
+from scipy.interpolate import RectBivariateSpline,interp2d
+
+class phase_shifts(object):
+    
+    def __init__(self,vnn,gp,gw,conv='Stapp',spline=True):
+        '''Define constants, interpolate vnn (vnn should be input in units fm)'''
+        
+        # Save convention
+        self.conv = conv
+        
+        # Maximum momentum in fm^-1
+        self.kmax = max(gp)
+
+        # Units are fm^-1
+        self.gp = gp # Momenta array
+        self.gw = gw # Gaussian weights
+        # Dimension
+        N = len(gp)
+        self.dim = N
+        
+        if spline:
+            # Interpolate each sub-block with RectBivariateSpline
+            self.V11_func = RectBivariateSpline(gp,gp,vnn[:N,:N])
+            self.V12_func = RectBivariateSpline(gp,gp,vnn[:N,N:2*N])
+            self.V21_func = RectBivariateSpline(gp,gp,vnn[N:2*N,:N])
+            self.V22_func = RectBivariateSpline(gp,gp,vnn[N:2*N,N:2*N])
+        else:
+            # Interpolate each sub-block with interp2d
+            self.V11_func = interp2d(gp,gp,vnn[:N,:N])
+            self.V12_func = interp2d(gp,gp,vnn[:N,N:2*N])
+            self.V21_func = interp2d(gp,gp,vnn[N:2*N,:N])
+            self.V22_func = interp2d(gp,gp,vnn[N:2*N,N:2*N])
+            
+        self.spline = spline
+        
+    def delta(self,e):
+        '''Returns phase shift as a function of lab energy, e [MeV]'''
+        
+        N = self.dim # Length of each sub-block
+        
+        k0 = np.sqrt(e/2.0/41.47) # fm^-1
+        kmax = self.kmax # fm^-1
+        
+        # Build u_j vector
+        k_vec = self.gp # fm^-1
+        w_vec = self.gw # fm^-1
+        # First N elements of u_vec
+        u_vec = 2.0/np.pi * ( w_vec*k_vec**2 ) / (k_vec**2-k0**2)
+        # N+1 element of u_vec
[…]

### 2019-05-20 Potentials/vsrg_macos/load_save_potentials.py
Added extra slides for NUCLEI 2019 meeting.

@@ -17,8 +17,8 @@
 # 119     Wendt LO non-local potential at 4 fm^-1 cutoff
 # 120     Wendt LO non-local potential at 9 fm^-1 cutoff
 # 121     Wendt LO non-local potential at 20 fm^-1 cutoff
-# 222     N2LO local potential at R_0 = 1.0 fm cutoff
-# 224     N2LO local potential at R_0 = 1.2 fm cutoff
+# 222     Gezerlis et al N2LO local potential at R_0 = 1.0 fm cutoff
+# 224     Gezerlis et al N2LO local potential at R_0 = 1.2 fm cutoff
 #
 # Also saves SRG or Magnus evolved potentials in the same directory.
 

### 2019-05-20 deuteron.py

@@ -163,7 +163,7 @@ class Deuteron(object):
             return np.zeros((2*m,2*m))
     
     
-    def bessel_transformation(self, channel):
+    def hankel_transformation(self, channel):
         '''Returns the <r|k;channel> matrix for given partial wave channel. If 
         len(r_array) = n and len(k_array) = m, then this function returns an 
         n x m matrix. Note, one must specify an r_array and step-size dr.'''
@@ -207,8 +207,8 @@ class Deuteron(object):
         o = np.zeros((m,m))
         
         # Transform to momentum-space and build coupled channel matrix
-        s_trans = self.bessel_transformation('3S1') # n x m matrices
-        d_trans = self.bessel_transformation('3D1')
+        s_trans = self.hankel_transformation('3S1') # n x m matrices
+        d_trans = self.hankel_transformation('3D1')
         # Each variable here corresponds to a sub-block of the coupled channel matrix
         ss = s_trans.T @ r2_coordinate_space @ s_trans
         dd = d_trans.T @ r2_coordinate_space @ d_trans
@@ -253,8 +253,8 @@ class Deuteron(object):
     def rms_radius_from_rspace(self, u, w, r2_operator):
         '''Returns the RMS half-radius of deuteron by evaluating 
         0.5 * Sqrt( <psi|r^2|psi> ) in momentum-space where the r^2 operator is
-        Bessel transformed to from coordinate- to momentum-space. Experimental
-        value is ~2.14 fm.'''
+        transformed from coordinate- to momentum-space. Experimental value is 
+        ~2.14 fm.'''
         
         return None
     

### 2019-05-20 evolve_hamiltonian.py

@@ -197,15 +197,18 @@ if __name__ == '__main__':
     #kvnn = 106 # RKE N3LO at Lambda = 450 MeV
     #kvnn = 107 # RKE N3LO at Lambda = 500 MeV
     #kvnn = 111 # RKE N4LO at Lambda = 450 MeV
-    kvnn = 112 # RKE N4LO at Lambda = 500 MeV
+    #kvnn = 112 # RKE N4LO at Lambda = 500 MeV
     #kvnn = 119 # Wendt at Lambda = 4 fm^-1
     #kvnn = 120 # Wendt at Lambda = 9 fm^-1
     #kvnn = 121 # Wendt at Lambda = 20 fm^-1
+    #kvnn = 222  # Gezerlis et al N2LO local potential at R_0 = 1.0 fm cutoff
+    kvnn = 224  # Gezerlis et al 2LO local potential at R_0 = 1.2 fm cutoff
     
     channel = '3S1'
     
     #kmax = 30.0
-    kmax = 8.0
+    #kmax = 8.0
+    kmax = 10.0
     #kmid = 4.0
     kmid = 2.0
     ntot = 120
@@ -219,13 +222,13 @@ if __name__ == '__main__':
     ds = 1e-5 # This won't affect SRG computations
     #ds = 1e-6
     
-    #generator = 'Wegner'
+    generator = 'Wegner'
     #generator = 'T'
-    generator = 'Block-diag'
-    #lambda_bd = 2.00 # This won't affect the band-diagonal generators
-    #lambda_bd = 3.00
+    #generator = 'Block-diag'
     #lambda_bd = 1.00
-    lambda_bd = 4.00
+    lambda_bd = 2.00 # This won't affect the band-diagonal generators
+    #lambda_bd = 3.00
+    #lambda_bd = 4.00
     
     #lambda_array = np.array([10.0,2.8,2.0,1.2])
     lambda_array = np.array([10.0,2.8,2.0,1.5])

### 2019-05-20 scratchwork.py

@@ -11,6 +11,7 @@ import numpy as np
 import numpy.linalg as la
 # Python scripts made by A.T.
 from Potentials.vsrg_macos import load_save_potentials as lp
+from evolve_hamiltonian import run_srg
 
 
 def wave_func(H_matrix, U=np.empty(0)):
@@ -109,4 +110,8 @@ def main(method, generator, lamb, lambda_bd=0.00):
     #f.savefig(name+'.jpg', bbox_inches='tight')
     #chdir(cwd)
     
+lambda_array = np.array([10.0,2.8,2.0,1.5])
+d1 = run_srg(224, '3S1', 10.0, 2.0, 120, 'Wegner', lambda_array, save=True)
+d2 = run_srg(222, '3S1', 10.0, 2.0, 120, 'Block-diag', lambda_array, 
+             lambda_bd=2.00, save=True)
     

### 2019-05-20 evolve_hamiltonian.py
Update evolve_hamiltonian.py

@@ -8,8 +8,8 @@
 # value of lambda.
 
 
-import time
 import numpy as np
+import time
 # Scripts made by A.T.
 from Potentials.vsrg_macos import load_save_potentials as lp
 from SRG_codes import srg_wegner
@@ -158,6 +158,7 @@ def run_magnus(kvnn, channel, kmax, kmid, ntot, method, generator, lambda_array,
     print('k_magnus = %d, ds = %.1e'%(k_magnus, ds))
     
     # Writes evolved potentials to files if save = True
+    # Otherwise, just return the dictionary d
     if save:
                 
         # Save evolved potential and Omega for each lambda value
@@ -180,8 +181,6 @@ def run_magnus(kvnn, channel, kmax, kmid, ntot, method, generator, lambda_array,
             Os_matrix = d['omega'][lamb]
             lp.save_omega(k_array, Os_matrix, kvnn, channel, kmax, kmid, ntot, \
                           generator, lamb, k_magnus=k_magnus, ds=step_size)
-                
-    # Otherwise, just return the dictionary d
 
     return d
     

### 2019-05-20 evolve_hamiltonian.py
Looked at scattering state evolution.

@@ -224,15 +224,16 @@ if __name__ == '__main__':
     generator = 'Wegner'
     #generator = 'T'
     #generator = 'Block-diag'
-    #lambda_bd = 1.00
-    lambda_bd = 2.00 # This won't affect the band-diagonal generators
+    #lambda_bd = 1.00 # This won't affect the band-diagonal generators
+    lambda_bd = 2.00 
     #lambda_bd = 3.00
     #lambda_bd = 4.00
     
     #lambda_array = np.array([10.0,2.8,2.0,1.2])
-    lambda_array = np.array([10.0,2.8,2.0,1.5])
+    #lambda_array = np.array([10.0,2.8,2.0,1.5])
     #lambda_array = np.array([10.0,2.8])
     #lambda_array = np.array([10.0])
+    #lambda_array = np.array([1.2])
     
     # Save the evolved Hamiltonian?
     save = True
@@ -245,7 +246,6 @@ if __name__ == '__main__':
         
         d = run_srg(kvnn, channel, kmax, kmid, ntot, generator, lambda_array, 
                     lambda_bd=lambda_bd, save=save)
-    
         
     elif method == 'magnus':
         

### 2019-05-20 scratchwork.py
Update scratchwork.py

@@ -10,16 +10,17 @@ import matplotlib.pyplot as plt
 import numpy as np
 import numpy.linalg as la
 # Python scripts made by A.T.
+from Figures import figures_functions as ff
 from Potentials.vsrg_macos import load_save_potentials as lp
-from evolve_hamiltonian import run_srg
 
 
-def wave_func(H_matrix, U=np.empty(0)):
-    '''Diagonalizes the Hamiltonian and returns the deuteron wave function as u 
-    and w corresponding to the 3S1 and 3D1 channels. The wave function is 
-    unitless, that is, the momenta and weights are factored in such that
-    \sum_i { u(k_i)^2 + w(k_i)^2 } = 1. For an evolved wave function, enter
-    in a unitary transformation U.'''
+def wave_func(H_matrix, index, U=np.empty(0)):
+    '''Diagonalizes the Hamiltonian and returns the ith wave function as u 
+    and w corresponding to the 3S1 and 3D1 channels where index is the ith 
+    sorted eigenvalue. The wave function is unitless, that is, the momenta 
+    and weights are factored in such that \sum_i { u(k_i)^2 + w(k_i)^2 } = 1. 
+    For an evolved wave function, enter in a unitary transformation U. Also
+    returns the eigenvalue in MeV.'''
         
     # Arguments
         
@@ -28,90 +29,112 @@ def wave_func(H_matrix, U=np.empty(0)):
 
     # Diagonalize Hamiltonian
     eigenvalues,eigenvectors = la.eig(H_matrix)
-    print(np.sort(eigenvalues))
     
-    # Decide which eigenvalue to select here by printing...
-    #bool_array = (eigenvalues<0.0)*(eigenvalues>-3.0)
-    # This is the integer index where eigenvalue[index] = eps_d
-    #index = list(bool_array).index(True) 
-    # Full wave function (unitless)
-    #psi = eigenvectors[:,index] 
+    eigenvalue = np.sort(eigenvalues)[index]
+    eigenvector_index = list(eigenvalues).index(eigenvalue)
+    psi = eigenvectors[:,eigenvector_index]
 
     # Evolve wave function by applying unitary transformation U
[…]

### 2019-05-20 Notes/Operator_evolution/operator_evolution_may20.tex
Beginning SRG operator evolution notes.

--- 2019-05-02 Notes/Magnus/magnus_Jan08.tex
@@
-% Notes on Magnus project
-% Created 01/08/19 by A.T. (tropiano.4@osu.edu)
-% Update: transitioning these notes into a draft of the eventual paper
+% Notes on SRG operator evolution project
+% Created 05/20/19 by A.T. (tropiano.4@osu.edu)
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Exploring the Magnus expansion and the in-medium similarity renormalization group}
+\title{SRG operator evolution}
 
@@
 \begin{abstract}
-\noindent{-- Test Magnus expansion SRG implementation on LO NN potential at high $\Lambda$. (Define SRG or IMSRG acronym in abstract.)}
-\\
--- High $\Lambda$ leads to spurious bound states in spin triplet channels.
-\\
--- Decouple spurious bound state(s) by using two approaches within the Magnus implementation to drive the Hamiltonian to band-diagonal, unitarily equivalent form.
-\\
--- One choice of generator where the deep bound state is decoupled outside low-momentum and another where it is shifted to low-momentum.
-\\
--- Deep bound state corrupts low-momentum physics.
-\\
--- Connection to IMSRG intruder state problem.
-\\
--- Confirm unitarity of Hamiltonian by evaluation of deuteron observables.
-\\
--- Lastly, study operator evolution.
+
+Abstract goes here.
+
 \end{abstract}
@@
 
-\noindent{-- In recent years \textit{ab initio} methods have made strides in nuclear structure and reactions.}
-\\
--- Realistic binding energies starting from NN and 3N forces have been calculated for many medium mass nuclei using different many-body methods.
-\\
--- The in-medium similarity renormalization group (IMSRG) is one such method \cite{Hergert:2015awm, Hergert:2016iju}.
-\\
--- The IMSRG separates energy scales in the nuclear Hamiltonian by decoupling the reference state from excited states to band- or block-diagonal form.
-\\
--- One can use the decoupled Hamiltonian to solve the many-body Sch{\"o}dinger equation extracting specific eigenvalues and eigenstates which qualifies the IMSRG as an \textit{ab initio} method.
-\\
-
-\noindent{-- The IMSRG procedure requires solving a system of nonlinear, coupled differential equations which can often be stiff necessitating a high-order ODE solver.}
-\\
--- In principle, the decoupled Hamiltonian (or any operator) is unitarily equivalent but the numerical error of solving the ODE can lead to error on observable quantities.
-\\
--- Furthermore, the model spaces for IMSRG calculations can be extremely large.
-\\
--- Evolving several operators is often impossible due to memory restrictions in storing several operators.
-\\
-
-\noindent{-- A variant of the IMSRG that utilizes the Magnus expansion can overcome these limitations.}
-\\
--- We will refer to this as the Magnus implementation or simply Magnus.
-\\
--- The Magnus solves for the unitary transformation directly whereas the IMSRG applies the transformation indirectly in steps of the differential flow equation.
-\\
--- From the form of the transformation, the numerical error leaves the unitarity of the evolved Hamiltonian un-affected.
-\\
--- By explicitly solving for the transformation, one can evolve several operators.
-\\
--- The Magnus implementation has become a standard technique in IMSRG calculations as studies have targeted observables such as radii, electromagnetic moments and transitions, etc., requiring consistently evolved operators.
-\\
-
-\noindent{-- We test the Magnus implementation on chiral non-local NN potentials in free-space for several EFT cutoffs.}
-\\
--- At high cutoffs, spin triplet channels feature spurious, deeply bound states from the strong, repulsive tensor force \cite{Nogga:2005hy}.
-\\
--- These bound states are features of high-momentum physics and lie outside the range of the EFT.
-\\
--- However, potentials with deeply bound states have shown sensitivity to SRG transformations \cite{Glazek:2008pg, Wendt:2011qj}.
-\\
--- Details of the SRG transformation can cause the spurious bound state(s) to corrupt the low-momentum physics.
-\\
--- An analogous problem occurs in IMSRG calculations for systems with intruder states where the intruder state can shift to the energy scale of the reference state in valence space.
-\\
--- This severely distorts low-energy properties such as the ground state wave function.
-\\
--- It is not understood how the IMSRG procedure evolves intruder state systems.
-\\
--- Due to the prominence of the Magnus in IMSRG, one must first understand if the Magnus approach matches the typical approach for difficult systems before investigating the intruder state problem.
-\\
--- NN potentials with spurious bound states offer a good test laboratory for the Magnus implementation to better understand if the Magnus is equivalent to the SRG approach. 
-\\
-
-\noindent{-- The past decade has seen a tremendous increase in the number of chiral NN potentials.}
-\\
--- Interactions can now be built up to N5LO and feature several different regularization schemes.
-\\
--- A natural question is to ask whether the SRG decouples these potentials in the same way.
-\\
--- There is evidence of universal, low-momentum matrix elements as seen from evolving different potentials with SRG transformations or $V_{low~k}$ \cite{Dainton:2013axa}.
-\\
--- There has also been renewed interest in chiral potentials at high-cutoffs but for a locally regulated potential \cite{Tews:2018sbi}.
-\\
--- Given the growing number of chiral interactions, it would be interesting to re-examine these areas from an SRG standpoint.
-\\
--- However, we would like to focus on a fixed comparison of the SRG and the Magnus approach as a first test, and therefore only consider evolving non-local LO NN potentials at various cutoffs.
-\\
--- We leave the other areas as topics for future studies.
-\\
-
-\noindent{-- The rest of the paper is organized as follows:}
-\\
--- In Sec. \ref{sec:formalism} we review the formalism of the SRG and the Magnus implementation emphasizing the major advantages of the Magnus.
-\\
--- In Sec. \ref{sec:results} we test the Magnus implementation on high-cutoff NN potentials.
-\\
--- We briefly review the SRG results for the same set of bare interactions and compare Magnus to SRG results.
-\\
--- With the Magnus evolved operators, we calculate several observables and explore operator evolution.
-\\
--- Lastly, we summarize our results in Sec. \ref{sec:conclusion}.
-\\
--- We discuss the implications for the Magnus expansion within the IMSRG.
+Introduction goes here.
 
@@
 
-\noindent{\textbf{SRG formalism}}
-\\
--- In this section we describe the SRG in the context of decoupling any operator.
-\\
--- The SRG decouples low- and high-momentum scales by applying a continuous unitary transformation $U(s)$ where $s=0 \rightarrow \infty$ is the flow parameter.
-\\
--- The `dressed' or evolved operator is given by
-%
-\begin{eqnarray}
-  \label{eq:srg_operator}
-  O(s) = U(s) O(0) U^{\dagger}(s),
-\end{eqnarray}
-%
-where $O(0)$ corresponds to the `bare' operator.
-\\
--- Because $U(s)$ is unitary, the observables of the operator are preserved.
-\\
--- In practice, the unitary transformation U(s) is not explicitly solved for; the evolved operator is given by a differential flow equation which is obtained by taking the derivative of Eqn.
-(\ref{eq:srg_operator}),
-%
-\begin{eqnarray}
-  \label{eq:srg_flow}
-  \frac{dO(s)}{ds} = [\eta(s), O(s)],
-\end{eqnarray}
-%
-where $\eta(s)=\frac{dU(s)}{ds} U^{\dagger}(s) = -\eta^{\dagger}(s)$ is the anti-hermitian SRG generator.
-\\
--- The generator is defined as a commutator,
-%
-\begin{eqnarray}
-  \label{eq:srg_generator}
-  \eta(s) = [G, H(s)],
-\end{eqnarray}
-%
-where $G$ specifies the type of flow or form of the decoupled operator.
-\\
--- To drive the operator to band-diagonal form, set $G=H_D(s)$, the diagonal of the Hamiltonian.
-\\
--- This choice was implemented by Wegner in condensed matter physics \cite{Wegner:1994ab}.
-\\
--- For notational convenience, we write the Wegner choice without the $s$ dependence in the rest of the paper.
-\\
--- In a similar option used in nuclear physics, $G$ is set to the relative kinetic energy, $T_{rel}$, which also drives to band-diagonal form.
-\\
--- In this paper, we consider both choices.
-\\
--- Generally the flow equation (\ref{eq:srg_flow}) is solved up to some finite value of $s$ with a high-order ODE solver.
-\\
--- It is convenient to define $\lambda \equiv s^{-1/4}$ which roughly measures the width of the diagonal in the decoupled operator.
-\\
-
-\noindent{\textbf{Magnus expansion formalism}}
-\\
--- We now consider the Magnus implementation.
-\\
--- Mathematically speaking, the Magnus expansion is a method for solving an initial value problem associated with a linear ordinary differential equation (ODE).
-\\
--- Formal details of the Magnus expansion are discussed in \cite{Blanes:2009ab}.
-\\
--- We will introduce the Magnus expansion in the context of SRG evolving any operator.
-\\
--- In an intermediate step in deriving Eqn. (\ref{eq:srg_flow}), we have a linear ODE for $U(s)$,
-%
-\begin{eqnarray}
-  \label{eq:unitary_trans}
-  \frac{dU(s)}{ds} = \eta(s) U(s).
-\end{eqnarray}
-%
--- Magnus showed that one can solve the following equation with a solution $U(s)=e^{\Omega(s)}$ where $\Omega(s)$ is expanded as a power series, $\sum_{n}^{\infty} \Omega_n$ (referred to as the Magnus expansion or Magnus series).
-\\
--- The terms of the series are given by integral expressions involving $\eta(s)$ (again, see \cite{Blanes:2009ab, Magnus:1954zz} for details).
-\\
--- For our case, we focus on the formally exact derivative of $\Omega(s)$,
-%
-\begin{eqnarray}
-  \label{eq:magnus_omega}
-  \frac{d\Omega(s)}{ds} = \sum_{k=0}^{\infty} \frac{B_k}{k!} ad_{\Omega}^{k}(\eta),
-\end{eqnarray}
-%
-where $B_k$ are the Bernoulli numbers, $ad_{\Omega}^{0}(\eta)=\eta(s)$, and $ad_{\Omega}^{k}(\eta)=[\Omega(s),ad_{\Omega}^{k-1}(\eta)]$.
-\\
--- We integrate this differential equation to find $\Omega(s)$ and evaluate the unitary transformation directly.
-\\
--- Then the evolved operator can be evaluated with the BCH formula:
-%
-\begin{eqnarray}
-  \label{eq:bch}
-  O(s) = e^{\Omega(s)} O e^{-\Omega(s)} = \sum_{k=0}^{\infty} \frac{1}{k!} ad_{\Omega}^{k}(O).
-\end{eqnarray}
-%
--- As $k \rightarrow \infty$ in both sums in Eqns. (\ref{eq:magnus_omega}) and (\ref{eq:bch}) the Magnus transformation matches the SRG transformation.
-\\
--- We investigate several truncations $k_{max}$ in Eqn. (\ref{eq:magnus_omega}) and take many terms, $k_{max} \sim 25$, in Eqn. (\ref{eq:bch}).
-\\
-\textcolor{red}{-- Here or earlier (for the following bullets)? Better to motivate the Magnus in the introduction or easier to explain given mathematical detail?}
-\\
--- There are significant advantages in the Magnus implementation.
-\\
--- In the typical approach, the numerical error associated with solving the flow equation affects the accuracy of the observables for the evolved operator.
-\\
--- Therefore, one must use a high-order ODE solver in integrating the flow equation (\ref{eq:srg_flow}).
-\\
--- In the Magnus implementation, unitarity is guaranteed by the form of $U(s)$; in fact, one could solve Eqn.
-(\ref{eq:magnus_omega}) with a simple first-order Euler step-method keeping the same observables while decoupling the operator as desired.
-\\
--- This offers a decent computational speed-up by avoiding a high-order solver.
-\\
--- In this paper, we demonstrate this advantage by applying the Magnus implementation using the first-order Euler step-method.
-\\
--- The second major advantage involves the evolution of multiple operators.
-\\
--- In many other situations, one may be interested in evolving several operators at a time.
-\\
--- In the SRG procedure, we would have another set of coupled equations in Eqn. (\ref{eq:srg_flow}), drastically increasing memory usage.
-\\
--- Each additional operator increases the set of equations - say $N$ equations - by another factor of $N$.
-\\
--- In the Magnus, one only needs $\Omega(s)$ to consistently evolve several operators.
-\\
--- We avoid the cost in memory by directly constructing $U(s)=e^{\Omega(s)}$.
-\\
--- This is especially useful in IMSRG calculations where the model space can be very large.
-\\
--- In the next section, we discuss results from Magnus evolved large-cutoff potentials focusing on the flow of the potential, observables, and operator evolution.
+Is this section necessary for now?
 
@@
 
-\noindent{\textbf{Evolution of potentials}}
-\\
--- In this section, we Magnus evolve LO non-local potentials in the $^{3}S_1-^{3}D_1$ channel at cutoffs of $\Lambda=4$, $9$, and $20 \, fm^{-1}$.
-\\
-\textcolor{red}{-- Option: add new regularization schemes?}
-\\
--- For the higher two cutoffs, the potentials have one and two spurious, deeply bound states, respectively.
-\\
--- In \cite{Wendt:2011qj}, potentials at large-cutoffs were SRG evolved with $G=H_D$ and $G=T_{rel}$.
-\\
--- At lower cutoffs ($\Lambda \lesssim 4 \, fm^{-1}$), potential matrix elements flowed toward a decoupled, universal form independent of $G$, that is the low-momentum matrix elements approached the same values as $\lambda \rightarrow 0$.
-\\
--- However, SRG evolution differed for potentials featuring one or more spurious bound states.
-\\
--- With one or more spurious bound states and $G=T_{rel}$, the SRG transformation shifted a spurious bound state toward the low-momentum block corrupting the low-energy physics (e.g., the deuteron wave function, phase shifts, etc.).
-\\
--- For $G=H_D$, the SRG decoupled the spurious bound state outside the low-momentum block matching the flow to universal low-momentum form independent of the cutoff $\Lambda$.
-\\
--- Similar behavior could be prevalent in IMSRG calculations where the choice in generator affects evolution of many-body Hamiltonians with intruder states as it does for these NN potentials in free-space SRG.
-\\
-
-\noindent{-- First, we compare Magnus to SRG evolution for large cutoff potentials with $G=H_D$ and $G=T_{rel}$.}
-\\
--- Figures \ref{fig:magnus_contours_Wendt_Lamb9_Wegner} and \ref{fig:magnus_contours_Wendt_Lamb9_T} show potential matrix element evolution for three truncations in the sum of Eqn.
-\ref{eq:magnus_omega} up to three values of $\lambda$ with $\Lambda=9 \, fm^{-1}$.
-\\
--- At this cutoff, the potential has one spurious bound state at about $-2000$ MeV.
-\\
-%	
-\begin{figure}
-  \captionsetup{singlelinecheck=false,justification=raggedright}
-  \centering
-  \includegraphics[width=10cm]{magnus_contours_Wendt_Lamb9_Wegner}
-  \hspace*{0.05\textwidth}
-  \caption{Contours of Magnus evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=H_{D}$ for $\lambda=2.8$ (left), $2.0$ (middle), and $1.2$ (right) $fm^{-1}$ and truncations in the Magnus $k_{max}=2$ (top), $6$ (middle), and $10$ (bottom).}
-  \label{fig:magnus_contours_Wendt_Lamb9_Wegner}
-\end{figure}
-%
-\begin{figure}
-  \captionsetup{singlelinecheck=false,justification=raggedright}
-  \centering
-  \includegraphics[width=10cm]{magnus_contours_Wendt_Lamb9_T}
-  \hspace*{0.05\textwidth}
-  \caption{Contours of Magnus evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=T_{rel}$ for $\lambda=2.8$ (left), $2.0$ (middle), and $1.2$ (right) $fm^{-1}$ and truncations in the Magnus $k_{max}=2$ (top), $6$ (middle), and $10$ (bottom).}
-  \label{fig:magnus_contours_Wendt_Lamb9_T}
-\end{figure}
-%
--- We see the same behavior with the Magnus in comparison to the SRG in \cite{Wendt:2011qj} for both generators.
-\\
--- For $G=H_D$, there is a deep, blue dot in the middle of the contours at $k \approx 1.75 \, fm^{-1}$ which corresponds to the decoupled spurious bound state.
-\\
--- We have checked other cutoffs and found that the evolved low-momentum matrix elements are independent of the cutoff $\Lambda$ implying a low-momentum, universal form.
-\\
--- The only major difference in Magnus or SRG evolution for various cutoffs is where spurious bound state(s) are decoupled.
-\\
--- This decoupling feature depends on the details of the starting interaction (i.e., the value of the bound state).
-\\
-%
-\begin{figure}
-  \captionsetup{singlelinecheck=false,justification=raggedright}
-  \centering
-  \includegraphics[width=14cm]{evolved_diags_Wendt_Lamb9_Wegner}
-  \hspace*{0.05\textwidth}
-  \caption{Diagonal (top row) and far off-diagonal (bottom row) matrix elements of evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=H_{D}$ for several values of $\lambda$ and truncations in the Magnus series $k_{max}$.}
-  \label{fig:evolved_diags_Wendt_Lamb9_Wegner}
-\end{figure}
-%
-\noindent{-- Furthermore, it is dependent on the momentum mesh on which the potential is generated.}
-\\
--- At $k_{max}=2$ and $\lambda=2.0 \, fm^{-1}$, we see large, positive off-diagonal values along the momentum axes where the deep bound state is decoupled.
-\\
--- Solving for $\Omega(s)$ at a low truncation leads to less desirable flow, that is, the transformation $U(s)$ is not quite the same transformation as the SRG $U(s)$.
-\\
--- However, the Magnus still guarantees the unitarity of $U(s)$, and we see a consistent decoupling of the spurious bound state in each row independent of $k_{max}$.
-\\
--- For $G=T_{rel}$, the spurious bound state is shifted up along the diagonal, and the low-momentum block drops to extremely negative values.
-\\
--- Here, the spurious bound state corrupts the low-momentum block matching the SRG evolution of different cutoffs, thus breaking universality.
-\\
-%
-\begin{figure}
-  \captionsetup{singlelinecheck=false,justification=raggedright}
-  \centering
-  \includegraphics[width=14cm]{evolved_diags_Wendt_Lamb9_T}
-  \hspace*{0.05\textwidth}
-  \caption{Diagonal (top row) and far off-diagonal (bottom row) matrix elements of evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=T_{rel}$ for several values of $\lambda$ and truncations in the Magnus series $k_{max}$.}
-  \label{fig:evolved_diags_Wendt_Lamb9_T}
-\end{figure}
-%
-\noindent{-- Figures \ref{fig:evolved_diags_Wendt_Lamb9_Wegner} and \ref{fig:evolved_diags_Wendt_Lamb9_T} show a more quantitative depiction of the evolved potentials.}
-\\
--- The black dotted line corresponds to the SRG evolved potential whereas the other lines are Magnus evolved potentials for different $k_{max}$ for diagonal and far-off diagonal matrix elements of $V_{\lambda}(k,k')$.
-\\
--- It is clear in these figures that the Magnus matches the SRG at $k_{max} \gtrsim 6$.
-\\
--- In Figure \ref{fig:evolved_diags_Wendt_Lamb9_Wegner} the decoupled spurious bound state is seen as the large negative drop in the curves at $k \approx 1.75 \, fm^{-1}$.
-\\
-\textcolor{red}{-- Unnecessary?
-\\
--- From applying the Magnus in several other cases, we have seen that harder potentials cause convergence issues in the Magnus expansion due to the relative size of the SRG generator $\eta(s)$.
-\\
--- To avoid convergence issues we can take a smaller step-size.
-\\
--- In the previous cases (and all other cases unless specified otherwise), we take $ds=10^-5$.}
-\\
-
-\noindent{\textbf{Observables}}
-\\
-%
-\begin{table}
-  \captionsetup{singlelinecheck=false,justification=raggedright}
-  \caption{Relative error on the deuteron bound state energy and the root mean square of eigenvalues where $\tilde{\epsilon}$ denotes an eigenvalue of an SRG or Magnus evolved Hamiltonian for $\Lambda=9 \, fm^{-1}$ and $\lambda=1.2 \, fm^{-1}$.}
-  \label{tab:energies}
-  \begin{ruledtabular}
-    \begin{tabular}{{>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{2in}}}
-      $  $ & $G$ & $ |\frac{\epsilon_d-\tilde{\epsilon}_d}{\epsilon_d}| $ & $\sqrt{\frac{1}{N} \, \sum_{i}^{N} (\tilde{\epsilon}_i-\epsilon_i)^2}$   [MeV] \\
-      \colrule
-      SRG & $ $ & $\num{1.165e-5}$ & $\num{3.016e-4}$ \\
-      Magnus, $k_{max}=2$ & $H_D$ & $\num{5.010e-10}$ & $\num{4.097e-9}$ \\
-      Magnus, $k_{max}=14$ & $ $ & $\num{1.206e-11}$ & $\num{3.950e-10}$ \\ \hline
-      SRG & $ $ & $\num{1.003e-4}$ & $\num{9.791e-5}$ \\
-      Magnus, $k_{max}=2$ & $T_{rel}$ & $\num{7.775e-8}$ & $\num{6.376e-8}$ \\
-      Magnus, $k_{max}=14$ & $ $ & $\num{7.607e-8}$ & $\num{6.359e-8}$ \\
-    \end{tabular}
-  \end{ruledtabular}
-\end{table}
-%
--- To emphasize the two major advantages of the Magnus implementation, we now consider evolved observables and operators for the remainder of the section.
-\\
--- Table \ref{tab:energies} shows the relative error on the deuteron bound state energy and root mean square of all eigenvalues for several evolution cases.
-\\
--- The Magnus approach preserves energies to several orders of magnitude better than the typical SRG approach.
-\\
--- Again, despite the inclusion of several more terms in the sum of Eqn.
-\ref{eq:magnus_omega}, we see consistent errors between $k_{max}=2$ and $14$ because of the guaranteed unitarity of $U(s)=e^{\Omega(s)}$
-\\
--- The errors on the Magnus energies are within the region of floating-point error whereas the SRG compounds error in solving the ODE \ref{eq:srg_flow}.
-\\
--- We have also checked the phase shifts from the evolved potentials match the bare potentials in all cases for Magnus and SRG evolution.
-\\ 
--- Next we show the evolved deuteron wave function for several cases.
-\\
--- Figure \ref{fig:momentum_dist_Wendt_Lamb9} shows the deuteron momentum probability density, $|\phi(k)|^2$, on a semi-log scale as a function of momentum for both band-diagonal generators.
-\\
--- With $G=H_D$, the evolved and un-evolved momentum distributions agree for low-momentum whereas $G=T_{rel}$ significantly distorts the distribution from the presence of the spurious bound state in the $\Lambda=9 \, fm^{-1}$ potential.
-\\
--- This illustrates the advantage of the Wegner generator: the spurious bound state at high-momentum does not affect the low-momentum physics under the SRG transformation.
-\\
--- In all cases of Magnus and SRG evolution, we can consistently evolve wave functions and operators to make reliable calculations of observables.
-\\
--- To demonstrate this, we calculate the deuteron RMS radius and quadrupole moment with the $\Lambda=9 \, fm^{-1}$ potential using the Magnus implementation with the Wegner generator.
-\\
--- The initial values of the chiral potential are $r_d = 2.022 \, fm$ and $Q_d = 0.287 \, fm^2$ compared to the experimental values $r_d^{exp} = 2.141 \, fm$ and $Q_d^{exp} = 0.286 \, fm^2$. 
-\\
--- We have checked for several cases with the Magnus and found near-perfect agreement to the initial values of both observables.
-\\
-
-\noindent{\textcolor{red}{UPDATED UP TO HERE 04/03/19}}
-\\
-\begin{figure}
-  \captionsetup{singlelinecheck=false,justification=raggedright}
-  \centering
-  \includegraphics[width=10cm]{momentum_dist_Wendt_Lamb9}
-  \hspace*{0.05\textwidth}
-  \caption{Momentum probability densities of the deuteron comparing the un-evolved wavefunction (black dotted line), SRG evolved wavefunction (blue dashed line), and two Magnus evolved wavefunctions with truncations $2$ and $14$ (green and red dash-dotted lines, respectively) where $\lambda=1.2 \, fm^{-1}$.
-The left panel shows evolution with $G=H_{D}$ and the right with $G=T_{rel}$.
-Here $\Lambda=9 \, fm^{-1}$.}
-  \label{fig:momentum_dist_Wendt_Lamb9}
-\end{figure}
-%
-\noindent{-- RMS radius and quadrupole moment of deuteron.}
-\\
--- Values from initial potential ($\Lambda=9 \, fm^{-1}$):
-\begin{itemize}
-  \item $r_d = 2.022 \, fm$ (using momentum-space derivatives)
-  \item $r_d = 2.465 \, fm$ (using Fourier transforms)
-  \item $Q_d = 0.287 \, fm^2$ (using momentum-space derivatives)
-\end{itemize}
--- Values from standard Magnus evolved potential ($G=H_D$, $\lambda=1.2 \, fm^{-1}$, and $k_{max}=6$):
-\begin{itemize}
-  \item $r_d = 2.022 \, fm$ (using momentum-space derivatives)
-  \item $Q_d = 0.287 \, fm^2$ (using momentum-space derivatives)s
-  \item Note: we apply $U^{\dagger}(s) U(s)$ to wave function to compute unitarily equivalent observables
-\end{itemize}
--- Experimental values:
-\begin{itemize}
-  \item $r_d = 2.141 \, fm$
-  \item $Q_d = 0.286 \, fm^2$
-\end{itemize}
-%
-\textbf{Evolution of operators}
-%
-\begin{figure}[H]
-  \captionsetup{singlelinecheck=false,justification=raggedright}
-  \centering
-  \includegraphics[width=14cm]{momentum_proj_operator_contours_q0,31_magnus_Wendt_Lamb9}
-  \hspace*{0.05\textwidth}
-  \caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ Magnus evolving in $\lambda$ right to left with $G=H_D$ (top) and $G=T_{rel}$ (bottom).
-Here $q=0.31 \, fm^{-1}$, $\Lambda=9 \, fm^{-1}$, and $k_{max}=6$.}
-  \label{fig:momentum_proj_operator_contours_q0,31_magnus_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-  \captionsetup{singlelinecheck=false,justification=raggedright}
-  \centering
-  \includegraphics[width=10cm]{momentum_proj_difference_q0,31_magnus_Wendt_Lamb9}
-  \hspace*{0.05\textwidth}
-  \caption{Difference in evolved and bare matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ Magnus evolving to $\lambda=1.2 \, fm^{-1}$ right to with $G=H_D$ (left) and $G=T_{rel}$ (right).
-Here $q=0.31 \, fm^{-1}$, $\Lambda=9 \, fm^{-1}$, and $k_{max}=6$.}
-  \label{fig:momentum_proj_operator_difference_q0,31_magnus_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-  \captionsetup{singlelinecheck=false,justification=raggedright}
-  \centering
-  \includegraphics[width=14cm]{momentum_proj_operator_contours_q3,04_magnus_Wendt_Lamb9}
-  \hspace*{0.05\textwidth}
-  \caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ Magnus evolving in $\lambda$ right to left with $G=H_D$ (top) and $G=T_{rel}$ (bottom).
-Here $q=3.04 \, fm^{-1}$, $\Lambda=9 \, fm^{-1}$, and $k_{max}=6$.}
-  \label{fig:momentum_proj_operator_contours_q3,04_magnus_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-  \captionsetup{singlelinecheck=false,justification=raggedright}
-  \centering
-  \includegraphics[width=10cm]{momentum_proj_difference_q3,04_magnus_Wendt_Lamb9}
-  \hspace*{0.05\textwidth}
-  \caption{Difference in evolved and bare matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ Magnus evolving to $\lambda=1.2 \, fm^{-1}$ with $G=H_D$ (left) and $G=T_{rel}$ (right).
-Here $q=3.04 \, fm^{-1}$, $\Lambda=9 \, fm^{-1}$, and $k_{max}=6$.}
-  \label{fig:momentum_proj_operator_difference_q3,04_magnus_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-  \captionsetup{singlelinecheck=false,justification=raggedright}
-  \centering
-  \includegraphics[width=14cm]{r2_operator_contours_magnus_Wendt_Lamb9}
-  \hspace*{0.05\textwidth}
-  \caption{Matrix elements of $\mel{k}{r^2}{k'}$ Magnus evolving in $\lambda$ right to left with $G=H_D$ (top) and $G=T_{rel}$ (bottom). Here $\Lambda=9 \, fm^{-1}$ and $k_{max}=6$.}
-  \label{fig:r2_operator_contours_srg_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-  \captionsetup{singlelinecheck=false,justification=raggedright}
-  \centering
-  \includegraphics[width=10cm]{r2_difference_magnus_Wendt_Lamb4}
-  \hspace*{0.05\textwidth}
-  \caption{Difference in evolved and bare matrix elements of $\mel{k}{r^2}{k'}$ Magnus evolving to $\lambda=1.2 \, fm^{-1}$ with $G=H_D$ (left) and $G=T_{rel}$ (right).
-Here $\Lambda=4 \, fm^{-1}$ and $k_{max}=6$.}
-  \label{fig:r2_difference_magnus_Wendt_Lamb4}
-\end{figure}
-%
-\begin{figure}[H]
-  \captionsetup{singlelinecheck=false,justification=raggedright}
-  \centering
-  \includegraphics[width=10cm]{r2_difference_magnus_Wendt_Lamb9}
-  \hspace*{0.05\textwidth}
-  \caption{Difference in evolved and bare matrix elements of $\mel{k}{r^2}{k'}$ Magnus evolving to $\lambda=1.2 \, fm^{-1}$ with $G=H_D$ (left) and $G=T_{rel}$ (right).
-Here $\Lambda=9 \, fm^{-1}$ and $k_{max}=6$.
-(Note the difference in color bar scales.)}
-  \label{fig:r2_difference_magnus_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-  \captionsetup{singlelinecheck=false,justification=raggedright}
-  \centering
-  \includegraphics[width=14cm]{r2_integrand_contours_magnus_Wendt_Lamb9}
-  \hspace*{0.05\textwidth}
-  \caption{Integrand of $\bra{\Psi}\ket{k} \mel{k}{r^2}{k'} \bra{k'}\ket{\Psi}$ Magnus evolving the wave function in $\lambda$ right to left with $G=H_D$ (top) and $G=T_{rel}$ (bottom).
-Here $\Lambda=9 \, fm^{-1}$, $k_{max}=6$, and the operator $r^2$ is un-evolved.}
-  \label{fig:r2_integrand_contours_srg_Wendt_Lamb9}
-\end{figure}
+Organize this according to the figures: what story do the figures tell?
 
@@
 
-\noindent{-- Summarize.}
-\\
--- Where does the Magnus implementation differ from the SRG result?
-\\
--- Connection to the IMSRG intruder state problem.
-\\
--- Outlook.
+Summarize.
 
@@
 
-\bibliography{tropiano_srg}
+\bibliography{tropiano_bib}
 

### 2019-05-20 scratchwork.py
Changed .jpg figures to .pdf for non-contour plots.

@@ -125,7 +125,7 @@ def main(index, kvnn, kmax, kmid, method, generator, lamb, lambda_bd=0.00):
     # Save figure
     folder = ff.current_date() # Gets current month and year
     chdir('Figures/%s'%folder)
-    f.savefig(name+'.jpg', bbox_inches='tight')
+    f.savefig(name+'.pdf', bbox_inches='tight')
     chdir(cwd)    
     
 

### 2019-05-23 Potentials/vsrg_macos/load_save_potentials.py
Renamed Wendt potentials as kvnn = 900, 901, 902.

@@ -14,11 +14,11 @@
 #  13     Entem/Machleidt N3LOW (400 MeV cutoff)
 #  32     Epelbaum et al N3LO (550/600 MeV cutoff)
 #  90     Reinert-Krebs-Epelbaum LO (400 MeV cutoff)
-# 119     Wendt LO non-local potential at 4 fm^-1 cutoff
-# 120     Wendt LO non-local potential at 9 fm^-1 cutoff
-# 121     Wendt LO non-local potential at 20 fm^-1 cutoff
 # 222     Gezerlis et al N2LO local potential at R_0 = 1.0 fm cutoff
 # 224     Gezerlis et al N2LO local potential at R_0 = 1.2 fm cutoff
+# 900     Wendt LO non-local potential at 4 fm^-1 cutoff
+# 901     Wendt LO non-local potential at 9 fm^-1 cutoff
+# 902     Wendt LO non-local potential at 20 fm^-1 cutoff
 #
 # Also saves SRG or Magnus evolved potentials in the same directory.
 
@@ -565,3 +565,5 @@ if __name__ == '__main__':
     
     # Example for loading an initial potential below
     V = load_potential(6,'3S1',30.0,4.0,120)
+    
+    # Rewrite Wendt potentials down here

### 2019-05-23 evolve_hamiltonian.py

@@ -197,9 +197,9 @@ if __name__ == '__main__':
     #kvnn = 107 # RKE N3LO at Lambda = 500 MeV
     #kvnn = 111 # RKE N4LO at Lambda = 450 MeV
     #kvnn = 112 # RKE N4LO at Lambda = 500 MeV
-    #kvnn = 119 # Wendt at Lambda = 4 fm^-1
-    #kvnn = 120 # Wendt at Lambda = 9 fm^-1
-    #kvnn = 121 # Wendt at Lambda = 20 fm^-1
+    #kvnn = 900 # Wendt at Lambda = 4 fm^-1
+    #kvnn = 901 # Wendt at Lambda = 9 fm^-1
+    #kvnn = 902 # Wendt at Lambda = 20 fm^-1
     #kvnn = 222  # Gezerlis et al N2LO local potential at R_0 = 1.0 fm cutoff
     kvnn = 224  # Gezerlis et al 2LO local potential at R_0 = 1.2 fm cutoff
     
@@ -230,7 +230,7 @@ if __name__ == '__main__':
     #lambda_bd = 4.00
     
     #lambda_array = np.array([10.0,2.8,2.0,1.2])
-    #lambda_array = np.array([10.0,2.8,2.0,1.5])
+    lambda_array = np.array([10.0,2.8,2.0,1.5])
     #lambda_array = np.array([10.0,2.8])
     #lambda_array = np.array([10.0])
     #lambda_array = np.array([1.2])

### 2019-05-23 scattering_states.py

@@ -1,0 +1,139 @@
+# Created 05/23/19 by A.T. (tropiano.4@osu.edu)
+
+# Looking at scattering state momentum distribution for 3S1 potential
+
+
+from os import chdir, getcwd
+from matplotlib.offsetbox import AnchoredText
+import matplotlib.pyplot as plt
+import numpy as np
+import numpy.linalg as la
+# Python scripts made by A.T.
+from Figures import figures_functions as ff
+from Potentials.vsrg_macos import load_save_potentials as lp
+
+
+def wave_func(H_matrix, index, U=np.empty(0)):
+    '''Diagonalizes the Hamiltonian and returns the ith wave function as u 
+    and w corresponding to the 3S1 and 3D1 channels where index is the ith 
+    sorted eigenvalue. The wave function is unitless, that is, the momenta 
+    and weights are factored in such that \sum_i { u(k_i)^2 + w(k_i)^2 } = 1. 
+    For an evolved wave function, enter in a unitary transformation U. Also
+    returns the eigenvalue in MeV.'''
+        
+    # Arguments
+        
+    # U (2-D NumPy array): Option to apply an SRG or Magnus unitary
+    # transformation to the wave function
+
+    # Diagonalize Hamiltonian
+    eigenvalues,eigenvectors = la.eig(H_matrix)
+    
+    eigenvalue = np.sort(eigenvalues)[index]
+    eigenvector_index = list(eigenvalues).index(eigenvalue)
+    psi = eigenvectors[:,eigenvector_index]
+
+    # Evolve wave function by applying unitary transformation U
+    if U.any():
+        psi = U @ psi
+        
+    u = psi[:120] # 3S1 part 
+    w = psi[120:] # 3D1 part
+        
+    # Check normalization in momentum-space
+    #normalization = np.sum((u**2+w**2))
+    #print('Normalization = %.4f (k-space)'%normalization)
+            
+    return u, w, eigenvalue
+    
+    
+def main(index, kvnn, kmax, kmid, method, generator, lamb, lambda_bd=0.00):
+    
+    cwd = getcwd()
+    
+    # Specify the potential
+    channel = '3S1'
+    ntot = 120
+    
+    # Load initial and evolved Hamiltonian
[…]

### 2019-05-23 scratchwork.py

@@ -1,140 +1,31 @@
 # Scratch Work
 
 # Test codes in progress in this script.
-# Last thing tested: Scattering state momentum distribution for 3S1 potential
+# Last thing tested: Re-write Wendt potential/omega files to new kvnn numbers
 
 
-from os import chdir, getcwd
-from matplotlib.offsetbox import AnchoredText
-import matplotlib.pyplot as plt
-import numpy as np
-import numpy.linalg as la
-# Python scripts made by A.T.
-from Figures import figures_functions as ff
-from Potentials.vsrg_macos import load_save_potentials as lp
+from os import chdir, getcwd, rename, walk
 
+cwd = getcwd()
 
-def wave_func(H_matrix, index, U=np.empty(0)):
-    '''Diagonalizes the Hamiltonian and returns the ith wave function as u 
-    and w corresponding to the 3S1 and 3D1 channels where index is the ith 
-    sorted eigenvalue. The wave function is unitless, that is, the momenta 
-    and weights are factored in such that \sum_i { u(k_i)^2 + w(k_i)^2 } = 1. 
-    For an evolved wave function, enter in a unitary transformation U. Also
-    returns the eigenvalue in MeV.'''
-        
-    # Arguments
-        
-    # U (2-D NumPy array): Option to apply an SRG or Magnus unitary
-    # transformation to the wave function
+#kvnn_new = '900'
+#kvnn_new = '901'
+kvnn_new = '902'
 
-    # Diagonalize Hamiltonian
-    eigenvalues,eigenvectors = la.eig(H_matrix)
+chdir('Potentials/vsrg_macos/vsrg_kvnn_%s_lam12.0_kmax30_kmid4_ntot120' % \
+      kvnn_new)
+
+for root, dirs, files in walk('.'):
     
-    eigenvalue = np.sort(eigenvalues)[index]
-    eigenvector_index = list(eigenvalues).index(eigenvalue)
-    psi = eigenvectors[:,eigenvector_index]
-
-    # Evolve wave function by applying unitary transformation U
-    if U.any():
-        psi = U @ psi
+    for name in files:
         
-    u = psi[:120] # 3S1 part 
-    w = psi[120:] # 3D1 part
+        name_list = name.split('_')
         
-    # Check normalization in momentum-space
[…]

### 2019-05-23 scattering_states.py
Update scattering_states.py

@@ -1,6 +1,7 @@
 # Created 05/23/19 by A.T. (tropiano.4@osu.edu)
 
-# Looking at scattering state momentum distribution for 3S1 potential
+# Looking at scattering state momentum distribution for 3S1 potential. This
+# needs to be generalized along with deuteron.py at some point.
 
 
 from os import chdir, getcwd

### 2019-05-23 phase_shifts.py
Update phase_shifts.py

@@ -1,11 +1,17 @@
-# 07/11/18
-# Calculates the phase shift as a function of energy from Magnus/SRG evolved
-# potential (coupled-channel).
-# Updated 09/25/18 to manually correct +/- shifts of pi in phase shifts
+# Created 07/11/18 by A.T. (tropiano.4@osu.edu)
+# Calculates NN phase shifts as a function of energy for the given potential.
+# Updated 09/25/18 by A.T. to manually correct +/- shifts of pi in phase shifts.
+
 
 import numpy as np
 import numpy.linalg as LA
 from scipy.interpolate import RectBivariateSpline,interp2d
+
+
+# Things to do: phase shifts should take coupled_channel Boolean variable as an
+# input. Use RectBivariateSpline as default (you can find interp2d method in
+# old codes if necessary). Good to have option to return one delta value. Keep
+# that format.
 
 class phase_shifts(object):
     

### 2019-05-23 phase_shifts.py
Update phase_shifts.py

@@ -11,9 +11,9 @@ from scipy.interpolate import RectBivariateSpline,interp2d
 # Things to do: phase shifts should take coupled_channel Boolean variable as an
 # input. Use RectBivariateSpline as default (you can find interp2d method in
 # old codes if necessary). Good to have option to return one delta value. Keep
-# that format.
+# that format. Make formatting equivalent to SRG, deuteron formatting.
 
-class phase_shifts(object):
+class Phase_shifts(object):
     
     def __init__(self,vnn,gp,gw,conv='Stapp',spline=True):
         '''Define constants, interpolate vnn (vnn should be input in units fm)'''

### 2019-05-23 deuteron.py
Update deuteron.py

@@ -16,6 +16,12 @@ from scipy.special import spherical_jn
 from scipy.interpolate import CubicSpline
 
 
+# Generalize this to any NN state (give energy of state and select closest
+# value)? Make epsilon = -2.22 MeV default. Or split this into returning the
+# deuteron wave function and observables using NN operators from operator.py.
+# Rename this observables.py?
+
+
 class Deuteron(object):
     
     

### 2019-05-23 operator.py
Create operator.py

@@ -1,0 +1,14 @@
+# Created 05/03/19 by A.T. (tropiano.4@osu.edu)
+
+# Operator code: ...
+
+
+import numpy as np
+import numpy.linalg as la
+from scipy.special import spherical_jn
+
+
+class Operator(object):
+    
+    def __init__(self):
+        

### 2019-05-23 phase_shifts.py
Update phase_shifts.py

@@ -13,38 +13,43 @@ from scipy.interpolate import RectBivariateSpline,interp2d
 # old codes if necessary). Good to have option to return one delta value. Keep
 # that format. Make formatting equivalent to SRG, deuteron formatting.
 
+
 class Phase_shifts(object):
     
-    def __init__(self,vnn,gp,gw,conv='Stapp',spline=True):
-        '''Define constants, interpolate vnn (vnn should be input in units fm)'''
+    
+    def __init__(self, V_matrix, k_array, k_weights, coupled_channel=False, 
+                 convention='Stapp'):
+        '''Define constants and interpolate potential.'''
+        
+        # Arguments
+        
+        # V (2-D NumPy array): Potential matrix in units fm^-2
+        # k_array (1-D NumPy array): Momentum array
+        # k_weights (1-D NumPy array): Momentum weights
+        # coupled_channel (Boolean): Value corresponding to whether the 
+        # potential is coupled channel or not
+        # convention (string): Convention for calculating phase shifts ('Stapp' 
+        # or 'Blatt')
         
         # Save convention
-        self.conv = conv
+        self.convention = convention
         
         # Maximum momentum in fm^-1
-        self.kmax = max(gp)
+        self.kmax = max(k_array)
 
-        # Units are fm^-1
-        self.gp = gp # Momenta array
-        self.gw = gw # Gaussian weights
-        # Dimension
-        N = len(gp)
+        # Save momentum and weights (units are fm^-1)
+        self.k_array = k_array # Momenta array
+        self.k_weights = k_weights # Momentum weights
+        # Dimension of momentum
+        N = len(k_array)
         self.dim = N
         
-        if spline:
-            # Interpolate each sub-block with RectBivariateSpline
-            self.V11_func = RectBivariateSpline(gp,gp,vnn[:N,:N])
-            self.V12_func = RectBivariateSpline(gp,gp,vnn[:N,N:2*N])
-            self.V21_func = RectBivariateSpline(gp,gp,vnn[N:2*N,:N])
-            self.V22_func = RectBivariateSpline(gp,gp,vnn[N:2*N,N:2*N])
-        else:
-            # Interpolate each sub-block with interp2d
-            self.V11_func = interp2d(gp,gp,vnn[:N,:N])
-            self.V12_func = interp2d(gp,gp,vnn[:N,N:2*N])
[…]

### 2019-05-23 SRG_codes/srg_wegner.py
Testing scipy ode for SRG.

@@ -5,7 +5,7 @@
 
 
 import numpy as np
-from scipy.integrate import odeint
+from scipy.integrate import odeint, ode
 
 
 class SRG(object):
@@ -85,7 +85,8 @@ class SRG(object):
         return A+(np.transpose(A)-np.diag(np.diag(A)))
     
     
-    def derivs(self, Hs_vector, s):
+    #def derivs(self, Hs_vector, s):
+    def derivs(self, s, Hs_vector):
         '''Returns RHS of SRG flow equation using the Wegner generator.'''
         
         # Arguments
@@ -144,3 +145,39 @@ class SRG(object):
             i += 1
         
         return d
+    
+    
+    def evolve_hamiltonian_ode(self, lambda_array):
+        '''Returns evolved Hamiltonian Hs_matrix at several values of lambda 
+        for given lambda array.'''
+    
+        # Arguments
+        
+        # lambda_array (1-D NumPy array): Array of lambda evolution values
+    
+        # Reshape initial hamiltonian to a vector
+        H0_vector = self.matrix2vector(self.H0_matrix)
+        
+        # Evaluate H(s) at the following values of lambda (or s)
+        s_array = 1.0/lambda_array**4.0
+        
+        # Set-up ODE
+        r = ode(self.derivs).set_integrator('vode', method='bdf')
+        r.set_initial_value(H0_vector, 0.0)
+        # Step-size
+        ds = 1e-5
+        
+        # Return a dictionary of H(s) at the values of s (i.e., d[1.2] returns 
+        # H(lambda=1.2) which is a matrix)
+        d = {}
+        i = 1
+        for s in s_array:
+            
+            while r.successful() and r.t < s:
+            
+                r.integrate(r.t+ds)
+            
+            d[lambda_array[i]] = self.vector2matrix(r.y)
+            i += 1
+        
+        return d        

### 2019-05-23 evolve_hamiltonian.py

@@ -57,12 +57,14 @@ def run_srg(kvnn, channel, kmax, kmid, ntot, generator, lambda_array, \
         
     elif generator == 'Block-diag':
         
-        cc = lp.coupled_channel(channel)
+        # Whether Hamiltonian is coupled channel or not (cc = True or False)
+        cc = lp.coupled_channel(channel) 
         evolve = srg_block_diagonal.SRG(H0_matrix, lambda_bd, k_array, cc)
         
     # Time the evolution and return dictionary d of evolved Hamiltonians
     t0 = time.time() # Start time
-    d = evolve.evolve_hamiltonian(lambda_array)
+    #d = evolve.evolve_hamiltonian(lambda_array)
+    d = evolve.evolve_hamiltonian_ode(lambda_array) # TESTING
     t1 = time.time() # End time
     
     mins = round((t1-t0)/60.0,2) # Minutes elapsed evolving H(s)
@@ -197,19 +199,19 @@ if __name__ == '__main__':
     #kvnn = 107 # RKE N3LO at Lambda = 500 MeV
     #kvnn = 111 # RKE N4LO at Lambda = 450 MeV
     #kvnn = 112 # RKE N4LO at Lambda = 500 MeV
-    #kvnn = 900 # Wendt at Lambda = 4 fm^-1
+    kvnn = 900 # Wendt at Lambda = 4 fm^-1
     #kvnn = 901 # Wendt at Lambda = 9 fm^-1
     #kvnn = 902 # Wendt at Lambda = 20 fm^-1
     #kvnn = 222  # Gezerlis et al N2LO local potential at R_0 = 1.0 fm cutoff
-    kvnn = 224  # Gezerlis et al 2LO local potential at R_0 = 1.2 fm cutoff
+    #kvnn = 224  # Gezerlis et al 2LO local potential at R_0 = 1.2 fm cutoff
     
     channel = '3S1'
     
-    #kmax = 30.0
-    #kmax = 8.0
-    kmax = 10.0
-    #kmid = 4.0
-    kmid = 2.0
+    kmax = 30.0
+    kmax = 8.0
+    #kmax = 10.0
+    kmid = 4.0
+    #kmid = 2.0
     ntot = 120
     
     
@@ -236,8 +238,8 @@ if __name__ == '__main__':
     #lambda_array = np.array([1.2])
     
     # Save the evolved Hamiltonian?
-    save = True
-    #save = False
+    #save = True
+    save = False
     
     
     # Evolve Hamiltonian

### 2019-05-29 operators.py
Splitting deuteron.py into operators.py and observables.py.

@@ -1,14 +1,208 @@
-# Created 05/03/19 by A.T. (tropiano.4@osu.edu)
+#!/usr/bin/env python3
 
-# Operator code: ...
+#------------------------------------------------------------------------------
+# File: operators.py
+#
+# Author:   A. J. Tropiano (tropiano.4@osu.edu)
+# Date:     May 29, 2019
+# 
+# Contains several functions for momentum-space operators. These functions can
+# be used in conjunction with functions from observables.py to calculate 
+# observable quantities such as the RMS radius. Or the functions can be used to
+# look at SRG evolved operators by applying unitary transformations to the
+# operator matrices.
+#
+# Notes:
+#   * The operators here only work for the 3S1 - 3D1 coupled channel. This code
+#     still needs to be generalized.
+#
+#------------------------------------------------------------------------------
 
 
 import numpy as np
-import numpy.linalg as la
 from scipy.special import spherical_jn
 
 
-class Operator(object):
+def find_q_index(q, k_array):
+    """
+    Finds the index of the k value nearest to q in the given momentum array.
+    For instance, say q = 3.0 fm^-1 and k_array does not contain 3.0 exactly.
+    Then this function would return an index corresponding to the k value
+    nearest to 3.0 in k_array (e.g. k_array[q_index] = 2.98 fm^-1).
     
-    def __init__(self):
-        '''.'''
+    Parameters
+    ----------
+    q : float
+        Momentum value in units fm^-1.
+    k_array : 1-D ndarray
+        Momentum array.
+        
+    Returns
+    -------
+    q_index : int
+        Index of the q (or nearest k) in k_array.
+        
+    """
+    
+    k_difference_array = abs(k_array - q)
+    k_difference_min = min(k_difference_array)
+    q_index = list(k_difference_array).index(k_difference_min)
+    
+    return q_index
+
+
+def momentum_projection_operator(q, k_array, k_weights, U=np.empty(0)):
+    """
+    ( a_q^dagger a_q ) momentum projection operator in momentum-space. When
+    applied to a wave function, returns the wave function at momentum value q.
+    For an evolved operator, enter in a unitary transformation U. The initial
+    operator is zero everywhere except where k, k' = q. For presentation, one
+    should divide out the momenta and weights by dividing by k_i * k_j *
+    Sqrt( w_i * w_j). This gives a mesh independent result.
[…]

### 2019-05-29 Figures/figures_functions.py
Updating srg_operator_evolution.ipynb to be compatible with new codes.
Specifically, needs to be updated along with operators.py and observables.py. Generated new figures with these codes. Most of the figures are the same but have over-written the old files in Figures/May_2019.

@@ -114,3 +114,38 @@ def kvnn_label_conversion(kvnn):
         label = r'$\Lambda = 20 \/ fm^{-1}$'
 
     return label
+
+
+def replace_periods_with_commas(file_name):
+    """
+    Replaces all periods in a file name with commas. This is necessary for
+    adding figures to LaTeX files which doesn't like periods unless they
+    specify a file type. For this reason, do not include the file type 
+    extension in the file name (i.e. .jpg, .pdf, etc.)
+    
+    Parameters
+    ----------
+    file_name : str
+        Original name of the file including periods.
+    
+    Returns
+    -------
+    new_file_name : str
+        New file name replacing periods with commas.
+        
+    """
+    
+    # Initialize new file name
+    new_file_name = ''
+    
+    # Loop over each character in the original file name and append to the new
+    # file name replacing periods with commas
+    for letter in file_name:
+        
+        if letter == '.':
+            
+            letter = ','
+            
+        new_file_name += letter
+        
+    return new_file_name

### 2019-05-29 observables.py
Further updates to observables.py and operators.py.
Using these two scripts in conjuction with srg_operator_evolution_figures.ipynb to generate figures for notes on SRG operator evolution.

@@ -1,13 +1,25 @@
-# Created 05/03/19 by A.T. (tropiano.4@osu.edu)
+#!/usr/bin/env python3
 
-# Deuteron code: Calculates observables for deuteron given an NN Hamiltonian 
-# (can be SRG evolved). The class contains functions that obtain the deuteron 
-# wave function in momentum-space, functions that calculate observable 
-# quantities, and functions that return operators in momentum-space.
-
-# Note to self: should probably generalize operator code to another script
-# independent of this. This code should use functions from the operator script
-# like r^2.
+#------------------------------------------------------------------------------
+# File: observables.py
+#
+# Author:   A. J. Tropiano (tropiano.4@osu.edu)
+# Date:     May 3, 2019
+# 
+# Contains several functions for calculation of NN observables given a
+# Hamiltonian. These functions can be used to look at wave functions or to 
+# calculate observable quantities with functions from operators.py
+#
+# Revision history:
+#   May 29, 2019 --- This file was renamed from deuteron.py to observables.py.
+#                    The idea was to generalize this code to observables for
+#                    any state given an NN potential.
+#
+# Notes:
+#   * Some functions here only work for the 3S1 - 3D1 coupled channel. This 
+#     code still needs to be further generalized.
+#
+#------------------------------------------------------------------------------
 
 
 import numpy as np
@@ -16,11 +28,125 @@ from scipy.special import spherical_jn
 from scipy.interpolate import CubicSpline
 
 
-# Generalize this to any NN state (give energy of state and select closest
-# value)? Make epsilon = -2.22 MeV default. Or split this into returning the
-# deuteron wave function and observables using NN operators from operator.py.
-# Rename this observables.py?
+def find_eps_index(eps, e_array):
+    """
+    Finds the index of the energy value nearest to eps in the given 
+    energy array. For instance, say eps = -2.22 MeV and energies does not 
+    contain -2.22 exactly. Then this function would return an index 
+    corresponding to the energy value nearest to -2.22 in e_array (e.g. 
+    e_array[eps_index] = -2.25 MeV).
+    
+    Parameters
+    ----------
+    eps : float
+        Energy value in units MeV.
+    e_array : 1-D ndarray
+        Energies array.
+        
+    Returns
+    -------
+    eps_index : int
[…]

### 2019-05-29 operators.py

@@ -40,7 +40,7 @@ def find_q_index(q, k_array):
     Returns
     -------
     q_index : int
-        Index of the q (or nearest k) in k_array.
+        Index of q (or nearest k) in k_array.
         
     """
     

### 2019-05-30 observables.py
Plotting momentum distributions.
Deuteron and continuum state momentum distribution figures have been generated and saved to Figures/May_2019.

@@ -25,7 +25,7 @@
 import numpy as np
 import numpy.linalg as la
 from scipy.special import spherical_jn
-from scipy.interpolate import CubicSpline
+#from scipy.interpolate import CubicSpline
 
 
 def find_eps_index(eps, e_array):

### 2019-05-30 scattering_states.py
Delete scattering_states.py.
This code has been implemented in "observables.py" and "srg_operator_evolution_figures.ipynb", hence being removed.

@@ -1,140 +1,0 @@
-# Created 05/23/19 by A.T. (tropiano.4@osu.edu)
-
-# Looking at scattering state momentum distribution for 3S1 potential. This
-# needs to be generalized along with deuteron.py at some point.
-
-
-from os import chdir, getcwd
-from matplotlib.offsetbox import AnchoredText
-import matplotlib.pyplot as plt
-import numpy as np
-import numpy.linalg as la
-# Python scripts made by A.T.
-from Figures import figures_functions as ff
-from Potentials.vsrg_macos import load_save_potentials as lp
-
-
-def wave_func(H_matrix, index, U=np.empty(0)):
-    '''Diagonalizes the Hamiltonian and returns the ith wave function as u 
-    and w corresponding to the 3S1 and 3D1 channels where index is the ith 
-    sorted eigenvalue. The wave function is unitless, that is, the momenta 
-    and weights are factored in such that \sum_i { u(k_i)^2 + w(k_i)^2 } = 1. 
-    For an evolved wave function, enter in a unitary transformation U. Also
-    returns the eigenvalue in MeV.'''
-        
-    # Arguments
-        
-    # U (2-D NumPy array): Option to apply an SRG or Magnus unitary
-    # transformation to the wave function
-
-    # Diagonalize Hamiltonian
-    eigenvalues,eigenvectors = la.eig(H_matrix)
-    
-    eigenvalue = np.sort(eigenvalues)[index]
-    eigenvector_index = list(eigenvalues).index(eigenvalue)
-    psi = eigenvectors[:,eigenvector_index]
-
-    # Evolve wave function by applying unitary transformation U
-    if U.any():
-        psi = U @ psi
-        
-    u = psi[:120] # 3S1 part 
-    w = psi[120:] # 3D1 part
-        
-    # Check normalization in momentum-space
-    #normalization = np.sum((u**2+w**2))
-    #print('Normalization = %.4f (k-space)'%normalization)
-            
-    return u, w, eigenvalue
-    
-    
-def main(index, kvnn, kmax, kmid, method, generator, lamb, lambda_bd=0.00):
-    
-    cwd = getcwd()
-    
-    # Specify the potential
-    channel = '3S1'
-    ntot = 120
-    
[…]

### 2019-05-30 Notes/SRG_operator_evolution/srg_operator_evolution.tex
Updates to Magnus notes.
Changed the name of files to "magnus" instead of "magnus_Jan08". Incorporated tropiano.bib from parent directory.
Updated SRG operator evolution notes.
Added several figures with minor changes to the outline.

--- 2019-05-20 Notes/Operator_evolution/operator_evolution_may20.tex
@@
-% Notes on SRG operator evolution project
-% Created 05/20/19 by A.T. (tropiano.4@osu.edu)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% File: srg_operator_evolution.tex
+%
+% Author: A. J. Tropiano (tropiano.4@osu.edu)
+% Date: May 20, 2019
+%
+% Notes on SRG operator evolution project.
+%
+% Revision history:
+% 	May 30, 2019 - Renamed srg_operator_evolution.tex from operator_evolution_May20.tex.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \usepackage{siunitx}
+\usepackage[caption=false]{subfig} % For sub-figures
 
@@
 		$^2$\mbox{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy,}  \\
-    \mbox{Michigan State University, East Lansing, MI 48824, USA}}
+		\mbox{Michigan State University, East Lansing, MI 48824, USA}
+}
 
@@
 
-Abstract goes here.
+Brief description of project.
 
@@
 
-Introduction goes here.
+Results on SRG-evolved operators from several NN potentials:
+\\
+-- How operators evolve from band- and block-diagonal SRG transformations.
+\\
+-- Operator evolution for different potentials (regulators, chiral order, etc.)
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Formalism}
-\label{sec:formalism}
+\section{Building SRG unitary transformations}
+\label{sec:srg_unitary_transformations}
 
-Is this section necessary for now?
+Brief description of how to make $U(s)$.
+\\
+
+Diagonalize initial and evolved Hamiltonians which we will call $H(0)$ and $H(s)$, respectively.
+This gives $\psi_{\alpha}(0)$ and $\psi_{\alpha}(s)$ for each eigenvalue indexed by $\alpha$.
+Then the SRG unitary transformation can be computed by taking a sum over outer products of the evolved and initial wave functions:
+
+\begin{eqnarray}
+	\label{eq:unitary_transformation}
+	U(s) = \sum_{\alpha=1}^{N} \ket{\psi_{\alpha}(s)} \bra{\psi_{\alpha}(0)},
+\end{eqnarray}
+
+where N is the dimension of the Hamiltonian matrix. Here the weights are factored into the wave functions, thus $U(s)$ is unitless.
+\\
+
+To evolve operators, we simply apply $U(s)$:
+
+\begin{eqnarray}
+	\label{eq:evolved_operator}
+	O(s) = U(s) O(0) U^{\dagger}(s),
+\end{eqnarray}
+
+where $O(0)$ is the bare operator.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\label{sec:results}
+\section{Operator evolution}
+\label{sec:operator_evolution}
 
-Organize this according to the figures: what story do the figures tell?
+Organize this according to the figures: what story do the figures tell? Format should be description of the calculation, followed by the figure, followed by takeaways.
+\\
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-\label{sec:conclusion}
+Add the following figures: momentum projection operator figures with accompanying momentum distributions for SRG transformations from N$^3$LO non-local potential \cite{Entem:2003ft}, N$^3$LO or N$^4$LO semi-local potentials \cite{Reinert:2017usi}, and N$^2$LO local potentials \cite{Gezerlis:2014zia}.
+\\
 
-Summarize.
+% Entem-Machleidt N3LO results
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn10_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn10_3S1_Block-diag2,00}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn10_3S1_Block-diag3,00}%
+	}
+	\caption{Caption.}
+	\label{momentum_projection_contours_q3,00_kvnn10}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q0,30_kvnn10_3S1_Wegner}
+	\caption{Caption.}
+	\label{momentum_projection_contours_q0,30_kvnn10}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.3\columnwidth]{deuteron_momentum_distribution_kvnn10_Wegner_lamb1,5}%
+	}
+	\quad
+	\subfloat[]{%
+	\includegraphics[clip,width=0.3\columnwidth]{deuteron_momentum_distribution_kvnn10_Block-diag2,00_lamb1,5}%
+	}
+	\quad
+	\subfloat[]{%
+	\includegraphics[clip,width=0.3\columnwidth]{deuteron_momentum_distribution_kvnn10_Block-diag3,00_lamb1,5}%
+	}
+	\caption{Caption.}
+	\label{deuteron_momentum_distribution_kvnn10}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.3\columnwidth]{continuum_state_momentum_distribution_eps200,0_kvnn10_Wegner_lamb1,5}%
+	}
+	\quad
+	\subfloat[]{%
+	\includegraphics[clip,width=0.3\columnwidth]{continuum_state_momentum_distribution_eps200,0_kvnn10_Block-diag2,00_lamb1,5}%
+	}
+	\quad
+	\subfloat[]{%
+	\includegraphics[clip,width=0.3\columnwidth]{continuum_state_momentum_distribution_eps200,0_kvnn10_Block-diag3,00_lamb1,5}%
+	}
+	\caption{Caption.}
+	\label{continuum_state_momentum_distribution_eps200,0_kvnn10}
+\end{figure}
+
+% RKE N3LO results
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn106_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn106_3S1_Block-diag2,00}%
+	}
+	\caption{Caption.}
+	\label{momentum_projection_contours_q3,00_kvnn106}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn107_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn107_3S1_Block-diag2,00}%
+	}
+	\caption{Caption.}
+	\label{momentum_projection_contours_q3,00_kvnn107}
+\end{figure}
+
+% RKE N4LO results
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn111_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn111_3S1_Block-diag2,00}%
+	}
+	\caption{Caption.}
+	\label{momentum_projection_contours_q3,00_kvnn111}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn112_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn112_3S1_Block-diag2,00}%
+	}
+	\caption{Caption.}
+	\label{momentum_projection_contours_q3,00_kvnn112}
+\end{figure}
+
+% Gez. et al. N2LO results
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn222_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn222_3S1_Block-diag2,00}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn222_3S1_Block-diag3,00}%
+	}
+	\caption{Caption.}
+	\label{momentum_projection_contours_q3,00_kvnn222}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn224_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn224_3S1_Block-diag2,00}%
+	}
+	\caption{Caption.}
+	\label{momentum_projection_contours_q3,00_kvnn224}
+\end{figure}
 
@@
 
-\bibliography{tropiano_bib}
+\bibliography{../tropiano_bib}
 

### 2019-05-31 Figures/figures_functions.py
Updated figures_functions.py.
Forgot to change the Wendt file kvnn numbers in one of the functions.

@@ -1,6 +1,14 @@
-# Created 05/03/19 by A.T. (tropiano.4@osu.edu)
+#!/usr/bin/env python3
 
+#------------------------------------------------------------------------------
+# File: figures_functions.py
+#
+# Author:   A. J. Tropiano (tropiano.4@osu.edu)
+# Date:     May 3, 2019
+# 
 # Functions useful for generating figures.
+#
+#------------------------------------------------------------------------------
 
 
 import datetime
@@ -9,9 +17,16 @@ from scipy.interpolate import interp2d
 
 
 def current_date():
-    '''This function returns the current month and year as string formatted as 
-    "Month_Year". This is used to save figures in the correct folder: 
-    /Figures/Month_Year.'''
+    """
+    This function is used to save figures in the correct folder: 
+    /Figures/Month_Year.
+    
+    Returns
+    -------
+    output : str
+        Current month and year as 'Month_Year'.
+    
+    """
     
     now = datetime.datetime.now()
 
@@ -51,15 +66,29 @@ def current_date():
 
 
 def interpolate_matrix(x_array, M, x_max, ntot=500):
-    '''Interpolate matrix over given array for contour plots. Returns 
-    interpolated matrix with new x array with ntot points up to x_max.'''
+    """
+    Interpolate matrix over given array for contour plots. Also adds more
+    points to given x_array.
     
-    # Arguments
-    
-    # x_array (1-D NumPy array): An array of x points (e.g. momentum array)
-    # M (2-D NumPy array): A matrix dependent on points x (e.g. Hamiltonian)
-    # x_max (float): Maximum value of x for extent of interpolation
-    # ntot (integer): Number of points for interpolation
+    Parameters
+    ----------
+    x_array : 1-D ndarray
+        Array of x points where the matrix M = M(x, x).
+    M : 2-D ndarray
+        Matrix to be interpolated.
+    x_max : float
+        Maximum value of x. This functions interpolates M up to this value.
+    ntot : int, optional
+        Desired length of the interpolated matrix and new x array.
+        
+    Returns
+    -------
+    x_array_new : 1-D ndarray
+        Array of ntot x points.
+    M_new : 2-D ndarray
+        Interpolated matrix.
+        
+    """
     
[…]

### 2019-05-31 Notes/SRG_operator_evolution/srg_operator_evolution.tex
Updates to SRG operator evolution notes.
Added captions to figures.

@@
 % Revision history:
-% 	May 30, 2019 - Renamed srg_operator_evolution.tex from operator_evolution_May20.tex.
+% 	May 31, 2019 - Renamed to srg_operator_evolution.tex from operator_evolution_May20.tex. Added a description of computing SRG unitary
+%                              transformations. Added momentum projection operator contours and momentum distribution plots.                            
 %
@@
 	}
-	\caption{Caption.}
+	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the Entem-Machleidt N$^3$LO non-local potential with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).
+Here $q=3$ fm$^{-1}$.}
 	\label{momentum_projection_contours_q3,00_kvnn10}
@@
 	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q0,30_kvnn10_3S1_Wegner}
-	\caption{Caption.}
+	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the Entem-Machleidt N$^3$LO non-local potential with the Wegner generator.
+Here $q=0.3$ fm$^{-1}$.}
 	\label{momentum_projection_contours_q0,30_kvnn10}
@@
 	}
-	\caption{Caption.}
+	\caption{Momentum probability densities of the deuteron SRG-evolving the wave function to $\lambda=1.5$ fm$^{-1}$ from the Entem-Machleidt N$^3$LO non-local potential with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).
+The black dotted line corresponds to the momentum probability density of the initial deuteron wave function.}
 	\label{deuteron_momentum_distribution_kvnn10}
@@
 	}
-	\caption{Caption.}
+	\caption{Momentum probability densities of the continuum state at $\epsilon \approx 200$ MeV SRG-evolving the wave function to $\lambda=1.5$ fm$^{-1}$ from the Entem-Machleidt N$^3$LO non-local potential with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).
+The black dotted line corresponds to the initial momentum probability density.}
 	\label{continuum_state_momentum_distribution_eps200,0_kvnn10}
@@
 	}
-	\caption{Caption.}
+	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the RKE N$^3$LO semi-local potential with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b).
+Here $q=3$ fm$^{-1}$ and the EFT cutoff is $450$ MeV.}
 	\label{momentum_projection_contours_q3,00_kvnn106}
@@
 	}
-	\caption{Caption.}
+	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the RKE N$^3$LO semi-local potential with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b).
+Here $q=3$ fm$^{-1}$ and the EFT cutoff is $500$ MeV.}
 	\label{momentum_projection_contours_q3,00_kvnn107}
@@
 	}
-	\caption{Caption.}
+	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the RKE N$^4$LO semi-local potential with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b).
+Here $q=3$ fm$^{-1}$ and the EFT cutoff is $450$ MeV.}
 	\label{momentum_projection_contours_q3,00_kvnn111}
@@
 	}
-	\caption{Caption.}
+	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the RKE N$^4$LO semi-local potential with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b).
+Here $q=3$ fm$^{-1}$ and the EFT cutoff is $500$ MeV.}
 	\label{momentum_projection_contours_q3,00_kvnn112}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.3\columnwidth]{continuum_state_momentum_distribution_eps200,0_kvnn111_Wegner_lamb1,5}%
+	}
+	\quad
+	\subfloat[]{%
+	\includegraphics[clip,width=0.3\columnwidth]{continuum_state_momentum_distribution_eps200,0_kvnn111_Block-diag2,00_lamb1,5}%
+	}
+	\quad
+	\subfloat[]{%
+	\includegraphics[clip,width=0.3\columnwidth]{continuum_state_momentum_distribution_eps200,0_kvnn111_Block-diag3,00_lamb1,5}%
+	}
+	\caption{Momentum probability densities of the continuum state at $\epsilon \approx 200$ MeV SRG-evolving the wave function to $\lambda=1.5$ fm$^{-1}$ from the RKE N$^4$LO semi-local potential with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).
+The black dotted line corresponds to the initial momentum probability density.
+Here the EFT cutoff is $450$ MeV.}
+	\label{continuum_state_momentum_distribution_eps200,0_kvnn111}
 \end{figure}
@@
 	}
-	\caption{Caption.}
+	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the Gezerlis et al.
+N$^2$LO local potential with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).
+Here $q=3$ fm$^{-1}$ and the EFT cutoff is $1$ fm.}
 	\label{momentum_projection_contours_q3,00_kvnn222}
@@
 	}
-	\caption{Caption.}
+	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the Gezerlis et al.
+N$^2$LO local potential with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b).
+Here $q=3$ fm$^{-1}$ and the EFT cutoff is $1.2$ fm.}
 	\label{momentum_projection_contours_q3,00_kvnn224}

### 2019-05-31 Notes/SRG_operator_evolution/srg_operator_evolution.tex
Updates to SRG operator evolution notes.
Further updates to the outline. Splitting results sections by non-local, semi-local, and local potentials. Also, adding a section for details of calculations where momentum and weights can be confusing.

@@
 
+\tableofcontents
+
 \newpage
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Building SRG unitary transformations}
+\section{Mathematical/computational details}
+\label{sec:math_comp_details}
+
+%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Building SRG unitary transformations}
 \label{sec:srg_unitary_transformations}
@@
 
+%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Momentum projection operator: $a^{\dagger}_q a_q$}
+\label{sec:momentum_proj_operator}
+
+%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Momentum distribution function: $\phi^2$}
+\label{sec:momentum_dist_funcs}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Operator evolution}
-\label{sec:operator_evolution}
+\section{Results}
+\label{sec:results}
 
 Organize this according to the figures: what story do the figures tell? Format should be description of the calculation, followed by the figure, followed by takeaways.
-\\
 
-Add the following figures: momentum projection operator figures with accompanying momentum distributions for SRG transformations from N$^3$LO non-local potential \cite{Entem:2003ft}, N$^3$LO or N$^4$LO semi-local potentials \cite{Reinert:2017usi}, and N$^2$LO local potentials \cite{Gezerlis:2014zia}.
-\\
-
-% Entem-Machleidt N3LO results
+%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Entem-Machleidt N$^3$LO non-local potential}
+\label{sec:nonlocal_results}
 
@@
 \end{figure}
+
+%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{RKE N$^3$LO and N$^4$LO semi-local potentials}
+\label{sec:semilocal_results}
 
@@
 
-% Gez. et al. N2LO results
+%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Gezerlis N$^2$LO local potentials}
+\label{sec:local_results}
 

### 2019-06-03 run_srg.py
Update run_srg.py

@@ -142,11 +142,11 @@ if __name__ == '__main__':
     #kvnn = 107 # RKE N3LO at Lambda = 500 MeV
     #kvnn = 111 # RKE N4LO at Lambda = 450 MeV
     #kvnn = 112 # RKE N4LO at Lambda = 500 MeV
+    #kvnn = 222  # Gezerlis et al N2LO local potential at R_0 = 1.0 fm cutoff
+    #kvnn = 224  # Gezerlis et al N2LO local potential at R_0 = 1.2 fm cutoff
     #kvnn = 900 # Wendt at Lambda = 4 fm^-1
     #kvnn = 901 # Wendt at Lambda = 9 fm^-1
     #kvnn = 902 # Wendt at Lambda = 20 fm^-1
-    #kvnn = 222  # Gezerlis et al N2LO local potential at R_0 = 1.0 fm cutoff
-    #kvnn = 224  # Gezerlis et al N2LO local potential at R_0 = 1.2 fm cutoff
     
     channel = '3S1'
     

### 2019-06-03 Notes/SRG_operator_evolution/srg_operator_evolution.tex
Updated SRG operator evolution notes.
Added brief descriptions of how to numerically compute momentum projection operators and distributions

@@
 % Revision history:
-% 	May 31, 2019 - Renamed to srg_operator_evolution.tex from operator_evolution_May20.tex. Added a description of computing SRG unitary
-%                              transformations. Added momentum projection operator contours and momentum distribution plots.                            
+% 	05/31/19 --- Renamed magnus.tex from magnus_Jan08.tex. - Renamed to srg_operator_evolution.tex from operator_evolution_May20.tex.
+%			   Added a description of computing SRG unitary transformations. Added momentum projection operator contours and momentum %                         distribution plots.
+%	06/03/19 --- Added brief descriptions of how to numerically compute momentum projection operators and distributions.                           
 %
@@
 
+Applying $a^{\dagger}_q a_q$ to a wave function $\psi(k)$ returns $\psi(q)$.
+For the discrete case, $\psi(k_i)$ is an $N \times 1$ vector and $a^{\dagger}_q a_q (k_i, k_j)$ is an $N \times N$ matrix where $i$, $j=1$, ...
+, $N$.
+Then $a^{\dagger}_q a_q$ acting on $\psi(k)$ is a matrix multiplication, implying a continuous integration over $d^3k$.
+Therefore, we include a factor of $1 / (k^2 dk) \implies 1 / (k_i k_j \sqrt{w_i w_j})$ in $a^{\dagger}_q a_q (k_i, k_j)$ where $w$ represents the momentum weights.
+In matrix form,
+
+\begin{eqnarray}
+	\label{eq:momentum_projection_operator}
+	a^{\dagger}_q a_q (k_i, k_j) = \frac{\delta_{k_i q} \delta_{k_j q}}{k_i k_j \sqrt{w_i w_j}},
+\end{eqnarray}
+
+which has units fm$^3$. To evolve operators, we apply $U(s)$ at this point. For mesh-independent figures, we must divide by an additional factor of $k_i k_j \sqrt{w_i w_j}$.
+
 %------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
@@
 \label{sec:momentum_dist_funcs}
+
+We diagonalize the Hamiltonian for eigenvectors $\phi_{\alpha}$.
+In the $^{3}S_1$-$^{3}D_1$ coupled channel, the S-component is given by $\phi_{\alpha}[:N]$ and the D-component by $\phi_{\alpha}[N:]$ where $N$ is the length of the momentum mesh.
+Then the momentum distribution is given by,
+
+\begin{eqnarray}
+	\label{eq:momentum_distribution}
+	|\phi(k)|^2 = |\phi_{\alpha}[:N]|^2 + |\phi_{\alpha}[N:]|^2.
+\end{eqnarray}
+
+This satisfies the normalization condition $\sum_{i=1}^N |\phi(k_i)|^2 = 1$, implying that the factor $k^2 dk$ (or in the discrete case $k_i^2 w_i$) is factored into the wave function.
+For mesh-independent figures, divide by $k_i^2 w_i$.
 
@@
 
-Organize this according to the figures: what story do the figures tell? Format should be description of the calculation, followed by the figure, followed by takeaways.
+Organize this according to the figures. Format should be description of the calculation (previous section), followed by the figure, followed by takeaways.
 
@@
 \label{sec:nonlocal_results}
+
+\textcolor{red}{Add takeaways for these figures.}
 
@@
 \label{sec:semilocal_results}
+
+\textcolor{red}{Add takeaways for these figures.}
 
@@
 
+\textcolor{red}{Add takeaways for these figures.}
+
 \begin{figure}[H]

### 2019-06-03 Potentials/vsrg_macos/load_save_potentials.py
Update load_save_potentials.py
Changed save_omega function.

@@ -527,7 +527,7 @@ def save_potential(k_array, k_weights, V, kvnn, channel, kmax, kmid, ntot,
     
     
 def save_omega(k_array, O, kvnn, channel, kmax, kmid, ntot, generator, lamb,
-               lambda_bd=0.00, k_magnus=6, ds=1e-5):
+               k_magnus, ds=1e-5):
     ''''''
     """
     Saves a Magnus evolved omega matrix.
@@ -549,15 +549,12 @@ def save_omega(k_array, O, kvnn, channel, kmax, kmid, ntot, generator, lamb,
     ntot : int
         Number of momentum points in mesh.
     generator : str
-        SRG generator 'Wegner', 'T', or 'Block-diag'.
+        SRG generator 'Wegner' or 'T'.
     lamb : float
         Evolution parameter lambda in units fm^-1.
-    lambda_bd : float, optional
-        Lambda value for block-diagonal decoupling (e.g. 2.00 fm^-1).
-    k_magnus : int, optional
-        Number of terms to include in Magnus sum (for Magnus only).
-    ds : float, optional
-        Step-size in the flow parameter s (for Magnus only).
+    k_magnus : int
+        Number of terms to include in Magnus sum (that is,
+        dOmega / dlambda ~ \sum_0^k_magnus ... )
         
     """
 
@@ -578,15 +575,8 @@ def save_omega(k_array, O, kvnn, channel, kmax, kmid, ntot, generator, lamb,
     chdir(potential_directory)
     
     # Name omega file and save
-    if generator == 'Block-diag':
-            
-        omega_file = 'omega_%s_kvnn_%s_%s%.2f_lambda%.1f_k%d_ds%.1e.out'%(
-                      channel, kvnn_string, generator, lambda_bd, lamb,
-                      k_magnus, ds)
-    else: 
-            
-        omega_file = 'omega_%s_kvnn_%s_%s_lambda%.1f_k%d_ds%.1e.out'%(channel,
-                      kvnn_string, generator, lamb, k_magnus, ds)
+    omega_file = 'omega_%s_kvnn_%s_%s_lambda%.1f_k%d_ds%.1e.out'%(channel,
+                  kvnn_string, generator, lamb, k_magnus, ds)
     
     f = open(omega_file,'w')
     

### 2019-06-03 Magnus_codes/magnus_split.py
Updates to Magnus codes.
Mostly formatting updates. Added several comments. Created run_magnus.py script separate from run_srg.py.

@@ -1,17 +1,38 @@
 #!/usr/bin/env python3
 
 #------------------------------------------------------------------------------
-# File: magnus_kinetic_energy.py
+# File: magnus_split.py
 #
 # Author:   A. J. Tropiano (tropiano.4@osu.edu)
 # Date:     June 3, 2019
 # 
 # Evolves Hamiltonian to band-diagonal, decoupled form with flow parameter s 
-# using the relative kinetic energy generator and the Magnus implementation.
+# using the Wegner generator and the Magnus "split thing" implementation. The
+# split thing method involves solving the Euler method equation for the 
+# difference in omega matrices,
+# 
+#   delta_omega = Omega(s_{i+1}) - Omega(s_i) = derivative(Omega, s) * ds.
+# 
+# We take the matrix delta_omega and use the BCH formula to update the evolving
+# Hamiltonian at each step in s,
+#
+#   H(s_{i+1}) = exp^(delta_omega) * H(s_i) * exp^(-delta_omega).
+#
+# Since Omega(s_{i+1}) - Omega(s_i) is directly proportional to ds, we can tune
+# ds to a small enough value to prevent delta_omega from diverging to infinity.
+# This method prevents the Magnus evolution from running into NaN or infinity
+# errors. However, we cannot save the full omega matrix since we only deal with
+# differences in the omega matrix.
 #
 # Notes:
-#   * Tried to do lambda differential equation similar to SRG codes but kept
-#     getting infinity errors in computing omega matrix.
+#   * For kvnn = 902 or 6 where this method is necessary, use ds = 10^-7. This
+#     will take a considerable amount of time to evolve but eventually works 
+#     (t ~ 8 days).
+#   * Currently this script is not set-up in run_magnus.py. For split thing
+#     runs, must use this script manually.
+#   * For very small step-sizes, ds ~ 10^-7, the Wegner SRG generator matches
+#     the relative kinetic energy generator. For this reason, we only need this
+#     Wegner version of the split thing method.
 #
 #------------------------------------------------------------------------------
 
@@ -24,24 +45,22 @@ from sympy import bernoulli
 class Magnus(object):
     
     
-    def __init__(self, H_initial, T_rel, k_magnus, ds=1e-5):
+    def __init__(self, H_initial, k_magnus, ds):
         """
-        Saves the initial Hamiltonian and relative kinetic energy in units 
-        fm^-2 and the length of the matrices. Also saves the number of terms in
-        the Magnus omega derivative equation, k_magnus, and the Euler method 
[…]

### 2019-06-03 Magnus_codes/magnus_wegner.py

@@ -1,41 +1,62 @@
-# Created 05/06/19 by A.T. (tropiano.4@osu.edu)
+#!/usr/bin/env python3
 
-# Magnus code: Evolves Hamiltonian to band-diagonal, decoupled form with 
-# parameter s using the Wegner generator.
+#------------------------------------------------------------------------------
+# File: magnus_wegner.py
+#
+# Author:   A. J. Tropiano (tropiano.4@osu.edu)
+# Date:     June 3, 2019
+# 
+# Evolves Hamiltonian to band-diagonal, decoupled form with flow parameter s 
+# using the Wegner generator and the Magnus implementation.
+#
+# Notes:
+#   * Tried to do lambda differential equation similar to SRG codes but kept
+#     getting infinity errors in computing omega matrix. Thus, we use the flow
+#     parameter s, which has worked before.
+#
+#------------------------------------------------------------------------------
 
 
 from math import factorial
 import numpy as np
-#from scipy.linalg import expm # Option to use this instead of BCH formula
 from sympy import bernoulli
 
 
 class Magnus(object):
     
     
-    def __init__(self, H0_matrix, k_magnus, ds):
-        '''Saves the initial Hamiltonian in units fm^-2 and dimension of the 
-        matrix. Also saves the number of terms to be summed in the Magnus
-        Omega(s) derivative sum.'''
+    def __init__(self, H_initial, k_magnus, ds=1e-5):
+        """
+        Saves the initial Hamiltonian in units fm^-2 and the length of the 
+        matrix. Also saves the number of terms in the Magnus omega derivative
+        equation, k_magnus, and the Euler method step-size ds. Initializes
+        arrays for factorials and Bernoulli numbers.
         
-        # Arguments
+        Parameters
+        ----------
+        H_initial : 2-D ndarray
+            Initial Hamiltonian matrix in units MeV.
+        k_magnus : int
+            Number of terms to include in Magnus sum (that is,
+            dOmega / ds ~ \sum_0^k_magnus ... )
+        ds : float, optional
+            Step-size in the flow parameter s.
         
-        # H0_matrix (2-D NumPy array): Hamiltonian matrix in units MeV
-        # k_magnus (integer): Number of terms to include in Magnus sum
-        # ds (float): Step-size in the flow parameter s
+        """
         
         # h-bar^2 / M [MeV fm^2]
         hbar_sq_over_M = 41.47
         
-        # Save matrices in units fm^-2
[…]

### 2019-06-03 run_magnus.py

@@ -1,28 +1,16 @@
 #!/usr/bin/env python3
 
 #------------------------------------------------------------------------------
-# File: srg_block_diagonal.py
+# File: run_magnus.py
 #
 # Author:   A. J. Tropiano (tropiano.4@osu.edu)
-# Date:     May 1, 2019
+# Date:     June 3, 2019
 # 
-# Revision history:
-#   May 28, 2019 --- Solve flow equation with respect to parameter lambda and 
-#                    use SciPy's ode function.
-# 
-# Evolves Hamiltonian to block-diagonal, decoupled form with flow parameter 
-# lambda [fm^-1] using the block-diagonal generator.
+# Magnus evolves a given Hamiltonian in units MeV. The run_magnus function 
+# returns a dictionary of the evolved Hamiltonian (in scattering units [fm^-2])
+# and omega matrix at each point in lambda (which serves as the key).
 #
 #------------------------------------------------------------------------------
-
-# Created 05/01/19 by A.T. (tropiano.4@osu.edu)
-# Updated 05/07/19 by A.T. to run Magnus implementation
-
-# Run SRG or Magnus. This script runs an SRG or Magnus evolution for a given
-# Hamiltonian in units MeV. SRG code return a dictionary of the evolved 
-# Hamiltonian (in units fm^-2) at each point in lambda (which serves as the 
-# key). Magnus code returns the evolved Hamiltonian and Omega matrix at a given
-# value of lambda.
 
 
 import numpy as np
@@ -33,94 +21,116 @@ from Magnus_codes import magnus_wegner
 from Magnus_codes import magnus_kinetic_energy
 
 
-def run_magnus(kvnn, channel, kmax, kmid, ntot, method, generator, lambda_array, \
+def run_magnus(kvnn, channel, kmax, kmid, ntot, generator, lambda_array,
                k_magnus=6, ds=1e-5, save=True):
-    '''This function evolves a specified Hamiltonian to several values of
-    lambda [fm^-1] and has the option to save the evolved potentials.'''
+    """
+    Magnus evolves a specified Hamiltonian to several values of lambda [fm^-1]
+    and has the option to save the evolved potentials and omega matrices.
     
-    # Arguments
-    
-    # kvnn (integer): This number specifies the potential
[…]

### 2019-06-03 test.py
Update test.py
Testing Magnus codes. Trial run with magnus_wegner.py on kvnn = 900 potential.

@@ -9,8 +9,8 @@
 # The purpose of this script is to test out codes.
 #
 # Last thing tested:
-#   Using plots to verify correct SRG evolution of various potentials with
-#   updates to SRG code.
+#   Using plots to verify correct Magnus evolution of various potentials with
+#   updates to Magnus code.
 #
 #------------------------------------------------------------------------------
 
@@ -20,11 +20,11 @@ import matplotlib.pyplot as plt
 from matplotlib.offsetbox import AnchoredText
 from Potentials.vsrg_macos import load_save_potentials as lp
 
-kvnn = 6
+#kvnn = 6
 #kvnn = 10
 #kvnn = 105
 #kvnn = 222
-#kvnn = 900
+kvnn = 900
 
 channel = '3S1'
 
@@ -37,11 +37,10 @@ kmid = 4.0
 
 ntot = 120
 
-#gen = 'Wegner'
-gen = 'T'
-#gen = 'Block-diag'
-lambda_bd = 2.00
-#lambda_bd = 3.00
+gen = 'Wegner'
+#gen = 'T'
+
+k_magnus = 6
 
 k_array = lp.load_momentum(kvnn, channel, kmax, kmid, ntot)[0]
     
@@ -57,8 +56,9 @@ d = {}
 for lamb in lambda_list:
 
     # Load potential
-    V_full = lp.load_potential(kvnn, channel, kmax, kmid, ntot, method='srg', 
-                               generator=gen, lamb=lamb, lambda_bd=lambda_bd)
+    V_full = lp.load_potential(kvnn, channel, kmax, kmid, ntot, 
+                               method='magnus', generator=gen, lamb=lamb, 
+                               k_magnus=k_magnus)
     # Resize to S-S block
     V = V_full[:120, :120]
     
@@ -72,9 +72,6 @@ if gen == 'Wegner':
     G_lbl = r'$G=H_{D}$'
 elif gen == 'T':
     G_lbl = r'$G=T_{rel}$'
-elif gen == 'Block-diag':
-    G_lbl = r'$G=H_{BD}$' + '\n' + r'$\Lambda_{BD} = %.2f \/ fm^{-1}$' \
-            % lambda_bd
     
 # Limits of color bar in fm
 mx = 1.0

### 2019-06-03 SRG_codes/srg_block_diagonal.py
Updates to SRG codes.
Very minor formatting changes.

@@ -183,7 +183,7 @@ class SRG(object):
         ----------
         lamb : float
             Evolution parameter lambda in units fm^-1.
-        H_evolved : 2-D ndarray
+        H_evolved : 1-D ndarray
             Evolving Hamiltonian which is a vector and function of lambda. 
             Units are fm^-2.
         
@@ -213,7 +213,7 @@ class SRG(object):
 
     def evolve_hamiltonian(self, lambda_initial, lambda_array):
         """
-        Evolved Hamiltonian H_matrix at each value of lambda in lambda_array.
+        Evolved Hamiltonian at each value of lambda in lambda_array.
         
         Parameters
         ----------
@@ -253,7 +253,7 @@ class SRG(object):
         # Loop over lambda values in lambda_array
         for lamb in lambda_array:
             
-            # Solve ode up to lamb and store in dictionary
+            # Solve ODE up to lamb and store in dictionary
             while solver.successful() and solver.t > lamb:
             
                 # Select step-size depending on extent of evolution

### 2019-06-03 SRG_codes/srg_kinetic_energy.py

@@ -33,7 +33,7 @@ class SRG(object):
         ----------
         H_initial : 2-D ndarray
             Initial Hamiltonian matrix in units MeV.
-        T : 2-D ndarray
+        T_rel : 2-D ndarray
             Relative kinetic energy matrix in units MeV.
         
         """
@@ -156,7 +156,7 @@ class SRG(object):
         ----------
         lamb : float
             Evolution parameter lambda in units fm^-1.
-        H_evolved : 2-D ndarray
+        H_evolved : 1-D ndarray
             Evolving Hamiltonian which is a vector and function of lambda. 
             Units are fm^-2.
         
@@ -188,7 +188,7 @@ class SRG(object):
 
     def evolve_hamiltonian(self, lambda_initial, lambda_array):
         """
-        Evolved Hamiltonian H_matrix at each value of lambda in lambda_array.
+        Evolved Hamiltonian at each value of lambda in lambda_array.
         
         Parameters
         ----------
@@ -228,7 +228,7 @@ class SRG(object):
         # Loop over lambda values in lambda_array
         for lamb in lambda_array:
             
-            # Solve ode up to lamb and store in dictionary
+            # Solve ODE up to lamb and store in dictionary
             while solver.successful() and solver.t > lamb:
             
                 # Select step-size depending on extent of evolution

### 2019-06-03 SRG_codes/srg_wegner.py

@@ -151,7 +151,7 @@ class SRG(object):
         ----------
         lamb : float
             Evolution parameter lambda in units fm^-1.
-        H_evolved : 2-D ndarray
+        H_evolved : 1-D ndarray
             Evolving Hamiltonian which is a vector and function of lambda. 
             Units are fm^-2.
         
@@ -181,7 +181,7 @@ class SRG(object):
 
     def evolve_hamiltonian(self, lambda_initial, lambda_array):
         """
-        Evolved Hamiltonian H_matrix at each value of lambda in lambda_array.
+        Evolved Hamiltonian at each value of lambda in lambda_array.
         
         Parameters
         ----------
@@ -221,7 +221,7 @@ class SRG(object):
         # Loop over lambda values in lambda_array
         for lamb in lambda_array:
             
-            # Solve ode up to lamb and store in dictionary
+            # Solve ODE up to lamb and store in dictionary
             while solver.successful() and solver.t > lamb:
             
                 # Select step-size depending on extent of evolution

### 2019-06-03 Potentials/vsrg_macos/load_save_potentials.py
Update to load_save_potentials.py.
Very minor formatting changes.

@@ -130,7 +130,8 @@ def load_potential(kvnn, channel, kmax, kmid, ntot, method='initial',
     lambda_bd : float, optional
         Lambda value for block-diagonal decoupling (e.g. 2.00 fm^-1).
     k_magnus : int, optional
-        Number of terms to include in Magnus sum (for Magnus only).
+        Number of terms to include in Magnus sum (that is,
+        dOmega / ds ~ \sum_0^k_magnus ... for Magnus only).
     ds : float, optional
         Step-size in the flow parameter s (for Magnus only).
         
@@ -275,7 +276,8 @@ def load_hamiltonian(kvnn, channel, kmax, kmid, ntot, method='initial',
     lambda_bd : float, optional
         Lambda value for block-diagonal decoupling (e.g. 2.00 fm^-1).
     k_magnus : int, optional
-        Number of terms to include in Magnus sum (for Magnus only).
+        Number of terms to include in Magnus sum (that is,
+        dOmega / ds ~ \sum_0^k_magnus ... for Magnus only).
     ds : float, optional
         Step-size in the flow parameter s (for Magnus only).
         
@@ -305,8 +307,8 @@ def load_hamiltonian(kvnn, channel, kmax, kmid, ntot, method='initial',
     return H
 
 
-def load_omega(kvnn, channel, kmax, kmid, ntot, generator, lamb, 
-               lambda_bd=0.00, k_magnus=6, ds=1e-5):
+def load_omega(kvnn, channel, kmax, kmid, ntot, generator, lamb, k_magnus=6,
+               ds=1e-5):
     """
     Loads a Magnus evolved omega matrix.
     
@@ -326,10 +328,9 @@ def load_omega(kvnn, channel, kmax, kmid, ntot, generator, lamb,
         SRG generator 'Wegner', 'T', or 'Block-diag'.
     lamb : float
         Evolution parameter lambda in units fm^-1.
-    lambda_bd : float, optional
-        Lambda value for block-diagonal decoupling (e.g. 2.00 fm^-1).
     k_magnus : int, optional
-        Number of terms to include in Magnus sum.
+        Number of terms to include in Magnus sum (that is,
+        dOmega / ds ~ \sum_0^k_magnus ... )
     ds : float, optional
         Step-size in the flow parameter s.
         
[…]

### 2019-06-03 Notes/SRG_operator_evolution/srg_operator_evolution.tex
Re-generated SRG-evolved potential figures from srg_operator_evolution_figures.ipynb
Made a minor change with the SRG generator label. Also had to had the figures to the Figures directory within the SRG_operator_evolution notes folder.

@@
 
-Results on SRG-evolved operators from several NN potentials:
+Results on SRG-evolved operators from several NN potentials.
 \\
@@
 \label{sec:srg_unitary_transformations}
-
-Brief description of how to make $U(s)$.
-\\
 
@@
 %------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Momentum distribution function: $\phi^2$}
+\subsection{Momentum distribution function: $\phi^2(k)$}
 \label{sec:momentum_dist_funcs}
 
-We diagonalize the Hamiltonian for eigenvectors $\phi_{\alpha}$.
-In the $^{3}S_1$-$^{3}D_1$ coupled channel, the S-component is given by $\phi_{\alpha}[:N]$ and the D-component by $\phi_{\alpha}[N:]$ where $N$ is the length of the momentum mesh.
-Then the momentum distribution is given by,
+We diagonalize the Hamiltonian for eigenvectors $\psi_{\alpha}$.
+In the $^{3}S_1$-$^{3}D_1$ coupled channel, the S-component is given by $\psi_{\alpha}[:N]$ and the D-component by $\psi_{\alpha}[N:]$ where $N$ is the length of the momentum mesh.
+Then the momentum distribution of the state $\alpha$ is given by,
 
@@
 	\label{eq:momentum_distribution}
-	|\phi(k)|^2 = |\phi_{\alpha}[:N]|^2 + |\phi_{\alpha}[N:]|^2.
+	|\phi_{\alpha}(k)|^2 = |\psi_{\alpha}[:N]|^2 + |\psi_{\alpha}[N:]|^2.
 \end{eqnarray}
 
-This satisfies the normalization condition $\sum_{i=1}^N |\phi(k_i)|^2 = 1$, implying that the factor $k^2 dk$ (or in the discrete case $k_i^2 w_i$) is factored into the wave function.
+This satisfies the normalization condition $\sum_{i=1}^N |\phi(k_i)|^2 = 1$, implying that the factor $k^2 dk$ (or in the discrete case, $k_i^2 w_i$) is factored into the wave function.
 For mesh-independent figures, divide by $k_i^2 w_i$.
@@
 
-\textcolor{red}{Add takeaways for these figures.}
+Non-local potential from \cite{Entem:2003ft}.
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Block-diag2,00}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Block-diag3,00}%
+	}
+	\caption{Caption.}
+	\label{potential_contours_kvnn10_3S1}
+\end{figure}
 
@@
 \end{figure}
+
+-- The top row of Fig.~\ref{momentum_projection_contours_q3,00_kvnn10} should match the top row in Fig. 4 of \cite{Anderson:2010aq}.
+-- Smeared delta function comment.
+-- Compared block-diagonal to Wegner.
+-- Another note about block-diagonal.
 
@@
 
-\textcolor{red}{Add takeaways for these figures.}
+\textcolor{red}{Add takeaways for these figures.} Semi-local potentials from \cite{Reinert:2017usi}.
 
 % RKE N3LO results
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn106_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn106_3S1_Block-diag2,00}%
+	}
+	\caption{Caption.}
+	\label{potential_contours_kvnn106_3S1}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn107_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn107_3S1_Block-diag2,00}%
+	}
+	\caption{Caption.}
+	\label{potential_contours_kvnn111_3S1}
+\end{figure}
 
@@
 % RKE N4LO results
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn111_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn111_3S1_Block-diag2,00}%
+	}
+	\caption{Caption.}
+	\label{potential_contours_kvnn111_3S1}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn112_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn112_3S1_Block-diag2,00}%
+	}
+	\caption{Caption.}
+	\label{potential_contours_kvnn112_3S1}
+\end{figure}
 
@@
 
-\textcolor{red}{Add takeaways for these figures.}
+\textcolor{red}{Add takeaways for these figures.} Local potentials from \cite{Gezerlis:2014zia}.
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn222_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn222_3S1_Block-diag2,00}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn222_3S1_Block-diag3,00}%
+	}
+	\caption{Caption.}
+	\label{potential_contours_kvnn222_3S1}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn224_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn224_3S1_Block-diag2,00}%
+	}
+	\caption{Caption.}
+	\label{potential_contours_kvnn224_3S1}
+\end{figure}
 

### 2019-06-04 Figures/figures_functions.py
Re-organized figures.
Now organizing figures by topic instead of date. For example, SRG operator evolution figures go to Figures/SRG_operator_evolution. LaTeX notes use these figures directly.

@@ -16,55 +16,6 @@ import numpy as np
 from scipy.interpolate import interp2d
 
 
-def current_date():
-    """
-    This function is used to save figures in the correct folder: 
-    /Figures/Month_Year.
-    
-    Returns
-    -------
-    output : str
-        Current month and year as 'Month_Year'.
-    
-    """
-    
-    now = datetime.datetime.now()
-
-    # Current month
-    month = now.month
-    # Convert month from integer to string
-    if month == 1:
-        month = 'January'
-    elif month == 2:
-        month = 'February'
-    elif month == 3:
-        month = 'March'
-    elif month == 4:
-        month = 'April'
-    elif month == 5:
-        month = 'May'
-    elif month == 6:
-        month = 'June'
-    elif month == 7:
-        month = 'July'
-    elif month == 8:
-        month = 'August'
-    elif month == 9:
-        month = 'September'
-    elif month == 10:
-        month = 'October'
-    elif month == 11:
-        month = 'November'
-    elif month == 12:
-        month = 'December'
-        
-    # Current year
-    year = now.year
-    
-    # Return current date as Month_Year (e.g. February_1994)
-    return '%s_%d'%(month,year)
-
-
 def interpolate_matrix(x_array, M, x_max, ntot=500):
     """
     Interpolate matrix over given array for contour plots. Also adds more
@@ -123,7 +74,8 @@ def interpolate_matrix(x_array, M, x_max, ntot=500):
 def kvnn_label_conversion(kvnn):
     """
     Converts a kvnn number to a label for plotting purposes (e.g. kvnn = 6 
-    gives 'AV18').
+    gives 'AV18'). THIS NEEDS TO BE UPDATED! DO THIS FOR SRG OPERATOR EVOLUTION
+    FIGURES!
     
     Parameters
     ----------

### 2019-06-04 Notes/SRG_operator_evolution/srg_operator_evolution.tex
Added SRG-evolved potential figures to these SRG operator evolution notes.
Re-organized figures.
Now organizing figures by topic instead of date. For example, SRG operator evolution figures go to Figures/SRG_operator_evolution. LaTeX notes use these figures directly.
Added captions to SRG-evolved potential figures.

@@
 % 	05/31/19 --- Renamed magnus.tex from magnus_Jan08.tex. - Renamed to srg_operator_evolution.tex from operator_evolution_May20.tex.
-%			   Added a description of computing SRG unitary transformations. Added momentum projection operator contours and momentum %                         distribution plots.
-%	06/03/19 --- Added brief descriptions of how to numerically compute momentum projection operators and distributions.                           
+%			   Added a description of computing SRG unitary transformations. Added momentum projection operator contours and momentum
+%                         distribution plots.
+%	06/03/19 --- Added brief descriptions of how to numerically compute momentum projection operators and distributions. Also added SRG-
+%        		   evolved potential contours for comparison with other operators.                  
 %
@@
 \usepackage{graphicx}
-\graphicspath{{Figures/}} % Setting the graphics path
+\graphicspath{{../../Figures/SRG_operator_evolution/}} % Setting the graphics path
 \usepackage{physics} % For bra-ket notation
@@
 	}
-	\caption{Caption.}
+	\caption{Matrix elements of the Entem-Machleidt N$^3$LO non-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).}
 	\label{potential_contours_kvnn10_3S1}
@@
 -- The top row of Fig.~\ref{momentum_projection_contours_q3,00_kvnn10} should match the top row in Fig. 4 of \cite{Anderson:2010aq}.
+\\
 -- Smeared delta function comment.
+\\
 -- Compared block-diagonal to Wegner.
+\\
 -- Another note about block-diagonal.
@@
 	}
-	\caption{Caption.}
+	\caption{Matrix elements of the RKE N$^3$LO semi-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b).
+Here the EFT cutoff is $450$ MeV.}
 	\label{potential_contours_kvnn106_3S1}
@@
 	}
-	\caption{Caption.}
+	\caption{Matrix elements of the RKE N$^3$LO semi-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b).
+Here the EFT cutoff is $500$ MeV.}
 	\label{potential_contours_kvnn111_3S1}
@@
 	}
-	\caption{Caption.}
+	\caption{Matrix elements of the RKE N$^4$LO semi-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b).
+Here the EFT cutoff is $450$ MeV.}
 	\label{potential_contours_kvnn111_3S1}
@@
 	}
-	\caption{Caption.}
+	\caption{Matrix elements of the RKE N$^4$LO semi-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b).
+Here the EFT cutoff is $500$ MeV.}
 	\label{potential_contours_kvnn112_3S1}
@@
 	}
-	\caption{Caption.}
+	\caption{Matrix elements of the Gezerlis et al.~N$^2$LO local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).
+Here the EFT cutoff is $1$ fm.}
 	\label{potential_contours_kvnn222_3S1}
@@
 	}
-	\caption{Caption.}
+	\caption{Matrix elements of the Gezerlis et al.~N$^2$LO local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b).
+Here the EFT cutoff is $1.2$ fm.}
 	\label{potential_contours_kvnn224_3S1}
@@
 	}
-	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the Gezerlis et al.
-N$^2$LO local potential with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).
+	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the Gezerlis et al.~N$^2$LO local potential with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).
 Here $q=3$ fm$^{-1}$ and the EFT cutoff is $1$ fm.}
@@
 	}
-	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the Gezerlis et al.
-N$^2$LO local potential with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b).
+	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the Gezerlis et al.~N$^2$LO local potential with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b).
 Here $q=3$ fm$^{-1}$ and the EFT cutoff is $1.2$ fm.}

### 2019-06-04 observables.py
Update observables.py
Very minor change.

@@ -79,6 +79,7 @@ def wave_function(H_matrix, eps=-2.22, U=np.empty(0)):
     -------
     psi : 1-D ndarray
         Wave function for the specified state (unitless).
+        
     """
     
     # Diagonalize Hamiltonian
@@ -148,6 +149,7 @@ def quadrupole_moment_from_kspace(psi):
     
     return None
 
+# Old deuteron observables code
 class Deuteron(object):
     
     

### 2019-06-04 observables.py
Update observables.py
Minor change.

@@ -30,10 +30,10 @@ from scipy.special import spherical_jn
 
 def find_eps_index(eps, e_array):
     """
-    Finds the index of the energy value nearest to eps in the given 
-    energy array. For instance, say eps = -2.22 MeV and energies does not 
-    contain -2.22 exactly. Then this function would return an index 
-    corresponding to the energy value nearest to -2.22 in e_array (e.g. 
+    Finds the index of the energy value nearest to eps in the given energy
+    array. For instance, say eps = -2.22 MeV and energies does not contain
+    -2.22 exactly. Then this function would return an index corresponding to 
+    the energy value nearest to -2.22 in e_array (e.g. 
     e_array[eps_index] = -2.25 MeV).
     
     Parameters

### 2019-06-10 Magnus_codes/magnus_kinetic_energy.py
No major changes. See description.
Magnus-evolved potentials differ very slighly from old files in Evolved_Hamiltonians folder from before. This is due to minor changes in how the evolved potentials are written or possibly switching from Python 2 to 3. It is possible to reproduce the numbers from before using strictly files in the old directory.

@@ -21,6 +21,7 @@
 
 from math import factorial
 import numpy as np
+from scipy.linalg import expm # Add to revision history for this
 from sympy import bernoulli
 
 
@@ -151,7 +152,9 @@ class Magnus(object):
         """
         
         # Compute the evolving Hamiltonian with the BCH formula
-        H_evolved = self.bch_formula(self.H_initial, O_evolved, 25)
+        #H_evolved = self.bch_formula(self.H_initial, O_evolved, 25)
+        # Use expm instead
+        H_evolved = expm(O_evolved) @ self.H_initial @ expm(-O_evolved)
         
         # Load relative kinetic energy in scattering units [fm^-2]
         T_rel = self.T_rel
@@ -210,20 +213,7 @@ class Magnus(object):
 
             # Next step in s
             O_evolved += self.derivative(O_evolved) * ds
-                
-            # Check for NaN's and infinities
-            # If true, stop evolving
-            if np.isnan(O_evolved).any() or np.isinf(O_evolved).any():
-                    
-                print('_'*85)
-                error = 'Infinities or NaNs encountered in omega matrix.'
-                print(error)
-                print('s = %.5e' % s)
-                suggestion = 'Try running magnus_split.py instead.'
-                print(suggestion)
-                    
-                return None
-                
+
             # Step to next s value
             s += ds
                 
@@ -290,7 +280,9 @@ class Magnus(object):
             d['omega'][lamb] = O_evolved
                 
             # Evaluate the evolved Hamiltonian matrix using the BCH formula
-            H_evolved = self.bch_formula(H_initial, O_evolved, 25)
+            #H_evolved = self.bch_formula(H_initial, O_evolved, 25)
+            # Use expm instead
+            H_evolved = expm(O_evolved) @ H_initial @ expm(-O_evolved)
             
             # Store evolved Hamiltonian matrix in dictionary
             d['hamiltonian'][lamb] = H_evolved

### 2019-06-10 Magnus_codes/magnus_wegner.py

@@ -23,7 +23,7 @@
 
 from math import factorial
 import numpy as np
-#from scipy.linalg import expm
+from scipy.linalg import expm
 from sympy import bernoulli
 
 
@@ -151,9 +151,9 @@ class Magnus(object):
         """
         
         # Compute the evolving Hamiltonian with the BCH formula
-        H_evolved = self.bch_formula(self.H_initial, O_evolved, 25)
+        #H_evolved = self.bch_formula(self.H_initial, O_evolved, 25)
         # Use expm instead
-        #H_evolved = expm(O_evolved) @ self.H_initial @ expm(-O_evolved)
+        H_evolved = expm(O_evolved) @ self.H_initial @ expm(-O_evolved)
 
         # Wegner SRG generator, eta = [G,H] where G = H_D (diagonal of the 
         # evolving Hamiltonian)
@@ -210,19 +210,6 @@ class Magnus(object):
 
             # Next step in s
             O_evolved += self.derivative(O_evolved) * ds
-                
-            # Check for NaN's and infinities
-            # If true, stop evolving
-            if np.isnan(O_evolved).any() or np.isinf(O_evolved).any():
-                    
-                print('_'*85)
-                error = 'Infinities or NaNs encountered in omega matrix.'
-                print(error)
-                print('s = %.5e' % s)
-                suggestion = 'Try running magnus_split.py instead.'
-                print(suggestion)
-                    
-                return None
                 
             # Step to next s value
             s += ds
@@ -290,9 +277,9 @@ class Magnus(object):
             d['omega'][lamb] = O_evolved
                 
             # Evaluate the evolved Hamiltonian matrix using the BCH formula
-            H_evolved = self.bch_formula(H_initial, O_evolved, 25)
+            #H_evolved = self.bch_formula(H_initial, O_evolved, 25)
             # Use expm instead
-            #H_evolved = expm(O_evolved) @ H_initial @ expm(-O_evolved)
+            H_evolved = expm(O_evolved) @ H_initial @ expm(-O_evolved)
             
             # Store evolved Hamiltonian matrix in dictionary
             d['hamiltonian'][lamb] = H_evolved

### 2019-06-10 run_magnus.py

@@ -81,11 +81,23 @@ def run_magnus(kvnn, channel, kmax, kmid, ntot, generator, lambda_array,
     # Time the evolution and return dictionary d of evolved Hamiltonians and
     # omega matrices where the keys are lambda values
     t0 = time.time() # Start time
-    d = evolve.evolve_hamiltonian(lambda_array)
+    # Check for OverflowError (this occurs when omega grows to infinity)
+    try:
+        d = evolve.evolve_hamiltonian(lambda_array)
+    except OverflowError:
+        print('_'*85)
+        print('Infinities NaNs encountered in omega matrix.')
+        print('Try using a smaller step-size or running magnus_split.py.')
+        return None
+    except ValueError:
+        print('_'*85)
+        print('Infinities NaNs encountered in omega matrix.')
+        print('Try using a smaller step-size or running magnus_split.py.')
+        return None
     t1 = time.time() # End time
     
     # Print details
-    mins = round((t1-t0)/60.0,2) # Minutes elapsed evolving H(s)
+    mins = round( (t1 - t0) / 60.0, 2) # Minutes elapsed evolving H(s)
     print('_'*85)
     print( 'H(s) done evolving to final lambda = %.1f fm^-1 after %f minutes'
           % (lambda_array[-1], mins) )
@@ -104,22 +116,9 @@ def run_magnus(kvnn, channel, kmax, kmid, ntot, generator, lambda_array,
 
             # Scattering units here [fm^-2]
             H_evolved = d['hamiltonian'][lamb]
-            # The evolved Hamiltonian will be None if there was an error in
-            # the Magnus evolution
-            
-            # Check for Magnus errors with try except
-            try:
-                
-                # Subtract off kinetic energy (need to convert T_rel from MeV
-                # to fm^-2)
-                V_evolved = H_evolved - T_rel / hbar_sq_over_M
-                
-            # There will be a TypeError when Magnus encounters NaNs or 
-            # infinities in the omega matrix
-            except TypeError:
-                
-                # Error statement is printed by Magnus scripts
-                return d
+            # Subtract off kinetic energy (need to convert T_rel from MeV to
+            # fm^-2)
+            V_evolved = H_evolved - T_rel / hbar_sq_over_M
             
             # Save evolved potential
[…]

### 2019-06-10 run_srg.py

@@ -98,7 +98,7 @@ def run_srg(kvnn, channel, kmax, kmid, ntot, generator, lambda_array,
     t1 = time.time() # End time
     
     # Print details
-    mins = round((t1-t0)/60.0,2) # Minutes elapsed evolving H(s)
+    mins = round( (t1 - t0) / 60.0, 2) # Minutes elapsed evolving H(s)
     print('_'*85)
     print( 'H(s) done evolving to final lambda = %.1f fm^-1 after %f minutes'
           % (lambda_array[-1], mins) )

### 2019-06-10 test.py

@@ -9,39 +9,65 @@
 # The purpose of this script is to test out codes.
 #
 # Last thing tested:
-#  Running run_magnus.py for the following: kvnn = 900-901, G= 'Wegner' and 
-#  'T', and k_magnus = 2, 6, and 10.
+#   Compare H(s) from run_magnus.py dictionary and saved H(s) in
+#   Potentials/vsrg_macos.
 #
 #------------------------------------------------------------------------------
 
 
 import numpy as np
 from run_magnus import run_magnus
+from Potentials.vsrg_macos import load_save_potentials as lp
 
+def vector2matrix(B,anti_hermitian=True):
+    '''Takes the vector of a top right matrix and returns the full matrix. If 
+    anti_hermitian = True, assumes B corresponds to a anti-hermitian matrix. If 
+    false, assumes B corresponds to a hermitian matrix.'''
+        
+    # Dimension of the vectorized matrix
+    n = len(B)
+    # Dimension of matrix (given by solving N*(N+1)/2 = n for N where n = len(B))
+    N = int( (-1 + np.sqrt(1+8*n) ) / 2 )
+    # Initialize matrix
+    A = np.zeros((N,N))
+    
+    # Build upper half of A with diagonal
 
-# Potential details
-kvnn_list = [900, 901]
+    first = 0
+    last = N
+
+    for i in range(N):
+
+        A[i,i:] = B[first:last]
+        first = last
+        last += N-i-1
+
+    # Reflect upper half to lower half to build full matrix
+    # [np.transpose(A)-np.diag(np.diag(A))] is the lower half of A excluding 
+    # the diagonal
+    if anti_hermitian:
+        return A-(np.transpose(A)-np.diag(np.diag(A)))
+    else: # Hermitian
+        return A+(np.transpose(A)-np.diag(np.diag(A)))
+
+# Set-up
+kvnn = 901
 channel = '3S1'
 kmax = 30.0
 kmid = 4.0
 ntot = 120
-    
-# Evolution details
-generator_list = ['Wegner', 'T']
-lambda_array = np.array( [10.0] )
-ds = 1e-6
-#lambda_array = np.array( [2.8, 2.0, 1.2] )
-#ds = 1e-5
-k_magnus_list = [2, 6, 10]    
 
-# Save the evolved Hamiltonian and omega?
-save = True
-    
-# Loop over each option
-for kvnn in kvnn_list:
[…]

### 2019-06-10 Notes/Magnus/magnus.tex
Updates to Magnus notes.
Changed the name of files to "magnus" instead of "magnus_Jan08". Incorporated tropiano.bib from parent directory.
Re-organized figures.
Now organizing figures by topic instead of date. For example, SRG operator evolution figures go to Figures/SRG_operator_evolution. LaTeX notes use these figures directly.
Minor updates to notes.

--- 2019-05-02 Notes/Magnus/magnus_Jan08.tex
@@
-% Notes on Magnus project
-% Created 01/08/19 by A.T. (tropiano.4@osu.edu)
-% Update: transitioning these notes into a draft of the eventual paper
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% File: magnus.tex
+%
+% Author: A. J. Tropiano (tropiano.4@osu.edu)
+% Date: January 8, 2019
+%
+% Notes on Magnus project.
+%
+% Revision history:
+% 	03/04/19 --- Transitioning these notes into a draft of the eventual paper.
+%     05/30/19 --- Renamed magnus.tex from magnus_Jan08.tex.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \usepackage{graphicx}
+% NOTE: Do not get rid of this path until all figures in Figures sub-folder are re-produced
 \graphicspath{{Figures/}} % Setting the graphics path
+% NEW PATH
+\graphicspath{{../../Figures/Magnus/}} % Setting the graphics path
 \usepackage{physics} % For bra-ket notation
 \usepackage{siunitx}
+\usepackage[caption=false]{subfig} % For sub-figures
 
@@
 
-\affiliation{
+\affiliation{%
 		$^1$\mbox{Department of Physics, The Ohio State University, Columbus, OH 43210, USA}  \\
 		$^2$\mbox{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy,}  \\
-    \mbox{Michigan State University, East Lansing, MI 48824, USA}}
+    		\mbox{Michigan State University, East Lansing, MI 48824, USA}
+}
 
@@
 \begin{abstract}
+
 \noindent{-- Test Magnus expansion SRG implementation on LO NN potential at high $\Lambda$. (Define SRG or IMSRG acronym in abstract.)}
@@
 -- Lastly, study operator evolution.
+
 \end{abstract}
@@
 
-\noindent{-- In recent years \textit{ab initio} methods have made strides in nuclear structure and reactions.}
+\noindent{%
+-- In recent years \textit{ab initio} methods have made strides in nuclear structure and reactions.
+}
 \\
@@
 
-\noindent{-- The IMSRG procedure requires solving a system of nonlinear, coupled differential equations which can often be stiff necessitating a high-order ODE solver.}
+\noindent{%
+-- The IMSRG procedure requires solving a system of nonlinear, coupled differential equations which can often be stiff necessitating a high-order ODE solver.
+}
 \\
@@
 
-\noindent{-- A variant of the IMSRG that utilizes the Magnus expansion can overcome these limitations.}
+\noindent{%
+-- A variant of the IMSRG that utilizes the Magnus expansion can overcome these limitations.
+}
 \\
@@
 
-\noindent{-- We test the Magnus implementation on chiral non-local NN potentials in free-space for several EFT cutoffs.}
+\noindent{%
+-- We test the Magnus implementation on chiral non-local NN potentials in free-space for several EFT cutoffs.
+}
 \\
@@
 
-\noindent{-- The past decade has seen a tremendous increase in the number of chiral NN potentials.}
+\noindent{%
+-- The past decade has seen a tremendous increase in the number of chiral NN potentials.
+}
 \\
@@
 
-\noindent{-- The rest of the paper is organized as follows:}
+\noindent{%
+-- The rest of the paper is organized as follows:
+}
 \\
@@
 
-\noindent{\textbf{SRG formalism}}
+\noindent{%
+\textbf{SRG formalism}
+}
 \\
@@
 
-\noindent{\textbf{Magnus expansion formalism}}
+\noindent{%
+\textbf{Magnus expansion formalism}
+}
 \\
@@
 \\
-\textcolor{red}{-- Here or earlier (for the following bullets)? Better to motivate the Magnus in the introduction or easier to explain given mathematical detail?}
+\textcolor{red}{%
+-- Here or earlier (for the following bullets)? Better to motivate the Magnus in the introduction or easier to explain given mathematical detail?
+}
 \\
@@
 
-\noindent{\textbf{Evolution of potentials}}
+\noindent{%
+\textbf{Evolution of potentials}
+}
 \\
@@
 \\
-\textcolor{red}{-- Option: add new regularization schemes?}
+\textcolor{red}{%
+-- Option: add new regularization schemes?
+}
 \\
@@
 
-\noindent{-- First, we compare Magnus to SRG evolution for large cutoff potentials with $G=H_D$ and $G=T_{rel}$.}
+\noindent{%
+-- First, we compare Magnus to SRG evolution for large cutoff potentials with $G=H_D$ and $G=T_{rel}$.
+}
 \\
@@
 %
-\noindent{-- Furthermore, it is dependent on the momentum mesh on which the potential is generated.}
+\noindent{%
+-- Furthermore, it is dependent on the momentum mesh on which the potential is generated.
+}
 \\
@@
 %
-\noindent{-- Figures \ref{fig:evolved_diags_Wendt_Lamb9_Wegner} and \ref{fig:evolved_diags_Wendt_Lamb9_T} show a more quantitative depiction of the evolved potentials.}
+\noindent{%
+-- Figures \ref{fig:evolved_diags_Wendt_Lamb9_Wegner} and \ref{fig:evolved_diags_Wendt_Lamb9_T} show a more quantitative depiction of the evolved potentials.
+}
 \\
@@
 \\
-\textcolor{red}{-- Unnecessary?
+\textcolor{red}{%
+-- Unnecessary?
 \\
@@
 \\
--- In the previous cases (and all other cases unless specified otherwise), we take $ds=10^-5$.}
+-- In the previous cases (and all other cases unless specified otherwise), we take $ds=10^-5$.
+}
 \\
 
-\noindent{\textbf{Observables}}
+\noindent{%
+\textbf{Observables}
+}
 \\
@@
 
-\noindent{\textcolor{red}{UPDATED UP TO HERE 04/03/19}}
+\noindent{%
+	\textcolor{red}{%
+	UPDATED UP TO HERE 04/03/19
+	}
+}
 \\
@@
 %
-\noindent{-- RMS radius and quadrupole moment of deuteron.}
+\noindent{%
+-- RMS radius and quadrupole moment of deuteron.
+}
 \\
@@
 
-\noindent{-- Summarize.}
+\noindent{%
+-- Summarize.
+}
 \\
@@
 
-\bibliography{tropiano_srg}
+\bibliography{../tropiano_bib}
 

### 2019-06-10 Notes/SRG_operator_evolution/srg_operator_evolution.tex
Minor updates to notes.

@@
 
-\affiliation{
+\affiliation{%
 		$^1$\mbox{Department of Physics, The Ohio State University, Columbus, OH 43210, USA} \\
@@
 Then the SRG unitary transformation can be computed by taking a sum over outer products of the evolved and initial wave functions:
-
+%
 \begin{eqnarray}
@@
 \end{eqnarray}
-
+%
 where N is the dimension of the Hamiltonian matrix. Here the weights are factored into the wave functions, thus $U(s)$ is unitless.
@@
 To evolve operators, we simply apply $U(s)$:
-
+%
 \begin{eqnarray}
@@
 \end{eqnarray}
-
+%
 where $O(0)$ is the bare operator.
@@
 In matrix form,
-
+%
 \begin{eqnarray}
@@
 \end{eqnarray}
-
+%
 which has units fm$^3$. To evolve operators, we apply $U(s)$ at this point. For mesh-independent figures, we must divide by an additional factor of $k_i k_j \sqrt{w_i w_j}$.
@@
 Then the momentum distribution of the state $\alpha$ is given by,
-
+%
 \begin{eqnarray}
@@
 \end{eqnarray}
-
+%
 This satisfies the normalization condition $\sum_{i=1}^N |\phi(k_i)|^2 = 1$, implying that the factor $k^2 dk$ (or in the discrete case, $k_i^2 w_i$) is factored into the wave function.

### 2019-06-13 Notes/Magnus/magnus.tex
Update magnus.tex
Added comments and edits.

@@
 %     05/30/19 --- Renamed magnus.tex from magnus_Jan08.tex.
+%     06/13/19 --- Added comments for editing purposes.
 %
@@
 \\
--- One choice of generator where the deep bound state is decoupled outside low-momentum and another where it is shifted to low-momentum.
+-- One choice of generator decouples the deep bound state outside low-momentum and another shifts it to low-momentum.
 \\
@@
 
+% Comments on this paragraph:
+% Maybe go with SRG first then mention IMSRG as an extension in solving the many-body problem.
 \noindent{%
@@
 \\
+% Replace the bullet below. See IMSRG term paper.
 -- One can use the decoupled Hamiltonian to solve the many-body Sch{\"o}dinger equation extracting specific eigenvalues and eigenstates which qualifies the IMSRG as an \textit{ab initio} method.
@@
 \\
+% Re-word the bullet below.
 -- From the form of the transformation, the numerical error leaves the unitarity of the evolved Hamiltonian un-affected.
@@
 \\
+% Need transition sentence here.
 
@@
 \\
+% Keep the last bullet in mind for the focus of this paper.
 
@@
 \\
--- With the Magnus evolved operators, we calculate several observables and explore operator evolution.
+-- With the Magnus-evolved operators, we calculate several observables and explore operator evolution.
 \\
@@
 \\
--- It is convenient to define $\lambda \equiv s^{-1/4}$ which roughly measures the width of the diagonal in the decoupled operator.
+-- It is convenient to define $\lambda \equiv s^{-1/4}$ which roughly measures the width of the band-diagonal in the decoupled operator.
 \\
@@
 %
--- As $k \rightarrow \infty$ in both sums in Eqns. (\ref{eq:magnus_omega}) and (\ref{eq:bch}) the Magnus transformation matches the SRG transformation.
+-- As $k \rightarrow \infty$ in both sums in Eqns. (\ref{eq:magnus_omega}) and (\ref{eq:bch}) the Magnus transformation matches the SRG transformation exactly.
 \\
@@
 \\
--- In the next section, we discuss results from Magnus evolved large-cutoff potentials focusing on the flow of the potential, observables, and operator evolution.
+-- In the next section, we discuss results from Magnus-evolved large-cutoff potentials focusing on the flow of the potential, observables, and operator evolution.
 
@@
 \\
--- In this section, we Magnus evolve LO non-local potentials in the $^{3}S_1-^{3}D_1$ channel at cutoffs of $\Lambda=4$, $9$, and $20 \, fm^{-1}$.
+-- In this section, we Magnus-evolve LO non-local potentials in the $^{3}S_1-^{3}D_1$ channel at cutoffs of $\Lambda=4$, $9$, and $20 \, fm^{-1}$.
 \\
@@
 \\
--- In \cite{Wendt:2011qj}, potentials at large-cutoffs were SRG evolved with $G=H_D$ and $G=T_{rel}$.
+-- In \cite{Wendt:2011qj}, potentials at large-cutoffs were SRG-evolved with $G=H_D$ and $G=T_{rel}$.
 \\
@@
 	\hspace*{0.05\textwidth}
-	\caption{Contours of Magnus evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=H_{D}$ for $\lambda=2.8$ (left), $2.0$ (middle), and $1.2$ (right) $fm^{-1}$ and truncations in the Magnus $k_{max}=2$ (top), $6$ (middle), and $10$ (bottom).}
+	\caption{Contours of Magnus-evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=H_{D}$ for $\lambda=2.8$ (left), $2.0$ (middle), and $1.2$ (right) $fm^{-1}$ and truncations in the Magnus $k_{max}=2$ (top), $6$ (middle), and $10$ (bottom).}
 	\label{fig:magnus_contours_Wendt_Lamb9_Wegner}
@@
   	\hspace*{0.05\textwidth}
-  	\caption{Contours of Magnus evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=T_{rel}$ for $\lambda=2.8$ (left), $2.0$ (middle), and $1.2$ (right) $fm^{-1}$ and truncations in the Magnus $k_{max}=2$ (top), $6$ (middle), and $10$ (bottom).}
+  	\caption{Contours of Magnus-evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=T_{rel}$ for $\lambda=2.8$ (left), $2.0$ (middle), and $1.2$ (right) $fm^{-1}$ and truncations in the Magnus $k_{max}=2$ (top), $6$ (middle), and $10$ (bottom).}
   	\label{fig:magnus_contours_Wendt_Lamb9_T}
@@
 \\
--- The black dotted line corresponds to the SRG evolved potential whereas the other lines are Magnus evolved potentials for different $k_{max}$ for diagonal and far-off diagonal matrix elements of $V_{\lambda}(k,k')$.
+-- The black dotted line corresponds to the SRG-evolved potential whereas the other lines are Magnus-evolved potentials for different $k_{max}$ for diagonal and far-off diagonal matrix elements of $V_{\lambda}(k,k')$.
 \\
@@
 	\captionsetup{singlelinecheck=false,justification=raggedright}
-	\caption{Relative error on the deuteron bound state energy and the root mean square of eigenvalues where $\tilde{\epsilon}$ denotes an eigenvalue of an SRG or Magnus evolved Hamiltonian for $\Lambda=9 \, fm^{-1}$ and $\lambda=1.2 \, fm^{-1}$.}
+	\caption{Relative error on the deuteron bound state energy and the root mean square of eigenvalues where $\tilde{\epsilon}$ denotes an eigenvalue of an SRG or Magnus-evolved Hamiltonian for $\Lambda=9 \, fm^{-1}$ and $\lambda=1.2 \, fm^{-1}$.}
 	\label{tab:energies}
@@
 \\
--- The errors on the Magnus energies are within the region of floating-point error whereas the SRG compounds error in solving the ODE \ref{eq:srg_flow}.
+-- The errors on the Magnus energies are within the region of floating-point error whereas the SRG compounds error in solving the ODE (\ref{eq:srg_flow}).
 \\
--- We have also checked the phase shifts from the evolved potentials match the bare potentials in all cases for Magnus and SRG evolution.
+-- We have also checked that the phase shifts from the evolved potentials match the bare potentials in all cases for Magnus and SRG evolution.
 \\ 
@@
 \\
+% Make sure it's clear that the distributions are not unitarily equivalent.
 -- Figure \ref{fig:momentum_dist_Wendt_Lamb9} shows the deuteron momentum probability density, $|\phi(k)|^2$, on a semi-log scale as a function of momentum for both band-diagonal generators.
@@
 }
+% Re-do the figure below with larger fonts. Can also split into LaTeX sub-plots (a) and (b).
 \\
@@
   	\hspace*{0.05\textwidth}
-  	\caption{Momentum probability densities of the deuteron comparing the un-evolved wavefunction (black dotted line), SRG evolved wavefunction (blue dashed line), and two Magnus evolved wavefunctions with truncations $2$ and $14$ (green and red dash-dotted lines, respectively) where $\lambda=1.2 \, fm^{-1}$.
+  	\caption{Momentum probability densities of the deuteron comparing the un-evolved wavefunction (black dotted line), SRG-evolved wavefunction (blue dashed line), and two Magnus-evolved wavefunctions with truncations $2$ and $14$ (green and red dash-dotted lines, respectively) where $\lambda=1.2 \, fm^{-1}$.
 The left panel shows evolution with $G=H_{D}$ and the right with $G=T_{rel}$.
@@
 \end{itemize}
--- Values from standard Magnus evolved potential ($G=H_D$, $\lambda=1.2 \, fm^{-1}$, and $k_{max}=6$):
+-- Values from standard Magnus-evolved potential ($G=H_D$, $\lambda=1.2 \, fm^{-1}$, and $k_{max}=6$):
 \begin{itemize}
@@
 %
-\textbf{Evolution of operators}
+\textbf{Evolution of operators} % Ask DF about what to include here.
 %

### 2019-07-01 Notes/Candidacy/Paper/candidacy_paper.tex
Added candidacy paper
Only an outline of the eventual paper at the moment.

--- 2019-06-10 Notes/Magnus/magnus.tex
@@
 %
-% File: magnus.tex
+% File: candidacy_paper.tex
 %
 % Author: A. J. Tropiano (tropiano.4@osu.edu)
-% Date: January 8, 2019
+% Date: July 1, 2019
 %
-% Notes on Magnus project.
+% Candidacy paper on the status of nuclear optical potentials and future prospects.
 %
 % Revision history:
-% 	03/04/19 --- Transitioning these notes into a draft of the eventual paper.
-%     05/30/19 --- Renamed magnus.tex from magnus_Jan08.tex.
+% 	xx/xx/xx --- ...             
 %
@@
 \usepackage{graphicx}
-% NOTE: Do not get rid of this path until all figures in Figures sub-folder are re-produced
-\graphicspath{{Figures/}} % Setting the graphics path
-% NEW PATH
-\graphicspath{{../../Figures/Magnus/}} % Setting the graphics path
+\graphicspath{{../../../Figures/Pictures/}} % Setting the graphics path
 \usepackage{physics} % For bra-ket notation
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Exploring the Magnus expansion and the in-medium similarity renormalization group}
+\title{Status of nuclear optical potentials and future prospects}
 
-\author{A.~J.~Tropiano$^{1}$, S.~K.~Bogner$^{2}$, R.~J.~Furnstahl$^{1}$}
+\author{A.~J.~Tropiano}
 
-\affiliation{%
-		$^1$\mbox{Department of Physics, The Ohio State University, Columbus, OH 43210, USA}  \\
-		$^2$\mbox{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy,}  \\
-    		\mbox{Michigan State University, East Lansing, MI 48824, USA}
-}
+\affiliation{\mbox{Department of Physics, The Ohio State University, Columbus, OH 43210, USA}}
 
 \date{\today}
-
-\begin{abstract}
-
-\noindent{-- Test Magnus expansion SRG implementation on LO NN potential at high $\Lambda$. (Define SRG or IMSRG acronym in abstract.)}
-\\
--- High $\Lambda$ leads to spurious bound states in spin triplet channels.
-\\
--- Decouple spurious bound state(s) by using two approaches within the Magnus implementation to drive the Hamiltonian to band-diagonal, unitarily equivalent form.
-\\
--- One choice of generator where the deep bound state is decoupled outside low-momentum and another where it is shifted to low-momentum.
-\\
--- Deep bound state corrupts low-momentum physics.
-\\
--- Connection to IMSRG intruder state problem.
-\\
--- Confirm unitarity of Hamiltonian by evaluation of deuteron observables.
-\\
--- Lastly, study operator evolution.
-
-\end{abstract}
 
@@
 
-\noindent{%
--- In recent years \textit{ab initio} methods have made strides in nuclear structure and reactions.
-}
-\\
--- Realistic binding energies starting from NN and 3N forces have been calculated for many medium mass nuclei using different many-body methods.
-\\
--- The in-medium similarity renormalization group (IMSRG) is one such method \cite{Hergert:2015awm, Hergert:2016iju}.
-\\
--- The IMSRG separates energy scales in the nuclear Hamiltonian by decoupling the reference state from excited states to band- or block-diagonal form.
-\\
--- One can use the decoupled Hamiltonian to solve the many-body Sch{\"o}dinger equation extracting specific eigenvalues and eigenstates which qualifies the IMSRG as an \textit{ab initio} method.
-\\
-
-\noindent{%
--- The IMSRG procedure requires solving a system of nonlinear, coupled differential equations which can often be stiff necessitating a high-order ODE solver.
-}
-\\
--- In principle, the decoupled Hamiltonian (or any operator) is unitarily equivalent but the numerical error of solving the ODE can lead to error on observable quantities.
-\\
--- Furthermore, the model spaces for IMSRG calculations can be extremely large.
-\\
--- Evolving several operators is often impossible due to memory restrictions in storing several operators.
-\\
-
-\noindent{%
--- A variant of the IMSRG that utilizes the Magnus expansion can overcome these limitations.
-}
-\\
--- We will refer to this as the Magnus implementation or simply Magnus.
-\\
--- The Magnus solves for the unitary transformation directly whereas the IMSRG applies the transformation indirectly in steps of the differential flow equation.
-\\
--- From the form of the transformation, the numerical error leaves the unitarity of the evolved Hamiltonian un-affected.
-\\
--- By explicitly solving for the transformation, one can evolve several operators.
-\\
--- The Magnus implementation has become a standard technique in IMSRG calculations as studies have targeted observables such as radii, electromagnetic moments and transitions, etc., requiring consistently evolved operators.
-\\
-
-\noindent{%
--- We test the Magnus implementation on chiral non-local NN potentials in free-space for several EFT cutoffs.
-}
-\\
--- At high cutoffs, spin triplet channels feature spurious, deeply bound states from the strong, repulsive tensor force \cite{Nogga:2005hy}.
-\\
--- These bound states are features of high-momentum physics and lie outside the range of the EFT.
-\\
--- However, potentials with deeply bound states have shown sensitivity to SRG transformations \cite{Glazek:2008pg, Wendt:2011qj}.
-\\
--- Details of the SRG transformation can cause the spurious bound state(s) to corrupt the low-momentum physics.
-\\
--- An analogous problem occurs in IMSRG calculations for systems with intruder states where the intruder state can shift to the energy scale of the reference state in valence space.
-\\
--- This severely distorts low-energy properties such as the ground state wave function.
-\\
--- It is not understood how the IMSRG procedure evolves intruder state systems.
-\\
--- Due to the prominence of the Magnus in IMSRG, one must first understand if the Magnus approach matches the typical approach for difficult systems before investigating the intruder state problem.
-\\
--- NN potentials with spurious bound states offer a good test laboratory for the Magnus implementation to better understand if the Magnus is equivalent to the SRG approach. 
-\\
-
-\noindent{%
--- The past decade has seen a tremendous increase in the number of chiral NN potentials.
-}
-\\
--- Interactions can now be built up to N5LO and feature several different regularization schemes.
-\\
--- A natural question is to ask whether the SRG decouples these potentials in the same way.
-\\
--- There is evidence of universal, low-momentum matrix elements as seen from evolving different potentials with SRG transformations or $V_{low~k}$ \cite{Dainton:2013axa}.
-\\
--- There has also been renewed interest in chiral potentials at high-cutoffs but for a locally regulated potential \cite{Tews:2018sbi}.
-\\
--- Given the growing number of chiral interactions, it would be interesting to re-examine these areas from an SRG standpoint.
-\\
--- However, we would like to focus on a fixed comparison of the SRG and the Magnus approach as a first test, and therefore only consider evolving non-local LO NN potentials at various cutoffs.
-\\
--- We leave the other areas as topics for future studies.
-\\
-
-\noindent{%
--- The rest of the paper is organized as follows:
-}
-\\
--- In Sec. \ref{sec:formalism} we review the formalism of the SRG and the Magnus implementation emphasizing the major advantages of the Magnus.
-\\
--- In Sec. \ref{sec:results} we test the Magnus implementation on high-cutoff NN potentials.
-\\
--- We briefly review the SRG results for the same set of bare interactions and compare Magnus to SRG results.
-\\
--- With the Magnus evolved operators, we calculate several observables and explore operator evolution.
-\\
--- Lastly, we summarize our results in Sec. \ref{sec:conclusion}.
-\\
--- We discuss the implications for the Magnus expansion within the IMSRG.
+Start text here.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Formalism}
-\label{sec:formalism}
+\section{Section 2}
+\label{sec:section_2}
 
-\noindent{%
-\textbf{SRG formalism}
-}
-\\
--- In this section we describe the SRG in the context of decoupling any operator.
-\\
--- The SRG decouples low- and high-momentum scales by applying a continuous unitary transformation $U(s)$ where $s=0 \rightarrow \infty$ is the flow parameter.
-\\
--- The `dressed' or evolved operator is given by
-%
-\begin{eqnarray}
-	\label{eq:srg_operator}
-	O(s) = U(s) O(0) U^{\dagger}(s),
-\end{eqnarray}
-%
-where $O(0)$ corresponds to the `bare' operator.
-\\
--- Because $U(s)$ is unitary, the observables of the operator are preserved.
-\\
--- In practice, the unitary transformation U(s) is not explicitly solved for; the evolved operator is given by a differential flow equation which is obtained by taking the derivative of Eqn.
-(\ref{eq:srg_operator}),
-%
-\begin{eqnarray}
-	\label{eq:srg_flow}
-	\frac{dO(s)}{ds} = [\eta(s), O(s)],
-\end{eqnarray}
-%
-where $\eta(s)=\frac{dU(s)}{ds} U^{\dagger}(s) = -\eta^{\dagger}(s)$ is the anti-hermitian SRG generator.
-\\
--- The generator is defined as a commutator,
-%
-\begin{eqnarray}
-	\label{eq:srg_generator}
-	\eta(s) = [G, H(s)],
-\end{eqnarray}
-%
-where $G$ specifies the type of flow or form of the decoupled operator.
-\\
--- To drive the operator to band-diagonal form, set $G=H_D(s)$, the diagonal of the Hamiltonian.
-\\
--- This choice was implemented by Wegner in condensed matter physics \cite{Wegner:1994ab}.
-\\
--- For notational convenience, we write the Wegner choice without the $s$ dependence in the rest of the paper.
-\\
--- In a similar option used in nuclear physics, $G$ is set to the relative kinetic energy, $T_{rel}$, which also drives to band-diagonal form.
-\\
--- In this paper, we consider both choices.
-\\
--- Generally the flow equation (\ref{eq:srg_flow}) is solved up to some finite value of $s$ with a high-order ODE solver.
-\\
--- It is convenient to define $\lambda \equiv s^{-1/4}$ which roughly measures the width of the diagonal in the decoupled operator.
-\\
-
-\noindent{%
-\textbf{Magnus expansion formalism}
-}
-\\
--- We now consider the Magnus implementation.
-\\
--- Mathematically speaking, the Magnus expansion is a method for solving an initial value problem associated with a linear ordinary differential equation (ODE).
-\\
--- Formal details of the Magnus expansion are discussed in \cite{Blanes:2009ab}.
-\\
--- We will introduce the Magnus expansion in the context of SRG evolving any operator.
-\\
--- In an intermediate step in deriving Eqn. (\ref{eq:srg_flow}), we have a linear ODE for $U(s)$,
-%
-\begin{eqnarray}
-	\label{eq:unitary_trans}
-	\frac{dU(s)}{ds} = \eta(s) U(s).
-\end{eqnarray}
-%
--- Magnus showed that one can solve the following equation with a solution $U(s)=e^{\Omega(s)}$ where $\Omega(s)$ is expanded as a power series, $\sum_{n}^{\infty} \Omega_n$ (referred to as the Magnus expansion or Magnus series).
-\\
--- The terms of the series are given by integral expressions involving $\eta(s)$ (again, see \cite{Blanes:2009ab, Magnus:1954zz} for details).
-\\
--- For our case, we focus on the formally exact derivative of $\Omega(s)$,
-%
-\begin{eqnarray}
-	\label{eq:magnus_omega}
-	\frac{d\Omega(s)}{ds} = \sum_{k=0}^{\infty} \frac{B_k}{k!} ad_{\Omega}^{k}(\eta),
-\end{eqnarray}
-%
-where $B_k$ are the Bernoulli numbers, $ad_{\Omega}^{0}(\eta)=\eta(s)$, and $ad_{\Omega}^{k}(\eta)=[\Omega(s),ad_{\Omega}^{k-1}(\eta)]$.
-\\
--- We integrate this differential equation to find $\Omega(s)$ and evaluate the unitary transformation directly.
-\\
--- Then the evolved operator can be evaluated with the BCH formula:
-%
-\begin{eqnarray}
-	\label{eq:bch}
-	O(s) = e^{\Omega(s)} O e^{-\Omega(s)} = \sum_{k=0}^{\infty} \frac{1}{k!} ad_{\Omega}^{k}(O).
-\end{eqnarray}
-%
--- As $k \rightarrow \infty$ in both sums in Eqns. (\ref{eq:magnus_omega}) and (\ref{eq:bch}) the Magnus transformation matches the SRG transformation.
-\\
--- We investigate several truncations $k_{max}$ in Eqn. (\ref{eq:magnus_omega}) and take many terms, $k_{max} \sim 25$, in Eqn. (\ref{eq:bch}).
-\\
-\textcolor{red}{%
--- Here or earlier (for the following bullets)? Better to motivate the Magnus in the introduction or easier to explain given mathematical detail?
-}
-\\
--- There are significant advantages in the Magnus implementation.
-\\
--- In the typical approach, the numerical error associated with solving the flow equation affects the accuracy of the observables for the evolved operator.
-\\
--- Therefore, one must use a high-order ODE solver in integrating the flow equation (\ref{eq:srg_flow}).
-\\
--- In the Magnus implementation, unitarity is guaranteed by the form of $U(s)$; in fact, one could solve Eqn.
-(\ref{eq:magnus_omega}) with a simple first-order Euler step-method keeping the same observables while decoupling the operator as desired.
-\\
--- This offers a decent computational speed-up by avoiding a high-order solver.
-\\
--- In this paper, we demonstrate this advantage by applying the Magnus implementation using the first-order Euler step-method.
-\\
--- The second major advantage involves the evolution of multiple operators.
-\\
--- In many other situations, one may be interested in evolving several operators at a time.
-\\
--- In the SRG procedure, we would have another set of coupled equations in Eqn. (\ref{eq:srg_flow}), drastically increasing memory usage.
-\\
--- Each additional operator increases the set of equations - say $N$ equations - by another factor of $N$.
-\\
--- In the Magnus, one only needs $\Omega(s)$ to consistently evolve several operators.
-\\
--- We avoid the cost in memory by directly constructing $U(s)=e^{\Omega(s)}$.
-\\
--- This is especially useful in IMSRG calculations where the model space can be very large.
-\\
--- In the next section, we discuss results from Magnus evolved large-cutoff potentials focusing on the flow of the potential, observables, and operator evolution.
+Start text here.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\label{sec:results}
+\section{Section 3}
+\label{sec:section_3}
 
-\noindent{%
-\textbf{Evolution of potentials}
-}
-\\
--- In this section, we Magnus evolve LO non-local potentials in the $^{3}S_1-^{3}D_1$ channel at cutoffs of $\Lambda=4$, $9$, and $20 \, fm^{-1}$.
-\\
-\textcolor{red}{%
--- Option: add new regularization schemes?
-}
-\\
--- For the higher two cutoffs, the potentials have one and two spurious, deeply bound states, respectively.
-\\
--- In \cite{Wendt:2011qj}, potentials at large-cutoffs were SRG evolved with $G=H_D$ and $G=T_{rel}$.
-\\
--- At lower cutoffs ($\Lambda \lesssim 4 \, fm^{-1}$), potential matrix elements flowed toward a decoupled, universal form independent of $G$, that is the low-momentum matrix elements approached the same values as $\lambda \rightarrow 0$.
-\\
--- However, SRG evolution differed for potentials featuring one or more spurious bound states.
-\\
--- With one or more spurious bound states and $G=T_{rel}$, the SRG transformation shifted a spurious bound state toward the low-momentum block corrupting the low-energy physics (e.g., the deuteron wave function, phase shifts, etc.).
-\\
--- For $G=H_D$, the SRG decoupled the spurious bound state outside the low-momentum block matching the flow to universal low-momentum form independent of the cutoff $\Lambda$.
-\\
--- Similar behavior could be prevalent in IMSRG calculations where the choice in generator affects evolution of many-body Hamiltonians with intruder states as it does for these NN potentials in free-space SRG.
-\\
+Start text here.
 
-\noindent{%
--- First, we compare Magnus to SRG evolution for large cutoff potentials with $G=H_D$ and $G=T_{rel}$.
-}
-\\
--- Figures \ref{fig:magnus_contours_Wendt_Lamb9_Wegner} and \ref{fig:magnus_contours_Wendt_Lamb9_T} show potential matrix element evolution for three truncations in the sum of Eqn.
-\ref{eq:magnus_omega} up to three values of $\lambda$ with $\Lambda=9 \, fm^{-1}$.
-\\
--- At this cutoff, the potential has one spurious bound state at about $-2000$ MeV.
-\\
-%	
-\begin{figure}
-	\captionsetup{singlelinecheck=false,justification=raggedright}
-	\centering
-	\includegraphics[width=10cm]{magnus_contours_Wendt_Lamb9_Wegner}
-	\hspace*{0.05\textwidth}
-	\caption{Contours of Magnus evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=H_{D}$ for $\lambda=2.8$ (left), $2.0$ (middle), and $1.2$ (right) $fm^{-1}$ and truncations in the Magnus $k_{max}=2$ (top), $6$ (middle), and $10$ (bottom).}
-	\label{fig:magnus_contours_Wendt_Lamb9_Wegner}
-\end{figure}
-%
-\begin{figure}
-	\captionsetup{singlelinecheck=false,justification=raggedright}
-	\centering
-	\includegraphics[width=10cm]{magnus_contours_Wendt_Lamb9_T}
-  	\hspace*{0.05\textwidth}
-  	\caption{Contours of Magnus evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=T_{rel}$ for $\lambda=2.8$ (left), $2.0$ (middle), and $1.2$ (right) $fm^{-1}$ and truncations in the Magnus $k_{max}=2$ (top), $6$ (middle), and $10$ (bottom).}
-  	\label{fig:magnus_contours_Wendt_Lamb9_T}
-\end{figure}
-%
--- We see the same behavior with the Magnus in comparison to the SRG in \cite{Wendt:2011qj} for both generators.
-\\
--- For $G=H_D$, there is a deep, blue dot in the middle of the contours at $k \approx 1.75 \, fm^{-1}$ which corresponds to the decoupled spurious bound state.
-\\
--- We have checked other cutoffs and found that the evolved low-momentum matrix elements are independent of the cutoff $\Lambda$ implying a low-momentum, universal form.
-\\
--- The only major difference in Magnus or SRG evolution for various cutoffs is where spurious bound state(s) are decoupled.
-\\
--- This decoupling feature depends on the details of the starting interaction (i.e., the value of the bound state).
-\\
-%
-\begin{figure}
-	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
-        \includegraphics[width=14cm]{evolved_diags_Wendt_Lamb9_Wegner}
-	\hspace*{0.05\textwidth}
-	\caption{Diagonal (top row) and far off-diagonal (bottom row) matrix elements of evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=H_{D}$ for several values of $\lambda$ and truncations in the Magnus series $k_{max}$.}
-	\label{fig:evolved_diags_Wendt_Lamb9_Wegner}
-\end{figure}
-%
-\noindent{%
--- Furthermore, it is dependent on the momentum mesh on which the potential is generated.
-}
-\\
--- At $k_{max}=2$ and $\lambda=2.0 \, fm^{-1}$, we see large, positive off-diagonal values along the momentum axes where the deep bound state is decoupled.
-\\
--- Solving for $\Omega(s)$ at a low truncation leads to less desirable flow, that is, the transformation $U(s)$ is not quite the same transformation as the SRG $U(s)$.
-\\
--- However, the Magnus still guarantees the unitarity of $U(s)$, and we see a consistent decoupling of the spurious bound state in each row independent of $k_{max}$.
-\\
--- For $G=T_{rel}$, the spurious bound state is shifted up along the diagonal, and the low-momentum block drops to extremely negative values.
-\\
--- Here, the spurious bound state corrupts the low-momentum block matching the SRG evolution of different cutoffs, thus breaking universality.
-\\
-%
-\begin{figure}
-	\captionsetup{singlelinecheck=false,justification=raggedright}
-	\centering
-	\includegraphics[width=14cm]{evolved_diags_Wendt_Lamb9_T}
-	\hspace*{0.05\textwidth}
-	\caption{Diagonal (top row) and far off-diagonal (bottom row) matrix elements of evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=T_{rel}$ for several values of $\lambda$ and truncations in the Magnus series $k_{max}$.}
-	\label{fig:evolved_diags_Wendt_Lamb9_T}
-\end{figure}
-%
-\noindent{%
--- Figures \ref{fig:evolved_diags_Wendt_Lamb9_Wegner} and \ref{fig:evolved_diags_Wendt_Lamb9_T} show a more quantitative depiction of the evolved potentials.
-}
-\\
--- The black dotted line corresponds to the SRG evolved potential whereas the other lines are Magnus evolved potentials for different $k_{max}$ for diagonal and far-off diagonal matrix elements of $V_{\lambda}(k,k')$.
-\\
--- It is clear in these figures that the Magnus matches the SRG at $k_{max} \gtrsim 6$.
-\\
--- In Figure \ref{fig:evolved_diags_Wendt_Lamb9_Wegner} the decoupled spurious bound state is seen as the large negative drop in the curves at $k \approx 1.75 \, fm^{-1}$.
-\\
-\textcolor{red}{%
--- Unnecessary?
-\\
--- From applying the Magnus in several other cases, we have seen that harder potentials cause convergence issues in the Magnus expansion due to the relative size of the SRG generator $\eta(s)$.
-\\
--- To avoid convergence issues we can take a smaller step-size.
-\\
--- In the previous cases (and all other cases unless specified otherwise), we take $ds=10^-5$.
-}
-\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Section 4}
+\label{sec:section_4}
 
-\noindent{%
-\textbf{Observables}
-}
-\\
-%
-\begin{table}
-	\captionsetup{singlelinecheck=false,justification=raggedright}
-	\caption{Relative error on the deuteron bound state energy and the root mean square of eigenvalues where $\tilde{\epsilon}$ denotes an eigenvalue of an SRG or Magnus evolved Hamiltonian for $\Lambda=9 \, fm^{-1}$ and $\lambda=1.2 \, fm^{-1}$.}
-	\label{tab:energies}
-	\begin{ruledtabular}
-		\begin{tabular}{{>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{2in}}}
-      			$  $ & $G$ & $ |\frac{\epsilon_d-\tilde{\epsilon}_d}{\epsilon_d}| $ & $\sqrt{\frac{1}{N} \, \sum_{i}^{N} (\tilde{\epsilon}_i-\epsilon_i)^2}$   [MeV] \\
-			\colrule
-      			SRG & $ $ & $\num{1.165e-5}$ & $\num{3.016e-4}$ \\
-      			Magnus, $k_{max}=2$ & $H_D$ & $\num{5.010e-10}$ & $\num{4.097e-9}$ \\
-      			Magnus, $k_{max}=14$ & $ $ & $\num{1.206e-11}$ & $\num{3.950e-10}$ \\ \hline
-      			SRG & $ $ & $\num{1.003e-4}$ & $\num{9.791e-5}$ \\
-      			Magnus, $k_{max}=2$ & $T_{rel}$ & $\num{7.775e-8}$ & $\num{6.376e-8}$ \\
-      			Magnus, $k_{max}=14$ & $ $ & $\num{7.607e-8}$ & $\num{6.359e-8}$ \\
-		\end{tabular}
-  	\end{ruledtabular}
-\end{table}
-%
--- To emphasize the two major advantages of the Magnus implementation, we now consider evolved observables and operators for the remainder of the section.
-\\
--- Table \ref{tab:energies} shows the relative error on the deuteron bound state energy and root mean square of all eigenvalues for several evolution cases.
-\\
--- The Magnus approach preserves energies to several orders of magnitude better than the typical SRG approach.
-\\
--- Again, despite the inclusion of several more terms in the sum of Eqn.
-\ref{eq:magnus_omega}, we see consistent errors between $k_{max}=2$ and $14$ because of the guaranteed unitarity of $U(s)=e^{\Omega(s)}$
-\\
--- The errors on the Magnus energies are within the region of floating-point error whereas the SRG compounds error in solving the ODE \ref{eq:srg_flow}.
-\\
--- We have also checked the phase shifts from the evolved potentials match the bare potentials in all cases for Magnus and SRG evolution.
-\\ 
--- Next we show the evolved deuteron wave function for several cases.
-\\
--- Figure \ref{fig:momentum_dist_Wendt_Lamb9} shows the deuteron momentum probability density, $|\phi(k)|^2$, on a semi-log scale as a function of momentum for both band-diagonal generators.
-\\
--- With $G=H_D$, the evolved and un-evolved momentum distributions agree for low-momentum whereas $G=T_{rel}$ significantly distorts the distribution from the presence of the spurious bound state in the $\Lambda=9 \, fm^{-1}$ potential.
-\\
--- This illustrates the advantage of the Wegner generator: the spurious bound state at high-momentum does not affect the low-momentum physics under the SRG transformation.
-\\
--- In all cases of Magnus and SRG evolution, we can consistently evolve wave functions and operators to make reliable calculations of observables.
-\\
--- To demonstrate this, we calculate the deuteron RMS radius and quadrupole moment with the $\Lambda=9 \, fm^{-1}$ potential using the Magnus implementation with the Wegner generator.
-\\
--- The initial values of the chiral potential are $r_d = 2.022 \, fm$ and $Q_d = 0.287 \, fm^2$ compared to the experimental values $r_d^{exp} = 2.141 \, fm$ and $Q_d^{exp} = 0.286 \, fm^2$. 
-\\
--- We have checked for several cases with the Magnus and found near-perfect agreement to the initial values of both observables.
-\\
-
-\noindent{%
-	\textcolor{red}{%
-	UPDATED UP TO HERE 04/03/19
-	}
-}
-\\
-\begin{figure}
-  	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
-  	\includegraphics[width=10cm]{momentum_dist_Wendt_Lamb9}
-  	\hspace*{0.05\textwidth}
-  	\caption{Momentum probability densities of the deuteron comparing the un-evolved wavefunction (black dotted line), SRG evolved wavefunction (blue dashed line), and two Magnus evolved wavefunctions with truncations $2$ and $14$ (green and red dash-dotted lines, respectively) where $\lambda=1.2 \, fm^{-1}$.
-The left panel shows evolution with $G=H_{D}$ and the right with $G=T_{rel}$.
-Here $\Lambda=9 \, fm^{-1}$.}
-  	\label{fig:momentum_dist_Wendt_Lamb9}
-\end{figure}
-%
-\noindent{%
--- RMS radius and quadrupole moment of deuteron.
-}
-\\
--- Values from initial potential ($\Lambda=9 \, fm^{-1}$):
-\begin{itemize}
-  	\item $r_d = 2.022 \, fm$ (using momentum-space derivatives)
-  	\item $r_d = 2.465 \, fm$ (using Fourier transforms)
-	\item $Q_d = 0.287 \, fm^2$ (using momentum-space derivatives)
-\end{itemize}
--- Values from standard Magnus evolved potential ($G=H_D$, $\lambda=1.2 \, fm^{-1}$, and $k_{max}=6$):
-\begin{itemize}
-  	\item $r_d = 2.022 \, fm$ (using momentum-space derivatives)
-  	\item $Q_d = 0.287 \, fm^2$ (using momentum-space derivatives)s
-  	\item Note: we apply $U^{\dagger}(s) U(s)$ to wave function to compute unitarily equivalent observables
-\end{itemize}
--- Experimental values:
-\begin{itemize}
-  	\item $r_d = 2.141 \, fm$
-  	\item $Q_d = 0.286 \, fm^2$
-\end{itemize}
-%
-\textbf{Evolution of operators}
-%
-\begin{figure}[H]
-  	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
- 	\includegraphics[width=14cm]{momentum_proj_operator_contours_q0,31_magnus_Wendt_Lamb9}
-  	\hspace*{0.05\textwidth}
-  	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ Magnus evolving in $\lambda$ right to left with $G=H_D$ (top) and $G=T_{rel}$ (bottom).
-Here $q=0.31 \, fm^{-1}$, $\Lambda=9 \, fm^{-1}$, and $k_{max}=6$.}
-  	\label{fig:momentum_proj_operator_contours_q0,31_magnus_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-	\captionsetup{singlelinecheck=false,justification=raggedright}
-	\centering
-  	\includegraphics[width=10cm]{momentum_proj_difference_q0,31_magnus_Wendt_Lamb9}
-  	\hspace*{0.05\textwidth}
-  	\caption{Difference in evolved and bare matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ Magnus evolving to $\lambda=1.2 \, fm^{-1}$ right to with $G=H_D$ (left) and $G=T_{rel}$ (right).
-Here $q=0.31 \, fm^{-1}$, $\Lambda=9 \, fm^{-1}$, and $k_{max}=6$.}
-  	\label{fig:momentum_proj_operator_difference_q0,31_magnus_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-  	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
-  	\includegraphics[width=14cm]{momentum_proj_operator_contours_q3,04_magnus_Wendt_Lamb9}
-  	\hspace*{0.05\textwidth}
-  	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ Magnus evolving in $\lambda$ right to left with $G=H_D$ (top) and $G=T_{rel}$ (bottom).
-Here $q=3.04 \, fm^{-1}$, $\Lambda=9 \, fm^{-1}$, and $k_{max}=6$.}
-  	\label{fig:momentum_proj_operator_contours_q3,04_magnus_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-  	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
-  	\includegraphics[width=10cm]{momentum_proj_difference_q3,04_magnus_Wendt_Lamb9}
-  	\hspace*{0.05\textwidth}
-  	\caption{Difference in evolved and bare matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ Magnus evolving to $\lambda=1.2 \, fm^{-1}$ with $G=H_D$ (left) and $G=T_{rel}$ (right).
-Here $q=3.04 \, fm^{-1}$, $\Lambda=9 \, fm^{-1}$, and $k_{max}=6$.}
-  	\label{fig:momentum_proj_operator_difference_q3,04_magnus_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-  	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
-  	\includegraphics[width=14cm]{r2_operator_contours_magnus_Wendt_Lamb9}
-  	\hspace*{0.05\textwidth}
-  	\caption{Matrix elements of $\mel{k}{r^2}{k'}$ Magnus evolving in $\lambda$ right to left with $G=H_D$ (top) and $G=T_{rel}$ (bottom). Here $\Lambda=9 \, fm^{-1}$ and $k_{max}=6$.}
-  	\label{fig:r2_operator_contours_srg_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-  	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
-  	\includegraphics[width=10cm]{r2_difference_magnus_Wendt_Lamb4}
-  	\hspace*{0.05\textwidth}
-  	\caption{Difference in evolved and bare matrix elements of $\mel{k}{r^2}{k'}$ Magnus evolving to $\lambda=1.2 \, fm^{-1}$ with $G=H_D$ (left) and $G=T_{rel}$ (right).
-Here $\Lambda=4 \, fm^{-1}$ and $k_{max}=6$.}
-  	\label{fig:r2_difference_magnus_Wendt_Lamb4}
-\end{figure}
-%
-\begin{figure}[H]
-  	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
-  	\includegraphics[width=10cm]{r2_difference_magnus_Wendt_Lamb9}
-  	\hspace*{0.05\textwidth}
-  	\caption{Difference in evolved and bare matrix elements of $\mel{k}{r^2}{k'}$ Magnus evolving to $\lambda=1.2 \, fm^{-1}$ with $G=H_D$ (left) and $G=T_{rel}$ (right).
-Here $\Lambda=9 \, fm^{-1}$ and $k_{max}=6$.
-(Note the difference in color bar scales.)}
-  	\label{fig:r2_difference_magnus_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-  	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
-  	\includegraphics[width=14cm]{r2_integrand_contours_magnus_Wendt_Lamb9}
-  	\hspace*{0.05\textwidth}
-  	\caption{Integrand of $\bra{\Psi}\ket{k} \mel{k}{r^2}{k'} \bra{k'}\ket{\Psi}$ Magnus evolving the wave function in $\lambda$ right to left with $G=H_D$ (top) and $G=T_{rel}$ (bottom).
-Here $\Lambda=9 \, fm^{-1}$, $k_{max}=6$, and the operator $r^2$ is un-evolved.}
-  	\label{fig:r2_integrand_contours_srg_Wendt_Lamb9}
-\end{figure}
+Start text here.
 
@@
 
-\noindent{%
--- Summarize.
-}
-\\
--- Where does the Magnus implementation differ from the SRG result?
-\\
--- Connection to the IMSRG intruder state problem.
-\\
--- Outlook.
+Summary and outlook. Example citation \cite{Rotureau:2016jpf}.
 

### 2019-07-02 Notes/Candidacy/Paper/candidacy_paper.tex
Update to candidacy notes
Added bullet points for outlining candidacy paper.

@@
 % Revision history:
-% 	xx/xx/xx --- ...             
+% 	07/02/19 --- Starting with bulleted outline. 
 %
@@
 
-Start text here.
+Things to include:
+\\
+-- r-process for motivation.
+\\
+-- Include multiple scattering, self-consistent Green's function methods.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Section 2}
+\section{Phenomenology of optical potentials}
 \label{sec:section_2}
 
-Start text here.
+Things to include:
+\\
+-- Form of the potential: Woods-Saxon shape, coulomb component, spin-orbit force.
+\\
+-- Fit strength, radii, and diffuseness of complex potential.
+\\
+-- Issue: fitting ambiguities, extractions to exotic regions of the nuclear chart.
+\\
+-- Make sure to touch on phenomenology of optical potentials in modern experimental analyses (key word is modern!)
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Section 3}
+\section{Ab initio optical potentials}
 \label{sec:section_3}
 
-Start text here.
+Things to include:
+\\
+-- Successes and limitations.
+\\
+-- Motivation: predictions for exotic region of the nuclear chart.
+\\
+-- Coupled cluster Green's function \cite{Rotureau:2016jpf}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Section 4}
+\section{Theoretical issues}
 \label{sec:section_4}
 
-Start text here.
+Things to include:
+\\
+-- Fitting ambiguities for phenomenological potential.
+\\
+-- Uncertainty quantification.
 
@@
 
-Summary and outlook. Example citation \cite{Rotureau:2016jpf}.
+Summary and outlook.
 

### 2019-07-03 Notes/Candidacy/Paper/candidacy_paper.tex
Minor updates to candidacy notes

@@
 \\
+-- Why are nuclear reactions important? (Processes that help us understand nuclear structure amongst other things.) List examples.
+\\
+-- How do optical potentials help us understand nuclear reactions?
+\\
 -- r-process for motivation.
@@
 -- Include multiple scattering, self-consistent Green's function methods.
+\\
+-- Should probably have a basic formalism section before going into phenomenology.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Ab initio optical potentials}
+\section{Ab initio optical potentials} % See how papers would refer to this "microscopic"
 \label{sec:section_3}
@@
 -- Uncertainty quantification.
+\\
+-- Add this to outlook in conclusion?
 

### 2019-07-05 Notes/Candidacy/Paper/candidacy_paper.tex
Updates to candidacy notes
Changed the sub-section headers.
Updates to candidacy paper
Adding more to candidacy paper outline.

@@
 \\
+-- r-process for motivation.
+\\
 -- How do optical potentials help us understand nuclear reactions?
 \\
--- r-process for motivation.
-\\
--- Include multiple scattering, self-consistent Green's function methods.
-\\
--- Should probably have a basic formalism section before going into phenomenology.
+-- References: ...
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Phenomenology of optical potentials}
-\label{sec:section_2}
+\section{Formalism}
+\label{sec:formalism}
 
@@
 \\
--- Form of the potential: Woods-Saxon shape, coulomb component, spin-orbit force.
+-- More general things from Thompson/Nunes: define optical potentials as complex potentials and consequences of this. Reaction cross section derivation.
+\\
+-- Derivation of the general optical potential (equation (2.15) in Feshbach).
+\\
+-- Properties of the potential: complex (meaning), non-local (derivation), dispersion relation.
+\\
+-- Relation to observables (basic quantum stuff?)
+\\
+-- References: \cite{Feshbach:1958nx}, \cite{Feshbach:1962ut}, Thompson/Nunes textbook (73, 126).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Phenomenology}
+\label{sec:phenomenology}
+
+Things to include:
+\\
+-- Form of the potential: Woods-Saxon shape, coulomb component, spin-orbit force. (Basic example in Thompson/Nunes.). Can start with discussion similar to Thompson/Nunes.
 \\
@@
 -- Make sure to touch on phenomenology of optical potentials in modern experimental analyses (key word is modern!)
+\\
+-- References: \cite{Dickhoff:2018wdd} section 3, \cite{Koning:2003zz}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Ab initio optical potentials} % See how papers would refer to this "microscopic"
-\label{sec:section_3}
+\section{Microscopic optical potentials}
+\label{sec:microscopic}
 
@@
 -- Coupled cluster Green's function \cite{Rotureau:2016jpf}.
+\\
+-- References: \cite{Dickhoff:2018wdd} section 4, \cite{Furumoto:2019anr} G-matrix interaction, \cite{Idini:2019hkq} self-consistent Green's function, \cite{Rotureau:2016jpf}.
 
@@
 -- Add this to outlook in conclusion?
+\\
+-- References: \cite{King:2018vzw}.
 
@@
 
-\bibliography{../tropiano_bib}
+\bibliography{../../tropiano_bib}
 

### 2019-07-08 Notes/Candidacy/Paper/candidacy_paper.tex
Updates to candidacy notes
Added more bullets to outline.

@@
 \\
--- References: \cite{Feshbach:1958nx}, \cite{Feshbach:1962ut}, Thompson/Nunes textbook (73, 126).
+-- References: \cite{Feshbach:1958nx}, \cite{Feshbach:1962ut}, \cite{thompson_nunes_2009}.
 
@@
 -- Fit strength, radii, and diffuseness of complex potential.
+\\
+-- Surface and volume component from Dickhoff?
 \\
@@
 -- Motivation: predictions for exotic region of the nuclear chart.
+\\
+-- Major methods: Multiple scattering (see references in Dickhoff paper) and Green's function based methods (coupled cluster).
 \\

### 2019-07-09 Notes/Candidacy/Paper/candidacy_paper.tex
Update candidacy_paper.tex

@@
 \\
--- Why are nuclear reactions important? (Processes that help us understand nuclear structure amongst other things.) List examples.
+-- Why are nuclear reactions important? (Processes that help us understand nuclear structure amongst other things. Exotic nuclei are short-lived and must used reactions to study them.) List examples.
 \\
@@
 \\
--- Properties of the potential: complex (meaning), non-local (derivation), dispersion relation.
+-- Relation to observables (basic quantum stuff?)
 \\
--- Relation to observables (basic quantum stuff?)
+-- Derivation with projection operators.
 \\
@@
 \\
--- Major methods: Multiple scattering (see references in Dickhoff paper) and Green's function based methods (coupled cluster).
+-- Major methods: Multiple scattering (see references in Dickhoff paper) and Green's function based methods (coupled cluster). SRG evolution.
 \\

### 2019-07-11 Notes/Candidacy/Paper/candidacy_paper.tex
Updated candidacy paper
Wrote most of the formalism section and added bullets to the phenomenology section. Unfinished parts are written in red.

@@
 % 	07/02/19 --- Starting with bulleted outline.
+%     07/10/19 --- Adding equations to formalism section.
+%	07/11/19 --- Put theoretical issues section as part of the conclusion. Also, wrote much of the formalism section.
 %
@@
 \\
--- More general things from Thompson/Nunes: define optical potentials as complex potentials and consequences of this. Reaction cross section derivation.
+-- Projectile strikes a nucleus: elastic scattering and more.
 \\
--- Derivation of the general optical potential (equation (2.15) in Feshbach).
+-- Derivation of the general optical potential (equation (2.15) in Feshbach). \textcolor{red}{Check.}
 \\
--- Relation to observables (basic quantum stuff?)
+-- More general things from Thompson/Nunes: define optical potentials as complex potentials and consequences of this. Reaction cross section derivation?
 \\
--- Derivation with projection operators.
+-- Drawbacks to this derivation. Transition to projection operator method.
+\\
+-- Relation to observables. Use Lippmann-Schwinger equation to bridge gap to observables: phase shifts and cross sections. Maybe this makes more sense in phenomenology section?
+\\
+-- Generalization: derivation with projection operators.
 \\
 -- References: \cite{Feshbach:1958nx}, \cite{Feshbach:1962ut}, \cite{thompson_nunes_2009}.
+\\
+
+\textcolor{red}{Add Feshbach reference somewhere.}
+\\
+
+First, we present the optical potential for an $A+1$ particle system consisting of an incident nucleon and a target nucleus of mass number $A$. The system is described by the Schr\"odinger equation
+%
+\begin{eqnarray}
+	\label{eq:schrodinger_equation}
+	\mathcal{H} \Psi = E \Psi,
+\end{eqnarray}
+%
+with the Hamiltonian $\mathcal{H}$ given below:
+%
+\begin{eqnarray}
+	\label{eq:total_hamiltonian}
+	\mathcal{H} = H_A(\textbf{r}_1, \cdots , \textbf{r}_A) + T_0 + V(\textbf{r}_0, \cdots , \textbf{r}_A).
+\end{eqnarray}
+%
+The variables $\textbf{r}_k$ correspond to position, spin, and isospin for the incident nucleon ($k=0$) and each nucleon in the target nucleus ($k=1 \cdots A$).
+$T_0$ is the kinetic energy of the incident nucleon and $V$ is the potential energy of the $A+1$ system.
+$H_A$ is the Hamiltonian for the target nucleus and satisfies the Schr\"odinger equation
+%
+\begin{eqnarray}
+	\label{eq:nuclear_schrodinger_equation}
+	H_A(\textbf{r}_1, \cdots , \textbf{r}_A) \psi_i(\textbf{r}_1, \cdots , \textbf{r}_A) = \epsilon_i \psi_i(\textbf{r}_1, \cdots , \textbf{r}_A),
+\end{eqnarray}
+%
+for nuclear wave functions $\psi_i$ and energies $\epsilon_i$.
+Here, the index $i$ corresponds to each state of the target nucleus with $i=0$ being the ground state.
+The nuclear wave functions $\psi_i$ form a complete, orthonormal set; thus, we expand the wave function $\Psi$ as follows:
+%
+\begin{eqnarray}
+	\label{eq:wave_function}
+	\Psi(\textbf{r}_0, \cdots , \textbf{r}_A) = \sum_{i} \psi_i(\textbf{r}_1, \cdots , \textbf{r}_A) u_i(\textbf{r}_0).
+\end{eqnarray}
+%
+Note, the factors $u_i$ carry the $\textbf{r}_0$ dependence.
+\\
+
+%
+\textcolor{red}{Mention hard-core problem.} In the following, we suppress the coordinate, spin, and isospin dependencies for brevity.
+We substitute \ref{eq:wave_function} into the Schr\"odinger equation \ref{eq:schrodinger_equation} and use the orthonormality of $\psi_i$ to derive a system of equations for the amplitudes $u_i$:
+%
+\begin{eqnarray}
+	\label{eq:u_equation}
+	(T_0 + V_{ii} + \epsilon_i - E) u_i = - \sum_{j \neq i} V_{ij} u_j,
+\end{eqnarray}
+%
+where the potential matrix elements are
+%
+\begin{eqnarray}
+	\label{eq:potential_matrix_elements}
+	V_{ij}(\textbf{r}_0) = \int{d^3 r_1 d^3 r_2 \cdots d^3 r_A \psi_i^* V \psi_j}.
+\end{eqnarray}
+%
+Next, we would like to derive an uncoupled equation for $u_0$ to describe elastic scattering in which the target nucleus is in its ground state with an incident nucleon of energy $E$.
+The other indices $i$ describe an emergent nucleon in a different state (e.g.
+energy, spin, isospin, etc.) from the incident nucleon.
+It is convenient to define the vectors
+%
+\begin{eqnarray}
+	\label{eq:u_vector}
+	\Phi \equiv
+	\begin{pmatrix}
+		u_1 \\
+		u_2 \\
+		\vdots \\
+	\end{pmatrix}
+	,
+\end{eqnarray}
+%
+\begin{eqnarray}
+	\label{eq:potential_vector}
+	\textbf{V}_0 =
+	\begin{pmatrix}
+		V_{01}, V_{02}, \cdots
+	\end{pmatrix}
+\end{eqnarray}
+%
+and the matrix operator $\textbf{H}$
+%
+\begin{eqnarray}
+	\label{eq:hamiltonian_operator}
+	H_{ij} = T_0 \delta_{ij} + V_{ij} + \epsilon_i \delta_{ij}.
+\end{eqnarray}
+%
+Then we can rewrite \ref{eq:u_equation} as
+%
+\begin{subequations}
+	\label{eq:u_vector_equation}
+	\begin{eqnarray}
+		\label{eq:u_vector_equation_a}
+		(T_0 + V_{00} - E) u_0 = -\textbf{V}_0 \Phi,
+	\end{eqnarray}
+	\begin{eqnarray}
+		\label{eq:u_vector_equation_b}
+		(\textbf{H}-E) \Phi = -\textbf{V}_0^{\dagger} u_0.
+	\end{eqnarray}
+\end{subequations}
+%
+We solve \ref{eq:u_vector_equation_b} for $\Phi$
+%
+\begin{eqnarray}
+	\label{eq:phi}
+	\Phi = \frac{1}{E - \textbf{H} + i \eta} \textbf{V}_0^{\dagger} u_0,
+\end{eqnarray}
+%
+where $\eta \rightarrow 0^+$ to ensure only outgoing waves are present in exit channels for $u_i$ with $i \geq 1$. Lastly, we substitute $\Phi$ into \ref{eq:u_vector_equation_a} to give
+%
+\begin{eqnarray}
+	\label{eq:u0_equation}
+	(T_0 + V_{00}  - \textbf{V}_0 \frac{1}{E-\textbf{H}+i\eta} \textbf{V}_0^{\dagger} - E) u_0 = 0,
+\end{eqnarray}
+%
+and define the optical potential as
+%
+\begin{eqnarray}
+	\label{eq:optical_potential}
+	V_{opt} = V_{00}  - \textbf{V}_0 \frac{1}{E-\textbf{H}+i\eta} \textbf{V}_0^{\dagger}.
+\end{eqnarray}
+%
+\textcolor{red}{Drawbacks of this derivation.}
+\\
+
+We can see from Eq.~\ref{eq:optical_potential} that the optical potential is complex and energy dependent.
+The factor of $i \eta$ leads to $V^{opt}$ being complex, and thus, non-hermitian.
+The factor of $i \eta$ accounts for incident particles leaving the entrance channel $u_0$ to an exit channel $u_i$ where $i \geq 1$.
+This only occurs if reactions are possible, that is, $E > \epsilon_1$.
+Because $V^{opt}$ is not hermitian, the S matrix is not unitary giving rise to complex scattering phase shifts.
+\\
+
+\textcolor{red}{Furthermore, the potential is non-local... Use reference \cite{Hodgson:1971ab}.}
+\\
+
+\textcolor{red}{%
+-- Generalization by using projection operators.
+\\
+-- What does $P$ and $Q$ do?
+\\
+-- Examples? (Feshbach.)}
+\\
+The projection operators satisfy the following relations: $P+Q=1$, $P^2 = P$, and $Q^2 = Q$.
+We act on Eq.~\ref{eq:schrodinger_equation} with $P$ and $Q$ and use the projection operator relations to obtain two equations:
+%
+\begin{subequations}
+	\label{eq:intermediate_effective_hamiltonian_equations}
+	\begin{eqnarray}
+		\label{eq:pp_pq}
+		(E - \mathcal{H}_{PP}) P \Psi = \mathcal{H}_{PQ} Q \Psi,
+	\end{eqnarray}
+	\begin{eqnarray}
+		\label{eq:qq_qp}
+		(E - \mathcal{H}_{QQ}) Q \Psi = \mathcal{H}_{QP} P \Psi.
+	\end{eqnarray}
+\end{subequations}
+%
+Solving \ref{eq:qq_qp} for $Q \Psi$ yields
+%
+\begin{eqnarray}
+	\label{eq:q_psi}
+	Q \Psi = \frac{1}{E - \mathcal{H}_{QQ}} \mathcal{H}_{QP} P \Psi.
+\end{eqnarray}
+%
+Note, if $P$ does not include all open channels, then a factor of $i \eta$ where $\eta \rightarrow 0^+$ must be inserted in the denominator as before to account for...
+\textcolor{red}{Finish this note.} Substituting $Q \Psi$ into Eq.~\ref{eq:pp_pq} and rearranging gives
+%
+\begin{eqnarray}
+	\label{p_psi}
+	(E - \mathcal{H}_{PP} - \mathcal{H}_{PQ} \frac{1}{E - \mathcal{H}_{QQ}} \mathcal{H}_{QP}) P \Psi = 0,
+\end{eqnarray}
+%
+where the effective Hamiltonian is
+%
+\begin{eqnarray}
+	\label{eq:effective_hamiltonian}
+	H_{eff} = \mathcal{H}_{PP} + \mathcal{H}_{PQ} \frac{1}{E - \mathcal{H}_{QQ}} \mathcal{H}_{QP}.
+\end{eqnarray}
+%
+\textcolor{red}{Advantages of the projection operator formulation.} Wider applicability with generalization of $P$.
 
@@
 \\
+-- Types: best fit, local, and global (see Koning). Advantages and disadvantages of each.
+\\
 -- Fit strength, radii, and diffuseness of complex potential.
@@
 \\
--- Issue: fitting ambiguities, extractions to exotic regions of the nuclear chart.
+-- Issue: fitting ambiguities, extractions to exotic regions of the nuclear chart. Some short-comings mentioned in Koning.
 \\
--- Make sure to touch on phenomenology of optical potentials in modern experimental analyses (key word is modern!)
+-- Make sure to touch on phenomenology of optical potentials in modern experimental analyses (key word is modern!) Koning.
 \\

### 2019-07-15 Notes/Candidacy/Paper/candidacy_paper.tex
Updated candidacy paper
Finished phenomenology section.

@@
 %	07/11/19 --- Put theoretical issues section as part of the conclusion. Also, wrote much of the formalism section.
+%	07/15/19 --- Wrote the phenomenology section.
 %
@@
 \\
+-- Basic introduction to optical potentials. Why are they complex? Historical introduction.
+\\
 -- References: ...
@@
 \\
--- Derivation of the general optical potential (equation (2.15) in Feshbach). \textcolor{red}{Check.}
+-- Derivation of the general optical potential (equation (2.15) in Feshbach).
 \\
@@
 Here, the index $i$ corresponds to each state of the target nucleus with $i=0$ being the ground state.
-The nuclear wave functions $\psi_i$ form a complete, orthonormal set; thus, we expand the wave function $\Psi$ as follows:
+The nuclear wave functions $\psi_i$ form a complete, orthonormal set; thus, we can expand the wave function $\Psi$ as follows:
 %
@@
 
-%
 \textcolor{red}{Mention hard-core problem.} In the following, we suppress the coordinate, spin, and isospin dependencies for brevity.
@@
 	\end{pmatrix}
+	,
 \end{eqnarray}
@@
 We can see from Eq.~\ref{eq:optical_potential} that the optical potential is complex and energy dependent.
-The factor of $i \eta$ leads to $V^{opt}$ being complex, and thus, non-hermitian.
+The factor of $i \eta$ leads to $V_{opt}$ being complex, and thus, non-hermitian.
 The factor of $i \eta$ accounts for incident particles leaving the entrance channel $u_0$ to an exit channel $u_i$ where $i \geq 1$.
 This only occurs if reactions are possible, that is, $E > \epsilon_1$.
-Because $V^{opt}$ is not hermitian, the S matrix is not unitary giving rise to complex scattering phase shifts.
+Because $V_{opt}$ is not hermitian, the $S$-matrix is not unitary giving rise to complex scattering phase shifts.
 \\
@@
 
-\textcolor{red}{%
--- Generalization by using projection operators.
-\\
--- What does $P$ and $Q$ do?
-\\
--- Examples? (Feshbach.)}
-\\
-The projection operators satisfy the following relations: $P+Q=1$, $P^2 = P$, and $Q^2 = Q$.
+\textcolor{red}{Generalization by using projection operators.
+What do $P$ and $Q$ do?
+Examples?
+(Feshbach.)} The projection operators satisfy the following relations: $P+Q=1$, $P^2 = P$, and $Q^2 = Q$.
 We act on Eq.~\ref{eq:schrodinger_equation} with $P$ and $Q$ and use the projection operator relations to obtain two equations:
@@
 
-Things to include:
+Historically, phenomenological optical potentials have been obtained by fitting elastic-scattering angular distributions with a complex potential of the form
+%
+\begin{eqnarray}
+	\label{eq:phenomenological_optical_potential}
+	V_{opt}(r) &=& V_C - V f(x_0) + (\frac{\hbar}{m_{\pi} c})^2 V_{SO}(\bm{\sigma} \cdot \textbf{l}) \frac{1}{r} \frac{d}{dr} f(x_{SO}) \nonumber \\ 
+& &- i [W f(x_W) - 4 W_D \frac{d}{dx_D} f(x_D)].
+\end{eqnarray}
+%
+The first term, $V_C$, accounts for charged-interactions between charged particles (e.g. an incident proton and a nuclear target with total charge $Z'$) where
+%
+\begin{eqnarray}
+	\label{eq:coulomb_potential}
+	V_C =
+	\begin{cases}
+		\frac{Z Z' e^2}{r} \qquad \text{if $r \geq R_C$} \\
+		\frac{Z Z' e^2}{2 R_C} (3 - \frac{r^2}{R_C^2}) \qquad \text{if $r \leq R_C$},
+	\end{cases}
+\end{eqnarray}
+%
+with $R_C = r_C A^{1/3}$.
+This is the Coulomb potential of a spherical, uniformly-charged distribution of radius $R_C$.
+Note, this term is zero if the projectile particles are neutral; for instance, incident neutrons.
+\textcolor{red}{Why $A^{1/3}$?}
 \\
--- Form of the potential: Woods-Saxon shape, coulomb component, spin-orbit force. (Basic example in Thompson/Nunes.). Can start with discussion similar to Thompson/Nunes.
+
+The remaining terms include Woods-Saxon form factors $f(x_i)$ where $x_i = \frac{r-r_i A^{1/3}}{a_i}$ with radius and diffusivity parameters $r_i$ and $a_i$.
+Woods-Saxon potentials have been used to describe the mean field potential of a nucleon in a nucleus, hence Woods-Saxon form factors serving as good candidates for modeling the projectile-nucleus interaction.
+The $V$ term gives the approximate interaction between the incident particle and the target nucleus and typically has a potential well depth of $V \approx 50$ MeV.
+$V_{SO}$ is the spin-orbit coupling term where $\bm{\sigma}$ is the spin operator and $\bm{l}$ is the angular momentum of the incident particle.
+\textcolor{red}{Important for describing analyzing powers.
+Mention derivative of form factor (peaks at surface of nucleus)?}
 \\
--- Types: best fit, local, and global (see Koning). Advantages and disadvantages of each.
+
+At higher energies, an imaginary component is necessary to describe absorption where particles penetrate into and through the target nucleus without losing energy.
+The first term, $W$, represents volume absorption, and the second, $W_D$, surface absorption.
+These components include a Woods-Saxon form factor and its derivative, respectively.
+Note, the derivative of the Woods-Saxon function peaks at the nuclear radius, hence the $W_D$ accounting for surface absorption.
+At lower energies ($E < 10$ MeV) the surface term dominates while at higher energies one must include the volume absorption component.
 \\
--- Fit strength, radii, and diffuseness of complex potential.
+
+Phenomenological optical potentials are often obtained by $\chi^2$ minimization fitting angular distributions, analyzing powers, or cross section with radii and diffusivity parameters.
+The $\chi^2$ function is dependent on experimental data which can heavily affect the fitted parameters depending on which data sets are used or the methodology to arrive at an average data set.
+In many situations, several sets of parameters can give a good fit to experimental data.
+Furthermore, optical models may have differing definitions of the $\chi^2$ function.
+Overall, this leads to an ambiguity in fitting an optical potential model.
+In the remainder of this section, we discuss three methods in parameterizing a phenomenological optical potential: best-fit, global-fit, and local-fit.
 \\
--- Surface and volume component from Dickhoff?
+
+A best-fit optical model is a model fit from one set of data (e.g.
+a single elastic angular distribution).
+With several parameters to obtain a satisfactory fit, these models can adequately describe a specific projectile and nuclear target.
+However, parameter sets from best-fit models are energy dependent and fail to make predictions at energies outside the range of data.
+The only recent use of best-fit models are to provide insight in global trends for optical model parameters across different energy ranges, and thus serve as a preliminary step for parameterizing either local or global optical models.
 \\
--- Issue: fitting ambiguities, extractions to exotic regions of the nuclear chart. Some short-comings mentioned in Koning.
+
+A global-fit model is the opposite of the best-fit model in the sense that global-fit models cover wide ranges of energy and mass number $A$.
+In this way, we can expect better predictive power from these models for nuclei where no experimental data exist.
+These parameterizations require a large range of data sets to give an ``average'' description of the projectile-nucleus interaction.
+However, these models are often unreliable since different nuclides are not smoothly dependent on $A$ or $Z$ unlike the Woods-Saxon parameters.
+This fault advocates the development of microscopic optical potentials which can consistently describe the interaction for various nuclei.
 \\
--- Make sure to touch on phenomenology of optical potentials in modern experimental analyses (key word is modern!) Koning.
+
+Lastly, the local-fit models are a combination of the former methods.
+Here, parameters are specific to a given target nucleus with energy-dependence expressed analytically.
+The parameters are fit by varying them around global-fit parameters for each nucleus of interest.
+The resulting parameters are similar for neighboring nuclei; however, the variation in parameters is still unpredictable.
+\textcolor{red}{Give example of local-fit optical model from Koning.
+Figures 3-5?
+Pick one.}
 \\
--- References: \cite{Dickhoff:2018wdd} section 3, \cite{Koning:2003zz}.
+
+In the next section, we discuss microscopic optical potentials which seek to overcome the shortcomings of the phenomenological models.
+\textcolor{red}{Motivate and transition to microscopic optical potentials.
+Try to focus on limitations of phenomenological models here (extractions to exotic regions of the nuclear chart).}
+\\
+
+References: \cite{Dickhoff:2018wdd} section 3, \cite{Perey:1976zz}, \cite{Koning:2003zz}.
 
@@
 Things to include:
+\\
+``In the microscopic optical model, the nucleon-nucleon effective interaction is folded with the matter density distribution to give a direct measure of the strength and shape of the nuclear potential."
 \\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Theoretical issues}
-\label{sec:section_4}
+\section{Conclusion}
+\label{sec:conclusion}
 
-Things to include:
+Summary and outlook.
+\\
+Theoretical issues:
 \\
@@
 \\
--- Add this to outlook in conclusion?
-\\
 -- References: \cite{King:2018vzw}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-\label{sec:conclusion}
-
-Summary and outlook.
 

### 2019-07-16 Notes/Candidacy/Paper/candidacy_paper.tex
Updated candidacy paper
Worked on introduction outline.

@@
 
-Things to include:
+-- Why are nuclear reactions important?
+(Processes that help us understand nuclear structure amongst other things.
+Exotic nuclei are short-lived and must used reactions to study them.) List examples.
+Connection to experiment.
+\textcolor{red}{Save this for last.}
 \\
--- Why are nuclear reactions important? (Processes that help us understand nuclear structure amongst other things. Exotic nuclei are short-lived and must used reactions to study them.) List examples.
+-- The nuclear scattering problem.
 \\
--- r-process for motivation.
+-- How do optical potentials help us understand nuclear reactions?.
+Basic introduction to optical potentials.
+Why are they complex?
+Historical introduction.
+Lead into phenomenology.
+Use basic references (old papers).
 \\
--- How do optical potentials help us understand nuclear reactions?
+-- Current progress on optical potentials. Ab initio approaches. Use references from Section \ref{sec:microscopic}.
 \\
--- Basic introduction to optical potentials. Why are they complex? Historical introduction.
+-- Overview of sections.
 \\
@@
 The nuclear wave functions $\psi_i$ form a complete, orthonormal set; thus, we can expand the wave function $\Psi$ as follows:
+% This neglects antisymmetrization requirements.
 %
@@
 %
+% Finish this derivation using Hodgson.
+%
 \textcolor{red}{Advantages of the projection operator formulation.} Wider applicability with generalization of $P$.
@@
 %
+% Nuclear radii are roughly proportional to A^1/3.
 with $R_C = r_C A^{1/3}$.
@@
 $V_{SO}$ is the spin-orbit coupling term where $\bm{\sigma}$ is the spin operator and $\bm{l}$ is the angular momentum of the incident particle.
-\textcolor{red}{Important for describing analyzing powers.
-Mention derivative of form factor (peaks at surface of nucleus)?}
+\textcolor{red}{Important for describing analyzing powers.}
 \\
@@
 At lower energies ($E < 10$ MeV) the surface term dominates while at higher energies one must include the volume absorption component.
+\textcolor{red}{Mention $W_{SO}$ term.}
 \\

### 2019-07-19 Notes/Candidacy/Paper/candidacy_paper.tex
Updated candidacy paper
Wrote microscopic optical potentials section.

@@
 %	07/15/19 --- Wrote the phenomenology section.
+%	07/17/19 --- Wrote the introduction section.
+%	07/19/19 --- Wrote microscopic optical potentials section.
 %
@@
 
--- Why are nuclear reactions important?
-(Processes that help us understand nuclear structure amongst other things.
-Exotic nuclei are short-lived and must used reactions to study them.) List examples.
-Connection to experiment.
-\textcolor{red}{Save this for last.}
+Nuclear reactions are central to many areas of physics.
+A good understanding of these processes is necessary to answer questions such as the origin of the heavy elements in the universe, fundamental symmetries, or the limits of nuclear stability.
+For example, half of the neutron-rich atomic nuclei past iron on the periodic table are created by the rapid neutron-capture process known as the r-process which involves a series of nuclear reactions even with nuclei that have never been experimentally produced.
+Construction of an ``r-process laboratory'' is underway, the Facility for Rare Isotope Beams (FRIB), which seeks to produce many exotic, neutron-rich isotopes (nuclei with fixed proton number and varying neutron number) and measure new data to better understand the areas mentioned above.
+\textcolor{red}{Talk about nuclear chart figure below (need to add figure).} Facilities must use reactions to produce and study short-lived exotic nuclei.
 \\
--- The nuclear scattering problem.
+
+From the theoretical side, the task is to solve the nuclear scattering problem, that is, a projectile particle scattering from a target nucleus interacting via the strong force.
+Typically, projectile particles consist of protons, neutrons, $\alpha$ particles, or nuclei.
+Scattering from a nuclear target leads to a quantum many-body problem since nuclei are composite particles composed of protons and neutrons; that is, the projectile interacts with several nucleons in the target nucleus.
+This presents a number of challenges.
+Nuclear many-body systems are often non-perturbative and the computational difficulty of the problem drastically increases with nuclear mass number $A$.
+Techniques to simplify the quantum many-body scattering problem are necessary.
 \\
--- How do optical potentials help us understand nuclear reactions?.
-Basic introduction to optical potentials.
-Why are they complex?
-Historical introduction.
-Lead into phenomenology.
-Use basic references (old papers).
+
+One such technique is to introduce a complex potential as an effective projectile-nucleus interaction to account for refraction and absorption of the incident particles.
+These complex potentials are called optical potentials.
+The term optical comes from an analogy where a complex index of refraction is used to describe light refraction and absorption.
+In nuclear scattering, refraction corresponds to elastic scattering whereas absorption corresponds to flux disappearing to inelastic channels.
+Optical potentials have been used to calculate observables of many direct reaction processes and play an important role in the development of nuclear reaction theory.
 \\
--- Current progress on optical potentials. Ab initio approaches. Use references from Section \ref{sec:microscopic}.
+
+Originally, optical potentials were constrained by data, that is, phenomenological models.
+Progress in effective field theory (EFT) and renormalization group methods (SRG) have led to a wealth of knowledge on the fundamental interaction between nucleons \cite{Epelbaum:2008ga}.
+These methods are referred to as \textit{ab initio} or microscopic approaches.
+We now have access to microscopic optical potentials where the interaction between two nucleons (NN force or interaction) is used in place of phenomenological models offering more predictive power for rare isotopes out of experimental reach.
 \\
--- Overview of sections.
-\\
--- References: ...
+
+This paper is organized as follows: in Section \ref{sec:formalism} we present the nuclear optical potential as derived by Feshbach several decades ago \cite{Feshbach:1958nx, Feshbach:1962ut}.
+We give a basic idea of optical potentials conceptually and how they can be used to calculate observable quantities.
+Section \ref{sec:phenomenology} gives an overview of phenomenological optical potentials and some recent results \cite{Koning:2003zz}.
+In Section \ref{sec:microscopic} we discuss two \textit{ab initio} approaches to constructing optical potentials and the successes and limitations of these models.
+Lastly, we summarize and discuss future topics in Section \ref{sec:conclusion}.
 
@@
 
-First, we present the optical potential for an $A+1$ particle system consisting of an incident nucleon and a target nucleus of mass number $A$. The system is described by the Schr\"odinger equation
+First, we present the optical potential for an $A+1$ particle system consisting of an incident nucleon and a target nucleus of mass number $A$ as derived in \cite{Feshbach:1958nx}.
+The system is described by the Schr\"odinger equation
 %
@@
 \textcolor{red}{Mention hard-core problem.} In the following, we suppress the coordinate, spin, and isospin dependencies for brevity.
-We substitute \ref{eq:wave_function} into the Schr\"odinger equation \ref{eq:schrodinger_equation} and use the orthonormality of $\psi_i$ to derive a system of equations for the amplitudes $u_i$:
+We substitute (\ref{eq:wave_function}) into the Schr\"odinger equation \ref{eq:schrodinger_equation} and use the orthonormality of $\psi_i$ to derive a system of equations for the amplitudes $u_i$:
 %
@@
 %
-Then we can rewrite \ref{eq:u_equation} as
+Then we can rewrite (\ref{eq:u_equation}) as
 %
@@
 %
-We solve \ref{eq:u_vector_equation_b} for $\Phi$
+We solve (\ref{eq:u_vector_equation_b}) for $\Phi$
 %
@@
 %
-where $\eta \rightarrow 0^+$ to ensure only outgoing waves are present in exit channels for $u_i$ with $i \geq 1$. Lastly, we substitute $\Phi$ into \ref{eq:u_vector_equation_a} to give
+where $\eta \rightarrow 0^+$ to ensure only outgoing waves are present in exit channels for $u_i$ with $i \geq 1$. Lastly, we substitute $\Phi$ into (\ref{eq:u_vector_equation_a}) to give
 %
@@
 
-We can see from Eq.~\ref{eq:optical_potential} that the optical potential is complex and energy dependent.
+We can see from Eq.~(\ref{eq:optical_potential}) that the optical potential is complex and energy dependent.
 The factor of $i \eta$ leads to $V_{opt}$ being complex, and thus, non-hermitian.
@@
 (Feshbach.)} The projection operators satisfy the following relations: $P+Q=1$, $P^2 = P$, and $Q^2 = Q$.
-We act on Eq.~\ref{eq:schrodinger_equation} with $P$ and $Q$ and use the projection operator relations to obtain two equations:
+We act on Eq.~(\ref{eq:schrodinger_equation}) with $P$ and $Q$ and use the projection operator relations to obtain two equations:
 %
@@
 %
-Solving \ref{eq:qq_qp} for $Q \Psi$ yields
+Solving (\ref{eq:qq_qp}) for $Q \Psi$ yields
 %
@@
 Note, if $P$ does not include all open channels, then a factor of $i \eta$ where $\eta \rightarrow 0^+$ must be inserted in the denominator as before to account for...
-\textcolor{red}{Finish this note.} Substituting $Q \Psi$ into Eq.~\ref{eq:pp_pq} and rearranging gives
+\textcolor{red}{Finish this note.} Substituting $Q \Psi$ into Eq.~(\ref{eq:pp_pq}) and rearranging gives
 %
@@
 %
-\textcolor{red}{Advantages of the projection operator formulation.} Wider applicability with generalization of $P$.
+\textcolor{red}{Advantages of the projection operator formulation.} Wider applicability with generalization of $P$. See Hodgson.
 
@@
 % Nuclear radii are roughly proportional to A^1/3.
-with $R_C = r_C A^{1/3}$.
+and $R_C = r_C A^{1/3}$ is the nuclear radius.
 This is the Coulomb potential of a spherical, uniformly-charged distribution of radius $R_C$.
@@
 
-Things to include:
+In this section, we present two methods to calculate microscopic optical potentials: the multiple scattering approach and nucleon self-energy methods.
+As mentioned before, it is important to have a theoretical grasp on applying microscopic NN potentials to the optical potential methodology in order to make predictions where no experimental data are available.
+Groups have attempted to fit global optical potentials to accomplish this goal but fail to consistently match experimental observables across several nuclei and energies primarily because of the lack of nuclear structure inputs to their models.
+Recently, a number of methods have been successful in calculating microscopic optical potentials (\textcolor{red}{add references here}).
 \\
-``In the microscopic optical model, the nucleon-nucleon effective interaction is folded with the matter density distribution to give a direct measure of the strength and shape of the nuclear potential."
+
+% Multiple-scattering approach
+
+The multiple-scattering approach includes important multiple scattering events in the NN $T$-matrix which is used to calculate the optical potential.
+The NN $T$-matrix uses pairwise interactions between the projectile particle and nucleons with realistic NN forces derived from \textit{ab initio} methods.
+We derive the optical potential using this approach following the notation in \cite{Dickhoff:2018wdd}.
 \\
--- Successes and limitations.
+
+First, we assume two-particle interactions between the projectile and a single nucleon within the target nucleus dominate.
+Then we can write the interaction between the projectile and the nucleus as a sum of all pairwise interactions:
+%
+\begin{eqnarray}
+	\label{eq:ms_total_potential}
+	V = \sum_{i=1}^A V(0, i),
+\end{eqnarray}
+%
+where the arguments in the parentheses indicate the interaction between the projectile ($0$) and a nucleon ($i$).
+Then the Hamiltonian of the $A+1$ system can be written with the approximated potential (\ref{eq:ms_total_potential})
+%
+\begin{eqnarray}
+	\label{eq:ms_hamiltonian}
+	\mathcal{H} = H_0 + H_A + \sum_{i=1}^A V(0, i) = \mathcal{H}_0 + \sum_{i=1}^A V(0, i),
+\end{eqnarray}
+%
+where $\mathcal{H}_0$ gives the energy of the non-interacting projectile and nucleus. The $T$-matrix for elastic scattering from the nuclear target's ground state is
+%
+\begin{eqnarray}
+	\label{eq:tmatrix}
+	T = V + V G_0(E) T,
+\end{eqnarray}
+%
+where the Green's function is given by $G_0(E) = \frac{1}{E - \mathcal{H}_0 + i \eta}$.
 \\
--- Motivation: predictions for exotic region of the nuclear chart.
+
+For elastic scattering, we re-introduce the projection operators from before, $P$ and $Q$, and re-write (\ref{eq:tmatrix})
+%
+\begin{eqnarray}
+	\label{eq:tmatrix_elastic}
+	T = U + U G_0(E) P T,
+\end{eqnarray}
+%
+where the optical potential $U$ describes elastic scattering:
+%
+\begin{eqnarray}
+	\label{eq:ms_optical_potential_elastic}
+	U = V + V G_0(E) Q T,
+\end{eqnarray}
+%
+and the full elastic-scattering $T$-matrix is
+%
+\begin{eqnarray}
+	\label{eq:tmatrix_full_elastic}
+	T_{el} = P U P + P U P G_0(E) P T_{el}.
+\end{eqnarray}
+%
+Now we apply the so-called spectator expansion to the optical potential $U$:
+%
+\begin{eqnarray}
+	\label{eqn:spec_exp}
+	U = \sum_{i=1}^A \tau(0, i) + \sum_{i \neq j}^A \tau(0, i) Q G_0(E) \tau(0, j) + \cdots,
+\end{eqnarray}
+%
+where
+\begin{eqnarray}
+	\label{eq:tau_equations}
+	\tau(0, i) &=& V(0, i) + V(0, i) G_0(E) Q \tau(0, i) = \hat{\tau}(0, i) - \hat{\tau}(0, i) G_0(E) P \tau(0, i),
+\end{eqnarray}
+%
+with the reduced amplitudes $\hat{\tau}(0, i) = V(0, i) + V(0, i) G_0(E) \hat{\tau}(0, i)$.
+The spectator expansion orders the scattering processes in a sequence of active projectile-target interactions.
+The first term corresponds to the projectile interacting with one nucleon while the rest are spectators.
+The second term corresponds to the projectile interacting with two nucleons, etc.
+We make the simplest approximation and take only the first term in the expansion.
 \\
--- Major methods: Multiple scattering (see references in Dickhoff paper) and Green's function based methods (coupled cluster). SRG evolution.
+
+Next, we introduce the new momentum variables
+%
+\begin{subequations}
+	\label{eq:momenta}
+	\begin{eqnarray}
+		\label{eq:momentum_transfer}
+		\textbf{q} = \textbf{k}' - \textbf{k},
+	\end{eqnarray}
+	\begin{eqnarray}
+		\label{eq:total_momentum}
+		\textbf{K} = \frac{1}{2} ( \textbf{k} + \textbf{k}' ),
+	\end{eqnarray}
+	\begin{eqnarray}
+		\label{eq:internal_momentum}
+		\textbf{P} = \frac{1}{2} ( \textbf{p} + \textbf{p}' ),
+	\end{eqnarray}
+\end{subequations}
+%
+which correspond to momentum transfer, total momentum, and total internal momentum of nucleons, given initial and final momenta $\textbf{k}$ and $\textbf{k}'$, respectively.
+We can write the optical potential as a convolution of the effective interaction with the target's ground state:
+%
+\begin{eqnarray}
+	\label{eq:ms_optical_potential}
+	U(\textbf{q}, \textbf{K}; E) = \sum_{\alpha} \int d^3 P \, \eta(\textbf{P}, \textbf{q}, \textbf{K}) \hat{\tau}_{\alpha}(\textbf{k}, \textbf{k}') \rho_{\alpha}(\textbf{P} - (A-1) \frac{\textbf{q}}{2 A}, \textbf{P} + (A-1) \frac{\textbf{q}}{2 A}),
+\end{eqnarray}
+%
+where $\eta$ imposes Lorentz invariance flux in transforming from the NN to the $A+1$ system and $\rho$ represents the one-body density matrix.
 \\
--- Coupled cluster Green's function \cite{Rotureau:2016jpf}.
+
+There are multiple ways to calculate the $T$-matrix and one-body density matrix $\rho$.
+For examples, recent studies have used the No-Core Shell Model method to calculate the density matrix which allows for a consistent NN interaction between the density matrix and $T$-matrix (\textcolor{red}{reference}).
+Other studies have used interactions softened by Similarity Renormalization Group (\textcolor{red}{reference}).
+Figure \textcolor{red}{figure number} shows cross sections and analyzing power for elastic proton scattering from $^{40}$Ca using the multiple-scattering approach.
+\textcolor{red}{Add figure here.}
 \\
--- References: \cite{Dickhoff:2018wdd} section 4, \cite{Furumoto:2019anr} G-matrix interaction, \cite{Idini:2019hkq} self-consistent Green's function, \cite{Rotureau:2016jpf}.
+% Add limitations of method.
+% Implementation of three body forces is challenging and limits the theory to large scattering energies (>200 MeV).
+
+% Nucleon self-energy
+
+There has been recent interest in the development of microscopic optical potentials based on chiral effective field theory, $\chi^{EFT}$.
+We will present the nucleon self-energy method from this perspective.
+In quantum many-body physics, the optical potential for scattering states is identified with the energy- and momentum-dependent single particle self-energy.
+Here, the basic idea is to calculate the nucleon self-energy in nuclear matter using chiral interactions.
+First, we give a brief description of $\chi^{EFT}$.
+\\
+
+In $\chi^{EFT}$, chiral perturbation theory is applied to nuclear systems and gives an EFT involving nucleons and Goldstone bosons, which are pions, due to chiral symmetry breaking.
+The theory is split into long- and short-range terms where the long-range terms (pion exchanges) are calculated explicitly, and the short-range terms (contact terms) are parameterized by NN scattering data.
+Chiral interactions can be softened by RG transformations to ameliorate obstacles in many-body calculations often due to the hard repulsive core in the NN force.
+However, being an effective field theory, a regularization procedure is necessary to separate high- and low-energy physics.
+From the optical potential perspective, this offers a trade-off.
+These theories are well suited to describe low-energy scattering but fail at energies near or above the momentum-space cutoff employed.
+\\
+
+We derive an optical potential by computing the nucleon self-energy in nuclear matter using chiral interactions.
+The first two perturbative contributions to the nucleon self-energy are shown in Figure \textcolor{red}{add figure here} and are given by
+%
+\begin{eqnarray}
+	\label{eq:nucleon_self_energy_1}
+	\Sigma_{2N}^{(1)} (q; k_f) = \sum_i \mel{\textbf{q} \textbf{h}_i s s_i t t_i}{V_{2N}^{eff}}{\textbf{q} \textbf{h}_i s s_i t t_i} n_i,
+\end{eqnarray}
+%
+\begin{eqnarray}
+	\label{eq:nucleon_self_energy_2a}
+	\Sigma_{2N}^{(2a)} (q, \omega; k_f) = \frac{1}{2} \sum_{ijk} \frac{|\mel{\textbf{p}_i \textbf{p}_k s_i s_k t_i t_k}{V_{2N}^{eff}}{\textbf{q} \textbf{h}_j s s_j t t_j}|^2}{\omega+\epsilon_j-\epsilon_i-\epsilon_k+i \eta} \bar{n}_i n_j \bar{n}_k,
+\end{eqnarray}
+%
+\begin{eqnarray}
+	\label{eq:nucleon_self_energy_2b}
+	\Sigma_{2N}^{(2b)} (q, \omega; k_f) = \frac{1}{2} \sum_{ijk} \frac{|\mel{\textbf{h}_i \textbf{h}_k s_i s_k t_i t_k}{V_{2N}^{eff}}{\textbf{q} \textbf{p}_j s s_j t t_j}|^2}{\omega+\epsilon_j-\epsilon_i-\epsilon_k-i \eta} n_i \bar{n}_j n_k,
+\end{eqnarray}
+%
+where $n_i$ is the occupation probability $\theta(k_f - k_i)$ for a filled state with momentum $\textbf{k}_i$ below the Fermi-surface, and the occupation probability for particle states is $\bar{n}_i = 1 - n_i$.
+The summations are over intermediate-state momenta for particles $\textbf{p}_i$ and holes $\textbf{h}_i$, their spins $s_i$, and isospins $t_i$ The energies are calculated self-consistently with $\epsilon_i = \frac{q^2}{2 M} + \Re \Sigma(q, \epsilon(q))$ where $M$ is the mass of the nucleon.
+\\
+
+The effective potentials $V_{2N}^{eff}$ consist of an NN potential with an effective, medium-dependent NN interaction.
+The medium-dependent interaction depends on the chiral three-nucleon force.
+The Hartree-Fock contribution (\ref{eq:nucleon_self_energy_1} is non-local, energy-independent, and real, whereas the next two terms (\ref{eq:nucleon_self_energy_2a} and \ref{eq:nucleon_self_energy_2b}) are non-local, energy dependent, and complex.
+The optical potential is  then given by
+%
+\begin{eqnarray}
+	\label{eq:nucleon_self_energy_optical_potential}
+	U_N(E; k_f^p, k_f^n) = V_N(E; k_f^p, k_f^n) + i W_N(E; k_f^p, k_f^n),
+\end{eqnarray}
+%
+where
+\begin{eqnarray}
+	\label{eq:nucleon_self_energy_optical_potential_real}
+	V_N(E; k_f^p, k_f^n) = \Re \Sigma_i (q, E(q); k_f^p, k_f^n),
+\end{eqnarray}
+%
+\begin{eqnarray}
+	\label{eq:nucleon_self_energy_optical_potential_imaginary}
+	W_N(E; k_f^p, k_f^n) = \frac{M_N^{k*}}{M} \Im \Sigma_i (q, E(q); k_f^p, k_f^n),
+\end{eqnarray}
+%
+where the subscript $N$ refers to a propagating proton or nucleon.
+Here, $M_N^{k*}$ is the nucleon effective $k$-mass defined by $\frac{M_N^{k*}}{M} = (1+\frac{M}{k} \frac{\partial}{\partial k} V_N(k, E(k)))^{-1}$.
+\\
+% Add limitations of method.
+
+\textcolor{red}{Successes and limitations.} References: \cite{Dickhoff:2018wdd} section 4, \cite{Furumoto:2019anr} G-matrix interaction, \cite{Idini:2019hkq} self-consistent Green's function, \cite{Rotureau:2016jpf}, \cite{Jeukenne:1977zz}.
 
@@
 \\
--- Uncertainty quantification.
+-- Uncertainty quantification. SRG evolution of optical potentials. Implementation of $\chi^{EFT}$.
 \\

### 2019-07-19 Notes/Candidacy/Paper/candidacy_paper.tex
Updated candidacy paper
First round of edits before sending to DF.

@@
 In nuclear scattering, refraction corresponds to elastic scattering whereas absorption corresponds to flux disappearing to inelastic channels.
-Optical potentials have been used to calculate observables of many direct reaction processes and play an important role in the development of nuclear reaction theory.
+Optical potentials have been used to calculate observables of many direct reaction processes and play an important role in the development of nuclear reaction theory \cite{thompson_nunes_2009}.
 \\
@@
 \label{sec:formalism}
-
-Things to include:
-\\
--- Projectile strikes a nucleus: elastic scattering and more.
-\\
--- Derivation of the general optical potential (equation (2.15) in Feshbach).
-\\
--- More general things from Thompson/Nunes: define optical potentials as complex potentials and consequences of this. Reaction cross section derivation?
-\\
--- Drawbacks to this derivation. Transition to projection operator method.
-\\
--- Relation to observables. Use Lippmann-Schwinger equation to bridge gap to observables: phase shifts and cross sections. Maybe this makes more sense in phenomenology section?
-\\
--- Generalization: derivation with projection operators.
-\\
--- References: \cite{Feshbach:1958nx}, \cite{Feshbach:1962ut}, \cite{thompson_nunes_2009}.
-\\
-
-\textcolor{red}{Add Feshbach reference somewhere.}
-\\
 
@@
 The nuclear wave functions $\psi_i$ form a complete, orthonormal set; thus, we can expand the wave function $\Psi$ as follows:
-% This neglects antisymmetrization requirements.
 %
@@
 
-\textcolor{red}{Mention hard-core problem.} In the following, we suppress the coordinate, spin, and isospin dependencies for brevity.
+In the following, we suppress the coordinate, spin, and isospin dependencies for brevity.
 We substitute (\ref{eq:wave_function}) into the Schr\"odinger equation \ref{eq:schrodinger_equation} and use the orthonormality of $\psi_i$ to derive a system of equations for the amplitudes $u_i$:
@@
 %
-\textcolor{red}{Drawbacks of this derivation.}
 \\
@@
 This only occurs if reactions are possible, that is, $E > \epsilon_1$.
-Because $V_{opt}$ is not hermitian, the $S$-matrix is not unitary giving rise to complex scattering phase shifts.
+Because $V_{opt}$ is non-hermitian, the $S$-matrix is not unitary giving rise to complex scattering phase shifts.
+Furthermore, the potential is non-local from the second term.
+The effective potential depends on the wave function throughout a surrounding region; mathematically, this corresponds to a potential $V(\textbf{r})$ being replaced by $\int d^3 r' \, V(\textbf{r}, \textbf{r}')$ \cite{Hodgson:1971ab}.
+The derivation only accounts for one nucleon in the exit channel, and thus, does not describe all types of reactions.
+Feshbach generalized the approach by using projection operators in \cite{Feshbach:1962ut} which is summarized below.
 \\
 
-\textcolor{red}{Furthermore, the potential is non-local... Use reference \cite{Hodgson:1971ab}.}
-\\
-
-\textcolor{red}{Generalization by using projection operators.
-What do $P$ and $Q$ do?
-Examples?
-(Feshbach.)} The projection operators satisfy the following relations: $P+Q=1$, $P^2 = P$, and $Q^2 = Q$.
+Here, we define the two projection operators $P$ and $Q$.
+$P$ projects the total wave function onto the ground state part of the target wave function: $P \Psi = \psi_0 u_0$.
+$Q$ projects onto all other states and is given by $Q = 1-P$.
+The projection operators satisfy the following relations: $P+Q=1$, $P^2 = P$, $Q^2 = Q$, and $P Q = 0$.
 We act on Eq.~(\ref{eq:schrodinger_equation}) with $P$ and $Q$ and use the projection operator relations to obtain two equations:
@@
 	\label{eq:q_psi}
-	Q \Psi = \frac{1}{E - \mathcal{H}_{QQ}} \mathcal{H}_{QP} P \Psi.
+	Q \Psi = \frac{1}{E - \mathcal{H}_{QQ} + i \eta} \mathcal{H}_{QP} P \Psi.
 \end{eqnarray}
 %
-Note, if $P$ does not include all open channels, then a factor of $i \eta$ where $\eta \rightarrow 0^+$ must be inserted in the denominator as before to account for...
-\textcolor{red}{Finish this note.} Substituting $Q \Psi$ into Eq.~(\ref{eq:pp_pq}) and rearranging gives
+Substituting $Q \Psi$ into Eq.~(\ref{eq:pp_pq}) and rearranging gives
 %
 \begin{eqnarray}
-	\label{p_psi}
-	(E - \mathcal{H}_{PP} - \mathcal{H}_{PQ} \frac{1}{E - \mathcal{H}_{QQ}} \mathcal{H}_{QP}) P \Psi = 0,
+	\label{eq:p_psi}
+	(E - \mathcal{H}_{PP} - \mathcal{H}_{PQ} \frac{1}{E - \mathcal{H}_{QQ} + i \eta} \mathcal{H}_{QP}) P \Psi = 0.
 \end{eqnarray}
 %
-where the effective Hamiltonian is
+By taking the ground state of the target nucleus to be zero, $H_A \psi_0 = 0$,  and using $P = \ket{\psi_0} \bra{\psi_0}$, one can show that Eq. \ref{eq:p_psi} becomes
 %
 \begin{eqnarray}
-	\label{eq:effective_hamiltonian}
-	H_{eff} = \mathcal{H}_{PP} + \mathcal{H}_{PQ} \frac{1}{E - \mathcal{H}_{QQ}} \mathcal{H}_{QP}.
+	\label{eq:p_psi_optical_potential}
+	(E - T - \mel{\psi_0}{V}{\psi_0} - \mel{\psi_0}{V Q \frac{1}{E - \mathcal{H}_{QQ} + i \eta} Q V}{\psi_0}) u_0 = 0,
 \end{eqnarray}
 %
-% Finish this derivation using Hodgson.
+similar to Eq. \ref{eq:u0_equation}. We identify the optical potential as
 %
-\textcolor{red}{Advantages of the projection operator formulation.} Wider applicability with generalization of $P$. See Hodgson.
+\begin{eqnarray}
+	\label{eq:optical_potential_projection}
+	V_{opt} = \mel{\psi_0}{V}{\psi_0} + \mel{\psi_0}{V Q \frac{1}{E - \mathcal{H}_{QQ} + i \eta} Q V}{\psi_0},
+\end{eqnarray}
+% 
+where the first term corresponds to pure elastic scattering, and the second term corresponds to virtual nuclear excitations and de-excitations back to the elastic channel.
+% Comment: add transition to next section here. Make concluding remarks.
 
@@
 %
-% Nuclear radii are roughly proportional to A^1/3.
 and $R_C = r_C A^{1/3}$ is the nuclear radius.
-This is the Coulomb potential of a spherical, uniformly-charged distribution of radius $R_C$.
+Nuclear radii are roughly proportional to $A^{1/3}$, hence the form of $R_C$.
+Here, $V_C$ is the Coulomb potential of a spherical, uniformly-charged distribution of radius $R_C$.
 Note, this term is zero if the projectile particles are neutral; for instance, incident neutrons.
-\textcolor{red}{Why $A^{1/3}$?}
 \\
 
-The remaining terms include Woods-Saxon form factors $f(x_i)$ where $x_i = \frac{r-r_i A^{1/3}}{a_i}$ with radius and diffusivity parameters $r_i$ and $a_i$.
-Woods-Saxon potentials have been used to describe the mean field potential of a nucleon in a nucleus, hence Woods-Saxon form factors serving as good candidates for modeling the projectile-nucleus interaction.
+The remaining terms include Woods-Saxon form factors $f(x_i)$ where $x_i = \frac{r-r_i A^{1/3}}{a_i}$ with radius and diffusivity parameters $r_i$ and $a_i$, respectively.
+Woods-Saxon potentials have been used to describe the mean field potential of a nucleon in a nucleus, thus Woods-Saxon form factors serve as good candidates for modeling the projectile-nucleus interaction.
 The $V$ term gives the approximate interaction between the incident particle and the target nucleus and typically has a potential well depth of $V \approx 50$ MeV.
-$V_{SO}$ is the spin-orbit coupling term where $\bm{\sigma}$ is the spin operator and $\bm{l}$ is the angular momentum of the incident particle.
-\textcolor{red}{Important for describing analyzing powers.}
+$V_{SO}$ is the spin-orbit coupling term where $\bm{\sigma}$ is the spin operator and $\bm{l}$ is the angular momentum of the incident particle and is important for describing analyzing powers.
+% Comment: explain what analyzing powers are.
 \\
@@
 At lower energies ($E < 10$ MeV) the surface term dominates while at higher energies one must include the volume absorption component.
-\textcolor{red}{Mention $W_{SO}$ term.}
+% Comment: mention $W_{SO}$ term.
 \\
@@
 These parameterizations require a large range of data sets to give an ``average'' description of the projectile-nucleus interaction.
-However, these models are often unreliable since different nuclides are not smoothly dependent on $A$ or $Z$ unlike the Woods-Saxon parameters.
+However, these models are often unreliable since different nuclei are not smoothly dependent on $A$ or $Z$ unlike the Woods-Saxon parameters.
 This fault advocates the development of microscopic optical potentials which can consistently describe the interaction for various nuclei.
@@
 The resulting parameters are similar for neighboring nuclei; however, the variation in parameters is still unpredictable.
-\textcolor{red}{Give example of local-fit optical model from Koning.
-Figures 3-5?
-Pick one.}
+\textcolor{red}{Give example of local-fit optical model from Koning with a figure.}
 \\
 
-In the next section, we discuss microscopic optical potentials which seek to overcome the shortcomings of the phenomenological models.
-\textcolor{red}{Motivate and transition to microscopic optical potentials.
-Try to focus on limitations of phenomenological models here (extractions to exotic regions of the nuclear chart).}
+\textcolor{red}{Summarize limitations of phenomenological optical models.} In the next section, we discuss microscopic optical potentials which seek to overcome the shortcomings of the phenomenological models.
 \\
 
-References: \cite{Dickhoff:2018wdd} section 3, \cite{Perey:1976zz}, \cite{Koning:2003zz}.
+References: \cite{Dickhoff:2018wdd}, \cite{Perey:1976zz}, \cite{Koning:2003zz}.
 
@@
 The first term corresponds to the projectile interacting with one nucleon while the rest are spectators.
-The second term corresponds to the projectile interacting with two nucleons, etc.
+The second term corresponds to the projectile interacting with two nucleons and so forth.
 We make the simplest approximation and take only the first term in the expansion.
@@
 
-Next, we introduce the new momentum variables
+Next, we introduce the momentum variables
 %
@@
 where $\eta$ imposes Lorentz invariance flux in transforming from the NN to the $A+1$ system and $\rho$ represents the one-body density matrix.
+% Comment: what is a one-body density matrix?
 \\
 
-There are multiple ways to calculate the $T$-matrix and one-body density matrix $\rho$.
-For examples, recent studies have used the No-Core Shell Model method to calculate the density matrix which allows for a consistent NN interaction between the density matrix and $T$-matrix (\textcolor{red}{reference}).
-Other studies have used interactions softened by Similarity Renormalization Group (\textcolor{red}{reference}).
-Figure \textcolor{red}{figure number} shows cross sections and analyzing power for elastic proton scattering from $^{40}$Ca using the multiple-scattering approach.
-\textcolor{red}{Add figure here.}
+There are several ways to calculate the $T$-matrix and one-body density matrix $\rho$.
+Recent studies have used the No-Core Shell Model method to calculate the density matrix which allows for a consistent NN interaction between the density matrix and $T$-matrix (\textcolor{red}{reference}).
+Other studies have used interactions softened by Similarity Renormalization Group transformations (\textcolor{red}{reference}).
+Figure \textcolor{red}{add figure} shows cross sections and analyzing power for elastic proton scattering from $^{40}$Ca using the multiple-scattering approach.
+\textcolor{red}{Discuss results in figure.
+Drawback to this method: the implementation of three-body forces is challenging and limits the theory to roughly $200$ MeV.}
 \\
-% Add limitations of method.
-% Implementation of three body forces is challenging and limits the theory to large scattering energies (>200 MeV).
 
@@
 The theory is split into long- and short-range terms where the long-range terms (pion exchanges) are calculated explicitly, and the short-range terms (contact terms) are parameterized by NN scattering data.
-Chiral interactions can be softened by RG transformations to ameliorate obstacles in many-body calculations often due to the hard repulsive core in the NN force.
+Chiral interactions can be softened by RG transformations to overcome obstacles in many-body calculations often due to the hard repulsive core in the NN force.
 However, being an effective field theory, a regularization procedure is necessary to separate high- and low-energy physics.
@@
 The effective potentials $V_{2N}^{eff}$ consist of an NN potential with an effective, medium-dependent NN interaction.
-The medium-dependent interaction depends on the chiral three-nucleon force.
+The medium-dependent interaction depends on the chiral three-nucleon force (3NF).
 The Hartree-Fock contribution (\ref{eq:nucleon_self_energy_1} is non-local, energy-independent, and real, whereas the next two terms (\ref{eq:nucleon_self_energy_2a} and \ref{eq:nucleon_self_energy_2b}) are non-local, energy dependent, and complex.
@@
 \\
-% Add limitations of method.
+% Comment: add limitations of method. See motivation on notes.
 
-\textcolor{red}{Successes and limitations.} References: \cite{Dickhoff:2018wdd} section 4, \cite{Furumoto:2019anr} G-matrix interaction, \cite{Idini:2019hkq} self-consistent Green's function, \cite{Rotureau:2016jpf}, \cite{Jeukenne:1977zz}.
+\textcolor{red}{Successes and limitations.} References (other methods): \cite{Dickhoff:2018wdd}, \cite{Furumoto:2019anr} G-matrix interaction, \cite{Idini:2019hkq} self-consistent Green's function, \cite{Rotureau:2016jpf}, \cite{Jeukenne:1977zz}.
 
@@
 
-Summary and outlook.
+Summary and outlook. Include theoretical issues here. Talk about SRG evolution of optical potentials, uncertainty quantification for optical potentials, and implementation of $\chi^{EFT}$.
 \\
-Theoretical issues:
-\\
--- Fitting ambiguities for phenomenological potential.
-\\
--- Uncertainty quantification. SRG evolution of optical potentials. Implementation of $\chi^{EFT}$.
-\\
--- References: \cite{King:2018vzw}.
+% Comment: references: \cite{King:2018vzw}.
 

### 2019-07-26 Notes/Candidacy/Paper/candidacy_paper.tex
Updates to candidacy paper
Added some sub-sections.
Updated candidacy paper
First draft complete. Added revisions to all sections outside of conclusion.

@@
 %	07/19/19 --- Wrote microscopic optical potentials section.
+%	07/25/19 --- Revised draft from introduction through multiple-scattering approach.
+%	07/26/19 --- Revised nucleon self-energy section and wrote conclusion.
 %
@@
 For example, half of the neutron-rich atomic nuclei past iron on the periodic table are created by the rapid neutron-capture process known as the r-process which involves a series of nuclear reactions even with nuclei that have never been experimentally produced.
-Construction of an ``r-process laboratory'' is underway, the Facility for Rare Isotope Beams (FRIB), which seeks to produce many exotic, neutron-rich isotopes (nuclei with fixed proton number and varying neutron number) and measure new data to better understand the areas mentioned above.
-\textcolor{red}{Talk about nuclear chart figure below (need to add figure).} Facilities must use reactions to produce and study short-lived exotic nuclei.
+Construction of an ``r-process laboratory'' is underway, the Facility for Rare Isotope Beams (FRIB), which seeks to produce many exotic, neutron-rich isotopes (isotopes are nuclei with fixed proton number and varying neutron number) and measure new data to better understand the areas mentioned above.
+Fig.~\ref{fig:nuclear_chart_2018} shows nuclei with the neutron number N on the x-axis and the proton number Z on the y-axis with stable nuclei as black squares.
+The r-process takes place below the line of stability with exotic, neutron-rich nuclei, which is the region where FRIB is expected to make substantial progress.
+It is critical to understand nuclear reactions since facilities must use reactions to produce and study short-lived exotic nuclei.
 \\
@@
 
+%
+\begin{figure}
+	\captionsetup{singlelinecheck=false,justification=raggedright}
+	\centering
+	\includegraphics[width=14cm]{nuclear_chart_2018}
+	\caption{Chart of nuclides with neutron number N counted horizontally and proton number Z counted vertically.
+The green squares correspond to experimentally observed nuclei, whereas the green shaded region depicts the theoretical limits for each isotope.
+Blue squares correspond to theoretical calculations by \textit{ab initio} methods which will be discussed later.
+(Figure from H.
+Hergert.)}
+	\label{fig:nuclear_chart_2018}
+\end{figure}
+%
+
 One such technique is to introduce a complex potential as an effective projectile-nucleus interaction to account for refraction and absorption of the incident particles.
@@
 The term optical comes from an analogy where a complex index of refraction is used to describe light refraction and absorption.
-In nuclear scattering, refraction corresponds to elastic scattering whereas absorption corresponds to flux disappearing to inelastic channels.
+In nuclear scattering, refraction corresponds to elastic scattering and absorption corresponds to flux disappearing to inelastic channels.
 Optical potentials have been used to calculate observables of many direct reaction processes and play an important role in the development of nuclear reaction theory \cite{thompson_nunes_2009}.
@@
 
-Originally, optical potentials were constrained by data, that is, phenomenological models.
-Progress in effective field theory (EFT) and renormalization group methods (SRG) have led to a wealth of knowledge on the fundamental interaction between nucleons \cite{Epelbaum:2008ga}.
-These methods are referred to as \textit{ab initio} or microscopic approaches.
-We now have access to microscopic optical potentials where the interaction between two nucleons (NN force or interaction) is used in place of phenomenological models offering more predictive power for rare isotopes out of experimental reach.
+Originally, optical potentials were constrained by nuclear scattering data to compute effective projectile-nucleus potentials.
+These phenomenological models are parametrized by fitting scattering observables with parameters such as nuclear radii, diffusivity, etc.
+Progress in effective field theory (EFT) and renormalization group (RG) methods have led to a wealth of knowledge on the fundamental interaction between nucleons \cite{Epelbaum:2008ga}.
+We now have access to optical potentials where the interaction between two nucleons (NN force or interaction) is used to compute an effective potential.
+These potentials are called \textit{ab initio} or microscopic optical potentials.
+Since microscopic models rely less on scattering data, they offer more predictive power for rare isotopes out of experimental reach.
+% Comment: say anything about blue squares in chart?
 \\
 
-This paper is organized as follows: in Section \ref{sec:formalism} we present the nuclear optical potential as derived by Feshbach several decades ago \cite{Feshbach:1958nx, Feshbach:1962ut}.
+This paper is organized as follows: in Sec.~\ref{sec:formalism} we present the nuclear optical potential as derived by Feshbach several decades ago \cite{Feshbach:1958nx, Feshbach:1962ut}.
 We give a basic idea of optical potentials conceptually and how they can be used to calculate observable quantities.
-Section \ref{sec:phenomenology} gives an overview of phenomenological optical potentials and some recent results \cite{Koning:2003zz}.
-In Section \ref{sec:microscopic} we discuss two \textit{ab initio} approaches to constructing optical potentials and the successes and limitations of these models.
-Lastly, we summarize and discuss future topics in Section \ref{sec:conclusion}.
+Sec.~\ref{sec:phenomenology} gives an overview of phenomenological optical potentials and some recent results \cite{Koning:2003zz}.
+In Sec.~\ref{sec:microscopic} we discuss two \textit{ab initio} approaches to constructing optical potentials and the successes and limitations of these models.
+Lastly, we summarize and discuss future topics in Sec.~\ref{sec:conclusion}.
 
@@
 %
-Note, the factors $u_i$ carry the $\textbf{r}_0$ dependence. 
+Note, the expansion coefficients $u_i$ carry the $\textbf{r}_0$ dependence. Physically, the expansion coefficients correspond to different outgoing channels with $u_0$ representing elastic scattering.
 \\
@@
 In the following, we suppress the coordinate, spin, and isospin dependencies for brevity.
-We substitute (\ref{eq:wave_function}) into the Schr\"odinger equation \ref{eq:schrodinger_equation} and use the orthonormality of $\psi_i$ to derive a system of equations for the amplitudes $u_i$:
+We substitute (\ref{eq:wave_function}) into the Schr\"odinger equation (\ref{eq:schrodinger_equation}) and use the orthonormality of $\psi_i$ to derive a system of equations for the expansion coefficients $u_i$:
 %
@@
 	\label{eq:hamiltonian_operator}
-	H_{ij} = T_0 \delta_{ij} + V_{ij} + \epsilon_i \delta_{ij}.
+	H_{ij} = T_0 \delta_{ij} + V_{ij} + \epsilon_i \delta_{ij},
 \end{eqnarray}
 %
-Then we can rewrite (\ref{eq:u_equation}) as
+for $i$, $j > 0$. Then we can rewrite (\ref{eq:u_equation}) as
 %
@@
 Furthermore, the potential is non-local from the second term.
-The effective potential depends on the wave function throughout a surrounding region; mathematically, this corresponds to a potential $V(\textbf{r})$ being replaced by $\int d^3 r' \, V(\textbf{r}, \textbf{r}')$ \cite{Hodgson:1971ab}.
+We can see the non-locality by acting the operator $V_{opt}$ on a wave function $\Psi$ in coordinate-space, giving an integral over the surrounding region.
+Mathematically, this corresponds to a term $\int d^3 r' \, V(\textbf{r}, \textbf{r}') \Psi(\textbf{r}')$ in the Schr\"odinger equation \cite{Hodgson:1971ab}.
 The derivation only accounts for one nucleon in the exit channel, and thus, does not describe all types of reactions.
@@
 		\label{eq:qq_qp}
-		(E - \mathcal{H}_{QQ}) Q \Psi = \mathcal{H}_{QP} P \Psi.
+		(E - \mathcal{H}_{QQ}) Q \Psi = \mathcal{H}_{QP} P \Psi,
 	\end{eqnarray}
@@
 %
-Solving (\ref{eq:qq_qp}) for $Q \Psi$ yields
+where $\mathcal{H}_{PP}$ refers to $P \mathcal{H} P$ and so forth. Solving (\ref{eq:qq_qp}) for $Q \Psi$ yields
 %
@@
 %
-By taking the ground state of the target nucleus to be zero, $H_A \psi_0 = 0$,  and using $P = \ket{\psi_0} \bra{\psi_0}$, one can show that Eq. \ref{eq:p_psi} becomes
+By taking the ground state of the target nucleus to be zero, $H_A \psi_0 = 0$,  and using $P = \ket{\psi_0} \bra{\psi_0}$, one can show that Eq.~(\ref{eq:p_psi}) becomes
 %
@@
 %
-similar to Eq. \ref{eq:u0_equation}. We identify the optical potential as
+similar to Eq.~(\ref{eq:u0_equation}). We identify the optical potential as
 %
@@
 where the first term corresponds to pure elastic scattering, and the second term corresponds to virtual nuclear excitations and de-excitations back to the elastic channel.
-% Comment: add transition to next section here. Make concluding remarks.
+Note, this is technically the same as Eq.~(\ref{eq:optical_potential}), as the inner products are written out explicitly in Eq.~(\ref{eq:optical_potential_projection}) and denoted with subscripts in Eq.~(\ref{eq:optical_potential}).
+Also, the two vector terms $\textbf{V}_0$ in the original equation accounts for couplings of the elastic channel to inelastic channels, while this is done with the $Q$ projection operator in the second definition of the optical potential.
+% Comment: concluding remarks or transition?
 
@@
 
-Historically, phenomenological optical potentials have been obtained by fitting elastic-scattering angular distributions with a complex potential of the form
+Historically, phenomenological optical potentials have been obtained by fitting elastic-scattering angular distributions with a complex potential of the form \cite{Perey:1976zz, Dickhoff:2018wdd}
 %
@@
 	\label{eq:phenomenological_optical_potential}
-	V_{opt}(r) &=& V_C - V f(x_0) + (\frac{\hbar}{m_{\pi} c})^2 V_{SO}(\bm{\sigma} \cdot \textbf{l}) \frac{1}{r} \frac{d}{dr} f(x_{SO}) \nonumber \\ 
-& &- i [W f(x_W) - 4 W_D \frac{d}{dx_D} f(x_D)].
+	V_{opt}(r, E) &=& V_C(r) - V(E) f(x_0) + (\frac{\hbar}{m_{\pi} c})^2 V_{SO}(E, \bm{\sigma} \cdot \textbf{l}) \frac{1}{r} \frac{d}{dr} f(x_{SO}) \nonumber \\ 
+& &- i [W(E) f(x_W) - 4 W_D(E) \frac{d}{dx_D} f(x_D)].
 \end{eqnarray}
+% Comment: how is this related to nuclear density or probability of finding a nucleon in the nucleus?
 %
@@
 Woods-Saxon potentials have been used to describe the mean field potential of a nucleon in a nucleus, thus Woods-Saxon form factors serve as good candidates for modeling the projectile-nucleus interaction.
-The $V$ term gives the approximate interaction between the incident particle and the target nucleus and typically has a potential well depth of $V \approx 50$ MeV.
-$V_{SO}$ is the spin-orbit coupling term where $\bm{\sigma}$ is the spin operator and $\bm{l}$ is the angular momentum of the incident particle and is important for describing analyzing powers.
-% Comment: explain what analyzing powers are.
+(A mean field potential is a potential that averages over the interactions of a system reducing a many-body problem to a one-body problem.) The $V$ term gives the approximate interaction between the incident particle and the target nucleus and typically has a potential well depth of $V \approx 50$ MeV.
+$V_{SO}$ is the spin-orbit coupling term where $\bm{\sigma}$ is the spin operator and $\bm{l}$ is the angular momentum of the incident particle and is important for describing analyzing powers (scattering observables related to spin-dependent cross sections).
 \\
 
-At higher energies, an imaginary component is necessary to describe absorption where particles penetrate into and through the target nucleus without losing energy.
+At higher energies, an imaginary component is necessary to describe absorption where particles penetrate into and through the target nucleus.
 The first term, $W$, represents volume absorption, and the second, $W_D$, surface absorption.
@@
 At lower energies ($E < 10$ MeV) the surface term dominates while at higher energies one must include the volume absorption component.
-% Comment: mention $W_{SO}$ term.
+In Fig.~\ref{fig:potential_wells_omp}, we show examples of the energy dependent terms in Eq.~\ref{eq:phenomenological_optical_potential}.
 \\
+
+%
+\begin{figure}
+	\captionsetup{singlelinecheck=false,justification=raggedright}
+	\centering
+	\includegraphics[width=10cm]{potential_wells_omp}
+	\caption{Potential well depths as a function of laboratory energy $E$ for each of the terms in Eq.~\ref{eq:phenomenological_optical_potential} including an imaginary spin-orbit term, $W_{SO}$.
+(Figure from \cite{Koning:2003zz}.)}
+	\label{fig:potential_wells_omp}
+\end{figure}
+%
 
@@
 The resulting parameters are similar for neighboring nuclei; however, the variation in parameters is still unpredictable.
-\textcolor{red}{Give example of local-fit optical model from Koning with a figure.}
+An example of a recent local-fit optical potential is given in \cite{Koning:2003zz}.
 \\
 
-\textcolor{red}{Summarize limitations of phenomenological optical models.} In the next section, we discuss microscopic optical potentials which seek to overcome the shortcomings of the phenomenological models.
-\\
-
-References: \cite{Dickhoff:2018wdd}, \cite{Perey:1976zz}, \cite{Koning:2003zz}.
+Phenomenological models have been successful in describing scattering from nuclei where data are available; however, the approach lacks realistic nuclear structure inputs like multi-pion exchange contributions, three-body interactions, etc.
+Without including these details, phenomenological models cannot make consistent predictions across all scattering systems or extend to exotic nuclei.
+Furthermore, there is no reliable way to quantify uncertainty in these models.
+In the next section, we discuss microscopic optical potentials which seek to overcome the shortcomings of the phenomenological models.
 
@@
 Groups have attempted to fit global optical potentials to accomplish this goal but fail to consistently match experimental observables across several nuclei and energies primarily because of the lack of nuclear structure inputs to their models.
-Recently, a number of methods have been successful in calculating microscopic optical potentials (\textcolor{red}{add references here}).
-\\
+Recently, a number of methods have been successful in calculating microscopic optical potentials \cite{Furumoto:2019anr, Idini:2019hkq, Rotureau:2016jpf}.
 
-% Multiple-scattering approach
+%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Multiple-scattering approach}
+\label{sec:multiple_scattering}
 
@@
 The NN $T$-matrix uses pairwise interactions between the projectile particle and nucleons with realistic NN forces derived from \textit{ab initio} methods.
-We derive the optical potential using this approach following the notation in \cite{Dickhoff:2018wdd}.
+We derive the optical potential using this approach following the notation in \cite{Dickhoff:2018wdd} and \cite{Burrows:2018ggt}.
 \\
@@
 where the arguments in the parentheses indicate the interaction between the projectile ($0$) and a nucleon ($i$).
-Then the Hamiltonian of the $A+1$ system can be written with the approximated potential (\ref{eq:ms_total_potential})
+(Note, one can include 3NF's at this step.) Then the Hamiltonian of the $A+1$ system can be written with the approximated potential (\ref{eq:ms_total_potential})
 %
@@
 \begin{eqnarray}
-	\label{eqn:spec_exp}
+	\label{eq:spec_exp}
 	U = \sum_{i=1}^A \tau(0, i) + \sum_{i \neq j}^A \tau(0, i) Q G_0(E) \tau(0, j) + \cdots,
@@
 The spectator expansion orders the scattering processes in a sequence of active projectile-target interactions.
-The first term corresponds to the projectile interacting with one nucleon while the rest are spectators.
+The first term corresponds to the projectile interacting with one nucleon while the rest are spectators depicted in Fig.~\ref{fig:single_scattering}.
 The second term corresponds to the projectile interacting with two nucleons and so forth.
-We make the simplest approximation and take only the first term in the expansion.
-\\
+We make the simplest approximation and take only the first term in the expansion called the impulse approximation.
+The impulse approximation is valid when the energy of the incident particle is much larger than the binding potential of the struck nucleon ($E > 100$ MeV).
+Also, 3NF's do not contribute in the impulse approximation since it only takes projectile-nucleon interactions into account.
+
+%
+\begin{figure}
+	\captionsetup{singlelinecheck=false,justification=raggedright}
+	\centering
+	\includegraphics[width=8cm]{single_scattering}
+	\caption{Diagram of the single scattering term in the spectator expansion where the momentum variables are defined below. (Figure from \cite{Burrows:2018ggt}.)}
+	\label{fig:single_scattering}
+\end{figure}
+%
 
@@
 %
-which correspond to momentum transfer, total momentum, and total internal momentum of nucleons, given initial and final momenta $\textbf{k}$ and $\textbf{k}'$, respectively.
-We can write the optical potential as a convolution of the effective interaction with the target's ground state:
+which correspond to momentum transfer, total momentum, and total internal momentum of nucleons, given initial and final momenta $\textbf{k}$ and $\textbf{k}'$, respectively (see Fig.~\ref{fig:single_scattering}).
+We can write the optical potential in momentum-space as a convolution of the effective interaction with the target's ground state:
 %
@@
 	\label{eq:ms_optical_potential}
-	U(\textbf{q}, \textbf{K}; E) = \sum_{\alpha} \int d^3 P \, \eta(\textbf{P}, \textbf{q}, \textbf{K}) \hat{\tau}_{\alpha}(\textbf{k}, \textbf{k}') \rho_{\alpha}(\textbf{P} - (A-1) \frac{\textbf{q}}{2 A}, \textbf{P} + (A-1) \frac{\textbf{q}}{2 A}),
+	U(\textbf{q}, \textbf{K}; E) = \sum_{\alpha = p, n} \int d^3 P \, \eta(\textbf{P}, \textbf{q}, \textbf{K}) \hat{\tau}_{\alpha}(\textbf{k}, \textbf{k}') \rho_{\alpha}(\textbf{P} - (A-1) \frac{\textbf{q}}{2 A}, \textbf{P} + (A-1) \frac{\textbf{q}}{2 A}),
 \end{eqnarray}
 %
-where $\eta$ imposes Lorentz invariance flux in transforming from the NN to the $A+1$ system and $\rho$ represents the one-body density matrix.
-% Comment: what is a one-body density matrix?
+where $\eta$, the M\o ller factor, relates the NN zero-momentum frame to the NA zero-momentum frame (details in \cite{Elster:1996xh}) and $\rho_{\alpha}$ represents the one-body density matrix (proton and neutron densities).
+There are several ways to calculate the $T$-matrix and one-body density matrix $\rho$.
+Recent studies have used the No-Core Shell Model method to calculate the density matrix which allows for a consistent NN interaction between the density matrix and $T$-matrix (\cite{Burrows:2018ggt, Gennari:2017yez}).
+Fig.~\ref{fig:burrows_figure} shows cross section results for elastic proton scattering from $^{4}$He using the multiple-scattering approach.
 \\
 
-There are several ways to calculate the $T$-matrix and one-body density matrix $\rho$.
-Recent studies have used the No-Core Shell Model method to calculate the density matrix which allows for a consistent NN interaction between the density matrix and $T$-matrix (\textcolor{red}{reference}).
-Other studies have used interactions softened by Similarity Renormalization Group transformations (\textcolor{red}{reference}).
-Figure \textcolor{red}{add figure} shows cross sections and analyzing power for elastic proton scattering from $^{40}$Ca using the multiple-scattering approach.
-\textcolor{red}{Discuss results in figure.
-Drawback to this method: the implementation of three-body forces is challenging and limits the theory to roughly $200$ MeV.}
-\\
+%
+\begin{figure}
+	\captionsetup{singlelinecheck=false,justification=raggedright}
+	\centering
+	\includegraphics[width=8cm]{burrows_figure}
+	\caption{Differential cross section divided by Rutherford cross section for elastic scattering of protons from $^{4}$He at lab energies $100$ (top), $150$ (middle), and $200$ (bottom) MeV.
+The lower axes show the momentum transfer $q$ and the upper axes show the center-of-mass angle.
+Lastly, the values of $\hbar \omega$ serve as inputs to the NCSM, and dashed vertical lines indicate the momentum transfer $q = 2.45$ fm$^{-1}$ corresponding to the lab energy $125$ MeV of the $np$ system.
+(Figure from \cite{Burrows:2018ggt}.)}
+	\label{fig:burrows_figure}
+\end{figure}
+%
 
-% Nucleon self-energy
+Overall, the multiple-scattering approach at first order approach describes experiments well in the energy range of $100$ to $200$ MeV and up to roughly $60$ degrees in the center-of-mass frame.
+At angles larger than this, 3NF's become important due to three-body scattering.
+Unfortunately, the implementation of 3NF's is challenging as including an extra term in Eq.~(\ref{eq:ms_total_potential}) forces one to take another term in the spectator expansion (\ref{eq:spec_exp}).
+
+%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Nucleon self-energy with chiral interactions}
+\label{sec:nucleon_self_energy}
 
@@
 In quantum many-body physics, the optical potential for scattering states is identified with the energy- and momentum-dependent single particle self-energy.
+Particle self-energy is the energy that a particle has as a result of changes that it itself causes in its environment.
+We will denote self-energy with $\Sigma$.
 Here, the basic idea is to calculate the nucleon self-energy in nuclear matter using chiral interactions.
@@
 In $\chi^{EFT}$, chiral perturbation theory is applied to nuclear systems and gives an EFT involving nucleons and Goldstone bosons, which are pions, due to chiral symmetry breaking.
-The theory is split into long- and short-range terms where the long-range terms (pion exchanges) are calculated explicitly, and the short-range terms (contact terms) are parameterized by NN scattering data.
+This gives a low-energy description of the nuclear force with proton, neutron, and pion degrees of freedom with protons and neutrons interacting by pion exchanges and contact forces.
+The theory contains long- and short-range terms where the long-range terms (pion exchanges) are calculated explicitly, and the short-range terms (contact forces) are parameterized by NN scattering data.
 Chiral interactions can be softened by RG transformations to overcome obstacles in many-body calculations often due to the hard repulsive core in the NN force.
 However, being an effective field theory, a regularization procedure is necessary to separate high- and low-energy physics.
+At high energies, the theory is no longer valid and a cutoff must be introduced.
 From the optical potential perspective, this offers a trade-off.
@@
 
-We derive an optical potential by computing the nucleon self-energy in nuclear matter using chiral interactions.
-The first two perturbative contributions to the nucleon self-energy are shown in Figure \textcolor{red}{add figure here} and are given by
+%
+\begin{figure}
+	\captionsetup{singlelinecheck=false,justification=raggedright}
+	\centering
+	\includegraphics[width=10cm]{nucleon_self_energy}
+	\caption{First- and second-order contributions to the nucleon self-energy where the solid lines indicate nucleon propagators and the wavy lines indicate the in-medium NN interaction.
+(Figure from \cite{Whitehead:2018bfs}.)}
+	\label{fig:nucleon_self_energy}
+\end{figure}
+%
+
+We derive an optical potential by computing the nucleon self-energy in nuclear matter using chiral interactions following the formalism of \cite{Whitehead:2018bfs}.
+The first two perturbative contributions to the nucleon self-energy are shown in Fig.~\ref{fig:nucleon_self_energy} and are given by
 %
@@
 The medium-dependent interaction depends on the chiral three-nucleon force (3NF).
-The Hartree-Fock contribution (\ref{eq:nucleon_self_energy_1} is non-local, energy-independent, and real, whereas the next two terms (\ref{eq:nucleon_self_energy_2a} and \ref{eq:nucleon_self_energy_2b}) are non-local, energy dependent, and complex.
+The Hartree-Fock contribution (\ref{eq:nucleon_self_energy_1}) is non-local, energy-independent, and real, whereas the next two terms (\ref{eq:nucleon_self_energy_2a} and \ref{eq:nucleon_self_energy_2b}) are non-local, energy dependent, and complex.
 The optical potential is  then given by
@@
 \\
-% Comment: add limitations of method. See motivation on notes.
 
-\textcolor{red}{Successes and limitations.} References (other methods): \cite{Dickhoff:2018wdd}, \cite{Furumoto:2019anr} G-matrix interaction, \cite{Idini:2019hkq} self-consistent Green's function, \cite{Rotureau:2016jpf}, \cite{Jeukenne:1977zz}.
+%
+\begin{figure}
+	\captionsetup{singlelinecheck=false,justification=raggedright}
+	\centering
+	\includegraphics[width=15cm]{whitehead_figure}
+	\caption{Differential cross section for elastic scattering of protons from calcium isotopes at lab energies $25$ (top), $35$ (middle), and $45$ (bottom) MeV.
+Blue lines correspond to the microscopic cross sections, green lines to a global phenomenological model, and red circles to experimental data.
+(Figure from \cite{Whitehead:2018bfs}.)}
+	\label{fig:whitehead_figure}
+\end{figure}
+%
+
+Fig.
+\ref{fig:whitehead_figure} shows cross section results using this method.
+We see good agreement between the chiral approach and data at forward scattering angles and slight deviation at larger angles.
+Optical models built from chiral interactions are well-suited to describe low-energy scattering data.
+As mentioned before, the momentum-space cutoff of the effective field theory limits the capability of these models.
+Therefore, we expect chiral models to break down for energies approaching the cutoff employed.
+Typically, this limits these models to $E < 200$ MeV.
 
@@
 
-Summary and outlook. Include theoretical issues here. Talk about SRG evolution of optical potentials, uncertainty quantification for optical potentials, and implementation of $\chi^{EFT}$.
+In summary, we described nuclear optical potentials as originally presented by Feshbach several decades ago.
+We discussed the history and current use of phenomenological models focusing on the advantages and disadvantages of different approaches.
+Overall, phenomenological models are restricted to describing systems where sufficient experimental data are present.
+This shortcoming warrants the development of theoretical approaches built from our current understanding of the nuclear force.
+We briefly presented two such approaches in Sec.~\ref{sec:microscopic}: the multiple-scattering approach and the nucleon self-energy approach.
+The former exceeds at describing scattering data up to high energies and large scattering angles.
+The implementation of 3NF's in multiple-scattering approaches is difficult and limits these models.
+However, in some cases, it is possible to consistently calculate the $T$-matrix and nuclear density which is a major advantage.
+The nucleon self-energy approach presented is largely limited by the underlying chiral interactions.
+Using chiral interactions allows for implementation of realistic interactions like pion exchanges, three-body interactions, and a means to quantify theoretical uncertainty estimates.
+Lastly, there are many microscopic approaches not covered in this paper such as the nuclear matter approach by Jeukenne, Lejeune, and Mahaux \cite{Jeukenne:1977zz} or Green's function based methods \cite{Dickhoff:2018wdd}.
+The reader may refer to these references for details.
 \\
-% Comment: references: \cite{King:2018vzw}.
+
+Despite the progress, microscopic models still face some of the challenges that global phenomenological models face in that they can be too imprecise across kinematic ranges or nuclei.
+However, current microscopic models can be used to guide phenomenological models; for instance, on the functional form of potential well depths.
+It is necessary to further understand what components are key in computing an \textit{ab initio} optical potential such as the effect of higher-body interactions or being able to reproduce nuclear structure observables like radii.
+Work is also being done on understanding uncertainty quantification for optical potential models \cite{King:2018vzw}.
+With a stronger grasp on uncertainty quantification, different models can be reliably compared.
+Another area interest involves an RG method called the Similarity Renormalization Group (SRG) which started as a way to soften NN potentials while preserving the underlying observables \cite{Bogner:2006pc, Bogner:2009bt}.
+Scattering observables are process-independent quantities but inherit scheme dependence from the factorization of nuclear structure from the scattering probe.
+Recently, the SRG was used to analyze a simple knockout reaction, deuteron electrodisintegration, to gain insight on the scheme dependence.
+It would be interesting to apply the same idea to optical potential models to investigate scheme dependence and the validity of common approximations.
+% Comment: closing sentence.
 

### 2019-07-29 Notes/Candidacy/Paper/candidacy_paper.tex
Finalized candidacy paper on optical potentials

@@
 %	07/26/19 --- Revised nucleon self-energy section and wrote conclusion.
+%     07/29/19 --- Finalized paper.
 %
@@
 
+\begin{abstract}
+We review current progress on nuclear optical potentials emphasizing the successes and limitations of several approaches.
+We present the basic formalism of the nuclear optical model as derived by Feshbach \cite{Feshbach:1958nx, Feshbach:1962ut}.
+We give an overview of phenomenological models and two microscopic approaches involving multiple-scattering and nucleon self-energy.
+We discuss key theoretical issues for these approaches and future work.
+\end{abstract}
+
 \maketitle
@@
 Construction of an ``r-process laboratory'' is underway, the Facility for Rare Isotope Beams (FRIB), which seeks to produce many exotic, neutron-rich isotopes (isotopes are nuclei with fixed proton number and varying neutron number) and measure new data to better understand the areas mentioned above.
-Fig.~\ref{fig:nuclear_chart_2018} shows nuclei with the neutron number N on the x-axis and the proton number Z on the y-axis with stable nuclei as black squares.
+Fig.~\ref{fig:nuclear_chart_2018} shows nuclei with the neutron number, N, on the x-axis and the proton number, Z, on the y-axis with stable nuclei as black squares.
 The r-process takes place below the line of stability with exotic, neutron-rich nuclei, which is the region where FRIB is expected to make substantial progress.
@@
 Typically, projectile particles consist of protons, neutrons, $\alpha$ particles, or nuclei.
-Scattering from a nuclear target leads to a quantum many-body problem since nuclei are composite particles composed of protons and neutrons; that is, the projectile interacts with several nucleons in the target nucleus.
+Scattering from a nuclear target leads to a quantum many-body problem since nuclei are composite particles composed of protons and neutrons meaning the projectile interacts with several nucleons in the target nucleus.
 This presents a number of challenges.
-Nuclear many-body systems are often non-perturbative and the computational difficulty of the problem drastically increases with nuclear mass number $A$.
-Techniques to simplify the quantum many-body scattering problem are necessary.
+Nuclear many-body systems are often non-perturbative, and the computational difficulty of the problem drastically increases with nuclear mass number $A$.
+Therefore, techniques to simplify the quantum many-body scattering problem are necessary.
 \\
@@
 	\includegraphics[width=14cm]{nuclear_chart_2018}
-	\caption{Chart of nuclides with neutron number N counted horizontally and proton number Z counted vertically.
+	\caption{Chart of nuclides with neutron number, N, counted horizontally and proton number, Z, counted vertically.
 The green squares correspond to experimentally observed nuclei, whereas the green shaded region depicts the theoretical limits for each isotope.
@@
 One such technique is to introduce a complex potential as an effective projectile-nucleus interaction to account for refraction and absorption of the incident particles.
-These complex potentials are called optical potentials.
+These complex potentials are called optical potentials and are used for interpretation of data from reaction experiments.
 The term optical comes from an analogy where a complex index of refraction is used to describe light refraction and absorption.
@@
 Optical potentials have been used to calculate observables of many direct reaction processes and play an important role in the development of nuclear reaction theory \cite{thompson_nunes_2009}.
+% Question: something you should be ready for, and perhaps add a couple of sentences about in your paper, is how optical potentials are actually used in the analysis of reaction experiments, such as might happen at FRIB
 \\
@@
 Since microscopic models rely less on scattering data, they offer more predictive power for rare isotopes out of experimental reach.
-% Comment: say anything about blue squares in chart?
 \\
 
-This paper is organized as follows: in Sec.~\ref{sec:formalism} we present the nuclear optical potential as derived by Feshbach several decades ago \cite{Feshbach:1958nx, Feshbach:1962ut}.
-We give a basic idea of optical potentials conceptually and how they can be used to calculate observable quantities.
+This paper is organized as follows: in Sec.~\ref{sec:formalism} we present the nuclear optical potential as derived by Feshbach several decades ago \cite{Feshbach:1958nx, Feshbach:1962ut} giving a basic idea of optical potentials conceptually.
 Sec.~\ref{sec:phenomenology} gives an overview of phenomenological optical potentials and some recent results \cite{Koning:2003zz}.
@@
 The variables $\textbf{r}_k$ correspond to position, spin, and isospin for the incident nucleon ($k=0$) and each nucleon in the target nucleus ($k=1 \cdots A$).
-$T_0$ is the kinetic energy of the incident nucleon and $V$ is the potential energy of the $A+1$ system.
+$T_0$ is the kinetic energy of the incident nucleon, and $V$ is the potential energy of the $A+1$ system.
 $H_A$ is the Hamiltonian for the target nucleus and satisfies the Schr\"odinger equation
@@
 Here, the index $i$ corresponds to each state of the target nucleus with $i=0$ being the ground state.
+Also, the decomposition of two-, three-, and higher-nucleon interactions in $H_A$ is implicit.
 The nuclear wave functions $\psi_i$ form a complete, orthonormal set; thus, we can expand the wave function $\Psi$ as follows:
@@
 
-In the following, we suppress the coordinate, spin, and isospin dependencies for brevity.
-We substitute (\ref{eq:wave_function}) into the Schr\"odinger equation (\ref{eq:schrodinger_equation}) and use the orthonormality of $\psi_i$ to derive a system of equations for the expansion coefficients $u_i$:
+% Comment: You go from a potential in (2) that is a function of A+1 nucleons.
+Where is there a discussion of the decomposition of the potential into two-body, three-body, ...
+potentials between nucleons?
+EMAIL DF
+In the following, we suppress the notation of coordinate, spin, and isospin dependencies for brevity.
+We substitute Eq.~(\ref{eq:wave_function}) into the Schr\"odinger equation (\ref{eq:schrodinger_equation}) and use the orthonormality of $\psi_i$ to derive a system of equations for the expansion coefficients $u_i$:
 %
@@
 The factor of $i \eta$ leads to $V_{opt}$ being complex, and thus, non-hermitian.
-The factor of $i \eta$ accounts for incident particles leaving the entrance channel $u_0$ to an exit channel $u_i$ where $i \geq 1$.
+It also accounts for incident particles leaving the entrance channel $u_0$ to an exit channel $u_i$ where $i \geq 1$.
 This only occurs if reactions are possible, that is, $E > \epsilon_1$.
@@
 Here, we define the two projection operators $P$ and $Q$.
-$P$ projects the total wave function onto the ground state part of the target wave function: $P \Psi = \psi_0 u_0$.
+$P$ projects the total wave function onto the ground state of the target wave function: $P \Psi = \psi_0 u_0$.
 $Q$ projects onto all other states and is given by $Q = 1-P$.
 The projection operators satisfy the following relations: $P+Q=1$, $P^2 = P$, $Q^2 = Q$, and $P Q = 0$.
-We act on Eq.~(\ref{eq:schrodinger_equation}) with $P$ and $Q$ and use the projection operator relations to obtain two equations:
+We act on Eq.~(\ref{eq:schrodinger_equation}) with $P$ and $Q$, and use the projection operator relations to obtain two equations:
 %
@@
 %
+% Question: be able to derive this below.
 By taking the ground state of the target nucleus to be zero, $H_A \psi_0 = 0$,  and using $P = \ket{\psi_0} \bra{\psi_0}$, one can show that Eq.~(\ref{eq:p_psi}) becomes
@@
 Note, this is technically the same as Eq.~(\ref{eq:optical_potential}), as the inner products are written out explicitly in Eq.~(\ref{eq:optical_potential_projection}) and denoted with subscripts in Eq.~(\ref{eq:optical_potential}).
-Also, the two vector terms $\textbf{V}_0$ in the original equation accounts for couplings of the elastic channel to inelastic channels, while this is done with the $Q$ projection operator in the second definition of the optical potential.
-% Comment: concluding remarks or transition?
+Also, the two vector terms $\textbf{V}_0$ in the original equation account for couplings of the elastic channel to inelastic channels, while this is done with the $Q$ projection operator in the second definition of the optical potential.
 
@@
 	\label{eq:phenomenological_optical_potential}
-	V_{opt}(r, E) &=& V_C(r) - V(E) f(x_0) + (\frac{\hbar}{m_{\pi} c})^2 V_{SO}(E, \bm{\sigma} \cdot \textbf{l}) \frac{1}{r} \frac{d}{dr} f(x_{SO}) \nonumber \\ 
+	V_{opt}(r, E) &=& V_C(r) - V(E) f(x_0) + (\frac{\hbar}{m_{\pi} c})^2 V_{SO}(E) \bm{\sigma} \cdot \textbf{l} \frac{1}{r} \frac{d}{dr} f(x_{SO}) \nonumber \\ 
 & &- i [W(E) f(x_W) - 4 W_D(E) \frac{d}{dx_D} f(x_D)].
 \end{eqnarray}
-% Comment: how is this related to nuclear density or probability of finding a nucleon in the nucleus?
+% Question: how is this related to nuclear density or probability of finding a nucleon in the nucleus?
 %
+% Put a couple sentences here explaining Woods-Saxon form factors and parameters. Combine V_C, V and V_SO. Then W paragraph.
+Here, $f(x_i) = (1 + \exp[x_i])^{-1}$ are Woods-Saxon form factors dependent on the radii and diffusivity parameters, $R_i$ and $a_i$, where $x_i = \frac{r-R_i}{a_i}$.
+The index $i$ specifies each of the terms above (e.g.
+$C$, $0$, $SO$, etc.), $a_i$ is the diffusivity, and $R_i = r_i A^{1/3}$ is the nuclear radius.
+Nuclear radii are roughly proportional to $A^{1/3}$, hence the form of $R_i$.
+Woods-Saxon potentials have been used to describe the mean field potential of a nucleon in a nucleus, thus serve as good candidates for modeling the projectile-nucleus interaction.
+(A mean field potential is a potential that averages over the interactions of a system reducing a many-body problem to a one-body problem.)
+\\
+
 The first term, $V_C$, accounts for charged-interactions between charged particles (e.g. an incident proton and a nuclear target with total charge $Z'$) where
@@
 		\frac{Z Z' e^2}{r} \qquad \text{if $r \geq R_C$} \\
-		\frac{Z Z' e^2}{2 R_C} (3 - \frac{r^2}{R_C^2}) \qquad \text{if $r \leq R_C$},
+		\frac{Z Z' e^2}{2 R_C} (3 - \frac{r^2}{R_C^2}) \qquad \text{if $r \leq R_C$}.
 	\end{cases}
@@
 %
-and $R_C = r_C A^{1/3}$ is the nuclear radius.
-Nuclear radii are roughly proportional to $A^{1/3}$, hence the form of $R_C$.
-Here, $V_C$ is the Coulomb potential of a spherical, uniformly-charged distribution of radius $R_C$.
-Note, this term is zero if the projectile particles are neutral; for instance, incident neutrons.
-\\
-
-The remaining terms include Woods-Saxon form factors $f(x_i)$ where $x_i = \frac{r-r_i A^{1/3}}{a_i}$ with radius and diffusivity parameters $r_i$ and $a_i$, respectively.
-Woods-Saxon potentials have been used to describe the mean field potential of a nucleon in a nucleus, thus Woods-Saxon form factors serve as good candidates for modeling the projectile-nucleus interaction.
-(A mean field potential is a potential that averages over the interactions of a system reducing a many-body problem to a one-body problem.) The $V$ term gives the approximate interaction between the incident particle and the target nucleus and typically has a potential well depth of $V \approx 50$ MeV.
+This is the Coulomb potential of a spherical, uniformly-charged distribution of radius $R_C$.
+Note, this term is zero if the projectile particles are neutral (e.g.
+incident neutrons).
+The $V$ term gives the approximate interaction between the incident particle and the target nucleus and typically has a potential well depth of $V \approx 50$ MeV.
 $V_{SO}$ is the spin-orbit coupling term where $\bm{\sigma}$ is the spin operator and $\bm{l}$ is the angular momentum of the incident particle and is important for describing analyzing powers (scattering observables related to spin-dependent cross sections).
@@
 At lower energies ($E < 10$ MeV) the surface term dominates while at higher energies one must include the volume absorption component.
-In Fig.~\ref{fig:potential_wells_omp}, we show examples of the energy dependent terms in Eq.~\ref{eq:phenomenological_optical_potential}.
+In Fig.~\ref{fig:potential_wells_omp}, we show examples of the energy dependent terms in Eq.~(\ref{eq:phenomenological_optical_potential}).
 \\
@@
 	\includegraphics[width=10cm]{potential_wells_omp}
-	\caption{Potential well depths as a function of laboratory energy $E$ for each of the terms in Eq.~\ref{eq:phenomenological_optical_potential} including an imaginary spin-orbit term, $W_{SO}$.
-(Figure from \cite{Koning:2003zz}.)}
+	\caption{Potential well depths as a function of laboratory energy $E$ for each of the terms in Eq.~\ref{eq:phenomenological_optical_potential} including an imaginary spin-orbit term, $W_{SO}$ \cite{Koning:2003zz}.}
 	\label{fig:potential_wells_omp}
@@
 These parameterizations require a large range of data sets to give an ``average'' description of the projectile-nucleus interaction.
-However, these models are often unreliable since different nuclei are not smoothly dependent on $A$ or $Z$ unlike the Woods-Saxon parameters.
+However, these models are often unreliable since different nuclei are not smoothly dependent on $A$ or $Z$, unlike the Woods-Saxon parameters.
 This fault advocates the development of microscopic optical potentials which can consistently describe the interaction for various nuclei.
@@
 
-In this section, we present two methods to calculate microscopic optical potentials: the multiple scattering approach and nucleon self-energy methods.
-As mentioned before, it is important to have a theoretical grasp on applying microscopic NN potentials to the optical potential methodology in order to make predictions where no experimental data are available.
+In this section, we present two methods to calculate microscopic optical potentials: the multiple-scattering approach and nucleon self-energy methods.
+As previously mentioned, it is important to have a theoretical grasp on applying microscopic NN potentials to the optical potential methodology in order to make predictions where no experimental data are available.
 Groups have attempted to fit global optical potentials to accomplish this goal but fail to consistently match experimental observables across several nuclei and energies primarily because of the lack of nuclear structure inputs to their models.
-Recently, a number of methods have been successful in calculating microscopic optical potentials \cite{Furumoto:2019anr, Idini:2019hkq, Rotureau:2016jpf}.
+Recently, a number of methods have been developed to calculate microscopic optical potentials \cite{Furumoto:2019anr, Idini:2019hkq, Rotureau:2016jpf}.
 
-%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+%___________________________________________________________________________________________________________________
 \subsection{Multiple-scattering approach}
@@
 
-The multiple-scattering approach includes important multiple scattering events in the NN $T$-matrix which is used to calculate the optical potential.
+The multiple-scattering approach includes important multiple-scattering events in the NN $T$-matrix which is used to calculate the optical potential.
 The NN $T$-matrix uses pairwise interactions between the projectile particle and nucleons with realistic NN forces derived from \textit{ab initio} methods.
@@
 where the arguments in the parentheses indicate the interaction between the projectile ($0$) and a nucleon ($i$).
-(Note, one can include 3NF's at this step.) Then the Hamiltonian of the $A+1$ system can be written with the approximated potential (\ref{eq:ms_total_potential})
+(Note, one can include three-nucleon forces (3NF's) at this step.) Then the Hamiltonian of the $A+1$ system can be written with the approximated potential (\ref{eq:ms_total_potential})
 %
@@
 with the reduced amplitudes $\hat{\tau}(0, i) = V(0, i) + V(0, i) G_0(E) \hat{\tau}(0, i)$.
-The spectator expansion orders the scattering processes in a sequence of active projectile-target interactions.
+The spectator expansion orders the scattering processes in a sequence of projectile-target interactions.
 The first term corresponds to the projectile interacting with one nucleon while the rest are spectators depicted in Fig.~\ref{fig:single_scattering}.
@@
 Also, 3NF's do not contribute in the impulse approximation since it only takes projectile-nucleon interactions into account.
+\\
 
@@
 	\includegraphics[width=8cm]{single_scattering}
-	\caption{Diagram of the single scattering term in the spectator expansion where the momentum variables are defined below. (Figure from \cite{Burrows:2018ggt}.)}
+	\caption{Diagram of the single scattering term in the spectator expansion where the momentum variables are defined below \cite{Burrows:2018ggt}.}
 	\label{fig:single_scattering}
@@
 %
-where $\eta$, the M\o ller factor, relates the NN zero-momentum frame to the NA zero-momentum frame (details in \cite{Elster:1996xh}) and $\rho_{\alpha}$ represents the one-body density matrix (proton and neutron densities).
+where $\eta$, the M\o ller factor, relates the NN zero-momentum frame to the NA zero-momentum frame (details in \cite{Elster:1996xh}), and $\rho_{\alpha}$ represents the one-body density matrix (proton and neutron densities).
 There are several ways to calculate the $T$-matrix and one-body density matrix $\rho$.
-Recent studies have used the No-Core Shell Model method to calculate the density matrix which allows for a consistent NN interaction between the density matrix and $T$-matrix (\cite{Burrows:2018ggt, Gennari:2017yez}).
-Fig.~\ref{fig:burrows_figure} shows cross section results for elastic proton scattering from $^{4}$He using the multiple-scattering approach.
+Recent studies have used the No-Core Shell Model (NCSM) method to calculate the density matrix which allows for a consistent NN interaction between the density matrix and $T$-matrix (\cite{Burrows:2018ggt, Gennari:2017yez}).
+It is possible to further simplify Eq.~(\ref{eq:ms_optical_potential}) by making the $\tau \rho$ approximation, which involves writing the potential where the density $\rho$ does not depend on the total internal momentum $\textbf{P}$, and the NN $T$-matrix and the M\o ller factor determine the non-local character of the potential.
+% Question: it would be useful to have a bit more discussion of (30) and what it implies.
+E.g., if one could do the integration over P by pulling the density matrix out of the integral with P=0, then we would have the \tau\rho approximation.
+How does this relate to the phenomenological forms?
+% Question: have an idea of the NCSM.
 \\
@@
 The lower axes show the momentum transfer $q$ and the upper axes show the center-of-mass angle.
-Lastly, the values of $\hbar \omega$ serve as inputs to the NCSM, and dashed vertical lines indicate the momentum transfer $q = 2.45$ fm$^{-1}$ corresponding to the lab energy $125$ MeV of the $np$ system.
-(Figure from \cite{Burrows:2018ggt}.)}
+Lastly, the values of $\hbar \omega$ serve as inputs to the NCSM, and dashed vertical lines indicate the momentum transfer $q = 2.45$ fm$^{-1}$ corresponding to the lab energy $125$ MeV of the $np$ system \cite{Burrows:2018ggt}.}
 	\label{fig:burrows_figure}
@@
 
-Overall, the multiple-scattering approach at first order approach describes experiments well in the energy range of $100$ to $200$ MeV and up to roughly $60$ degrees in the center-of-mass frame.
+Fig.~\ref{fig:burrows_figure} shows cross section results for elastic proton scattering from $^{4}$He using the multiple-scattering approach.
+Overall, the multiple-scattering approach at first order describes experiments well in the energy range of $100$ to $200$ MeV and up to roughly $60$ degrees in the center-of-mass frame.
 At angles larger than this, 3NF's become important due to three-body scattering.
 Unfortunately, the implementation of 3NF's is challenging as including an extra term in Eq.~(\ref{eq:ms_total_potential}) forces one to take another term in the spectator expansion (\ref{eq:spec_exp}).
+% Question: why are 3NF's important eventually? Why are they difficult to implement (math only).
 
-%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+%___________________________________________________________________________________________________________________
 \subsection{Nucleon self-energy with chiral interactions}
@@
 In quantum many-body physics, the optical potential for scattering states is identified with the energy- and momentum-dependent single particle self-energy.
-Particle self-energy is the energy that a particle has as a result of changes that it itself causes in its environment.
+Particle self-energy is the modification to particle energy due to interactions with its environment (in this case, the nuclear medium) and is used in many-body perturbation theory.
 We will denote self-energy with $\Sigma$.
@@
 First, we give a brief description of $\chi^{EFT}$.
+% Question: where did you get the definition of the self-energy as the energy as a result of changes it itself causes in its environment? That is not a definition I would have used.
 \\
@@
 These theories are well suited to describe low-energy scattering but fail at energies near or above the momentum-space cutoff employed.
+% Question: this may imply questions about the cutoff.
 \\
@@
 	\includegraphics[width=10cm]{nucleon_self_energy}
-	\caption{First- and second-order contributions to the nucleon self-energy where the solid lines indicate nucleon propagators and the wavy lines indicate the in-medium NN interaction.
-(Figure from \cite{Whitehead:2018bfs}.)}
+	\caption{First- and second-order contributions to the nucleon self-energy where the solid lines indicate nucleon propagators and the wavy lines indicate the in-medium, anti-symmetrized NN interaction \cite{Whitehead:2018bfs}.}
 	\label{fig:nucleon_self_energy}
 \end{figure}
+% Question: Looking at Figure 5, you state the characteristics of the contributions resulting from each of the diagrams.  How do I see them? 
+% For (a), the diagram looks local (with a local potential).
+Why is it actually non-local?
+(Hint: the figure actually only shows the Hartree term unless you say that the wavy lines are the *antisymmetrized* NN interactions.
+% How can I see that (b) and (c) have imaginary parts?  (This may be evident from (32) and (33), but how do I see that from the diagrams?) 
+% If I think of time running upwards, how would you describe the processes depicted in the figures?
+% For (a) - we know the antisymmetrized NN interaction includes contact and exchange. See https://journals.aps.org/prc/pdf/10.1103/PhysRevC.88.024614.
 %
 
-We derive an optical potential by computing the nucleon self-energy in nuclear matter using chiral interactions following the formalism of \cite{Whitehead:2018bfs}.
+We derive an optical potential by computing the nucleon self-energy in nuclear matter using chiral interactions following the formalism of \cite{Whitehead:2018bfs, Holt:2013tna}.
 The first two perturbative contributions to the nucleon self-energy are shown in Fig.~\ref{fig:nucleon_self_energy} and are given by
@@
 The effective potentials $V_{2N}^{eff}$ consist of an NN potential with an effective, medium-dependent NN interaction.
-The medium-dependent interaction depends on the chiral three-nucleon force (3NF).
+The medium-dependent interaction depends on the chiral three-nucleon force.
 The Hartree-Fock contribution (\ref{eq:nucleon_self_energy_1}) is non-local, energy-independent, and real, whereas the next two terms (\ref{eq:nucleon_self_energy_2a} and \ref{eq:nucleon_self_energy_2b}) are non-local, energy dependent, and complex.
@@
 %
-where the subscript $N$ refers to a propagating proton or nucleon.
+where the subscript, $N$, refers to a propagating proton or nucleon.
 Here, $M_N^{k*}$ is the nucleon effective $k$-mass defined by $\frac{M_N^{k*}}{M} = (1+\frac{M}{k} \frac{\partial}{\partial k} V_N(k, E(k)))^{-1}$.
@@
 	\caption{Differential cross section for elastic scattering of protons from calcium isotopes at lab energies $25$ (top), $35$ (middle), and $45$ (bottom) MeV.
-Blue lines correspond to the microscopic cross sections, green lines to a global phenomenological model, and red circles to experimental data.
-(Figure from \cite{Whitehead:2018bfs}.)}
+Blue lines correspond to the microscopic cross sections, green lines to a global phenomenological model, and red circles to experimental data \cite{Whitehead:2018bfs}.}
 	\label{fig:whitehead_figure}
@@
 We briefly presented two such approaches in Sec.~\ref{sec:microscopic}: the multiple-scattering approach and the nucleon self-energy approach.
-The former exceeds at describing scattering data up to high energies and large scattering angles.
+The former adequately describes scattering data up to high energies and large scattering angles.
 The implementation of 3NF's in multiple-scattering approaches is difficult and limits these models.
@@
 Despite the progress, microscopic models still face some of the challenges that global phenomenological models face in that they can be too imprecise across kinematic ranges or nuclei.
-However, current microscopic models can be used to guide phenomenological models; for instance, on the functional form of potential well depths.
+However, current microscopic models can be used to guide phenomenological models, for instance, on the functional form of potential well depths.
 It is necessary to further understand what components are key in computing an \textit{ab initio} optical potential such as the effect of higher-body interactions or being able to reproduce nuclear structure observables like radii.
@@
 With a stronger grasp on uncertainty quantification, different models can be reliably compared.
-Another area interest involves an RG method called the Similarity Renormalization Group (SRG) which started as a way to soften NN potentials while preserving the underlying observables \cite{Bogner:2006pc, Bogner:2009bt}.
+Another area of interest involves an RG method called the Similarity Renormalization Group (SRG) which started as a way to soften NN potentials while preserving the underlying observables \cite{Bogner:2006pc, Bogner:2009bt}.
 Scattering observables are process-independent quantities but inherit scheme dependence from the factorization of nuclear structure from the scattering probe.
@@
 It would be interesting to apply the same idea to optical potential models to investigate scheme dependence and the validity of common approximations.
-% Comment: closing sentence.
 

### 2019-08-08 Notes/SRG_operator_evolution/srg_operator_evolution.tex
Minor update to SRG operator evolution notes

@@
 , $N$.
-Then $a^{\dagger}_q a_q$ acting on $\psi(k)$ is a matrix multiplication, implying a continuous integration over $d^3k$.
-Therefore, we include a factor of $1 / (k^2 dk) \implies 1 / (k_i k_j \sqrt{w_i w_j})$ in $a^{\dagger}_q a_q (k_i, k_j)$ where $w$ represents the momentum weights.
+Then $a^{\dagger}_q a_q$ acting on $\psi(k)$ is a matrix multiplication, implying a continuous integration over $d^3k / (2 \pi)^3 = 2 / (\pi k^2 dk)$ in spherical coordinates.
+Therefore, we include a factor of $\pi / (2 k_i k_j \sqrt{w_i w_j})$ in $a^{\dagger}_q a_q (k_i, k_j)$ where $w$ represents the momentum weights.
 In matrix form,
@@
 	\label{eq:momentum_projection_operator}
-	a^{\dagger}_q a_q (k_i, k_j) = \frac{\delta_{k_i q} \delta_{k_j q}}{k_i k_j \sqrt{w_i w_j}},
+	a^{\dagger}_q a_q (k_i, k_j) = \frac{\pi \delta_{k_i q} \delta_{k_j q}}{2 k_i k_j \sqrt{w_i w_j}},
 \end{eqnarray}

### 2019-08-08 operators.py
Minor updates to operator.py
Messing with factors of pi / 2, etc.

@@ -94,7 +94,8 @@ def momentum_projection_operator(q, k_array, k_weights, U=np.empty(0)):
         
     # Build momentum projection operator 
     operator = np.zeros( (m, m) )
-    operator[q_index, q_index] = 1 / ( q**2 * q_weight )
+    #operator[q_index, q_index] = 1 / ( q**2 * q_weight )
+    operator[q_index, q_index] = np.pi / ( 2 * q**2 * q_weight )
     
     # Matrix of zeros (m x m) for coupled-channel operator
     o = np.zeros( (m, m) )
@@ -145,7 +146,8 @@ def hankel_transformation(channel, k_array, r_array):
         
         L = 2
         
-    M = np.sqrt(2/np.pi) * k_cols**2 * r_rows * spherical_jn(L, k_cols*r_rows)
+    #M = np.sqrt(2/np.pi) * k_cols**2 * r_rows * spherical_jn(L, k_cols*r_rows)
+    M = np.sqrt(2/np.pi) * r_rows * spherical_jn(L, k_cols*r_rows)
 
     return M
 
@@ -208,4 +210,5 @@ def r2_operator(k_array, k_weights, r_array, dr, U=np.empty(0)):
     # Factor of dr for one integration over dr (the other dr' integration is 
     # killed by delta function) - not sure what the weights should be???
     return r2_momentum_space * dr
+    #return r2_momentum_space / dr
     #return r2_momentum_space

### 2019-08-08 test.py
Update test.py
No actual changes.

@@ -63,8 +63,6 @@ w_initial = psi_initial[ntot:] # 3D1 component
 phi_squared_initial = ( u_initial**2 + w_initial**2 ) / \
                       ( k_array**2 * k_weights )
 
-
-### DO EVOLVED CALCULATION HERE (SEE WHITEBOARD) ###
 # Load evolved wave function
 psi_evolved = ob.wave_function(H_initial, eps, U_matrix) # Unitless
 

### 2019-08-23 run_srg.py
Generated SRG-evolved potentials
kvnn = 10, channel = '3S1', kmax = 30, kmid = 3, ntot = 100, generator = 'Wegner' to lambda = 1.5 fm^-1.

@@ -164,7 +164,7 @@ if __name__ == '__main__':
     ntot = 100
     #ntot = 121
     #ntot = 140
-    #ntot = 140
+    #ntot = 141
     
     # Specify evolution
     

### 2019-08-23 Notes/Operator_evolution/operator_evolution.tex
Started draft of paper
Looking to combine notes in Notes\Magnus and Notes\SRG_operator_evolution.

--- 2019-06-10 Notes/Magnus/magnus.tex
@@
 %
-% File: magnus.tex
+% File: operator_evolution.tex
 %
 % Author: A. J. Tropiano (tropiano.4@osu.edu)
-% Date: January 8, 2019
+% Date: August 23, 2019
 %
-% Notes on Magnus project.
+% Draft of paper on SRG operator evolution and the Magnus expansion.
 %
 % Revision history:
-% 	03/04/19 --- Transitioning these notes into a draft of the eventual paper.
-%     05/30/19 --- Renamed magnus.tex from magnus_Jan08.tex.
+%	...
 %
@@
 \usepackage{graphicx}
-% NOTE: Do not get rid of this path until all figures in Figures sub-folder are re-produced
-\graphicspath{{Figures/}} % Setting the graphics path
-% NEW PATH
-\graphicspath{{../../Figures/Magnus/}} % Setting the graphics path
+\graphicspath{{../../Figures/Operator_evolution/}} % Setting the graphics path
 \usepackage{physics} % For bra-ket notation
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Exploring the Magnus expansion and the in-medium similarity renormalization group}
+\title{Operator evolution from the similarity renormalization group and the Magnus expansion}
 
@@
 
-\noindent{-- Test Magnus expansion SRG implementation on LO NN potential at high $\Lambda$. (Define SRG or IMSRG acronym in abstract.)}
+\noindent{Ideas for Magnus / SRG operator evolution paper}
 \\
--- High $\Lambda$ leads to spurious bound states in spin triplet channels.
+-- Testing the Magnus expansion for high cutoff potentials using the potentials from Wendt 2011 for comparison. Spurious bound states and connection to intruder states in IMSRG calculations.
 \\
--- Decouple spurious bound state(s) by using two approaches within the Magnus implementation to drive the Hamiltonian to band-diagonal, unitarily equivalent form.
+-- SRG/Magnus evolution in different potentials (non-local, local, semi-local). Universality. High cutoffs?
 \\
--- One choice of generator where the deep bound state is decoupled outside low-momentum and another where it is shifted to low-momentum.
+-- Block-diagonal generator for high cutoff potentials and operator evolution. How the block-diagonal generator handles spurious bound states.
 \\
--- Deep bound state corrupts low-momentum physics.
-\\
--- Connection to IMSRG intruder state problem.
-\\
--- Confirm unitarity of Hamiltonian by evaluation of deuteron observables.
-\\
--- Lastly, study operator evolution.
+-- SRG operator evolution for different potentials and generators.
 
@@
 
-\noindent{%
--- In recent years \textit{ab initio} methods have made strides in nuclear structure and reactions.
-}
-\\
--- Realistic binding energies starting from NN and 3N forces have been calculated for many medium mass nuclei using different many-body methods.
-\\
--- The in-medium similarity renormalization group (IMSRG) is one such method \cite{Hergert:2015awm, Hergert:2016iju}.
-\\
--- The IMSRG separates energy scales in the nuclear Hamiltonian by decoupling the reference state from excited states to band- or block-diagonal form.
-\\
--- One can use the decoupled Hamiltonian to solve the many-body Sch{\"o}dinger equation extracting specific eigenvalues and eigenstates which qualifies the IMSRG as an \textit{ab initio} method.
-\\
-
-\noindent{%
--- The IMSRG procedure requires solving a system of nonlinear, coupled differential equations which can often be stiff necessitating a high-order ODE solver.
-}
-\\
--- In principle, the decoupled Hamiltonian (or any operator) is unitarily equivalent but the numerical error of solving the ODE can lead to error on observable quantities.
-\\
--- Furthermore, the model spaces for IMSRG calculations can be extremely large.
-\\
--- Evolving several operators is often impossible due to memory restrictions in storing several operators.
-\\
-
-\noindent{%
--- A variant of the IMSRG that utilizes the Magnus expansion can overcome these limitations.
-}
-\\
--- We will refer to this as the Magnus implementation or simply Magnus.
-\\
--- The Magnus solves for the unitary transformation directly whereas the IMSRG applies the transformation indirectly in steps of the differential flow equation.
-\\
--- From the form of the transformation, the numerical error leaves the unitarity of the evolved Hamiltonian un-affected.
-\\
--- By explicitly solving for the transformation, one can evolve several operators.
-\\
--- The Magnus implementation has become a standard technique in IMSRG calculations as studies have targeted observables such as radii, electromagnetic moments and transitions, etc., requiring consistently evolved operators.
-\\
-
-\noindent{%
--- We test the Magnus implementation on chiral non-local NN potentials in free-space for several EFT cutoffs.
-}
-\\
--- At high cutoffs, spin triplet channels feature spurious, deeply bound states from the strong, repulsive tensor force \cite{Nogga:2005hy}.
-\\
--- These bound states are features of high-momentum physics and lie outside the range of the EFT.
-\\
--- However, potentials with deeply bound states have shown sensitivity to SRG transformations \cite{Glazek:2008pg, Wendt:2011qj}.
-\\
--- Details of the SRG transformation can cause the spurious bound state(s) to corrupt the low-momentum physics.
-\\
--- An analogous problem occurs in IMSRG calculations for systems with intruder states where the intruder state can shift to the energy scale of the reference state in valence space.
-\\
--- This severely distorts low-energy properties such as the ground state wave function.
-\\
--- It is not understood how the IMSRG procedure evolves intruder state systems.
-\\
--- Due to the prominence of the Magnus in IMSRG, one must first understand if the Magnus approach matches the typical approach for difficult systems before investigating the intruder state problem.
-\\
--- NN potentials with spurious bound states offer a good test laboratory for the Magnus implementation to better understand if the Magnus is equivalent to the SRG approach. 
-\\
-
-\noindent{%
--- The past decade has seen a tremendous increase in the number of chiral NN potentials.
-}
-\\
--- Interactions can now be built up to N5LO and feature several different regularization schemes.
-\\
--- A natural question is to ask whether the SRG decouples these potentials in the same way.
-\\
--- There is evidence of universal, low-momentum matrix elements as seen from evolving different potentials with SRG transformations or $V_{low~k}$ \cite{Dainton:2013axa}.
-\\
--- There has also been renewed interest in chiral potentials at high-cutoffs but for a locally regulated potential \cite{Tews:2018sbi}.
-\\
--- Given the growing number of chiral interactions, it would be interesting to re-examine these areas from an SRG standpoint.
-\\
--- However, we would like to focus on a fixed comparison of the SRG and the Magnus approach as a first test, and therefore only consider evolving non-local LO NN potentials at various cutoffs.
-\\
--- We leave the other areas as topics for future studies.
-\\
-
-\noindent{%
--- The rest of the paper is organized as follows:
-}
-\\
--- In Sec. \ref{sec:formalism} we review the formalism of the SRG and the Magnus implementation emphasizing the major advantages of the Magnus.
-\\
--- In Sec. \ref{sec:results} we test the Magnus implementation on high-cutoff NN potentials.
-\\
--- We briefly review the SRG results for the same set of bare interactions and compare Magnus to SRG results.
-\\
--- With the Magnus evolved operators, we calculate several observables and explore operator evolution.
-\\
--- Lastly, we summarize our results in Sec. \ref{sec:conclusion}.
-\\
--- We discuss the implications for the Magnus expansion within the IMSRG.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:formalism}
-
-\noindent{%
-\textbf{SRG formalism}
-}
-\\
--- In this section we describe the SRG in the context of decoupling any operator.
-\\
--- The SRG decouples low- and high-momentum scales by applying a continuous unitary transformation $U(s)$ where $s=0 \rightarrow \infty$ is the flow parameter.
-\\
--- The `dressed' or evolved operator is given by
-%
-\begin{eqnarray}
-	\label{eq:srg_operator}
-	O(s) = U(s) O(0) U^{\dagger}(s),
-\end{eqnarray}
-%
-where $O(0)$ corresponds to the `bare' operator.
-\\
--- Because $U(s)$ is unitary, the observables of the operator are preserved.
-\\
--- In practice, the unitary transformation U(s) is not explicitly solved for; the evolved operator is given by a differential flow equation which is obtained by taking the derivative of Eqn.
-(\ref{eq:srg_operator}),
-%
-\begin{eqnarray}
-	\label{eq:srg_flow}
-	\frac{dO(s)}{ds} = [\eta(s), O(s)],
-\end{eqnarray}
-%
-where $\eta(s)=\frac{dU(s)}{ds} U^{\dagger}(s) = -\eta^{\dagger}(s)$ is the anti-hermitian SRG generator.
-\\
--- The generator is defined as a commutator,
-%
-\begin{eqnarray}
-	\label{eq:srg_generator}
-	\eta(s) = [G, H(s)],
-\end{eqnarray}
-%
-where $G$ specifies the type of flow or form of the decoupled operator.
-\\
--- To drive the operator to band-diagonal form, set $G=H_D(s)$, the diagonal of the Hamiltonian.
-\\
--- This choice was implemented by Wegner in condensed matter physics \cite{Wegner:1994ab}.
-\\
--- For notational convenience, we write the Wegner choice without the $s$ dependence in the rest of the paper.
-\\
--- In a similar option used in nuclear physics, $G$ is set to the relative kinetic energy, $T_{rel}$, which also drives to band-diagonal form.
-\\
--- In this paper, we consider both choices.
-\\
--- Generally the flow equation (\ref{eq:srg_flow}) is solved up to some finite value of $s$ with a high-order ODE solver.
-\\
--- It is convenient to define $\lambda \equiv s^{-1/4}$ which roughly measures the width of the diagonal in the decoupled operator.
-\\
-
-\noindent{%
-\textbf{Magnus expansion formalism}
-}
-\\
--- We now consider the Magnus implementation.
-\\
--- Mathematically speaking, the Magnus expansion is a method for solving an initial value problem associated with a linear ordinary differential equation (ODE).
-\\
--- Formal details of the Magnus expansion are discussed in \cite{Blanes:2009ab}.
-\\
--- We will introduce the Magnus expansion in the context of SRG evolving any operator.
-\\
--- In an intermediate step in deriving Eqn. (\ref{eq:srg_flow}), we have a linear ODE for $U(s)$,
-%
-\begin{eqnarray}
-	\label{eq:unitary_trans}
-	\frac{dU(s)}{ds} = \eta(s) U(s).
-\end{eqnarray}
-%
--- Magnus showed that one can solve the following equation with a solution $U(s)=e^{\Omega(s)}$ where $\Omega(s)$ is expanded as a power series, $\sum_{n}^{\infty} \Omega_n$ (referred to as the Magnus expansion or Magnus series).
-\\
--- The terms of the series are given by integral expressions involving $\eta(s)$ (again, see \cite{Blanes:2009ab, Magnus:1954zz} for details).
-\\
--- For our case, we focus on the formally exact derivative of $\Omega(s)$,
-%
-\begin{eqnarray}
-	\label{eq:magnus_omega}
-	\frac{d\Omega(s)}{ds} = \sum_{k=0}^{\infty} \frac{B_k}{k!} ad_{\Omega}^{k}(\eta),
-\end{eqnarray}
-%
-where $B_k$ are the Bernoulli numbers, $ad_{\Omega}^{0}(\eta)=\eta(s)$, and $ad_{\Omega}^{k}(\eta)=[\Omega(s),ad_{\Omega}^{k-1}(\eta)]$.
-\\
--- We integrate this differential equation to find $\Omega(s)$ and evaluate the unitary transformation directly.
-\\
--- Then the evolved operator can be evaluated with the BCH formula:
-%
-\begin{eqnarray}
-	\label{eq:bch}
-	O(s) = e^{\Omega(s)} O e^{-\Omega(s)} = \sum_{k=0}^{\infty} \frac{1}{k!} ad_{\Omega}^{k}(O).
-\end{eqnarray}
-%
--- As $k \rightarrow \infty$ in both sums in Eqns. (\ref{eq:magnus_omega}) and (\ref{eq:bch}) the Magnus transformation matches the SRG transformation.
-\\
--- We investigate several truncations $k_{max}$ in Eqn. (\ref{eq:magnus_omega}) and take many terms, $k_{max} \sim 25$, in Eqn. (\ref{eq:bch}).
-\\
-\textcolor{red}{%
--- Here or earlier (for the following bullets)? Better to motivate the Magnus in the introduction or easier to explain given mathematical detail?
-}
-\\
--- There are significant advantages in the Magnus implementation.
-\\
--- In the typical approach, the numerical error associated with solving the flow equation affects the accuracy of the observables for the evolved operator.
-\\
--- Therefore, one must use a high-order ODE solver in integrating the flow equation (\ref{eq:srg_flow}).
-\\
--- In the Magnus implementation, unitarity is guaranteed by the form of $U(s)$; in fact, one could solve Eqn.
-(\ref{eq:magnus_omega}) with a simple first-order Euler step-method keeping the same observables while decoupling the operator as desired.
-\\
--- This offers a decent computational speed-up by avoiding a high-order solver.
-\\
--- In this paper, we demonstrate this advantage by applying the Magnus implementation using the first-order Euler step-method.
-\\
--- The second major advantage involves the evolution of multiple operators.
-\\
--- In many other situations, one may be interested in evolving several operators at a time.
-\\
--- In the SRG procedure, we would have another set of coupled equations in Eqn. (\ref{eq:srg_flow}), drastically increasing memory usage.
-\\
--- Each additional operator increases the set of equations - say $N$ equations - by another factor of $N$.
-\\
--- In the Magnus, one only needs $\Omega(s)$ to consistently evolve several operators.
-\\
--- We avoid the cost in memory by directly constructing $U(s)=e^{\Omega(s)}$.
-\\
--- This is especially useful in IMSRG calculations where the model space can be very large.
-\\
--- In the next section, we discuss results from Magnus evolved large-cutoff potentials focusing on the flow of the potential, observables, and operator evolution.
 
@@
 
-\noindent{%
-\textbf{Evolution of potentials}
-}
-\\
--- In this section, we Magnus evolve LO non-local potentials in the $^{3}S_1-^{3}D_1$ channel at cutoffs of $\Lambda=4$, $9$, and $20 \, fm^{-1}$.
-\\
-\textcolor{red}{%
--- Option: add new regularization schemes?
-}
-\\
--- For the higher two cutoffs, the potentials have one and two spurious, deeply bound states, respectively.
-\\
--- In \cite{Wendt:2011qj}, potentials at large-cutoffs were SRG evolved with $G=H_D$ and $G=T_{rel}$.
-\\
--- At lower cutoffs ($\Lambda \lesssim 4 \, fm^{-1}$), potential matrix elements flowed toward a decoupled, universal form independent of $G$, that is the low-momentum matrix elements approached the same values as $\lambda \rightarrow 0$.
-\\
--- However, SRG evolution differed for potentials featuring one or more spurious bound states.
-\\
--- With one or more spurious bound states and $G=T_{rel}$, the SRG transformation shifted a spurious bound state toward the low-momentum block corrupting the low-energy physics (e.g., the deuteron wave function, phase shifts, etc.).
-\\
--- For $G=H_D$, the SRG decoupled the spurious bound state outside the low-momentum block matching the flow to universal low-momentum form independent of the cutoff $\Lambda$.
-\\
--- Similar behavior could be prevalent in IMSRG calculations where the choice in generator affects evolution of many-body Hamiltonians with intruder states as it does for these NN potentials in free-space SRG.
-\\
-
-\noindent{%
--- First, we compare Magnus to SRG evolution for large cutoff potentials with $G=H_D$ and $G=T_{rel}$.
-}
-\\
--- Figures \ref{fig:magnus_contours_Wendt_Lamb9_Wegner} and \ref{fig:magnus_contours_Wendt_Lamb9_T} show potential matrix element evolution for three truncations in the sum of Eqn.
-\ref{eq:magnus_omega} up to three values of $\lambda$ with $\Lambda=9 \, fm^{-1}$.
-\\
--- At this cutoff, the potential has one spurious bound state at about $-2000$ MeV.
-\\
-%	
-\begin{figure}
-	\captionsetup{singlelinecheck=false,justification=raggedright}
-	\centering
-	\includegraphics[width=10cm]{magnus_contours_Wendt_Lamb9_Wegner}
-	\hspace*{0.05\textwidth}
-	\caption{Contours of Magnus evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=H_{D}$ for $\lambda=2.8$ (left), $2.0$ (middle), and $1.2$ (right) $fm^{-1}$ and truncations in the Magnus $k_{max}=2$ (top), $6$ (middle), and $10$ (bottom).}
-	\label{fig:magnus_contours_Wendt_Lamb9_Wegner}
-\end{figure}
-%
-\begin{figure}
-	\captionsetup{singlelinecheck=false,justification=raggedright}
-	\centering
-	\includegraphics[width=10cm]{magnus_contours_Wendt_Lamb9_T}
-  	\hspace*{0.05\textwidth}
-  	\caption{Contours of Magnus evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=T_{rel}$ for $\lambda=2.8$ (left), $2.0$ (middle), and $1.2$ (right) $fm^{-1}$ and truncations in the Magnus $k_{max}=2$ (top), $6$ (middle), and $10$ (bottom).}
-  	\label{fig:magnus_contours_Wendt_Lamb9_T}
-\end{figure}
-%
--- We see the same behavior with the Magnus in comparison to the SRG in \cite{Wendt:2011qj} for both generators.
-\\
--- For $G=H_D$, there is a deep, blue dot in the middle of the contours at $k \approx 1.75 \, fm^{-1}$ which corresponds to the decoupled spurious bound state.
-\\
--- We have checked other cutoffs and found that the evolved low-momentum matrix elements are independent of the cutoff $\Lambda$ implying a low-momentum, universal form.
-\\
--- The only major difference in Magnus or SRG evolution for various cutoffs is where spurious bound state(s) are decoupled.
-\\
--- This decoupling feature depends on the details of the starting interaction (i.e., the value of the bound state).
-\\
-%
-\begin{figure}
-	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
-        \includegraphics[width=14cm]{evolved_diags_Wendt_Lamb9_Wegner}
-	\hspace*{0.05\textwidth}
-	\caption{Diagonal (top row) and far off-diagonal (bottom row) matrix elements of evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=H_{D}$ for several values of $\lambda$ and truncations in the Magnus series $k_{max}$.}
-	\label{fig:evolved_diags_Wendt_Lamb9_Wegner}
-\end{figure}
-%
-\noindent{%
--- Furthermore, it is dependent on the momentum mesh on which the potential is generated.
-}
-\\
--- At $k_{max}=2$ and $\lambda=2.0 \, fm^{-1}$, we see large, positive off-diagonal values along the momentum axes where the deep bound state is decoupled.
-\\
--- Solving for $\Omega(s)$ at a low truncation leads to less desirable flow, that is, the transformation $U(s)$ is not quite the same transformation as the SRG $U(s)$.
-\\
--- However, the Magnus still guarantees the unitarity of $U(s)$, and we see a consistent decoupling of the spurious bound state in each row independent of $k_{max}$.
-\\
--- For $G=T_{rel}$, the spurious bound state is shifted up along the diagonal, and the low-momentum block drops to extremely negative values.
-\\
--- Here, the spurious bound state corrupts the low-momentum block matching the SRG evolution of different cutoffs, thus breaking universality.
-\\
-%
-\begin{figure}
-	\captionsetup{singlelinecheck=false,justification=raggedright}
-	\centering
-	\includegraphics[width=14cm]{evolved_diags_Wendt_Lamb9_T}
-	\hspace*{0.05\textwidth}
-	\caption{Diagonal (top row) and far off-diagonal (bottom row) matrix elements of evolved $V_{\lambda}(k,k')$ with $\Lambda=9 \, fm^{-1}$ and $G=T_{rel}$ for several values of $\lambda$ and truncations in the Magnus series $k_{max}$.}
-	\label{fig:evolved_diags_Wendt_Lamb9_T}
-\end{figure}
-%
-\noindent{%
--- Figures \ref{fig:evolved_diags_Wendt_Lamb9_Wegner} and \ref{fig:evolved_diags_Wendt_Lamb9_T} show a more quantitative depiction of the evolved potentials.
-}
-\\
--- The black dotted line corresponds to the SRG evolved potential whereas the other lines are Magnus evolved potentials for different $k_{max}$ for diagonal and far-off diagonal matrix elements of $V_{\lambda}(k,k')$.
-\\
--- It is clear in these figures that the Magnus matches the SRG at $k_{max} \gtrsim 6$.
-\\
--- In Figure \ref{fig:evolved_diags_Wendt_Lamb9_Wegner} the decoupled spurious bound state is seen as the large negative drop in the curves at $k \approx 1.75 \, fm^{-1}$.
-\\
-\textcolor{red}{%
--- Unnecessary?
-\\
--- From applying the Magnus in several other cases, we have seen that harder potentials cause convergence issues in the Magnus expansion due to the relative size of the SRG generator $\eta(s)$.
-\\
--- To avoid convergence issues we can take a smaller step-size.
-\\
--- In the previous cases (and all other cases unless specified otherwise), we take $ds=10^-5$.
-}
-\\
-
-\noindent{%
-\textbf{Observables}
-}
-\\
-%
-\begin{table}
-	\captionsetup{singlelinecheck=false,justification=raggedright}
-	\caption{Relative error on the deuteron bound state energy and the root mean square of eigenvalues where $\tilde{\epsilon}$ denotes an eigenvalue of an SRG or Magnus evolved Hamiltonian for $\Lambda=9 \, fm^{-1}$ and $\lambda=1.2 \, fm^{-1}$.}
-	\label{tab:energies}
-	\begin{ruledtabular}
-		\begin{tabular}{{>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{2in}}}
-      			$  $ & $G$ & $ |\frac{\epsilon_d-\tilde{\epsilon}_d}{\epsilon_d}| $ & $\sqrt{\frac{1}{N} \, \sum_{i}^{N} (\tilde{\epsilon}_i-\epsilon_i)^2}$   [MeV] \\
-			\colrule
-      			SRG & $ $ & $\num{1.165e-5}$ & $\num{3.016e-4}$ \\
-      			Magnus, $k_{max}=2$ & $H_D$ & $\num{5.010e-10}$ & $\num{4.097e-9}$ \\
-      			Magnus, $k_{max}=14$ & $ $ & $\num{1.206e-11}$ & $\num{3.950e-10}$ \\ \hline
-      			SRG & $ $ & $\num{1.003e-4}$ & $\num{9.791e-5}$ \\
-      			Magnus, $k_{max}=2$ & $T_{rel}$ & $\num{7.775e-8}$ & $\num{6.376e-8}$ \\
-      			Magnus, $k_{max}=14$ & $ $ & $\num{7.607e-8}$ & $\num{6.359e-8}$ \\
-		\end{tabular}
-  	\end{ruledtabular}
-\end{table}
-%
--- To emphasize the two major advantages of the Magnus implementation, we now consider evolved observables and operators for the remainder of the section.
-\\
--- Table \ref{tab:energies} shows the relative error on the deuteron bound state energy and root mean square of all eigenvalues for several evolution cases.
-\\
--- The Magnus approach preserves energies to several orders of magnitude better than the typical SRG approach.
-\\
--- Again, despite the inclusion of several more terms in the sum of Eqn.
-\ref{eq:magnus_omega}, we see consistent errors between $k_{max}=2$ and $14$ because of the guaranteed unitarity of $U(s)=e^{\Omega(s)}$
-\\
--- The errors on the Magnus energies are within the region of floating-point error whereas the SRG compounds error in solving the ODE \ref{eq:srg_flow}.
-\\
--- We have also checked the phase shifts from the evolved potentials match the bare potentials in all cases for Magnus and SRG evolution.
-\\ 
--- Next we show the evolved deuteron wave function for several cases.
-\\
--- Figure \ref{fig:momentum_dist_Wendt_Lamb9} shows the deuteron momentum probability density, $|\phi(k)|^2$, on a semi-log scale as a function of momentum for both band-diagonal generators.
-\\
--- With $G=H_D$, the evolved and un-evolved momentum distributions agree for low-momentum whereas $G=T_{rel}$ significantly distorts the distribution from the presence of the spurious bound state in the $\Lambda=9 \, fm^{-1}$ potential.
-\\
--- This illustrates the advantage of the Wegner generator: the spurious bound state at high-momentum does not affect the low-momentum physics under the SRG transformation.
-\\
--- In all cases of Magnus and SRG evolution, we can consistently evolve wave functions and operators to make reliable calculations of observables.
-\\
--- To demonstrate this, we calculate the deuteron RMS radius and quadrupole moment with the $\Lambda=9 \, fm^{-1}$ potential using the Magnus implementation with the Wegner generator.
-\\
--- The initial values of the chiral potential are $r_d = 2.022 \, fm$ and $Q_d = 0.287 \, fm^2$ compared to the experimental values $r_d^{exp} = 2.141 \, fm$ and $Q_d^{exp} = 0.286 \, fm^2$. 
-\\
--- We have checked for several cases with the Magnus and found near-perfect agreement to the initial values of both observables.
-\\
-
-\noindent{%
-	\textcolor{red}{%
-	UPDATED UP TO HERE 04/03/19
-	}
-}
-\\
-\begin{figure}
-  	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
-  	\includegraphics[width=10cm]{momentum_dist_Wendt_Lamb9}
-  	\hspace*{0.05\textwidth}
-  	\caption{Momentum probability densities of the deuteron comparing the un-evolved wavefunction (black dotted line), SRG evolved wavefunction (blue dashed line), and two Magnus evolved wavefunctions with truncations $2$ and $14$ (green and red dash-dotted lines, respectively) where $\lambda=1.2 \, fm^{-1}$.
-The left panel shows evolution with $G=H_{D}$ and the right with $G=T_{rel}$.
-Here $\Lambda=9 \, fm^{-1}$.}
-  	\label{fig:momentum_dist_Wendt_Lamb9}
-\end{figure}
-%
-\noindent{%
--- RMS radius and quadrupole moment of deuteron.
-}
-\\
--- Values from initial potential ($\Lambda=9 \, fm^{-1}$):
-\begin{itemize}
-  	\item $r_d = 2.022 \, fm$ (using momentum-space derivatives)
-  	\item $r_d = 2.465 \, fm$ (using Fourier transforms)
-	\item $Q_d = 0.287 \, fm^2$ (using momentum-space derivatives)
-\end{itemize}
--- Values from standard Magnus evolved potential ($G=H_D$, $\lambda=1.2 \, fm^{-1}$, and $k_{max}=6$):
-\begin{itemize}
-  	\item $r_d = 2.022 \, fm$ (using momentum-space derivatives)
-  	\item $Q_d = 0.287 \, fm^2$ (using momentum-space derivatives)s
-  	\item Note: we apply $U^{\dagger}(s) U(s)$ to wave function to compute unitarily equivalent observables
-\end{itemize}
--- Experimental values:
-\begin{itemize}
-  	\item $r_d = 2.141 \, fm$
-  	\item $Q_d = 0.286 \, fm^2$
-\end{itemize}
-%
-\textbf{Evolution of operators}
-%
-\begin{figure}[H]
-  	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
- 	\includegraphics[width=14cm]{momentum_proj_operator_contours_q0,31_magnus_Wendt_Lamb9}
-  	\hspace*{0.05\textwidth}
-  	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ Magnus evolving in $\lambda$ right to left with $G=H_D$ (top) and $G=T_{rel}$ (bottom).
-Here $q=0.31 \, fm^{-1}$, $\Lambda=9 \, fm^{-1}$, and $k_{max}=6$.}
-  	\label{fig:momentum_proj_operator_contours_q0,31_magnus_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-	\captionsetup{singlelinecheck=false,justification=raggedright}
-	\centering
-  	\includegraphics[width=10cm]{momentum_proj_difference_q0,31_magnus_Wendt_Lamb9}
-  	\hspace*{0.05\textwidth}
-  	\caption{Difference in evolved and bare matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ Magnus evolving to $\lambda=1.2 \, fm^{-1}$ right to with $G=H_D$ (left) and $G=T_{rel}$ (right).
-Here $q=0.31 \, fm^{-1}$, $\Lambda=9 \, fm^{-1}$, and $k_{max}=6$.}
-  	\label{fig:momentum_proj_operator_difference_q0,31_magnus_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-  	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
-  	\includegraphics[width=14cm]{momentum_proj_operator_contours_q3,04_magnus_Wendt_Lamb9}
-  	\hspace*{0.05\textwidth}
-  	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ Magnus evolving in $\lambda$ right to left with $G=H_D$ (top) and $G=T_{rel}$ (bottom).
-Here $q=3.04 \, fm^{-1}$, $\Lambda=9 \, fm^{-1}$, and $k_{max}=6$.}
-  	\label{fig:momentum_proj_operator_contours_q3,04_magnus_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-  	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
-  	\includegraphics[width=10cm]{momentum_proj_difference_q3,04_magnus_Wendt_Lamb9}
-  	\hspace*{0.05\textwidth}
-  	\caption{Difference in evolved and bare matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ Magnus evolving to $\lambda=1.2 \, fm^{-1}$ with $G=H_D$ (left) and $G=T_{rel}$ (right).
-Here $q=3.04 \, fm^{-1}$, $\Lambda=9 \, fm^{-1}$, and $k_{max}=6$.}
-  	\label{fig:momentum_proj_operator_difference_q3,04_magnus_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-  	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
-  	\includegraphics[width=14cm]{r2_operator_contours_magnus_Wendt_Lamb9}
-  	\hspace*{0.05\textwidth}
-  	\caption{Matrix elements of $\mel{k}{r^2}{k'}$ Magnus evolving in $\lambda$ right to left with $G=H_D$ (top) and $G=T_{rel}$ (bottom). Here $\Lambda=9 \, fm^{-1}$ and $k_{max}=6$.}
-  	\label{fig:r2_operator_contours_srg_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-  	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
-  	\includegraphics[width=10cm]{r2_difference_magnus_Wendt_Lamb4}
-  	\hspace*{0.05\textwidth}
-  	\caption{Difference in evolved and bare matrix elements of $\mel{k}{r^2}{k'}$ Magnus evolving to $\lambda=1.2 \, fm^{-1}$ with $G=H_D$ (left) and $G=T_{rel}$ (right).
-Here $\Lambda=4 \, fm^{-1}$ and $k_{max}=6$.}
-  	\label{fig:r2_difference_magnus_Wendt_Lamb4}
-\end{figure}
-%
-\begin{figure}[H]
-  	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
-  	\includegraphics[width=10cm]{r2_difference_magnus_Wendt_Lamb9}
-  	\hspace*{0.05\textwidth}
-  	\caption{Difference in evolved and bare matrix elements of $\mel{k}{r^2}{k'}$ Magnus evolving to $\lambda=1.2 \, fm^{-1}$ with $G=H_D$ (left) and $G=T_{rel}$ (right).
-Here $\Lambda=9 \, fm^{-1}$ and $k_{max}=6$.
-(Note the difference in color bar scales.)}
-  	\label{fig:r2_difference_magnus_Wendt_Lamb9}
-\end{figure}
-%
-\begin{figure}[H]
-  	\captionsetup{singlelinecheck=false,justification=raggedright}
-  	\centering
-  	\includegraphics[width=14cm]{r2_integrand_contours_magnus_Wendt_Lamb9}
-  	\hspace*{0.05\textwidth}
-  	\caption{Integrand of $\bra{\Psi}\ket{k} \mel{k}{r^2}{k'} \bra{k'}\ket{\Psi}$ Magnus evolving the wave function in $\lambda$ right to left with $G=H_D$ (top) and $G=T_{rel}$ (bottom).
-Here $\Lambda=9 \, fm^{-1}$, $k_{max}=6$, and the operator $r^2$ is un-evolved.}
-  	\label{fig:r2_integrand_contours_srg_Wendt_Lamb9}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:conclusion}
-
-\noindent{%
--- Summarize.
-}
-\\
--- Where does the Magnus implementation differ from the SRG result?
-\\
--- Connection to the IMSRG intruder state problem.
-\\
--- Outlook.
 

### 2019-08-27 Notes/Operator_evolution/operator_evolution.tex
Updated operator evolution notes
Added bits and pieces of magnus.tex and srg_operator_evolution.tex to this file. Outlining the structure of the paper.

@@
 \graphicspath{{../../Figures/Operator_evolution/}} % Setting the graphics path
+\graphicspath{{../../Figures/SRG_operator_evolution/}}
 \usepackage{physics} % For bra-ket notation
@@
 \\
--- Testing the Magnus expansion for high cutoff potentials using the potentials from Wendt 2011 for comparison. Spurious bound states and connection to intruder states in IMSRG calculations.
-\\
--- SRG/Magnus evolution in different potentials (non-local, local, semi-local). Universality. High cutoffs?
+-- SRG/Magnus evolution in different potentials (non-local, local, semi-local). Universality. High cutoffs.
 \\
@@
 \\
--- SRG operator evolution for different potentials and generators.
+-- Testing the Magnus expansion for high cutoff potentials using the potentials from Wendt 2011 for comparison. Spurious bound states and connection to intruder states in IMSRG calculations.
+\\
+-- Operator evolution for different potentials and generators.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Formalism}
-\label{sec:formalism}
+\noindent{%
+\textbf{Background on modern nuclear potentials.}
+}
+\\
+-- Variety of potentials.
+\\
+-- Implementation to many-body calculations and SRG decoupling.
+\\
+-- Regulators, order, cutoff, etc. Universality.
+\\
+\textbf{SRG formalism}
+\\
+-- The SRG decouples low- and high-momentum scales by applying a continuous unitary transformation $U(s)$ where $s=0 \rightarrow \infty$ is the flow parameter.
+\\
+-- The `dressed' or evolved operator is given by
+%
+\begin{eqnarray}
+	\label{eq:srg_operator}
+	O(s) = U(s) O(0) U^{\dagger}(s),
+\end{eqnarray}
+%
+where $O(0)$ corresponds to the `bare' operator.
+\\
+-- Because $U(s)$ is unitary, the observables of the operator are preserved.
+\\
+-- In practice, the unitary transformation U(s) is not explicitly solved for; the evolved operator is given by a differential flow equation which is obtained by taking the derivative of Eqn.
+(\ref{eq:srg_operator}),
+%
+\begin{eqnarray}
+	\label{eq:srg_flow}
+	\frac{dO(s)}{ds} = [\eta(s), O(s)],
+\end{eqnarray}
+%
+where $\eta(s)=\frac{dU(s)}{ds} U^{\dagger}(s) = -\eta^{\dagger}(s)$ is the anti-hermitian SRG generator.
+\\
+-- The generator is defined as a commutator,
+%
+\begin{eqnarray}
+	\label{eq:srg_generator}
+	\eta(s) = [G, H(s)],
+\end{eqnarray}
+%
+where $G$ specifies the type of flow or form of the decoupled operator.
+\\
+-- To drive the operator to band-diagonal form, set $G=H_D(s)$, the diagonal of the Hamiltonian.
+\\
+-- This choice was implemented by Wegner in condensed matter physics \cite{Wegner:1994ab}.
+\\
+-- For notational convenience, we write the Wegner choice without the $s$ dependence in the rest of the paper.
+\\
+-- In a similar option used in nuclear physics, $G$ is set to the relative kinetic energy, $T_{rel}$, which also drives to band-diagonal form.
+\\
+-- In this paper, we consider both choices.
+\\
+\textcolor{red}{%
+-- Add block-diagonal generator.
+}
+\\
+-- Generally the flow equation (\ref{eq:srg_flow}) is solved up to some finite value of $s$ with a high-order ODE solver.
+\\
+-- It is convenient to define $\lambda \equiv s^{-1/4}$ which roughly measures the width of the band-diagonal in the decoupled operator.
+\\
+\textbf{Operator evolution}
+\\
+-- State how a potential changes: how does this affect other operators?
+\\
+-- How operators evolve from band- and block-diagonal SRG transformations.
+\\
+-- Operator evolution for different potentials (regulators, chiral order, etc.)
+\\
+\textcolor{red}{%
+-- Mention the Magnus expansion?
+}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\label{sec:results}
+\section{SRG evolution of NN potentials}
+\label{sec:srg_evolution_nn_potentials}
+
+\noindent{%
+-- Example figure. EM N$^3$LO potential.
+}
+%
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Block-diag2,00}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Block-diag3,00}%
+	}
+	\caption{Matrix elements of the Entem-Machleidt N$^3$LO non-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).}
+	\label{potential_contours_kvnn10_3S1}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{The Magnus expansion}
+\label{sec:magnus_expansion}
+
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+\subsection{Formalism}
+\label{sec:magnus_expansion_formalism}
+
+\noindent{%
+-- We now consider the Magnus implementation.
+}
+\\
+-- Mathematically speaking, the Magnus expansion is a method for solving an initial value problem associated with a linear ordinary differential equation (ODE).
+\\
+-- Formal details of the Magnus expansion are discussed in \cite{Blanes:2009ab}.
+\\
+-- We will introduce the Magnus expansion in the context of SRG evolving any operator.
+\\
+-- In an intermediate step in deriving Eqn. (\ref{eq:srg_flow}), we have a linear ODE for $U(s)$,
+%
+\begin{eqnarray}
+	\label{eq:unitary_trans}
+	\frac{dU(s)}{ds} = \eta(s) U(s).
+\end{eqnarray}
+%
+-- Magnus showed that one can solve the following equation with a solution $U(s)=e^{\Omega(s)}$ where $\Omega(s)$ is expanded as a power series, $\sum_{n}^{\infty} \Omega_n$ (referred to as the Magnus expansion or Magnus series).
+\\
+-- The terms of the series are given by integral expressions involving $\eta(s)$ (again, see \cite{Blanes:2009ab, Magnus:1954zz} for details).
+\\
+-- For our case, we focus on the formally exact derivative of $\Omega(s)$,
+%
+\begin{eqnarray}
+	\label{eq:magnus_omega}
+	\frac{d\Omega(s)}{ds} = \sum_{k=0}^{\infty} \frac{B_k}{k!} ad_{\Omega}^{k}(\eta),
+\end{eqnarray}
+%
+where $B_k$ are the Bernoulli numbers, $ad_{\Omega}^{0}(\eta)=\eta(s)$, and $ad_{\Omega}^{k}(\eta)=[\Omega(s),ad_{\Omega}^{k-1}(\eta)]$.
+\\
+-- We integrate this differential equation to find $\Omega(s)$ and evaluate the unitary transformation directly.
+\\
+-- Then the evolved operator can be evaluated with the BCH formula:
+%
+\begin{eqnarray}
+	\label{eq:bch}
+	O(s) = e^{\Omega(s)} O e^{-\Omega(s)} = \sum_{k=0}^{\infty} \frac{1}{k!} ad_{\Omega}^{k}(O).
+\end{eqnarray}
+%
+-- As $k \rightarrow \infty$ in both sums in Eqns. (\ref{eq:magnus_omega}) and (\ref{eq:bch}) the Magnus transformation matches the SRG transformation exactly.
+\\
+-- We investigate several truncations $k_{max}$ in Eqn. (\ref{eq:magnus_omega}) and take many terms, $k_{max} \sim 25$, in Eqn. (\ref{eq:bch}).
+\\
+\textcolor{red}{%
+-- Here or earlier (for the following bullets)? Better to motivate the Magnus in the introduction or easier to explain given mathematical detail?
+}
+\\
+-- There are significant advantages in the Magnus implementation.
+\\
+-- In the typical approach, the numerical error associated with solving the flow equation affects the accuracy of the observables for the evolved operator.
+\\
+-- Therefore, one must use a high-order ODE solver in integrating the flow equation (\ref{eq:srg_flow}).
+\\
+-- In the Magnus implementation, unitarity is guaranteed by the form of $U(s)$; in fact, one could solve Eqn.
+(\ref{eq:magnus_omega}) with a simple first-order Euler step-method keeping the same observables while decoupling the operator as desired.
+\\
+-- This offers a decent computational speed-up by avoiding a high-order solver.
+\\
+-- In this paper, we demonstrate this advantage by applying the Magnus implementation using the first-order Euler step-method.
+\\
+-- The second major advantage involves the evolution of multiple operators.
+\\
+-- In many other situations, one may be interested in evolving several operators at a time.
+\\
+-- In the SRG procedure, we would have another set of coupled equations in Eqn. (\ref{eq:srg_flow}), drastically increasing memory usage.
+\\
+-- Each additional operator increases the set of equations - say $N$ equations - by another factor of $N$.
+\\
+-- In the Magnus, one only needs $\Omega(s)$ to consistently evolve several operators.
+\\
+-- We avoid the cost in memory by directly constructing $U(s)=e^{\Omega(s)}$.
+\\
+-- This is especially useful in IMSRG calculations where the model space can be very large.
+\\
+-- In the next section, we discuss results from Magnus-evolved large-cutoff potentials focusing on the flow of the potential, observables, and operator evolution.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Evolution of other operators}
+\label{sec:evolution_other_operators}
+
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+\subsection{Building SRG unitary transformations}
+\label{sec:srg_unitary_transformations}
+
+Diagonalize initial and evolved Hamiltonians which we will call $H(0)$ and $H(s)$, respectively.
+This gives $\psi_{\alpha}(0)$ and $\psi_{\alpha}(s)$ for each eigenvalue indexed by $\alpha$.
+Then the SRG unitary transformation can be computed by taking a sum over outer products of the evolved and initial wave functions:
+%
+\begin{eqnarray}
+	\label{eq:unitary_transformation}
+	U(s) = \sum_{\alpha=1}^{N} \ket{\psi_{\alpha}(s)} \bra{\psi_{\alpha}(0)},
+\end{eqnarray}
+%
+where N is the dimension of the Hamiltonian matrix. Here the weights are factored into the wave functions, thus $U(s)$ is unitless.
+\\
+
+To evolve operators, we simply apply $U(s)$:
+%
+\begin{eqnarray}
+	\label{eq:evolved_operator}
+	O(s) = U(s) O(0) U^{\dagger}(s),
+\end{eqnarray}
+%
+where $O(0)$ is the bare operator.
+
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+\subsection{Momentum projection operator: $a^{\dagger}_q a_q (k, k')$}
+\label{sec:momentum_proj_operator}
+
+Applying $a^{\dagger}_q a_q (k, k')$ to a wave function $\psi(k)$ returns $\psi(q)$.
+For the discrete case, $\psi(k_i)$ is an $N \times 1$ vector and $a^{\dagger}_q a_q (k_i, k_j)$ is an $N \times N$ matrix where $i$, $j=1\cdots N$.
+Then $a^{\dagger}_q a_q (k, k')$ acting on $\psi(k)$ is a matrix multiplication, implying a continuous integration over $d^3k / (2 \pi)^3 = 2 / (\pi k^2 dk)$ in spherical coordinates.
+Therefore, we include a factor of $\pi / (2 k_i k_j \sqrt{w_i w_j})$ in $a^{\dagger}_q a_q (k_i, k_j)$ where $w$ represents the momentum weights.
+In matrix form,
+%
+\begin{eqnarray}
+	\label{eq:momentum_projection_operator}
+	a^{\dagger}_q a_q (k_i, k_j) = \frac{\pi \delta_{k_i q} \delta_{k_j q}}{2 k_i k_j \sqrt{w_i w_j}},
+\end{eqnarray}
+%
+which has units fm$^3$.
+To evolve operators, we apply $U(s)$ at this point.
+For mesh-independent figures, we must divide by an additional factor of $k_i k_j \sqrt{w_i w_j}$.
+This operator is inherently mesh-dependent based off discretizing $\delta_{k_i q} \delta_{k_j q}$ above.
+
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+\subsection{Momentum distribution function: $\phi^2(k)$}
+\label{sec:momentum_dist_funcs}
+
+We diagonalize the Hamiltonian for eigenvectors $\psi_{\alpha}$.
+In the $^{3}S_1$-$^{3}D_1$ coupled channel, the S-component is given by $\psi_{\alpha}[: \!
+N]$ and the D-component by $\psi_{\alpha}[N \!
+:]$ where $N$ is the length of the momentum mesh.
+Then the momentum distribution of the state $\alpha$ is given by,
+%
+\begin{eqnarray}
+	\label{eq:momentum_distribution}
+	|\phi_{\alpha}(k)|^2 = |\psi_{\alpha}[: \! N]|^2 + |\psi_{\alpha}[N \! :]|^2.
+\end{eqnarray}
+%
+This satisfies the normalization condition $\sum_{i=1}^N |\phi(k_i)|^2 = 1$, implying that the factor $k^2 dk$ (or in the discrete case, $k_i^2 w_i$) is factored into the wave function.
+For mesh-independent figures, divide by $k_i^2 w_i$.
 
@@
 \label{sec:conclusion}
+
+\noindent{%
+-- Summary.
+}
+\\
+-- Outlook.
 

### 2019-08-28 Notes/Operator_evolution/operator_evolution.tex
Update to operator evolution paper
Added bullets for organization purposes.

@@
 \\
--- Variety of potentials.
+-- Wide range of NN potentials: how do they change under SRG transformations?
 \\
@@
 \\
--- Regulators, order, cutoff, etc. Universality.
+-- Motivate long list of unaddressed questions: regulator, generator dependence, universality, high cutoffs, the Magnus expansion.
 \\
@@
 \\
--- State how a potential changes: how does this affect other operators?
+-- State how a potential and wave function changes: how does this affect other operators?
 \\
@@
 -- Operator evolution for different potentials (regulators, chiral order, etc.)
-\\
-\textcolor{red}{%
--- Mention the Magnus expansion?
-}
 
@@
 \noindent{%
+-- Comparison of potential evolution with different regulators, orders, generators.
+}
+\\
+-- Universality.
+\\
+-- Discussion of high cutoffs, block-diagonal generator at high cutoffs, and how it handles spurious bound states.
+\\
+-- Use high cutoffs to transition to Magnus test problem.
+\\
 -- Example figure. EM N$^3$LO potential.
-}
 %
@@
 
+\noindent{%
+-- Summary of Wendt high cutoff results and connection to IMSRG intruder state.
+}
+
 % - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
@@
 \noindent{%
+-- Motivation: simplifies computational problem for evolving multiple operators, exact unitarity.
+}
+\\
 -- We now consider the Magnus implementation.
-}
 \\
@@
 
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+\subsection{Results}
+\label{sec:magnus_expansion_results}
+
+\noindent{%
+-- Comparison to Wendt problem.
+}
+\\
+-- Implications for IMSRG.
+\\
+-- Use discussion of operator evolution to transition to next section.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:evolution_other_operators}
+
+\noindent{%
+-- SRG operator evolution for different potentials and generators.
+}
 

### 2019-08-28 Notes/Operator_evolution/operator_evolution.tex
Update operator_evolution.tex
Updated revision history and graphicspath.
No changes

@@
 % Revision history:
-%	...
+%	08/28/19 --- Started outlining and added pieces from old notes.
 %
@@
 \usepackage{graphicx}
-\graphicspath{{../../Figures/Operator_evolution/}} % Setting the graphics path
-\graphicspath{{../../Figures/SRG_operator_evolution/}}
+\graphicspath{{../../Figures/}} % Setting the graphics path
 \usepackage{physics} % For bra-ket notation
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Wegner}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/potential_contours_kvnn10_3S1_Wegner}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Block-diag2,00}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/potential_contours_kvnn10_3S1_Block-diag2,00}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Block-diag3,00}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/potential_contours_kvnn10_3S1_Block-diag3,00}%
 	}

### 2019-08-28 phase_shifts.py
Update phase_shifts.py
Started skeleton of functions that will be added to observables.py.

@@ -240,3 +240,44 @@ class Phase_shifts(object):
                     deltas[i] -= 180.0
 
         return deltas  
+    
+    
+# -----------------------------------------------------------------------------
+# Try to do everything above in one function that takes V(k, k'), e_array, and
+# convention as arguments
+        
+    
+def phase_shifts(e_array, V_matrix, k_array, k_weights, convention='Stapp'):
+    """
+    Description.
+    
+    Parameters
+    ----------
+    
+    
+    Returns
+    -------
+    
+    
+    Notes
+    -----
+    
+    """
+    
+    return None
+
+
+def phase_corrector(phase_array):
+    """
+    Description.
+    
+    Parameters
+    ----------
+    
+    
+    Returns
+    -------
+    
+    """
+    
+    return None

### 2019-09-09 Figures/figures_functions.py
Updated figures_functions.py
Add channel label function.

@@ -16,6 +16,9 @@
 #                styles function that works in the same way as xkcd_colors.
 #   09/05/19 --- Added generator_label_conversion function. Analogous to
 #                kvnn_label_conversion function.
+#   09/09/19 --- Added channel_label_conversion function. Analogous to
+#                kvnn_label_conversion and generator_label_conversion
+#                functions.
 #
 #------------------------------------------------------------------------------
 
@@ -23,6 +26,28 @@
 import numpy as np
 from scipy.interpolate import interp2d
 
+
+def channel_label_conversion(channel):
+    """
+    Converts a channel string argument to a label for plotting purposes.
+    
+    Parameters
+    ----------
+    channel : str
+        The partial wave channel ('1S0', '3S1', etc.)
+        
+    Returns
+    -------
+    label : str
+        Label for the channel.
+        
+    """
+    
+    # Make numbers super- and sub-scripts
+    label = r'$^%s$' % channel[0] + channel[1] + r'$_%s$' % channel[2]
+    
+    return label
+        
 
 def generator_label_conversion(generator, lambda_bd=0.00):
     """

### 2019-09-09 Notes/Operator_evolution/operator_evolution.tex
Updated operator_evolution notes
Added bullets to introduction and further organized things.

@@
 %	08/28/19 --- Started outlining and added pieces from old notes.
+%	09/09/19 --- Added more bullets to the introduction. Further organization.
 %
@@
 \\
--- Wide range of NN potentials: how do they change under SRG transformations?
-\\
+-- Wide range of NN potentials.
+%
+\begin{itemize}
+	\item Chiral EFT background.
+	\item Different potential matrix elements but give same $S$-matrix.
+\end{itemize}
+%
 -- Implementation to many-body calculations and SRG decoupling.
-\\
--- Motivate long list of unaddressed questions: regulator, generator dependence, universality, high cutoffs, the Magnus expansion.
-\\
+%
+\begin{itemize}
+	\item Strong coupling between low- and high-momentum matrix elements in realistic potentials.
+	\item Very difficult to implement these interactions in many-body methods using basis expansions. Matrix dimension becomes too large for accurate calculations.
+	\item RG transformations are used to soften the interaction to make many-body methods feasible. One such method, the SRG, also preserves observables from unitarity.
+	\item How do different interactions change under SRG transformations?
+\end{itemize}
+%
 \textbf{SRG formalism}
@@
 \\
--- The generator is defined as a commutator,
-%
-\begin{eqnarray}
-	\label{eq:srg_generator}
-	\eta(s) = [G, H(s)],
-\end{eqnarray}
-%
-where $G$ specifies the type of flow or form of the decoupled operator.
+-- The generator is defined as a commutator, $\eta(s) = [G, H(s)]$, where $G$ specifies the type of flow or form of the decoupled operator.
 \\
@@
 \\
--- For notational convenience, we write the Wegner choice without the $s$ dependence in the rest of the paper.
-\\
 -- In a similar option used in nuclear physics, $G$ is set to the relative kinetic energy, $T_{rel}$, which also drives to band-diagonal form.
 \\
--- In this paper, we consider both choices.
+-- It is convenient to define $\lambda \equiv s^{-1/4}$ which roughly measures the width of the band-diagonal in the decoupled operator.
 \\
-\textcolor{red}{%
--- Add block-diagonal generator.
-}
+-- For block-diagonal decoupling, denoted $G=H_{BD}(s)$, the operator is split into low- and high-momentum sub-blocks by specifying a separation in momentum $\Lambda_{BD}$.
+\\
+-- These transformations are similar to $V_{low k}$ Lee-Suzuki transformations but keep the high-momentum matrix elements non-zero, although entirely decoupled from the low-momentum sub-block.
 \\
@@
 \\
--- It is convenient to define $\lambda \equiv s^{-1/4}$ which roughly measures the width of the band-diagonal in the decoupled operator.
+-- For notational convenience, we write the generators without the $s$ dependence in the rest of the paper.
 \\
+\textbf{Universality}
+\\
+-- The explicit long-range physics should be the same.
+Decoupling low- and high-energy gives matching low-energy matrix elements.
+In the NN potential, this means softened NN interactions should have the same low-momentum matrix elements after sufficient decoupling.
+\\
+-- Add takeaways from Dainton: phase shift equivalence implies matrix element equivalence for $\lambda$ approaching the momenta of phase equivalence.
+Correct binding energy is critical or the lowest matrix elements will not match.
+\\
+-- Motivate long list of unaddressed questions: regulator, generator dependence, high cutoffs, the Magnus expansion.
+%
+\begin{itemize}
+	\item Regulator. Functional dependence of regulator. Reasons for implementing each.
+	\item Generators. Band- and block-diagonal transformations.
+	\item High cutoffs. Cite Nogga, Wendt, and Tews papers.
+	\item The Magnus expansion. High cutoffs and connection to IMSRG intruder state problem.
+\end{itemize}
+%
 \textbf{Operator evolution}
@@
 \\
+-- Operator evolution for different potentials (regulators, chiral order, etc.)
+\\
 -- How operators evolve from band- and block-diagonal SRG transformations.
 \\
--- Operator evolution for different potentials (regulators, chiral order, etc.)
+\textbf{Overview of sections.}
 
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/potential_contours_kvnn10_3S1_Wegner}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Wegner}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/potential_contours_kvnn10_3S1_Block-diag2,00}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Block-diag2,00}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/potential_contours_kvnn10_3S1_Block-diag3,00}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Block-diag3,00}%
 	}

### 2019-09-09 run_srg.py
Update run_srg.py
Generated several SRG-evolved potentials: Gezerlis et al N2LO (1 fm) and EM N3LO (500 MeV) for various partial wave channels and SRG generators.

@@ -149,8 +149,8 @@ if __name__ == '__main__':
     #kvnn = 901 # Wendt at Lambda = 9 fm^-1
     #kvnn = 902 # Wendt at Lambda = 20 fm^-1
     
-    channel = '1S0'
-    #channel = '3S1'
+    #channel = '1S0'
+    channel = '3S1'
     #channel = '1P1'
     #channel = '3P0'
     
@@ -171,9 +171,9 @@ if __name__ == '__main__':
     
     # Specify evolution
     
-    generator = 'Wegner'
+    #generator = 'Wegner'
     #generator = 'T'
-    #generator = 'Block-diag'
+    generator = 'Block-diag'
     
     lambda_bd = 1.00 # This won't affect the band-diagonal generators
     #lambda_bd = 2.00 # Default

### 2019-09-09 run_srg.py
Generated SRG-evolved potentials for various cases
All done with block-diagonal generator (1 fm^-1). EM N3LO, RKE N3LO, Gezerlis et al N2LO. 1S0 and 1P1 channels.

@@ -150,8 +150,8 @@ if __name__ == '__main__':
     #kvnn = 902 # Wendt at Lambda = 20 fm^-1
     
     #channel = '1S0'
-    channel = '3S1'
-    #channel = '1P1'
+    #channel = '3S1'
+    channel = '1P1'
     #channel = '3P0'
     
     kmax = 30.0

### 2019-09-10 run_srg.py
Generated block-diagonal SRG-evolved potentials for various cases
EM N3LO (500 MeV), RKE N3LO and N4LO (400-500 MeV), Gezerlis N2LO (1-1.2 fm) for Lambda_BD = 6, 1.5 fm^-1 and lambda = 6 to 1.5 fm^-1.

@@ -150,8 +150,8 @@ if __name__ == '__main__':
     #kvnn = 902 # Wendt at Lambda = 20 fm^-1
     
     #channel = '1S0'
-    #channel = '3S1'
-    channel = '1P1'
+    channel = '3S1'
+    #channel = '1P1'
     #channel = '3P0'
     
     kmax = 30.0
@@ -175,14 +175,16 @@ if __name__ == '__main__':
     #generator = 'T'
     generator = 'Block-diag'
     
-    lambda_bd = 1.00 # This won't affect the band-diagonal generators
+    #lambda_bd = 1.00 # This won't affect the band-diagonal generators
+    lambda_bd = 1.50
     #lambda_bd = 2.00 # Default
     #lambda_bd = 3.00
     #lambda_bd = 4.00
+    #lambda_bd = 6.00
     
     #lambda_array = np.array( [10.0, 2.8, 2.0, 1.2] )
-    #lambda_array = np.array( [6.0, 3.0, 2.0, 1.5] ) # Default
-    lambda_array = np.array( [6.0, 3.0, 2.0, 1.5, 1.0] )
+    lambda_array = np.array( [6.0, 3.0, 2.0, 1.5] ) # Default
+    #lambda_array = np.array( [6.0, 3.0, 2.0, 1.5, 1.0] )
     #lambda_array = np.array( [2.8] )
     #lambda_array = np.array( [1.2] )
     #lambda_array = np.array( [10.0] )

### 2019-09-10 Notes/Operator_evolution/operator_evolution.tex
Started adding some figures to operator evolution notes
Added SRG-evolved potentials figures.

@@
 -- Use high cutoffs to transition to Magnus test problem.
-\\
--- Example figure. EM N$^3$LO potential.
 %
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Wegner}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Wegner_potential}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Block-diag2,00}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_3S1_Wegner_potential}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Block-diag3,00}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn222_3S1_Wegner_potential}%
 	}
-	\caption{Matrix elements of the Entem-Machleidt N$^3$LO non-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).}
-	\label{potential_contours_kvnn10_3S1}
+	\caption{NEED TO UPDATE THIS CAPTION: Matrix elements of the Entem-Machleidt N$^3$LO non-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).}
+	\label{potential_contours_3S1_EM_RKE_Gezerlis_Wegner}
+\end{figure}
+%
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Wegner_generator}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Block-diag_generator}%
+	}
+	\caption{NEED TO UPDATE THIS CAPTION: Matrix elements of the Entem-Machleidt N$^3$LO non-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b).}
+	\label{potential_contours_3S1_EM_Wegner_Block-diag}
 \end{figure}

### 2019-09-11 test.py
Generated several SRG-evolved potentials with the block-diagonal generator
EM N3LO, RKE N3LO, Gezerlis et al N2LO.

@@ -20,25 +20,41 @@
 #                useful for plotting codes. Created
 #                momentum_projection_operator_testv1.py in Old_codes based off
 #                last tests in this script.
+#   09/10/19 --- Using this script to run SRG evolution on several potentials.
 #
 #------------------------------------------------------------------------------
 
 
-def func(channel, *args):
+import numpy as np
+from run_srg import run_srg
 
-    print(channel)
-    for arg in args:
-        print('kvnn = %d'%arg[0])
-        print('kmax = %.1f'%arg[1])
-        print('kmid = %.1f'%arg[2])
-        print('generator = %s'%arg[3])
-        if arg[3] == 'Block-diag':
-            print('Lambda_bd = %.2f'%arg[4])
 
-channel = '3S1'
+kvnn_list = [10, 106, 222]
+channel_list = ['1S0', '1P1']
+ntot = 120
 
-em_n3lo_wegner = (10, 30.0, 4.0, 'Wegner')
-rke_n3lo_wegner = (106, 8.0, 2.0, 'Wegner')
-gez_n2lo_wegner = (222, 10.0, 2.0, 'Block-diag', 2.00)
+generator = 'Block-diag'
+lambda_array = np.array( [6.0, 3.0, 2.0, 1.5, 1.0] )
+# Save the evolved Hamiltonian?
+save = True
 
-func(channel, em_n3lo_wegner, rke_n3lo_wegner, gez_n2lo_wegner)
+
+for kvnn in kvnn_list:
+    
+    if kvnn == 10:
+        kmax = 30.0
+        kmid = 4.0
+    elif kvnn == 106:
+        kmax = 8.0
+        kmid = 2.0
+    else:
+        kmax = 10.0
+        kmid = 2.0
+    
+    for channel in channel_list:
+        
+        for lamb in lambda_array:
+            
+            # Evolve Hamiltonian
+            d = run_srg(kvnn, channel, kmax, kmid, ntot, generator,
+                        lambda_array, lamb, save)

### 2019-09-13 Notes/Operator_evolution/operator_evolution.tex
Updated operator evolution notes
Added several figures to the draft: phase shifts, SRG-evolved potentials: contours and slices.

--- 2019-09-09 Notes/Operator_evolution/operator_evolution.tex
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Wegner}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_1S0_Wegner_channel_label}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Block-diag2,00}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_3S1_Wegner_channel_label}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Block-diag3,00}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_1P1_Wegner_channel_label}%
 	}
-	\caption{Matrix elements of the Entem-Machleidt N$^3$LO non-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).}
-	\label{potential_contours_kvnn10_3S1}
+	\caption{Matrix elements of the RKE N$^3$LO potential SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator in the $^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) channels.}
+	\label{potential_contours_RKE_Wegner}
 \end{figure}
+%
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Wegner_potential_label}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_3S1_Wegner_potential_label}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn222_3S1_Wegner_potential_label}%
+	}
+	\caption{Matrix elements of the EM N$^3$LO (a), RKE N$^3$LO (b), and Gezerlis et al.
+N$^2$LO (c) potentials SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator in the $^3$S$_1$ channel.}
+	\label{potential_contours_3S1_Wegner}
+\end{figure}
+%
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_3S1_Wegner_generator_label}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_3S1_Block-diag_generator_label}%
+	}
+	\caption{Matrix elements of the RKE N$^3$LO potential SRG-evolving right to left under transformations with Wegner (a) and block-diagonal (b) generators in the $^3$S$_1$ channel.
+Here, we use $\lambda$ for Wegner evolution in the top row and $\Lambda$ for block-diagonal evolution in the bottom row.
+For block-diagonal evolution, we fix $\lambda=1.5$ fm$^{-1}$.}
+	\label{potential_contours_3S1_RKE}
+\end{figure}
+%
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_1S0_kvnns_10_106_222}%
+	}
+	\quad
+	\subfloat[]{%
+	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_3S1_kvnns_10_106_222}%
+	}
+	\quad
+	\subfloat[]{%
+	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_1P1_kvnns_10_106_222}%
+	}
+	\caption{$^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) phase shifts for the EM N$^3$LO (solid black), RKE N$^3$LO (red dash-dotted), and Gezerlis et al. N$^2$LO (blue dashed) potentials.}
+	\label{phase_shifts}
+\end{figure}
+%
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_1S0_kvnns_10_106_222_lamb1,0}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_1S0_kvnns_10_106_222_lamb1,0}%
+	}
+	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the EM N$^3$LO (black), RKE N$^3$LO (red) and Gezerlis et al.
+N$^2$LO (blue) potentials SRG-evolving right to left under transformations with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^1$S$_0$ channel.
+Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution.
+For block-diagonal evolution, we fix $\lambda=1.0$ fm$^{-1}$.}
+	\label{potential_slices_1S0}
+\end{figure}
+%
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_3S1_kvnns_10_106_222_lamb1,0}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_3S1_kvnns_10_106_222_lamb1,0}%
+	}
+	\caption{Same as Fig.~\ref{fig:potential_slices_1S0} but in the $^3$S$_1$ channel.}
+	\label{potential_slices_3S1}
+\end{figure}
+%
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_1P1_kvnns_10_106_222_lamb1,0}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_1P1_kvnns_10_106_222_lamb1,0}%
+	}
+	\caption{Same as Figs.~\ref{fig:potential_slices_1S0} and \ref{fig:potential_slices_3S1} but in the $^1$P$_1$ channel.}
+	\label{potential_slices_1P1}
+\end{figure}
+%
+% Ideas for high cutoffs:
+%	- Last thing to look at in potentials: cutoff dependence.
+%	- Recap Wendt (2011).
+%	- Test block-diagonal evolution for the 3 cutoffs.
+%	- Lead into Magnus expansion.
 
@@
 \noindent{%
--- Summary of Wendt high cutoff results and connection to IMSRG intruder state.
+-- Connection to IMSRG intruder state.
 }
@@
 We diagonalize the Hamiltonian for eigenvectors $\psi_{\alpha}$.
-In the $^{3}S_1$-$^{3}D_1$ coupled channel, the S-component is given by $\psi_{\alpha}[: \!
+In the $^3$S$_1$-$^3$D$_1$ coupled channel, the S-component is given by $\psi_{\alpha}[: \!
 N]$ and the D-component by $\psi_{\alpha}[N \!

### 2019-09-16 test.py
Generated block-diagonal SRG-evolved potentials
kvnn = 900, channel = 3S1, up to Lambda_BD = 1.2 fm^-1 and lambda = 1.2 fm^-1.

@@ -29,9 +29,9 @@ import numpy as np
 from run_srg import run_srg
 
 
-#kvnn = 900
+kvnn = 900
 #kvnn = 901
-kvnn = 902
+#kvnn = 902
 # Could add the RKE 1-20 fm^-1 LO potentials as 903, 904, ...
 channel = '3S1'
 kmax = 30.0

### 2019-09-16 Notes/Operator_evolution/operator_evolution.tex
Updated operator evolution notes
Added minor corrections to introduction.

@@
 %
+% Add what you have from IMSRG paper.
 \begin{itemize}
 	\item Chiral EFT background.
-	\item Different potential matrix elements but give same $S$-matrix.
+	\item Different potentials but give same $S$-matrix.
 \end{itemize}
@@
 \begin{itemize}
-	\item Strong coupling between low- and high-momentum matrix elements in realistic potentials.
+	\item Strong coupling between low- and high-momentum matrix elements in NN potentials.
 	\item Very difficult to implement these interactions in many-body methods using basis expansions. Matrix dimension becomes too large for accurate calculations.
 	\item RG transformations are used to soften the interaction to make many-body methods feasible. One such method, the SRG, also preserves observables from unitarity.
-	\item How do different interactions change under SRG transformations?
+	\item How do different potentials change under SRG transformations?
 \end{itemize}
@@
 \\
--- To drive the operator to band-diagonal form, set $G=H_D(s)$, the diagonal of the Hamiltonian.
+-- By setting $G=H_D(s)$, the diagonal of the Hamiltonian, the operator is driven to band-diagonal form.
 \\
@@
 -- In a similar option used in nuclear physics, $G$ is set to the relative kinetic energy, $T_{rel}$, which also drives to band-diagonal form.
+% Do I need to explain the intermediate step here?
 \\
@@
 \\
+% Try to understand this better. Ask DF.
 -- The explicit long-range physics should be the same.
@@
 	\caption{Matrix elements of the RKE N$^3$LO potential SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator in the $^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) channels.}
-	\label{potential_contours_RKE_Wegner}
+	\label{fig:potential_contours_RKE_Wegner}
 \end{figure}
@@
 N$^2$LO (c) potentials SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator in the $^3$S$_1$ channel.}
-	\label{potential_contours_3S1_Wegner}
+	\label{fig:potential_contours_3S1_Wegner}
 \end{figure}
@@
 For block-diagonal evolution, we fix $\lambda=1.5$ fm$^{-1}$.}
-	\label{potential_contours_3S1_RKE}
+	\label{fig:potential_contours_3S1_RKE}
 \end{figure}
@@
 	\caption{$^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) phase shifts for the EM N$^3$LO (solid black), RKE N$^3$LO (red dash-dotted), and Gezerlis et al. N$^2$LO (blue dashed) potentials.}
-	\label{phase_shifts}
+	\label{fig:phase_shifts}
 \end{figure}
@@
 Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution.
-For block-diagonal evolution, we fix $\lambda=1.0$ fm$^{-1}$.}
-	\label{potential_slices_1S0}
+For block-diagonal evolution, we fix $\lambda=1$ fm$^{-1}$.}
+	\label{fig:potential_slices_1S0}
 \end{figure}
@@
 	\caption{Same as Fig.~\ref{fig:potential_slices_1S0} but in the $^3$S$_1$ channel.}
-	\label{potential_slices_3S1}
+	\label{fig:potential_slices_3S1}
 \end{figure}
@@
 	\caption{Same as Figs.~\ref{fig:potential_slices_1S0} and \ref{fig:potential_slices_3S1} but in the $^1$P$_1$ channel.}
-	\label{potential_slices_1P1}
+	\label{fig:potential_slices_1P1}
 \end{figure}
@@
 %	- Last thing to look at in potentials: cutoff dependence.
-%	- Recap Wendt (2011).
+%	- Recap Wendt (2011) focusing on universality in matrix elements.
 %	- Test block-diagonal evolution for the 3 cutoffs.

### 2019-09-17 test.py
Generated SRG-evolved potentials
kvnn = 900 and 901
channel = 3S1
generators = Wegner, block-diagonal up to lambda = 1 fm^-1 and Lambda = 6, 3, 2, 1.5, 1 fm^-1.

@@ -29,22 +29,30 @@ import numpy as np
 from run_srg import run_srg
 
 
-kvnn = 900
-#kvnn = 901
-#kvnn = 902
+kvnn_list = [900, 901, 902]
 # Could add the RKE 1-20 fm^-1 LO potentials as 903, 904, ...
 channel = '3S1'
 kmax = 30.0
 kmid = 4.0
 ntot = 120
 
-generator = 'Block-diag'
-lambda_array = np.array( [10.0, 2.8, 2.0, 1.2] )
+generator_list = ['Wegner', 'T', 'Block-diag']
+lambda_array = np.array( [6.0, 3.0, 2.0, 1.5, 1.0] )
 # Save the evolved Hamiltonian?
 save = True
 
-for lamb in lambda_array:
+for kvnn in kvnn_list:
+    for generator in generator_list:
+        
+        if generator == 'Block-diag':
+            for lamb in lambda_array:
             
-    # Evolve Hamiltonian
-    d = run_srg(kvnn, channel, kmax, kmid, ntot, generator, lambda_array, lamb,
-                save)
+                # Evolve Hamiltonian
+                d = run_srg(kvnn, channel, kmax, kmid, ntot, generator,
+                            lambda_array, lamb, save)
+                
+        else:
+            
+            # Evolve Hamiltonian
+            d = run_srg(kvnn, channel, kmax, kmid, ntot, generator, 
+                        lambda_array, 0.00, save)

### 2019-09-17 Figures/figures_functions.py
Update figures_functions.py
Changed kvnn label for kvnn = 900-902 from Lambda = ... fm^-1 to just ... fm^-1 in kvnn_label_conversion.

@@ -19,6 +19,8 @@
 #   09/09/19 --- Added channel_label_conversion function. Analogous to
 #                kvnn_label_conversion and generator_label_conversion
 #                functions.
+#   09/17/19 --- Changed kvnn label for kvnn = 900-902 from Lambda = ... fm^-1
+#                to just ... fm^-1.
 #
 #------------------------------------------------------------------------------
 
@@ -177,11 +179,14 @@ def kvnn_label_conversion(kvnn):
         label = 'Gezerlis N' + r'$^2$' + 'LO'
     # Wendt LO non-local potential
     elif kvnn == 900: # Cutoff 4 fm^-1
-        label = r'$\Lambda = 4$' + ' fm' + r'$^{-1}$'
+        #label = r'$\Lambda = 4$' + ' fm' + r'$^{-1}$'
+        label = '4 fm' + r'$^{-1}$'
     elif kvnn == 901: # Cutoff 9 fm^-1
-        label = r'$\Lambda = 9$' + ' fm' + r'$^{-1}$'
+        #label = r'$\Lambda = 9$' + ' fm' + r'$^{-1}$'
+        label = '9 fm' + r'$^{-1}$'
     elif kvnn == 902: # Cutoff 20 fm^-1
-        label = r'$\Lambda = 20$' + ' fm' + r'$^{-1}$'
+        #label = r'$\Lambda = 20$' + ' fm' + r'$^{-1}$'
+        label = '20 fm' + r'$^{-1}$'
 
     return label
 

### 2019-09-17 Figures/figures_functions.py
Update figures_functions.py
Minor updates.

@@ -145,7 +145,7 @@ def interpolate_matrix(x_array, M, x_max, ntot=500):
     return x_array_new, M_new
 
 
-def kvnn_label_conversion(kvnn):
+def kvnn_label_conversion(kvnn, full_label=True):
     """
     Converts a kvnn number to a label for plotting purposes (e.g. kvnn = 6 
     gives 'AV18').
@@ -154,6 +154,10 @@ def kvnn_label_conversion(kvnn):
     ----------
     kvnn : int
         This number specifies the potential.
+    full_label : bool, optional
+        For some labels, there is a shortened version. Set full_label = False
+        for the shortened version. For example, kvnn = 902 gives
+        '\Lambda = 20 fm^-1' normally, but the shortened version is '20 fm^-1'.
         
     Returns
     -------
@@ -165,28 +169,38 @@ def kvnn_label_conversion(kvnn):
     # Argonne v18
     if kvnn == 6:
         label = 'AV18'
+        
     # Entem/Machleidt N3LO (500 MeV cutoff)   
     elif kvnn == 10:
         label = 'EM N' + r'$^3$' + 'LO'
+        
     # RKE N3LO (400, 450, 500 MeV cutoffs)
     elif kvnn in [105, 106, 107]:
         label = 'RKE N' + r'$^3$' + 'LO'
     # RKE N4LO (400, 450, 500 MeV cutoffs)
     elif kvnn in [110, 111, 112]:
         label = 'RKE N' + r'$^4$' + 'LO'
+        
     # Gezrelis N2LO (1 and 1.2 fm cutoff)
     elif kvnn in [222, 224]:
         label = 'Gezerlis N' + r'$^2$' + 'LO'
+        
     # Wendt LO non-local potential
     elif kvnn == 900: # Cutoff 4 fm^-1
-        #label = r'$\Lambda = 4$' + ' fm' + r'$^{-1}$'
-        label = '4 fm' + r'$^{-1}$'
+        if full_label:
+            label = r'$\Lambda = 4$' + ' fm' + r'$^{-1}$'
+        else:
+            label = '4 fm' + r'$^{-1}$'
     elif kvnn == 901: # Cutoff 9 fm^-1
-        #label = r'$\Lambda = 9$' + ' fm' + r'$^{-1}$'
-        label = '9 fm' + r'$^{-1}$'
+        if full_label:
[…]

### 2019-09-18 Notes/Operator_evolution/operator_evolution.tex
Updated operator evolution notes
Minor changes.

@@
 %	09/09/19 --- Added more bullets to the introduction. Further organization.
+%	09/17/19 --- Added more bullets to section 2.
 %
@@
 \noindent{%
+\textbf{General outline of the section}
+}
+\\
 -- Comparison of potential evolution with different regulators, orders, generators.
-}
 \\
@@
 -- Use high cutoffs to transition to Magnus test problem.
+\\
+\textbf{Analysis of figures}
+\\
+-- Fig.~\ref{fig:potential_contours_RKE_Wegner} illustrates the SRG in a nutshell.
+Here, we evolve three partial wave channels of RKE N$^3$LO \cite{Reinert:2017usi} where the cutoff $\Lambda=450$ MeV to $\lambda=1.5$ fm$^{-1}$.
+We see that the off-diagonal elements of the potential approach zero as the potential evolves approaching a band-diagonal form.
 %
@@
 \end{figure}
+%
+-- In Fig.~\ref{fig:potential_contours_3S1_Wegner} we consider three different SRG-evolved potentials in the $^3$S$_1$ channel: EM N$^3$LO (500 MeV cutoff) \cite{Entem:2003ft}, RKE N$^3$LO (450 MeV cutoff) \cite{Reinert:2017usi}, and Gezerlis et al.
+N$^2$LO (1 fm cutoff) \cite{Gezerlis:2014zia}.
 %

### 2019-09-19 SRG_codes/srg_wegner.py
Generated SRG-evolved potentials
kvnn = 902, channel = 3S1, generator = block-diagonal, lambda = 1 fm^-1 for Lambda_BD = 6, 3, 2, 1.5, 1 fm^-1.

@@ -12,12 +12,13 @@
 # Revision history:
 #   05/27/19 --- Solve flow equation with respect to parameter lambda and use 
 #                SciPy's ode function.
+#   09/18/19 --- Added odeint as an option for the ODE solver instead of ode.
 #
 #------------------------------------------------------------------------------
 
 
 import numpy as np
-from scipy.integrate import ode
+from scipy.integrate import ode, odeint
   
 
 class SRG(object):
@@ -179,7 +180,7 @@ class SRG(object):
         return dH_vector
 
 
-    def evolve_hamiltonian(self, lambda_initial, lambda_array):
+    def evolve_hamiltonian(self, lambda_initial, lambda_array, method='ode'):
         """
         Evolved Hamiltonian at each value of lambda in lambda_array.
         
@@ -191,6 +192,8 @@ class SRG(object):
             run_generate_vsrg_vlowk.pl to be sure.)
         lambda_array : 1-D ndarray
             Lambda evolution values in units fm^-1.
+        method : str, optional
+            ODE solver to use: SciPy 'ode' or 'odeint'. 'ode' is the default.
             
         Returns
         -------
@@ -203,46 +206,65 @@ class SRG(object):
 
         # Set-up ODE
         
-        # Initial Hamiltonian as a vector
+        # Initial Hamiltonian as a vector and dictionary
         H_initial = self.matrix2vector(self.H_initial)
-
-        # Use SciPy's ode function to solve flow equation
-        solver = ode(self.derivative)
-        # Following the example in Hergert:2016iju with modifications to nsteps
-        # and error tolerances
-        solver.set_integrator('vode', method='bdf', order=5, nsteps=1000000, 
-                              atol=1e-6, rtol=1e-6)
-        # Set initial value of Hamiltonian at lambda = lambda_initial
-        solver.set_initial_value(H_initial, lambda_initial)
-    
-        # Initialize dictionary
         d = {}
+        
+        # Use SciPy's ode function to solve flow equation
+        if method == 'ode':
+
+            solver = ode(self.derivative)
+            # Following the example in Hergert:2016iju with modifications to
+            # nsteps and error tolerances
+            solver.set_integrator('vode', method='bdf', order=5,
+                                  atol=1e-6, rtol=1e-6, nsteps=1000000)
+            # Set initial value of Hamiltonian at lambda = lambda_initial
+            solver.set_initial_value(H_initial, lambda_initial)
     
-        # Loop over lambda values in lambda_array
[…]

### 2019-09-19 test.py

@@ -29,30 +29,30 @@ import numpy as np
 from run_srg import run_srg
 
 
-kvnn_list = [900, 901, 902]
+kvnn = 902
 # Could add the RKE 1-20 fm^-1 LO potentials as 903, 904, ...
 channel = '3S1'
 kmax = 30.0
 kmid = 4.0
 ntot = 120
 
-generator_list = ['Wegner', 'T', 'Block-diag']
+#generator_list = ['Wegner', 'T']
+generator_list = ['Block-diag']
 lambda_array = np.array( [6.0, 3.0, 2.0, 1.5, 1.0] )
 # Save the evolved Hamiltonian?
 save = True
 
-for kvnn in kvnn_list:
-    for generator in generator_list:
+for generator in generator_list:
         
-        if generator == 'Block-diag':
-            for lamb in lambda_array:
-            
-                # Evolve Hamiltonian
-                d = run_srg(kvnn, channel, kmax, kmid, ntot, generator,
-                            lambda_array, lamb, save)
-                
-        else:
+    if generator == 'Block-diag':
+        for lamb in lambda_array:
             
             # Evolve Hamiltonian
-            d = run_srg(kvnn, channel, kmax, kmid, ntot, generator, 
-                        lambda_array, 0.00, save)
+            d = run_srg(kvnn, channel, kmax, kmid, ntot, generator,
+                        lambda_array, lamb, save)
+                
+    else:
+            
+        # Evolve Hamiltonian
+        d = run_srg(kvnn, channel, kmax, kmid, ntot, generator, lambda_array,
+                    0.00, save)

### 2019-09-19 SRG_codes/srg_wegner.py
Update srg_wegner.py
Changed mxstep of odeint method from 1,000,000 to 5,000,000.

@@ -252,7 +252,7 @@ class SRG(object):
         elif method == 'odeint':
         
             sol = odeint(self.derivative, lambda_initial, lambda_array,
-                         atol=1e-6, rtol=1e-6, mxstep=1000000, tfirst=True)
+                         atol=1e-6, rtol=1e-6, mxstep=5000000, tfirst=True)
             
             # Store each evolved Hamiltonian matrix in dictionary
             i = 1

### 2019-09-19 Notes/Operator_evolution/operator_evolution.tex
Updated operator evolution notes
Add bullets to section 2 and placeholders for Magnus figures.

@@
 %	09/09/19 --- Added more bullets to the introduction. Further organization.
-%	09/17/19 --- Added more bullets to section 2.
+%	09/19/19 --- Added more bullets to section 2.
 %
@@
 Here, we evolve three partial wave channels of RKE N$^3$LO \cite{Reinert:2017usi} where the cutoff $\Lambda=450$ MeV to $\lambda=1.5$ fm$^{-1}$.
-We see that the off-diagonal elements of the potential approach zero as the potential evolves approaching a band-diagonal form.
+We see that the off-diagonal elements of the potential approach zero and the potential is driven to band-diagonal form.
 %
@@
 %
+\noindent{%
 -- In Fig.~\ref{fig:potential_contours_3S1_Wegner} we consider three different SRG-evolved potentials in the $^3$S$_1$ channel: EM N$^3$LO (500 MeV cutoff) \cite{Entem:2003ft}, RKE N$^3$LO (450 MeV cutoff) \cite{Reinert:2017usi}, and Gezerlis et al.
 N$^2$LO (1 fm cutoff) \cite{Gezerlis:2014zia}.
+The major difference in these three potentials are the regulator functions in the contact and pion-exchange terms.
+The EM N$^3$LO interaction is a non-local potential where both contact and pion-exchange interactions feature a non-local regulator function of the form exp$[-(p/\Lambda)^{2n}-(p'/\Lambda)^{2n}]$, where $\Lambda$ is the momentum-space cutoff and $n$ is an integer.
+However, a non-local regulator function for pion-exchange contributions can introduce regulator artifacts for cutoffs $\Lambda$ lower than the breakdown scale $\Lambda_b$.
+Several semi-local chiral potentials have been introduced to reduce regulator artifacts, such as the RKE N$^3$LO potential.
+Here, a local regulator function is applied for the long-range interactions in momentum-space, while a non-local regulator function is used for the short-range interactions.
+In some instances, non-local interactions are not suitable for $\textit{ab initio}$ approaches such as the quantum Monte Carlo (QMC) method motivating the need for fully local potentials.
+The Gezerlis et al.
+N$^2$LO potential is an example of a local interaction where the long-range terms have a local regulator function in coordinate-space and the short-range terms have a local regulator function in momentum-space.
+}
+\\
+-- Takeaways from Fig.~\ref{fig:potential_contours_3S1_Wegner}: completely different at $\lambda=6$ fm$^{-1}$ but low-momentum matrix elements are similar at $\lambda=1$ fm$^{-1}$.
+Decoupled, low-momentum matrix elements are necessarily the same since the pion-exchange terms are calculated explicitly.
+(Cutoff dependence can play a role though for lower cutoffs.)
 %
@@
 %
+\noindent{%
+-- Fig.~\ref{fig:potential_contours_3S1_RKE} shows the SRG-evolved RKE N$^3$LO (450 MeV cutoff) potential in the $^3$S$_1$ channel for two SRG generators: the Wegner and block-diagonal generators which drive the potential to band- and block-diagonal form, respectively.
+We continue to evolve to band-diagonal form with respect to the parameter $\lambda$, but for the block-diagonal generator, we label sub-plots with the parameter $\Lambda$ which characterizes the sharp cutoff in decoupling the low- and high-momentum matrix elements.
+}
+\\
+-- Takeaways from Fig.~\ref{fig:potential_contours_3S1_RKE}: smooth decoupling for Wegner and sharp for block-diagonal, each unique generator should have its own type of universality.
+Check this more quantitatively by comparing matrix element ``slices''.
+%
 \begin{figure}[H]
@@
 %
+\noindent{%
+-- Fig.~\ref{fig:phase_shifts} shows the NN phase shifts of EM N$^3$LO, RKE N$^3$LO, and Gezerlis et al.
+N$^2$LO potentials in the $^1$S$_0$, $^3$S$_1$, and $^1$P$_1$ channels.
+In \cite{Dainton:2013axa}, it was found that phase equivalence up to some value of momentum $k$ implies matrix element equivalence up to the same value of $k$ in SRG-evolved potentials.
+We verify this conclusion by checking the matrix elements in Fig.~\ref{fig:potential_slices_1S0} where we see a collapse of the different potential matrix elements to the same line in the last column ($\lambda=1$ fm$^{-1}$).
+Note, Figs.~\ref{fig:potential_slices_1S0}-\ref{fig:potential_slices_1P1} show both Wegner and block-diagonal evolution where the solid lines correspond to the Wegner generator and dash-dotted to block-diagonal evolution.
+We see each generator collapses the potential to a different form because the low- and high-momentum matrix elements decouple in a different manner.
+}
+\\
+-- In the $^3$S$_1$ channel, we see a slight deviation in the lowest momentum potential matrix element from EM N$^3$LO and the other two potentials.
+This is due to a minor difference in the deuteron binding energy ($\approx 1\%$ difference).
+\\
+-- The bottom row of Fig.~\ref{fig:potential_slices_1P1} shows $V(k,0.5)$ instead of $V(k,0)$ because the far off-diagonal matrix elements in the $^1$P$_1$ channel are all zero.
 \begin{figure}[H]
@@
 %
-% Ideas for high cutoffs:
-%	- Last thing to look at in potentials: cutoff dependence.
-%	- Recap Wendt (2011) focusing on universality in matrix elements.
-%	- Test block-diagonal evolution for the 3 cutoffs.
-%	- Lead into Magnus expansion.
+\noindent{%
+\textbf{High cutoffs}
+}
+\begin{itemize}
+	\item Cutoff dependence in non-local LO (Wendt) potential.
+	\item Band- and block-diagonal evolution and universality. Add figure analogous to Fig.~\ref{fig:potential_slices_3S1} but for $\Lambda=4$, $9$, and $20$ fm$^{-1}$.
+	\item Spurious bound state(s).
+	\item Discussion on how the block-diagonal generator handles spurious bound states. Where they are ``decoupled'' in the matrix compared to Wegner.
+	\item Transition to Magnus expansion.
+\end{itemize}
 
@@
 -- Use discussion of operator evolution to transition to next section.
+%
+\begin{figure}[H]
+	\centering
+	\includegraphics[clip,width=0.9\columnwidth]{Magnus/potential_diagonals_offdiags_kvnn901_Wegner}%
+	\caption{Caption.}
+	\label{fig:potential_slices_high_cutoffs_Wegner}
+\end{figure}
+%
+\begin{figure}[H]
+	\centering
+	\includegraphics[clip,width=0.9\columnwidth]{Magnus/potential_diagonals_offdiags_kvnn901_T}%
+	\caption{Caption.}
+	\label{fig:potential_slices_high_cutoffs_T}
+\end{figure}
+%
 

### 2019-09-20 SRG_codes/srg_wegner.py
Testing updates to srg_wegner.py

@@ -251,11 +251,14 @@ class SRG(object):
         # Use SciPy's odeint function to solve flow equation
         elif method == 'odeint':
         
-            sol = odeint(self.derivative, lambda_initial, lambda_array,
+            if lambda_array[0] < 12.0:
+                lambda_array = np.append(np.array([12.0]), lambda_array)
+                
+            sol = odeint(self.derivative, H_initial, lambda_array,
                          atol=1e-6, rtol=1e-6, mxstep=5000000, tfirst=True)
             
             # Store each evolved Hamiltonian matrix in dictionary
-            i = 1
+            i = 0
             for lamb in lambda_array:
             
                 H_evolved = sol[i] # This is a vector

### 2019-09-20 test.py

@@ -26,7 +26,10 @@
 
 
 import numpy as np
-from run_srg import run_srg
+import time
+# Scripts made by A.T.
+from Potentials.vsrg_macos import load_save_potentials as lp
+from SRG_codes import srg_wegner
 
 
 kvnn = 902
@@ -36,23 +39,50 @@ kmax = 30.0
 kmid = 4.0
 ntot = 120
 
-#generator_list = ['Wegner', 'T']
-generator_list = ['Block-diag']
 lambda_array = np.array( [6.0, 3.0, 2.0, 1.5, 1.0] )
-# Save the evolved Hamiltonian?
-save = True
+generator = 'Wegner'
+#generator = 'T'
 
-for generator in generator_list:
-        
-    if generator == 'Block-diag':
-        for lamb in lambda_array:
-            
-            # Evolve Hamiltonian
-            d = run_srg(kvnn, channel, kmax, kmid, ntot, generator,
-                        lambda_array, lamb, save)
-                
-    else:
-            
-        # Evolve Hamiltonian
-        d = run_srg(kvnn, channel, kmax, kmid, ntot, generator, lambda_array,
-                    0.00, save)
+# Load initial Hamiltonian, kinetic energy, and weights
+H_initial = lp.load_hamiltonian(kvnn, channel, kmax, kmid, ntot)
+T_rel = lp.load_kinetic_energy(kvnn, channel, kmax, kmid, ntot)     
+k_array, k_weights = lp.load_momentum(kvnn, channel, kmax, kmid, ntot)
+    
+# h-bar^2 / M [MeV fm^2] for conversion from MeV to scattering units
+hbar_sq_over_M = 41.47
+    
+# Initial value of lambda in units fm^-1 (most potentials in 
+# Potentials/vsrg_macos are generated at lambda = 12 fm^-1 but check 
+# run_generate_vsrg_vlowk.pl to be sure)
+lambda_initial = 12.0
+
+evolve = srg_wegner.SRG(H_initial)
+# NEED TO ADD ODEINT TO T IF IT WORKS
+#evolve = srg_kinetic_energy.SRG(H_initial, T_rel)
+    
+# Time the evolution and return dictionary d of evolved Hamiltonians where
+# the keys are lambda values
+t0 = time.time() # Start time
+d = evolve.evolve_hamiltonian(lambda_initial, lambda_array, method='odeint')
+t1 = time.time() # End time
+    
+# Print details
[…]

### 2019-09-20 SRG_codes/srg_block_diagonal.py
Minor changes to SRG scripts

@@ -242,7 +242,7 @@ class SRG(object):
         solver = ode(self.derivative)
         # Following the example in Hergert:2016iju with modifications to nsteps
         # and error tolerances
-        solver.set_integrator('vode', method='bdf', order=5, nsteps=1000000, 
+        solver.set_integrator('vode', method='bdf', order=5, nsteps=5000000, 
                               atol=1e-6, rtol=1e-6)
         # Set initial value of Hamiltonian at lambda = lambda_initial
         solver.set_initial_value(H_initial, lambda_initial)

### 2019-09-20 SRG_codes/srg_kinetic_energy.py

@@ -216,7 +216,7 @@ class SRG(object):
         solver = ode(self.derivative)
         # Following the example in Hergert:2016iju with modifications to nsteps
         # and error tolerances
-        solver.set_integrator('vode', method='bdf', order=5, nsteps=1000000, 
+        solver.set_integrator('vode', method='bdf', order=5, nsteps=5000000, 
                               atol=1e-6, rtol=1e-6)
         # Set initial value of Hamiltonian at lambda = lambda_initial
         solver.set_initial_value(H_initial, lambda_initial)

### 2019-09-20 SRG_codes/srg_wegner.py

@@ -211,63 +211,39 @@ class SRG(object):
         d = {}
         
         # Use SciPy's ode function to solve flow equation
-        if method == 'ode':
-
-            solver = ode(self.derivative)
-            # Following the example in Hergert:2016iju with modifications to
-            # nsteps and error tolerances
-            solver.set_integrator('vode', method='bdf', order=5,
-                                  atol=1e-6, rtol=1e-6, nsteps=1000000)
-            # Set initial value of Hamiltonian at lambda = lambda_initial
-            solver.set_initial_value(H_initial, lambda_initial)
+        solver = ode(self.derivative)
+        # Following the example in Hergert:2016iju with modifications to nsteps
+        # and error tolerances
+        solver.set_integrator('vode', method='bdf', order=5, atol=1e-6,
+                              rtol=1e-6, nsteps=5000000)
+        # Set initial value of Hamiltonian at lambda = lambda_initial
+        solver.set_initial_value(H_initial, lambda_initial)
     
-            # Loop over lambda values in lambda_array
-            for lamb in lambda_array:
+        # Loop over lambda values in lambda_array
+        for lamb in lambda_array:
             
-                # Solve ODE up to lamb and store in dictionary
-                while solver.successful() and solver.t > lamb:
+            # Solve ODE up to lamb and store in dictionary
+            while solver.successful() and solver.t > lamb:
             
-                    # Select step-size depending on extent of evolution
-                    if solver.t >= 6.0:
-                        dlamb = 1.0
-                    elif solver.t < 6.0 and solver.t >= 2.5:
-                        dlamb = 0.5
-                    elif solver.t < 2.5 and solver.t >= lamb:
-                        dlamb = 0.1
+                # Select step-size depending on extent of evolution
+                if solver.t >= 6.0:
+                    dlamb = 1.0
+                elif solver.t < 6.0 and solver.t >= 2.5:
+                    dlamb = 0.5
+                elif solver.t < 2.5 and solver.t >= lamb:
+                    dlamb = 0.1
                 
-                    # This if statement prevents the solver from over-shooting 
-                    # lambda and takes a step in lambda equal to the exact
-                    # amount necessary to reach the specified lambda value
-                    if solver.t - dlamb < lamb:
+                # This if statement prevents the solver from over-shooting 
+                # lambda and takes a step in lambda equal to the exact amount
+                # necessary to reach the specified lambda value
+                if solver.t - dlamb < lamb:
[…]

### 2019-09-20 run_srg.py
Generated SRG-evolved potentials for various cases
kvnn = 10, 222
channel = 3S1
generator = Wegner, block-diagonal up to lambda = 1 fm^-1.

@@ -154,13 +154,13 @@ if __name__ == '__main__':
     #channel = '1P1'
     #channel = '3P0'
     
-    kmax = 30.0
-    #kmax = 8.0
+    #kmax = 30.0
+    kmax = 8.0
     #kmax = 10.0
     #kmax = 6.0
     
-    kmid = 4.0
-    #kmid = 2.0
+    #kmid = 4.0
+    kmid = 2.0
     #kmid = 3.0
     
     ntot = 120 # Default
@@ -175,8 +175,8 @@ if __name__ == '__main__':
     #generator = 'T'
     generator = 'Block-diag'
     
-    #lambda_bd = 1.00 # This won't affect the band-diagonal generators
-    lambda_bd = 1.50
+    lambda_bd = 1.00 # This won't affect the band-diagonal generators
+    #lambda_bd = 1.50
     #lambda_bd = 2.00 # Default
     #lambda_bd = 3.00
     #lambda_bd = 4.00

### 2019-09-20 test.py

@@ -26,63 +26,32 @@
 
 
 import numpy as np
-import time
 # Scripts made by A.T.
-from Potentials.vsrg_macos import load_save_potentials as lp
-from SRG_codes import srg_wegner
+from run_srg import run_srg
 
 
-kvnn = 902
+#kvnn = 902
+kvnn = 10
 # Could add the RKE 1-20 fm^-1 LO potentials as 903, 904, ...
 channel = '3S1'
-kmax = 30.0
-kmid = 4.0
+#kmax = 30.0
+kmax = 8.0
+#kmid = 4.0
+kmid = 2.0
 ntot = 120
 
-lambda_array = np.array( [6.0, 3.0, 2.0, 1.5, 1.0] )
-generator = 'Wegner'
-#generator = 'T'
+#lambda_array = np.array( [6.0, 3.0, 2.0, 1.5, 1.0] )
+lambda_array = np.array( [6.0, 3.0, 2.0, 1.5] )
+#generator_list = ['Wegner', 'T']
 
-# Load initial Hamiltonian, kinetic energy, and weights
-H_initial = lp.load_hamiltonian(kvnn, channel, kmax, kmid, ntot)
-T_rel = lp.load_kinetic_energy(kvnn, channel, kmax, kmid, ntot)     
-k_array, k_weights = lp.load_momentum(kvnn, channel, kmax, kmid, ntot)
+#for generator in generator_list:
     
-# h-bar^2 / M [MeV fm^2] for conversion from MeV to scattering units
-hbar_sq_over_M = 41.47
-    
-# Initial value of lambda in units fm^-1 (most potentials in 
-# Potentials/vsrg_macos are generated at lambda = 12 fm^-1 but check 
-# run_generate_vsrg_vlowk.pl to be sure)
-lambda_initial = 12.0
+    #d = run_srg(kvnn, channel, kmax, kmid, ntot, generator, lambda_array,
+                #save=True)
+                
+generator = 'Block-diag'
 
-evolve = srg_wegner.SRG(H_initial)
-# NEED TO ADD ODEINT TO T IF IT WORKS
-#evolve = srg_kinetic_energy.SRG(H_initial, T_rel)
-    
-# Time the evolution and return dictionary d of evolved Hamiltonians where
-# the keys are lambda values
-t0 = time.time() # Start time
-d = evolve.evolve_hamiltonian(lambda_initial, lambda_array, method='odeint')
-t1 = time.time() # End time
-    
-# Print details
[…]

### 2019-09-20 SRG_codes/srg_wegner.py
Update srg_wegner.py
Removed odeint import since it's not be used in code.

@@ -18,7 +18,7 @@
 
 
 import numpy as np
-from scipy.integrate import ode, odeint
+from scipy.integrate import ode
   
 
 class SRG(object):

### 2019-09-23 Notes/Operator_evolution/operator_evolution_notes.tex
Created operator_evolution_notes.tex
This will document technicalities of the operator evolution paper. Think of it like an appendix.

--- 2019-09-16 Notes/Operator_evolution/operator_evolution.tex
@@
 %
-% File: operator_evolution.tex
+% File: operator_evolution_notes.tex
 %
 % Author: A. J. Tropiano (tropiano.4@osu.edu)
-% Date: August 23, 2019
+% Date: September 23, 2019
 %
-% Draft of paper on SRG operator evolution and the Magnus expansion.
+% PUT DESCRIPTION HERE.
 %
 % Revision history:
-%	08/28/19 --- Started outlining and added pieces from old notes.
-%	09/09/19 --- Added more bullets to the introduction. Further organization.
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Operator evolution from the similarity renormalization group and the Magnus expansion}
+\title{Operator evolution notes}
 
-\author{A.~J.~Tropiano$^{1}$, S.~K.~Bogner$^{2}$, R.~J.~Furnstahl$^{1}$}
+\author{A.~J.~Tropiano$^{1}$}
 
-\affiliation{%
-		$^1$\mbox{Department of Physics, The Ohio State University, Columbus, OH 43210, USA}  \\
-		$^2$\mbox{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy,}  \\
-    		\mbox{Michigan State University, East Lansing, MI 48824, USA}
-}
+\affiliation{$^1$\mbox{Department of Physics, The Ohio State University, Columbus, OH 43210, USA}}
 
 \date{\today}
-
-\begin{abstract}
-
-\noindent{Ideas for Magnus / SRG operator evolution paper}
-\\
--- SRG/Magnus evolution in different potentials (non-local, local, semi-local). Universality. High cutoffs.
-\\
--- Block-diagonal generator for high cutoff potentials and operator evolution. How the block-diagonal generator handles spurious bound states.
-\\
--- Testing the Magnus expansion for high cutoff potentials using the potentials from Wendt 2011 for comparison. Spurious bound states and connection to intruder states in IMSRG calculations.
-\\
--- Operator evolution for different potentials and generators.
-
-\end{abstract}
 
@@
 \newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-\label{sec:intro}
-
-\noindent{%
-\textbf{Background on modern nuclear potentials.}
-}
-\\
--- Wide range of NN potentials.
-%
-% Add what you have from IMSRG paper.
-\begin{itemize}
-	\item Chiral EFT background.
-	\item Different potentials but give same $S$-matrix.
-\end{itemize}
-%
--- Implementation to many-body calculations and SRG decoupling.
-%
-\begin{itemize}
-	\item Strong coupling between low- and high-momentum matrix elements in NN potentials.
-	\item Very difficult to implement these interactions in many-body methods using basis expansions. Matrix dimension becomes too large for accurate calculations.
-	\item RG transformations are used to soften the interaction to make many-body methods feasible. One such method, the SRG, also preserves observables from unitarity.
-	\item How do different potentials change under SRG transformations?
-\end{itemize}
-%
-\textbf{SRG formalism}
-\\
--- The SRG decouples low- and high-momentum scales by applying a continuous unitary transformation $U(s)$ where $s=0 \rightarrow \infty$ is the flow parameter.
-\\
--- The `dressed' or evolved operator is given by
-%
-\begin{eqnarray}
-	\label{eq:srg_operator}
-	O(s) = U(s) O(0) U^{\dagger}(s),
-\end{eqnarray}
-%
-where $O(0)$ corresponds to the `bare' operator.
-\\
--- Because $U(s)$ is unitary, the observables of the operator are preserved.
-\\
--- In practice, the unitary transformation U(s) is not explicitly solved for; the evolved operator is given by a differential flow equation which is obtained by taking the derivative of Eqn.
-(\ref{eq:srg_operator}),
-%
-\begin{eqnarray}
-	\label{eq:srg_flow}
-	\frac{dO(s)}{ds} = [\eta(s), O(s)],
-\end{eqnarray}
-%
-where $\eta(s)=\frac{dU(s)}{ds} U^{\dagger}(s) = -\eta^{\dagger}(s)$ is the anti-hermitian SRG generator.
-\\
--- The generator is defined as a commutator, $\eta(s) = [G, H(s)]$, where $G$ specifies the type of flow or form of the decoupled operator.
-\\
--- By setting $G=H_D(s)$, the diagonal of the Hamiltonian, the operator is driven to band-diagonal form.
-\\
--- This choice was implemented by Wegner in condensed matter physics \cite{Wegner:1994ab}.
-\\
--- In a similar option used in nuclear physics, $G$ is set to the relative kinetic energy, $T_{rel}$, which also drives to band-diagonal form.
-% Do I need to explain the intermediate step here?
-\\
--- It is convenient to define $\lambda \equiv s^{-1/4}$ which roughly measures the width of the band-diagonal in the decoupled operator.
-\\
--- For block-diagonal decoupling, denoted $G=H_{BD}(s)$, the operator is split into low- and high-momentum sub-blocks by specifying a separation in momentum $\Lambda_{BD}$.
-\\
--- These transformations are similar to $V_{low k}$ Lee-Suzuki transformations but keep the high-momentum matrix elements non-zero, although entirely decoupled from the low-momentum sub-block.
-\\
--- Generally the flow equation (\ref{eq:srg_flow}) is solved up to some finite value of $s$ with a high-order ODE solver.
-\\
--- For notational convenience, we write the generators without the $s$ dependence in the rest of the paper.
-\\
-\textbf{Universality}
-\\
-% Try to understand this better. Ask DF.
--- The explicit long-range physics should be the same.
-Decoupling low- and high-energy gives matching low-energy matrix elements.
-In the NN potential, this means softened NN interactions should have the same low-momentum matrix elements after sufficient decoupling.
-\\
--- Add takeaways from Dainton: phase shift equivalence implies matrix element equivalence for $\lambda$ approaching the momenta of phase equivalence.
-Correct binding energy is critical or the lowest matrix elements will not match.
-\\
--- Motivate long list of unaddressed questions: regulator, generator dependence, high cutoffs, the Magnus expansion.
-%
-\begin{itemize}
-	\item Regulator. Functional dependence of regulator. Reasons for implementing each.
-	\item Generators. Band- and block-diagonal transformations.
-	\item High cutoffs. Cite Nogga, Wendt, and Tews papers.
-	\item The Magnus expansion. High cutoffs and connection to IMSRG intruder state problem.
-\end{itemize}
-%
-\textbf{Operator evolution}
-\\
--- State how a potential and wave function changes: how does this affect other operators?
-\\
--- Operator evolution for different potentials (regulators, chiral order, etc.)
-\\
--- How operators evolve from band- and block-diagonal SRG transformations.
-\\
-\textbf{Overview of sections.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{SRG evolution of NN potentials}
-\label{sec:srg_evolution_nn_potentials}
-
-\noindent{%
--- Comparison of potential evolution with different regulators, orders, generators.
-}
-\\
--- Universality.
-\\
--- Discussion of high cutoffs, block-diagonal generator at high cutoffs, and how it handles spurious bound states.
-\\
--- Use high cutoffs to transition to Magnus test problem.
-%
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_1S0_Wegner_channel_label}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_3S1_Wegner_channel_label}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_1P1_Wegner_channel_label}%
-	}
-	\caption{Matrix elements of the RKE N$^3$LO potential SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator in the $^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) channels.}
-	\label{fig:potential_contours_RKE_Wegner}
-\end{figure}
-%
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Wegner_potential_label}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_3S1_Wegner_potential_label}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn222_3S1_Wegner_potential_label}%
-	}
-	\caption{Matrix elements of the EM N$^3$LO (a), RKE N$^3$LO (b), and Gezerlis et al.
-N$^2$LO (c) potentials SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator in the $^3$S$_1$ channel.}
-	\label{fig:potential_contours_3S1_Wegner}
-\end{figure}
-%
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_3S1_Wegner_generator_label}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_3S1_Block-diag_generator_label}%
-	}
-	\caption{Matrix elements of the RKE N$^3$LO potential SRG-evolving right to left under transformations with Wegner (a) and block-diagonal (b) generators in the $^3$S$_1$ channel.
-Here, we use $\lambda$ for Wegner evolution in the top row and $\Lambda$ for block-diagonal evolution in the bottom row.
-For block-diagonal evolution, we fix $\lambda=1.5$ fm$^{-1}$.}
-	\label{fig:potential_contours_3S1_RKE}
-\end{figure}
-%
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_1S0_kvnns_10_106_222}%
-	}
-	\quad
-	\subfloat[]{%
-	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_3S1_kvnns_10_106_222}%
-	}
-	\quad
-	\subfloat[]{%
-	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_1P1_kvnns_10_106_222}%
-	}
-	\caption{$^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) phase shifts for the EM N$^3$LO (solid black), RKE N$^3$LO (red dash-dotted), and Gezerlis et al. N$^2$LO (blue dashed) potentials.}
-	\label{fig:phase_shifts}
-\end{figure}
-%
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_1S0_kvnns_10_106_222_lamb1,0}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_1S0_kvnns_10_106_222_lamb1,0}%
-	}
-	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the EM N$^3$LO (black), RKE N$^3$LO (red) and Gezerlis et al.
-N$^2$LO (blue) potentials SRG-evolving right to left under transformations with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^1$S$_0$ channel.
-Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution.
-For block-diagonal evolution, we fix $\lambda=1$ fm$^{-1}$.}
-	\label{fig:potential_slices_1S0}
-\end{figure}
-%
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_3S1_kvnns_10_106_222_lamb1,0}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_3S1_kvnns_10_106_222_lamb1,0}%
-	}
-	\caption{Same as Fig.~\ref{fig:potential_slices_1S0} but in the $^3$S$_1$ channel.}
-	\label{fig:potential_slices_3S1}
-\end{figure}
-%
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_1P1_kvnns_10_106_222_lamb1,0}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_1P1_kvnns_10_106_222_lamb1,0}%
-	}
-	\caption{Same as Figs.~\ref{fig:potential_slices_1S0} and \ref{fig:potential_slices_3S1} but in the $^1$P$_1$ channel.}
-	\label{fig:potential_slices_1P1}
-\end{figure}
-%
-% Ideas for high cutoffs:
-%	- Last thing to look at in potentials: cutoff dependence.
-%	- Recap Wendt (2011) focusing on universality in matrix elements.
-%	- Test block-diagonal evolution for the 3 cutoffs.
-%	- Lead into Magnus expansion.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Magnus expansion}
-\label{sec:magnus_expansion}
-
-\noindent{%
--- Connection to IMSRG intruder state.
-}
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-\subsection{Formalism}
-\label{sec:magnus_expansion_formalism}
-
-\noindent{%
--- Motivation: simplifies computational problem for evolving multiple operators, exact unitarity.
-}
-\\
--- We now consider the Magnus implementation.
-\\
--- Mathematically speaking, the Magnus expansion is a method for solving an initial value problem associated with a linear ordinary differential equation (ODE).
-\\
--- Formal details of the Magnus expansion are discussed in \cite{Blanes:2009ab}.
-\\
--- We will introduce the Magnus expansion in the context of SRG evolving any operator.
-\\
--- In an intermediate step in deriving Eqn. (\ref{eq:srg_flow}), we have a linear ODE for $U(s)$,
-%
-\begin{eqnarray}
-	\label{eq:unitary_trans}
-	\frac{dU(s)}{ds} = \eta(s) U(s).
-\end{eqnarray}
-%
--- Magnus showed that one can solve the following equation with a solution $U(s)=e^{\Omega(s)}$ where $\Omega(s)$ is expanded as a power series, $\sum_{n}^{\infty} \Omega_n$ (referred to as the Magnus expansion or Magnus series).
-\\
--- The terms of the series are given by integral expressions involving $\eta(s)$ (again, see \cite{Blanes:2009ab, Magnus:1954zz} for details).
-\\
--- For our case, we focus on the formally exact derivative of $\Omega(s)$,
-%
-\begin{eqnarray}
-	\label{eq:magnus_omega}
-	\frac{d\Omega(s)}{ds} = \sum_{k=0}^{\infty} \frac{B_k}{k!} ad_{\Omega}^{k}(\eta),
-\end{eqnarray}
-%
-where $B_k$ are the Bernoulli numbers, $ad_{\Omega}^{0}(\eta)=\eta(s)$, and $ad_{\Omega}^{k}(\eta)=[\Omega(s),ad_{\Omega}^{k-1}(\eta)]$.
-\\
--- We integrate this differential equation to find $\Omega(s)$ and evaluate the unitary transformation directly.
-\\
--- Then the evolved operator can be evaluated with the BCH formula:
-%
-\begin{eqnarray}
-	\label{eq:bch}
-	O(s) = e^{\Omega(s)} O e^{-\Omega(s)} = \sum_{k=0}^{\infty} \frac{1}{k!} ad_{\Omega}^{k}(O).
-\end{eqnarray}
-%
--- As $k \rightarrow \infty$ in both sums in Eqns. (\ref{eq:magnus_omega}) and (\ref{eq:bch}) the Magnus transformation matches the SRG transformation exactly.
-\\
--- We investigate several truncations $k_{max}$ in Eqn. (\ref{eq:magnus_omega}) and take many terms, $k_{max} \sim 25$, in Eqn. (\ref{eq:bch}).
-\\
-\textcolor{red}{%
--- Here or earlier (for the following bullets)? Better to motivate the Magnus in the introduction or easier to explain given mathematical detail?
-}
-\\
--- There are significant advantages in the Magnus implementation.
-\\
--- In the typical approach, the numerical error associated with solving the flow equation affects the accuracy of the observables for the evolved operator.
-\\
--- Therefore, one must use a high-order ODE solver in integrating the flow equation (\ref{eq:srg_flow}).
-\\
--- In the Magnus implementation, unitarity is guaranteed by the form of $U(s)$; in fact, one could solve Eqn.
-(\ref{eq:magnus_omega}) with a simple first-order Euler step-method keeping the same observables while decoupling the operator as desired.
-\\
--- This offers a decent computational speed-up by avoiding a high-order solver.
-\\
--- In this paper, we demonstrate this advantage by applying the Magnus implementation using the first-order Euler step-method.
-\\
--- The second major advantage involves the evolution of multiple operators.
-\\
--- In many other situations, one may be interested in evolving several operators at a time.
-\\
--- In the SRG procedure, we would have another set of coupled equations in Eqn. (\ref{eq:srg_flow}), drastically increasing memory usage.
-\\
--- Each additional operator increases the set of equations - say $N$ equations - by another factor of $N$.
-\\
--- In the Magnus, one only needs $\Omega(s)$ to consistently evolve several operators.
-\\
--- We avoid the cost in memory by directly constructing $U(s)=e^{\Omega(s)}$.
-\\
--- This is especially useful in IMSRG calculations where the model space can be very large.
-\\
--- In the next section, we discuss results from Magnus-evolved large-cutoff potentials focusing on the flow of the potential, observables, and operator evolution.
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-\subsection{Results}
-\label{sec:magnus_expansion_results}
-
-\noindent{%
--- Comparison to Wendt problem.
-}
-\\
--- Implications for IMSRG.
-\\
--- Use discussion of operator evolution to transition to next section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Evolution of other operators}
-\label{sec:evolution_other_operators}
-
-\noindent{%
--- SRG operator evolution for different potentials and generators.
-}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-\label{sec:conclusion}
-
-\noindent{%
--- Summary.
-}
-\\
--- Outlook.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliography{../tropiano_bib}
-
 \end{document}

### 2019-09-23 Potentials/vsrg_macos/run_generate_vsrg_vlowk.pl
Generated EM N3LO and RKE potentials on different mesh
Set k_max = 10 fm^-1 and k_mid = 2 fm^-1. ntot remains the same at 120.

@@ -56,7 +56,8 @@ $ntot = 120; # momentum points for P+Q = full = bare space
 #$ntot = 140; # changes made by AT
 #$ntot = 141;
 #$kmax = 6.0;
-$kmax = 8.0; # kmax ==> maximum momentum for bare potential   # following the sample code by Evgeny 30-Nov-2017
+#$kmax = 8.0; # kmax ==> maximum momentum for bare potential   # following the sample code by Evgeny 30-Nov-2017
+$kmax = 10.0;
 #$kmax = 30.0;
 $kmid = 2.0;  # mesh goes from 0 to kmid, then kmid to kmax
 #$kmid = 3.0; # setting in Anderson:2010aq
@@ -94,11 +95,11 @@ $kmid = 2.0;  # mesh goes from 0 to kmid, then kmid to kmax
 #     cutnum = 1,2,3,4--> 400, 450, 500, 550 MeV cutoff
 
 #@kvnns = (06); # Argonne v18
-#@kvnns = (10); # Entem-Machleidt
+@kvnns = (10); # Entem-Machleidt
 #@kvnns = (32); # Epelbaum
 #@kvnns = (90,91,92,93,95,96,97,98,100,101,102,103,105,106,107,108,110,111,112,113,115,116,117,118); # RKE semi-local potentials
 #@kvnns = (90); # RKE semi-local potential at LO with specified cutoff (unless changed it's 400 MeV)
-@kvnns = (105,106,107,110,111,112); # RKE semi-local potential at N3LO and N4LO
+#@kvnns = (105,106,107,110,111,112); # RKE semi-local potential at N3LO and N4LO
 
 # The following list is all of the semi-local EKM potentials
 #@kvnns = (40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,64);
@@ -149,7 +150,7 @@ $J_max = 13;  # highest J value
         "3Q12","1Q12","3Q13"
         );
 #@pws = ("1S0","3S1");
-@pws = ("1P1", "3P0");
+@pws = ("1S0","3S1","1P1","3P0");
 #@pws = ("3P0");
 #@pws = ("3N12","1M10","1O12");
 

### 2019-09-23 Notes/Operator_evolution/operator_evolution.tex
Update to operator evolution notes
Minor changes.
Updated operator evolution draft
Added a couple figures for high cutoffs analysis.

@@
 \end{itemize}
+%
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_3S1_kvnns_900_901_902_lamb1,2}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_3S1_kvnns_900_901_902_lamb1,2}%
+	}
+	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the non-local LO potentials at cutoffs $\Lambda=4$ (black), $9$ (red) and $20$ (blue) fm$^{-1}$ SRG-evolving right to left under transformations with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^3$S$_1$ channel.
+Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution.
+For block-diagonal evolution, we fix $\lambda=1.2$ fm$^{-1}$.}
+	\label{fig:potential_slices_high_cutoffs}
+\end{figure}
+%
 
@@
 	\includegraphics[clip,width=0.9\columnwidth]{Magnus/potential_diagonals_offdiags_kvnn901_Wegner}%
-	\caption{Caption.}
+	%\caption{Caption.}
 	\label{fig:potential_slices_high_cutoffs_Wegner}
@@
 	\includegraphics[clip,width=0.9\columnwidth]{Magnus/potential_diagonals_offdiags_kvnn901_T}%
-	\caption{Caption.}
+	%\caption{Caption.}
 	\label{fig:potential_slices_high_cutoffs_T}
@@
 }
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-\subsection{Building SRG unitary transformations}
-\label{sec:srg_unitary_transformations}
-
-Diagonalize initial and evolved Hamiltonians which we will call $H(0)$ and $H(s)$, respectively.
-This gives $\psi_{\alpha}(0)$ and $\psi_{\alpha}(s)$ for each eigenvalue indexed by $\alpha$.
-Then the SRG unitary transformation can be computed by taking a sum over outer products of the evolved and initial wave functions:
+\\
+-- General questions to address: universality for operators, different generators.
+\\
+-- Momentum projection operator.
 %
-\begin{eqnarray}
-	\label{eq:unitary_transformation}
-	U(s) = \sum_{\alpha=1}^{N} \ket{\psi_{\alpha}(s)} \bra{\psi_{\alpha}(0)},
-\end{eqnarray}
+\begin{itemize}
+	\item Contours and general behavior: SRG transformation shifts strength of operator to low-momentum.
+	\item Deuteron momentum distributions. Why does this make sense with the transformed operators?
+	\item Diagonals and far off-diagonals. Universality.
+	\item Same questions but with figures of the integrand.
+\end{itemize}
 %
-where N is the dimension of the Hamiltonian matrix. Here the weights are factored into the wave functions, thus $U(s)$ is unitless.
-\\
-
-To evolve operators, we simply apply $U(s)$:
-%
-\begin{eqnarray}
-	\label{eq:evolved_operator}
-	O(s) = U(s) O(0) U^{\dagger}(s),
-\end{eqnarray}
-%
-where $O(0)$ is the bare operator.
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-\subsection{Momentum projection operator: $a^{\dagger}_q a_q (k, k')$}
-\label{sec:momentum_proj_operator}
-
-Applying $a^{\dagger}_q a_q (k, k')$ to a wave function $\psi(k)$ returns $\psi(q)$.
-For the discrete case, $\psi(k_i)$ is an $N \times 1$ vector and $a^{\dagger}_q a_q (k_i, k_j)$ is an $N \times N$ matrix where $i$, $j=1\cdots N$.
-Then $a^{\dagger}_q a_q (k, k')$ acting on $\psi(k)$ is a matrix multiplication, implying a continuous integration over $d^3k / (2 \pi)^3 = 2 / (\pi k^2 dk)$ in spherical coordinates.
-Therefore, we include a factor of $\pi / (2 k_i k_j \sqrt{w_i w_j})$ in $a^{\dagger}_q a_q (k_i, k_j)$ where $w$ represents the momentum weights.
-In matrix form,
-%
-\begin{eqnarray}
-	\label{eq:momentum_projection_operator}
-	a^{\dagger}_q a_q (k_i, k_j) = \frac{\pi \delta_{k_i q} \delta_{k_j q}}{2 k_i k_j \sqrt{w_i w_j}},
-\end{eqnarray}
-%
-which has units fm$^3$.
-To evolve operators, we apply $U(s)$ at this point.
-For mesh-independent figures, we must divide by an additional factor of $k_i k_j \sqrt{w_i w_j}$.
-This operator is inherently mesh-dependent based off discretizing $\delta_{k_i q} \delta_{k_j q}$ above.
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-\subsection{Momentum distribution function: $\phi^2(k)$}
-\label{sec:momentum_dist_funcs}
-
-We diagonalize the Hamiltonian for eigenvectors $\psi_{\alpha}$.
-In the $^3$S$_1$-$^3$D$_1$ coupled channel, the S-component is given by $\psi_{\alpha}[: \!
-N]$ and the D-component by $\psi_{\alpha}[N \!
-:]$ where $N$ is the length of the momentum mesh.
-Then the momentum distribution of the state $\alpha$ is given by,
-%
-\begin{eqnarray}
-	\label{eq:momentum_distribution}
-	|\phi_{\alpha}(k)|^2 = |\psi_{\alpha}[: \! N]|^2 + |\psi_{\alpha}[N \! :]|^2.
-\end{eqnarray}
-%
-This satisfies the normalization condition $\sum_{i=1}^N |\phi(k_i)|^2 = 1$, implying that the factor $k^2 dk$ (or in the discrete case, $k_i^2 w_i$) is factored into the wave function.
-For mesh-independent figures, divide by $k_i^2 w_i$.
+-- $\hat{r}^2$ operator.
 

### 2019-09-23 operators.py
Update operators.py
Generalized momentum_projection_operator to any channel, not just coupled-channels.

@@ -15,6 +15,8 @@
 # Revision history:
 #   08/07/19 --- Minor revisions to r^2 operator.
 #   08/22/19 --- Changed find_q_index function to use np.fabs() and .argmin()
+#   09/23/19 --- Generalized momentum_projection_operator to any channel, not
+#                just coupled-channels.
 #
 # Notes:
 #   * The operators here only work for the 3S1 - 3D1 coupled channel. This code
@@ -25,6 +27,8 @@
 
 import numpy as np
 from scipy.special import spherical_jn
+# Scripts made by A.T.
+from Potentials.vsrg_macos import load_save_potentials as lp
 
 
 def find_q_index(q, k_array):
@@ -54,7 +58,8 @@ def find_q_index(q, k_array):
     return q_index
 
 
-def momentum_projection_operator(q, k_array, k_weights, U=np.empty(0)):
+def momentum_projection_operator(q, k_array, k_weights, channel,
+                                 U=np.empty(0)):
     """
     ( a_q^dagger a_q ) momentum projection operator in momentum-space. When
     applied to a wave function, returns the wave function at momentum value q.
@@ -71,6 +76,10 @@ def momentum_projection_operator(q, k_array, k_weights, U=np.empty(0)):
         Momentum array.
     k_weights: 1-D ndarray
         Momentum weights.
+    channel : str
+        The partial wave channel ('1S0', '3S1', etc.) This allows the function
+        to distinguish whether the operator should work for coupled-channels or
+        not.
     U : 2-D ndarray, optional
         Unitary transformation matrix. If no unitary transformation is
         provided, the function will skip the line where it evolves the
@@ -98,18 +107,21 @@ def momentum_projection_operator(q, k_array, k_weights, U=np.empty(0)):
     #operator[q_index, q_index] = np.pi / ( 2 * q**2 * q_weight )
     #operator[q_index, q_index] = 1
     
-    # Matrix of zeros (m x m) for coupled-channel operator
-    o = np.zeros( (m, m) )
+    # Build coupled channel operator 
+    if lp.coupled_channel(channel):
     
-    # Build coupled channel operator
-    coupled_channel_operator = np.vstack( ( np.hstack( (operator, o) ),
-                                            np.hstack( (o, operator) ) ) )
+        # Matrix of zeros (m x m) for coupled-channel operator
+        o = np.zeros( (m, m) )
+    
+        # Build coupled channel operator
+        operator = np.vstack( ( np.hstack( (operator, o) ),
[…]

### 2019-09-23 run_srg.py
Ran SRG evolution on several potentials

@@ -137,13 +137,13 @@ if __name__ == '__main__':
     # Specify potential
     
     #kvnn = 6 # AV18
-    kvnn = 10 # EM N3LO
+    #kvnn = 10 # EM N3LO
     #kvnn = 105 # RKE N3LO at Lambda = 400 MeV
     #kvnn = 106 # RKE N3LO at Lambda = 450 MeV
     #kvnn = 107 # RKE N3LO at Lambda = 500 MeV
     #kvnn = 111 # RKE N4LO at Lambda = 450 MeV
     #kvnn = 112 # RKE N4LO at Lambda = 500 MeV
-    #kvnn = 222 # Gezerlis et al N2LO local potential at R_0 = 1.0 fm
+    kvnn = 222 # Gezerlis et al N2LO local potential at R_0 = 1.0 fm
     #kvnn = 224 # Gezerlis et al N2LO local potential at R_0 = 1.2 fm
     #kvnn = 900 # Wendt at Lambda = 4 fm^-1
     #kvnn = 901 # Wendt at Lambda = 9 fm^-1
@@ -155,8 +155,8 @@ if __name__ == '__main__':
     #channel = '3P0'
     
     #kmax = 30.0
-    kmax = 8.0
-    #kmax = 10.0
+    #kmax = 8.0
+    kmax = 10.0
     #kmax = 6.0
     
     #kmid = 4.0
@@ -175,20 +175,20 @@ if __name__ == '__main__':
     #generator = 'T'
     generator = 'Block-diag'
     
-    lambda_bd = 1.00 # This won't affect the band-diagonal generators
-    #lambda_bd = 1.50
+    #lambda_bd = 1.00 # This won't affect the band-diagonal generators
+    lambda_bd = 1.50
     #lambda_bd = 2.00 # Default
     #lambda_bd = 3.00
     #lambda_bd = 4.00
     #lambda_bd = 6.00
     
     #lambda_array = np.array( [10.0, 2.8, 2.0, 1.2] )
-    lambda_array = np.array( [6.0, 3.0, 2.0, 1.5] ) # Default
+    #lambda_array = np.array( [6.0, 3.0, 2.0, 1.5] ) # Default
     #lambda_array = np.array( [6.0, 3.0, 2.0, 1.5, 1.0] )
     #lambda_array = np.array( [2.8] )
     #lambda_array = np.array( [1.2] )
     #lambda_array = np.array( [10.0] )
-    #lambda_array = np.array( [1.0] )
[…]

### 2019-09-23 test.py
Update test.py
Ran SRG-evolution on several potentials.

@@ -30,17 +30,28 @@ import numpy as np
 from run_srg import run_srg
 
 
-kvnn = 902
+kvnn_list = [10, 106]
 # Could add the RKE 1-20 fm^-1 LO potentials as 903, 904, ...
-channel = '3S1'
-kmax = 30.0
-kmid = 4.0
+channel_list = ['1S0', '3S1', '1P1']
+kmax = 10.0
+kmid = 2.0
 ntot = 120
 
-lambda_array = np.array( [6.0, 3.0, 2.0, 1.5, 1.0] )
-generator_list = ['T']
+lambda_array = np.array( (6.0, 3.0, 2.0, 1.5, 1.0) )
+generator_list = ['Wegner', 'Block-diag']
 
-for generator in generator_list:
+for kvnn in kvnn_list:
+    for channel in channel_list:
+        for generator in generator_list:
     
-    d = run_srg(kvnn, channel, kmax, kmid, ntot, generator, lambda_array,
-                save=True)
+            if generator == 'Wegner':
+            
+                d = run_srg(kvnn, channel, kmax, kmid, ntot, generator,
+                            lambda_array, save=True)
+                
+            else:
+        
+                for lamb in lambda_array:
+            
+                    d = run_srg(kvnn, channel, kmax, kmid, ntot, generator,
+                                lambda_array, lambda_bd=lamb, save=True)

### 2019-09-24 Potentials/vsrg_macos/run_generate_vsrg_vlowk.pl
Generated EM N3LO, RKE N3LO, RKE N4LO potentials
Fixed the mesh to match Gezerlis et al. local potential: kmax = 10, kmid = 2 fm^-1 with nmod = 60 and ntot = 120.

@@ -48,7 +48,8 @@ $nsmooth = 0;     # integer smoothness parameter [exponent] (0 for SRG)
 $rsmooth = 0.00;  # real smoothness parameter [for non-exponential] (0.0 for SRG)
 
 # Set the momentum mesh parameters
-$nmod = 54;  # momentum points for low-k = P space (up to lambda for SRG)
+#$nmod = 54;  # momentum points for low-k = P space (up to lambda for SRG)
+$nmod = 60;
 #$nmod = 74; # changes made by AT to test SRG evolution of momentum projection operator
 #$ntot = 100; # setting in Anderson:2010aq
 $ntot = 120; # momentum points for P+Q = full = bare space
@@ -95,11 +96,11 @@ $kmid = 2.0;  # mesh goes from 0 to kmid, then kmid to kmax
 #     cutnum = 1,2,3,4--> 400, 450, 500, 550 MeV cutoff
 
 #@kvnns = (06); # Argonne v18
-@kvnns = (10); # Entem-Machleidt
+#@kvnns = (10); # Entem-Machleidt
 #@kvnns = (32); # Epelbaum
 #@kvnns = (90,91,92,93,95,96,97,98,100,101,102,103,105,106,107,108,110,111,112,113,115,116,117,118); # RKE semi-local potentials
 #@kvnns = (90); # RKE semi-local potential at LO with specified cutoff (unless changed it's 400 MeV)
-#@kvnns = (105,106,107,110,111,112); # RKE semi-local potential at N3LO and N4LO
+@kvnns = (105,106,107,110,111,112); # RKE semi-local potential at N3LO and N4LO
 
 # The following list is all of the semi-local EKM potentials
 #@kvnns = (40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,64);

### 2019-09-24 test.py
Generated SRG-evolved potentials
kvnns=10, 106
channels=1S0, 3S1, 1P1
generators=Wegner, block-diagonal up lamba=1 fm^-1.

@@ -31,7 +31,6 @@ from run_srg import run_srg
 
 
 kvnn_list = [10, 106]
-# Could add the RKE 1-20 fm^-1 LO potentials as 903, 904, ...
 channel_list = ['1S0', '3S1', '1P1']
 kmax = 10.0
 kmid = 2.0

### 2019-09-24 test.py
Update test.py
Comparing wave functions from different SRG-evolved potentials by looking at momentum distribution functions.

@@ -21,36 +21,106 @@
 #                momentum_projection_operator_testv1.py in Old_codes based off
 #                last tests in this script.
 #   09/10/19 --- Using this script to run SRG evolution on several potentials.
-#
+#   09/24/19 --- Comparing wave functions from different SRG-evolved potentials
+#                by looking at momentum distribution functions.
 #------------------------------------------------------------------------------
 
 
+import matplotlib.pyplot as plt
 import numpy as np
 # Scripts made by A.T.
-from run_srg import run_srg
+from Potentials.vsrg_macos import load_save_potentials as lp
+import observables as ob
+from SRG_codes.srg_unitary_transformation import SRG_unitary_transformation
 
 
+# --- Set up --- #
+
+# Potential details
 kvnn_list = [10, 106]
-channel_list = ['1S0', '3S1', '1P1']
+channel = '3S1'
 kmax = 10.0
 kmid = 2.0
 ntot = 120
 
-lambda_array = np.array( (6.0, 3.0, 2.0, 1.5, 1.0) )
-generator_list = ['Wegner', 'Block-diag']
+# SRG details
+generator = 'Wegner'
+lamb = 1.5
 
+# Deuteron energy in MeV
+eps = -2.22
+
+
+# --- Load wave functions, calculate momentum distribution, and store --- #
+
+d = {}
+d['init'] = {}
+d['srg'] = {}
 for kvnn in kvnn_list:
-    for channel in channel_list:
-        for generator in generator_list:
     
-            if generator == 'Wegner':
-            
-                d = run_srg(kvnn, channel, kmax, kmid, ntot, generator,
-                            lambda_array, save=True)
-                
-            else:
+    # Load momentum and weights
+    k_array, k_weights = lp.load_momentum(kvnn, channel, kmax, kmid, ntot)
+    
+    # Load initial Hamiltonian
+    H_initial = lp.load_hamiltonian(kvnn, channel, kmax, kmid, ntot)
+    
+    # Compute initial wave function
+    psi_initial = ob.wave_function(H_initial, eps)
+    u_initial = psi_initial[:ntot] # 3S1 component
+    w_initial = psi_initial[ntot:] # 3D1 component
+    
[…]

### 2019-09-25 Notes/Operator_evolution/operator_evolution.tex
Updated operator evolution draft
Minor addition.
Updated operator evolution notes
Changing the order of things in the introduction.

@@
 \noindent{%
-\textbf{Background on modern nuclear potentials.}
+\textbf{NN interaction and SRG decoupling.}
 }
-\\
--- Wide range of NN potentials.
-%
-% Add what you have from IMSRG paper.
-\begin{itemize}
-	\item Chiral EFT background.
-	\item Different potentials but give same $S$-matrix.
-\end{itemize}
-%
--- Implementation to many-body calculations and SRG decoupling.
 %
@@
 	\item RG transformations are used to soften the interaction to make many-body methods feasible. One such method, the SRG, also preserves observables from unitarity.
-	\item How do different potentials change under SRG transformations?
 \end{itemize}
@@
 \\
+\textbf{Background on modern nuclear potentials.}
+\\
+-- Wide range of NN potentials.
+%
+% Add what you have from IMSRG paper.
+\begin{itemize}
+	\item Chiral EFT background.
+	\item Different potentials but give same $S$-matrix.
+	\item How do different potentials change under SRG transformations?
+\end{itemize}
+%
 \textbf{Universality}
@@
 %
+-- Note, the unitary transformations and evolved wave functions for different potentials are not the same (at low momentum too) swhich implies that evolved operators cannot have the same universality property as the evolved potentials since they are dependent on the evolved wave functions.
+\\
 -- $\hat{r}^2$ operator.

### 2019-09-26 test.py
Update test.py
Minor change.

@@ -23,6 +23,7 @@
 #   09/10/19 --- Using this script to run SRG evolution on several potentials.
 #   09/24/19 --- Comparing wave functions from different SRG-evolved potentials
 #                by looking at momentum distribution functions.
+#
 #------------------------------------------------------------------------------
 
 

### 2019-09-27 Notes/Operator_evolution/operator_evolution.tex
Updated operator evolution draft
Wrote the introduction and swapped the Magnus and operator sections.

@@
 %	09/19/19 --- Added more bullets to section 2.
+%	09/27/19 --- Wrote the introduction and swapped the Magnus and operator sections.
 %
@@
 }
-%
-\begin{itemize}
-	\item Strong coupling between low- and high-momentum matrix elements in NN potentials.
-	\item Very difficult to implement these interactions in many-body methods using basis expansions. Matrix dimension becomes too large for accurate calculations.
-	\item RG transformations are used to soften the interaction to make many-body methods feasible. One such method, the SRG, also preserves observables from unitarity.
-\end{itemize}
-%
+\\
+The nuclear many-body problem has long been hindered by the short-range repulsive core and strong tensor force in nucleon-nucleon (NN) interactions leading to non-perturbative few- and many-body systems and strongly correlated wave functions.
+The Fourier transform of NN interactions gives rise to the coupling of low- and high-momentum modes, which is manifested as non-zero off-diagonal potential matrix elements.
+It is very difficult to implement these interactions in many-body methods using basis expansions, because the matrix dimension becomes too large for accurate calculations.
+Renormalization group (RG) methods can be used to soften the interaction to make many-body methods feasible.
+One such method, the similarity renormalization group (SRG), allows for a continuous change in resolution of the potential without changing the observables.
+More generally, the SRG can evolve any operator and wave function for consistent calculation of observables.
+\\
+
+\noindent{%
 \textbf{SRG formalism}
+}
 \\
--- The SRG decouples low- and high-momentum scales by applying a continuous unitary transformation $U(s)$ where $s=0 \rightarrow \infty$ is the flow parameter.
-\\
--- The `dressed' or evolved operator is given by
+The SRG decouples low- and high-momentum scales by applying a continuous unitary transformation $U(s)$ where $s=0 \rightarrow \infty$ is the flow parameter. The evolved operator is given by
 %
@@
 %
-where $O(0)$ corresponds to the `bare' operator.
-\\
--- Because $U(s)$ is unitary, the observables of the operator are preserved.
-\\
--- In practice, the unitary transformation U(s) is not explicitly solved for; the evolved operator is given by a differential flow equation which is obtained by taking the derivative of Eqn.
+where $O(0)$ corresponds to the initial operator.
+Because $U(s)$ is unitary, the observables of the operator are preserved.
+In practice, the unitary transformation U(s) is not explicitly solved for; the evolved operator is given by solving a differential flow equation which is obtained by taking the derivative of Eqn.
 (\ref{eq:srg_operator}),
@@
 where $\eta(s)=\frac{dU(s)}{ds} U^{\dagger}(s) = -\eta^{\dagger}(s)$ is the anti-hermitian SRG generator.
+The generator is defined as a commutator, $\eta(s) = [G, H(s)]$, where $G$ specifies the type of flow.
+The choice in $G$ determines the pattern of decoupling in the operator.
+By setting $G=H_D(s)$, the diagonal of the Hamiltonian, the operator is driven to band-diagonal form.
+This choice was implemented by Wegner in condensed matter physics \cite{Wegner:1994ab}.
+In a similar option used in nuclear physics, $G$ is set to the relative kinetic energy, $T_{rel}$, which also drives to band-diagonal form.
+In most cases, these two choices give the same evolved operators.
+In exceptional cases, which will be discussed later in the paper, the two band-diagonal choices can have drastically different behavior.
+For band-diagonal decoupling, it is convenient to define $\lambda \equiv s^{-1/4}$ which roughly measures the width of the band-diagonal in the decoupled operator.
+For block-diagonal decoupling, $G=P H(s) P + Q H(s) Q \equiv H_{BD}(s)$, where $P$ and $Q$ are low- and high-momentum projection operators, the operator is split into low- and high-momentum sub-blocks by specifying a separation in momentum $\Lambda$.
+These transformations are similar to V\textsubscript{low k} transformations \textcolor{red}{(references?)} but keep the high-momentum matrix elements non-zero, although entirely decoupled from the low-momentum sub-block.
+Generally the flow equation (\ref{eq:srg_flow}) is solved up to some finite value of $s$ with a high-order ODE solver.
+For notational convenience, we write the generators without the $s$ dependence in the rest of the paper.
 \\
--- The generator is defined as a commutator, $\eta(s) = [G, H(s)]$, where $G$ specifies the type of flow or form of the decoupled operator.
+
+\noindent{%
+\textbf{Background on modern nuclear potentials and universality.}
+}
 \\
--- By setting $G=H_D(s)$, the diagonal of the Hamiltonian, the operator is driven to band-diagonal form.
+There has been tremendous progress in development of NN interactions from chiral effective field theory ($\chi^{EFT}$) in the last decade.
+Previous SRG studies were limited to phenomenological interactions or some of the first non-local chiral interactions \cite{Entem:2003ft}, but with much more variance in modern chiral interactions, we would like to revisit the question of how different potentials and other operators change under SRG transformations.
+Since $\chi^{EFT}$ is an effective field theory, different potentials will still give the same $S$-matrix, that is, the potentials are phase equivalent up to some higher energy.
+However, the potentials themselves can differ in many ways such as the regulator functions, cutoff, order, and so forth, and thus, the potential matrix elements are not the same.
+Dainton \textit{et al.} \cite{Dainton:2013axa} demonstrated SRG transformations drive different NN potentials to the same low-momentum matrix elements, that is, a flow to universality up to the momentum value of phase inequivalence.
+We address the question of universality for modern chiral potentials as well as how other operators change with respect to the corresponding SRG transformations.
 \\
--- This choice was implemented by Wegner in condensed matter physics \cite{Wegner:1994ab}.
+
+\noindent{%
+\textbf{High cutoffs}
+}
 \\
--- In a similar option used in nuclear physics, $G$ is set to the relative kinetic energy, $T_{rel}$, which also drives to band-diagonal form.
-% Do I need to explain the intermediate step here?
+There has also been renewed interest in studying chiral interactions at high cutoffs \cite{Tews:2018sbi}.
+In spin-triplet channels and at leading-order (LO), taking the cutoff to high values can result in spurious, deeply bound states from a highly singular short-ranged tensor force.
+In principle, these deep bound states are outside the range of the EFT and are absorbed by counterterms at higher order.
+In \cite{Wendt:2011qj}, it was shown that band-diagonal SRG decoupling of NN potentials in partial waves with spurious bound states changes significantly depending on the choice of SRG generator.
+These high cutoff potentials provide a unique opportunity to understand some of the previous points about universality, the choice of SRG generator and decoupling, as well as a good test problem for a variant of the SRG, which utilizes the Magnus expansion \cite{Morris:2015yna}.
 \\
--- It is convenient to define $\lambda \equiv s^{-1/4}$ which roughly measures the width of the band-diagonal in the decoupled operator.
+
+\noindent{%
+\textbf{The Magnus expansion}
+}
 \\
--- For block-diagonal decoupling, denoted $G=H_{BD}(s)$, the operator is split into low- and high-momentum sub-blocks by specifying a separation in momentum $\Lambda_{BD}$.
+The Magnus expansion gives the SRG the capability to solve for the unitary transformation explicitly which can then be applied to any other operator of interest.
+This offers a huge numerical simplification in Fock-space where the matrix size of operators can become very large.
+The Magnus expansion is often used in in-medium SRG (IMSRG) calculations to solve the nuclear many-body problem directly.
+In some IMSRG calculations, intruder states can shift to the energy scale of the reference state in valence-space and severely distort low-energy properties.
+It is not understood how the IMSRG procedure evolves intruder state systems.
+Due to the prominence of the Magnus expansion in IMSRG, one must first understand if the Magnus approach matches the typical approach for difficult systems before investigating the intruder state problem.
+For this reason, NN potentials with spurious bound states offer a good test laboratory for the Magnus implementation to better understand if the Magnus is equivalent to the SRG approach.
 \\
--- These transformations are similar to $V_{low k}$ Lee-Suzuki transformations but keep the high-momentum matrix elements non-zero, although entirely decoupled from the low-momentum sub-block.
-\\
--- Generally the flow equation (\ref{eq:srg_flow}) is solved up to some finite value of $s$ with a high-order ODE solver.
-\\
--- For notational convenience, we write the generators without the $s$ dependence in the rest of the paper.
-\\
-\textbf{Background on modern nuclear potentials.}
-\\
--- Wide range of NN potentials.
-%
-% Add what you have from IMSRG paper.
-\begin{itemize}
-	\item Chiral EFT background.
-	\item Different potentials but give same $S$-matrix.
-	\item How do different potentials change under SRG transformations?
-\end{itemize}
-%
-\textbf{Universality}
-\\
-% Try to understand this better. Ask DF.
--- The explicit long-range physics should be the same.
-Decoupling low- and high-energy gives matching low-energy matrix elements.
-In the NN potential, this means softened NN interactions should have the same low-momentum matrix elements after sufficient decoupling.
-\\
--- Add takeaways from Dainton: phase shift equivalence implies matrix element equivalence for $\lambda$ approaching the momenta of phase equivalence.
-Correct binding energy is critical or the lowest matrix elements will not match.
-\\
--- Motivate long list of unaddressed questions: regulator, generator dependence, high cutoffs, the Magnus expansion.
-%
-\begin{itemize}
-	\item Regulator. Functional dependence of regulator. Reasons for implementing each.
-	\item Generators. Band- and block-diagonal transformations.
-	\item High cutoffs. Cite Nogga, Wendt, and Tews papers.
-	\item The Magnus expansion. High cutoffs and connection to IMSRG intruder state problem.
-\end{itemize}
-%
-\textbf{Operator evolution}
-\\
--- State how a potential and wave function changes: how does this affect other operators?
-\\
--- Operator evolution for different potentials (regulators, chiral order, etc.)
-\\
--- How operators evolve from band- and block-diagonal SRG transformations.
-\\
+
+\noindent{%
 \textbf{Overview of sections.}
+}
 
@@
 
+% Summarize what we're looking at in this section and general conclusions. What did I not cover in the introduction?
+%
 \noindent{%
@@
 \\
--- Comparison of potential evolution with different regulators, orders, generators.
+-- Comparison of potential evolution with different potentials and SRG generators.
 \\
 -- Universality.
-\\
--- Discussion of high cutoffs, block-diagonal generator at high cutoffs, and how it handles spurious bound states.
-\\
--- Use high cutoffs to transition to Magnus test problem.
 \\
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Evolution of other operators}
+\label{sec:evolution_other_operators}
+
+\noindent{%
+-- SRG operator evolution for different potentials and generators.
+}
+\\
+-- General questions to address: universality for operators, different generators.
+\\
+-- Momentum projection operator.
 %
+\begin{itemize}
+	\item Contours and general behavior: SRG transformation shifts strength of operator to low-momentum.
+	\item Deuteron momentum distributions. Why does this make sense with the transformed operators?
+	\item Diagonals and far off-diagonals. Universality.
+	\item Same questions but with figures of the integrand.
+\end{itemize}
+%
+-- Note, the unitary transformations and evolved wave functions for different potentials are not the same (at low momentum too) swhich implies that evolved operators cannot have the same universality property as the evolved potentials since they are dependent on the evolved wave functions.
+\\
+-- $\hat{r}^2$ operator.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{High cutoffs and the Magnus expansion}
+\label{sec:magnus_expansion}
+
 \noindent{%
@@
 	\item Spurious bound state(s).
-	\item Discussion on how the block-diagonal generator handles spurious bound states. Where they are ``decoupled'' in the matrix compared to Wegner.
 	\item Transition to Magnus expansion.
@@
 %
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Magnus expansion}
-\label{sec:magnus_expansion}
-
-\noindent{%
--- Connection to IMSRG intruder state.
-}
 
@@
 \\
--- Use discussion of operator evolution to transition to next section.
+-- Discussion on how the block-diagonal generator handles spurious bound states. Where they are ``decoupled'' in the matrix compared to Wegner. One figure to show this?
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Evolution of other operators}
-\label{sec:evolution_other_operators}
-
-\noindent{%
--- SRG operator evolution for different potentials and generators.
-}
-\\
--- General questions to address: universality for operators, different generators.
-\\
--- Momentum projection operator.
-%
-\begin{itemize}
-	\item Contours and general behavior: SRG transformation shifts strength of operator to low-momentum.
-	\item Deuteron momentum distributions. Why does this make sense with the transformed operators?
-	\item Diagonals and far off-diagonals. Universality.
-	\item Same questions but with figures of the integrand.
-\end{itemize}
-%
--- Note, the unitary transformations and evolved wave functions for different potentials are not the same (at low momentum too) swhich implies that evolved operators cannot have the same universality property as the evolved potentials since they are dependent on the evolved wave functions.
-\\
--- $\hat{r}^2$ operator.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}

### 2019-09-27 Notes/Operator_evolution/operator_evolution.tex
Added a couple momentum projection operator figures to the notes

@@
 \\
+-- Give relevant equations. Unitary transformation equation.
+\\
 -- Momentum projection operator.
+\\
+-- Relevant equations: just the momentum projection operator in momentum-space.
 %
@@
 %
--- Note, the unitary transformations and evolved wave functions for different potentials are not the same (at low momentum too) swhich implies that evolved operators cannot have the same universality property as the evolved potentials since they are dependent on the evolved wave functions.
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/momentum_projection_diag_q3,00_3S1_kvnns_10_106_222_lamb1,5}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/momentum_projection_off-diag_q3,00_3S1_kvnns_10_106_222_lamb1,5}%
+	}
+	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the momentum projection operator under SRG transformations with EM N$^3$LO (black), RKE N$^3$LO (red) and Gezerlis et al.
+N$^2$LO (blue) potentials evolving right to left with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^3$S$_1$ channel.
+Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution.
+For block-diagonal evolution, we fix $\lambda=1.5$ fm$^{-1}$.}
+	\label{fig:momentum_proj_3S1}
+\end{figure}
+%
+-- Note, the unitary transformations and evolved wave functions for different potentials are not the same (at low momentum too) which implies that evolved operators cannot have the same universality property as the evolved potentials since they are dependent on the evolved wave functions.
 \\
 -- $\hat{r}^2$ operator.
+\\
+-- Relevant equations: operator in coordinate-space and Hankel transformation.
 

### 2019-10-21 Notes/Operator_evolution/operator_evolution.tex
Update operator_evolution.tex
Added a minor comment at the beginning of section 2.
Updated operator_evolution.tex
Commented out a paragraph and a figure. Updated some figures from RKE N3LO to N4LO.

@@
 %	08/28/19 --- Started outlining and added pieces from old notes.
-%	09/09/19 --- Added more bullets to the introduction. Further organization.
-%	09/19/19 --- Added more bullets to section 2.
+%	09/19/19 --- Added more bullets up through section 2.
 %	09/27/19 --- Wrote the introduction and swapped the Magnus and operator sections.
@@
 
-\noindent{%
-\textbf{NN interaction and SRG decoupling.}
-}
-\\
-The nuclear many-body problem has long been hindered by the short-range repulsive core and strong tensor force in nucleon-nucleon (NN) interactions leading to non-perturbative few- and many-body systems and strongly correlated wave functions.
+% Unnecessary paragraph.
+%\noindent{%
+%\textbf{NN interaction and SRG decoupling.}
+%}
+%\\
+%The nuclear many-body problem has long been hindered by the short-range repulsive core and strong tensor force in nucleon-nucleon (NN) interactions leading to non-perturbative few- and many-body systems and strongly correlated wave functions.
 The Fourier transform of NN interactions gives rise to the coupling of low- and high-momentum modes, which is manifested as non-zero off-diagonal potential matrix elements.
@@
 More generally, the SRG can evolve any operator and wave function for consistent calculation of observables.
+%\\
+
+\noindent{%
+\textbf{Modern nuclear potentials and universality.}
+}
+\\
+There has been tremendous progress in development of NN interactions from chiral effective field theory ($\chi^{EFT}$) in the last decade.
+Previous SRG studies were limited to phenomenological interactions or some of the first non-local chiral interactions \cite{Entem:2003ft}, but with much more variance in modern chiral interactions, we would like to revisit the question of how different potentials and other operators change under SRG transformations.
+Since $\chi^{EFT}$ is an effective field theory, different potentials will still give the same $S$-matrix, that is, the potentials are phase equivalent up to some higher energy.
+However, the potentials themselves can differ in many ways such as the regulator functions, cutoff, order, and so forth, and thus, the potential matrix elements are not the same.
+Dainton \textit{et al.} \cite{Dainton:2013axa} demonstrated SRG transformations drive different NN potentials to the same low-momentum matrix elements, that is, a flow to universality up to the momentum value of phase inequivalence.
+We address the question of universality for modern chiral potentials as well as how other operators change with respect to the corresponding SRG transformations.
 \\
@@
 \\
+% Reword this section to be consistent with conclusions: decoupling and operator evolution.
 The SRG decouples low- and high-momentum scales by applying a continuous unitary transformation $U(s)$ where $s=0 \rightarrow \infty$ is the flow parameter. The evolved operator is given by
@@
 For notational convenience, we write the generators without the $s$ dependence in the rest of the paper.
-\\
-
-\noindent{%
-\textbf{Background on modern nuclear potentials and universality.}
-}
-\\
-There has been tremendous progress in development of NN interactions from chiral effective field theory ($\chi^{EFT}$) in the last decade.
-Previous SRG studies were limited to phenomenological interactions or some of the first non-local chiral interactions \cite{Entem:2003ft}, but with much more variance in modern chiral interactions, we would like to revisit the question of how different potentials and other operators change under SRG transformations.
-Since $\chi^{EFT}$ is an effective field theory, different potentials will still give the same $S$-matrix, that is, the potentials are phase equivalent up to some higher energy.
-However, the potentials themselves can differ in many ways such as the regulator functions, cutoff, order, and so forth, and thus, the potential matrix elements are not the same.
-Dainton \textit{et al.} \cite{Dainton:2013axa} demonstrated SRG transformations drive different NN potentials to the same low-momentum matrix elements, that is, a flow to universality up to the momentum value of phase inequivalence.
-We address the question of universality for modern chiral potentials as well as how other operators change with respect to the corresponding SRG transformations.
 \\
@@
 \\
--- Fig.~\ref{fig:potential_contours_RKE_Wegner} illustrates the SRG in a nutshell.
-Here, we evolve three partial wave channels of RKE N$^3$LO \cite{Reinert:2017usi} where the cutoff $\Lambda=450$ MeV to $\lambda=1.5$ fm$^{-1}$.
+%-- Fig.~\ref{fig:potential_contours_RKE_Wegner} illustrates the SRG in a nutshell.
+Here, we evolve three partial wave channels of RKE N$^4$LO \cite{Reinert:2017usi} where the cutoff $\Lambda=450$ MeV to $\lambda=1.5$ fm$^{-1}$.
 We see that the off-diagonal elements of the potential approach zero and the potential is driven to band-diagonal form.
 %
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_1S0_Wegner_channel_label}%
-	}
+% Unnecessary figure.
+%\begin{figure}[H]
+%	\centering
+%	\subfloat[]{%
+%	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn111_1S0_Wegner_channel_label}%
+%	}
 
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_3S1_Wegner_channel_label}%
-	}
+%	\subfloat[]{%
+%	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn111_3S1_Wegner_channel_label}%
+%	}
 
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_1P1_Wegner_channel_label}%
-	}
-	\caption{Matrix elements of the RKE N$^3$LO potential SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator in the $^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) channels.}
-	\label{fig:potential_contours_RKE_Wegner}
-\end{figure}
+%	\subfloat[]{%
+%	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn111_1P1_Wegner_channel_label}%
+%	}
+%	\caption{Matrix elements of the RKE N$^4$LO potential SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator in the $^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) channels.}
+%	\label{fig:potential_contours_RKE_Wegner}
+%\end{figure}
 %
 \noindent{%
--- In Fig.~\ref{fig:potential_contours_3S1_Wegner} we consider three different SRG-evolved potentials in the $^3$S$_1$ channel: EM N$^3$LO (500 MeV cutoff) \cite{Entem:2003ft}, RKE N$^3$LO (450 MeV cutoff) \cite{Reinert:2017usi}, and Gezerlis et al.
+-- In Fig.~\ref{fig:potential_contours_3S1_Wegner} we consider three different SRG-evolved potentials in the $^3$S$_1$ channel: EM N$^3$LO (500 MeV cutoff) \cite{Entem:2003ft}, RKE N$^4$LO (450 MeV cutoff) \cite{Reinert:2017usi}, and Gezerlis et al.
 N$^2$LO (1 fm cutoff) \cite{Gezerlis:2014zia}.
@@
 However, a non-local regulator function for pion-exchange contributions can introduce regulator artifacts for cutoffs $\Lambda$ lower than the breakdown scale $\Lambda_b$.
-Several semi-local chiral potentials have been introduced to reduce regulator artifacts, such as the RKE N$^3$LO potential.
+Several semi-local chiral potentials have been introduced to reduce regulator artifacts, such as the RKE N$^4$LO potential.
 Here, a local regulator function is applied for the long-range interactions in momentum-space, while a non-local regulator function is used for the short-range interactions.
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_3S1_Wegner_potential_label}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn111_3S1_Wegner_potential_label}%
 	}
@@
 	}
-	\caption{Matrix elements of the EM N$^3$LO (a), RKE N$^3$LO (b), and Gezerlis et al.
+	\caption{Matrix elements of the EM N$^3$LO (a), RKE N$^4$LO (b), and Gezerlis et al.
 N$^2$LO (c) potentials SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator in the $^3$S$_1$ channel.}
@@
 \noindent{%
--- Fig.~\ref{fig:potential_contours_3S1_RKE} shows the SRG-evolved RKE N$^3$LO (450 MeV cutoff) potential in the $^3$S$_1$ channel for two SRG generators: the Wegner and block-diagonal generators which drive the potential to band- and block-diagonal form, respectively.
+-- Fig.~\ref{fig:potential_contours_1P1_RKE} shows the SRG-evolved RKE N$^4$LO (450 MeV cutoff) potential in the $^1$P$_1$ channel for two SRG generators: the Wegner and block-diagonal generators which drive the potential to band- and block-diagonal form, respectively.
 We continue to evolve to band-diagonal form with respect to the parameter $\lambda$, but for the block-diagonal generator, we label sub-plots with the parameter $\Lambda$ which characterizes the sharp cutoff in decoupling the low- and high-momentum matrix elements.
@@
 \\
--- Takeaways from Fig.~\ref{fig:potential_contours_3S1_RKE}: smooth decoupling for Wegner and sharp for block-diagonal, each unique generator should have its own type of universality.
+-- Takeaways from Fig.~\ref{fig:potential_contours_1P1_RKE}: smooth decoupling for Wegner and sharp for block-diagonal, each unique generator should have its own type of universality.
 Check this more quantitatively by comparing matrix element ``slices''.
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_3S1_Wegner_generator_label}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn111_1P1_Wegner_generator_label}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_3S1_Block-diag_generator_label}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn111_1P1_Block-diag_generator_label}%
 	}
-	\caption{Matrix elements of the RKE N$^3$LO potential SRG-evolving right to left under transformations with Wegner (a) and block-diagonal (b) generators in the $^3$S$_1$ channel.
+	\caption{Matrix elements of the RKE N$^4$LO potential SRG-evolving right to left under transformations with Wegner (a) and block-diagonal (b) generators in the $^1$P$_1$ channel.
 Here, we use $\lambda$ for Wegner evolution in the top row and $\Lambda$ for block-diagonal evolution in the bottom row.
 For block-diagonal evolution, we fix $\lambda=1.5$ fm$^{-1}$.}
-	\label{fig:potential_contours_3S1_RKE}
+	\label{fig:potential_contours_1P1_RKE}
 \end{figure}
@@
 \noindent{%
--- Fig.~\ref{fig:phase_shifts} shows the NN phase shifts of EM N$^3$LO, RKE N$^3$LO, and Gezerlis et al.
+-- Fig.~\ref{fig:phase_shifts} shows the NN phase shifts of EM N$^3$LO, RKE N$^4$LO, and Gezerlis et al.
 N$^2$LO potentials in the $^1$S$_0$, $^3$S$_1$, and $^1$P$_1$ channels.
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_1S0_kvnns_10_106_222}%
+	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_1S0_kvnns_10_111_222}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_3S1_kvnns_10_106_222}%
+	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_3S1_kvnns_10_111_222}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_1P1_kvnns_10_106_222}%
+	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_1P1_kvnns_10_111_222}%
 	}
-	\caption{$^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) phase shifts for the EM N$^3$LO (solid black), RKE N$^3$LO (red dash-dotted), and Gezerlis et al. N$^2$LO (blue dashed) potentials.}
+	\caption{$^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) phase shifts for the EM N$^3$LO (solid black), RKE N$^4$LO (red dash-dotted), and Gezerlis et al. N$^2$LO (blue dashed) potentials.}
 	\label{fig:phase_shifts}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_1S0_kvnns_10_106_222_lamb1,0}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_1S0_kvnns_10_111_222_lamb1,0}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_1S0_kvnns_10_106_222_lamb1,0}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_1S0_kvnns_10_111_222_lamb1,0}%
 	}
-	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the EM N$^3$LO (black), RKE N$^3$LO (red) and Gezerlis et al.
+	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the EM N$^3$LO (black), RKE N$^4$LO (red) and Gezerlis et al.
 N$^2$LO (blue) potentials SRG-evolving right to left under transformations with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^1$S$_0$ channel.
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_3S1_kvnns_10_106_222_lamb1,0}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_3S1_kvnns_10_111_222_lamb1,0}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_3S1_kvnns_10_106_222_lamb1,0}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_3S1_kvnns_10_111_222_lamb1,0}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_1P1_kvnns_10_106_222_lamb1,0}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_1P1_kvnns_10_111_222_lamb1,0}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_1P1_kvnns_10_106_222_lamb1,0}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_1P1_kvnns_10_111_222_lamb1,0}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/momentum_projection_diag_q3,00_3S1_kvnns_10_106_222_lamb1,5}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/momentum_projection_diag_q3,00_3S1_kvnns_10_111_222_lamb1,5}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/momentum_projection_off-diag_q3,00_3S1_kvnns_10_106_222_lamb1,5}%
+	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/momentum_projection_off-diag_q3,00_3S1_kvnns_10_111_222_lamb1,5}%
 	}
-	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the momentum projection operator under SRG transformations with EM N$^3$LO (black), RKE N$^3$LO (red) and Gezerlis et al.
+	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the momentum projection operator under SRG transformations with EM N$^3$LO (black), RKE N$^4$LO (red) and Gezerlis et al.
 N$^2$LO (blue) potentials evolving right to left with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^3$S$_1$ channel.

### 2019-10-24 operators.py
Update operators.py
Might try mpmath Bessel functions.

@@ -27,6 +27,7 @@
 
 import numpy as np
 from scipy.special import spherical_jn
+#from mpmath import besselj
 # Scripts made by A.T.
 from Potentials.vsrg_macos import load_save_potentials as lp
 

### 2019-10-25 run_srg.py
Update run_srg.py
Generated SRG-evolved potentials.

@@ -155,8 +155,8 @@ if __name__ == '__main__':
     #channel = '3P0'
     
     #kmax = 30.0
-    #kmax = 8.0
-    kmax = 10.0
+    kmax = 8.0
+    #kmax = 10.0
     #kmax = 6.0
     
     #kmid = 4.0
@@ -171,12 +171,12 @@ if __name__ == '__main__':
     
     # Specify evolution
     
-    generator = 'Wegner'
+    #generator = 'Wegner'
     #generator = 'T'
-    #generator = 'Block-diag'
+    generator = 'Block-diag'
     
-    #lambda_bd = 1.00 # This won't affect the band-diagonal generators
-    lambda_bd = 1.50
+    lambda_bd = 1.00 # This won't affect the band-diagonal generators
+    #lambda_bd = 1.50
     #lambda_bd = 2.00 # Default
     #lambda_bd = 3.00
     #lambda_bd = 4.00

### 2019-10-25 test.py
Update test.py
Trying a different Lambda_BD value and doing a scattering state.

@@ -52,11 +52,12 @@ lamb = 1.5
 #lamb = 1.0
 #lamb = 3.0
 #lamb = 6.0
-Lamb = 2.0
-#Lamb = 3.0
+#Lamb = 2.0
+Lamb = 3.0
 #Lamb = 1.5
 
-eps = -2.22
+#eps = -2.22
+eps = 200.0
 
 # Load initial Hamiltonian (and momentum)
 k_array, k_weights = lp.load_momentum(kvnn, channel, kmax, kmid, ntot)

### 2019-10-28 Notes/Operator_evolution/operator_evolution.tex
Update operator_evolution.tex
Added a bullet point to operator evolution section.
Updated operator_evolution notes
Minor changes.

@@
 However, the potentials themselves can differ in many ways such as the regulator functions, cutoff, order, and so forth, and thus, the potential matrix elements are not the same.
-Dainton \textit{et al.} \cite{Dainton:2013axa} demonstrated SRG transformations drive different NN potentials to the same low-momentum matrix elements, that is, a flow to universality up to the momentum value of phase inequivalence.
+Dainton \textit{et al.}~\cite{Dainton:2013axa} demonstrated SRG transformations drive different NN potentials to the same low-momentum matrix elements, that is, a flow to universality up to the momentum value of phase inequivalence.
 We address the question of universality for modern chiral potentials as well as how other operators change with respect to the corresponding SRG transformations.
@@
 \noindent{%
--- In Fig.~\ref{fig:potential_contours_3S1_Wegner} we consider three different SRG-evolved potentials in the $^3$S$_1$ channel: EM N$^3$LO (500 MeV cutoff) \cite{Entem:2003ft}, RKE N$^4$LO (450 MeV cutoff) \cite{Reinert:2017usi}, and Gezerlis et al.
-N$^2$LO (1 fm cutoff) \cite{Gezerlis:2014zia}.
+-- In Fig.~\ref{fig:potential_contours_3S1_Wegner} we consider three different SRG-evolved potentials in the $^3$S$_1$ channel: EM N$^3$LO (500 MeV cutoff) \cite{Entem:2003ft}, RKE N$^4$LO (450 MeV cutoff) \cite{Reinert:2017usi}, and Gezerlis et al.~N$^2$LO (1 fm cutoff) \cite{Gezerlis:2014zia}.
 The major difference in these three potentials are the regulator functions in the contact and pion-exchange terms.
@@
 In some instances, non-local interactions are not suitable for $\textit{ab initio}$ approaches such as the quantum Monte Carlo (QMC) method motivating the need for fully local potentials.
-The Gezerlis et al.
-N$^2$LO potential is an example of a local interaction where the long-range terms have a local regulator function in coordinate-space and the short-range terms have a local regulator function in momentum-space.
+The Gezerlis et al.~N$^2$LO potential is an example of a local interaction where the long-range terms have a local regulator function in coordinate-space and the short-range terms have a local regulator function in momentum-space.
 }
@@
 	}
-	\caption{Matrix elements of the EM N$^3$LO (a), RKE N$^4$LO (b), and Gezerlis et al.
-N$^2$LO (c) potentials SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator in the $^3$S$_1$ channel.}
+	\caption{Matrix elements of the EM N$^3$LO (a), RKE N$^4$LO (b), and Gezerlis et al.~N$^2$LO (c) potentials SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator in the $^3$S$_1$ channel.}
 	\label{fig:potential_contours_3S1_Wegner}
@@
 \noindent{%
--- Fig.~\ref{fig:phase_shifts} shows the NN phase shifts of EM N$^3$LO, RKE N$^4$LO, and Gezerlis et al.
-N$^2$LO potentials in the $^1$S$_0$, $^3$S$_1$, and $^1$P$_1$ channels.
+-- Fig.~\ref{fig:phase_shifts} shows the NN phase shifts of EM N$^3$LO, RKE N$^4$LO, and Gezerlis et al.~N$^2$LO potentials in the $^1$S$_0$, $^3$S$_1$, and $^1$P$_1$ channels.
 In \cite{Dainton:2013axa}, it was found that phase equivalence up to some value of momentum $k$ implies matrix element equivalence up to the same value of $k$ in SRG-evolved potentials.
@@
 	}
-	\caption{$^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) phase shifts for the EM N$^3$LO (solid black), RKE N$^4$LO (red dash-dotted), and Gezerlis et al. N$^2$LO (blue dashed) potentials.}
+	\caption{$^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) phase shifts for the EM N$^3$LO (solid black), RKE N$^4$LO (red dash-dotted), and Gezerlis et al.~N$^2$LO (blue dashed) potentials.}
 	\label{fig:phase_shifts}
@@
 	}
-	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the EM N$^3$LO (black), RKE N$^4$LO (red) and Gezerlis et al.
-N$^2$LO (blue) potentials SRG-evolving right to left under transformations with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^1$S$_0$ channel.
+	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the EM N$^3$LO (black), RKE N$^4$LO (red) and Gezerlis et al.~N$^2$LO (blue) potentials SRG-evolving right to left under transformations with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^1$S$_0$ channel.
 Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution.
@@
 	}
-	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the momentum projection operator under SRG transformations with EM N$^3$LO (black), RKE N$^4$LO (red) and Gezerlis et al.
-N$^2$LO (blue) potentials evolving right to left with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^3$S$_1$ channel.
+	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the momentum projection operator under SRG transformations with EM N$^3$LO (black), RKE N$^4$LO (red) and Gezerlis et al.~N$^2$LO (blue) potentials evolving right to left with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^3$S$_1$ channel.
 Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution.
@@
 -- Relevant equations: operator in coordinate-space and Hankel transformation.
+\\
+-- Add continuum state momentum distributions and how to understand operator evolution. If
 

### 2019-10-30 Notes/Operator_evolution/operator_evolution.tex
Update operator_evolution.tex

@@
 \noindent{%
-\textbf{Modern nuclear potentials and universality.}
+\textbf{Modern nuclear potentials and universality}
 }
 \\
-There has been tremendous progress in development of NN interactions from chiral effective field theory ($\chi^{EFT}$) in the last decade.
-Previous SRG studies were limited to phenomenological interactions or some of the first non-local chiral interactions \cite{Entem:2003ft}, but with much more variance in modern chiral interactions, we would like to revisit the question of how different potentials and other operators change under SRG transformations.
+There has been rapid development of new NN interactions from chiral effective field theory ($\chi^{EFT}$) in the last decade.
+Previous SRG studies were limited to phenomenological interactions or some of the first non-local chiral interactions \cite{Entem:2003ft}, but with much more variety in modern chiral interactions, we would like to revisit the question of how different potentials and other operators change under SRG transformations.
 Since $\chi^{EFT}$ is an effective field theory, different potentials will still give the same $S$-matrix, that is, the potentials are phase equivalent up to some higher energy.
@@
 We address the question of universality for modern chiral potentials as well as how other operators change with respect to the corresponding SRG transformations.
+\\
+
+% Add something on operator evolution.
+The decoupling of matrix elements will not necessarily hold in other operators as it does in the Hamiltonian.
+In a previous work \cite{Anderson:2010aq}, it was shown that SRG transformations induce low-momentum contributions in high-momentum operators and change very little in low-momentum operators.
+What are the main questions here?
+How do we look into these questions?
 \\
@@
 % Reword this section to be consistent with conclusions: decoupling and operator evolution.
-The SRG decouples low- and high-momentum scales by applying a continuous unitary transformation $U(s)$ where $s=0 \rightarrow \infty$ is the flow parameter. The evolved operator is given by
+The SRG decouples low- and high-momentum scales in the Hamiltonian by applying a continuous unitary transformation $U(s)$ where $s=0 \rightarrow \infty$ is the flow parameter.
+An evolved operator is given by
 %
@@
 where $\eta(s)=\frac{dU(s)}{ds} U^{\dagger}(s) = -\eta^{\dagger}(s)$ is the anti-hermitian SRG generator.
-The generator is defined as a commutator, $\eta(s) = [G, H(s)]$, where $G$ specifies the type of flow.
-The choice in $G$ determines the pattern of decoupling in the operator.
-By setting $G=H_D(s)$, the diagonal of the Hamiltonian, the operator is driven to band-diagonal form.
+The generator is defined as a commutator, $\eta(s) = [G, H(s)]$, where $G$ specifies the type of flow and $H(s)$ is the evolved Hamiltonian.
+The choice in $G$ determines the pattern of decoupling in the Hamiltonian.
+By setting $G=H_D(s)$, the diagonal of the Hamiltonian, the Hamiltonian is driven to band-diagonal form.
 This choice was implemented by Wegner in condensed matter physics \cite{Wegner:1994ab}.
@@
 These transformations are similar to V\textsubscript{low k} transformations \textcolor{red}{(references?)} but keep the high-momentum matrix elements non-zero, although entirely decoupled from the low-momentum sub-block.
-Generally the flow equation (\ref{eq:srg_flow}) is solved up to some finite value of $s$ with a high-order ODE solver.
+Generally, the flow equation (\ref{eq:srg_flow}) is solved up to some finite value of $s$ with a high-order ODE solver.
 For notational convenience, we write the generators without the $s$ dependence in the rest of the paper.

### 2019-11-04 Notes/Operator_evolution/operator_evolution.tex
Updated operator evolution draft
Edited the introduction and added a bit more on operator evolution.

@@
 
-\noindent{%
-\textbf{Modern nuclear potentials and universality}
-}
-\\
-There has been rapid development of new NN interactions from chiral effective field theory ($\chi^{EFT}$) in the last decade.
+Nuclear physics has seen a massive increase in the number of new NN interactions from chiral effective field theory ($\chi^{EFT}$) in the last decade.
 Previous SRG studies were limited to phenomenological interactions or some of the first non-local chiral interactions \cite{Entem:2003ft}, but with much more variety in modern chiral interactions, we would like to revisit the question of how different potentials and other operators change under SRG transformations.
@@
 
-% Add something on operator evolution.
-The decoupling of matrix elements will not necessarily hold in other operators as it does in the Hamiltonian.
-In a previous work \cite{Anderson:2010aq}, it was shown that SRG transformations induce low-momentum contributions in high-momentum operators and change very little in low-momentum operators.
-What are the main questions here?
-How do we look into these questions?
-\\
-
-\noindent{%
-\textbf{SRG formalism}
-}
-\\
-% Reword this section to be consistent with conclusions: decoupling and operator evolution.
 The SRG decouples low- and high-momentum scales in the Hamiltonian by applying a continuous unitary transformation $U(s)$ where $s=0 \rightarrow \infty$ is the flow parameter.
@@
 The choice in $G$ determines the pattern of decoupling in the Hamiltonian.
+\\
+
 By setting $G=H_D(s)$, the diagonal of the Hamiltonian, the Hamiltonian is driven to band-diagonal form.
@@
 In a similar option used in nuclear physics, $G$ is set to the relative kinetic energy, $T_{rel}$, which also drives to band-diagonal form.
-In most cases, these two choices give the same evolved operators.
+In most cases, these two choices give the same evolved operators \textcolor{red}{(check that is true for momentum projection operator and $r^2$ operator)}.
 In exceptional cases, which will be discussed later in the paper, the two band-diagonal choices can have drastically different behavior.
 For band-diagonal decoupling, it is convenient to define $\lambda \equiv s^{-1/4}$ which roughly measures the width of the band-diagonal in the decoupled operator.
-For block-diagonal decoupling, $G=P H(s) P + Q H(s) Q \equiv H_{BD}(s)$, where $P$ and $Q$ are low- and high-momentum projection operators, the operator is split into low- and high-momentum sub-blocks by specifying a separation in momentum $\Lambda$.
-These transformations are similar to V\textsubscript{low k} transformations \textcolor{red}{(references?)} but keep the high-momentum matrix elements non-zero, although entirely decoupled from the low-momentum sub-block.
+For block-diagonal decoupling,
+%
+\begin{eqnarray}
+	\label{eq:block_diag_g}
+	G =
+	\begin{pmatrix}
+		PH(s)P & 0 \\
+		0 & QH(s)Q \\
+	\end{pmatrix}
+	\equiv H_{BD}(s),
+\end{eqnarray}
+%
+where $P$ and $Q$ are low- and high-momentum projection operators, the Hamiltonian is split into low- and high-momentum sub-blocks by specifying a separation in momentum $\Lambda$ and taking $s \rightarrow \infty$.
+In momentum-space, the projection operators are step functions defined by the sharp cutoff in $\Lambda$.
+These transformations are similar to V\textsubscript{low $k$} transformations \cite{Bogner:2001gq, Bogner:2001jn, Bogner:2003wn} but keep the high-momentum matrix elements non-zero, although entirely decoupled from the low-momentum sub-block.
 Generally, the flow equation (\ref{eq:srg_flow}) is solved up to some finite value of $s$ with a high-order ODE solver.
@@
 
-\noindent{%
-\textbf{High cutoffs}
-}
+The decoupling of matrix elements does not necessarily hold in other operators as it does in the Hamiltonian.
+In a previous work \cite{Anderson:2010aq}, it was shown that SRG transformations induce low-momentum contributions in high-momentum operators and change very little in low-momentum operators.
+We apply SRG band- and block-diagonal transformations to other operators from building the unitary transformations explicitly using the eigenvectors of the initial and evolved Hamiltonians.
+SRG-evolved operators depend on the NN interaction despite having the same initial operator, since the flow equation (\ref{eq:srg_flow}) depends on $H(s)$ from the definition of $\eta(s)$.
 \\
+
 There has also been renewed interest in studying chiral interactions at high cutoffs \cite{Tews:2018sbi}.
@@
 In principle, these deep bound states are outside the range of the EFT and are absorbed by counterterms at higher order.
-In \cite{Wendt:2011qj}, it was shown that band-diagonal SRG decoupling of NN potentials in partial waves with spurious bound states changes significantly depending on the choice of SRG generator.
+In \cite{Wendt:2011qj}, it was shown that band-diagonal SRG decoupling of NN potentials in partial waves with spurious bound states differs significantly depending on the choice of SRG generator.
 These high cutoff potentials provide a unique opportunity to understand some of the previous points about universality, the choice of SRG generator and decoupling, as well as a good test problem for a variant of the SRG, which utilizes the Magnus expansion \cite{Morris:2015yna}.
@@
 
-\noindent{%
-\textbf{The Magnus expansion}
-}
-\\
 The Magnus expansion gives the SRG the capability to solve for the unitary transformation explicitly which can then be applied to any other operator of interest.
@@
 %
-\noindent{%
-\textbf{General outline of the section}
-}
-\\
--- Comparison of potential evolution with different potentials and SRG generators.
-\\
--- Universality.
-\\
-\textbf{Analysis of figures}
-\\
+%
 %-- Fig.~\ref{fig:potential_contours_RKE_Wegner} illustrates the SRG in a nutshell.
@@
 %
-\noindent{%
--- In Fig.~\ref{fig:potential_contours_3S1_Wegner} we consider three different SRG-evolved potentials in the $^3$S$_1$ channel: EM N$^3$LO (500 MeV cutoff) \cite{Entem:2003ft}, RKE N$^4$LO (450 MeV cutoff) \cite{Reinert:2017usi}, and Gezerlis et al.~N$^2$LO (1 fm cutoff) \cite{Gezerlis:2014zia}.
+Here, we analyze SRG evolution of various chiral potentials with the Wegner band-diagonal generator and the block-diagonal generator.
+In Fig.~\ref{fig:potential_contours_3S1_Wegner} we consider three different SRG-evolved potentials in the $^3$S$_1$ channel: EM N$^3$LO (500 MeV cutoff) \cite{Entem:2003ft}, RKE N$^4$LO (450 MeV cutoff) \cite{Reinert:2017usi}, and Gezerlis et al.~N$^2$LO (1 fm cutoff) \cite{Gezerlis:2014zia}.
 The major difference in these three potentials are the regulator functions in the contact and pion-exchange terms.
@@
 The Gezerlis et al.~N$^2$LO potential is an example of a local interaction where the long-range terms have a local regulator function in coordinate-space and the short-range terms have a local regulator function in momentum-space.
-}
 \\

### 2019-11-05 run_srg.py
Generated SRG-evolved RKE N4LO potentials with T_rel

@@ -155,8 +155,8 @@ if __name__ == '__main__':
     #channel = '3P0'
     
     #kmax = 30.0
-    kmax = 8.0
-    #kmax = 10.0
+    #kmax = 8.0
+    kmax = 10.0
     #kmax = 6.0
     
     #kmid = 4.0
@@ -172,8 +172,8 @@ if __name__ == '__main__':
     # Specify evolution
     
     #generator = 'Wegner'
-    #generator = 'T'
-    generator = 'Block-diag'
+    generator = 'T'
+    #generator = 'Block-diag'
     
     lambda_bd = 1.00 # This won't affect the band-diagonal generators
     #lambda_bd = 1.50

### 2019-11-05 Notes/Operator_evolution/operator_evolution.tex
Updated operator evolution draft
Minor changes.

@@
 %	08/28/19 --- Started outlining and added pieces from old notes.
-%	09/19/19 --- Added more bullets up through section 2.
 %	09/27/19 --- Wrote the introduction and swapped the Magnus and operator sections.
@@
 In a similar option used in nuclear physics, $G$ is set to the relative kinetic energy, $T_{rel}$, which also drives to band-diagonal form.
-In most cases, these two choices give the same evolved operators \textcolor{red}{(check that is true for momentum projection operator and $r^2$ operator)}.
+In most cases, these two choices give the same evolved operators.
 In exceptional cases, which will be discussed later in the paper, the two band-diagonal choices can have drastically different behavior.
 For band-diagonal decoupling, it is convenient to define $\lambda \equiv s^{-1/4}$ which roughly measures the width of the band-diagonal in the decoupled operator.
-For block-diagonal decoupling,
+For block-diagonal decoupling \cite{Anderson:2008mu},
 %
@@
 In a previous work \cite{Anderson:2010aq}, it was shown that SRG transformations induce low-momentum contributions in high-momentum operators and change very little in low-momentum operators.
-We apply SRG band- and block-diagonal transformations to other operators from building the unitary transformations explicitly using the eigenvectors of the initial and evolved Hamiltonians.
+We investigate whether this is a general trend of the SRG for any potential and SRG generator.
+Instead of solving another set of flow equations, we apply SRG band- and block-diagonal transformations to other operators by building the unitary transformations explicitly using the eigenvectors of the initial and evolved Hamiltonians.
 SRG-evolved operators depend on the NN interaction despite having the same initial operator, since the flow equation (\ref{eq:srg_flow}) depends on $H(s)$ from the definition of $\eta(s)$.
@@
 \label{sec:magnus_expansion}
+% Split this section into two sections?
 
@@
 \begin{itemize}
-	\item Cutoff dependence in non-local LO (Wendt) potential.
+	\item Cutoff dependence in non-local LO (Wendt) potential. Recap of Wendt.
 	\item Band- and block-diagonal evolution and universality. Add figure analogous to Fig.~\ref{fig:potential_slices_3S1} but for $\Lambda=4$, $9$, and $20$ fm$^{-1}$.
-	\item Spurious bound state(s).
+	\item Spurious bound state(s). Decoupling with block-diagonal.
 	\item Transition to Magnus expansion.
@@
 
+% What was said in the introduction: The Magnus expansion gives the SRG the capability to solve for the unitary transformation explicitly which can then be applied to any other operator of interest.
+This offers a huge numerical simplification in Fock-space where the matrix size of operators can become very large.
+The Magnus expansion is often used in in-medium SRG (IMSRG) calculations to solve the nuclear many-body problem directly
 \noindent{%
@@
 -- We investigate several truncations $k_{max}$ in Eqn. (\ref{eq:magnus_omega}) and take many terms, $k_{max} \sim 25$, in Eqn. (\ref{eq:bch}).
-\\
-\textcolor{red}{%
--- Here or earlier (for the following bullets)? Better to motivate the Magnus in the introduction or easier to explain given mathematical detail?
-}
 \\

### 2019-11-12 Notes/Operator_evolution/operator_evolution.tex
Update operator_evolution.tex
Minor changes.

@@
 In Fig.~\ref{fig:potential_contours_3S1_Wegner} we consider three different SRG-evolved potentials in the $^3$S$_1$ channel: EM N$^3$LO (500 MeV cutoff) \cite{Entem:2003ft}, RKE N$^4$LO (450 MeV cutoff) \cite{Reinert:2017usi}, and Gezerlis et al.~N$^2$LO (1 fm cutoff) \cite{Gezerlis:2014zia}.
-The major difference in these three potentials are the regulator functions in the contact and pion-exchange terms.
-The EM N$^3$LO interaction is a non-local potential where both contact and pion-exchange interactions feature a non-local regulator function of the form exp$[-(p/\Lambda)^{2n}-(p'/\Lambda)^{2n}]$, where $\Lambda$ is the momentum-space cutoff and $n$ is an integer.
+A major difference in these three potentials are the regulator functions in the contact and pion-exchange terms.
+The EM N$^3$LO interaction is a non-local potential where both contact and pion-exchange interactions feature a non-local regulator function of the form exp$[-(k/\Lambda)^{2n}-(k'/\Lambda)^{2n}]$, where $\Lambda$ is the momentum-space cutoff and $n$ is an integer ($n=2$ in this case).
 However, a non-local regulator function for pion-exchange contributions can introduce regulator artifacts for cutoffs $\Lambda$ lower than the breakdown scale $\Lambda_b$.
@@
 \\
+% Connect back to motivation. Why are we looking at this figure? Takeaways in this paragraph too.
 -- Takeaways from Fig.~\ref{fig:potential_contours_3S1_Wegner}: completely different at $\lambda=6$ fm$^{-1}$ but low-momentum matrix elements are similar at $\lambda=1$ fm$^{-1}$.
@@
 %
+% Transition to SRG-decoupling in next paragraph.
 \noindent{%
@@
 \\
+% Can completely different chiral potentials be driven to the same potential?
 -- Takeaways from Fig.~\ref{fig:potential_contours_1P1_RKE}: smooth decoupling for Wegner and sharp for block-diagonal, each unique generator should have its own type of universality.
@@
 \\
--- Add continuum state momentum distributions and how to understand operator evolution. If
+-- Add continuum state momentum distributions and how to understand operator evolution.
 

### 2019-11-13 Notes/Operator_evolution/operator_evolution.tex
Updated operator evolution notes
Minor changes.

@@
 Here, we analyze SRG evolution of various chiral potentials with the Wegner band-diagonal generator and the block-diagonal generator.
-In Fig.~\ref{fig:potential_contours_3S1_Wegner} we consider three different SRG-evolved potentials in the $^3$S$_1$ channel: EM N$^3$LO (500 MeV cutoff) \cite{Entem:2003ft}, RKE N$^4$LO (450 MeV cutoff) \cite{Reinert:2017usi}, and Gezerlis et al.~N$^2$LO (1 fm cutoff) \cite{Gezerlis:2014zia}.
+In Fig.~\ref{fig:potential_contours_3S1_Wegner} we show three different SRG-evolved potentials in the $^3$S$_1$ channel: EM N$^3$LO (500 MeV cutoff) \cite{Entem:2003ft}, RKE N$^4$LO (450 MeV cutoff) \cite{Reinert:2017usi}, and Gezerlis \textit{et al.}~N$^2$LO (1 fm cutoff) \cite{Gezerlis:2014zia}.
 A major difference in these three potentials are the regulator functions in the contact and pion-exchange terms.
@@
 In some instances, non-local interactions are not suitable for $\textit{ab initio}$ approaches such as the quantum Monte Carlo (QMC) method motivating the need for fully local potentials.
-The Gezerlis et al.~N$^2$LO potential is an example of a local interaction where the long-range terms have a local regulator function in coordinate-space and the short-range terms have a local regulator function in momentum-space.
+The Gezerlis \textit{et al.}~N$^2$LO potential is an example of a local interaction where the long-range terms have a local regulator function in coordinate-space and the short-range terms have a local regulator function in momentum-space.
 \\
-% Connect back to motivation. Why are we looking at this figure? Takeaways in this paragraph too.
--- Takeaways from Fig.~\ref{fig:potential_contours_3S1_Wegner}: completely different at $\lambda=6$ fm$^{-1}$ but low-momentum matrix elements are similar at $\lambda=1$ fm$^{-1}$.
-Decoupled, low-momentum matrix elements are necessarily the same since the pion-exchange terms are calculated explicitly.
-(Cutoff dependence can play a role though for lower cutoffs.)
+
+These chiral interactions give the same low-energy phase shifts but the matrix elements of the potential are entirely different.
+In \cite{Dainton:2013axa}, with the SRG $T_{rel}$ generator, different phenomenological potentials were driven to universal low-momentum matrix elements.
+We see in Fig.~\ref{fig:potential_contours_3S1_Wegner} that the modern chiral potentials follow the same pattern.
+On the left-hand column where $\lambda=6$ fm$^{-1}$, the three potentials differ.
+Further along the SRG evolution (right-hand side), the potentials are driven to band-diagonal form where the upper right corner of the contours, corresponding to low-momentum matrix elements, are the same.
+Note, we use the Wegner generator, $G=H_D$, in this SRG-evolution instead of $T_{rel}$.
+For realistic nuclear interactions, these two choices are essentially the same.
+There will only be a difference Only in extreme cases will there be a difference in the SRG-evolution.
+Lastly, we have checked that the same SRG flow to universality occurs in other partial wave channels.
 %
@@
 	}
-	\caption{Matrix elements of the EM N$^3$LO (a), RKE N$^4$LO (b), and Gezerlis et al.~N$^2$LO (c) potentials SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator in the $^3$S$_1$ channel.}
+	\caption{Matrix elements of the EM N$^3$LO 500 MeV (a), RKE N$^4$LO 450 MeV (b), and Gezerlis \textit{et al.}~N$^2$LO 1 fm (c) potentials SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator in the $^3$S$_1$ channel.}
 	\label{fig:potential_contours_3S1_Wegner}
@@
 \noindent{%
--- Fig.~\ref{fig:phase_shifts} shows the NN phase shifts of EM N$^3$LO, RKE N$^4$LO, and Gezerlis et al.~N$^2$LO potentials in the $^1$S$_0$, $^3$S$_1$, and $^1$P$_1$ channels.
+-- Fig.~\ref{fig:phase_shifts} shows the NN phase shifts of EM N$^3$LO, RKE N$^4$LO, and Gezerlis \textit{et al.}~N$^2$LO potentials in the $^1$S$_0$, $^3$S$_1$, and $^1$P$_1$ channels.
 In \cite{Dainton:2013axa}, it was found that phase equivalence up to some value of momentum $k$ implies matrix element equivalence up to the same value of $k$ in SRG-evolved potentials.
@@
 	}
-	\caption{$^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) phase shifts for the EM N$^3$LO (solid black), RKE N$^4$LO (red dash-dotted), and Gezerlis et al.~N$^2$LO (blue dashed) potentials.}
+	\caption{$^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) phase shifts for the EM N$^3$LO (solid black), RKE N$^4$LO (red dash-dotted), and Gezerlis \textit{et al.}~N$^2$LO (blue dashed) potentials.}
 	\label{fig:phase_shifts}
@@
 	}
-	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the EM N$^3$LO (black), RKE N$^4$LO (red) and Gezerlis et al.~N$^2$LO (blue) potentials SRG-evolving right to left under transformations with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^1$S$_0$ channel.
+	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the EM N$^3$LO (black), RKE N$^4$LO (red) and Gezerlis \textit{et al.}~N$^2$LO (blue) potentials SRG-evolving right to left under transformations with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^1$S$_0$ channel.
 Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution.
@@
 	}
-	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the momentum projection operator under SRG transformations with EM N$^3$LO (black), RKE N$^4$LO (red) and Gezerlis et al.~N$^2$LO (blue) potentials evolving right to left with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^3$S$_1$ channel.
+	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the momentum projection operator under SRG transformations with EM N$^3$LO (black), RKE N$^4$LO (red) and Gezerlis \textit{et al.}~N$^2$LO (blue) potentials evolving right to left with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^3$S$_1$ channel.
 Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution.

### 2019-11-15 observables.py
Update observables.py
Minor changes. Simplified energies function.

@@ -123,7 +123,7 @@ def energies(H_matrix, bound_states_only=True):
         
     Returns
     -------
-    energies : 1-D ndarray
+    output : 1-D ndarray
         Array of energies in units MeV.
         
     """
@@ -134,20 +134,12 @@ def energies(H_matrix, bound_states_only=True):
     # Return only the bound state energies
     if bound_states_only:
             
-        # Store energies in this list 
-        energies = np.empty(0)
-            
-        i = 0
-        while eigenvalues[i] < 0.0:
-            energies = np.append(energies, eigenvalues[i])
-            i += 1
+        return eigenvalues[ eigenvalues < 0.0 ]
         
     # Otherwise return all energies
     else:
             
-        energies = eigenvalues
-            
-    return energies
+        return eigenvalues
 
 
 def phase_shifts(e_array, V_matrix, k_array, k_weights):
@@ -172,7 +164,6 @@ def phase_shifts(e_array, V_matrix, k_array, k_weights):
     -------
     phase_shifts : 1-D ndarray
         Array of phase shifts in degrees for each lab energy in e_array.
-    
     
     Notes
     -----
@@ -273,7 +264,6 @@ def coupled_channel_phase_shifts(e_array, V_matrix, k_array, k_weights,
         in e_array. For example, phase_shifts[i, 0] returns delta_a at the ith
         lab energy in e_array. For an entire array of one type of phase shift,
         take phase_shifts[:, i] where i = 0, 1, or 2.
-    
     
     Notes
     -----

### 2019-11-15 Notes/Operator_evolution/operator_evolution.tex
Updated operator evolution draft
Wrote the section on SRG evolved potentials.

@@
 %	08/28/19 --- Started outlining and added pieces from old notes.
-%	09/27/19 --- Wrote the introduction and swapped the Magnus and operator sections.
+%	09/27/19 --- Wrote the introduction.
+%	11/15/19 --- Editing introduction, figures, and wrote the SRG potential evolution section.
 %
@@
 $^1$\mbox{Department of Physics, The Ohio State University, Columbus, OH 43210, USA}  \\
-$^2$\mbox{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy,}  \\
+$^2$\mbox{Facility for Rare Isotope Beams and Department of Physics and Astronomy,}  \\
 \mbox{Michigan State University, East Lansing, MI 48824, USA}
@@
 Nuclear physics has seen a massive increase in the number of new NN interactions from chiral effective field theory ($\chi^{EFT}$) in the last decade.
-Previous SRG studies were limited to phenomenological interactions or some of the first non-local chiral interactions \cite{Entem:2003ft}, but with much more variety in modern chiral interactions, we would like to revisit the question of how different potentials and other operators change under SRG transformations.
+Previous SRG studies were limited to phenomenological interactions or the first non-local chiral interaction \cite{Entem:2003ft}, but with much more variety in modern chiral interactions, we would like to revisit the question of how different potentials and other operators change under SRG transformations.
 Since $\chi^{EFT}$ is an effective field theory, different potentials will still give the same $S$-matrix, that is, the potentials are phase equivalent up to some higher energy.
@@
 Instead of solving another set of flow equations, we apply SRG band- and block-diagonal transformations to other operators by building the unitary transformations explicitly using the eigenvectors of the initial and evolved Hamiltonians.
-SRG-evolved operators depend on the NN interaction despite having the same initial operator, since the flow equation (\ref{eq:srg_flow}) depends on $H(s)$ from the definition of $\eta(s)$.
+SRG-evolved operators depend on the NN interaction despite having the same initial operator, since the flow equation (\ref{eq:srg_flow}) includes $H(s)$ from the definition of $\eta(s)$.
 \\
@@
 In principle, these deep bound states are outside the range of the EFT and are absorbed by counterterms at higher order.
-In \cite{Wendt:2011qj}, it was shown that band-diagonal SRG decoupling of NN potentials in partial waves with spurious bound states differs significantly depending on the choice of SRG generator.
-These high cutoff potentials provide a unique opportunity to understand some of the previous points about universality, the choice of SRG generator and decoupling, as well as a good test problem for a variant of the SRG, which utilizes the Magnus expansion \cite{Morris:2015yna}.
+In \cite{Wendt:2011qj}, it was shown that band-diagonal SRG decoupling of NN potentials in partial waves with spurious bound states differs significantly depending on the choice of SRG generator ($G=T_{rel}$ or $H_{D}$).
+These high cutoff potentials provide a test case to understand some of the previous points about universality, the choice of SRG generator and decoupling, as well as a good test problem for a variant of the SRG, which utilizes the Magnus expansion \cite{Morris:2015yna}.
 \\
@@
 \noindent{%
-\textbf{Overview of sections.}
+\textcolor{red}{Overview of sections.}
 }
@@
 
-% Summarize what we're looking at in this section and general conclusions. What did I not cover in the introduction?
-%
-%
 %-- Fig.~\ref{fig:potential_contours_RKE_Wegner} illustrates the SRG in a nutshell.
@@
 However, a non-local regulator function for pion-exchange contributions can introduce regulator artifacts for cutoffs $\Lambda$ lower than the breakdown scale $\Lambda_b$.
-Several semi-local chiral potentials have been introduced to reduce regulator artifacts, such as the RKE N$^4$LO potential.
+Several semi-local chiral potentials have been introduced to reduce regulator artifacts, such as the RKE potentials.
 Here, a local regulator function is applied for the long-range interactions in momentum-space, while a non-local regulator function is used for the short-range interactions.
@@
 The Gezerlis \textit{et al.}~N$^2$LO potential is an example of a local interaction where the long-range terms have a local regulator function in coordinate-space and the short-range terms have a local regulator function in momentum-space.
-\\
-
-These chiral interactions give the same low-energy phase shifts but the matrix elements of the potential are entirely different.
-In \cite{Dainton:2013axa}, with the SRG $T_{rel}$ generator, different phenomenological potentials were driven to universal low-momentum matrix elements.
-We see in Fig.~\ref{fig:potential_contours_3S1_Wegner} that the modern chiral potentials follow the same pattern.
-On the left-hand column where $\lambda=6$ fm$^{-1}$, the three potentials differ.
-Further along the SRG evolution (right-hand side), the potentials are driven to band-diagonal form where the upper right corner of the contours, corresponding to low-momentum matrix elements, are the same.
-Note, we use the Wegner generator, $G=H_D$, in this SRG-evolution instead of $T_{rel}$.
-For realistic nuclear interactions, these two choices are essentially the same.
-There will only be a difference Only in extreme cases will there be a difference in the SRG-evolution.
-Lastly, we have checked that the same SRG flow to universality occurs in other partial wave channels.
 %
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Wegner_potential_label}%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Wegner_potential_label}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn111_3S1_Wegner_potential_label}%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_potentials/potential_contours_kvnn111_3S1_Wegner_potential_label}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn222_3S1_Wegner_potential_label}%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_potentials/potential_contours_kvnn222_3S1_Wegner_potential_label}%
 	}
@@
 %
-% Transition to SRG-decoupling in next paragraph.
-\noindent{%
--- Fig.~\ref{fig:potential_contours_1P1_RKE} shows the SRG-evolved RKE N$^4$LO (450 MeV cutoff) potential in the $^1$P$_1$ channel for two SRG generators: the Wegner and block-diagonal generators which drive the potential to band- and block-diagonal form, respectively.
-We continue to evolve to band-diagonal form with respect to the parameter $\lambda$, but for the block-diagonal generator, we label sub-plots with the parameter $\Lambda$ which characterizes the sharp cutoff in decoupling the low- and high-momentum matrix elements.
-}
-\\
-% Can completely different chiral potentials be driven to the same potential?
--- Takeaways from Fig.~\ref{fig:potential_contours_1P1_RKE}: smooth decoupling for Wegner and sharp for block-diagonal, each unique generator should have its own type of universality.
-Check this more quantitatively by comparing matrix element ``slices''.
+These chiral interactions give the same low-energy phase shifts but the matrix elements of the potential are entirely different.
+In \cite{Dainton:2013axa}, with the SRG $T_{rel}$ generator, different phenomenological potentials were driven to universal low-momentum matrix elements.
+We see in Fig.~\ref{fig:potential_contours_3S1_Wegner} that the modern chiral potentials follow the same pattern.
+On the left-hand column where $\lambda=6$ fm$^{-1}$, the three potentials differ substantially.
+Further along the SRG evolution (right-hand side), the potentials are driven to band-diagonal form where the upper right corner of the contours, corresponding to low-momentum matrix elements, are the same.
+Note, we use the Wegner generator, $G=H_D$, in this SRG-evolution instead of $T_{rel}$ as in \cite{Dainton:2013axa}.
+For realistic nuclear interactions, these two band-diagonal choices are essentially the same.
+Only in extreme cases will there be a difference in the SRG-evolution.
 %
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn111_1P1_Wegner_generator_label}%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_potentials/potential_contours_kvnn111_1P1_Wegner_generator_label}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn111_1P1_Block-diag_generator_label}%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_potentials/potential_contours_kvnn111_1P1_Block-diag_generator_label}%
 	}
-	\caption{Matrix elements of the RKE N$^4$LO potential SRG-evolving right to left under transformations with Wegner (a) and block-diagonal (b) generators in the $^1$P$_1$ channel.
+	\caption{Matrix elements of the RKE N$^4$LO 450 MeV potential SRG-evolving right to left under transformations with Wegner (a) and block-diagonal (b) generators in the $^1$P$_1$ channel.
 Here, we use $\lambda$ for Wegner evolution in the top row and $\Lambda$ for block-diagonal evolution in the bottom row.
-For block-diagonal evolution, we fix $\lambda=1.5$ fm$^{-1}$.}
+For block-diagonal evolution, we fix $\lambda=1$ fm$^{-1}$.}
 	\label{fig:potential_contours_1P1_RKE}
@@
 %
-\noindent{%
--- Fig.~\ref{fig:phase_shifts} shows the NN phase shifts of EM N$^3$LO, RKE N$^4$LO, and Gezerlis \textit{et al.}~N$^2$LO potentials in the $^1$S$_0$, $^3$S$_1$, and $^1$P$_1$ channels.
-In \cite{Dainton:2013axa}, it was found that phase equivalence up to some value of momentum $k$ implies matrix element equivalence up to the same value of $k$ in SRG-evolved potentials.
-We verify this conclusion by checking the matrix elements in Fig.~\ref{fig:potential_slices_1S0} where we see a collapse of the different potential matrix elements to the same line in the last column ($\lambda=1$ fm$^{-1}$).
-Note, Figs.~\ref{fig:potential_slices_1S0}-\ref{fig:potential_slices_1P1} show both Wegner and block-diagonal evolution where the solid lines correspond to the Wegner generator and dash-dotted to block-diagonal evolution.
-We see each generator collapses the potential to a different form because the low- and high-momentum matrix elements decouple in a different manner.
-}
-\\
--- In the $^3$S$_1$ channel, we see a slight deviation in the lowest momentum potential matrix element from EM N$^3$LO and the other two potentials.
-This is due to a minor difference in the deuteron binding energy ($\approx 1\%$ difference).
-\\
--- The bottom row of Fig.~\ref{fig:potential_slices_1P1} shows $V(k,0.5)$ instead of $V(k,0)$ because the far off-diagonal matrix elements in the $^1$P$_1$ channel are all zero.
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_1S0_kvnns_10_111_222}%
-	}
-	\quad
-	\subfloat[]{%
-	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_3S1_kvnns_10_111_222}%
-	}
-	\quad
-	\subfloat[]{%
-	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_1P1_kvnns_10_111_222}%
-	}
-	\caption{$^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) phase shifts for the EM N$^3$LO (solid black), RKE N$^4$LO (red dash-dotted), and Gezerlis \textit{et al.}~N$^2$LO (blue dashed) potentials.}
-	\label{fig:phase_shifts}
-\end{figure}
+Fig.~\ref{fig:potential_contours_1P1_RKE} shows the SRG-evolved RKE N$^4$LO (450 MeV cutoff) potential in the $^1$P$_1$ partial wave channel for band- and block-diagonal SRG generators on the top and bottom rows, respectively.
+We continue to evolve to band-diagonal form with respect to the parameter $\lambda$, but for the block-diagonal generator, we label sub-plots with the parameter $\Lambda$ which characterizes the sharp cutoff in decoupling the low- and high-momentum matrix elements.
+In the case of block-diagonal decoupling, one should take $s \rightarrow \infty$ which corresponds to $\lambda \rightarrow 0$.
+Of course, this is impossible numerically, so we take $\lambda=1$ fm$^{-1}$ for sufficiently decoupled sub-blocks.
+Thus, we see a small non-zero width in between the sub-blocks due to a non-zero value of $\lambda$.
+With block-diagonal decoupling, one can truncate the Hamiltonian at the value of $\Lambda$, separately diagonalize each sub-block, and retain all eigenvalues to high accuracy.
+We have tested several cases and acquired the same eigenvalues to less than roughly $.1$\% for both the low- and high-momentum sub-blocks.
 %
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_1S0_kvnns_10_111_222_lamb1,0}%
+	\includegraphics[clip,width=0.25\columnwidth]{SRG_observables/phase_shifts_1S0_kvnns_10_111_222}%
+	}
+	\quad
+	\subfloat[]{%
+	\includegraphics[clip,width=0.25\columnwidth]{SRG_observables/phase_shifts_3S1_kvnns_10_111_222}%
+	}
+	\quad
+	\subfloat[]{%
+	\includegraphics[clip,width=0.25\columnwidth]{SRG_observables/phase_shifts_1P1_kvnns_10_111_222}%
+	}
+	\caption{$^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) phase shifts for the EM N$^3$LO 500 MeV (solid black), RKE N$^4$LO 450 MeV (red dash-dotted), and Gezerlis \textit{et al.}~N$^2$LO 1 fm (blue dashed) potentials.}
+	\label{fig:phase_shifts}
+\end{figure}
+%
+In \cite{Dainton:2013axa}, it was found that phase equivalence up to some value of momentum $k$ implies potential matrix element equivalence up to the same value of $k$ in SRG-evolved potentials.
+We verify this conclusion for modern chiral potentials by checking the matrix elements in comparison to the phase shifts.
+Fig.~\ref{fig:phase_shifts} shows the NN phase shifts of EM N$^3$LO (500 MeV), RKE N$^4$LO (450 MeV), and Gezerlis \textit{et al.}~N$^2$LO (1 fm) potentials in the $^1$S$_0$, $^3$S$_1$, and $^1$P$_1$ partial wave channels.
+The phase shifts roughly agree up to some momentum value in the range $1-2$ fm$^{-1}$, and therefore, we expect the matrix elements of the SRG-evolved potentials to collapse up to these momentum values for each partial wave channel.
+To see this more quantitatively, we show the diagonal and far off-diagonal matrix elements of evolved potentials in Figs.~\ref{fig:potential_slices_1S0}, \ref{fig:potential_slices_3S1}, and \ref{fig:potential_slices_1P1}.
+%
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_potentials/potential_diag_1S0_kvnns_10_111_222_lamb1,0}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_1S0_kvnns_10_111_222_lamb1,0}%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_potentials/potential_off-diag_1S0_kvnns_10_111_222_lamb1,0}%
 	}
-	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the EM N$^3$LO (black), RKE N$^4$LO (red) and Gezerlis \textit{et al.}~N$^2$LO (blue) potentials SRG-evolving right to left under transformations with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^1$S$_0$ channel.
+	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the EM N$^3$LO 500 MeV (black), RKE N$^4$LO 450 MeV (red) and Gezerlis \textit{et al.}~N$^2$LO 1 fm (blue) potentials SRG-evolving right to left under transformations with Wegner (solid) and block-diagonal (dashed) generators in the $^1$S$_0$ channel.
 Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution.
@@
 %
+In each of these figures, we show the diagonal matrix elements on the top row and the far off-diagonal matrix elements on the bottom row.
+(Note, in Fig.~\ref{fig:potential_slices_1P1}, the bottom row shows $V(k,0.5)$ instead of $V(k,0)$ because the far off-diagonal matrix elements in the $^1$P$_1$ channel are all zero.) Band- and block-diagonal evolved potentials are shown on the same plots indicated by solid and dashed lines, respectively, where the color indicates the potential.
+In the case of band-diagonal decoupling, as $\lambda$ is driven to a lower value than the $k$ value of phase shift equivalence, the low-momentum potential matrix elements collapse to the same line.
+For block-diagonal decoupling, the agreement only occurs for momentum-values less than the sharp cutoff $\Lambda$ where $\lambda$ is fixed to 1 fm$^{-1}$.
+The two generators collapse the potential to a different form, because the induced contributions from SRG flow depend on how the potential is decoupled, that is, the choice in $G$.
+In the $^3$S$_1$ channel (Fig.~\ref{fig:potential_slices_3S1}), we see a slight deviation in the lowest momentum potential matrix element from EM N$^3$LO and the other two potentials.
+This is due to a minor difference in the deuteron binding energy ($\approx 1\%$ difference).
+We will see in the next section that bound states significantly impact universality in SRG decoupling.
+%
 \begin{figure}[H]
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_3S1_kvnns_10_111_222_lamb1,0}%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_potentials/potential_diag_3S1_kvnns_10_111_222_lamb1,0}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_3S1_kvnns_10_111_222_lamb1,0}%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_potentials/potential_off-diag_3S1_kvnns_10_111_222_lamb1,0}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_1P1_kvnns_10_111_222_lamb1,0}%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_potentials/potential_diag_1P1_kvnns_10_111_222_lamb1,0}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_1P1_kvnns_10_111_222_lamb1,0}%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_potentials/potential_off-diag_1P1_kvnns_10_111_222_lamb1,0}%
 	}
@@
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Evolution of other operators}
-\label{sec:evolution_other_operators}
-
-\noindent{%
--- SRG operator evolution for different potentials and generators.
-}
-\\
--- General questions to address: universality for operators, different generators.
-\\
--- Give relevant equations. Unitary transformation equation.
-\\
--- Momentum projection operator.
-\\
--- Relevant equations: just the momentum projection operator in momentum-space.
 %
-\begin{itemize}
-	\item Contours and general behavior: SRG transformation shifts strength of operator to low-momentum.
-	\item Deuteron momentum distributions. Why does this make sense with the transformed operators?
-	\item Diagonals and far off-diagonals. Universality.
-	\item Same questions but with figures of the integrand.
-\end{itemize}
-%
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/momentum_projection_diag_q3,00_3S1_kvnns_10_111_222_lamb1,5}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/momentum_projection_off-diag_q3,00_3S1_kvnns_10_111_222_lamb1,5}%
-	}
-	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the momentum projection operator under SRG transformations with EM N$^3$LO (black), RKE N$^4$LO (red) and Gezerlis \textit{et al.}~N$^2$LO (blue) potentials evolving right to left with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^3$S$_1$ channel.
-Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution.
-For block-diagonal evolution, we fix $\lambda=1.5$ fm$^{-1}$.}
-	\label{fig:momentum_proj_3S1}
-\end{figure}
-%
--- Note, the unitary transformations and evolved wave functions for different potentials are not the same (at low momentum too) which implies that evolved operators cannot have the same universality property as the evolved potentials since they are dependent on the evolved wave functions.
-\\
--- $\hat{r}^2$ operator.
-\\
--- Relevant equations: operator in coordinate-space and Hankel transformation.
-\\
--- Add continuum state momentum distributions and how to understand operator evolution.
+\textcolor{red}{Updated up to here.}
 
@@
 \section{High cutoffs and the Magnus expansion}
-\label{sec:magnus_expansion}
-% Split this section into two sections?
+\label{sec:high_cutoffs_magnus_exp}
 
-\noindent{%
-\textbf{High cutoffs}
-}
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+\subsection{High cutoffs and spurious bound states}
+\label{sec:high_cutoffs}
+
 \begin{itemize}
@@
 	\item Band- and block-diagonal evolution and universality. Add figure analogous to Fig.~\ref{fig:potential_slices_3S1} but for $\Lambda=4$, $9$, and $20$ fm$^{-1}$.
-	\item Spurious bound state(s). Decoupling with block-diagonal.
+	\item Spurious bound state(s). Discussion on how the block-diagonal generator handles spurious bound states. Where they are ``decoupled'' in the matrix compared to Wegner. One figure to show this?
 	\item Transition to Magnus expansion.
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_3S1_kvnns_900_901_902_lamb1,2}%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_potentials/potential_diag_3S1_kvnns_900_901_902_lamb1,2}%
 	}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_3S1_kvnns_900_901_902_lamb1,2}%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_potentials/potential_off-diag_3S1_kvnns_900_901_902_lamb1,2}%
 	}
-	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the non-local LO potentials at cutoffs $\Lambda=4$ (black), $9$ (red) and $20$ (blue) fm$^{-1}$ SRG-evolving right to left under transformations with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^3$S$_1$ channel.
+	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the non-local LO potentials at cutoffs $\Lambda=4$ (black), $9$ (red) and $20$ (blue) fm$^{-1}$ SRG-evolving right to left under transformations with Wegner (solid) and block-diagonal (dashed) generators in the $^3$S$_1$ channel.
 Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution.
@@
 % - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-\subsection{Formalism}
-\label{sec:magnus_expansion_formalism}
+\subsection{The Magnus expansion}
+\label{sec:magnus_expansion}
 
@@
 This offers a huge numerical simplification in Fock-space where the matrix size of operators can become very large.
-The Magnus expansion is often used in in-medium SRG (IMSRG) calculations to solve the nuclear many-body problem directly
+The Magnus expansion is often used in in-medium SRG (IMSRG) calculations to solve the nuclear many-body problem directly.
 \noindent{%
@@
 \\
--- In the next section, we discuss results from Magnus-evolved large-cutoff potentials focusing on the flow of the potential, observables, and operator evolution.
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-\subsection{Results}
-\label{sec:magnus_expansion_results}
-
-\noindent{%
+-- We discuss results from Magnus-evolved large-cutoff potentials focusing on the flow of the potential, observables, and operator evolution.
+\\
 -- Comparison to Wendt problem.
-}
 \\
@@
 \\
--- Discussion on how the block-diagonal generator handles spurious bound states. Where they are ``decoupled'' in the matrix compared to Wegner. One figure to show this?
+-- Transition to operator evolution.
 %
@@
 	\centering
-	\includegraphics[clip,width=0.9\columnwidth]{Magnus/potential_diagonals_offdiags_kvnn901_Wegner}%
+	\includegraphics[clip,width=0.7\columnwidth]{Magnus/potential_diagonals_offdiags_kvnn901_Wegner}%
 	%\caption{Caption.}
@@
 	\centering
-	\includegraphics[clip,width=0.9\columnwidth]{Magnus/potential_diagonals_offdiags_kvnn901_T}%
+	\includegraphics[clip,width=0.7\columnwidth]{Magnus/potential_diagonals_offdiags_kvnn901_T}%
 	%\caption{Caption.}
 	\label{fig:potential_slices_high_cutoffs_T}
+\end{figure}
+%
+%
+\begin{table}
+	\captionsetup{singlelinecheck=false,justification=raggedright}
+	\caption{Relative error on the deuteron bound state energy and the root mean square of eigenvalues where $\tilde{\epsilon}$ denotes an eigenvalue of an SRG or Magnus-evolved Hamiltonian for $\Lambda=9 \, fm^{-1}$ and $\lambda=1.2 \, fm^{-1}$.}
+	\label{tab:energies}
+	\begin{ruledtabular}
+		\begin{tabular}{{>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{1in}>{\centering\arraybackslash}m{1.5in}>{\centering\arraybackslash}m{2in}}}
+      			$  $ & $G$ & $ |\frac{\epsilon_d-\tilde{\epsilon}_d}{\epsilon_d}| $ & $\sqrt{\frac{1}{N} \, \sum_{i}^{N} (\tilde{\epsilon}_i-\epsilon_i)^2}$   [MeV] \\
+			\colrule
+      			SRG & $ $ & $\num{1.165e-5}$ & $\num{3.016e-4}$ \\
+      			Magnus, $k_{max}=2$ & $H_D$ & $\num{5.010e-10}$ & $\num{4.097e-9}$ \\
+      			Magnus, $k_{max}=14$ & $ $ & $\num{1.206e-11}$ & $\num{3.950e-10}$ \\ \hline
+      			SRG & $ $ & $\num{1.003e-4}$ & $\num{9.791e-5}$ \\
+      			Magnus, $k_{max}=2$ & $T_{rel}$ & $\num{7.775e-8}$ & $\num{6.376e-8}$ \\
+      			Magnus, $k_{max}=14$ & $ $ & $\num{7.607e-8}$ & $\num{6.359e-8}$ \\
+		\end{tabular}
+  	\end{ruledtabular}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Evolution of other operators}
+\label{sec:evolution_other_operators}
+
+\noindent{%
+-- SRG operator evolution for different potentials and generators.
+}
+\\
+-- General questions to address: universality for operators, different generators.
+\\
+-- Give relevant equations. Unitary transformation equation.
+\\
+\textbf{Momentum projection operator}
+\\
+-- Relevant equations: just the momentum projection operator in momentum-space.
+%
+\begin{itemize}
+	\item Contours and general behavior: SRG transformation shifts strength of operator to low-momentum.
+	\item Deuteron momentum distributions. Why does this make sense with the transformed operators?
+	\item Diagonals and far off-diagonals. Universality.
+	\item Same questions but with figures of the integrand.
+\end{itemize}
+%
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_operators/momentum_projection_contours_q0,30_kvnn111_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_operators/momentum_projection_contours_q0,30_kvnn111_3S1_Block-diag}%
+	}
+	\caption{Caption.}
+	\label{fig:momentum_projection_contours_q0,30_3S1_RKE}
+\end{figure}
+%
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_operators/momentum_projection_contours_q3,00_kvnn111_3S1_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_operators/momentum_projection_contours_q3,00_kvnn111_3S1_Block-diag}%
+	}
+	\caption{Caption.}
+	\label{fig:momentum_projection_contours_q3,00_3S1_RKE}
+\end{figure}
+%
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_operators/momentum_projection_diag_q3,00_3S1_kvnns_10_111_222_lamb1,5}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_operators/momentum_projection_off-diag_q3,00_3S1_kvnns_10_111_222_lamb1,5}%
+	}
+	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the momentum projection operator under SRG transformations with EM N$^3$LO (black), RKE N$^4$LO (red) and Gezerlis \textit{et al.}~N$^2$LO (blue) potentials evolving right to left with Wegner (solid) and block-diagonal (dashed) generators in the $^3$S$_1$ channel.
+Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution.
+For block-diagonal evolution, we fix $\lambda=1.5$ fm$^{-1}$.}
+	\label{fig:momentum_proj_3S1}
+\end{figure}
+%
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_operators/momentum_projection_integrand_contours_q3,00_kvnn111_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_operators/momentum_projection_integrand_contours_q3,00_kvnn111_Block-diag}%
+	}
+	\caption{Caption.}
+	\label{fig:momentum_projection_integrand_contours_q3,00_RKE}
+\end{figure}
+%
+\textbf{$\hat{r}^2$ operator}
+\\
+-- Relevant equations: operator in coordinate-space and Hankel transformation.
+\\
+-- Add continuum state momentum distributions and how to understand operator evolution.
+%
+\begin{figure}[H]
+	\centering
+	\subfloat[]{%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_operators/r2_contours_kvnn111_Wegner}%
+	}
+
+	\subfloat[]{%
+	\includegraphics[clip,width=0.7\columnwidth]{SRG_operators/r2_diff_contours_kvnn111_Wegner}%
+	}
+	\caption{Caption.}
+	\label{fig:r2_contours_RKE}
 \end{figure}

### 2019-11-18 Notes/Operator_evolution/operator_evolution.tex
Minor updates to operator evolution draft

@@
 % - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-\subsection{The Magnus expansion}
-\label{sec:magnus_expansion}
+\subsection{The Magnus expansion: Formalism}
+\label{sec:magnus_expansion_formalism}
 
@@
 -- Transition to operator evolution.
+
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+\subsection{The Magnus expansion: Results}
+\label{sec:magnus_expansion_results}
+
 %
@@
 	\includegraphics[clip,width=0.7\columnwidth]{Magnus/potential_diagonals_offdiags_kvnn901_Wegner}%
-	%\caption{Caption.}
+	\caption{Caption.}
 	\label{fig:potential_slices_high_cutoffs_Wegner}
@@
 	\includegraphics[clip,width=0.7\columnwidth]{Magnus/potential_diagonals_offdiags_kvnn901_T}%
-	%\caption{Caption.}
+	\caption{Caption.}
 	\label{fig:potential_slices_high_cutoffs_T}

### 2020-06-18 test.py
Update test.py
Testing time scaling with error precision in solving SRG flow equation.

@@ -33,7 +33,277 @@
 
 
 # Description of this test:
-#   Test the approximation K(p) ~ \int_0_\LambdaBD[p'^2 U(p,p')].
+#   Test error tolerances of SRG.
 
 
-from Potentials.vsrg_macos import load_save_potentials as lsp 
+import numpy as np
+import numpy.linalg as la
+from scipy.integrate import ode
+import time
+from Potentials.vsrg_macos import load_save_potentials as lsp
+  
+
+class SRG(object):
+    
+    
+    def __init__(self, H_initial):
+        """
+        Saves the initial Hamiltonian in units fm^-2 and the length of the 
+        matrix.
+        
+        Parameters
+        ----------
+        H_initial : 2-D ndarray
+            Initial Hamiltonian matrix [MeV].
+        
+        """
+        
+        # h-bar^2 / M [MeV fm^2]
+        self.hbar_sq_over_M = 41.47
+        
+        # Save matrices in scattering units [fm^-2]
+        self.H_initial = H_initial / self.hbar_sq_over_M
+        
+        # Save length of matrix
+        self.N = len(H_initial)
+
+    
+    def commutator(self, A, B):
+        """
+        Commutator of A and B, [A,B] where A and B are square matrices.
+        
+        Parameters
+        ----------
+        A : 2-D ndarray
+            First input square matrix.
+        B : 2-D ndarray
+            Second input square matrix.
+            
+        Returns
+        -------
+        out : 2-D ndarray
+            Commutator of the two input matrices.
+            
+        """
+        
+        return A @ B - B @ A
+    
+    
+    def matrix2vector(self, A):
+        """
+        Takes the upper triangle of the matrix A (including the diagonal) 
+        and reshapes it into a vector B of length N*(N+1)/2.
+        
+        Parameters
+        ----------
+        A : 2-D ndarray
+            Input matrix.
+            
+        Returns
+        -------
+        B : 1-D ndarray
+            Output vector.
+            
+        """
+    
+        # Length of matrix
+        N = self.N
+        # Length of vectorized matrix
+        n = int(N*(N+1)/2)
+        
+        # Initialize vectorized matrix
+        B = np.zeros(n)
+    
+        a = 0
+        b = N
+    
+        for i in range(N):
+        
+            B[a:b] = A[i][i:]
+            a = b
+            b += N-i-1
+
+        return B
+
+ 
[…]

### 2020-06-19 Notes/Operator_evolution/operator_evolution.tex
Adding Overleaf files to repository for operator evolution project
This has all the figures and Latex files for "Operator evolution from the SRG and the Magnus expansion".

--- 2019-11-13 Notes/Operator_evolution/operator_evolution.tex
@@
 %
-% Author: A. J. Tropiano (tropiano.4@osu.edu)
-% Date: August 23, 2019
-%
-% Draft of paper on SRG operator evolution and the Magnus expansion.
-%
-% Revision history:
-%	08/28/19 --- Started outlining and added pieces from old notes.
-%	09/27/19 --- Wrote the introduction and swapped the Magnus and operator sections.
+% Authors: Anthony Tropiano (tropiano.4@osu.edu),
+%          Dick Furnstahl (furnstahl.1@osu.edu),
+%          Scott Bogner (bogner@frib.msu.edu).
 %
@@
 
-\documentclass[preprintnumbers,floatfix,aps,prc,preprint,nofootinbib]{revtex4-1}
+\documentclass[10pt,aps,prc,floatfix,twocolumn,nofootinbib]{revtex4-1}
+%\documentclass[preprintnumbers,floatfix,aps,prc,preprint,nofootinbib]{revtex4-1}
 
 % Packages
+\usepackage{amsfonts}
 \usepackage{amsmath}
-\usepackage{amsfonts}
 \usepackage{amssymb}
+\usepackage{bbold}
 \usepackage{bm}
-\usepackage[font=small,skip=0pt]{caption} % For captions on figures and tables
 \usepackage{cellspace}
@@
 \usepackage{enumerate}
-\usepackage{epsfig}
+\usepackage{graphicx}
+\graphicspath{{Figures/}} % Setting the graphics path
+\usepackage{hyperref} % For clickable links to sections within table of contents
+\usepackage{physics} % For bra-ket notation
 \usepackage[figuresright]{rotating}
-\usepackage{float}
-\usepackage{hyperref} % For clickable links to sections within table of contents
-\usepackage{graphicx}
-\graphicspath{{../../Figures/}} % Setting the graphics path
-\usepackage{physics} % For bra-ket notation
 \usepackage{siunitx}
 \usepackage[caption=false]{subfig} % For sub-figures
+%\usepackage{floatrow}
 
-\newcommand{\eps}{\varepsilon}
+% Macros
+\newcommand{\chiEFT}{\ensuremath{\chi{\textrm{EFT}}}}
+\newcommand{\LambdaBD}{{\Lambda_{\text{BD}}}}
+\newcommand{\Trel}{\ensuremath{T_{\textrm{rel}}}}
+\newcommand{\ataq}{a^{\dagger}_q a_q}
+\newcommand{\abi}{\textit{ab initio}}
+
+\newcommand{\mystrut}{\rule{0pt}{0.9\normalbaselineskip}}
+\newcommand{\Klo}{K_{\text{lo}}}
+\newcommand{\Khi}{K_{\text{hi}}}
+\newcommand{\dst}{\displaystyle}
+
+\newcommand{\PP}{\ensuremath{P\mbox{--}P}}
+\newcommand{\PQ}{\ensuremath{P\mbox{--}Q}}
+\newcommand{\QP}{\ensuremath{Q\mbox{--}P}}
+\newcommand{\QQ}{\ensuremath{Q\mbox{--}Q}}
+
+%\floatsetup[figure]{style=plain, subcapbesideposition=top}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Operator evolution from the similarity renormalization group and the Magnus expansion}
+\title{Operator evolution from the similarity renormalization group \texorpdfstring{\\}{}
+and the Magnus expansion}
 
@@
 \begin{abstract}
-
-\noindent{Ideas for Magnus / SRG operator evolution paper}
-\\
--- SRG/Magnus evolution in different potentials (non-local, local, semi-local). Universality. High cutoffs.
-\\
--- Block-diagonal generator for high cutoff potentials and operator evolution. How the block-diagonal generator handles spurious bound states.
-\\
--- Testing the Magnus expansion for high cutoff potentials using the potentials from Wendt 2011 for comparison. Spurious bound states and connection to intruder states in IMSRG calculations.
-\\
--- Operator evolution for different potentials and generators.
-
+The Magnus expansion is an efficient alternative to solving similarity renormalization group (SRG) flow equations with high-order, memory-intensive ordinary differential equation solvers.
+The numerical simplifications it offers for operator evolution are particularly valuable for in-medium SRG calculations, though challenges remain for difficult problems involving intruder states.
+Here we test the Magnus approach in an analogous but more accessible situation, which is the free-space SRG treatment of the spurious bound-states arising from a leading-order chiral effective field theory (EFT) potential with very high cutoffs.
+We show that the Magnus expansion passes these tests and then use the investigations as a springboard to address various aspects of operator evolution that have renewed relevance in the context of the scale and scheme dependence of nuclear processes.
+These aspects include SRG operator flow with band- versus block-diagonal generators, universality for chiral EFT Hamiltonians and associated operators with different regularization schemes, and the impact of factorization arising from scale separation.
+Implications for short-range correlations physics and the possibilities for reconciling high- and low-resolution treatments of nuclear structure and reactions are discussed.
 \end{abstract}
@@
 
-% Unnecessary paragraph.
-%\noindent{%
-%\textbf{NN interaction and SRG decoupling.}
-%}
-%\\
-%The nuclear many-body problem has long been hindered by the short-range repulsive core and strong tensor force in nucleon-nucleon (NN) interactions leading to non-perturbative few- and many-body systems and strongly correlated wave functions.
-The Fourier transform of NN interactions gives rise to the coupling of low- and high-momentum modes, which is manifested as non-zero off-diagonal potential matrix elements.
-It is very difficult to implement these interactions in many-body methods using basis expansions, because the matrix dimension becomes too large for accurate calculations.
-Renormalization group (RG) methods can be used to soften the interaction to make many-body methods feasible.
-One such method, the similarity renormalization group (SRG), allows for a continuous change in resolution of the potential without changing the observables.
-More generally, the SRG can evolve any operator and wave function for consistent calculation of observables.
-%\\
+Similarity renormalization group (SRG) transformations are a valuable tool for low-energy nuclear physics, whether applied in free space to soften input Hamiltonians for few- and many-body calculations, or for in-medium SRG (IMSRG) calculations that directly target the ground state or low-lying states in a given nucleus ~\cite{Bogner:2009bt,Furnstahl:2013oba,Hergert:2016iju}.
+For both free-space and in-medium formulations, it is imperative that other operators are consistently and accurately evolved so that measurable quantities are left invariant.  
+In the present work, we address the robustness of the Magnus expansion as a method to solve free-space SRG flow equations, and examine other issues of SRG operator evolution in light of the proliferation of new chiral EFT (\chiEFT) interactions~\cite{Epelbaum:2014efa,Gezerlis:2014zia,Piarulli:2014bda,Ekstrom:2015rta,Carlsson:2015vda,Reinert:2017usi,Ekstrom:2017koy,Entem:2017gor}, the scale dependence of short-range-correlation (SRC) physics~\cite{Hen:2016kwk,Weiss:2016obx,Cruz-Torres:2019fum,Schmidt:2020kcl}, recent interest in high-cutoff effective field theories (EFTs) and renormalization~\cite{Tews:2018sbi,Hammer:2019poc,vanKolck:2020llt,Tews:2020hgp}, and the universality of evolved operators~\cite{Dainton:2013axa,Arriola:2016fkr}.
 
-Nuclear physics has seen a massive increase in the number of new NN interactions from chiral effective field theory ($\chi^{EFT}$) in the last decade.
-Previous SRG studies were limited to phenomenological interactions or some of the first non-local chiral interactions \cite{Entem:2003ft}, but with much more variety in modern chiral interactions, we would like to revisit the question of how different potentials and other operators change under SRG transformations.
-Since $\chi^{EFT}$ is an effective field theory, different potentials will still give the same $S$-matrix, that is, the potentials are phase equivalent up to some higher energy.
-However, the potentials themselves can differ in many ways such as the regulator functions, cutoff, order, and so forth, and thus, the potential matrix elements are not the same.
-Dainton \textit{et al.}~\cite{Dainton:2013axa} demonstrated SRG transformations drive different NN potentials to the same low-momentum matrix elements, that is, a flow to universality up to the momentum value of phase inequivalence.
-We address the question of universality for modern chiral potentials as well as how other operators change with respect to the corresponding SRG transformations.
-\\
-
-The SRG decouples low- and high-momentum scales in the Hamiltonian by applying a continuous unitary transformation $U(s)$ where $s=0 \rightarrow \infty$ is the flow parameter.
+The SRG decouples low- and high-momentum scales in a Hamiltonian by applying a continuous unitary transformation $U(s)$, where $s=0 \rightarrow \infty$ is the flow parameter~\cite{Bogner:2006pc}.
 An evolved operator is given by
@@
 %
-where $O(0)$ corresponds to the initial operator.
-Because $U(s)$ is unitary, the observables of the operator are preserved.
-In practice, the unitary transformation U(s) is not explicitly solved for; the evolved operator is given by solving a differential flow equation which is obtained by taking the derivative of Eqn.
-(\ref{eq:srg_operator}),
+where $O(0)$ is the initial operator.
+Because $U(s)$ is unitary, matrix elements of the operator in evolved states are preserved.
+An evolved operator can be found by solving a differential flow equation obtained by taking the derivative of Eq.~\eqref{eq:srg_operator},
 %
@@
 %
-where $\eta(s)=\frac{dU(s)}{ds} U^{\dagger}(s) = -\eta^{\dagger}(s)$ is the anti-hermitian SRG generator.
-The generator is defined as a commutator, $\eta(s) = [G, H(s)]$, where $G$ specifies the type of flow and $H(s)$ is the evolved Hamiltonian.
-The choice in $G$ determines the pattern of decoupling in the Hamiltonian.
-\\
+where $\eta(s)=\frac{dU(s)}{ds} U^{\dagger}(s) = -\eta^{\dagger}(s)$ is 
+the anti-hermitian SRG generator.
+For the free-space SRG, the generator is typically defined as a commutator, $\eta(s) = [G, H(s)]$, where $G$ specifies the type of flow.
+The choice of $G$ determines the pattern of decoupling in the Hamiltonian.
 
-By setting $G=H_D(s)$, the diagonal of the Hamiltonian, the Hamiltonian is driven to band-diagonal form.
-This choice was implemented by Wegner in condensed matter physics \cite{Wegner:1994ab}.
-In a similar option used in nuclear physics, $G$ is set to the relative kinetic energy, $T_{rel}$, which also drives to band-diagonal form.
-In most cases, these two choices give the same evolved operators.
-In exceptional cases, which will be discussed later in the paper, the two band-diagonal choices can have drastically different behavior.
-For band-diagonal decoupling, it is convenient to define $\lambda \equiv s^{-1/4}$ which roughly measures the width of the band-diagonal in the decoupled operator.
-For block-diagonal decoupling \cite{Anderson:2008mu},
+By setting $G=H_D(s)$, the diagonal of the Hamiltonian, the Hamiltonian is driven to band-diagonal form~\cite{Wegner:1994ab}.
+In low-energy nuclear physics, $G$ is usually taken to be the relative kinetic energy, \Trel; i.e., the diagonal of the potential is not included in $G$. 
+In most nuclear physics applications these two choices give the same evolved operators. 
+But in exceptional cases involving evolution across bound states, which we consider in the next section, the two band-diagonal choices can have drastically different behaviors~\cite{Glazek:2008pg,Wendt:2011qj}.
+For band-diagonal decoupling, it is convenient to define $\lambda \equiv s^{-1/4}$, which roughly measures the width of the band-diagonal in the decoupled Hamiltonian~\cite{Anderson:2010aq}.
+
+For block-diagonal decoupling~\cite{Anderson:2008mu,Szpigel:2016rbt}, $G$ is formed by splitting the Hamiltonian into low- and high-momentum sub-blocks as specified by a momentum separation scale $\LambdaBD$,
 %
@@
 	\end{pmatrix}
-	\equiv H_{BD}(s),
+	\equiv H_{BD}(s).
 \end{eqnarray}
 %
-where $P$ and $Q$ are low- and high-momentum projection operators, the Hamiltonian is split into low- and high-momentum sub-blocks by specifying a separation in momentum $\Lambda$ and taking $s \rightarrow \infty$.
-In momentum-space, the projection operators are step functions defined by the sharp cutoff in $\Lambda$.
-These transformations are similar to V\textsubscript{low $k$} transformations \cite{Bogner:2001gq, Bogner:2001jn, Bogner:2003wn} but keep the high-momentum matrix elements non-zero, although entirely decoupled from the low-momentum sub-block.
-Generally, the flow equation (\ref{eq:srg_flow}) is solved up to some finite value of $s$ with a high-order ODE solver.
-For notational convenience, we write the generators without the $s$ dependence in the rest of the paper.
-\\
+Here $P$ and $Q$ are low- and high-momentum projection operators.
+In momentum space, the projection operators are step functions defined by the sharp cutoff $\LambdaBD$, although smoothed versions are also possible and may be preferred in some applications to avoid numerical artifacts~\cite{Anderson:2008mu}.
+These transformations are similar to V\textsubscript{low $k$} transformations~\cite{Bogner:2001gq,Bogner:2001jn,Bogner:2003wn} but keep the high-momentum matrix elements non-zero, maintaining a unitary transformation in the full space.
+Complete decoupling of the blocks is in principle only reached in the $s \rightarrow \infty$ limit. 
+In practice it is sufficient to solve the flow equation \eqref{eq:srg_flow} up to some finite value of $s$ with a high-order ODE solver such that the remaining ``neck'' between blocks is much narrower than $\LambdaBD$.
 
-The decoupling of matrix elements does not necessarily hold in other operators as it does in the Hamiltonian.
-In a previous work \cite{Anderson:2010aq}, it was shown that SRG transformations induce low-momentum contributions in high-momentum operators and change very little in low-momentum operators.
-We investigate whether this is a general trend of the SRG for any potential and SRG generator.
-Instead of solving another set of flow equations, we apply SRG band- and block-diagonal transformations to other operators by building the unitary transformations explicitly using the eigenvectors of the initial and evolved Hamiltonians.
-SRG-evolved operators depend on the NN interaction despite having the same initial operator, since the flow equation (\ref{eq:srg_flow}) depends on $H(s)$ from the definition of $\eta(s)$.
-\\
+The SRG procedure can be implemented by solving the flow equation Eq.~\eqref{eq:srg_flow} for the evolved Hamiltonian simultaneously with other operators of interest.
+However, one can also solve Eq.~\eqref{eq:srg_flow} exclusively for the evolved Hamiltonian and build the unitary transformation directly using the eigenvectors of the evolved and initial Hamiltonians (as is done in Sec.~\ref{sec:evolution_other_operators}).
+Another approach is to solve the following equation for the unitary transformation
+%
+\begin{eqnarray}
+	\label{eq:unitary_trans}
+	\frac{dU(s)}{ds} = \eta(s) U(s),
+\end{eqnarray}
+%
+which arises in an intermediate step in deriving Eq.~\eqref{eq:srg_flow}.
+This is the starting point in the Magnus expansion implementation of the SRG.
 
-There has also been renewed interest in studying chiral interactions at high cutoffs \cite{Tews:2018sbi}.
-In spin-triplet channels and at leading-order (LO), taking the cutoff to high values can result in spurious, deeply bound states from a highly singular short-ranged tensor force.
-In principle, these deep bound states are outside the range of the EFT and are absorbed by counterterms at higher order.
-In \cite{Wendt:2011qj}, it was shown that band-diagonal SRG decoupling of NN potentials in partial waves with spurious bound states differs significantly depending on the choice of SRG generator.
-These high cutoff potentials provide a unique opportunity to understand some of the previous points about universality, the choice of SRG generator and decoupling, as well as a good test problem for a variant of the SRG, which utilizes the Magnus expansion \cite{Morris:2015yna}.
-\\
+The Magnus expansion gives us the capability to solve for the SRG unitary transformation with negligible violations of unitarity from numerically solving the ODEs,%
+\footnote{There is a small numerical violation of unitarity in the standard approach to solving SRG equations due to accumulated time-step errors.
+With the Magnus expansion, unitarity is preserved to much higher precision because of the form of the transformation, as detailed in Sec.~\ref{sec:magnus_expansion_formalism}.}
+after which it can be applied to any other operator of interest~\cite{Morris:2015yna}.
+By utilizing an exponential parameterization for the transformation, $U(s)=e^{\Omega(s)}$, Eq.~\eqref{eq:unitary_trans} is recast as a flow equation for the anti-Hermitian operator $\Omega(s)$.
+The solution of the flow equation for $\Omega(s)$ permits the use of cheap low-order ODE methods since the exponentiated operator is still unitary even if it has accumulated non-negligible time-step errors~\cite{Morris:2015yna}.
+The Magnus expansion also offers important advantages over the direct solution of Eq.~\eqref{eq:unitary_trans} in Fock space, where practical calculations require operators to be truncated at the $a-$body level ($a<A$).
+For instance, even if the Magnus flow equations are truncated at the two-body level, the resulting unitary transformation contains higher-body components from the exponentiation of $\Omega$.%
+\footnote{This is similar to the advantages of truncated Coupled Cluster theory calculations relative to truncated Configuration Interaction calculations.}
 
-The Magnus expansion gives the SRG the capability to solve for the unitary transformation explicitly which can then be applied to any other operator of interest.
-This offers a huge numerical simplification in Fock-space where the matrix size of operators can become very large.
-The Magnus expansion is often used in in-medium SRG (IMSRG) calculations to solve the nuclear many-body problem directly.
-In some IMSRG calculations, intruder states can shift to the energy scale of the reference state in valence-space and severely distort low-energy properties.
-It is not understood how the IMSRG procedure evolves intruder state systems.
-Due to the prominence of the Magnus expansion in IMSRG, one must first understand if the Magnus approach matches the typical approach for difficult systems before investigating the intruder state problem.
-For this reason, NN potentials with spurious bound states offer a good test laboratory for the Magnus implementation to better understand if the Magnus is equivalent to the SRG approach.
-\\
+Due to these advantages, most large-scale IMSRG calculations now utilize the Magnus expansion.
+There are still open problems though.
+For instance, in applications of the IMSRG to derive effective valence shell model Hamiltonians in multi-shell valence spaces, intruder states, which are low-lying states whose wave functions are dominated by high-energy configurations outside the model space, can severely distort low-energy properties or even prevent the flow from converging.
+It is not yet fully understood how the IMSRG procedure evolves intruder state systems, though it appears that induced three- and higher-body operators rapidly grow in size for such systems, destroying the cluster hierarchy ($2N \gg 3N \gg 4N \gg \ldots$) in the evolved Hamiltonian~\cite{Stroberg:2019mxo}.
 
-\noindent{%
-\textbf{Overview of sections.}
-}
+Interestingly, there is an analog to the intruder state problem in the much simpler two-nucleon problem.
+In spin-triplet channels and at leading-order (LO) in \chiEFT, taking the EFT cutoff to high values can result in spurious, deep-bound states due to the highly singular short-ranged tensor force from one-pion exchange.
+In principle, these deep-bound states are not a problem because they are outside the range of the EFT.
+In practice, there are subtleties analogous to the intruder state problem when one attempts to soften such Hamiltonians with free space SRG evolution.
+In Ref.~\cite{Wendt:2011qj}, it was shown that band-diagonal SRG decoupling of NN potentials in partial waves with spurious bound states fails for the standard $G=\Trel$ generator, as the flow forces the deep bound state into the low-momentum sector.
+As a result, there is no decoupling of high- and low-momentum physics, and the evolved interactions become increasingly singular at low momentum.
+In contrast, the Wegner generator $G=H_{D}$ succeeds at depositing the spurious state(s) along the diagonal in the high-momentum sector, which is more natural as it allows a clean decoupling of high- and low-momentum physics.
+Since these findings were for the direct solution of Eq.~\eqref{eq:srg_flow}, this  provides a good test case for the Magnus approach and we document its performance in detail.
+More generally, there has been renewed interest in studying chiral interactions at high cutoffs~\cite{Tews:2018sbi}. 
+These high-cutoff chiral potentials provide us a laboratory to explore the effects of the SRG generator on decoupling, universality, and SRCs.
+These issues also inform the behavior of standard \chiEFT\ potentials.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{SRG evolution of NN potentials}
-\label{sec:srg_evolution_nn_potentials}
+While interactions from \chiEFT\ have become the standard choice for \abi\ calculations of nuclei, they are not unique, even when restricted to the commonly used Weinberg power counting, because of many choices for regularization schemes and fitting protocols and even degrees of freedom (i.e., with or without Deltas).
+In the early applications of \chiEFT\ potentials to nuclei, these choices were not explored but in recent years there has been a proliferation of nucleon-nucleon (NN) potentials and associated three-nucleon forces (e.g., see Refs.~\cite{Epelbaum:2014efa,Gezerlis:2014zia,Piarulli:2014bda,Ekstrom:2015rta,Carlsson:2015vda,Reinert:2017usi,Ekstrom:2017koy,Entem:2017gor}).
+This diversification motivates us to revisit SRG operator evolution.
+Past studies were limited to phenomenological interactions or a single class of chiral interactions (namely the non-local-regulated potentials from Refs.~\cite{Entem:2003ft} or \cite{Epelbaum:2004fk}).
+Here we examine the fate of scheme dependence for new-generation NN potentials and associated operators as they are evolved to lower resolutions.
 
-% Summarize what we're looking at in this section and general conclusions. What did I not cover in the introduction?
-%
-%
-%-- Fig.~\ref{fig:potential_contours_RKE_Wegner} illustrates the SRG in a nutshell.
-Here, we evolve three partial wave channels of RKE N$^4$LO \cite{Reinert:2017usi} where the cutoff $\Lambda=450$ MeV to $\lambda=1.5$ fm$^{-1}$.
-We see that the off-diagonal elements of the potential approach zero and the potential is driven to band-diagonal form.
-%
-% Unnecessary figure.
-%\begin{figure}[H]
-%	\centering
-%	\subfloat[]{%
-%	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn111_1S0_Wegner_channel_label}%
-%	}
+One intriguing aspect is universality.
+By virtue of fitting to the same data or phase shifts, different \chiEFT\ potentials generate close to the same $S$-matrix in the energy range where there is a good fit; that is, the potentials are phase equivalent in that range.
+However, matrix elements of the potentials in momentum space differ significantly based on the EFT order and the choice of regulator function and cutoff (scale and scheme dependence). 
+Nevertheless, it has been observed that SRG transformations drive different NN potentials toward the same low-momentum matrix elements; in particular, this flow to universality is seen up to the momentum value of phase inequivalence~\cite{Bogner:2003wn,Bogner:2001gq,Dainton:2013axa}.
+We examine whether universality holds for modern chiral potentials but also address universality for other operators evolving under the corresponding SRG transformations.
+This has implications for the analysis of reactions at different resolution scales~\cite{Furnstahl:2013dsa,More:2015tpa,More:2017syr}.
 
-%	\subfloat[]{%
-%	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn111_3S1_Wegner_channel_label}%
-%	}
+The question of whether non-Hamiltonian operators decouple or take universal forms has not been fully addressed in the literature.%
+\footnote{Note that if the wave functions are decoupled, it is not necessary for the operators themselves to decouple to get decoupled matrix elements. See examples below.}
+In fact, the decoupling of matrix elements does not necessarily result for other operators as it does for the Hamiltonian.
+In previous work \cite{Anderson:2010aq,Bogner:2012zm}, it was found that SRG evolution induces low-momentum contributions in high-momentum operators and changes low-momentum operators very little, as might be expected from general EFT considerations.
+We investigate whether this is a general trend of the SRG for a wider selection of potentials and SRG generators, explicitly analyze the nature of the evolution for representative high-momentum and low-momentum operators, and relate these observations to the high-resolution picture of SRCs and the role of factorization.
 
-%	\subfloat[]{%
-%	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn111_1P1_Wegner_channel_label}%
-%	}
-%	\caption{Matrix elements of the RKE N$^4$LO potential SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator in the $^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) channels.}
-%	\label{fig:potential_contours_RKE_Wegner}
-%\end{figure}
-%
-Here, we analyze SRG evolution of various chiral potentials with the Wegner band-diagonal generator and the block-diagonal generator.
-In Fig.~\ref{fig:potential_contours_3S1_Wegner} we show three different SRG-evolved potentials in the $^3$S$_1$ channel: EM N$^3$LO (500 MeV cutoff) \cite{Entem:2003ft}, RKE N$^4$LO (450 MeV cutoff) \cite{Reinert:2017usi}, and Gezerlis \textit{et al.}~N$^2$LO (1 fm cutoff) \cite{Gezerlis:2014zia}.
-A major difference in these three potentials are the regulator functions in the contact and pion-exchange terms.
-The EM N$^3$LO interaction is a non-local potential where both contact and pion-exchange interactions feature a non-local regulator function of the form exp$[-(k/\Lambda)^{2n}-(k'/\Lambda)^{2n}]$, where $\Lambda$ is the momentum-space cutoff and $n$ is an integer ($n=2$ in this case).
-However, a non-local regulator function for pion-exchange contributions can introduce regulator artifacts for cutoffs $\Lambda$ lower than the breakdown scale $\Lambda_b$.
-Several semi-local chiral potentials have been introduced to reduce regulator artifacts, such as the RKE N$^4$LO potential.
-Here, a local regulator function is applied for the long-range interactions in momentum-space, while a non-local regulator function is used for the short-range interactions.
-In some instances, non-local interactions are not suitable for $\textit{ab initio}$ approaches such as the quantum Monte Carlo (QMC) method motivating the need for fully local potentials.
-The Gezerlis \textit{et al.}~N$^2$LO potential is an example of a local interaction where the long-range terms have a local regulator function in coordinate-space and the short-range terms have a local regulator function in momentum-space.
-\\
-
-These chiral interactions give the same low-energy phase shifts but the matrix elements of the potential are entirely different.
-In \cite{Dainton:2013axa}, with the SRG $T_{rel}$ generator, different phenomenological potentials were driven to universal low-momentum matrix elements.
-We see in Fig.~\ref{fig:potential_contours_3S1_Wegner} that the modern chiral potentials follow the same pattern.
-On the left-hand column where $\lambda=6$ fm$^{-1}$, the three potentials differ.
-Further along the SRG evolution (right-hand side), the potentials are driven to band-diagonal form where the upper right corner of the contours, corresponding to low-momentum matrix elements, are the same.
-Note, we use the Wegner generator, $G=H_D$, in this SRG-evolution instead of $T_{rel}$.
-For realistic nuclear interactions, these two choices are essentially the same.
-There will only be a difference Only in extreme cases will there be a difference in the SRG-evolution.
-Lastly, we have checked that the same SRG flow to universality occurs in other partial wave channels.
-%
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Wegner_potential_label}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn111_3S1_Wegner_potential_label}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn222_3S1_Wegner_potential_label}%
-	}
-	\caption{Matrix elements of the EM N$^3$LO 500 MeV (a), RKE N$^4$LO 450 MeV (b), and Gezerlis \textit{et al.}~N$^2$LO 1 fm (c) potentials SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator in the $^3$S$_1$ channel.}
-	\label{fig:potential_contours_3S1_Wegner}
-\end{figure}
-%
-% Transition to SRG-decoupling in next paragraph.
-\noindent{%
--- Fig.~\ref{fig:potential_contours_1P1_RKE} shows the SRG-evolved RKE N$^4$LO (450 MeV cutoff) potential in the $^1$P$_1$ channel for two SRG generators: the Wegner and block-diagonal generators which drive the potential to band- and block-diagonal form, respectively.
-We continue to evolve to band-diagonal form with respect to the parameter $\lambda$, but for the block-diagonal generator, we label sub-plots with the parameter $\Lambda$ which characterizes the sharp cutoff in decoupling the low- and high-momentum matrix elements.
-}
-\\
-% Can completely different chiral potentials be driven to the same potential?
--- Takeaways from Fig.~\ref{fig:potential_contours_1P1_RKE}: smooth decoupling for Wegner and sharp for block-diagonal, each unique generator should have its own type of universality.
-Check this more quantitatively by comparing matrix element ``slices''.
-%
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn111_1P1_Wegner_generator_label}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn111_1P1_Block-diag_generator_label}%
-	}
-	\caption{Matrix elements of the RKE N$^4$LO potential SRG-evolving right to left under transformations with Wegner (a) and block-diagonal (b) generators in the $^1$P$_1$ channel.
-Here, we use $\lambda$ for Wegner evolution in the top row and $\Lambda$ for block-diagonal evolution in the bottom row.
-For block-diagonal evolution, we fix $\lambda=1.5$ fm$^{-1}$.}
-	\label{fig:potential_contours_1P1_RKE}
-\end{figure}
-%
-\noindent{%
--- Fig.~\ref{fig:phase_shifts} shows the NN phase shifts of EM N$^3$LO, RKE N$^4$LO, and Gezerlis \textit{et al.}~N$^2$LO potentials in the $^1$S$_0$, $^3$S$_1$, and $^1$P$_1$ channels.
-In \cite{Dainton:2013axa}, it was found that phase equivalence up to some value of momentum $k$ implies matrix element equivalence up to the same value of $k$ in SRG-evolved potentials.
-We verify this conclusion by checking the matrix elements in Fig.~\ref{fig:potential_slices_1S0} where we see a collapse of the different potential matrix elements to the same line in the last column ($\lambda=1$ fm$^{-1}$).
-Note, Figs.~\ref{fig:potential_slices_1S0}-\ref{fig:potential_slices_1P1} show both Wegner and block-diagonal evolution where the solid lines correspond to the Wegner generator and dash-dotted to block-diagonal evolution.
-We see each generator collapses the potential to a different form because the low- and high-momentum matrix elements decouple in a different manner.
-}
-\\
--- In the $^3$S$_1$ channel, we see a slight deviation in the lowest momentum potential matrix element from EM N$^3$LO and the other two potentials.
-This is due to a minor difference in the deuteron binding energy ($\approx 1\%$ difference).
-\\
--- The bottom row of Fig.~\ref{fig:potential_slices_1P1} shows $V(k,0.5)$ instead of $V(k,0)$ because the far off-diagonal matrix elements in the $^1$P$_1$ channel are all zero.
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_1S0_kvnns_10_111_222}%
-	}
-	\quad
-	\subfloat[]{%
-	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_3S1_kvnns_10_111_222}%
-	}
-	\quad
-	\subfloat[]{%
-	\includegraphics[clip,width=0.3\columnwidth]{SRG_observables/phase_shifts_1P1_kvnns_10_111_222}%
-	}
-	\caption{$^1$S$_0$ (a), $^3$S$_1$ (b), and $^1$P$_1$ (c) phase shifts for the EM N$^3$LO (solid black), RKE N$^4$LO (red dash-dotted), and Gezerlis \textit{et al.}~N$^2$LO (blue dashed) potentials.}
-	\label{fig:phase_shifts}
-\end{figure}
-%
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_1S0_kvnns_10_111_222_lamb1,0}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_1S0_kvnns_10_111_222_lamb1,0}%
-	}
-	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the EM N$^3$LO (black), RKE N$^4$LO (red) and Gezerlis \textit{et al.}~N$^2$LO (blue) potentials SRG-evolving right to left under transformations with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^1$S$_0$ channel.
-Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution.
-For block-diagonal evolution, we fix $\lambda=1$ fm$^{-1}$.}
-	\label{fig:potential_slices_1S0}
-\end{figure}
-%
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_3S1_kvnns_10_111_222_lamb1,0}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_3S1_kvnns_10_111_222_lamb1,0}%
-	}
-	\caption{Same as Fig.~\ref{fig:potential_slices_1S0} but in the $^3$S$_1$ channel.}
-	\label{fig:potential_slices_3S1}
-\end{figure}
-%
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_1P1_kvnns_10_111_222_lamb1,0}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_1P1_kvnns_10_111_222_lamb1,0}%
-	}
-	\caption{Same as Figs.~\ref{fig:potential_slices_1S0} and \ref{fig:potential_slices_3S1} but in the $^1$P$_1$ channel.}
-	\label{fig:potential_slices_1P1}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Evolution of other operators}
-\label{sec:evolution_other_operators}
-
-\noindent{%
--- SRG operator evolution for different potentials and generators.
-}
-\\
--- General questions to address: universality for operators, different generators.
-\\
--- Give relevant equations. Unitary transformation equation.
-\\
--- Momentum projection operator.
-\\
--- Relevant equations: just the momentum projection operator in momentum-space.
-%
-\begin{itemize}
-	\item Contours and general behavior: SRG transformation shifts strength of operator to low-momentum.
-	\item Deuteron momentum distributions. Why does this make sense with the transformed operators?
-	\item Diagonals and far off-diagonals. Universality.
-	\item Same questions but with figures of the integrand.
-\end{itemize}
-%
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/momentum_projection_diag_q3,00_3S1_kvnns_10_111_222_lamb1,5}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/momentum_projection_off-diag_q3,00_3S1_kvnns_10_111_222_lamb1,5}%
-	}
-	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the momentum projection operator under SRG transformations with EM N$^3$LO (black), RKE N$^4$LO (red) and Gezerlis \textit{et al.}~N$^2$LO (blue) potentials evolving right to left with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^3$S$_1$ channel.
-Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution.
-For block-diagonal evolution, we fix $\lambda=1.5$ fm$^{-1}$.}
-	\label{fig:momentum_proj_3S1}
-\end{figure}
-%
--- Note, the unitary transformations and evolved wave functions for different potentials are not the same (at low momentum too) which implies that evolved operators cannot have the same universality property as the evolved potentials since they are dependent on the evolved wave functions.
-\\
--- $\hat{r}^2$ operator.
-\\
--- Relevant equations: operator in coordinate-space and Hankel transformation.
-\\
--- Add continuum state momentum distributions and how to understand operator evolution.
+The plan of the paper is as follows.
+We first revisit the high-cutoff problem, and test the Magnus approach in Sec.~\ref{sec:high_cutoffs_magnus_exp}.
+We consider evolution of new-generation NN Hamiltonians in Sec.~\ref{sec:srg_evolution_nn_potentials} and then turn to other operators in Sec.~\ref{sec:evolution_other_operators}.
+Our conclusions and outlook are summarized in Sec.~\ref{sec:summary}.
 
@@
 \section{High cutoffs and the Magnus expansion}
-\label{sec:magnus_expansion}
-% Split this section into two sections?
+\label{sec:high_cutoffs_magnus_exp}
 
-\noindent{%
-\textbf{High cutoffs}
-}
-\begin{itemize}
-	\item Cutoff dependence in non-local LO (Wendt) potential. Recap of Wendt.
-	\item Band- and block-diagonal evolution and universality. Add figure analogous to Fig.~\ref{fig:potential_slices_3S1} but for $\Lambda=4$, $9$, and $20$ fm$^{-1}$.
-	\item Spurious bound state(s). Decoupling with block-diagonal.
-	\item Transition to Magnus expansion.
-\end{itemize}
+%........................................................................
+\subsection{High cutoffs and spurious bound states}
+\label{sec:high_cutoffs}
+
 %
-\begin{figure}[H]
-	\centering
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_diag_3S1_kvnns_900_901_902_lamb1,2}%
-	}
-
-	\subfloat[]{%
-	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_off-diag_3S1_kvnns_900_901_902_lamb1,2}%
-	}
-	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the non-local LO potentials at cutoffs $\Lambda=4$ (black), $9$ (red) and $20$ (blue) fm$^{-1}$ SRG-evolving right to left under transformations with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^3$S$_1$ channel.
-Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution.
-For block-diagonal evolution, we fix $\lambda=1.2$ fm$^{-1}$.}
+\begin{figure*}[tbh]
+    \includegraphics[clip,width=0.8\textwidth]{potential_slices_3S1_kvnns_900_901_902.pdf}
+	\caption{Diagonal and far off-diagonal matrix elements of non-local LO potentials at cutoffs $\Lambda=4$ (black), $9$ (red) and $20$\,fm$^{-1}$ (blue), SRG-evolving left to right under transformations with Wegner (solid) and block-diagonal (dashed) generators in the $^3$S$_1$ channel.
+	We vary the SRG flow parameter $\lambda$ for Wegner evolution and fix it at $\lambda=1.2$\,fm$^{-1}$ for block-diagonal evolution.
+The decoupling scale in the block-diagonal generator is denoted by $\LambdaBD$.}
 	\label{fig:potential_slices_high_cutoffs}
-\end{figure}
+\end{figure*}
 %
 
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-\subsection{Formalism}
+The \chiEFT\ potentials used in most \abi\ nuclear calculations are not renormalizable in the sense that dependence on the regulator is not suppressed by taking the momentum cutoff increasingly high (or low, if a coordinate-space regulator).
+However, Nogga \textit{et al.}~\cite{Nogga:2005hy} showed that the LO version of these interactions, with promoted counterterms in some channels, \emph{is} renormalizable in this sense.
+There is active work on renormalizable power counting for \chiEFT\ beyond LO (see references cited in \cite{Tews:2018sbi}).
+
+The LO theory at high cutoff is a useful laboratory for testing the SRG (as well as providing insight into the evolution of SRC physics, see Sec.~\ref{sec:evolution_other_operators}).
+It features the appearance of spurious, deeply bound states in some channels, which is ultraviolet physics beyond the range of the EFT, and thus does not violate EFT principles.
+However, these present a major challenge to the SRG.
+Wendt \textit{et al.} studied SRG band-diagonal transformations of high-cutoff LO potentials~\cite{Wendt:2011qj} and showed that channels with spurious deep-bound states did not automatically exhibit the expected decoupling and universality of the potential if the conventional SRG generator is used.
+In particular, the spurious bound state(s) is driven from high to low momentum in the evolved potential when applying transformations with $G=\Trel$.
+The observables remain unchanged because the transformation is still unitary, but the potential and wave functions are altered significantly by the presence of the spurious bound state at low momentum.
+In contrast, if the Wegner generator is used, the spurious state(s) is decoupled, subsequently yielding universality in low-momentum matrix elements of the potential.
+
+In Fig.~\ref{fig:potential_slices_high_cutoffs} we show SRG band- and block-diagonal evolution of high-cutoff non-local potentials at LO, 
+which consists of one-pion exchange and a contact interaction.
+We restrict our attention to the $^3$S$_1$--$^3$S$_1$ sub-block of the coupled $^3$S$_1$--$^3$D$_1$ channel (note that spurious, deeply bound states only appear in spin-triplet channels~\cite{Nogga:2005hy}).
+The contact interaction is determined by fitting the associated low-energy constant to $E_{\text{lab}}=10$ MeV phase shift data.
+In the diagonal matrix elements of Fig.~\ref{fig:potential_slices_high_cutoffs}, we see a steep drop-off in the Wegner transformed potentials around $k \approx 1.6-1.75$\,fm$^{-1}$.
+This corresponds to the decoupled spurious bound state ($\varepsilon \approx -2000$ MeV).
+The value of momentum where the spurious bound state decouples is a scheme-dependent quantity that is sensitive to how momentum space is discretized (the momentum mesh).
+Due to this dependence, we have been unable to predict the value of $k$ at which the spurious state decouples.
+However, when the spurious state is decoupled outside the low-momentum part of the potential, the Wegner evolution collapses the low-momentum matrix elements of the different potentials to the same mesh-independent values in accordance with universality.
+There is no drop-off in the $\Lambda=4$\,fm$^{-1}$ potential as it has no spurious state.
+
+We also see universality for the block-diagonal evolved matrix elements as before, but there is no noticeable influence from the spurious bound state.
+This is due to the band-diagonal generator locally decoupling the matrix elements whereas the block-diagonal generator cleanly separates the potential into a low-momentum sub-block and a high-momentum sub-block.
+In the limit $\lambda \rightarrow 0$ with $\LambdaBD$ sufficiently low, the spurious deep-bound state(s) is contained entirely in the high-momentum sub-block.
+We verified this by diagonalizing the sub-blocks separately to see which one contained the spurious bound state.
+We identify $\LambdaBD \approx 4.5$\,fm$^{-1}$ as the approximate value at which the spurious bound state switches from the low-momentum sub-block to the high-momentum sub-block.
+Thus, the block-diagonal transformations decouple the spurious state(s) at a higher value of momentum than the Wegner transformations, which isolates the physical states more effectively.
+Tests with different meshes found the same value of momentum, suggesting a scheme-independent result.
+However, we do not have an analytic understanding of these scales.
+
+We can draw a loose analogy to intruder states corrupting low-energy physics in IMSRG calculations with spurious bound states corrupting universality in SRG-evolved potentials.
+From the analysis so far, it is evident that the choice of SRG generator is important in properly decoupling the high-momentum spurious state from low-momentum physics.
+It would be interesting to generalize this conclusion to an $A$-body system and analyze how different generators deal with intruder states.
+However, we must first verify that the Magnus approach is the same as the conventional SRG approach for difficult systems because of its use in IMSRG calculations.
+In the following sub-sections, we present the Magnus approach and compare to the conventional SRG using high-cutoff potentials with spurious states as a test case.
+
+%........................................................................
+\subsection{The Magnus expansion: Formalism}
 \label{sec:magnus_expansion_formalism}
 
-% What was said in the introduction: The Magnus expansion gives the SRG the capability to solve for the unitary transformation explicitly which can then be applied to any other operator of interest.
-This offers a huge numerical simplification in Fock-space where the matrix size of operators can become very large.
-The Magnus expansion is often used in in-medium SRG (IMSRG) calculations to solve the nuclear many-body problem directly
-\noindent{%
--- Motivation: simplifies computational problem for evolving multiple operators, exact unitarity.
-}
-\\
--- We now consider the Magnus implementation.
-\\
--- Mathematically speaking, the Magnus expansion is a method for solving an initial value problem associated with a linear ordinary differential equation (ODE).
-\\
--- Formal details of the Magnus expansion are discussed in \cite{Blanes:2009ab}.
-\\
--- We will introduce the Magnus expansion in the context of SRG evolving any operator.
-\\
--- In an intermediate step in deriving Eqn. (\ref{eq:srg_flow}), we have a linear ODE for $U(s)$,
+We briefly review the formalism of the Magnus expansion and its use in the SRG.
+Mathematically speaking, the Magnus expansion is a method for solving an initial value problem associated with a linear ordinary differential equation.
+Formal details of the Magnus expansion are discussed in \cite{Blanes:2009ab}.
+We will introduce the Magnus expansion in the context of SRG operator evolution.
+
+%
+\begin{figure*}[tbh]
+	\includegraphics[clip,width=0.8\textwidth]{potential_slices_kvnn_901_Wegner_k_magnus_values_2_6_10.pdf}%
+	\caption{Comparison of SRG- and Magnus-evolved diagonal and far off-diagonal matrix elements of the non-local LO potential (9\,fm$^{-1}$) in the $^3$S$_1$ channel for several truncations $k_{\rm max}$ in the Magnus sum \eqref{eq:magnus_omega}.
+Here we evolve in $\lambda$ left to right using the Wegner generator $G=H_D$.}
+	\label{fig:potential_slices_high_cutoffs_Wegner}
+\end{figure*}
+%
+\begin{figure*}[tbh]
+	\includegraphics[clip,width=0.8\textwidth]{potential_slices_kvnn_901_T_k_magnus_values_2_6_10.pdf}%
+	\caption{Same as in Fig.~\ref{fig:potential_slices_high_cutoffs_Wegner} but with $G=\Trel$.}
+	\label{fig:potential_slices_high_cutoffs_T}
+\end{figure*}
+%
+
+We can solve Eq.~\eqref{eq:unitary_trans} with a solution $U(s)=e^{\Omega(s)}$ where $\Omega^{\dagger}(s) = -\Omega(s)$, and $\Omega(0) = 0$.
+$\Omega(s)$ is expanded as a power series in $\eta(s)$:
 %
 \begin{eqnarray}
-	\label{eq:unitary_trans}
-	\frac{dU(s)}{ds} = \eta(s) U(s).
+    \label{eq:magnus_expansion}
+    \Omega(s) = \sum_{n=1}^{\infty} \Omega_n(s),
 \end{eqnarray}
 %
--- Magnus showed that one can solve the following equation with a solution $U(s)=e^{\Omega(s)}$ where $\Omega(s)$ is expanded as a power series, $\sum_{n}^{\infty} \Omega_n$ (referred to as the Magnus expansion or Magnus series).
-\\
--- The terms of the series are given by integral expressions involving $\eta(s)$ (again, see \cite{Blanes:2009ab, Magnus:1954zz} for details).
-\\
--- For our case, we focus on the formally exact derivative of $\Omega(s)$,
+where the terms of the series are given by integral expressions involving $\eta(s)$,
+%
+\begin{align}
+    \label{eq:omega_terms}
+    \Omega_1(s) &= \int_0^s\, ds_1 \eta(s_1), \nonumber \\        
+    \Omega_2(s) &= \frac{1}{2} \int_0^s ds_1 \int_0^{s_1} ds_2 \, [\eta(s_1), \eta(s_2)], \\
+    & \quad\vdots \nonumber
+\end{align}
+%
+Equation~\eqref{eq:magnus_expansion} is referred to as the Magnus expansion.
+(Again, see \cite{Blanes:2009ab, Magnus:1954zz} for further
+details.)
+We avoid computing the integral terms $\Omega_n(s)$ since it requires storing $\eta(s)$ over a range of $s$ values, which is impractical for large-scale calculations.
+We focus instead on the derivative of $\Omega(s)$,
 %
@@
 where $B_k$ are the Bernoulli numbers, $ad_{\Omega}^{0}(\eta)=\eta(s)$, and $ad_{\Omega}^{k}(\eta)=[\Omega(s),ad_{\Omega}^{k-1}(\eta)]$.
-\\
--- We integrate this differential equation to find $\Omega(s)$ and evaluate the unitary transformation directly.
-\\
--- Then the evolved operator can be evaluated with the BCH formula:
+We integrate this differential equation to find $\Omega(s)$ and evaluate the unitary transformation.
+Then the evolved operator can be evaluated with the Baker-Cambell-Hausdorff formula~\cite{Morris:2015yna},
 %
@@
 	\label{eq:bch}
-	O(s) = e^{\Omega(s)} O e^{-\Omega(s)} = \sum_{k=0}^{\infty} \frac{1}{k!} ad_{\Omega}^{k}(O).
+	O(s) = e^{\Omega(s)} O(0) e^{-\Omega(s)} = \sum_{k=0}^{\infty} \frac{1}{k!} ad_{\Omega}^{k}(O).
 \end{eqnarray}
 %
--- As $k \rightarrow \infty$ in both sums in Eqns. (\ref{eq:magnus_omega}) and (\ref{eq:bch}) the Magnus transformation matches the SRG transformation exactly.
-\\
--- We investigate several truncations $k_{max}$ in Eqn. (\ref{eq:magnus_omega}) and take many terms, $k_{max} \sim 25$, in Eqn. (\ref{eq:bch}).
-\\
--- There are significant advantages in the Magnus implementation.
-\\
--- In the typical approach, the numerical error associated with solving the flow equation affects the accuracy of the observables for the evolved operator.
-\\
--- Therefore, one must use a high-order ODE solver in integrating the flow equation (\ref{eq:srg_flow}).
-\\
--- In the Magnus implementation, unitarity is guaranteed by the form of $U(s)$; in fact, one could solve Eqn.
-(\ref{eq:magnus_omega}) with a simple first-order Euler step-method keeping the same observables while decoupling the operator as desired.
-\\
--- This offers a decent computational speed-up by avoiding a high-order solver.
-\\
--- In this paper, we demonstrate this advantage by applying the Magnus implementation using the first-order Euler step-method.
-\\
--- The second major advantage involves the evolution of multiple operators.
-\\
--- In many other situations, one may be interested in evolving several operators at a time.
-\\
--- In the SRG procedure, we would have another set of coupled equations in Eqn. (\ref{eq:srg_flow}), drastically increasing memory usage.
-\\
--- Each additional operator increases the set of equations - say $N$ equations - by another factor of $N$.
-\\
--- In the Magnus, one only needs $\Omega(s)$ to consistently evolve several operators.
-\\
--- We avoid the cost in memory by directly constructing $U(s)=e^{\Omega(s)}$.
-\\
--- This is especially useful in IMSRG calculations where the model space can be very large.
-\\
--- In the next section, we discuss results from Magnus-evolved large-cutoff potentials focusing on the flow of the potential, observables, and operator evolution.
+As $k \rightarrow \infty$ in both sums in Eqs.~\eqref{eq:magnus_omega} and \eqref{eq:bch}, the Magnus transformation matches the SRG transformation exactly.%
+\footnote{Note that this equivalence is exact only if both series converge and the ODEs in Eq.~\eqref{eq:magnus_omega} are solved exactly.}
+We investigate several truncations $k_{\rm max}$ in Eq.~\eqref{eq:magnus_omega} and take many terms, $k_{\rm max} \sim 25$, in Eq.~\eqref{eq:bch}.
 
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-\subsection{Results}
+%
+\begin{figure*}[tbh]
+	\includegraphics[clip,width=0.67\textwidth]{eta_omega_norms_kvnns_900_901_902_3S1_Wegner_k_magnus_6_ds1,0e-05.pdf}%
+	\caption{Frobenius norms of $\eta(s)$ and $\Omega(s)$ from Magnus-evolving the high-cutoff LO potentials in the $^3$S$_1$--$^3$D$_1$ coupled channel: $\Lambda=4$ (black dashed), $9$ (red dash-dotted) and $20$\,fm$^{-1}$ (blue solid) where $G=H_D$ and $k_{\rm max}=6$.}
+	\label{fig:eta_omega_norms}
+\end{figure*}
+%
+
+There are significant advantages to the Magnus implementation in IMSRG calculations.
+In the conventional approach, the numerical error associated with solving Eq.~\eqref{eq:srg_flow} accumulates directly in the operator and can distort the eigenvalues of the transformed Hamiltonian.
+To guard against this, one must use a high-order ODE solver, which can become prohibitive for large-scale calculations due to the memory-intensive nature of such solvers.  
+In the Magnus implementation, unitarity is guaranteed by the form of $U(s)$.
+One can solve Eq.~\eqref{eq:magnus_omega} with a low-order stepping method with a substantially lower memory footprint, which nevertheless preserves the eigenvalues exactly while still decoupling as desired.
+Here we demonstrate this advantage by applying the Magnus implementation using the first-order Euler step-method.
+
+The second major advantage involves the evolution of multiple operators.
+In many situations, one may be interested in evolving several operators at a time.
+In the standard procedure, we would have another set of coupled equations in Eq.~\eqref{eq:srg_flow}, drastically increasing memory usage.
+Each additional operator increases the set of equations - say $N$ equations - by another factor of $N$.
+In the Magnus approach, one only needs $\Omega(s)$ to consistently evolve several operators via explicit construction of $U(s)=e^{\Omega(s)}$.
+While operator evolution is not an issue for NN evolution, the capability to calculate $U(s)$ directly is crucial in IMSRG calculations where the model space can be very large.
+While it is possible to solve for $U(s)$ by directly integrating Eq.~\eqref{eq:unitary_trans}, this suffers from the same memory limitations as Eq.~\eqref{eq:srg_flow} due to the necessity of a high-order ODE solver to guard against the loss of unitarity.
+
+%........................................................................
+\subsection{The Magnus expansion: Results}
 \label{sec:magnus_expansion_results}
 
-\noindent{%
--- Comparison to Wendt problem.
+We compare the SRG evolution of the non-local LO potential with cutoff at 9\,fm$^{-1}$ using the conventional approach and the Magnus approach.
+At this particular cutoff, the potential has one spurious bound state in the $^3$S$_1$--$^3$D$_1$ coupled channel of about $-2000$ MeV in addition to the deuteron bound-state energy. 
+Figures~\ref{fig:potential_slices_high_cutoffs_Wegner} and \ref{fig:potential_slices_high_cutoffs_T} show the diagonal and far off-diagonal matrix elements of the evolving potential using both methods at several different truncations $k_{\rm max}$ for Magnus-evolution for the two band-diagonal generators, $G=H_D$ and \Trel, respectively.
+In both cases, as we take higher values of $k_{\rm max}$ the Magnus evolution approaches the SRG despite the presence of a spurious bound state.
+The agreement is rather poor for the lowest truncation shown, $k_{\rm max}=2$.
+Although the observables for the Magnus-evolved potentials are still unaltered independent of $k_{\rm max}$, the presence of the decoupled spurious bound state has effects on the flow to band-diagonal form.
+That is, there is more variation with respect to $k_{\rm max}$ in band-diagonal decoupling of these potential matrix elements.
+
+We have tested other, softer potentials such as the lower cutoff of 4\,fm$^{-1}$ and higher-order chiral potentials, and found that the Magnus implementation always works as intended.
+The Magnus implementation nearly matches the SRG results in all cases where small differences come from the difference in ODE solver and truncations in the Magnus approach.
+Thus, we only show results for the high cutoff of 9\,fm$^{-1}$.
+
+In some cases, $\eta(s)$ grows as $s$ increases, leading to convergence issues in the Magnus expansion.
+When $\eta(s)$ begins increasing, $\Omega(s)$ grows prohibitively large.
+In Ref.~\cite{Blanes:2009ab} the convergence of the Magnus expansion is described in terms of the Frobenius norm of $\eta(s)$, stating that convergence is satisfied if $\int_0^S ||\eta(s)|| ds < r_c$ over an interval $0 < s < S$, where $r_c = \pi$ for calculations involving real matrices.
+
+In Fig.~\ref{fig:eta_omega_norms} we show the Frobenius norms of $\eta(s)$ and $\Omega(s)$ for the three high-cutoff potentials tested using $G=H_D$.
+The convergence issue arises for $\Lambda=20$\,fm$^{-1}$ at $s \sim 10^{-4}$ where $||\eta(s)||$ and subsequently $||\Omega(s)||$ jump several orders of magnitude.
+However, the problem is completely avoided when the block-diagonal generator is used.
+We have tested different Magnus truncations $k_{\rm max}$ and Euler method step-sizes and found the same behavior.
+
+Overall, the Magnus implementation reproduces the generator-dependent SRG behavior for high-cutoff potentials, where the universality of the different potentials is achieved with the Wegner generator but not the relative kinetic energy generator.
+We note that the block-diagonal generator decouples the spurious bound state(s) at a much higher momentum value than the Wegner band-diagonal generator and still flows to a universal form in the low-momentum matrix elements.
+Although we fixed $k_{\rm max}$ in our results, one could use an adaptive method of selecting $k_{\rm max}$ values at each step in $s$ where criteria is based on flow to band- or block-diagonal form.
+One could also truncate Eq.~\eqref{eq:magnus_omega} when the Frobenius matrix norm of the $k^{\rm th}$ term is significantly smaller than the matrix norm of the $0^{\rm th}$ term (see Ref.~\cite{Morris:2015yna} for further details).
+
+From the convergence standpoint, the initial interaction and generator $\eta(s)$ clearly play a significant role in how the Magnus implementation works.
+This should be no surprise from how $\eta(s)$ is defined in terms of the Hamiltonian.
+In connection to the Magnus expansion in the IMSRG context, similar convergence issues arise for intruder state problems~\cite{Stroberg:2019mxo}.
+At least for the NN system, our results imply that the choice of SRG generator can play a significant role in overcoming the issues stemming from intruder states, though we leave this as work for a future study.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{SRG evolution of NN potentials}
+\label{sec:srg_evolution_nn_potentials}
+
+%........................................................................
+\subsection{Modern chiral NN potentials}
+\label{subsec:modern_chiral}
+
+Next we extend our analysis of the SRG evolution of high-cutoff LO potentials to include higher-order chiral potentials.
+In Ref.~\cite{Dainton:2013axa}, the conditions under which different potentials are driven to universal low-momentum matrix elements were studied.
+Here we apply both band- and block-diagonal transformations to several newer chiral potentials, also focusing on universality.
+For band-diagonal evolution, we use the Wegner generator, $G=H_D$, instead of \Trel, which was used in \cite{Dainton:2013axa}.
+For these interactions with cutoffs of order 2--3\,fm$^{-1}$,  the two band-diagonal choices are essentially equivalent, unlike for the potentials considered in the previous section when the cutoff was above 4\,fm$^{-1}$.
+
+We will consider three representative potentials: the N$^4$LO potential with 500\,MeV cutoff from Ref.~\cite{Entem:2017gor} (denoted EMN N$^4$LO), the N$^4$LO potential with 450\,MeV cutoff from Ref.~\cite{Reinert:2017usi} (denoted RKE N$^4$LO), and the N$^2$LO potential with 1\,fm cutoff from Ref.~\cite{Gezerlis:2014zia} (denoted Gezerlis N$^2$LO).
+These three potentials differ in the regulator functions applied to the contact and pion-exchange terms.
+
+%
+\begin{figure*}[htb]
+	\includegraphics[clip,width=0.85\textwidth]{potential_contours_3S1_Wegner_kvnns_79_111_222.png}%
+	\caption{Momentum-space matrix elements of the EMN N$^4$LO 500 MeV, RKE N$^4$LO 450 MeV, and Gezerlis \textit{et al.}~N$^2$LO 1 fm potentials SRG-evolved in $\lambda$ with the Wegner generator in the coupled $^3$S$_1$--$^3$D$_1$ channel (only $^3$S$_1$ is shown here.)}
+	\label{fig:potential_contours_3S1_Wegner}
+\end{figure*}
+%
+\begin{figure*}[tbh]
+    \includegraphics[clip,width=0.85\textwidth]{potential_contours_kvnn_111_1P1_generators_Wegner_Block-diag.png}%
+	\caption{Matrix elements of the RKE N$^4$LO 450 MeV potential SRG-evolving left to right under transformations with Wegner and block-diagonal generators in the $^1$P$_1$ channel.
+We vary the SRG flow parameter $\lambda$ for Wegner evolution and fix it at $\lambda=1$\,fm$^{-1}$ for block-diagonal evolution.
+The decoupling scale in the block-diagonal generator is denoted by $\LambdaBD$.}
+	\label{fig:potential_contours_1P1_RKE}
+\end{figure*}
+%
+\begin{figure*}[tbh]
+	\subfloat[]{%
+	\raisebox{.5in}{%
+	\includegraphics[clip,width=0.25\textwidth]{phase_shifts_3S1_kvnns_79_111_222.pdf}}}
+	\hfill
+	\subfloat[]{%
+	\includegraphics[clip,width=0.72\textwidth]{potential_slices_3S1_kvnns_79_111_222.pdf}%
 	}
-\\
--- Implications for IMSRG.
-\\
--- Discussion on how the block-diagonal generator handles spurious bound states. Where they are ``decoupled'' in the matrix compared to Wegner. One figure to show this?
+	\caption{(a) $^3$S$_1$ phase shifts for the EMN N$^4$LO 500 MeV (solid black), RKE N$^4$LO 450 MeV (red dash-dotted), and Gezerlis \textit{et al.}~N$^2$LO 1 fm (blue dashed) potentials.
+(b) Diagonal and far off-diagonal matrix elements of the EMN N$^4$LO 500 MeV (black), RKE N$^4$LO 450 MeV (red) and Gezerlis \textit{et al.}~N$^2$LO 1 fm (blue) potentials SRG-evolved with Wegner (solid) and block-diagonal (dashed) generators in the $^3$S$_1$ channel.
+For block-diagonal evolution, we fix $\lambda=1$\,fm$^{-1}$.}
+	\label{fig:potential_universality_3S1}
+\end{figure*}
 %
-\begin{figure}[H]
-	\centering
-	\includegraphics[clip,width=0.9\columnwidth]{Magnus/potential_diagonals_offdiags_kvnn901_Wegner}%
-	%\caption{Caption.}
-	\label{fig:potential_slices_high_cutoffs_Wegner}
+
+The EMN N$^4$LO interaction is a non-local potential where both contact and pion-exchange interactions feature a non-local regulator function of the form exp$[-(k/\Lambda)^{2n}-(k'/\Lambda)^{2n}]$, where $\Lambda$ is the momentum-space cutoff and $n$ is an integer.
+A non-local regulator function for pion-exchange contributions can introduce regulator artifacts by distorting the known analytic structure of the NN scattering amplitudes near threshold for cutoffs $\Lambda$ lower than the breakdown scale $\Lambda_b$~\cite{Epelbaum:2014efa}.
+Semi-local chiral potentials have been introduced to reduce regulator artifacts, such as the RKE potentials.
+Here, a local regulator function is applied for the long-range interactions in momentum space, while a non-local regulator function is used for the short-range interactions.
+Non-local interactions are generally not suitable for continuum quantum Monte Carlo methods, motivating the need for fully local chiral potentials.
+The Gezerlis \textit{et al.}~N$^2$LO potential is an example of a local interaction where both the long-range and short-range terms have a local regulator function in coordinate space.
+
+These chiral interactions give the same low-energy phase shifts but the matrix elements of the potential are often completely different.
+We show band-diagonal SRG evolution of the three potentials in the $^3$S$_1$ channel in Fig.~\ref{fig:potential_contours_3S1_Wegner}.
+On the left-hand column where $\lambda=6$\,fm$^{-1}$, the three potentials differ dramatically.
+Further along the SRG evolution (right-hand side), the potentials are driven to band-diagonal form where the upper left corner of the contours, corresponding to low-momentum matrix elements, become close to the same.
+
+Figure~\ref{fig:potential_contours_1P1_RKE} shows the SRG-evolved RKE N$^4$LO (450 MeV cutoff) potential in the $^1$P$_1$ partial wave channel for band- and block-diagonal SRG generators on the top and bottom rows, respectively.
+We continue to evolve to band-diagonal form with respect to the parameter $\lambda$, but for the block-diagonal generator, we label sub-plots with the parameter $\LambdaBD$ that characterizes the sharp cutoff in decoupling the low- and high-momentum matrix elements.
+For complete block-diagonal decoupling, one should take $s \rightarrow \infty$, which corresponds to $\lambda \rightarrow 0$.
+This is difficult to carry out in practice since the ODEs become stiff, so we stop the evolution at $\lambda=1$\,fm$^{-1}$.
+We see a small non-zero width in between the sub-blocks due to the non-zero value of $\lambda$, but when the width is this small the sub-blocks are effectively decoupled.
+With block-diagonal decoupling, one can truncate the Hamiltonian at the chosen value of $\LambdaBD$, separately diagonalize each sub-block, and retain all eigenvalues to high accuracy.
+We have tested representative cases and found the same eigenvalues to better than $0.1$\% for both the low- and high-momentum sub-blocks.
+
+%
+\begin{figure*}[tbh]
+    \includegraphics[clip,clip,width=0.75\textwidth]{universality_test_with_norm_kvnns_79_111_222_channels_1S0_3S1_1P1_1F3_1G4_Wegner.pdf}%
+    \caption{Frobenius norm of the difference of two SRG-evolved potentials for several partial wave channels, $^1$S$_0$ (black), $^3$S$_1$ (red), $^1$P$_1$ (blue), $^1$F$_3$ (green), and $^1$G$_4$ (orange), comparing the three default potentials, EMN N$^4$LO 500 MeV, RKE N$^4$LO 450 MeV, and Gezerlis \textit{et al.}~N$^2$LO 1 fm.}
+    \label{fig:universality_test_with_norm_Wegner}
+\end{figure*}
+%
+\begin{figure*}[tbh]
+    \includegraphics[clip,clip,width=0.75\textwidth]{universality_test_with_sdt_coeff_kvnns_79_111_222_channels_1S0_3S1_1P1_1F3_1G4_Wegner.pdf}%
+    \caption{SDT angle $\theta_{V,V'}$ between two SRG-evolved potentials for several partial wave channels, $^1$S$_0$ (black), $^3$S$_1$ (red), $^1$P$_1$ (blue), $^1$F$_3$ (green), and $^1$G$_4$ (orange), comparing EMN N$^4$LO 500 MeV, RKE N$^4$LO 450 MeV, and Gezerlis \textit{et al.}~N$^2$LO 1 fm.}
+    \label{fig:universality_test_with_sdt_coeff_Wegner}
+\end{figure*}
+%
+
+In Ref.~\cite{Dainton:2013axa}, it was found that shared long-distance physics (e.g., the common pion-exchange tail) plus phase equivalence up to some value of scattering momentum $k_0$ implies potential matrix element equivalence up to the same value $k_0$ in SRG-evolved potentials where $\lambda$, $\LambdaBD \leq k_0$ (see Figs.\ 1--4 in \cite{Dainton:2013axa}).
+We verify the conclusion from~\cite{Dainton:2013axa} in the representative chiral potentials showing the $^3$S$_1$ channel as an example.
+Figure~\ref{fig:potential_universality_3S1}(a) shows the NN phase shifts of EMN N$^4$LO 500 MeV, RKE N$^4$LO 450 MeV, and Gezerlis \textit{et al.}~N$^2$LO 1 fm potentials in the $^3$S$_1$ partial wave channel.
+Figure~\ref{fig:potential_universality_3S1}(b) shows the diagonal and far off-diagonal matrix elements of the evolved potentials in the $^3$S$_1$ channel on the top and bottom row, respectively.
+Band- and block-diagonal evolved potentials are shown on the same sub-plots indicated by solid and dashed lines, respectively, where the color indicates the potential.
+The $^3$S$_1$ phase shifts agree to within 1\% for $k \leq 2$\,fm$^{-1}$, and as we see in Fig.~\ref{fig:potential_universality_3S1}(b), universality occurs once the potentials are SRG evolved past $2$\,fm$^{-1}$.
+The matrix elements of the potentials all begin to collapse to the same line as $\lambda$ and $\LambdaBD$ decrease to the point of phase equivalence.
+In this sense, we can think of the SRG evolution like an attractor; the potentials evolve in the same manner contingent on the SRG generator with a wide variety of starting points.
+The two generators collapse the potential to a different form, because the induced contributions from SRG flow depend on how the potential is decoupled, that is, the choice in $G$.
+
+%........................................................................
+\subsection{Quantifying universality}
+\label{subsec:quantifying_universality}
+
+Next, to quantify universality in the potentials, we calculate the Frobenius norm of the difference in potentials in Fig.~\ref{fig:universality_test_with_norm_Wegner}.
+Here, we use $G=H_D$ as an example for several partial wave channels.
+We evolve the three default potentials to $\lambda=6$, $3$, $2$, $1.5$, and $1$\,fm$^{-1}$.
+To focus on the region of universality, we truncate each potential matrix up to the momentum value $\lambda$ and divide the difference by the average norm of the three truncated potentials.
+(This prevents the norm from decreasing with lower $\lambda$ because the matrices become smaller in dimension due to truncation.)
+The momentum value of phase equivalence occurs somewhere in the range of $1$--$2$\,fm$^{-1}$ for most of the channels included.
+We see a sharp drop in the matrix norm at $\lambda$ near this range.
+
+Notice that the $^3$S$_1$ channel differs significantly in comparing Gezerlis N$^2$LO to the other two potentials.
+This is due to the $^3$S$_1$ being dominated by the contact force, where for Gezerlis N$^2$LO the regulator function is local, while it is  non-local for the other two potentials.
+A similar difference is seen in the $^1$G$_4$ channel, which is dominated by pion-exchange, but now for EMN N$^4$LO compared to the other two.
+Again, this is caused by the difference in regulator functions, where EMN N$^4$LO uses a non-local regulator and the other two a local regulator.
+The difference in regulator functions between the various potentials affects the flow to universality in channels primarily affected by contact forces or pion exchange, but the difference is small and unnoticeable in the previous figures.
+
+We can also use techniques from spectral distribution theory (SDT) to analyze universality~\cite{Johnson:2017uor}.
+In SDT the expectation value of a potential is defined as
+%
+\begin{eqnarray}
+    \label{eq:sdt_exp_value}
+    \expval{V} = \frac{1}{N} \Tr V,
+\end{eqnarray}
+%
+where $N$ is the dimension of the matrix $V$.
+The inner product of two potentials $V$ and $V'$ is defined as,
+%
+\begin{eqnarray}
+    \label{eq:sdt_inner_product}
+    (V,V') &=& \expval{(V^{\dagger}-\expval{V^{\dagger}})(V'-\expval{V'})} \nonumber \\
+    &=& \expval{V^{\dagger} V'} - \expval{V^{\dagger}}\expval{V'}.
+\end{eqnarray}
+%
+We can now define the correlation coefficient $\zeta_{V,V'}$ which gives a measure of the ``similarity'' between the two potentials,
+%
+\begin{eqnarray}
+    \label{eq:sdt_corr_coeff}
+    \zeta_{V,V'} = \frac{(V,V')}{\sigma_V \sigma_{V'}},
+\end{eqnarray}
+%
+where $\sigma_V$ is the positive square root of the variance,
+%
+\begin{eqnarray}
+    \label{eq:sdt_variance}
+    \sigma^2_V = (V,V) = \expval{V^2} - \expval{V}^2.
+\end{eqnarray}
+%
+Geometrically, we can think of the potentials as two vectors with $\theta_{V,V'} \equiv \textrm{arccos}(\zeta_{V,V'})$ measuring the angle between them.
+Further details of the relevant formulas in SDT can be found in Refs.~\cite{Sviratcheva:2007bp,Launey:2013ysa}.
+
+Although these calculations have been used to quantify the differences in nuclear Hamiltonians, we provide calculations of $\theta_{V,V'}$ instead since the relative kinetic energy is the same in the three representative Hamiltonians.
+Analogous to Fig.~\ref{fig:universality_test_with_norm_Wegner}, we show the angle between pairs of the potentials for the same values of $\lambda$ in Fig.~\ref{fig:universality_test_with_sdt_coeff_Wegner}.
+Again, we make a truncation in the potential matrices up to the value of $\lambda$.
+With SRG evolution, $\theta_{V,V'} \rightarrow 0$ corresponding to strong correlations between the compared potentials.
+The differences in the behavior of the various channels as noted previously show in Fig.~\ref{fig:universality_test_with_sdt_coeff_Wegner} as well.
+
+%........................................................................
+\subsection{Evolved wave functions and SRCs}
+\label{subsec:wfs_and_SRCs}
+
+%
+\begin{figure}[t!]
+    \includegraphics[clip,width=0.48\textwidth]{deuteron_wave_func_coord_space_kvnns_79_111_222_Wegner1,2.pdf}%
+    \caption{Deuteron wave functions in coordinate space for the same three chiral potentials as in Fig.~\ref{fig:universality_test_with_sdt_coeff_Wegner} under band-diagonal SRG transformations with $G=H_D$ and $\lambda=1.2$\,fm$^{-1}$.
+The solid lines correspond to the S-states, and the dashed lines correspond to the D-states.}
+    \label{fig:deuteron_wave_funcs_soft}
 \end{figure}
 %
-\begin{figure}[H]
-	\centering
-	\includegraphics[clip,width=0.9\columnwidth]{Magnus/potential_diagonals_offdiags_kvnn901_T}%
-	%\caption{Caption.}
-	\label{fig:potential_slices_high_cutoffs_T}
+\begin{figure}[tbh]
+    \includegraphics[clip,width=0.48\textwidth]{deuteron_wave_func_coord_space_kvnns_6_900_901_Wegner1,2.pdf}%
+    \caption{Same as Fig.~\ref{fig:deuteron_wave_funcs_soft} but for the high-cutoff LO potentials with $\Lambda=4$ and $9$\,fm$^{-1}$ and AV18, and $\lambda=1.2$\,fm$^{-1}$.
+The inset plot on the left panel shows the initial wave functions zoomed out on the y-axis up to $r=2$ fm.}
+    \label{fig:deuteron_wave_funcs_hard}
 \end{figure}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-\label{sec:conclusion}
+Universality in the potentials for a given SRG generator is naturally reflected in the low-energy wave functions.
+In Fig.~\ref{fig:deuteron_wave_funcs_soft} we show the initial and evolved deuteron wave functions in coordinate space for the three chiral potentials, where the solid lines correspond to the S-state components and the dashed lines to the D-state components.
+The wave functions are evolved using a band-diagonal, $\lambda=1.2$\,fm$^{-1}$ transformation.
+The short-distance part of the S-state differs initially but flows to the same form, while the initial D-state also differs and becomes suppressed after evolving.
+This reflects the flow to universality in the low-momentum matrix elements of the potentials.
+Despite the scheme dependence of the initial UV treatment, decoupling the low- and high-momentum physics means the states flow to the same wave function at low resolution.
+Furthermore, the same low-resolution wave functions result for initial
+deuteron wave functions with harder potentials such as Argonne $v_{18}$ (AV18) \cite{Wiringa:1994wb} and the LO high-cutoff potentials from the previous section, as seen in Fig.~\ref{fig:deuteron_wave_funcs_hard}.
 
-\noindent{%
--- Summary.
-}
-\\
--- Outlook.
+Consider these results from the perspective of SRC phenomenology~\cite{Hen:2016kwk,Weiss:2016obx,Cruz-Torres:2019fum,Schmidt:2020kcl}.
+In Fig.~\ref{fig:deuteron_wave_funcs_hard}, the dip at small $r$ in $\psi_d(r)$ in the initial S-states reflects a strong repulsive core in the initial potential (with the node for $\Lambda=9$\,fm$^{-1}$ because of the spurious deep-bound state for that potential) while the D-wave strength at short distance is from a strong tensor force.
+These are the signatures of the SRC proton-neutron pair in the deuteron; there will be corresponding intermediate-momentum (D-state) and high-momentum (S-state) signatures in the momentum wave functions.
+Note the qualitative similarity of AV18 and the chiral $\Lambda=4$\,fm$^{-1}$ wave functions, which demonstrates that even though the LO chiral potential is only adjusted to fit very low energy phase shifts, the same SRC structure is found because of the common iterated-pion-exchange and similar regularization scale in the respective Hamiltonians.
+(This suggests that one is unlikely to explore fine details of the NN interaction from SRC physics.)
+The higher momenta extend well beyond the chiral EFT breakdown scale of about 3\,fm$^{-1}$, where UV physics is incorrect.
+
+The scale and scheme dependence of SRCs is manifest in these two figures.
+But by shifting the resolution scale through SRG evolution, the SRC physics is dissolved as the deuteron state becomes decoupled from high-energy contributions.
+All physical observables will be preserved with these uncorrelated wave functions if the corresponding operators are also SRG evolved.
+The purely high-momentum contributions removed from the wave function are compensated in the evolved operator as smeared contact operators, as illustrated in the following section.
+This reflects a natural factorization of the short-distance physics for low-energy states, which will be the same in all nuclei (with $^1$S$_0$ contributions as well for $A>2$).
+This factorization accounts for the short-distance or high-momentum pair distributions for a \emph{fixed} high-resolution Hamiltonian being the same as well (so they are universal in a difference sense than we have been considering)~\cite{Anderson:2010aq,Bogner:2012zm}.
+
+The flow to universality in the wave functions for a well-specified SRG scheme suggests that the lower resolution scales for nuclear structure from soft potentials and the shell model can be matched by a well-specified reaction operator structure~\cite{More:2017syr}.
+The S-state versus D-state probabilities of the deuteron can be viewed as spectroscopic factors for single-particle strengths~\cite{Furnstahl:2010wd}.
+If one analyzed scattering from the deuteron S-state with a high-resolution reaction model but the low-resolution wave function, the reduced D-state component would lead one to conclude that the ratio of experiment to theory cross sections was less than one.
+This is the analog of what is found in knock-out experiments analyzed with an eikonal reaction model and shell model wave functions~\cite{Tostevin:2014usa}.
+The flow to universal structure may provide a controlled resolution of these discrepancies.
+
+In summary, we have examined the flow to universality of several recently developed \chiEFT\ potentials.
+We verified that the general conclusions of Ref.~\cite{Dainton:2013axa} still hold, namely that potential matrix elements collapse to similar values in regions of phase equivalence. 
+We quantified this collapse using both Frobenius norm and the SDT angle $\theta_{V,V'}$, which highlight the differences in the three representative potentials from the regulator functions.
+Lastly, we illustrated the consequence of this universality for low-energy wave functions of the potentials by applying transformations to the deuteron.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Evolution of other operators}
+\label{sec:evolution_other_operators}
 
-\bibliography{../tropiano_bib}
+%
+\begin{figure*}[t!]
+	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_contours_q0,30_kvnn_111_3S1.png}%
+	\caption{Momentum projection operator $\mel{k}{\ataq}{k'}$ for $q=0.3$\,fm$^{-1}$ under SRG transformations using the RKE N$^4$LO 450 MeV potential, evolving with Wegner ($H_D$) and block-diagonal ($H_{BD}$) generators in the $^3$S$_1$ channel.
+The SRG flow parameter $\lambda$ is varied for $G = H_D$ evolution and fixed at $\lambda=1$\,fm$^{-1}$ for $G = H_{BD}$ evolution.
+The decoupling scale for $G = H_{BD}$ is $\LambdaBD$.}
+	\label{fig:momentum_projection_contours_q0,30_3S1_RKE}
+
+\medskip\smallskip
+
+	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_contours_q3,00_kvnn_111_3S1.png}%
+	\caption{Same as Fig.~\ref{fig:momentum_projection_contours_q0,30_3S1_RKE} but for $q=3$\,fm$^{-1}$.}
+	\label{fig:momentum_projection_contours_q3,00_3S1_RKE}
+\end{figure*}
+%
+
+%........................................................................
+\subsection{SRG for representative operators}
+\label{subsec:representative_ops}
+
+In this section, we analyze SRG operator evolution using the radius squared operator $r^2$ and the momentum projection operator $\ataq$, where $q$ is the relative momentum.
+These serve as examples of long-distance operators ($r^2$) and low- and high-momentum operators (by specifying different $q$ in $\ataq$). 
+We look to whether the observations on universality for SRG-evolved Hamiltonians can be generalized to universality for \emph{any} SRG-evolved operator and contrast the evolution for different generators.
+In evolving these operators, we build the SRG unitary transformations explicitly using the eigenvectors of the bare and evolved Hamiltonians, that is,
+%
+\begin{eqnarray}
+	\label{eq:unitary_transformation}
+	U(s) = \sum_{\alpha=1}^{N} \ket{\psi_{\alpha}(s)} \bra{\psi_{\alpha}(0)},
+\end{eqnarray}
+%
+where $\alpha$ indexes the states of the Hamiltonian.
+Then to evolve the operator, we apply $U(s)$ as in Eq.~\eqref{eq:srg_operator}.
+
+We start by considering the relative momentum projection operator,
+$\ataq$, which works in a very simple way in the two-body system.
+The expectation value of $\ataq$ in some state $\ket{\psi}$ gives the momentum distribution evaluated at $q$, that is, $\mel{\psi}{\ataq}{\psi}=\abs{\psi(q)}^2$.
+Hence, the $k$, $k'$ matrix element of this operator is proportional to two delta functions: $\delta(k-q) \delta(k'-q)$.
+In the simplest discretization, this corresponds to a matrix of zeros at every point in $k$ and $k'$ except where $k=k'=q$, which makes the SRG-induced contributions quite clear.
+More generally, we can use smeared delta functions with non-zero entries, appropriately weighted to integrate to one, for the matrix elements near $k=k'=q$. 
+In Figs.~\ref{fig:momentum_projection_contours_q0,30_3S1_RKE} and \ref{fig:momentum_projection_contours_q3,00_3S1_RKE} we show two different sets of SRG-evolved momentum projection operators (for $q=0.3$ and $3$\,fm$^{-1}$) with the Wegner and block-diagonal generators using a slightly smeared operator.
+For large $\lambda$ and $\LambdaBD$ values in both figures, we see the initial regularized delta functions as a dark red dot where $k=k'=q$, which persists with SRG evolution.
+(See Figs. 3 and 4 in Ref.~\cite{Anderson:2010aq} for similar visualizations with the simplest discretization.)
+
+In Fig.~\ref{fig:momentum_projection_contours_q0,30_3S1_RKE} where $q=0.3$\,fm$^{-1}$, the most evident induced contributions are non-zero bands for $k=q$ or $k'=q$ and then smooth induced contributions eventually become visible at $k,k'<2$\,fm$^{-1}$.
+These features are independent of the smearing of the delta function and matrix elements in the deuteron are the same up to small discretization artifacts.
+We can understand the bands by taking one infinitestimal step $\Delta s$ in the SRG evolution in Eq.~\eqref{eq:srg_flow} and taking $k,k'$ matrix elements,
+%
+\begin{align}
+    \mel{k}{\Delta \ataq(s)}{k'} &= \mel{k}{[\eta, \ataq(0)]}{k'} \Delta s.
+\end{align}
+%
+After inserting an intermediate integration, $\ataq(0)$ will evaluate to two (smeared) delta functions, one of which survives each term as $\delta(k-q)$ or $\delta(k'-q)$.
+These delta function contributions persist throughout the evolution and therefore show up as (smeared) bands.
+For the Wegner generator the low-momentum induced contributions are much larger than in the case of the block-diagonal generator. 
+This reflects that the Hamiltonian is being modified more at high momentum by the band-diagonal evolution.
+Consequently the block-diagonal transformation roughly keeps the same low-$k$ wave function (assuming a low-energy state), therefore a low-momentum operator will change less under block-diagonal transformations.
+This is analyzed further in Sec.~\ref{subsec:connecting}.
+
+Figure~\ref{fig:momentum_projection_contours_q3,00_3S1_RKE} shows SRG evolution of $\mel{k}{\ataq}{k'}$ again but for $q=3$\,fm$^{-1}$.
+The band-diagonal SRG transformation induces low-momentum contributions where the initial operator was entirely zero.
+A similar change happens for the block-diagonal transformation except the induced contributions at low momentum sharply drop to zero at the block-diagonal cutoff $\LambdaBD$.
+The smooth low-momentum contributions are what is expected from an EFT perspective, as they can be expanded as regulated (smeared) contact operators that absorb the high-momentum contributions to low-energy states that are decoupled by the evolution.
+These features are independent of the mesh and the discretization of the delta functions.
+This is an example of an operator product expansion factorization~\cite{Anderson:2010aq,Bogner:2012zm}, which is reviewed in Sect.~\ref{subsec:factorization}.
+
+%
+\begin{figure}[t!]
+    \includegraphics[clip,width=0.48\textwidth]{r2_3d_plot_unregulated.png}%
+    \caption{Visualization of the $r^2$ operator in momentum space, $\langle k | r^2 | k'\rangle$, regulated only by the coordinate and momentum meshes.
+    The integration factors of $k$ and $k'$ are included.}
+    \label{fig:r2_unregulated}
+
+\medskip\smallskip
+
+    \includegraphics[clip,width=0.48\textwidth]{r2_3d_plot_regulated_a6.png}%
+    \caption{Same as Fig.~\ref{fig:r2_unregulated} but with a coordinate-space regulator function $e^{-r^2/a^2}$ where $a=6$ fm.}
+    \label{fig:r2_regulated}
+\end{figure}
+%
+\begin{figure*}[htb]
+    \includegraphics[clip,width=0.9\textwidth]{r2_srg_changes_kvnn_111_Block-diag.png}%
+    \caption{SRG contributions to $P r^2 P$ in momentum space, splitting $PU(\LambdaBD)r^2(\infty)U^{\dagger}(\LambdaBD)P$ into four components as in Eq.~\eqref{eq:r2_PP_contributions}.
+We apply a block-diagonal transformation from RKE N$^4$LO 450 MeV in the $^3$S$_1$ channel with $\LambdaBD=2$\,fm$^{-1}$.}
+    \label{fig:r2_srg_changes}
+\end{figure*}
+%
+
+Next, we consider the $r^2$ operator, relying on Ref.~\cite{Anderson:2010aq} for formulas and some basic results.
+In the absence of an explicit regulator for large $r$, the meshes used to create the $r^2$ matrix in coordinate space and then Fourier transform to momentum will act as regulators. 
+Visualizations of the bare $r^2$ operator will then be highly mesh dependent, even though 
+expectation values of $r^2$ will be stable for sufficiently large cutoff in $r$ or small mesh spacing in $k$.
+With this in mind, we show visualizations of $\langle k | r^2 | k'\rangle$ in Figs.~\ref{fig:r2_unregulated} and \ref{fig:r2_regulated}, where the latter has an added regularization to illustrate the strong regulator dependence.
+(The $r^2$ operator in Figs.~\ref{fig:r2_unregulated} and \ref{fig:r2_regulated} include integration factors $k$ and $k'$ such that evaluating $\mel{\psi}{r^2}{\psi}$ in momentum space with wave functions equipped with additional factors $k$ or $k'$ will give the correct integration.)
+As evident in both figures, there is strength near the diagonal for all $k$, so the contribution to the $r^2$ expectation value for a particular state will be dictated by its momentum wave function.
+
+%
+\begin{figure*}[tbh]
+	\subfloat[]{%
+	\includegraphics[clip,width=0.35\textwidth]{deuteron_momentum_distributions_kvnn111.pdf}%
+	}
+	\quad
+	\subfloat[]{%
+	\includegraphics[clip,width=0.35\textwidth]{high_energy_state_eps300,0_momentum_distributions_kvnn111.pdf}%
+	}
+	\caption{Momentum distributions from deuteron (a) and a high-energy state (b) with the RKE N$^4$LO 450 MeV potential.
+Here, we compare SRG-evolved distributions, $G=H_D$ (red solid), $G=H_{BD}$ at $\LambdaBD=2$\,fm$^{-1}$ (blue dash-dotted), and $G=H_{BD}$ at $\LambdaBD=3$\,fm$^{-1}$ (green dashed) each with $\lambda=1.5$\,fm$^{-1}$, to the initial distribution (black dotted).
+Also, $\varepsilon \approx 300$ MeV for the high-energy state in (b).}
+	\label{fig:momentum_distributions_RKE}
+\end{figure*}
+%
+
+The SRG evolution of the regulated $r^2$ operator is barely noticeable in contour plots (e.g., see Ref.~\cite{Anderson:2010aq}), so we focus instead on the induced changes in the operator when evolving to low momentum.
+We use block-diagonal evolution for clarity and split the contribution to $r^2$ according to its origin in different blocks of momentum space defined by $P = \theta (\LambdaBD - k)$ and $Q = \theta(k - \LambdaBD)$ projection operators.
+In particular, the four contributions to the evolved $r^2$ operator (designated $r^2(\LambdaBD$)) in the low-momentum block is decomposed as:
+%
+\begin{align}
+    \label{eq:r2_PP_contributions}
+    P r^2(\LambdaBD) P &= P U(\LambdaBD) P r^2(\infty) P U^{\dagger}(\LambdaBD) P \nonumber \\
+    & \null + P U(\LambdaBD) P r^2(\infty) Q U^{\dagger}(\LambdaBD) P \nonumber \\
+    & \null + P U(\LambdaBD) Q r^2(\infty) P U^{\dagger}(\LambdaBD) P \nonumber \\
+    & \null + P U(\LambdaBD) Q r^2(\infty) Q U^{\dagger}(\LambdaBD) P.
+\end{align}
+%
+In Fig.~\ref{fig:r2_srg_changes} we show a representative set of these contributions for the RKE N$^4$LO 450\,MeV potential, labeled by their origin before the block-diagonal unitary transformations.
+
+The $\QQ$ panel in Fig.~\ref{fig:r2_srg_changes} is very similar to the corresponding $\PP$ block for the evolved high-momentum $\ataq$ shown in Fig.~\ref{fig:momentum_projection_contours_q3,00_3S1_RKE}.
+This is not a coincidence: these smooth low-momentum contributions have the same origin and same understanding from EFT and OPE factorization (see Sect.~\ref{subsec:factorization}).
+The $\PQ$ block is roughly constant in $k'$ for the same reason, while the $k$ dependence is dependent on the mesh, as is the full contribution in the $\PP$ block (likewise for the $\QP$ block, swapping $k'$ and $k$).
+The implications for matrix elements in the deuteron are given in the next section.
+The decomposition for other potentials or other choices for $\LambdaBD$ is qualitatively similar, with the $\QQ$ contribution scaling with the hardness of the interaction, which reflects the extent of initial high-momentum components (i.e., the short-range correlations).
+
+%
+\begin{figure*}[tbh]
+	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_integrand_contours_q3,00_kvnn_111.png}%
+	\caption{Integrand of $\mel{\psi_d}{\ataq}{\psi_d}$ in momentum space where $\psi_d$ is the deuteron wave function and $q=3$\,fm$^{-1}$.
+Here, we SRG-evolve the operator and wave function where each successive column indicates further evolution under the Wegner and block-diagonal generators with the RKE N$^4$LO 450 MeV potential.
+We vary the SRG flow parameter $\lambda$ for Wegner evolution and fix it at $\lambda=1$\,fm$^{-1}$ for block-diagonal evolution.
+The decoupling scale in the block-diagonal generator is denoted by $\LambdaBD$.}
+	\label{fig:momentum_projection_integrand_contours_q3,00_RKE}
+\end{figure*}
+%
+\begin{figure*}[tbh]
+	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_integrand_contours_q3,00_kvnn_111_eps300,0.png}%
+	\caption{Same as Fig.~\ref{fig:momentum_projection_integrand_contours_q3,00_RKE} but with a high-energy state $\psi_{\varepsilon}$ where $\varepsilon \approx 300$ MeV.}
+	\label{fig:momentum_projection_integrand_contours_q3,00_eps300_RKE}
+\end{figure*}
+%
+
+%........................................................................
+\subsection{Connecting to wave function evolution}
+\label{subsec:connecting}
+
+%
+\begin{table*}[htb]
+	\caption{SRG contributions to $\mel{\psi_d}{P r^2 P}{\psi_d}$ splitting $PU(\LambdaBD)r^2(\infty)U^{\dagger}(\LambdaBD)P$ into four components as in Eq.~\eqref{eq:r2_PP_contributions} where $\PQ$ and $\QP$ are combined.
+	For the $\PP$ contribution, the unevolved $\mel{\psi_d}{P r^2 P}{\psi_d}$ value is subtracted.
+	We apply block-diagonal transformations from RKE N$^4$LO 450 MeV and AV18 in the $^3$S$_1$ channel with $\LambdaBD=2\,$fm$^{-1}$.
+For comparison, we also show results for $\ataq$ with $q = 3\,\mbox{fm}^{-1}$.}
+	\label{tab:evolved_r2_contributions}
+	\begin{ruledtabular}
+		\begin{tabular}{c||ccc||ccc}
+		   & \multicolumn{3}{c||}{$\mel{\psi_d}{P r^2 P}{\psi_d}$ [fm$^2$]} &
+		   \multicolumn{3}{c}{$\mel{\psi_d}{P \ataq P}{\psi_d}$ [fm$^3$]} \\
+      	\mystrut	Potential &  $\PP$ & $\PQ+\QP$ & $\QQ$ & $\PP$ & $\PQ+\QP$ & $\QQ$\\
+			\colrule
+      			RKE N$^4$LO 450\,MeV & $\num{-2.90e-02}$ & $\num{-3.22e-01}$ & $\num{1.66e-01}$ &
+      			$\num{0.0}$ & $\num{0.0}$ & $\num{5.05e-04}$
+                    \mystrut\\
+      			AV18 & 
+      			\num{-4.83e-02} & \num{-4.33e-01} & \num{2.33e-01}
+      			& $\num{0.0}$ & $\num{0.0}$  & \num{1.61e-03} \mystrut
+		\end{tabular}
+  	\end{ruledtabular}
+\end{table*}
+%
+\begin{figure}[htb]
+    \includegraphics[clip,width=0.4\textwidth]{r_convergence_rel_err_Wegner_kvnns_6_111.pdf}%
+    \caption{Relative error of the deuteron rms radius from AV18 (black) and RKE N$^4$LO $450$ MeV (red) truncating the momentum-space calculation $\mel{\psi_d}{r^2}{\psi_d}$ at $k_{\rm max}$.
+Solid lines indicate the fully unevolved calculation and dashed lines indicate the SRG-evolved calculation where $\lambda=1.5$\,fm$^{-1}$.}
+    \label{fig:r_convergence_with_kmax}
+\end{figure}
+%
+
+SRG transformations are unitary, meaning that the matrix elements of the evolved operator are preserved.
+Therefore, the changes in the operator must be accounted for in the evolved wave functions.
+We can examine the evolved wave functions to understand the differences in band- and block-diagonal evolution of operators.
+
+Figure~\ref{fig:momentum_distributions_RKE} shows initial and evolved momentum distributions for the deuteron and a high-energy state at $\varepsilon \approx 300$ MeV using the RKE N$^4$LO 450 MeV potential.
+For the deuteron, the strength of the wave function is shifted to lower momentum with the band-diagonal generator.
+With the block-diagonal generators, the wave function is nearly the same up to the value of the cutoff $\LambdaBD$.
+For the high-energy state, the band-diagonal generator keeps the strength of the wave function near the spike at $k \approx 2.7$\,fm$^{-1}$.
+However, in the case of the block-diagonal generator, the wave function changes in different ways depending on the cutoff $\LambdaBD$.
+For $\LambdaBD=2$\,fm$^{-1}$, we see the evolved distribution roughly matching the initial one for $k>\LambdaBD$, and vice versa for $\LambdaBD=3$\,fm$^{-1}$. 
+Recall that in block-diagonal SRG decoupling the Hamiltonian is split into a low-momentum sub-block, $P H P$, and a high-momentum sub-block, $Q H Q$.
+When $\LambdaBD=2$\,fm$^{-1}$, the $\varepsilon \approx 300$ MeV state is contained in $Q H Q$, whereas for $\LambdaBD=3$\,fm$^{-1}$ it is contained in $P H P$.
+Note that the deuteron, being the lowest energy state, is also contained in $P H P$, which is consistent with what is seen in Fig.~\ref{fig:momentum_distributions_RKE}(a).
+A block-diagonal-evolved wave function remains approximately unchanged in the sub-block where the state resides with the rest of the wave function dropping to zero.
+
+Generally speaking, SRG transformations change operators based on how the transformations change the wave functions, which depends on the type of decoupling.
+Consider the momentum projection operator with $q=3$\,fm$^{-1}$ and a block-diagonal transformation with $\LambdaBD=2$\,fm$^{-1}$.
+We see the evolved wave functions for the deuteron and the high-energy state are opposite in the sense that the evolved deuteron wave function matches the initial wave function for $k<\LambdaBD$ and the high-energy state wave function matches for $k>\LambdaBD$.
+
+We can use the momentum projection operator $\ataq$ to understand the contrasting behavior in the wave functions.
+With $\mel{\psi(0)}{\ataq(0)}{\psi(0)} = \mel{\psi(s)}{\ataq(s)}{\psi(s)}$ from unitarity, how does the evolved projection operator for $q=3$\,fm$^{-1}$ and $\LambdaBD=2$\,fm$^{-1}$ make sense given these changes to the example wave functions?
+For the deuteron wave function, the expectation value takes strength from the induced low-momentum contributions in the evolved operator where the evolved deuteron wave function is strongest ($k<2$\,fm$^{-1}$).
+For the high-energy state, the expectation value depends more on the remnants of the delta functions from the initial operator because the strength of the wave function is at high momentum.
+In each case, the expectation value remains the same.
+
+%
+\begin{figure*}[tbh]
+	\includegraphics[clip,width=0.85\textwidth]{unitary_transformation_ratios_k0_0,1_kpoints_0,5_1,0_1,5_3,0kvnns_79_111_222_3S1_Wegner.pdf}%
+	\caption{Numerical tests of factorization of the unitary transformation  by plotting ratios of $|U(k,q)|$ in the $^3$S$_1$ channel as a function of $q$ for fixed $k=k_0$ in the denominator and several values of $k_i$ in the numerator.
+    Plateaus in $q$ indicate factorization $U(k,q) \approx \Klo(k)\Khi(q)$, which is expected for $q\gg\lambda$ (outside shaded box) \emph{and} $k < \lambda$.
+The unitary transformations are generated in each panel for a different chiral EFT potential, all evolved to $\lambda = 2\,\mbox{fm}^{-1}$ with $G = H_D$.}
+	\label{fig:factorization_ratios}
+\end{figure*}
+%
+
+The SRG does not decouple \emph{every} operator in the sense that it decouples matrix elements as in the Hamiltonian, but instead reflects the changes made to the wave functions.
+In Figs.~\ref{fig:momentum_projection_integrand_contours_q3,00_RKE} and \ref{fig:momentum_projection_integrand_contours_q3,00_eps300_RKE} we show the evolution of the integrand of the expectation value $\mel{\psi}{\ataq}{\psi}$ for deuteron and a high-energy state $\varepsilon \approx 300$ MeV, respectively, where $q=3$\,fm$^{-1}$.
+Both the wave function and operator are SRG evolved so the total strength is preserved.
+
+In Fig.~\ref{fig:momentum_projection_integrand_contours_q3,00_RKE}, the SRG transformations shift the strength in the integrand to lower momentum, matching the changes in the SRG-evolved deuteron wave function.
+The band-diagonal transformation in the top row smoothly approaches lower and lower momentum, eliminating the delta functions, while the block-diagonal shows similar behavior but roughly sets an upper limit $\LambdaBD$ on the intermediate integrations.
+The low-momentum contributions in the expectation value are relatively constant as the fall off of the wave function $\psi(k)$ largely cancels out with the integration factors $k^2$ and $k'^2$.
+In Fig.~\ref{fig:momentum_projection_integrand_contours_q3,00_eps300_RKE}, band-diagonal evolution locally decouples the expectation value at high momentum.
+Block-diagonal evolution sharply isolates the expectation value to low- or high-momentum sub-blocks depending on the value of $\LambdaBD$.
+In the first two columns with block-diagonal decoupling, the expectation value resides in the low-momentum sub-block, but then switches to the high-momentum sub-block in the last two columns with lower $\LambdaBD$.
+
+The expectation value $\mel{\psi_d}{r^2}{\psi_d}$ shows little variation with SRG evolution as the strength of initial operator resides predominantly at low momentum.
+Thus, softening the high-momentum tail of the deuteron wave function leads to only a small change in the expectation value with $r^2$.
+In Fig.~\ref{fig:r_convergence_with_kmax} the contributions from different regions in $k$ to the unevolved deuteron matrix element of $r^2$ are shown for the AV18 and RKE N$^4$LO 450\,MeV potentials by plotting the relative error made by integrating only up to $k_{\text{max}}$.
+Only about 1\% of the expectation value comes from above 2\,fm$^{-1}$ in the initial wave function for either potential and there is negligible contribution above 2\,fm$^{-1}$ once they are evolved to $\lambda=1.5\,\mbox{fm}^{-1}$.
+Table~\ref{tab:evolved_r2_contributions} shows the contributions from the blocks in Fig.~\ref{fig:r2_srg_changes} to the deuteron.
+In contrast to the entries for $\ataq$ with $q = 3\,\mbox{fm}^{-1}$, which come entirely from the high-momentum \QQ\ block, the four blocks each contribute to the induced $r^2$ expectation values.
+This implies that attempts to estimate the high-resolution SRC contribution to the low-resolution radius in schematic models, as in Ref.~\cite{Miller:2018mfb}, are rather subtle.
+We have checked that contributions to $\mel{\psi_d}{P r^2P }{\psi_d}$ with transformations from other potentials are consistent with the results in Table~\ref{tab:evolved_r2_contributions}.
+
+%........................................................................
+\subsection{Factorization}
+\label{subsec:factorization}
+
+In Refs.~\cite{Bogner:2007jb,Anderson:2010aq} it was shown that when there is a scale separation in its momentum arguments, the SRG unitary transformation should factorize into separate functions of low and high momentum, that is, $U(k,q) \rightarrow \Klo(k)\Khi(q)$ for $k < \lambda \ll q$.%
+\footnote{In Ref.~\cite{Anderson:2010aq}, $\Klo$ was denoted $K$ and $\Khi$ was denoted $Q$. We switch notation here to avoid confusion with the projection operator $Q$.}
+This is expected from general considerations of the operator product expansion~\cite{Anderson:2010aq,Bogner:2012zm}.
+A test of factorization for three chiral EFT potentials is shown in Fig.~\ref{fig:factorization_ratios} by plotting the ratio $|U(k_i,q)/U(k_0,q)|$ versus $q$ with $k_0=0.1\,\mbox{fm}^{-1}$ for several different $k_i$.
+In general this ratio should vary widely with $q$ but should reduce to $|\Klo(k_i)/\Klo(k_0)|$, which is independent of $q$, when the conditions for factorization are satisfied.
+This is validated in the figure as plateaus of the $U$ ratio in the expected region in $q$ for $k_i < \lambda$.
+Furthermore, these plateaus are close to one and vary slowly with $k_i$, so the same is true of $\Klo(k)$.
+We show only the $^3$S$_1$ channel in Fig.~\ref{fig:factorization_ratios} but have verified factorization in other channels as well.
+
+Consider the consequences of this factorization for block-diagonal SRG evolution of an unevolved high-momentum operator, which we define as one with support only in the $\QQ$ block as in Sec.~\ref{subsec:representative_ops}:
+%
+\begin{align}
+    [O_Q]_\infty = Q [O_Q]_\infty Q.
+\end{align}
+%
+This includes $\ataq$ for $q$ in $Q$ and $Qr^2(\infty)Q$ in \eqref{eq:r2_PP_contributions}.
+In the low-momentum block, the evolved operator becomes
+%
+\begin{align}
+    P [O_Q]_\LambdaBD P &=
+      P U(\LambdaBD)Q[O_Q]_\infty Q U^\dagger(\LambdaBD) P \notag \\
+      &\approx P \Klo \bigl[\Khi [O_Q]_\infty \Khi\bigr] \Klo P
+\end{align}
+%
+or, for $k,k'$ in the $\PP$ block,
+%
+\begin{align} \label{eq:factored_op}
+   & \mel{k}{[O_Q]_\LambdaBD}{k'} \approx 
+        \Klo(k) \Klo(k') \notag \\
+  &  \quad \times
+     \biggl[
+      \int_{\LambdaBD}^{\infty} d\tilde{q}' 
+      \int_{\LambdaBD}^{\infty} d\tilde{q}''\, \Khi(q') [O_Q]_\infty(q',q'') \Khi(q'')
+     \biggr],
+\end{align}
+%
+where $d\tilde{k} \equiv \frac{2}{\pi} k^2 dk$.
+As all of the $k,k'$ dependence comes from the smooth functions $\Klo(k)\Klo(k')$, this universal result directly explains the particular cases of the $\PP$ block behavior in Fig.~\ref{fig:momentum_projection_contours_q3,00_3S1_RKE} and the $\QQ$ panel of Fig.~\ref{fig:r2_srg_changes}.
+The same analysis goes through with the band-diagonal SRG, but with $\LambdaBD \rightarrow \lambda$ and the boundaries not so sharply defined.
+
+%
+\begin{figure*}[tbh]
+	\includegraphics[clip,width=0.75\textwidth]{momentum_projection_ratios_q3,00_3S1_Wegner_kvnns_111_79_6_222.pdf}%
+	\caption{Ratio of evolved matrix elements $R[\ataq(k,k)]$ (diagonal) and $R[\ataq(k,0)]$ (full off-diagonal) as defined in \eqref{eq:momentum_proj_matrix_elements_ratio} in the $^3$S$_1$ channel for $q = 3,\mbox{fm}^{-1}$.
+	Three potentials are compared to RKE N$^4$LO after evolution to several values of $\lambda$ with $G = H_D$.
+	The dotted lines indicate the value of $|\psi^A_{\infty}(q)|^2 / |\psi^B_{\infty}(q)|^2$.}
+	\label{fig:R_ratio_comparison}
+\end{figure*}
+%
+
+If we apply Eq.~\eqref{eq:factored_op} to matrix elements of $O_Q$ for the same Hamiltonian but in different nuclei, the integrations in the $\QQ$ block will be the same, so matrix-element ratios will be determined by soft (``mean-field'') physics and be independent of high-momentum details~\cite{Anderson:2010aq} (up to higher-order corrections beyond \eqref{eq:factored_op}).
+This explains why the high-momentum or short-distance behavior of momentum distributions is universal in nuclei~\cite{Anderson:2010aq,Bogner:2012zm,Neff:2015xda,Cruz-Torres:2019fum}.
+
+%
+\begin{figure*}[tbh]
+	\includegraphics[clip,width=0.75\textwidth]{unitary_transformation_contours_kvnns_79_111_222_lamb1,5_Lamb2,0.png}%
+	\caption{Matrix elements of $\delta U(k,k')$ with the EMN N$^4$LO 500\,MeV, RKE N$^4$LO 450\,MeV, and Gezerlis \textit{et al.}~N$^2$LO 1\,fm potentials with Wegner and block-diagonal generators in the $^3$S$_1$ channel.
+Here we set $\lambda=1.5$\,fm$^{-1}$ for band-diagonal evolution, and $\LambdaBD=2$ and $\lambda=1$\,fm$^{-1}$ for block-diagonal evolution.}
+	\label{fig:delta_U_default_potentials}
+\end{figure*}
+
+We can also use \eqref{eq:factored_op} to make comparisons for the same nucleus but with different potentials.
+We use $\ataq$ with $q \gg \lambda$ or $\LambdaBD$ as an example, so 
+%
+\begin{align}
+    \mel{q'}{[O_Q]_\infty}{q''} \rightarrow \delta(q'-q)\delta(q''-q)
+\end{align}
+%
+and  the ratio for two different potentials A and B is
+%
+\begin{align}
+	\label{eq:momentum_proj_matrix_elements_ratio}
+	R[\ataq(k,k')] &\equiv
+	\frac{\mel{k}{\bigl[\ataq\bigr]^A_{\lambda}}{k'}}
+	{\mel{k}{\bigl[\ataq\bigr]^B_{\lambda}}{k'}} 
+	\notag \\
+   &\approx \frac{\Klo^A(k)\Klo^A(k') \Khi^A(q)^2}
+             {\Klo^B(k)\Klo^B(k') \Khi^B(q)^2}
+   .
+\end{align}
+%
+From Fig.~\ref{fig:factorization_ratios} we verify that the $\Klo$ functions should be approximately the same for several chiral EFT potentials, so this ratio should be roughly constant for $k,k' < \lambda$ and $q \gg \lambda$.
+This is illustrated in Fig.~\ref{fig:R_ratio_comparison} for these same potentials in the $^3$S$_1$ channel for $q = 3\,\mbox{fm}^{-1}$.
+After evolution to $\lambda \ll q$, the ratio $R$ is quite flat in the unshaded region.
+The value of the ratio at $q$ is well approximated at lower $\lambda$ by
+%
+\begin{align}
+    \label{eq:momentum_proj_factorization_ratio}
+    \frac{|\psi^A_{\infty}(q)|^2}{|\psi^B_{\infty}(q)|^2} =
+	\frac{\mel{\psi^A_\lambda}{\bigl[\ataq\bigr]^A_{\lambda}}{\psi^A_\lambda}}
+	{\mel{\psi^B_\lambda}{\bigl[\ataq\bigr]^B_{\lambda}}{\psi^B_\lambda}} 
+	\approx \frac{\Khi^A(q)^2}
+             { \Khi^B(q)^2}
+    \equiv f(q),
+\end{align}
+%
+where $\psi$ denotes the various deuteron wave functions, which share the same low-momentum structure so that the $\Klo$ dependence roughly cancels.
+
+The high-momentum function $f(q)$ is dependent on the differences in the UV behavior of each of the representative potentials.
+This does not mean, however, that one of the potentials is correct and the others are wrong.
+Indeed, matrix elements of the representative operators considered in this section, $\ataq$ and $r^2$, cannot be absolutely measured by themselves in experiments. 
+To relate them to measurable quantities, one must build and calibrate the initial operators for particular experimental observables, as done with EFTs.
+A recent example is the precision calculation of the deuteron structure radius in Ref.~\cite{Filin:2019eoe}, which requires the inclusion of two-body currents that will have scale and scheme dependent contributions to match the measured charge form factor.
+Only after the consistent construction of the Hamiltonian and current operators, with an assessment of uncertainties from theory discrepancies (such as EFT truncation errors), can one reliably compare predictions.
+
+\begin{figure*}[tbh]
+	\includegraphics[clip,width=0.75\textwidth]{unitary_transformation_contours_kvnns_900_901_902_lamb1,2_Lamb2,0.png}%
+    \caption{Matrix elements of $\delta U(k,k')$ with the high-cutoff LO potentials with Wegner and block-diagonal generators in the $^3$S$_1$ channel.
+Here we set $\lambda=1.2$\,fm$^{-1}$ for band-diagonal evolution, and $\LambdaBD=2$ and $\lambda=1$\,fm$^{-1}$ for block-diagonal evolution.}
+	\label{fig:delta_U_high_cutoffs}
+\end{figure*}
+%
+
+For visual insight into factorization, we consider the SRG transformation directly.
+We can write the SRG unitary transformation as
+%
+\begin{eqnarray}
+    \label{eq:delta_U}
+    U(s) = \mathbb{1} + \delta U(s),
+\end{eqnarray}
+%
+where $\delta U(s)$ is responsible for the induced changes in transformed operators.
+In Fig.~\ref{fig:delta_U_default_potentials} we show contours of $\delta U(s)$ in momentum space in the $^{3}S_1$ channel for the three representative potentials all evolved to $\lambda=1.5$\,fm$^{-1}$ with $G=H_D$ in the top row, and to $\lambda=1$ and $\LambdaBD=2$\,fm$^{-1}$ with $G=H_{BD}$ in the bottom row.
+Figure~\ref{fig:delta_U_default_potentials} depicts factorization in the following sense.
+By fixing $k'$ to a value much higher than $\lambda$ or $\LambdaBD$, we can take vertical lines up to $k=\lambda$ or $\LambdaBD$ and see little to no variation in the transformation.
+The transformation approximately depends only on a function of high momentum $\Khi(k')$ in these regions, hence the same shade of color.
+One can verify factorization in the opposite block by fixing $k \gg \lambda$ and taking horizontal lines up to $k'=\lambda$.
+
+The difference in regulator functions between the three representative potentials is apparent in these figures.
+For instance, in the EMN N$^4$LO case, the non-local regulator kills off the high-momentum matrix elements of $\delta U(s)$ because $U(s)$ is expressed in terms of the SRG generator $\eta(s)$ which contains the potential $V(k,k')$.
+In the subsequent panels, the local momentum dependence of RKE N$^4$LO (semi-local) and Gezerlis N$^2$LO (local) is seen in non-zero matrix elements at higher momentum values.
+
+Figure \ref{fig:delta_U_high_cutoffs} shows matrix elements of $\delta U(s)$ for the high-cutoff LO potentials.
+These potentials still exhibit factorization of the SRG transformation, although the function of high momentum $\Khi(q)$ will have much different behavior than the softer chiral potentials.
+Furthermore, we see the appearance of positive, horizontal bands for the band-diagonal transformations.
+In the first column, the band corresponds to the region in which the high-momentum contributions of the initial potential accumulate up to the momentum space cutoff $\Lambda=4$\,fm$^{-1}$.
+For $\Lambda=9$ and $20$\,fm$^{-1}$, the large and positive band corresponds to the decoupled spurious bound state.
+This piece of the transformation decouples the spurious bound state along the diagonal in the evolved potential.
+Otherwise, the low-momentum matrix elements are quite similar to the softer transformations in Fig.~\ref{fig:delta_U_default_potentials}, with larger contributions at high momentum due to the high momentum-space cutoffs.
+
+In this section, we examined the characteristics of SRG evolution for representative operators $\ataq$ and $r^2$.
+The SRG changes in the operator do not lead to any complications that would offset the desired features in the decoupled NN potential.
+Corresponding wave functions are decoupled in momentum space, either collapsing locally to one region with band-diagonal evolution, or cleanly cut off from low- or high-momentum sub-spaces with block-diagonal evolution (depending on the energy of the state).
+The matrix elements of expectation values using the evolved operators and states show how one can take advantage of scale and scheme dependence to calculate consistent observable quantities at lower resolution.
+Lastly, we used factorization to show that high momentum operators exhibit universal scaling dependent on the high-momentum physics of the underlying NN potential.
+That is, the high-momentum (short-distance) physics in the initial wave function appears in the evolved operator.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary and outlook}
+\label{sec:summary}
+
+Operator evolution is a critical aspect of SRG evolution in free-space and in-medium implementations.
+Our initial focus here was on a technical aspect of this evolution: the efficacy and robustness of the Magnus expansion, which we evaluated in a difficult test environment with large cutoffs and spurious states.
+But this study led us to reconsider and expand past studies of operator evolution in light of scheme dependencies arising both from different SRG generators and from different regulators of recent chiral EFT Hamiltonians.
+The flow to low resolutions leads to universality (in the sense of independence from initial scheme dependence) in Hamiltonians and low-energy wave functions.
+The constraint of unitarity then has implications for the corresponding flow of operators, while the scale separation from decoupling leads to consequences from factorization.
+Each of these aspects can be exploited in future analyses of nuclear reactions that account for scale and scheme dependence.
+
+We first used high-cutoff EFTs to verify that the Magnus expansion offers an improved variant of the standard SRG solution methods.
+The Magnus implementation performs SRG transformations to exact unitarity which allows one to solve the flow equation \eqref{eq:srg_flow} using simple, efficient methods.
+In Fock space, the benefits of the Magnus expansion are especially important as evolution of several operators simultaneously can be quite difficult for many-body systems, hence the prominence of the Magnus expansion in IMSRG calculations.
+Here we showed that the Magnus implementation works effectively for a difficult free-space test problem in decoupling bound states using LO chiral potentials at high cutoffs.
+The Magnus expansion reproduces the generator dependence seen in Ref.~\cite{Wendt:2011qj} and obtains eigen-energies to high accuracy.
+In carrying out this test, we also showed that the block-diagonal generator decouples spurious, deeply bound states cleanly in the high-momentum sub-block but at higher momentum values than the band-diagonal generators and without apparent dependence on the discretization mesh.
+However, the Magnus expansion does not converge in some cases, which is similar to a related issue in IMSRG calculations involving intruder states.
+The NN convergence problem is related to the interaction and can be avoided in at least some cases by a careful selection of generator $G$.
+
+The initial high-cutoff LO Hamiltonians and the contrasting evolution with band- and block-diagonal generators represent extremes of scale and scheme dependence.
+Recently introduced chiral EFT Hamiltonians are characterized by a different type of scheme dependence in the use of qualitatively distinct regulators. 
+In comparing their flows to low resolution, we confirmed that the momentum-space matrix elements of this new generation of \chiEFT\ Hamiltonians flow to a universal form when the decoupling scale is below the region of phase equivalence.
+This happens for either band or block diagonal generators, but the universal form is not the same~\cite{Dainton:2013axa}.
+We found small deviations from universality in channels dominated by one-pion exchange or only contact forces, which are attributed to the difference in regulator functions.
+This was examined quantitatively using the Frobenius norm and SDT correlation coefficient and angle $\theta_{V,V'}$ as measures of the differences in the evolved potentials.
+
+The flow to near-universality for potentials leads to almost perfect universality of deuteron wave functions.
+Dramatically different initial wave functions in both their S-wave and D-wave characteristics collapse to near-indistinguishable low-resolution versions. 
+We expect a similar collapse, if not as extreme, for the lowest-energy states in other nuclei.
+This is encouraging for our goal of a controlled understanding of how spectroscopic factors are quenched in terms of a mismatch of high-resolution reaction models and low-resolution structure.
+With universal wave functions at low resolution, we expect to identify universal features in the evolved reaction operators.
+
+This goal led us to revisit the SRG evolution of non-Hamiltonian operators first studied in \cite{Anderson:2010aq,Bogner:2012zm} (see also \cite{Schuster:2013sda,Schuster:2014lga}).
+We first extended our SRG analysis to momentum projection operators at low and high momentum.
+Evolution of the momentum projection operator exemplifies the benefits that arise from SRG-transformed operators.
+In particular, with decoupling at lower resolution there is a shift of strength to low momentum in matrix element of low-energy wave functions through induced two-body contributions (and smaller higher-body contributions that do not contribute to the deuteron).
+This induced structure is very smooth and does not exhibit artifacts from the discretization of the operator.
+The smoothness and universal properties are well understood from the factorization of the unitary transformations for well-separated momentum arguments.
+The ratios of the same hard operators for different potentials scale with the high momentum and differ in magnitude as expected from differences in the ultraviolet content of the potentials.
+(Note that to get the \emph{same} matrix elements, the operators themselves would have to be appropriately matched for the experimental observable in question.)
+This suggests that a reliable theoretical understanding of high-energy reactions is possible using low-energy structure components (the initial wave function) with no insurmountable complications from the evolved operators.
+
+Another representative operator is $r^2$, which is sensitive to the long-distance wave-function structure in coordinate space.
+In momentum space, this operator has strength at all momentum scales and its visual form is highly sensitive to the momentum discretization scheme.
+The two-body induced contributions from this operator to a low-energy state like the deuteron are small (see Ref.~\cite{Schuster:2014lga} for results on induced three-body contribution).
+We isolated four types of contribution to the induced operator (see Fig.~\ref{fig:r2_srg_changes}).
+The part originating fully from the high-momentum sector takes the same smooth form as the induced two-body operator for the high-$q$ momentum projection operator, and is explained in the same way by factorization.
+However the other pieces are not so clearly characterized (see Table~\ref{tab:evolved_r2_contributions}).
+This implies that even roughly estimating the net contribution, as in Ref.~\cite{Miller:2018mfb}, may be difficult.
+
+The features highlighted here and in work on the electrodisintegration of the deuteron~\cite{More:2015tpa,More:2017syr} on the interplay of structure (wave functions) and reaction (operators) are promising for a cleaner theoretical understanding of FRIB-type knock-out reactions~\cite{Moro:2018mdk}.
+By exploiting the unitary invariance of measured observables, we can shift the focus from correcting many-body wave functions to the computationally simpler RG flow of the operators. 
+The long-standing and well-documented mismatch of experimental and theoretical cross sections for knock-out reactions (see Ref.~\cite{Tostevin:2014usa} and references therein) can be understood at least in part as a failure to do consistent matching of resolution scales.
+That is, the over-prediction of cross sections with (low resolution) shell model wave functions should be understood as arising because a high-resolution reaction mechanism is used in the analysis. 
+Exploiting the flow to universal soft wave functions and the corresponding consistent operators can open the door to process-independent analyses of these reactions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{acknowledgments}
+We thank A. Garcia, P. Millican, and X. Zhang for fruitful discussions and feedback.
+We are grateful to E. Epelbaum, R. Machleidt, and I. Tews for providing subroutines for calculating the chiral EFT NN potentials used in this work.
+The work of AJT and RJF was supported by the National Science Foundation under Grant Nos.~PHY--1614460 and PHY--1913069, and the NUCLEI SciDAC Collaboration under US Department of Energy MSU subcontract RC107839-OSU\@.
+The work of SKB was supported by the National Science Foundation under Grant No.
+PHY-1713901 and the U.S.
+Department of Energy, Office of Science, Office of Nuclear Physics under Grant No.
+de-sc0018083 (NUCLEI SciDAC Collaboration).
+\end{acknowledgments}
+
+\bibliography{tropiano_bib}
 

### 2020-06-19 Notes/Operator_evolution/operator_evolution.tex
Update operator_evolution.tex
Updated a couple minor typos in figure captions.

@@
 	\caption{Momentum distributions from deuteron (a) and a high-energy state (b) with the RKE N$^4$LO 450 MeV potential.
-Here, we compare SRG-evolved distributions, $G=H_D$ (red solid), $G=H_{BD}$ at $\LambdaBD=2$\,fm$^{-1}$ (blue dash-dotted), and $G=H_{BD}$ at $\LambdaBD=3$\,fm$^{-1}$ (green dashed) each with $\lambda=1.5$\,fm$^{-1}$, to the initial distribution (black dotted).
+Here, we compare SRG-evolved distributions, $G=H_D$ (red solid), $G=H_{BD}$ at $\LambdaBD=2$\,fm$^{-1}$ (blue dash-dotted), and $G=H_{BD}$ at $\LambdaBD=3$\,fm$^{-1}$ (green dash-dotted) each with $\lambda=1.5$\,fm$^{-1}$, to the initial distribution (black dotted).
 Also, $\varepsilon \approx 300$ MeV for the high-energy state in (b).}
@@
 	\includegraphics[clip,width=0.75\textwidth]{momentum_projection_ratios_q3,00_3S1_Wegner_kvnns_111_79_6_222.pdf}%
-	\caption{Ratio of evolved matrix elements $R[\ataq(k,k)]$ (diagonal) and $R[\ataq(k,0)]$ (full off-diagonal) as defined in \eqref{eq:momentum_proj_matrix_elements_ratio} in the $^3$S$_1$ channel for $q = 3,\mbox{fm}^{-1}$.
+	\caption{Ratio of evolved matrix elements $R[\ataq(k,k)]$ (diagonal) and $R[\ataq(k,0)]$ (full off-diagonal) as defined in \eqref{eq:momentum_proj_matrix_elements_ratio} in the $^3$S$_1$ channel for $q = 3\,\mbox{fm}^{-1}$.
 	Three potentials are compared to RKE N$^4$LO after evolution to several values of $\lambda$ with $G = H_D$.

### 2020-07-07 Notes/Operator_evolution/operator_evolution.tex
Updating operator evolution notes
Most up-to-date files which were recently submitted to PRC.

@@
 \begin{figure*}[tbh]
-	\includegraphics[clip,width=0.67\textwidth]{eta_omega_norms_kvnns_900_901_902_3S1_Wegner_k_magnus_6_ds1,0e-05.pdf}%
+	\includegraphics[clip,width=0.67\textwidth]{eta_omega_norms_kvnns_900_901_902_3S1_Wegner_k_magnus_6_ds1p0e-05.pdf}%
 	\caption{Frobenius norms of $\eta(s)$ and $\Omega(s)$ from Magnus-evolving the high-cutoff LO potentials in the $^3$S$_1$--$^3$D$_1$ coupled channel: $\Lambda=4$ (black dashed), $9$ (red dash-dotted) and $20$\,fm$^{-1}$ (blue solid) where $G=H_D$ and $k_{\rm max}=6$.}
@@
 \begin{figure}[t!]
-    \includegraphics[clip,width=0.48\textwidth]{deuteron_wave_func_coord_space_kvnns_79_111_222_Wegner1,2.pdf}%
+    \includegraphics[clip,width=0.48\textwidth]{deuteron_wave_func_coord_space_kvnns_79_111_222_Wegner1p2.pdf}%
     \caption{Deuteron wave functions in coordinate space for the same three chiral potentials as in Fig.~\ref{fig:universality_test_with_sdt_coeff_Wegner} under band-diagonal SRG transformations with $G=H_D$ and $\lambda=1.2$\,fm$^{-1}$.
@@
 \begin{figure}[tbh]
-    \includegraphics[clip,width=0.48\textwidth]{deuteron_wave_func_coord_space_kvnns_6_900_901_Wegner1,2.pdf}%
+    \includegraphics[clip,width=0.48\textwidth]{deuteron_wave_func_coord_space_kvnns_6_900_901_Wegner1p2.pdf}%
     \caption{Same as Fig.~\ref{fig:deuteron_wave_funcs_soft} but for the high-cutoff LO potentials with $\Lambda=4$ and $9$\,fm$^{-1}$ and AV18, and $\lambda=1.2$\,fm$^{-1}$.
@@
 \begin{figure*}[t!]
-	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_contours_q0,30_kvnn_111_3S1.png}%
+	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_contours_q0p30_kvnn_111_3S1.png}%
 	\caption{Momentum projection operator $\mel{k}{\ataq}{k'}$ for $q=0.3$\,fm$^{-1}$ under SRG transformations using the RKE N$^4$LO 450 MeV potential, evolving with Wegner ($H_D$) and block-diagonal ($H_{BD}$) generators in the $^3$S$_1$ channel.
@@
 
-	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_contours_q3,00_kvnn_111_3S1.png}%
+	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_contours_q3p00_kvnn_111_3S1.png}%
 	\caption{Same as Fig.~\ref{fig:momentum_projection_contours_q0,30_3S1_RKE} but for $q=3$\,fm$^{-1}$.}
@@
 	\subfloat[]{%
-	\includegraphics[clip,width=0.35\textwidth]{high_energy_state_eps300,0_momentum_distributions_kvnn111.pdf}%
+	\includegraphics[clip,width=0.35\textwidth]{high_energy_state_eps300p0_momentum_distributions_kvnn111.pdf}%
 	}
@@
 \begin{figure*}[tbh]
-	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_integrand_contours_q3,00_kvnn_111.png}%
+	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_integrand_contours_q3p00_kvnn_111.png}%
 	\caption{Integrand of $\mel{\psi_d}{\ataq}{\psi_d}$ in momentum space where $\psi_d$ is the deuteron wave function and $q=3$\,fm$^{-1}$.
@@
 \begin{figure*}[tbh]
-	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_integrand_contours_q3,00_kvnn_111_eps300,0.png}%
+	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_integrand_contours_q3p00_kvnn_111_eps300p0.png}%
 	\caption{Same as Fig.~\ref{fig:momentum_projection_integrand_contours_q3,00_RKE} but with a high-energy state $\psi_{\varepsilon}$ where $\varepsilon \approx 300$ MeV.}
@@
 \begin{figure*}[tbh]
-	\includegraphics[clip,width=0.85\textwidth]{unitary_transformation_ratios_k0_0,1_kpoints_0,5_1,0_1,5_3,0kvnns_79_111_222_3S1_Wegner.pdf}%
+	\includegraphics[clip,width=0.85\textwidth]{unitary_transformation_ratios_k0_0p1_kpoints_0p5_1p0_1p5_3p0kvnns_79_111_222_3S1_Wegner.pdf}%
 	\caption{Numerical tests of factorization of the unitary transformation  by plotting ratios of $|U(k,q)|$ in the $^3$S$_1$ channel as a function of $q$ for fixed $k=k_0$ in the denominator and several values of $k_i$ in the numerator.
@@
 \begin{figure*}[tbh]
-	\includegraphics[clip,width=0.75\textwidth]{momentum_projection_ratios_q3,00_3S1_Wegner_kvnns_111_79_6_222.pdf}%
+	\includegraphics[clip,width=0.75\textwidth]{momentum_projection_ratios_q3p00_3S1_Wegner_kvnns_111_79_6_222.pdf}%
 	\caption{Ratio of evolved matrix elements $R[\ataq(k,k)]$ (diagonal) and $R[\ataq(k,0)]$ (full off-diagonal) as defined in \eqref{eq:momentum_proj_matrix_elements_ratio} in the $^3$S$_1$ channel for $q = 3\,\mbox{fm}^{-1}$.
@@
 \begin{figure*}[tbh]
-	\includegraphics[clip,width=0.75\textwidth]{unitary_transformation_contours_kvnns_79_111_222_lamb1,5_Lamb2,0.png}%
+	\includegraphics[clip,width=0.75\textwidth]{unitary_transformation_contours_kvnns_79_111_222_lamb1p5_Lamb2p0.png}%
 	\caption{Matrix elements of $\delta U(k,k')$ with the EMN N$^4$LO 500\,MeV, RKE N$^4$LO 450\,MeV, and Gezerlis \textit{et al.}~N$^2$LO 1\,fm potentials with Wegner and block-diagonal generators in the $^3$S$_1$ channel.
@@
 \begin{figure*}[tbh]
-	\includegraphics[clip,width=0.75\textwidth]{unitary_transformation_contours_kvnns_900_901_902_lamb1,2_Lamb2,0.png}%
+	\includegraphics[clip,width=0.75\textwidth]{unitary_transformation_contours_kvnns_900_901_902_lamb1p2_Lamb2p0.png}%
     \caption{Matrix elements of $\delta U(k,k')$ with the high-cutoff LO potentials with Wegner and block-diagonal generators in the $^3$S$_1$ channel.

### 2020-08-18 test.py
Magnus run

@@ -33,40 +33,191 @@
 
 
 # Description of this test:
-#   Test convert_ticks_to_labels function here
+#   Compare times on Magnus v. SRG evolution for a couple potentials.
 
 
 import numpy as np
-from Figures import figures_functions as ff
+from scipy.integrate import solve_ivp
+import time
+# Scripts made by A.T.
+from Potentials.vsrg_macos import vnn
+from run_magnus import run_magnus
 
-x_max = 4.0
-x_stepsize = 1.0 # Step-size in labeling tick marks
-x_ticks = np.arange(0.0, x_max + x_stepsize, x_stepsize)
-x_ticks_strings = ff.convert_ticks_to_labels(x_ticks)
-print(x_ticks_strings)
 
-ylim = (-4.5, 2.5)
-y_stepsize = 1.0
-y_ticks = np.arange(ylim[0] + 0.5, ylim[1] + 0.5, y_stepsize)
-y_ticks_strings = ff.convert_ticks_to_labels(y_ticks)
-print(y_ticks_strings)
+class SRG(object):
+    
+    
+    def __init__(self, H_initial):
+        
+        # h-bar^2 / M [MeV fm^2]
+        hbar_sq_over_m = 41.47
+        
+        # Save matrices in scattering units [fm^-2]
+        self.H_initial = H_initial / hbar_sq_over_m
+        
+        # Save length of matrix
+        self.N = len(H_initial)
 
-ylim = (-4.0, 2.0)
-y_stepsize = 1.0
-y_ticks = np.arange(ylim[0], ylim[1] + y_stepsize, y_stepsize)
-y_ticks_strings = ff.convert_ticks_to_labels(y_ticks)
-print(y_ticks_strings)
+    
+    def commutator(self, A, B):
+        
+        return A @ B - B @ A
+    
+    
+    def matrix2vector(self, A):
+    
+        # Length of matrix
+        N = self.N
+        # Length of vectorized matrix
+        n = int( N * (N+1) / 2 )
+        
+        # Initialize vectorized matrix
+        B = np.zeros(n)
+    
+        a = 0
+        b = N
+    
+        for i in range(N):
+        
+            B[a:b] = A[i][i:]
+            a = b
+            b += N-i-1
 
-colorbar_limits = (-1.0, 1.0)
-mn = colorbar_limits[0]
-mx = colorbar_limits[1]
-levels_ticks = np.linspace(mn, mx, 9)
[…]

### 2020-08-18 Notes/Operator_evolution/operator_evolution.tex
Update operator_evolution.tex

@@
 Here we demonstrate this advantage by applying the Magnus implementation using the first-order Euler step-method.
+Note that the execution time for Magnus applied to free-space SRG is roughly the same as for conventional SRG evolution, because the more complicated evaluations in Eq.~\eqref{eq:magnus_omega} are offset by the fewer evaluations needed with a low-order ODE solver.
 
@@
 For these interactions with cutoffs of order 2--3\,fm$^{-1}$, the two band-diagonal choices are essentially equivalent, unlike for the potentials considered in the previous section when the cutoff was above 4\,fm$^{-1}$.
+We restrict our analysis in this section and the following section to the typical SRG approach as results with the Magnus implementation and standard SRG are indistinguishable for soft potentials.
 
@@
 These features are independent of the mesh and the discretization of the delta functions.
-This is an example of an operator product expansion factorization~\cite{Anderson:2010aq,Bogner:2012zm}, which is reviewed in Sect.~\ref{subsec:factorization}.
+This is an example of an operator product expansion factorization~\cite{Anderson:2010aq,Bogner:2012zm}, which is reviewed in Sec.~\ref{subsec:factorization}.
 
@@
     \caption{SRG contributions to $P r^2 P$ in momentum space, splitting $PU(\LambdaBD)r^2(\infty)U^{\dagger}(\LambdaBD)P$ into four components as in Eq.~\eqref{eq:r2_PP_contributions}.
+For the $\PP$ contribution, the unevolved operator $P r^2 P$ is subtracted out.
 We apply a block-diagonal transformation from RKE N$^4$LO 450 MeV in the $^3$S$_1$ channel with $\LambdaBD=2$\,fm$^{-1}$.}
@@
 In the absence of an explicit regulator for large $r$, the meshes used to create the $r^2$ matrix in coordinate space and then Fourier transform to momentum will act as regulators. 
-Visualizations of the bare $r^2$ operator will then be highly mesh dependent, even though 
-expectation values of $r^2$ will be stable for sufficiently large cutoff in $r$ or small mesh spacing in $k$.
+Visualizations of the bare $r^2$ operator will then be highly mesh dependent, even though expectation values of $r^2$ will be stable for sufficiently large cutoff in $r$ or small mesh spacing in $k$.
 With this in mind, we show visualizations of $\langle k | r^2 | k'\rangle$ in Figs.~\ref{fig:r2_unregulated} and \ref{fig:r2_regulated}, where the latter has an added regularization to illustrate the strong regulator dependence.
@@
 The $\QQ$ panel in Fig.~\ref{fig:r2_srg_changes} is very similar to the corresponding $\PP$ block for the evolved high-momentum $\ataq$ shown in Fig.~\ref{fig:momentum_projection_contours_q3,00_3S1_RKE}.
-This is not a coincidence: these smooth low-momentum contributions have the same origin and same understanding from EFT and OPE factorization (see Sect.~\ref{subsec:factorization}).
-The $\PQ$ block is roughly constant in $k'$ for the same reason, while the $k$ dependence is dependent on the mesh, as is the full contribution in the $\PP$ block (likewise for the $\QP$ block, swapping $k'$ and $k$).
+This is not a coincidence: these smooth low-momentum contributions have the same origin and same understanding from EFT and OPE factorization.
+The $\PQ$ block is roughly constant in $k'$ for the same reason, while the $k$ dependence is associated with the bare operator, and therefore with the regularization (here as in Fig.~\ref{fig:r2_unregulated}), as is the full contribution in the $\PP$ block (likewise for the $\QP$ block, swapping $k'$ and $k$).
 The implications for matrix elements in the deuteron are given in the next section.
+We discuss how the behavior in each panel of Fig.~\ref{fig:r2_srg_changes} follows from factorization in Sec.~\ref{subsec:factorization}.
 The decomposition for other potentials or other choices for $\LambdaBD$ is qualitatively similar, with the $\QQ$ contribution scaling with the hardness of the interaction, which reflects the extent of initial high-momentum components (i.e., the short-range correlations).
@@
 
+Note that in the non-$\QQ$ panels of Fig.~\ref{fig:r2_srg_changes} at least one of the two SRG transformations does not factorize and is fully in the low-momentum $P$ sub-space.
+For instance, in the $\PQ$ panel, we have one integral over low momentum and another over high momentum.
+This yields oscillatory behavior in $k$ from the form of the bare $r^2$ operator (which is scheme dependent) and little variation in $k'$ because the factorized function $\Klo(k')$ is constant at leading order.
+
 %
@@
 
-In this section, we examined the characteristics of SRG evolution for representative operators $\ataq$ and $r^2$.
+In this section, we examined the characteristics of SRG evolution for representative operators $\ataq$ and $r^2$, extending the treatment in Ref.~\cite{Anderson:2010aq}.
 The SRG changes in the operator do not lead to any complications that would offset the desired features in the decoupled NN potential.
@@
 The matrix elements of expectation values using the evolved operators and states show how one can take advantage of scale and scheme dependence to calculate consistent observable quantities at lower resolution.
-Lastly, we used factorization to show that high momentum operators exhibit universal scaling dependent on the high-momentum physics of the underlying NN potential.
+We used factorization to show that high-momentum operators exhibit universal scaling dependent only on the high-momentum physics of the underlying NN potential.
 That is, the high-momentum (short-distance) physics in the initial wave function appears in the evolved operator.
+
+While the results of operator evolution generally have the same behavior for different potentials, the underlying scheme dependence is apparent.
+The induced high-momentum (short-distance) contributions in non-Hamiltonian operators are dependent on the UV scheme of the NN potential.
+Furthermore, the remaining SRG components of non-Hamiltonian operators reflect the scheme dependence of the bare operator.
+For example, contrasting smeared delta functions to the single-point delta functions in $\ataq$ from \cite{Anderson:2010aq} gives differing behavior in the SRG-evolved matrix elements at $k,k'=q$.
+Lastly, we demonstrated that the characteristics of operator evolution are the same for band- and block-diagonal SRG schemes, but the evolved matrix elements are different and reflect the SRG decoupling scheme.
 
@@
 The part originating fully from the high-momentum sector takes the same smooth form as the induced two-body operator for the high-$q$ momentum projection operator, and is explained in the same way by factorization.
-However the other pieces are not so clearly characterized (see Table~\ref{tab:evolved_r2_contributions}).
+However while the qualitative behavior of the other pieces is still explained by factorization, the numerical contributions are scheme dependent (see Table~\ref{tab:evolved_r2_contributions}).
 This implies that even roughly estimating the net contribution, as in Ref.~\cite{Miller:2018mfb}, may be difficult.

### 2020-08-18 Notes/Operator_evolution/referee_response.tex
Create referee_response.tex

% Response to referee comments.

\documentclass[preprintnumbers,floatfix,aps,prc,preprint,nofootinbib]{revtex4-1}

\usepackage{physics} % For bra-ket notation

\newcommand{\ataq}{a^{\dagger}_q a_q}
\newcommand{\PP}{\ensuremath{P\mbox{--}P}}
\newcommand{\PQ}{\ensuremath{P\mbox{--}Q}}
\newcommand{\QP}{\ensuremath{Q\mbox{--}P}}
\newcommand{\QQ}{\ensuremath{Q\mbox{--}Q}}
\newcommand{\Klo}{K_{\text{lo}}}
\newcommand{\Khi}{K_{\text{hi}}}
\newcommand{\LambdaBD}{{\Lambda_{\text{BD}}}}

\begin{document}

We thank the referee for her/his careful reading of our paper and for the questions and suggestions. We address each of the points in turn.

\begin{enumerate}

    \item ``The results of section II nicely demonstrate the benefits of the Magnus expansion. I would find it useful if the authors could add some brief discussion on the computational cost of the Magnus expansion (as a function of $k_{\rm max}$) compared to the traditional SRG evolution for a given choice of tolerance for the ODE solver.''

    For the range of applications in the paper, the computational cost is roughly comparable to the conventional free-space SRG.
    While the evaluation of the RHS of the Magnus formulation Eq.~(7) is more complicated with increasing $k_{\rm max}$, it allows the use of a simple ODE solver such as the first-order Euler method, which takes fewer evaluations of the RHS than a typical adaptive high-order solver required to solve Eq.~(2) to comparable precision.
    We've added a sentence to this effect in section II B (on page 5).
    To reiterate what we say in the paper, the computational benefits of the Magnus approach are particularly for the in-medium SRG.

    \item ``At the beginning of section III the authors should add a statement to clarify to what extend the studies in this section are connected to the previous section. First, I assumed that the SRG studies would also be based on the Magnus expansion, this time applied to the high-order NN interaction. However, it seems that these two sections are not immediately related. Is there a reason why the Magnus method was not used for the calculations? Is the agreement between the Magnus method and the traditional evolution expected to be comparable to the results shown in section II?''

    We use the SRG for sections III-IV because the Magnus implementation and typical SRG approach are indistinguishable with soft potentials, unlike the case in section II where we tested high-cutoff potentials, which are intrinsically hard. We added a statement clarifying this at the end of the first paragraph in section III.

    \item ``I find the results shown if Fig.~16 somewhat confusing, especially those in the left three panels. What is the significance of the apparent oscillatory behavior? In the main text these features are attributed to the 'dependence on the mesh'. What does that mean? Is it then even useful to study these matrix elements? I would naively expect that the P-P part in the left panel should be a smooth function without the visible oscillatory artefacts. It would be helpful for me if the authors could comment on that in some more detail.''

    The oscillations seen in Fig.~16 are dependent on the bare $r^2$ operator, which depends on its regularization (which is what we meant by dependent on the mesh) as illustrated in Figs.~14 and 15.
    It is useful to visualize these results, which illustrate factorization and in particular the form of the \QQ\ part.
    We can see the origin of the oscillations by using factorization of the SRG transformation, where $U(k,q) \approx \Klo(k) \Khi(q)$ and from Ref.~[26], $U(k'',k') \approx Z(\LambdaBD) \delta(k''-k')$ where $k,k',k'' < \LambdaBD \ll q$.
    We can take the $\QP$ contribution to $Pr^2P$ as an example. It has the approximate form 
    \begin{align}
       \Klo(k) &\int_{\LambdaBD}^{\infty} dq\, \int_0^{\LambdaBD} dk''\, \Khi(q) \mel{q}{r^2}{k''} Z(\LambdaBD) \delta(k''-k')
       \notag \\
       & \approx 
       \Klo(k) \int_{\LambdaBD}^{\infty} dq\, \Khi(q) \mel{q}{r^2}{k'} Z(\LambdaBD)
    \end{align}
    The $k$-dependence drops out (to leading order $\Klo(k)$ is a constant), and the $k'$-dependence is oscillatory due to the form of the bare $r^2$.
    This explains the vertical stripes in the middle two panels of Fig.~16 being nearly constant within each stripe.
    The oscillatory artefacts are based on setting a sharp cutoff in coordinate space (i.e., an unregulated coordinate-space operator, see Fig.~14 for momentum-space matrix elements).
    Indeed, we can regulate the coordinate-space $r^2$ operator and smooth out the oscillations as in Fig. 15, which keeps a similar induced form in the $\QQ$ panel.
    The oscillations in the \PP\ panel are emphasized because we subtract out the initial $P r^2 P$ operator in Fig.~16;
    we have added a note about this in the caption of Fig.~16.
    At the end of section IV A we added some discussion on the non-$\QQ$ panels, pointing to section IV C for more detail.
    In section IV C, we added further explanation of the terms in Eq.~(15) and Fig.~16 using factorization.

    \item ``It seems that several of the presented results in section IV are directly related to the discussions and results presented in Ref.~[26]. It would be helpful if the authors could add a paragraph in which they summarize the new aspects and insights, as well as differences and similarities of the discussed results compared to Ref.~[26].''

    Our results in Sec.~IV heavily build on the results of Ref.~[26], but extend the conclusions of Ref.~[26] with an emphasis on scheme dependence by contrasting several NN potentials, utilizing band- and block-diagonal SRG decoupling, and varying the bare operators through the implementation of smeared delta functions in $\ataq$ or adding a coordinate-space regulator to $r^2$. We highlight the different forms of scheme dependence in several examples throughout the section. 
    We also apply factorization more widely (as for the $r^2$ analysis) and discuss the implications for different knock-out experiments.
    To summarize these new aspects, we added a paragraph to the end of Sec.~IV on how scheme dependence affects our conclusions on SRG operator evolution.

\end{enumerate}

\end{document}

### 2021-06-18 densities.py
Update densities.py

@@ -18,7 +18,7 @@
 #                averaging over \int dr r^2 to snmd.py and pmd.py separately.
 #                Renamed from lda.py to densities.py where lda.py is now in
 #                Old_codes.
-#   06/17/21 --- Added He3 from www.phy.anl.gov/theory/research/density/.
+#   06/17/21 --- Added He4 from www.phy.anl.gov/theory/research/density/.
 #
 #------------------------------------------------------------------------------
 

### 2021-06-18 pmd.py
Update pmd.py

@@ -450,18 +450,6 @@ class pair_momentum_distributions(object):
             # 1, \delta U, and \delta U^2 where the 1 term includes two r-
             # integrations
             
-            # QUESTIONS:
-            # 1. Why do the 1 term and \delta U terms differ by a factor of
-            # (2*\pi)^3?
-            # 2. What should the normalization of \int d3q give with Q=0?
-            
-            # # 1 term
-            # n_lambda[i, 1] = 1/(2*np.pi)**3 * 2 * n_lambda_temp[i, 0] * \
-            #                   n_lambda_temp[i, 1]
-            
-            # # \delta U and \delta U^2 terms
-            # n_lambda[i, 2:] = n_lambda_temp[i, 2:]
-            
             # 1 term
             n_lambda[i, 1] = 2 * n_lambda_temp[i, 0] * n_lambda_temp[i, 1]
             

### 2021-08-02 potentials/xvsrg_macos/src/convergence.f90
Organizing GitHub directories

@@ -1,0 +1,471 @@
+ module convergence
+      use myinterpolation, only: vkku399lag
+      implicit none
+      private
+      logical :: inmedium
+      real(8), parameter :: hb2m = 41.47
+      complex(16), allocatable :: psivec(:,:), etas(:) 
+      public::weinberg !,diagonalizeK,weinberg_u,weinberg_c
+
+ contains
+
+
+ subroutine weinberg(coupled,P,xkf,lambda,Ecm,xk,wk,vnn,np,eta,psi)
+      logical:: coupled
+      integer:: np
+      real(8):: P, xkf, lambda, Ecm, xk(:), wk(:), vnn(:,:)
+      complex(16) :: eta(size(vnn(1,:))), psi(size(vnn(1,:)),size(vnn(1,:)))
+      intent(in) :: coupled, P, xkf, lambda, Ecm, xk, wk, vnn, np
+      intent(out) :: eta, psi
+
+      inmedium=.FALSE.
+      IF(xkf .gt. 0.0001d0) inmedium = .TRUE.
+       
+      IF(coupled)ALLOCATE(psivec(1:2*np,1:2*np),etas(1:2*np))
+      IF(.not.coupled)ALLOCATE(psivec(1:np,1:np),etas(1:np))
+
+      IF(Ecm .gt. 0)THEN
+           
+          IF(coupled)THEN
+              
+              CALL weinberg_c(P,xkf,lambda, Ecm, xk, wk, vnn,np)
+          ELSE 
+              CALL weinberg_u(P,xkf,lambda, Ecm, xk, wk, vnn(1:np,1:np),np)
+          ENDIF
+  
+      ELSE
+
+        IF(coupled)THEN  
+           CALL diagonalizeK(xkf,P,lambda,coupled,Ecm,1,xk,wk,vnn(1:2*np,1:2*np),np)
+        ELSE
+          CALL diagonalizeK(xkf,P,lambda,coupled,Ecm,1,xk,wk,vnn(1:np,1:np),np)
+        ENDIF
+      ENDIF
+
+      eta = etas
+      psi = psivec
+
+      DEALLOCATE(psivec,etas)
+
+ end subroutine weinberg
+
+
+ subroutine weinberg_u(P,xkf,lambda,Elab,xk,wk,vnn,np)
+!      use vnn_module, ONLY:hb2m
[…]

### 2021-08-02 xnotes/nn_operator_conventions/operator_conventions.tex
Organizing GitHub directories

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% File: operator_conventions.tex
%
% Author: A. J. Tropiano (tropiano.4@osu.edu)
% Date: March 11, 2020
%
% Notes on calculating NN operators in momentum space documenting our
% convention in detail.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[preprintnumbers,floatfix,aps,prc,preprint,nofootinbib]{revtex4-1}

% Packages
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bbold}
\usepackage{bm}
\usepackage{cellspace}
\usepackage{color}
\usepackage{enumerate}
\usepackage{graphicx}
\graphicspath{{Figures/}} % Setting the graphics path
\usepackage{hyperref} % For clickable links to sections within table of contents
\usepackage{physics} % For bra-ket notation
\usepackage[figuresright]{rotating}
\usepackage{siunitx}
\usepackage[caption=false]{subfig} % For sub-figures

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{NN operator conventions}

\author{A.~J.~Tropiano$^{1}$}

\affiliation{%
$^1$\mbox{Department of Physics, The Ohio State University, Columbus, OH 43210, USA}
}

\date{\today}

\begin{abstract}
Notes on calculating NN operators in momentum space documenting our convention in detail.
\end{abstract}

\maketitle

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Wave functions and potentials}
\label{sec:wave_functions_potentials}

We implement our calculations in two-particle partial-wave momentum-space with basis states $\ket{klm}$ where $k$ is the magnitude of the relative momentum of the nucleons, $l$ is the orbital momentum associated with the relative motion, and $m$ is the projection of the orbital momentum onto the z-axis in units where $\hbar=1$.
According to Dirac QM2 conventions, the completeness relation is given by
%
\begin{eqnarray}
    \label{eq:completeness_relation}
    \mathbb{1} = \frac{2}{\pi} \sum_{l,m} \int_0^{\infty} dk k^2 \ket{klm} \bra{klm}.
\end{eqnarray}
%
Projecting onto a partial-wave channel and suppressing the indices reduces this relation to
%
\begin{eqnarray}
    \label{eq:completeness_relation_reduced}
    \mathbb{1} = \frac{2}{\pi} \int_0^{\infty} dk k^2 \ket{k} \bra{k}.
\end{eqnarray}
%

In our situation, we diagonalize a Hamiltonian $H$ for eigenenergies $E_{\alpha}$ (both of which are in units MeV) and eigenfunctions $\ket{\psi_{\alpha}}$, that is,
%
\begin{eqnarray}
    \label{eq:schrodinger_equation}
    H \ket{\psi_{\alpha}} = E_{\alpha} \ket{\psi_{\alpha}}.
\end{eqnarray}
%
We write Eq.~\eqref{eq:schrodinger_equation} in momentum-space using the completeness relation Eq.~\eqref{eq:completeness_relation_reduced}
%
\begin{eqnarray}
    \label{eq:schrodinger_equation_cont}
    \frac{2}{\pi} \int_0^{\infty} dk' k'^2 \mel{k}{H}{k'} \bra{k'} \ket{\psi_{\alpha}} = E_{\alpha} \bra{k} \ket{\psi_{\alpha}}.
\end{eqnarray}
%
Numerically, the problem is discrete.
We construct an array of momentum values $k_i$ with weights $w_i$ using Gaussian-Legendre quadrature where $i=1 \cdots N$.
Then Eq.~\eqref{eq:schrodinger_equation_cont} takes the following form,
%
\begin{eqnarray}
    \label{eq:schrodinger_equation_disc_1}
    \frac{2}{\pi} \sum_{j=1}^{N} w_j k_j^2 \mel{k_i}{H}{k_j} \bra{k_j} \ket{\psi_{\alpha}} = E_{\alpha} \bra{k_i} \ket{\psi_{\alpha}}.
\end{eqnarray}
%
Let's rewrite Eq.~\eqref{eq:schrodinger_equation_disc_1} such that the momenta and weights are absorbed into the Hamiltonian and wave functions so we can connect to numerically diagonalizing a matrix as is done in practice.
Start by multiplying by a factor of $\sqrt{\frac{2 w_i}{\pi}} k_i$ on both sides of Eq.~\eqref{eq:schrodinger_equation_disc_1}:
%
\begin{eqnarray}
    \label{eq:schrodinger_equation_disc_2}
    \frac{2}{\pi} \sum_{j=1}^{N} \sqrt{\frac{2 w_i}{\pi}} k_i w_j k_j^2 \mel{k_i}{H}{k_j} \bra{k_j} \ket{\psi_{\alpha}} = E_{\alpha} \sqrt{\frac{2 w_i}{\pi}} k_i \bra{k_i} \ket{\psi_{\alpha}}.
\end{eqnarray}
%
Rearranging the momenta and weights, we have
%
\begin{eqnarray}
    \label{eq:schrodinger_equation_disc_3}
    \sum_{j=1}^{N} ( \frac{2}{\pi} k_i k_j \sqrt{w_i w_j} \mel{k_i}{H}{k_j} ) ( \sqrt{\frac{2 w_j}{\pi}} k_j \bra{k_j} \ket{\psi_{\alpha}} ) = E_{\alpha} ( \sqrt{\frac{2 w_i}{\pi}} k_i \bra{k_i} \ket{\psi_{\alpha}} ),
\end{eqnarray}
%
\begin{eqnarray}
    \label{eq:schrodinger_equation_disc_4}
    \sum_{j=1}^{N} \tilde{H}_{ij} (\tilde{\psi_{\alpha}})_j = E_{\alpha} (\tilde{\psi_{\alpha}})_i,
\end{eqnarray}
%
where
%
\begin{eqnarray}
    \label{eq:hamiltonian_with_factor}
    \tilde{H}_{ij} \equiv \frac{2}{\pi} k_i k_j \sqrt{w_i w_j} \mel{k_i}{H}{k_j},
\end{eqnarray}
%
\begin{eqnarray}
    \label{eq:wave_func_with_factor}
    (\tilde{\psi_{\alpha}})_i \equiv \sqrt{\frac{2 w_i}{\pi}} k_i \bra{k_i} \ket{\psi_{\alpha}}.
\end{eqnarray}
%
If one does not include the factor of $\sqrt{\frac{2}{\pi}}$ in Eq.~\eqref{eq:wave_func_with_factor}, then $\bra{\psi_{\alpha}} \ket{\psi_{\alpha}} = \frac{2}{\pi}$ given our completeness relation Eq.~\eqref{eq:completeness_relation_reduced}.

In practice, we diagonalize the Hamiltonian $\tilde{H}$ for normalized eigenvectors which are the wave functions $\tilde{\psi_{\alpha}}$.
Note, both $\tilde{H}$ and $\tilde{\psi_{\alpha}}$ include the momentum/weight factors.
Therefore, in presenting potentials and wave functions that are independent of the momentum-mesh, we must plot quantities with the factors of momenta and weights divided out, $\tilde{V}_{ij} \times \frac{\pi}{2 k_i k_j \sqrt{w_i w_j}}$ and $\tilde{\psi}_{i} \times \frac{\sqrt{\pi}}{k_i \sqrt{2 w_i}}$. In Fig.~\ref{fig:momentum_distributions} we show deuteron momentum distributions using $\bra{k_i} \ket{\psi_d}$ for two different momentum meshes.

% \textcolor{red}{Question: Is there ambiguity in the factor of $\frac{2}{\pi}$?}
% For instance, start from the following equation and follow the same line of logic as before:
% %
% \begin{eqnarray}
%     \label{eq:schrodinger_equation_proj_1}
%     \mel{\psi_{\alpha}}{H}{\psi_{\alpha}} = E_{\alpha},
% \end{eqnarray}
% %
% \begin{eqnarray}
%     \label{eq:schrodinger_equation_proj_2}
%     (\frac{2}{\pi})^2 \sum_{i=1}^{N} \sum_{j=1}^{N} w_i w_j k_i^2 k_j^2 \bra{\psi_{\alpha}} \ket{k_i} \mel{k_i}{H}{k_j} \bra{k_j} \ket{\psi_{\alpha}} = E_{\alpha},
% \end{eqnarray}
% %
% \begin{eqnarray}
%     \label{eq:schrodinger_equation_proj_3}
%     \sum_{i=1}^{N} \sum_{j=1}^{N} (\tilde{\psi_{\alpha}})_i \tilde{H}_{ij} (\tilde{\psi_{\alpha}})_j = E_{\alpha},
% \end{eqnarray}
% %
% which implies
% \begin{eqnarray}
%     \label{eq:hamiltonian_with_factor_alt}
%     \tilde{H}_{ij} \equiv (\frac{2}{\pi})^2 k_i k_j \sqrt{w_i} \sqrt{w_j} \mel{k_i}{H}{k_j},
% \end{eqnarray}
% %
% \begin{eqnarray}
%     \label{eq:wave_func_with_factor_alt}
%     (\tilde{\psi_{\alpha}})_i \equiv k_i \sqrt{w_i} \bra{k_i} \ket{\psi_{\alpha}}.
% \end{eqnarray}
% %
% This doesn't change the wave function but gives an extra factor of $\frac{2}{\pi}$ in defining $\tilde{H}$ in contradiction to Eq.~\eqref{eq:hamiltonian_with_factor}.
% \emph{I have had this issue in whether there should be an extra factor of $\frac{2}{\pi}$ in defining the momentum projection operator and radius-squared operator because I typically start from the inner product $\mel{\psi}{O}{\psi}$.}

% Let's be careful starting from Eq.~\eqref{eq:schrodinger_equation_proj_1} because there is an implied normalization.  It really should read:
% %
% \begin{align}
%     \label{eq:schrodinger_equation_proj_1b}
%     \mel{\psi_{\alpha}}{H}{\psi_{\alpha}} = E_{\alpha} \braket{\psi_{\alpha}}{\psi_{\alpha}},
% \end{align}
% %
% if we haven't ensured that $\braket{\psi_{\alpha}}{\psi_{\alpha}} = 1$.
% What we know for sure is that
% %
% \begin{align}
%   \label{eq:psi_alpha_norm_tilde}
%     \sum_{i=1}^{N} (\tilde{\psi_{\alpha}})_i^2 = 1 
%      = \sum_{i=1}^{N} k_i^2 w_i 
%         \braket{\psi_\alpha}{k_i} \braket{k_i}{\psi_\alpha} ,
% \end{align}
% %
% using Eq.~\eqref{eq:wave_func_with_factor_alt}.
% But using the completeness relation,
% %
% \begin{align}
%      \braket{\psi_{\alpha}}{\psi_{\alpha}} &= \frac{2}{\pi}\int_0^\infty
%       dk\, k^2\, \braket{\psi_{\alpha}}{k} \braket{k}{\psi_{\alpha}} \\
%       & \longrightarrow
%       \frac{2}{\pi} \sum_{i=1}^{N} k_i^2 w_i 
%         \braket{\psi_\alpha}{k_i} \braket{k_i}{\psi_\alpha}
%         = \frac{2}{\pi}.
% \end{align}
% %
% So there is the extra factor of $2/\pi$.

%
\begin{figure*}[tbh]
    \includegraphics[clip,clip,width=0.6\textwidth]{momentum_distribution_test.png}%
    \caption{Deuteron momentum distributions from the EM N$^3$LO 500 MeV potential with two different momentum meshes: $k_{\rm max}=10$ and $30$ fm$^{-1}$.}
    \label{fig:momentum_distributions}
\end{figure*}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Momentum projection operator}
\label{sec:momentum_projection_operator}

%
\begin{figure*}[tbh]
    \includegraphics[clip,clip,width=0.9\textwidth]{momentum_projection_operator_test.png}%
    \caption{Momentum projection operators with $q=2$ fm$^{-1}$ under SRG transformations from EM N$^3$LO 500 MeV potential with two different momentum meshes: $N=121$ and $141$ where $k_{\rm max}=6$ and $k_{\rm mid}=2$ fm$^{-1}$. (This allows for the same value of $q=1.999$ fm$^{-1}$ in each mesh, so the initial operator is identical.) Here, we use the Wegner generator and set $\lambda=1.5$ fm$^{-1}$.}
    \label{fig:momentum_projection_operators}
\end{figure*}
%

In two-particle momentum-space, the momentum occupation operator $a^{\dagger}_q a_q$ is the same as the momentum projection operator $\ket{q} \bra{q}$.
We can connect the momentum projection operator to the normalization of the wave functions $\ket{\psi_{\alpha}}$.
We suppress the state index $\alpha$ in the following:
%
\begin{align}
    \label{eq:momentum_proj_operator_derivation}
    1 &= \bra{\psi} \ket{\psi} \nonumber \\
    &= \frac{2}{\pi} \int_0^{\infty} dq q^2 \bra{\psi} \ket{q} \bra{q} \ket{\psi} \nonumber \\
    &= (\frac{2}{\pi})^3 \int_0^{\infty} dq q^2 \int_0^{\infty} dk k^2 \int_0^{\infty} dk' k'^2 \bra{\psi} \ket{k} \mel{k}{a^{\dagger}_q a_q}{k'} \bra{k'} \ket{\psi} \nonumber \\
    &\approx (\frac{2}{\pi})^3 \sum_{n=1}^{N} w_n q_n^2 \sum_{i=1}^{N} w_i k_i^2 \sum_{j=1}^{N} w_j k_j^2 \bra{\psi} \ket{k_i} \mel{k_i}{a^{\dagger}_{q_n} a_{q_n}}{k_j} \bra{k_j} \ket{\psi} \nonumber \\
    &= \sum_{n=1}^{N} \sum_{i=1}^{N} \sum_{j=1}^{N} ( \sqrt{\frac{2 w_i}{\pi}} k_i \bra{\psi} \ket{k_i} ) ( \frac{2}{\pi} w_n q_n^2 \frac{2}{\pi} k_i k_j \sqrt{w_i w_j} \mel{k_i}{a^{\dagger}_{q_n} a_{q_n}}{k_j} ) ( \sqrt{\frac{2 w_j}{\pi}} k_j \bra{k_j} \ket{\psi} ) \nonumber \\
    &= \sum_{n=1}^{N} \sum_{i=1}^{N} \sum_{j=1}^{N} (\tilde{\psi_{\alpha}^*})_i \frac{2}{\pi} w_n q_n^2 ( \tilde{a}^{\dagger}_{q_n} \tilde{a}_{q_n})_{ij} (\tilde{\psi_{\alpha}})_j.
\end{align}
%
From this, we identify
%
\begin{align}
    \label{eq:momentum_proj_op_with_factors}
    (\tilde{a}^{\dagger}_{q_n} \tilde{a}_{q_n})_{ij} = \frac{\pi \delta_{ni} \delta_{nj}}{2 w_n q_n^2},
\end{align}
%
\begin{align}
    \label{eq:momentum_proj_op}
    \mel{k_i}{a^{\dagger}_{q_n} a_{q_n}}{k_j} = \frac{\pi (\tilde{a}^{\dagger}_{q_n} \tilde{a}_{q_n})_{ij}}{2 k_i k_j \sqrt{w_i w_j}}.
\end{align}
%

For the purposes of presentation, we want to plot mesh-independent results analogous to plotting mesh-independent potentials.
This concept should be generalized to \emph{any} operator.
Thus, we plot Eq.~\ref{eq:momentum_proj_op} to visualize the momentum projection operator.
In applying SRG transformations to this operator, use Eq.~\eqref{eq:momentum_proj_op_with_factors}, because the transformations are typically constructed out of the normalized eigenvectors of the initial and evolved Hamiltonians meaning the transformation matrix already includes the momenta and weights for ``integrating'' over $dk$ and $dk'$.
Figure \ref{fig:momentum_projection_operators} shows SRG-evolved momentum projection operators $\mel{k_i}{a^{\dagger}_{q_n} a_{q_n}}{k_j}_{\lambda}$ at $q=2$ fm$^{-1}$ and $\lambda=1.5$ fm$^{-1}$ for two different momentum meshes.

Let's do a sanity check by evaluating $\mel{\psi}{a^{\dagger}_q a_q}{\psi}=|\psi(q)|^2$. Note, this is the squared value of the wave function $\psi$ with momenta and weights divided out, evaluated at some momentum value $q$ where the units are fm$^3$.
In the following check, let $q$ also denote the index of the momentum value $q$ within the momentum array.
%
\begin{align}
    \label{eq:momentum_proj_check}
    \mel{\psi}{a^{\dagger}_q a_q}{\psi} &= (\frac{2}{\pi})^2 \int_0^{\infty} dk k^2 \int_0^{\infty} dk' k'^2 \bra{\psi} \ket{k} \mel{k}{a^{\dagger}_q a_q}{k'} \bra{k'} \ket{\psi} \nonumber \\
    &\approx (\frac{2}{\pi})^2 \sum_{i=1}^{N} w_i k_i^2 \sum_{j=1}^{N} w_j k_j^2 \bra{\psi} \ket{k_i} \mel{k_i}{a^{\dagger}_{q} a_{q}}{k_j} \bra{k_j} \ket{\psi} \nonumber \\
    &= (\frac{2}{\pi})^2 \sum_{i=1}^{N} w_i k_i^2 \sum_{j=1}^{N} w_j k_j^2 \bra{\psi} \ket{k_i} \frac{\pi^2 \delta_{ni} \delta_{nj}}{4 q_n^2 w_n k_i k_j \sqrt{w_i w_j}} \bra{k_j} \ket{\psi} \nonumber \\
    &= \bra{\psi} \ket{q} \bra{q} \ket{\psi} \nonumber \\
    &= |\psi(q)|^2.
\end{align}
%

\noindent{
\textbf{Alternative derivation of the momentum projection operator}
}

Let's start by defining the projection operator in Dirac notation for discrete states $\alpha$.
The states are orthogonal and satisfy the completeness relation
%
\begin{align}
    \label{eq:orthogonality}
    \bra{\alpha} \ket{\beta} = \delta_{\alpha \beta},
\end{align}
%
\begin{align}
    \label{eq:completeness}
    \mathbb{1} = \sum_{\alpha} \ket{\alpha} \bra{\alpha} \equiv \sum_{\alpha} P_{\alpha},
\end{align}
%
where $P_{\alpha} \equiv \ket{\alpha} \bra{\alpha}$ is the projection operator for the state $\alpha$.
We can expand any state $\ket{\psi}$ in terms of the states $\ket{\alpha}$,
%
\begin{align}
    \label{eq:expansion_of_psi}
    \ket{\psi} = \sum_{\alpha} \bra{\alpha} \ket{\psi} \ket{\alpha} = \sum_{\alpha} P_{\alpha} \ket{\psi}.
\end{align}
%
Matrix elements of the projection operator are given by
%
\begin{align}
    \label{eq:projection_operator}
    \mel{\beta}{P_{\alpha}}{\gamma} = \bra{\beta} \ket{\alpha} \bra{\alpha} \ket{\gamma} = \delta_{\beta \alpha} \delta_{\alpha \gamma},
\end{align}
%
where we used the orthogonality relation Eq.~\eqref{eq:orthogonality} in the last step.
We can make a consistency check with the projection operator $P_{\alpha}$ by using it to evaluate the normalization of the wave function,
%
\begin{align}
    \label{eq:normalization}
    \sum_{\alpha} \mel{\psi}{P_{\alpha}}{\psi} &= \sum_{\alpha} \sum_{\beta} \sum_{\gamma} \bra{\psi} \ket{\beta} \mel{\beta}{P_{\alpha}}{\gamma} \bra{\gamma} \ket{\psi} \nonumber \\
    &= \sum_{\alpha} \sum_{\beta} \sum_{\gamma} \bra{\psi} \ket{\beta} \bra{\beta} \ket{\alpha} \bra{\alpha} \ket{\gamma} \bra{\gamma} \ket{\psi} \nonumber \\
    &= \sum_{\alpha} \sum_{\beta} \sum_{\gamma} \bra{\psi} \ket{\beta} \delta_{\beta \alpha} \delta_{\alpha \gamma} \bra{\gamma} \ket{\psi} \nonumber \\
    &= \sum_{\alpha} \bra{\psi} \ket{\alpha} \bra{\alpha} \ket{\psi} \nonumber \\
    &= \bra{\psi} \ket{\psi}.
\end{align}
%

Now, let's do the same derivation but for two-particle partial-wave momentum-space with basis states $\ket{klm}$.
In this basis, the orthogonality condition is given by
%
\begin{align}
    \label{eq:orthogonality_ms}
    \bra{klm} \ket{k'l'm'} = \frac{\pi}{2kk'} \delta(k-k') \delta_{ll'} \delta_{mm'}.
\end{align}
%
(This can be verified by taking $\ket{k'l'm'}$ to both sides of Eq.~\eqref{eq:completeness_relation}.)
Likewise we can expand any state $\ket{\psi}$ using the completeness relation Eq.~\eqref{eq:completeness_relation},
%
\begin{align}
    \label{eq:expansion_of_psi_ms}
    \ket{\psi} = \frac{2}{\pi} \sum_{l,m} \int_0^{\infty} dk k^2 \bra{klm} \ket{\psi} \ket{klm} = \frac{2}{\pi} \sum_{l,m} \int_0^{\infty} dk k^2 P_{klm} \ket{\psi},
\end{align}
%
where $P_{klm} \equiv \ket{klm} \bra{klm}$.
Matrix elements of the projection operator are then
%
\begin{align}
    \label{eq:projection_operator_ms_1}
    \mel{klm}{P_{ql''m''}}{k'l'm'} &= \bra{klm} \ket{ql''m''} \bra{ql''m''} \ket{k'l'm'} \nonumber \\
    &= \frac{\pi}{2kq} \delta(k-q) \delta_{ll''} \delta_{mm''} \frac{\pi}{2qk'} \delta(q-k') \delta_{l''l'} \delta_{m''m'}.
\end{align}
%
If we fix the relative orbital angular momentum and projection to $l$ and $m$, respectively, we obtain
%
\begin{align}
    \label{eq:projection_operator_ms_2}
    \mel{k}{P_{q}}{k'} = \frac{\pi^2}{4q^2kk'} \delta(k-q) \delta(q-k'),
\end{align}
%
in agreement with Eqs.~\eqref{eq:momentum_proj_op_with_factors} and \eqref{eq:momentum_proj_op}.
(Note, this has not accounted for the ``discrete'' numerical problem.
Going one step further would introduce sums and weights instead of the integral over $dk$.)
The normalization check is very straight forward and proceeds in the same manner as Eq.~\eqref{eq:momentum_proj_operator_derivation}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Radius-squared operator}
\label{sec:radius_squared_operator}

In order to plot the $r^2$ operator in partial-wave momentum-space, we must change the operator from coordinate-space to partial-wave momentum-space.
Technically, we could make calculations with the $r^2$ operator fully in momentum-space where the operator involves derivatives $\frac{d}{dk}$ acting on a wave function.
However, we avoid this as the derivatives make it impossible to see the operator directly.
In coordinate-space, the operator is given by
%
\begin{align}
    \label{eq:r2_operator_coordinate_space}
    \mel{\mathbf{r}}{r^2}{\mathbf{r'}} = r^2 \delta(\mathbf{r}-\mathbf{r'}).
\end{align}
%
We can transform the operator to partial-wave momentum-space using
%
\begin{align}
    \label{eq:hankel_transformation}
    \bra{\mathbf{r}} \ket{klm} \equiv i^l j_l(kr) Y_{lm}(\Omega_r),
\end{align}
%
and the completeness relation in coordinate-space,
%
\begin{align}
    \label{eq:completeness_relation_coordinate_space}
    \mathbb{1} = \int d\mathbf{r} \ket{\mathbf{r}} \bra{\mathbf{r}},
\end{align}
%
(see Dirac QM2 for further details.)

Now we can isolate the radius-squared operator in momentum-space,
%
\begin{align}
    \label{eq:r2_operator_momentum_space_1}
    \mel{klm}{r^2}{k'l'm'} &= \int d\mathbf{r} \int d\mathbf{r'} \bra{klm} \ket{\mathbf{r}} \mel{\mathbf{r}}{r^2}{\mathbf{r'}} \bra{\mathbf{r'}} \ket{k'l'm'} \nonumber \\
    &= \int d\mathbf{r} \int d\mathbf{r'} [i^l j_l(kr) Y_{lm}(\Omega_r)]^* r^2 \delta(\mathbf{r}-\mathbf{r'}) [i^{l'} j_{l'}(k'r') Y_{l'm'}(\Omega_{r'})] \nonumber \\
    &= \int_0^{\infty} dr r^2 \int d\Omega_r (i^l)^* j_l(kr) Y_{lm}^*(\Omega_r) r^2 i^{l'} j_{l'}(k'r) Y_{l'm'}(\Omega_r) \nonumber \\
    &= \delta_{ll'} \delta_{mm'} (i^l)^* i^{l'} \int_0^{\infty} dr r^4 j_l(kr) j_{l'}(k'r),
\end{align}
%
where we have used the normalization of the spherical harmonic functions in the last step.
Rewriting Eq.~\eqref{eq:r2_operator_momentum_space_1} for the case $l=l'$ and $m=m'$ gives
%
\begin{align}
    \label{eq:r2_operator_momentum_space_2}
    \mel{k}{r^2}{k'}_{lm} = \int_0^{\infty} dr r^4 j_l(kr) j_{l}(k'r).
\end{align}
%
Then switching from a continuous to a discrete basis gives
%
\begin{align}
    \label{eq:r2_operator_momentum_space_3}
    \mel{k_i}{r^2}{k_j}_{lm} = \sum_{m=1}^M \Delta r r_m^4 j_l(k_i r_m) j_{l}(k_j r_m),
\end{align}
%
where we have a linearly spaced array of $r$ values where $dr \rightarrow \Delta r$ and $M$ is the number of values in the array.
Following the general convention from before, we define the operator with momenta and weights factored in,
%
\begin{align}
    \label{eq:r2_operator_momentum_space_with_factors}
    (\tilde{r}_{lm}^2)_{ij} \equiv \frac{2}{\pi} k_i k_j \sqrt{w_i w_j} \mel{k_i}{r^2}{k_j}_{lm}.
\end{align}
%
\begin{figure*}[tbh]
    \includegraphics[clip,clip,width=0.9\textwidth]{r2_operator_test.png}%
    \caption{$r^2$ operators under SRG transformations from EM N$^3$LO 500 MeV potential with two different momentum meshes: $k_{\rm max}=10$ and $30$ fm$^{-1}$. Here, we use the Wegner generator and set $\lambda=1.5$ fm$^{-1}$.}
    \label{fig:r2_operators}
\end{figure*}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{tropiano_bib}

\end{document}

### 2021-08-02 xnotes/physics8820_term_paper/tropiano_term_paper.tex
Organizing GitHub directories

% Quantum many-body physics term paper
% Created 03/29/19 by A.T. (tropiano.4@osu.edu)

\documentclass{article}

% Packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}
\usepackage[font=small,skip=0pt]{caption}
\usepackage{cellspace}
\usepackage{color}
\usepackage{enumerate}
\usepackage{epsfig}
\usepackage[figuresright]{rotating}
\usepackage{float}
\usepackage{graphicx}
\graphicspath{{Figures/}} % Setting the graphics path
\usepackage{hyperref} % For clickable links to sections within table of contents
\usepackage{indentfirst}
\usepackage{physics} % For bra-ket notation
\usepackage{simplewick} % For contractions
\usepackage{siunitx}
\usepackage{subfigure} % For figures with multiple images or pdf's

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{The nuclear many-body problem and the in-medium similarity renormalization group}

\author{Anthony Tropiano}

\date{\today}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}

Low-energy nuclear physics addresses the structure and reactions of atomic nuclei. A current area of interest experimentally targets the properties and limits of stability for different isotopes (nuclei with a fixed number of protons and varying number of neutrons). Rare isotope science connects several areas of physics. In nuclear astrophysics, low-energy nuclear reactions can provide insight on the origin of heavy elements in the universe. From the sub-atomic physics standpoint, we can understand fundamental symmetries and interactions from the interplay of the strong, electromagnetic, and weak interactions in atomic nuclei giving rise to physics beyond the Standard Model. Furthermore, rare isotopes have many practical applications in areas outside of physics; for instance, medicinal sciences, material science, and national security. New rare isotope beam facilities have greatly increased our understanding of these areas.
\\

Solving the nuclear many-body problem is the central task for nuclear structure and reactions. The problem at hand is solving a system of protons and neutrons interacting via the strong force. Progress in theoretical nuclear physics has long been impeded by highly correlated many-body wave functions and highly non-perturbative few- and many-body systems. However, there has been substantial headway in the past decade due to effective field theory (EFT) \cite{Epelbaum:2008ga} and renormalization group (RG) methods combined with computational power. We will focus on the theoretical side of low-energy nuclear physics - in particular, the in-medium similarity renormalization group (IMSRG).
\\

A preliminary step in the nuclear many-body problem is to choose efficient degrees of freedom. Quantum chromodynamics (QCD) is widely accepted as the correct underlying theory for the strong interaction; however, it is not an efficient method of calculating nuclei. With EFT we can choose colorless hadron degrees of freedom instead where the properties of nuclei are manifested by interacting protons and neutrons instead of quarks and gluons. This picture is still complicated by high-energy degrees of freedom making many-body methods difficult or even impossible for medium mass and heavier nuclei. With RG methods we can decouple the low- and high-energy degrees of freedom while still preserving the low-energy observables. First, we give a brief description of an EFT called Chiral EFT. Chiral EFT applies chiral perturbation theory to nuclear systems and gives an EFT involving nucleons (N) and Goldstone bosons, which are pions, due to chiral symmetry breaking. This theory is split into long- and short-range terms where the long-range terms (pion exchanges) are calculated explicitly, and the short-range terms (contact terms) are parametrized by NN scattering data. This provides a clear separation of energy scales in the underlying interaction. RG methods allow us to decouple these energy scales while still preserving the low-energy properties of the initial nuclear potential. These are called ``softened'' potentials and serve as inputs to nuclear many-body calculations. This process is considered an \textit{ab initio} method which essentially means making predictions for A-body nuclei starting from microscopic NN and 3N forces. In Fig.~\ref{fig:nuclear_hockey_stick} we see the tremendous progress \textit{ab initio} methods have made in the past decade where each point on the scatter plot corresponds to a binding energy \textit{ab initio} calculation for an A-body nucleus where A is the total number of nucleons.
\\

%
\begin{figure}
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=10cm]{nuclear_hockey_stick}
  \caption{Binding energies for A-body nuclei within 5\% of the experimental value calculated from \textit{ab initio} methods.}
  \label{fig:nuclear_hockey_stick}
\end{figure}
%

In the SRG procedure, one applies a unitary transformation to an operator to decouple energy scales \cite{Bogner:2006pc, Bogner:2009bt}. For instance, consider an NN potential in momentum-space; it is useful to think of the potential as a matrix $V(\bf{k},\bf{k'})$ dependent on two momenta $\bf{k}$ and $\bf{k'}$. It is common to express nuclear potentials as a function of the magnitudes $k$ and $k'$ via a partial wave expansion. In momentum-space, the coupling of low- and high-momenta means that $V(k,k')$ has non-zero off-diagonal matrix elements. Applying an SRG transformation to $V(k,k')$ renders the potential as band- or block-diagonal form where the off-diagonal matrix elements are driven zero. One can then truncate the matrix keeping the low-momentum part and still calculate low-energy observables to high accuracy.
\\

The in-medium SRG works in the same manner but targets nuclear Hamiltonians in second quantized form, that is, in Fock-space, and solves the A-body problem directly \cite{Hergert:2015awm, Hergert:2016iju}. Now we can imagine a Hamiltonian matrix that couples some reference state to particle-hole excitations. One must choose a basis and reference state for the system. Typically, we take a harmonic oscillator (HO) configuration-space to describe the single-particle states of protons and neutrons in an A-body nucleus. The low-lying spectrum of the system is dominated by particle-hole excitations near the Fermi level. Thus, a single Slater determinant near the nucleus' ground-state is usually taken as the reference state. An IMSRG transformation decouples the reference state from particle-hole excitations, and in the same way as before, we can obtain all low-energy observables with the decoupled reference state. Fig.~\ref{fig:imsrg_decoupling} depicts this process where the reference state 0p0h is decoupled from particle-hole excitations on the right-hand side. Since the model space can be extremely large, the evolved Hamiltonian is truncated to include only the low-lying space and is used to directly tackle the nuclear many-body problem.
\\

%
\begin{figure}
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=10cm]{imsrg_decoupling}
  \caption{Schematic representation of a nuclear Hamiltonian in Fock-space initially (left) and IMSRG evolved (right) where 0p0h, 1p1h, 2p2h, ... means zero, one, and two particle-hole excitations and so forth with respect to the reference state. White squares correspond to matrix elements equal to zero. (Figure from H. Hergert.)}
  \label{fig:imsrg_decoupling}
\end{figure}
%

The remainder of this paper is organized as follows: Section \ref{sec:formalism} presents the mathematical background of the IMSRG and the formulation in Fock-space in the context of transforming a nuclear Hamiltonian. In Section \ref{sec:applications} we give some results from IMSRG calculations and discuss applications of the IMSRG including effective Hamiltonians, the Magnus expansion, and operator evolution. Lastly, we summarize in Section \ref{sec:conclusion}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Formalism}
\label{sec:formalism}

% .....................................................................................................................................................................................................................................
\subsection{Preliminaries}

The SRG decouples operators by applying a continuous unitary transformation $U(s)$ where $s=0 \rightarrow \infty$ is the flow parameter; that is,
%
\begin{eqnarray}
  \label{eq:srg_hamiltonian}
  H(s) = U(s) H(0) U^{\dagger}(s),
\end{eqnarray}
%
where $H(0)$ corresponds to the `bare' Hamiltonian and $H(s)$ corresponds to the evolved, decoupled Hamiltonian at $s>0$. In practice, the unitary transformation $U(s)$ is not explicitly solved for; the evolved Hamiltonian is given by a differential flow equation. To see this, we take the derivative of Eq.~\ref{eq:srg_hamiltonian},
%
\begin{eqnarray}
  \label{eq:hamiltonian_derivative_1}
  \frac{dH(s)}{ds} = \frac{dU(s)}{ds} H(0) U^{\dagger}(s) + U(s) H(0) \frac{dU^{\dagger}(s)}{ds}.
\end{eqnarray}
%
Rearranging Eq.~(\ref{eq:srg_hamiltonian}) for $H(0)$ and substituting into Eq.~(\ref{eq:hamiltonian_derivative_1}) gives
%
\begin{eqnarray}
  \label{eq:hamiltonian_derivative_2}
  \frac{dH(s)}{ds} = \frac{dU(s)}{ds} U^{\dagger}(s) H(s) + H(s) U(s) \frac{dU^{\dagger}(s)}{ds}.
\end{eqnarray}
%
Because $U(s)$ is unitary, we see that
%
\begin{eqnarray}
  \label{eq:antihermitian_transformation}
  \frac{d}{ds} (U(s) U^{\dagger}(s)) = \frac{d}{ds} (I) = 0 \implies \frac{dU(s)}{ds} U^{\dagger}(s) = -U(s) \frac{dU^{\dagger}(s)}{ds}.
\end{eqnarray}
%
The anti-hermitian SRG generator $\eta(s)$ is defined below in terms of the unitary transformation and its derivative,
%
\begin{eqnarray}
  \label{eq:eta}
  \eta(s) \equiv \frac{dU(s)}{ds} U^{\dagger}(s) = -\eta^{\dagger}(s).
\end{eqnarray}
%
We can now write a concise flow equation for $H(s)$ in terms of the SRG generator $\eta(s)$ by substituting Eq.~(\ref{eq:eta}) into Eq.~(\ref{eq:hamiltonian_derivative_2}),
%
\begin{eqnarray}
  \label{eq:srg_flow}
  \frac{dH(s)}{ds} = [ \eta(s), H(s) ].
\end{eqnarray}
%
We can specify the type of flow for the transformation by choosing $G$ in the equation below,
%
\begin{eqnarray}
  \label{eq:srg_generator}
  \eta(s) = [ G, H(s) ].
\end{eqnarray}
%
For instance, to evolve the Hamiltonian to a band-diagonal form, one can set $G=H_{D}(s)$ (the diagonal of the evolving Hamiltonian), also known as the ``Wegner" generator originally implemented in condensed matter physics \cite{Wegner:1994ab}. Another option is the block-diagonal generator which separates the evolved Hamiltonian into low- and high-momentum sub-blocks \cite{Anderson:2008mu}. For the IMSRG, we must formulate the flow equation (\ref{eq:srg_flow}) and Hamiltonian in the language of second quantization.

% .....................................................................................................................................................................................................................................
\subsection{Normal-ordered A-body Hamiltonian}

Since we are dealing with fermions, consider the fermionic creation and annihilation operators, $a_i^\dagger$ and $a_i$, with the anti-commutation relations
%
\begin{eqnarray}
  \label{eq:fermionic_anticommutators}
  \{ a_i^\dagger, a_j^\dagger \} = \{ a_i, a_j \} = 0, \quad \{ a_i^\dagger, a_j \} = \delta_{ij},
\end{eqnarray}
%
where the indices label single-particle quantum states. We can build a many-body basis by acting the creation operator on the vacuum state,
%
\begin{eqnarray}
  \label{eq:manybody_basis}
  \ket{\Phi(i_1, ... \, , i_A)} = \prod_{k=1}^{A} a_{i_k}^\dagger \ket{0}.
\end{eqnarray}
%
As mentioned before, it is much more efficient to work with a reference state near the Fermi level for construction and organization of the many-body basis. Therefore, we take a reference state $\ket{\Phi}$ near the ground-state of the A-body nucleus. We introduce a one-body operator that is normal-ordered with respect to the reference state below,
% 
\begin{eqnarray}
  \label{eq:normal_ordering}
  a_i^\dagger a_j \equiv \, : \! a_i^\dagger a_j \! : + \contraction{}{a}{_i^\dagger}{a} a_i^\dagger a_j,
\end{eqnarray}
%
where the $: \! ... \! :$ indicates normal-ordering and the brace over $a_i^\dagger$ and $a_j$ means they have been contracted. A contraction is the expectation value of the operator in the reference state $\ket{\Phi}$:
%
\begin{eqnarray}
  \label{wick_contraction}
  \contraction{}{a}{_i^\dagger}{a} a_i^\dagger a_j \equiv \mel{\Phi}{a^\dagger_i a_j}{\Phi} \equiv \rho_{ji}.
\end{eqnarray}
%
We can now write any A-body operator as a normal-ordered operator by evaluating contractions between creation and annihilation operators. 
\\

Because nuclei are self-bound objects and therefore translationally invariant, we only need to consider nucleon momenta relative to the center of mass in writing the total kinetic energy. Thus, we consider an intrinsic Hamiltonian where the center of mass kinetic energy is subtracted out: $T_{int} = T - T_{cm}$. We refer to $T_{int}$ as $T$ in the rest of the paper. Then an A-body Hamiltonian with both NN and 3N interactions can be written as,
%
\begin{eqnarray}
  \label{eq:intrinsic_hamiltonian}
  H = (1-\frac{1}{A}) T^{(1)} + \frac{1}{A} T^{(2)} + V^{(2)} + V^{(3)},
\end{eqnarray}
%
where the one- and two-body kinetic energy terms are
%
\begin{eqnarray}
  \label{eq:one_body_kinetic_energy}
  T^{(1)} = \sum_i \frac{ \textbf{p}_i^2 }{ 2m },
\end{eqnarray}
%
\begin{eqnarray}
  \label{eq:one_body_kinetic_energy}
  T^{(2)} = - \frac{1}{m} \sum_{i<j} \textbf{p}_i \cdot \textbf{p}_j.
\end{eqnarray}
%
Note, the sum of the one- and two-body kinetic energy terms are equivalent to a kinetic energy term, $T = \frac{2}{A } \sum_{i<j} \frac{ \textbf{q}_{ij}^2 }{ 2 \mu }$, where $\textbf{q}_{ij}$ is the momentum transfer between two nucleons and $\mu$ is the reduced mass \cite{Hergert:2009na}. Now we can write the Hamiltonian in terms of normal-ordered zero-, one-, two-, and three-body terms where the labels have been chosen for historical reasons,
%
\begin{eqnarray}
  \label{eq:exact_hamiltonian}
  H &=& E + \sum_{ij} f_{ij} : \! a_i^\dagger a_j \! : + \frac{1}{4} \sum_{ijkl} \Gamma_{ijkl} : \! a_i^\dagger a_j^\dagger a_l a_k \! : \nonumber \\
& & + \frac{1}{36} \sum_{ijklmn} W_{ijklmn} : \! a_i^\dagger a_j^\dagger a_k^\dagger a_n a_m a_l \! :.
\end{eqnarray}
%
It is convenient to work in the eigenbasis of the one-body density matrix in defining each contribution in Eq.~(\ref{eq:exact_hamiltonian}), such that
%
\begin{eqnarray}
  \label{eq:one_body_density_matrix}
  \rho_{ab} = n_a \delta_{ab}, \quad n_a \in \{ 0, 1 \}.
\end{eqnarray}
%
Then the normal-ordered terms are given by the following:
%
\begin{eqnarray}
  \label{eq:zero_body_hamiltonian}
  E &=& (1-\frac{1}{A}) \sum_a \mel{a}{T^{(1)}}{a} n_a + \frac{1}{2} \sum_{ab} \mel{ab}{ \frac{1}{A} T^{(2)} + V^{(2)} }{ab} n_a n_b \nonumber \\ 
& & + \frac{1}{6} \sum_{abc} \mel{abc}{V^{(3)}}{abc} n_a n_b n_c,
\end{eqnarray}
%
\begin{eqnarray}
  \label{eq:one_body_hamiltonian}
  f_{ij} &=& (1-\frac{1}{A}) \mel{i}{T^{(1)}}{j} + \sum_{a} \mel{ia}{ \frac{1}{A} T^{(2)} + V^{(2)} }{ja} n_a \nonumber \\
& & + \frac{1}{2} \sum_{ab} \mel{iab}{V^{(3)}}{jab} n_a n_b,
\end{eqnarray}
%
\begin{eqnarray}
  \label{eq:two_body_hamiltonian}
  \Gamma_{ijkl} = \mel{ij}{ \frac{1}{A} T^{(2)} + V^{(2)} }{kl} + \sum_{a} \mel{ija}{V^{(3)}}{kla} n_a,
\end{eqnarray}
%
\begin{eqnarray}
  \label{eq:three_body_hamiltonian}
  W_{ijklmn} = \mel{ijk}{V^{(3)}}{lmn}.
\end{eqnarray}
%
Due to the occupation numbers in Eqs.~(\ref{eq:zero_body_hamiltonian})-(\ref{eq:two_body_hamiltonian}), the sums run over only hole states leading to a 3N contribution in each term.

% .....................................................................................................................................................................................................................................
\subsection{IMSRG flow equations}

When carried out exactly, the evaluation of the commutator on the RHS of Eq.~(\ref{eq:srg_flow}) induces higher-body interactions, implying that $H(s)$ and $\eta(s)$ are A-body operators despite starting out with a lower particle rank at $s=0$. This is seen by considering the following commutator and applying Wick's theorem to evaluate the product of normal-ordered operators,
%
\begin{eqnarray}
  \label{eq:induced_forces}
  [ \, : \! a_i^\dagger a_j^\dagger a_l a_k \! :, \, :a_p^\dagger a_q^\dagger a_s a_r \! : \, ] = \delta_{kp} : \! a_i^\dagger a_j^\dagger a_q^\dagger a_s a_r a_l \! : + \, ...
\end{eqnarray}
%
Hence, every integration step in the flow equation contributes an induced, higher-body term to $H(s)$. Keeping all induced terms is not numerically feasible and a truncation scheme must be introduced. We will consider a simple truncation scheme in which three-body and higher normal-ordered terms in $H(s)$ and $\eta(s)$ are excluded. That is,
%
\begin{eqnarray}
  \label{eq:imsrg2_hamiltonian}
  H(s) \approx E(s) + f(s) + \Gamma(s),
\end{eqnarray}
%
\begin{eqnarray}
  \label{eq:imsrg2_eta}
  \eta(s) \approx \eta^{(1)}(s) + \eta^{(2)}(s).
\end{eqnarray}
%
This is called the IMSRG(2) truncation. Now we can write the IMSRG(2) flow equations in terms of the normal-ordered contributions. Define the permutation symbol as
%
\begin{eqnarray}
  \label{eq:permutation_symbol}
  P_{ij} g(... \, , i, ... \, , j) \equiv g(... \, , j, ... \, , i).
\end{eqnarray}
%
Then the IMSRG(2) flow equations can be written as
%
\begin{eqnarray}
  \label{imsrg_flow_zero_body}
  \frac{dE}{ds} = \sum_{ab} (n_a - n_b) \eta_{ab} f_{ba} + \frac{1}{2} \sum_{abcd} \eta_{abcd} \Gamma_{cdab} n_a n_b \bar{n}_c \bar{n}_d ,
\end{eqnarray}
%
\begin{eqnarray}
  \label{imsrg_flow_one_body}
  \frac{df_{ij}}{ds} &=& \sum_a (1+P_{ij}) \eta_{ia} f_{aj} + \sum_{ab} (n_a-n_b) ( \eta_{ab} \Gamma_{biaj} - f_{ab} \eta_{biaj} ) \nonumber \\
& & + \frac{1}{2} \sum_{abc} ( n_a n_b \bar{n}_c + \bar{n}_a \bar{n}_b n_c ) (1+P_{ij}) \eta_{ciab} \Gamma_{abcj},
\end{eqnarray}
%
\begin{eqnarray}
  \label{imsrg_flow_two_body}
  \frac{d\Gamma_{ijkl}}{ds} &=& \sum_{a} \{ (1-P_{ij})( \eta_{ia} \Gamma_{ajkl} - f_{ia} \eta_{ajkl} ) - (1-P_{kl})( \eta_{ak} \Gamma_{ijal} - f_{ak} \eta_{ijal} ) \} \nonumber \\ 
& & + \frac{1}{2} \sum_{ab} (1-n_a-n_b) ( \eta_{ijab} \Gamma_{abkl} - \Gamma_{ijab} \eta_{abkl} ) \nonumber \\
& & + \sum_{ab} (n_a-n_b)(1-P_{ij})(1-P_{kl}) \eta_{aibk} \Gamma_{bjal},
\end{eqnarray}
%
where $\bar{n}_i = 1 - n_i$. By integrating the IMSRG flow equations, we can decouple an A-body nuclear Hamiltonian and obtain low-energy observables.
\\

The previous description of the IMSRG flow equations are referred to as the M-scheme flow equations. An extension of this, called the J-scheme flow equations, is designed for spherically symmetric systems. We take a spherically symmetric reference state and preserve rotational symmetry in every term of the nuclear Hamiltonian. Then the flow equations become block-diagonal in angular momentum and independent of angular momentum projection quantum numbers. Implementing the J-scheme flow equations greatly reduces the computational cost of evolving the Hamiltonian.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Applications}
\label{sec:applications}

% .....................................................................................................................................................................................................................................
\subsection{Example calculations}

A number of IMSRG example calculations and applications are presented in the following sections. First, we explore how decoupling of a nuclear Hamiltonian works in practice. In Fig.~\ref{fig:imsrg_40Ca_decoupling} we show matrix elements of $^{40}$Ca in the $J^{\pi}=0^+$ neutron-neutron interaction for several different values of $s$. The notation $J^{\pi}=0^+$ means the total angular momentum of the two nucleons is zero with parity +1. The evolution of the Hamiltonian is carried out by integrating the IMSRG(2) J-scheme flow equations with a high-order ODE solver. The input interaction is a chiral NN potential softened by SRG evolution. We see that as $s$ is taken to higher values, the off-diagonal $hhpp$ and $pphh$ matrix elements are driven to zero, that is, $\Gamma_{pp'hh'}(s)$ becomes small as desired.
\\

%
\begin{figure}
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=12cm]{imsrg_40Ca_decoupling}
  \caption{Matrix elements of $^{40}$Ca in the $J^{\pi}=0^+$ neutron-neutron interaction for IMSRG(2) evolutions of $s=0.0$, $1.2$, $2.0$, and $18.3$. Only the hhhh, hhpp, pphh, and pppp sub-blocks of the matrix are shown. (Figure from \cite{Hergert:2015awm}.)}
  \label{fig:imsrg_40Ca_decoupling}
\end{figure}
%

We show IMSRG predictions for ground-state energies of several nuclei. Figure \ref{fig:imsrg_gs_energies} shows IMSRG ground-state energies for $^{78}$Ni, $^{100}$Sn, and $^{132}$Sn with respect to $\hbar \omega$ and single-particle basis size $e_{max}$. These calculations were done using the IMSRG(2) J-scheme with the same NN interaction as before. The gray-dashed line is the found by extrapolating $e_{max} \geq 10$ data sets to infinite basis size. We see a convergence pattern for increasing basis size $e_{max}$ and $\hbar \omega$ in each panel. Overall, the convergent ground-state energies are consistent with other many-body methods such as the No-Core Shell Model or Coupled Cluster methods.
\\

All of the nuclei presented so far are closed-shell nuclei, that is, the occupation orbitals in the nuclear shell model are all filled similar to filled electron orbitals for a noble gas. An open-shell nuclei is a system with valence nucleons occupying states outside an inert core. The following section discusses a method that allows the IMSRG to target open-shell nuclei.
\\

%
\begin{figure}
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=12cm]{imsrg_gs_energies}
  \caption{Convergence of ground-state energies for $^{78}$Ni, $^{100}$Sn, and $^{132}$Sn using IMSRG(2). (Figure from \cite{Hergert:2015awm}.)}
  \label{fig:imsrg_gs_energies}
\end{figure}
%

% .....................................................................................................................................................................................................................................
\subsection{Effective Hamiltonians}

We can target open-shell nuclei by splitting up the single-particle basis into three parts: hole states (h), valence states (v), and non-valence (q) states. We take our reference state $\ket{\Phi}$ as the wave function of the inert core, which can be obtained from a spherical Hartree-Fock (HF) calculation. That is, the nuclear Hamiltonian is normal-ordered with respect to the inert core. Then following the nuclear shell model, we can build an effective Hamiltonian where nucleons in the valence states serve as the degrees of freedom (called valence nucleons). This process can be done microscopically using many-body perturbation theory (MBPT); however, the order-by-order convergence is unclear and results are sensitive to the configuration-space details (HO frequency, choice of valence-space, etc.)
\\

The IMSRG can derive effective valence-space Hamiltonians by decoupling the reference state from valence states. Furthermore, we can decouple valence states (v) from non-valence states (q). Then by diagonalizing the effective Hamiltonian, we can predict the ground-state energy and low-lying excited states. This method is commonly referred to as valence-space IMSRG (VS-IMSRG). In Fig.~\ref{fig:imsrg_O_energy_spectra} we show a comparison of VS-IMSRG calculations to other methods and experimental data for oxygen excitation energies. Gysbers \textit{et al.}~\cite{Gysbers:2019uyb} recently showed significant improvement in nuclear $\beta$-decay calculations using the VS-IMSRG method with consistently evolved operators over the phenomenological shell model approach.

%
\begin{figure}
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=12cm]{imsrg_O_energy_spectra}
  \caption{Excitation spectra of oxygen isotopes using effective interactions derived by VS-IMSRG decoupling (blue solid and dashed lines where the shaded band represents varying $\hbar \omega$ from 20-24 MeV), the coupled-cluster effective interaction (CCEI) approach (green lines), and phenomenological USDB interaction (red lines) in comparison to experimental data (black lines). The dashed lines represent the neutron separation energies. (Figure from \cite{Hergert:2016etg}.)}
  \label{fig:imsrg_O_energy_spectra}
\end{figure}
%

% .....................................................................................................................................................................................................................................
\subsection{The Magnus expansion}

The IMSRG procedure requires solving a system of nonlinear, coupled differential equations which can often be stiff, necessitating a high-order ODE solver. In principle, the evolved Hamiltonian (or any operator) is unitarily equivalent but the numerical error of solving the ODE can lead to error on observable quantities. Furthermore, the model spaces for IMSRG calculations can be extremely large. Evolving several operators is often impossible due to computational memory restrictions in storing several operators. A variant of the IMSRG that utilizes a mathematical technique called the Magnus expansion can overcome these limitations \cite{Morris:2015yna}. We will refer to this as the Magnus implementation or simply Magnus.
\\

The Magnus posits that the unitary transformation takes the form $U(s)=e^{\Omega(s)}$ where $\Omega(s)$ is an anti-hermitian matrix. We then solve for $\Omega(s)$ by integrating its formally exact derivative (details are in \cite{Morris:2015yna}) which allows one to construct $U(s)$ explicitly. From the form of the transformation, any numerical error from solving the ODE leaves the unitarity of the evolved Hamiltonian un-affected preserving the observables. In fact, we can apply a first-order ODE method in solving for $\Omega(s)$ and keep the observables intact. This offers a decent computational speed-up by avoiding a high-order solver. In Fig.~\ref{fig:magnus_16O_gs_energy} we show the $^{16}$O ground-state energy evolving with $s$ comparing the typical IMSRG approach and Magnus implementation where a first-order Euler method ODE solver is used for two step-sizes $\delta s$. An IMSRG curve using a high-order solver is included for comparison. We see that the Magnus approaches the high-order IMSRG result despite the crude first-order method whereas the IMSRG suffers from using a first-order solver. This illustrates the advantage of guaranteed unitarity from the Magnus implementation.
\\

%
\begin{figure}
  \captionsetup{singlelinecheck=false,justification=raggedright}
  \centering
  \includegraphics[width=6cm]{magnus_16O_gs_energy}
  \caption{Ground-state energy of $^{16}$O with respect to the flow parameter $s$ for two SRG softened potentials. The black line corresponds to the standard IMSRG(2) method with a high-order ODE solver. The red dotted and yellow dashed lines correspond to the Magnus implementation using the first-order Euler method where $\delta s$ represents the step-size. The blue dash-dotted and green dash-dotted lines correspond to the IMSRG(2) using the first-order Euler method. (Figure from \cite{Morris:2015yna}.)}
  \label{fig:magnus_16O_gs_energy}
\end{figure}
%

By explicitly solving for the transformation, one can evolve several operators. We simply apply $U(s)$ to any bare operator using the Baker-Campbell-Hausdorff (BCH) formula. In the standard procedure, the solution vector in the flow equation would contain the evolving Hamiltonian as well as any additional operator making drastic demands on computational memory. For these reasons, the Magnus implementation has become a standard technique in IMSRG calculations as studies have targeted observables such as radii, electromagnetic moments and transitions, etc., requiring consistently evolved operators \cite{Parzuchowski:2017wcq}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:conclusion}

In summary, we discussed the \textit{ab initio} IMSRG approach to solving the nuclear many-body problem. In the IMSRG method, a reference state for some A-body system is decoupled from higher excitations via a unitary transformation. The decoupled reference state then contains unitarily equivalent low-energy observables solving the A-body problem. We detailed the IMSRG procedure in second quantization following the M-scheme IMSRG(2) method. Closed-shell results show decoupling and convergent ground-state energies. We briefly presented the VS-IMSRG method in which the Hamiltonian is configured in valence-space to serve as an effective Hamiltonian in shell model calculations. Lastly, we introduced the Magnus expansion in the context of the IMSRG and its importance in general operator evolution.
\\

There are several interesting applications of the IMSRG that were not covered in this paper. In many cases, often for open-shell nuclei, the energy gap in the single-particle spectrum is small leading to near-degenerate excited states with respect to the reference state giving strong configuration mixing. The wave function is said to feature collective correlations when configurations involve many nucleons that are excited simultaneously. The multi-reference IMSRG (MR-IMSRG) method accounts for collective correlations in the wave function of the reference state, extending the reach to more diverse systems such as open-shell nuclei . Furthermore, new studies have focused on consistent evolution of operators other than the Hamiltonian. It is important to understand the effects these transformations have on general operators in the sense that we expect induced interactions from the SRG framework. Lastly, since the introduction of the SRG method to nuclear physics, there has been considerable progress in constructing EFT potentials differing in a number of ways. It would be good to revisit SRG evolution of these interactions to gain insight on renormalizability.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}

\bibitem{Epelbaum:2008ga}
E.~Epelbaum, H.~-W.~Hammer, and U.~G.~Meißner,
Rev. Mod. Phys. {\bf 81}, 1773 (2009) arXiv:0811.1338 [nucl-th].

\bibitem{Bogner:2006pc}
S.~K.~Bogner, R.~J.~Furnstahl, and R.~J.~Perry,
Phys. Rev. C. {\bf 75}, 061001 (2007), arXiv:nucl-th/0609003.

\bibitem{Bogner:2009bt}
S.~K.~Bogner, R.~J.~Furnstahl, and A.~Schwenk,
Prog. Part. Nucl. Phys. {\bf 65}, 94 (2010), arXiv:0912.3688 [nucl-th].

\bibitem{Hergert:2015awm}
H.~Hergert, S.~K.~Bogner, T.~D.~Morris, A.~Schwenk, and K.~Tsukiyama,
Phys. Rept. {\bf 621}, 165 (2016), arXiv:1512.06956 [nucl-th].

\bibitem{Hergert:2016iju}
H.~Hergert, S.~K.~Bogner, J.~G.~Lietz, T.~D.~Morris, S.~Novario, N.~M.~Parzuchowski, and F.~Yuan,
Lect. Notes Phys. {\bf 936}, 477 (2017), arXiv:1612.08315 [nucl-th].

\bibitem{Wegner:1994ab}
F.~Wegner,
Annalen der Physik {\bf 506}, 77 (1994).

\bibitem{Anderson:2008mu}
E.~Anderson, S.~K.~Bogner, R.~J.~Furnstahl, E.~D.~Jurgenson, R.~J.~Perry, and A.~Schwenk,
Phys. Rev. C {\bf 77}, 037001 (2008), arXiv:0801.1098 [nucl-th].

\bibitem{Hergert:2009na}
H.~Hergert, and R.~Roth,
Phys. Lett. B {\bf 682}, 27 (2009), arXiv:0908.1334 [nucl-th].

\bibitem{Gysbers:2019uyb}
P.~Gysbers, \textit{et al.},
Nature Physics, (2019), arXiv:1903.00047 [nucl-th].

\bibitem{Hergert:2016etg}
H.~Hergert,
Phys. Scr. {\bf 92}, 023002 (2017), arXiv:1607.06882 [nucl-th].

\bibitem{Morris:2015yna}
T.~D.~Morris, N.~Parzuchowski, S.~K.~Bogner,
Phys. Rev. C {\bf 92}, 034331 (2015), arXiv:1507.06725 [nucl-th].

\bibitem{Parzuchowski:2017wcq}
N.~M.~Parzuchowski, S.~R.~Stroberg, S.~R.~Navr\'atil, H.~Hergert, and S.~K.~Bogner,
Phys. Rev. C {\bf 96}, 034324 (2017), arXiv:1705.05511 [nucl-th].

\end{thebibliography}

\end{document}

### 2021-08-02 notes/src_physics/src_low_res.tex
Organizing GitHub directories

\documentclass[10pt,aps,prc,floatfix,twocolumn,nofootinbib]{revtex4-1}

% Packages
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bbold}
\usepackage{bm}
\usepackage{cellspace}
\usepackage{color}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{physics} % For bra-ket notation
\usepackage[figuresright]{rotating}
\usepackage{siunitx}
\usepackage[caption=false]{subfig} % For sub-figures
\usepackage{simpler-wick}
\usepackage{xfrac}
\usepackage{hyperref} % For clickable links to sections within table of contents

\graphicspath{{figures_low_res/},{figures/}} % Setting the graphics path

%\floatsetup[figure]{style=plain, subcapbesideposition=top}
\input{macros}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Short-range correlation physics at low RG resolution}

\author{A.~J.~Tropiano$^{1}$, S.~K.~Bogner$^{2}$, R.~J.~Furnstahl$^{1}$}

\affiliation{%
$^1$\mbox{Department of Physics, The Ohio State University, Columbus, OH 43210, USA}  \\
$^2$\mbox{Facility for Rare Isotope Beams and Department of Physics and Astronomy,}  \\
\mbox{Michigan State University, East Lansing, MI 48824, USA}
}

\date{\today}

\begin{abstract}
Recent experiments have succeeded in isolating processes for which short-range correlation (SRC) physics is dominant and well accounted for by SRC phenomenology.
But an alternative and compelling picture emerges from renormalization group (RG) evolution to low RG resolution.
At high RG resolution, SRCs are identified as components in the nuclear wave function with relative pair momenta greater than the Fermi momentum.
Scale separation results in wave-function factorization that can be exploited with phenomenologies such as the generalized contact formalism or the low-order correlation operator approximation. 
Evolution to lower resolution shifts SRC physics from nuclear structure to the reaction operators without changing the measured observables.
We show how the features of SRC phenomenology manifested at high RG resolution are cleanly identified 
at low RG resolution
using simple two-body operators and local-density approximations with uncorrelated wave functions,
all of which can be systematically generalized.
We verify that the experimental consequences to date follow directly at low resolution from well-established properties of nucleon-nucleon interactions such as the tensor force.
Thus the RG reconciles the contrasting pictures of the same experiment and shows how to get correct results using wave functions without SRC components.
Our demonstration has implications for the analysis of knock-out reactions for which SRC physics is not cleanly isolated.

\end{abstract}

\maketitle

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} \label{sec:introduction}

Short-range correlations (SRCs) in atomic nuclei are usually identified as components of the nuclear wave function with nucleon pair momenta well above the Fermi momentum~\cite{Hen:2016kwk}. 
There has long been an apparent need for such SRCs to account for measured cross sections~\cite{Brueckner:1955zzd}, but direct evidence has been nebulous until recent experiments succeeded in cleanly isolating this physics~\cite{Hen:2016kwk,Korover:2014dma,Hen:2014nza,Duer:2018sby,Duer:2018sxh,Schmookler:2019nvf,Cruz-Torres:2020uke,Schmidt:2020kcl,Korover:2020lqf}. 
SRC phenomenologies have been developed that account for the observations, but they seem to be at odds with successful descriptions of nuclear structure such as the shell model that do not feature explicit short-range structure in the nuclear wave function. 
The application of the renormalization group (RG) can make sense of this conflict. 
RG methods are used to analyze critical phenomena in condensed matter and evolve the strong coupling and parton distributions in high-energy quantum chromodynamics (QCD).
Applied to nuclei, the RG shows how SRC physics is manifested differently at varying resolution scales. 
Here we will illustrate how the RG can bridge low- and high-resolution treatments of the same experiment, shedding light on the implications of SRC physics and on long-standing discrepancies between theory and experiment~\cite{Aumann:2020tcq}.

To avoid misunderstanding, we must from the beginning distinguish between experimental resolution and RG resolution as manifested in nuclear applications.
The experimental resolution is set by the momentum of the probe, with the resolving power limited to distances of order the corresponding wavelength.
The RG resolution is also determined by a limiting wavelength, which is set not by external kinematics but by the choice of decoupling scale in the RG-evolved Hamiltonian.
This scale dictates the minimum wavelength or maximum momentum available for the wave functions of low-energy states (and the nuclear ground states in particular).
A high-RG-resolution description has a ``hard'' Hamiltonian that mixes high-momentum components into low-energy states, i.e., SRCs. 
A low-RG-resolution description has a ``soft'' Hamiltonian for which the ground-state wave function is closer to the mean-field limit with the largest momenta not far from the Fermi momentum $\kF$.
We emphasize that either of these descriptions (or a continuum of intermediate RG resolutions) can be applied to the same experiment.

\begin{figure}[tbh]
    \centering
    (a)\includegraphics[width=0.44\columnwidth]{low_rg_resolution_cartoon_1.pdf}~~%
    (b)\includegraphics[width=0.44\columnwidth]{high_rg_resolution_cartoon_1.pdf}
    \caption{Cartoon snapshots of a nucleus at (a) low-RG  and (b) high-RG resolutions. 
    The back-to-back nucleons at high-RG resolution are an SRC pair with small center-of-mass momentum.
    }
    \label{fig:cartoon_nuclei}
\end{figure}

\begin{figure}[tbh]
    \centering
    \includegraphics[width=0.9\columnwidth]{Cartoon_momentum_distribution.pdf}
    \caption{Cartoon of a nuclear single-particle momentum distribution at high RG resolution.
    The region below $\kF$ is a Fermi sea of nucleons.
    Above $\kF$ the distribution is dominated by SRC pairs, with center-of-mass momenta of order $\kF$.
    At low RG resolution, the upper branch is greatly suppressed.
    }
    \label{fig:cartoon_mom_dist}
\end{figure}

For visualization, cartoon pictures of these resolutions are shown in Figs.~\ref{fig:cartoon_nuclei} and \ref{fig:cartoon_mom_dist}.
Although only qualitative, such pictures give intuition for interpreting experiments.
In Fig.~\ref{fig:cartoon_nuclei} we visualize configurations that might be sampled at different RG resolutions. Only at high-RG resolution do we find a high-momentum pair.
In practice we associate the high-resolution picture with local phenomenological Hamiltonians, in particular the Argonne V18 (AV18) potential~\cite{Wiringa:1994wb} and its associated three-body forces, which have been featured in most of the recent analyses of SRC experiments. 
AV18 describes nucleon-nucleon observables within experimental accuracy up to the inelastic threshold and the elastic part of the cross section reasonably well up to much higher energies.
The AV18 momentum distributions in nuclei extend well above 4\,fm$^{-1}$ or 800\,MeV (in units where $\hbar = c = 1$), as caricatured in Fig.~\ref{fig:cartoon_mom_dist} (see also the figures in Sec.~\ref{sec:low_resolution}).
For concreteness we associate the low-resolution picture with the shell model (configuration interaction), either in its phenomenological form or derived from ab initio methods such as coupled cluster or the in-medium similarity RG.
In this picture, nucleon momentum distributions die off rapidly above $\kF$.

The smoking gun experiments for SRCs in the high-RG-resolution picture come in two varieties: inclusive reactions with carefully chosen kinematics~\cite{Egiyan:2003vg,Egiyan:2005hs,Fomin:2011ng,Ye:2017mvo,Nguyen:2020mgo} and experiments featuring the knock-out and detection of two high-momentum nucleons~\cite{Hen:2014nza,Higinbotham:2014xna,Korover:2014dma,Duer:2018sxh,Duer:2018sby,Schmookler:2019nvf,Schmidt:2020kcl}.
These experiments manifest key features of high-resolution SRC phenomenology~\cite{Hen:2016kwk}:
\begin{enumerate}
  \item \textbf{Universal high-momentum nucleon distributions.}
  Ratios of inclusive cross sections at selective kinematics (high $Q^2$ and $x \gtrsim 1.4$--1.5) for different nuclei show plateaus, implying that momentum distributions at high momenta have the same shape for all nuclei.
  The relative height of the plateau defines the SRC scaling factor $a_2$ and is related to the relative probability of finding a two-nucleon SRC in the nuclei (e.g., see Ref.~\cite{Ryckebusch:2019oya}).

   \item \textbf{Kinematics of the knocked-out nucleons.}
   SRC pairs are in S-waves with relative momentum larger than $\kF$ and total momentum of order or less than $\kF$.
   So when one of the paired nucleons has a direct one-body interaction (e.g., it absorbs a virtual photon), the other flies out almost back-to-back with respect to the original momentum in the lab frame.
   The experimental analysis implies that roughly 10--20\% of nucleons in the nucleus are members of an SRC pair.

  \item \textbf{Ratio of $np$ to $pp$ knocked-out pairs for intermediate relative momentum (300--500 MeV).}
  One might expect that the ratio of neutron-proton ($np$) to proton-proton ($pp$) pairs knocked out would be given by basic counting~\cite{Colle:2015ena}.
  In fact the ratio for intermediate momenta shows a strong dominance of $np$ pairs over $pp$ or $nn$ pairs.
  This is interpreted as resulting from the dominance of the nucleon-nucleon (NN) tensor interaction in this momentum regime, which generates \tripletS\ ($np$ only) but not \singletS\ SRC pairs.

   \item \textbf{Ratio of knock-out cross sections from neutron-rich nuclei compared to $N=Z$ nuclei.}
   The ratios imply that the high-momentum fraction of protons is greater for $N>Z$ than for $N=Z$.
   The SRC interpretation is that excess neutrons correlate with core protons, so that protons ``speed-up'' in neutron-rich nuclei.
   In contrast, the high-momentum fraction of neutrons remains constant.

  \item \textbf{Transition from $np$ dominance of SRC pairs to ratios expected from scalar counting.}
  As the momentum of the knocked-out pairs increases, the dominance of the tensor part of the NN interaction gives way to probing the repulsive core, which affects all pairs equally.
  Therefore the ratio of $np$ to $pp$ pairs relaxes toward the scalar limit.

\end{enumerate}
These effects are all consistent with two phenomenological approaches. 
The Generalized Contact Formalism (GCF) model uses a factorization ansatz for the nuclear many-body wavefunction applied to these high-momentum transfer processes~\cite{Weiss:2015mba,Weiss:2016obx,Weiss:2018tbu,Weiss:2021zyb}. 
The low-order correlation operator approximation (LCA)~\cite{Vanhalst:2014cqa,Ryckebusch:2018rct,Ryckebusch:2019oya} is used to compute how SRCs affect nuclear momentum distributions; it does so by shifting the SRC physics from the wave function to a correlation operator, which is in turn parametrized
(the LCA will be discussed further in Sec.~\ref{sec:low_resolution}).

The GCF embodies the pictures in Fig.~\ref{fig:cartoon_nuclei}(b) and Fig.~\ref{fig:cartoon_mom_dist}, with the nuclear wavefunction relevant for SRC physics events represented as a product of a short-distance piece that multiplies a mean-field piece.
When applied to the distribution of pair momenta in coordinate and momentum space (meaning the probability to find two nucleons within a distance $r$ or having a relative momentum $q$), these quantities take the factorized form:
%
\begin{align}
     \rho^A_{{\rm\scriptscriptstyle GCF},\alpha}(r)  &= C_{A}^{NN,\alpha} |\phi^\alpha_{NN}(r)|^2 \;,
     \label{eq:GCF_coordinate}
    \\
    n^A_{{\rm\scriptscriptstyle GCF},\alpha}(q) &= C_{A}^{NN,\alpha} |\widetilde \phi^\alpha_{NN}(q)|^2
    \;. \label{eq:GCF_momentum}
\end{align}
%
Here $A$ is the nucleon number (protons plus neutrons) and $\alpha$ is a spin index.
The common coefficient is called a ``contact'' in analogy to the quantity defined in cold atom physics.
The two-body functions are extracted from the short-distance (high-momentum) dependence of the zero-energy solutions to the Sch\"odinger equation for a given NN interaction.%
\footnote{It would be misleading to call them wave functions, as pointed out originally in Ref.~\cite{Brueckner:1955zzd}.}

There is by now a substantial literature on applying the GCF phenomenology to SRC experiments~\cite{Weiss:2015mba,Weiss:2016obx,Weiss:2018tbu,Cruz-Torres:2019fum,Weiss:2021zyb,Pybus:2020itv,Schmidt:2020kcl}; we summarize only the major features here.
%More generally we will take the position that demonstrating the emergence of the GCF ansatz will mean that all of its successes will carry over.
The $A$-independence of the $\phi$ functions immediately implies that both the short-distance and high-momentum dependence of the pair distributions in different nuclei will be universal.
This suggests that taking ratios will divide out model dependence, giving support to the early focus on cross section ratios of various sorts in experimental analyses (e.g., two-nucleon knock-out to integrated single-nucleon knock-out).
Ratios of contacts are scale and scheme independent, as validated by microscopic ab initio calculations using both hard and soft (although not fully soft) interactions.
Three-body effects are implicitly treated as negligible.

The success of the SRC pair interpretations and the GCF might seem to be conclusive evidence that the high-RG-resolution picture is the only correct one.
But in fact these observations can be explained as well by a very different picture, in which the Hamiltonian is at low-RG resolution and therefore soft, while the interaction of a virtual photon probe is not with a single nucleon that is part of an SRC pair but with two nucleons in the Fermi sea (i.e., a two-body current).
We claim that all of the same observables are reproduced in this alternative picture, with simpler calculations.
This might seem to be a nuclear Rashomon effect~\cite{Rashomon:2016}, in which different observers give contradictory interpretations of the same event.
The RG shows how these pictures can both describe the phenomena and how to continuously transform from one to the other.
We note that these contrasting pictures have been discussed in the nuclear RG literature for at least a decade~\cite{Anderson:2010aq,Bogner:2012zm,Furnstahl:2013dsa,Tropiano:2020zwb}, but this work has not made a substantial impact or when cited has often been misunderstood.
We hope the presentation here will prove to be more accessible.

In the remainder of this paper we flesh out the story, striving to provide intuitive explanations of how it plays out.
In Sec.~\ref{sec:historical} we give a selected history of the two alternative pictures of nuclei and the experiments that seemed to require SRCs in nuclei.
This takes us up to the present where the conflict persists; we reconcile the pictures in Sec.~\ref{sec:reconciliation} by means of the RG.
We provide low-resolution explanations of the SRC experiments, some directly and some by showing how the GCF phenomenology emerges from an RG treatment and the operator product expansion.
A basic second-quantized treatment that enables a systematic many-body treatment of the unitary RG approach, along with representative calculations supporting the Sec.~\ref{sec:reconciliation} explanations, is presented in Sec.~\ref{sec:low_resolution}.
Section~\ref{sec:implications} provides a selection of takeaways in the form of questions and answers, and some implications for other experiments where SRC physics may play a role.
Section~\ref{sec:summary} is a brief summary and guide to future work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Historical Antecedents} \label{sec:historical}

Since the 1950's, two apparently contradictory pictures of nuclear structure have been developed and successfully applied~\cite{preston1975structure}.
The first stems from the shell model of Goeppert Mayer and Jensen, originally a description of independent particles moving in a mean field.
Refinements from that era include the collective model of Bohr and Mottelson, which showed that the
vibrational and rotational excitations of nuclei can be described in terms of the time evolution of a self-consistent mean field.
This provided a unified description of single-particle and collective degrees of freedom in nuclei.
The key characteristic for our discussion is that the momentum distribution did not include high-momentum nucleons (that is, with momenta well above $\kF$), as depicted in Fig.~\ref{fig:cartoon_nuclei}(a).

In Ref.~\cite{Brueckner:1955zzd}, Brueckner et al.\ considered the possibility of nonlinear phenomena altering the strong short-range interaction evident in free space: ``\ldots the success of the shell model has often been assumed to indicate that the two-body forces in nuclear matter are in fact much weaker and long-ranged and can lead in an excellent approximation to a uniform Hartree field acting on the nucleons.''
They go on to soundly reject this conjecture by considering five high-energy reactions and concluding that the measured cross sections can only result from a nucleon momentum distribution with a significant tail: ``This momentum distribution differs substantially from that for the shell model of the nucleus and thus provides strong evidence for correlation in the nuclear ground-state wave function.''
This is the alternative picture in Figs.~\ref{fig:cartoon_nuclei}(b) and \ref{fig:cartoon_mom_dist}, which features in particular a component of the nuclear wave function consisting of \emph{pairs} of nucleons with large relative momentum but a center-of-mass momentum of order the Fermi momentum.
Brueckner et al.\ explained this picture as arising from the strong short-range repulsion in the nucleon-nucleon (NN) interaction, which was the accepted explanation for the NN S-wave phase shifts turning negative at high energies.
Thus the SRC was born.

A key takeaway from Ref.~\cite{Brueckner:1955zzd} is that SRCs were argued for as essential wavefunction features because there was \emph{no other way} to explain the cross section: 
``Consequently it follows that the usual assumptions of the shell-model theory of the nucleus, that the particles move independently in a uniform potential, cannot be other than very approximately correct.''
Each example was analyzed in the Born approximation, which gave a transparent interpretation.
For example, deuteron pickup: ejection by fast neutrons (of order 100\,MeV) of fast deuterons by nuclei.
In the picture of Fig.~\ref{fig:cartoon_nuclei}(a), the fast incident neutron would have too-small matrix elements with the mean-field protons to enable the observed deuterons to form; this required the picture of Fig.~\ref{fig:cartoon_nuclei}(b).
At this level of approximation, a momentum distribution with a tail like in Fig.~\ref{fig:cartoon_mom_dist} could be fit.

However, this clear picture was subsequently muddied by consideration of final state (and initial state) interactions (e.g., see Ref.~\cite{PhysRev.114.786}). 
The clean extraction of a momentum distribution was no longer clean.
Nevertheless, the picture associated with a hard Hamiltonian persisted and Brueckner led the way in developing methods to handle such interactions and also explain how independent-particle behavior could arise.
This proved to be a difficult program to carry out with precision using the expansion and resummation techniques of Brueckner theory.
Instead, the most successful demonstration that hard Hamiltonians (and the Argonne potential in particular) led to quantitative predictions of the low-lying spectra of light nuclei was made using quantum Monte Carlo methods~\cite{Pieper:2001mp,Carlson:2014vla}.
This might have seemed to seal the deal on which picture was correct.
Yet in the meantime, ``phenomenological'' approaches such as the shell model and nuclear energy density functionals  were successful in describing a wide range of data using soft interactions~\cite{preston1975structure,Ring:2005}.

An experimental advance that promised to shed light on nuclear momentum distributions was the development of electron scattering facilities that could detect knocked-out protons in coincidence with the scattered electrons.
At NIKHEF and other electron scattering facilities, these $(e,e'p)$ experiments were used to probe occupied shell-model orbitals and map out their momentum distributions~\cite{Dieperink:1990uk,Kelly:1996hd}.
The extracted shapes were consistent with orbitals having the appropriate separation energy and radius, but the overall normalization was significantly lower than predicted by an independent-particle model.
In the high-resolution picture, this was explained by the depletion of orbitals by both short-range and long-range correlations, of order 15--20\% for each.
Once again, however, this potentially clean resolution was spoiled by final-state interactions (despite efforts to use parallel or anti-parallel kinematics to suppress other reaction mechanisms)~\cite{Bianconi:1995mz}.
The picture was further muddied by purely theoretical considerations in Ref.~\cite{Furnstahl:2001xq}, which showed that field redefinitions or unitary transformations imply the picture of high-momentum SRC pairs is not unique.
This would turn out to be a foreshadowing of the RG reconciliation of hard and soft pictures.

With subsequent experimental and theoretical advances, the modern nuclear Rashomon effect grew more acute from both sides.
The problem of cleanly verifying the picture in Fig.~\ref{fig:cartoon_nuclei}(b) was apparently solved by experiments first at Brookhaven National Laboratory (BNL) and then more extensively at Jefferson Laboratory (JLab) that knocked out and detected \emph{both} members of SRC pairs (plus inclusive experiments with specially chosen kinematics).
By restricting to events with the appropriate kinematics in the final states, a series of experiments has established the key features listed in Sec.~\ref{sec:introduction}~\cite{Hen:2016kwk}.
At the same time, a picture closer to Fig.~\ref{fig:cartoon_nuclei}(a) (or at least with reduced high-momentum SRCs) has been behind explosive progress in ab initio (microscopic) calculations of nuclei, which have pushed well beyond where calculations with hard potentials have been computationally feasible~\cite{Hergert:2020bxy}.
To reconcile these pictures, we need to modify the hard potential into a soft one, while at the same time preserving the results from high-momentum-transfer experiments.
This can be accomplished by \emph{unitary} renormalization group evolution.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Reconciliation by the renormalization group} \label{sec:reconciliation}

\subsection{Applying a unitary RG}

The renormalization group techniques developed by Wilson in the late 1960s and early 1970s formalized the ideas of block spinning introduced by Kadanoff, through which shorter distance scales in a system are averaged over, leaving only contributions from successively longer distance scales~\cite{PhysicsPhysiqueFizika.2.263,Wilson:1971bg,Wilson:1974mb}.
By eliminating these degrees of freedom (dofs), the underlying universal behavior was revealed, which was directly applied to explain critical phenomena (second-order phase transitions).
The other major class of RG applications from this period aimed to improve perturbation theory.
This use of RG dates from Gell-Mann and Low in 1954~\cite{GellMann:1954fq} and matured in applications to high-energy scattering in QCD~\cite{Gross:1973id,Politzer:1973fx}.
The basic idea is that a mismatch of external energy scales and those internal to loop integrals (i.e., sums over states) can generate large logarithms that modify the naive convergence of perturbation theory.
Running the RG can shift strength between couplings and loop integrals to minimize the impact of the logarithms~\cite{Weinberg:1981qq}.
The nuclear applications of the RG inherit features of both types of RG applications~\cite{Bogner:2006vp}.

In the early 1990's, independent efforts by Glazek and Wilson, who sought a Hamiltonian formalism for quantum chromodynamics (QCD)~\cite{Glazek:1993rc,Glazek:1994qc}, and  Wegner, who worked on condensed matter problems~\cite{Wegner:1994ab}, led to unitary RG evolution approaches that drove many-particle Hamiltonians to be increasingly energy diagonal.
This alleviates problems with small energy denominators.
The similarity RG (or SRG), particularly in the unitary flow equation form proposed by Wegner~\cite{Wegner:2001ab}, subsequently proved to be well suited for low-energy nuclear physics.
SRG applications built on a long history of unitary transformation methods in nuclear physics and especially the earlier introduction of RG for nuclear Hamiltonians by Bogner and Schwenk~\cite{Bogner:2001gq,Bogner:2001jn,Bogner:2003wn}.
The SRG is technically simpler (e.g., for evolving 3-body forces) and highly versatile; it can be applied in free space for interactions and operators~\cite{Tropiano:2020zwb}, and in the nuclear medium as a many-body solution method~\cite{Bogner:2009bt,Furnstahl:2013oba,Hergert:2020bxy}.

\subsection{Schematic look at factorized matrix elements}

\begin{figure*}[ptb]
     \centering
    (a)\includegraphics[width=0.25\textwidth]{schematic_SRC_1.png}
    \quad
    (b)\!\!\!\!\!\!\!\!\!\raisebox{23pt}{{$\xrightarrow{\quad\includegraphics[width=0.15\textwidth]{schematic_SRC_UdagU.png}\quad}$}}
    \quad
    (c)\includegraphics[width=0.44\textwidth]{schematic_SRC_2.png}

    \vspace{.2in}
    \quad
    (d)\!\!\!\!\!\raisebox{18pt}{{$\xrightarrow{\quad \includegraphics[width=0.18\textwidth]{schematic_SRC_Upsi.png}\quad}$}}
    \quad
    (e)\includegraphics[width=0.34\textwidth]{schematic_SRC_3.png}

    \vspace{.2in}
    \quad
    (f)\!\!\!\!\!\raisebox{18pt}{{$\xrightarrow[k < \lambda;\ k' \gg \lambda]{\quad\includegraphics[width=0.14\textwidth]{schematic_SRC_Ufact.png}\quad}$}}
    \quad
    (g)\includegraphics[width=0.35\textwidth]{schematic_SRC_4.png}

    \vspace{.2in}
    \quad\raisebox{32pt}{$\xrightarrow{\hspace*{.3in}}$}\quad
    (h)\includegraphics[width=0.37\textwidth]{schematic_SRC_5.png}
    \quad\raisebox{32pt}{$\xrightarrow{\hspace*{.3in}}$}\quad
    (i)\includegraphics[width=0.19\textwidth]{schematic_SRC_6.png}

    \caption{Schematics of what happens with high-momentum operators and low resolution states. (See the text for details.)
    }
    \label{fig:schematic_SRC_physics}

\end{figure*}

The technical aspects of the SRG are well documented in the literature~\cite{Bogner:2009bt,Furnstahl:2013oba,Roth:2013fqa,Binder:2013xaa,Hergert:2016iju}.
For our purposes we do not need to know how the unitary transformations are generated, but only their actions and characteristics.
Figure~\ref{fig:schematic_SRC_physics} provides a schematic guide to how a ratio of matrix elements of high-momentum operators is transformed from high RG resolution to low RG resolution.
For simplicity we take ground-state matrix elements and a ratio between nucleus with $A$ nucleons to the deuteron.
This setup is directly related to the experiments for inclusive cross section ratios~\cite{Egiyan:2003vg,Egiyan:2005hs,Fomin:2011ng,Ye:2017mvo,Nguyen:2020mgo}, but we can interpret the details more generally.
In Sec.~\ref{sec:low_resolution} we provide a second-quantized formulation that validates the developments sketched here.

The SRG parameter $\lambda$ is taken to be of order $\kF$ or slightly higher; it provides a dividing scale between mean-field and high-momentum physics as in Fig.~\ref{fig:cartoon_mom_dist} and it serves as the resolution scale (because only momenta less than $\lambda$ are included in the low-energy wave functions).
Details of the subplots in Fig.~\ref{fig:schematic_SRC_physics}:
\begin{enumerate}
    \renewcommand{\theenumi}{\alph{enumi}}

    \item The ground-state bra and ket are coded blue to indicate they are calculated using an unevolved hard interaction (e.g., AV18 plus three-body for definiteness). 
    There are both high-momentum and low-momentum contributions to $|\psi_A\rangle$ and $|\psi_d\rangle$.
    The operator is also blue, which signifies there are \emph{only} contributions from high momenta $q > \lambda$.
    For example, it could be a pair or single-nucleon momentum distribution evaluated at $q$.

    \item The unitary transformation at $\lambda$ is denoted $U_\lambda$. 
    Here we write it as a momentum matrix. 
    The combination $U_\lambda^\dagger U_\lambda$ is the identity matrix, so it can be inserted anywhere in our expression.

    \item We insert $U_\lambda^\dagger U_\lambda$ between the operator and wave function vectors with the plan of acting with the transformations on each.
    The ratio of matrix elements is unchanged.

    \item We designate the soft evolved ground-state matrix element with $\lambda$ and code it red. 
    Acting with $U_\lambda$ on the original wave function yields the same result as evolving the Hamiltonian and then diagonalizing to extract the ground state.

    \item It is evident here that to maintain the same matrix element that the operator must also be evolved by $U_\lambda O U_\lambda^\dagger$.

    \item When the unitary transformation is sandwiched between a part that is purely low momentum ($k < \lambda$) and a part that is purely high momentum ($q > \lambda$), then it approximately factorizes into disjoint pieces.
    This factorization is derived in Refs.~\cite{Anderson:2010aq} and \cite{Bogner:2012zm}. 
    The low-momentum part $F^{\rm lo}(k)$ is only weakly dependent on momentum.
    The factorization approximation is typically good at the 10--15\% level and corrections are calculable. 
    The leading factorization explains the dominant behavior but if greater precision is desired one can always simply use the full unitary transformation.

    \item Upon substitution of the factorized unitary transformation, we see that the numerator and denominator have individually separated into a purely high-momentum part that carries the full dependence on the momentum of the operator but is state independent, and a purely low-momentum part that is independent of the operator but depends on the nucleus.

    \item For convenience we have simply rearranged the factorized parts of the matrix elements.
    This is the leading term in an operator product expansion.
    If we focus on the red (high momentum) parts, we immediately obtain the universal (i.e., state-independent) behavior of \emph{any} high-momentum operator. Note that this applies to low-lying excited states as well.
    With the choice of a momentum distribution this is also the embodiment of 
    the GCF in Eq.~\eqref{eq:GCF_momentum} (or Eq.~\eqref{eq:GCF_coordinate} if we work in coordinate space instead).

    \item
    For the case of the same operator in numerator and denominator, they cancel, leaving a purely low-momentum ratio that turns out to be scale and scheme independent (to leading order).
    This is the GCF contact ratio, which is the type of ratio that will dominate the ratio of inclusive cross sections.
    Note that it is a ``mean-field'' quantity, i.e., it only depends on the soft ground-state wave function.
\end{enumerate}
%
Thus the GCF physics naturally emerges from a low-resolution perspective but in a form that is systematically improvable and more easily generalized.

\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.7\columnwidth]{figures_low_res/srg_transformation_ratios_k0_0p1_lamb_1p35_kvnns_6_222_kmax_15p0.png}
  \caption{Ratio of $|U(k_0,q)U^\dagger(q,k_0)|$ with fixed $k_0 = 0.1\,\fmi$ for the coupled $\tripletS$ to $\singletS$ channels.
  Results are for the AV18~\cite{Wiringa:1994wb} and Gezerlis \NNLO\ (1.0\,fm)~\cite{Gezerlis:2014zia} potentials.}
  \label{fig:ratio_1p35_kvnn_6_222}
\end{figure}

Returning to (e) and (g) for the specific case of the pair distribution at high momentum, we see that it is sufficient to look at the unitary transformation of the high-resolution operator in a two- or three-body space, independent of any nucleus or state.
The two-body unitary transformation can be expanded in the NN channels without reference to a particular state (see Sec.~\ref{sec:low_resolution} for details).
In Fig.~\ref{fig:ratio_1p35_kvnn_6_222} the ratio of
$|U(k_0,q)U^\dagger(q,k_0)|$ for the coupled $\tripletS$ to $\singletS$ channels  is plotted as a function of $q$ with fixed $k_0 = 0.1\,\fmi$.
This ratio directly relates to the fraction of knocked-out pairs that are $np$ versus $pp$ or $nn$.
We see the dominance of $\tripletS$ to $\singletS$ in the region around 2\,\fmi (400\,MeV), where the tensor force is strong and the $\singletS$ potential has a node, decaying to a combinatoric fraction at high momentum.
The result is insensitive to details as the dependence on $k_0$ is very weak for $q > \lambda$.
We also see that similar results are obtained for the local chiral EFT potential from Gezerlis et al.~\cite{Gezerlis:2014zia} (this is true for any other chiral potential~\cite{Tropiano:2021prep}).

\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.9\columnwidth]{AV18_percentages_deuteron_band.png}
  \caption{Percentage contributions from each channel to the matrix element
  of the momentum distribution in the deuteron with $q=2$, $3$, and $4\,\fmi$ for AV18. We compare unevolved and SRG-evolved (both wave function and operator, so the net matrix element is unchanged) results where $\lambda=1.35\,\fmi$.}
  \label{fig:barcharts_AV18}
\end{figure}

\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.9\columnwidth]{Gezerlis_percentages_deuteron_band.png}
  \caption{Same as Fig.~\ref{fig:barcharts_AV18} but for the Gezerlis \NNLO\ potential.}
  \label{fig:barcharts_Gezerlis}
\end{figure}

One might have expected that the dominance of the tensor means that the operator will be sensitive to $^3\mbox{D}_1$ admixtures in the ground state even when evolved.
This is not the case, as illustrated in Figs.~\ref{fig:barcharts_AV18} and \ref{fig:barcharts_Gezerlis}. 
The high-resolution results ($\lambda = \infty$) do come dominantly from the $\tripletD$--$\tripletD$ part for momenta $q$ where the tensor force dominates while it is more evenly split with $\tripletS$--$\tripletS$ (in a scheme/scale dependent way) at higher momenta.
But the low-resolution results ($\lambda = 1.35\,\fmi$ here) are always heavily dominated by the $\tripletS$--$\tripletS$ part.
This implies that simple ground-state wave functions with local density approximations (LDAs) will work quite well at low RG resolution, as illustrated in the next section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Calculating at low RG resolution} \label{sec:low_resolution}

In this section we use second quantization to more precisely characterize the SRC physics and show how simplified calculations (e.g., using LDAs) are meaningful.
The details of how factorization works in second-quantized form have already been worked out in Ref.~\cite{Bogner:2012zm}, which we build on for the current discussion.
The results presented here are only a sampling of what is possible, using the crudest approximation.
Nevertheless, they suffice to show that low-RG resolution calculations can reproduce all the features of SRG phenomenology listed in Sec.~\ref{sec:introduction}.
In future work we will explore more accurate approximations and calibrate the theoretical uncertainties~\cite{Tropiano:2021prep}.

\subsection{Second-quantized unitary transformations}
\label{subsec:second-quantization}

The SRG unitary transformation at flow parameter $\lambda$ takes the schematic second-quantized form:
%
\begin{align} 
    \Uhat_\lambda = \Ihat 
     &+ \sum  \delta U^{(2)}_\lambda \,
    \akdag\akdag aa
    \notag\\ 
    \null &+ \sum \delta U^{(3)}_\lambda\akdag\akdag\akdag aaa
     + [\mbox{4-body}] + \cdots
    \;,  \label{eq:Uschematic} 
\end{align}
%
where we have suppressed the single-particle indices and combinatoric factors.
There is no one-body term, which would have only a sum over $\akdag a$ operators.
The leading approximations illustrated in Fig.~\ref{fig:schematic_SRC_physics} can be formulated in second-quantization by always consistently truncating the operator products such as $\Uhatlam \widehat O \Uhatlamdag$ at the (vacuum) two-body level. 
In practice this is cleanly carried out by applying Wick's theorem in operator form.

The two-body term in \eqref{eq:Uschematic} in a plane-wave single-particle basis is
%
\begin{align} 
    \frac{1}{4} \sum_{\kvec,\kvec',\Kvec} \!  \delUtilde^{(2)}_\lambda(\kvec,\kvec') \,
    \akdag_{\frac{1}{2}\Kvec + \kvec} \akdag_{\frac{1}{2}\Kvec - \kvec} 
    \ak_{\frac{1}{2}\Kvec - \kvec'} \ak_{\frac{1}{2}\Kvec + \kvec'} 
    ,  \label{eq:Uform} 
\end{align}
%
where $\kvec$ and $\kvec'$ are relative momenta in the two-body subspace, $\Kvec$ is the total momentum, and $\delUtilde^{(2)}_\lambda$ is an anti-symmetrized matrix element (i.e., $\delUtilde^{(2)}_\lambda = \delta U_\lambda^{(2)} (1 + P_{12})$, where $P_{12}$ exchanges particles 1 and 2). 
For notational compactness we suppress the spin and isospin indices on $\delUtilde^{(2)}_\lambda$;
the latter dependence will be explicit later when $\delUtilde^{(2)}_\lambda$ is decomposed into the usual NN partial-wave channels.
The form in Eq.~\eqref{eq:Uform} follows from the structure of the SRG flow equation and the properties of the two-nucleon Hamiltonian, which are inherited by $\delUtilde^{(2)}_\lambda$.
Particular features of relevance in the present context are that  the first-quantized function $\delUtilde^{(2)}_\lambda$ is completely determined in the two-body system and depends on $\kvec$ and $\kvec'$ but not $\Kvec$ from Galilean invariance, three-body contributions are subleading (more on this below), and $\delUtilde^{(2)}_\lambda(\kvec,\kvec')$ factorizes as in Fig.~\ref{fig:schematic_SRC_physics}(f) for $|\kvec| < \lambda$ and $|\kvec'|\gg \lambda$.

A simple example of how truncating at the two-body level plays out is the verification of the  unitary condition in Fig.~\ref{fig:schematic_SRC_physics}(b).
We start by multiplying Eq.~\eqref{eq:Uschematic} and its hermitian conjugate and note that even maximally contracted terms involving three-body or higher terms from $\Uhat^\dagger$ or $\Uhat$ will be three-body or more, and therefore are omitted. 
Only the fully contracted part of the $\akdag\akdag a  a\akdag\akdag a a$ term from the $\delta U$ pieces will have the leading two-body form, so the net result for the leading approximation in the plane-wave basis as in \eqref{eq:Uform} is
%
\begin{align}
    \Uhatlamdag \Uhatlam &= \Ihat + \frac{1}{4}\sum_{\kvec,\kvec',\Kvec}
    [\delUtilde^{(2)\dagger}_\lambda(\kvec,\kvec') + \delUtilde^{(2)}_\lambda(\kvec,\kvec')
    \notag \\
    & \qquad\qquad \null + \frac{1}{2}\sum_{\kvec''} \delUtilde^{(2)\dagger}_\lambda(\kvec,\kvec'')\delUtilde^{(2)}_\lambda(\kvec'',\kvec') ]
    \notag \\
    & \qquad\qquad \null \times
     \akdag_{\frac{1}{2}\Kvec + \kvec} \akdag_{\frac{1}{2}\Kvec - \kvec} 
    \ak_{\frac{1}{2}\Kvec - \kvec'} \ak_{\frac{1}{2}\Kvec + \kvec'} 
    \notag \\
    &= \Ihat ,
    \label{eq:UdaggerU}
\end{align}
%
where the coefficient function in square brackets is identically zero from the unitary condition applied to (unsymmetrized) $U^{(2)}(\kvec,\kvec') = \delta_{\kvec,\kvec'} + \delta U^{(2)}(\kvec,\kvec')$.

To find the evolved form of other operators, we simply sandwich the second-quantized operator expansion between $\Uhatlam$ and $\Uhatlamdag$, apply Wick's theorem and truncate at the two-body level.
%
For example, the leading approximation for the evolved pair momentum distribution $\nhatlo^{\tau\tau'}(\qvec,\Qvec)$ for isospin projections $\tau$ and $\tau'$ takes the form
\begin{widetext}
%
\begin{align} \label{eq:pair_mom_dist_op}
     \nhatlo(\qvec,\Qvec) &=
    \Uhatlam\nhathi(\qvec,\Qvec)\Uhatlamdag \notag \\
    &\approx \nhathi(\qvec,\Qvec) 
    + \frac14\sum_{\kvec} \delUtilde^{(2)}_\lambda(\kvec,\qvec)
    \akdag_{\frac{1}{2}\Qvec + \kvec} \akdag_{\frac{1}{2}\Qvec - \kvec} 
    \ak_{\frac{1}{2}\Qvec - \qvec} \ak_{\frac{1}{2}\Qvec + \qvec}
    + \frac14\sum_{\kvec} \delUtilde^{(2)\dagger}_\lambda(\qvec,\kvec)
    \akdag_{\frac{1}{2}\Qvec + \qvec} \akdag_{\frac{1}{2}\Qvec - \qvec} 
    \ak_{\frac{1}{2}\Qvec - \kvec} \ak_{\frac{1}{2}\Qvec + \kvec} \notag \\
    & \quad \null + \frac18 \sum_{\kvec,\kvec'} \delUtilde^{(2)}_\lambda(\kvec,\qvec)\delUtilde^{(2)\dagger}_\lambda(\qvec,\kvec')
    \akdag_{\frac{1}{2}\Qvec + \kvec} \akdag_{\frac{1}{2}\Qvec - \kvec} 
    \ak_{\frac{1}{2}\Qvec - \kvec'} \ak_{\frac{1}{2}\Qvec + \kvec'},
\end{align}
\end{widetext}
%
where the unevolved ($\lambda = \infty$) pair momentum distribution is
%
\begin{equation} \label{eq:n_infinity}
    \nhathi(\qvec,\Qvec) = 
       \frac{1}{2}\sum_{\sg,\sg'} \akdag_{\frac{1}{2}\Qvec + \qvec} \akdag_{\frac{1}{2}\Qvec - \qvec} 
    \ak_{\frac{1}{2}\Qvec - \qvec} \ak_{\frac{1}{2}\Qvec + \qvec},
\end{equation}
%
and we have suppressed spin and isospin indices in \eqref{eq:pair_mom_dist_op} and \eqref{eq:n_infinity}.
If Eq.~\eqref{eq:pair_mom_dist_op} is summed over $\qvec$ at fixed $\Qvec$, a simple change of labels in the sums manifests that by consistently truncating to the two-body operators, the full normalization comes from the unevolved distribution, with the terms depending on $\delUtilde^{(2)}_\lambda$ canceling by the unitary condition, as in \eqref{eq:UdaggerU}. 
%

In practice we evaluate matrix elements of $\delUtilde^{(2)}_\lambda$ in the two-body space using antisymmetrized kets expanded in partial waves~\cite{Dickhoff:2005text}:
%
\begin{align}
    \label{eq:pw_ket}
   & \ket{\kvec_1 \sg1 \ta1 \, \kvec_2\sg2\ta2}  = 
    \frac{1}{\sqrt{2}} \sum_{S,M_S}\sum_{L,M_L}\sum_{J,M_J}\sum_{T,M_T}\!
    \braket{\sg1 \sg2}{S M_S} \notag \\
    & \qquad\quad \null\times \braket{\ta1 \ta2}{T M_T} 
    \sqrt{\frac{2}{\pi}}Y^*_{LM_L}(\khat) \braket{L M_L S M_S}{J M_J} \notag \\
    & \qquad\quad \null \times
    [1 - (-1)^{L+S+T}]\,
    |\Kvec k (LS) J M_J T M_T) ,
\end{align}
%
%
where 
%we have written two nucleons of momenta $\kvec_1$ and $\kvec_2$ in the usual center-of-mass variables 
$\kvec \equiv \half(\kvec_1 - \kvec_2)$, $\Kvec \equiv \kvec_1 + \kvec_2$,
and $\sigma$ and $\tau$ denote the spin and isospin projections, respectively.
The factor of $\sqrt{2/\pi}$ comes from the completeness relation in relative momentum space $1 = \frac{2}{\pi} \int_0^{\infty} dk k^2 \ketbra{k}{k}$.
Formulas are given in Appendix~\ref{sec:formulas} for the momentum distributions in the LDA that are used in Sec.~\ref{subsec:LDA}.

The decomposition in Eq.~\eqref{eq:pair_mom_dist_op} is exact for the deuteron. The contributions of the individual pieces are shown in Fig.~\ref{fig:deuteron_md_contributions} for the AV18 potential unevolved and evolved to $\lambda = 1.35\,\fmi$, which we take as a representative low-resolution RG scale for nuclear ground states.
The full momentum distribution at high-resolution is shown as a solid line, which is also equal to the sum of the low-resolution pieces.
The matrix element of the ``$\Ihat$'' piece from \eqref{eq:pair_mom_dist_op} (first term) has support only for low momenta; in heavier nuclei it will correspond to the mean-field region of Fig.~\ref{fig:cartoon_mom_dist}.
The terms linear in $\delUtilde$ are negative at low momentum, removing strength from this region.
(Note, the absolute value of $\delUtilde$ is shown in Fig.~\ref{fig:deuteron_md_contributions}.)
The $\delUtilde\delUtilde^{\dagger}$ piece is the sole contributor to the high-momentum region above 2\,\fmi.
The region where the ``$\Ihat$'' and linear $\delUtilde$ terms fall off while the $\delUtilde\delUtilde^{\dagger}$ term dominates is shifted to higher momenta with increasing values of $\lambda$~\cite{Tropiano:2021prep}.

When taking matrix elements of the $\delUtilde\delUtilde^{\dagger}$ term in a low-resolution wave function, $\Qvec,\kvec,\kvec'$ will all be soft, so for $|\qvec| > \kF$ the $\delUtilde$ functions will be in the factorization regime.
This will isolate the $\qvec$ dependence of the pair distribution as in Fig.~\ref{fig:schematic_SRC_physics}(h).
For the deuteron, only the \Striplet--\Dtriplet\,part of $\delUtilde$ will contribute.
%(and dominantly the \Striplet, as shown earlier).

\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\columnwidth]{figures_low_res/n_lambda_deuteron_decomposition_kvnn_6_lamb_1p35_kmax_15p0_curves_4.png}
    \caption{Contributions to the deuteron momentum distribution $n_\lambda^d(q)$ with AV18 and $\lambda=1.35$ \fmi\, from the expectation value of Eq.~\eqref{eq:pair_mom_dist_op} in the unevolved ($\lambda = \infty$, labeled ``High res.'') and evolved wave functions. The latter is split into three pieces, with the sum indistinguishable from the unevolved curve. The normalization  is $\frac{2}{\pi} \int_0^{\infty} dq\, q^2 n^d_{\lambda}(q)$ = 1.}
    \label{fig:deuteron_md_contributions}
\end{figure}

How accurate will the truncation to the two-body level be for $A>2$?
Calculations of bulk quantities such as energies and radii are sensitive to three-body contributions at low resolution, but their role is amplified by cancellations of the kinetic and potential energies.
The cluster hierarchy of the potential itself is maintained in the SRG evolution.
For high-momentum distributions, we expect that the two-body contribution will dominate.
This is supported by the work of Neff et al.~\cite{Neff:2015xda} on the pair distribution in the alpha particle, which showed some $\lambda$ dependence near $2\,\fmi$ in  the dominant $S=1,T=0$ spin-isospin channel when integrating over the center-of-mass momentum $\Qvec$ (with significant dependence in the other channels) but very little dependence at $\Qvec = 0$; in all cases there is little dependence above $3\,\fmi$.
In future work we will use the RG running (i.e., the $\lambda$ dependence) to test the truncation error in our calculations~\cite{Tropiano:2021prep}.
We emphasize that corrections from three-body operators are fully accessible within our approach and that good approximations to these contributions are possible.
Finally, we note that truncation at the two-body level has much in common with the leading term of the Brueckner expansion~\cite{Brueckner:1955zzd,Tropiano:2021prep}. This has implications for SRC physics at high density, e.g., in neutron stars, where three-body physics is essential for a quantitative description.

\begin{figure*}[tbh]
	\includegraphics[clip,width=0.85\textwidth]{figures_low_res/snmd_tails_with_AV18_multiplot_channels_1S0_3S1_kvnn_6_lamb_1p35_kmax_15p0.png}
    \caption{Proton momentum distributions for $^{12}$C, $^{16}$O, and $^{40}$Ca calculated in the LDA for $q>0.6\,\fmi$. Here we use AV18 to SRG-evolve the operator setting $\lambda=1.35$ \fmi, and divide each distribution by the proton number $Z$. The gray-shaded sections are where $q<\lambda$. Black dots correspond to AV18 quantum Monte Carlo calculations~\cite{Wiringa:single_distributions}.}
    \label{fig:proton_momentum_distributions}
\end{figure*}
%

%It is useful to have expressions for both the evolved Fock space creation and annihilation operators and the unitary transformation themselves.

\subsection{Local density approximation calculations}
  \label{subsec:LDA}

At low resolution there are various options for calculating SRC physics as manifested in the experiments described in Sec.~\ref{sec:introduction}.
By softening the Hamiltonian, the nuclear ground-state wave functions become less correlated, more amenable to many-body perturbation theory, and more universal in nature.
Furthermore, for operators evaluated at the highest momenta, the details of long-range correlations should become less important.
Indeed, the physics is focused on short distances, which suggests that an LDA should work well, particularly as the unitary transformations in the factorization region ($\delUtilde^{(2)}_\lambda(\kvec,\kvec')$ with $|\kvec| < \lambda$ and $|\kvec'|\gg \lambda$) are weakly dependent on the low momentum~\cite{Tropiano:2020zwb}.

We illustrate how to formulate an LDA by starting with the second-quantized version of the unevolved single-particle momentum distribution for isospin projection $\tau$ from coordinate-space integrals (cf.\ Ref.~\cite{Wiringa:2013ala}):
%
\begin{align} \label{eq:nk_from_dm}
    n^\tau(\qvec) &= \int d\rvec \int d\rvec' \,
     \mel{\Psi_A}{\psihat^\dagger_\tau(\rvec')\psihat^{\phantom{\dagger}}_\tau(\rvec)}{\Psi_A}
      e^{-i\qvec\cdot(\rvec - \rvec')}  \notag \\
     &= \int d\Rvec \int d\svec \,
     \rhoDM^\tau(\Rvec,\svec) e^{i\qvec\cdot\svec},
\end{align}
%
where $\Rvec = (\rvec + \rvec')/2$, $\svec = \rvec' - \rvec$,
and $\rhoDM^\tau(\Rvec,\svec)$ is the density matrix for the $A$-body nucleus.
We implement an LDA as the leading term in a density matrix expansion (DME)~\cite{Negele:1972zp}:
%
\begin{align} \label{eq:dme}
    \rhoDM^\tau(\Rvec,\svec) \approx \rho^\tau(R) \rhoSL(s \kF^\tau(R)) + \cdots
\end{align}
where the Slater function is $\rhoSL(z) \equiv \frac{3}{z}j_1(z)$, the local Fermi momentum is $\kF^\tau(R) = (3\pi^2\rho^\tau(R))^{1/3}$ with $\rho^\tau$ the proton or neutron number density normalized to $Z$ or $N$, and we have applied angle averaging.
Negele and Vautherin showed this was a good approximation for not-too-large values of $s$~\cite{Negele:1972zp}.

If we substitute \eqref{eq:dme} into \eqref{eq:nk_from_dm} and integrate over $s$, we find
%
\begin{align}
    n^\tau(q) \approx 2 \int d\Rvec\, \theta(\kF^\tau(R) - q),
\end{align}
%
with the factor of 2 from the spin sum.
This is a poor approximation at very low $q$ because of the contribution to the integral from large $s$,
but its generalizations to include the SRG unitary transformations provide a quantitative
reproduction of momentum distributions at high momenta.  
All of the second-quantized terms with $\delUtilde$ will be of the form $a^\dagger a^\dagger a a$. 
These have the same structure as a Hartree-Fock energy for a non-local potential, to which we can apply the corresponding DME from Refs.~\cite{Negele:1972zp,Bogner:2008kj}.
This approximation has a single spatial integration with two $\theta$ functions featuring the local Fermi momenta.
(The explicit formulas for the low-resolution LDA momentum distributions are given in the appendix.)

We demonstrate the LDA for proton momentum distributions using the AV18 potential in Fig.~\ref{fig:proton_momentum_distributions}, for which we can compare to quantum Monte Carlo calculations~\cite{Wiringa:2013ala,Lonardoni:2017egu,Wiringa:single_distributions}.
We use proton and neutron densities generated from the SLy4 Skyrme interaction using the HFBRAD code~\cite{Bennaceur:2005mx}.
We expect the approximations to be valid at least for momenta above the gray-shaded regions and indeed the agreement is quite reasonable, particularly at the highest momenta.
(We exclude the predictions below $q = 0.6\,\fmi$ because of the poor approximation; better treatments will be presented in Ref.~\cite{Tropiano:2021prep}.)
It is evident that the high momentum tails are very similar across the nuclei; this is the manifestation of the universal behavior of these distributions.
From Table~\ref{tab:partial_wave_contributions} we see evidence that the s-waves dominate the contributions to these momentum distributions.

\begin{table}[htb]
	\caption{Percentage contributions from s-waves and selected p-waves to proton momentum distributions for $q>2\,\fmi$. We show $N_X/N$ with $N \sim \int_2^{\infty} dq\, q^2 n_{\lambda}^A(q)$, where $n_{\lambda}^A(q)$ is the distribution for nucleus $A$ with evolved operator at $\lambda = 1.35\,\fmi$ and $X$ denotes using only one partial wave.}
	\label{tab:partial_wave_contributions}
	\begin{ruledtabular}
		\begin{tabular}{c|ccccc}
		   Nucleus & $^{1}$S$_0$ [\%] & $^{3}$S$_1$ [\%] & $^{3}$P$_0$ [\%] & $^{1}$P$_1$ [\%] & $^{3}$P$_1$ [\%]
		   \mystrut\\
			\colrule
      			$^{12}$C & $15.5$ & $78.9$ & $1.0$ &
      			$0.8$ & $3.8$
                    \mystrut\\
      			$^{16}$O & $15.5$ & $79.1$ & $1.0$ &
      			$0.8$ & $3.6$
                    \mystrut\\
      			$^{40}$Ca & $15.4$ & $78.7$ & $1.1$ &
      			$0.9$ & $4.0$
                    \mystrut\\
      			$^{48}$Ca & $15.4$ & $78.5$ & $1.1$ &
      			$0.9$ & $4.1$
                    \mystrut\\
      			$^{56}$Fe & $15.4$ & $78.4$ & $1.1$ &
      			$0.9$ & $4.2$
                    \mystrut\\
      			$^{208}$Pb & $15.4$ & $78.4$ & $1.1$ &
      			$0.9$ & $4.2$
                    \mystrut
		\end{tabular}
  	\end{ruledtabular}
\end{table}

The high-momentum tail of any momentum distribution will be scale- and scheme-dependent, i.e., dependent on the potential used. 
We can reproduce results at low-RG resolution for any initial potential, but the reaction operators must consistently evolved.
As evident from Fig.~\ref{fig:schematic_SRC_physics}, we can cancel out the scale and scheme dependence in many cases by taking ratios.
We show examples in Figs.~\ref{fig:pp_plus_pn_ratios}, and \ref{fig:pp_to_pn_ratios} for the pair distribution at $Q=0$.
A clarifying feature of the LDA is that the theta functions defining the Fermi sea imply simple consequences for the pair distribution when $Q=0$.
In particular, the proton and neutron Fermi spheres overlap, so when $N \geq Z$ the product of the theta functions  is unity for the proton Fermi momentum below $\kF^p$, independent of $\kF^n$.

\begin{figure}[tbh]
    \centering
    \includegraphics[width=0.85\columnwidth]{figures_low_res/p_n_pmd_ratios_C12_O16_Ca40_Ca48_Fe56_Pb208_channels_1S0_3S1_kvnn_6_lamb_1p35_kmax_15p0.png}
    \caption{Ratios of pp + pn to nn + np for various nuclei calculated in the LDA with the leading two-body truncation of the pair distribution operator evaluated at $Q=0$. Here we use AV18 and set $\lambda=1.35$ \fmi.}
    \label{fig:pp_plus_pn_ratios}
\end{figure}

\begin{figure}[tbh]
    \centering
    \includegraphics[width=0.85\columnwidth]{figures_low_res/pp_pn_pmd_ratios_C12_O16_Ca40_Ca48_Fe56_Pb208_channels_1S0_3S1_kvnn_6_lamb_1p35_kmax_15p0.png}
    \caption{Ratios of proton-proton to proton-neutron distributions using AV18 and $\lambda=1.35$ \fmi.}
    \label{fig:pp_to_pn_ratios}
\end{figure}

In Fig.~\ref{fig:pp_plus_pn_ratios} we show ratios of the pp + pn to nn + np pair momentum distributions at $Q=0$ as a function of $q$ for six nuclei from $^{12}$C to $^{208}$Pb.
We restrict the range of the plot to the region where SRC physics is expected to dominate.
The ratio is equal to one for $N=Z$ nuclei at all $q$, as expected from factorization as illustrated in Fig.~\ref{fig:schematic_SRC_physics} if the nucleus in numerator and denominator are the same.
Even though there are no high-momentum nucleons in the low-resolution wave function, the result is consistent with phenomenology that the proton and neutron high-momentum distributions should be about the same.
In the region of np dominance near $q=2\,\fmi$ (400\,MeV), this ratio should be unity independent of $N/Z$, while there is $N/Z$ dependence away from this region because there are more nn than pp pairs.

In Fig.~\ref{fig:pp_to_pn_ratios} we show ratios of the pp to pn pair distributions as a function of $q$ for the same nuclei as in Fig.~\ref{fig:pp_plus_pn_ratios}.
The ratio dips down to essentially zero just before 2\,\fmi and then rises to about 0.15 at 4\,\fmi.
This trend is also observed in the GCF calculations~\cite{Cruz-Torres:2019fum,Korover:2020lqf} and reflects the transition from the dominant effect of the tensor force toward the scalar limit.
In the low-resolution calculations here, this dependence on $q$ is purely from the high-momentum part of the factorized unitary transformations.
The ratio shows no dependence on $N/Z$ because the pair momentum distribution at high-$q$ and $Q=0$ is restricted entirely by the proton Fermi sphere in the $\delUtilde\delUtilde^{\dagger}$ term of Eq.~\eqref{eq:pmd_partial_waves} for $N \ge Z$ nuclei.
%smaller of the proton or neutron Fermi spheres in the $\delUtilde\delUtilde^{\dagger}$ term of Eq.~\eqref{eq:pmd_partial_waves}.
%For $N \ge Z$ both the numerator and denominator are constrained by the proton Fermi sphere which cancels in the ratio.

\begin{figure}[tbh]
    \centering
\includegraphics[width=0.82\columnwidth]{figures_low_res/a2_errorbars_C12_O16_Ca40_Ca48_Fe56_Pb208_channels_1S0_3S1_kvnn_6_lamb_1p35.png}
    \caption{SRC scaling factors $a_2$ calculated using AV18 according to Eq.~\eqref{eq:a2}. See text for further details.}
    \label{fig:src_scaling_factors_a2}
\end{figure}

Finally, in Fig.~\ref{fig:src_scaling_factors_a2} we compare calculated SRC scaling factors $a_2$ using AV18 to values for even-even nuclei extracted from inclusive cross section ratios.
Following the prescription of Ref.~\cite{Ryckebusch:2019oya}, we estimate $a_2$ by integrating single-nucleon probability distributions (phase-space weighted $n_{\lambda}^A(q)$) over a high-momentum range:
%
\begin{align}
    \label{eq:a2}
    a_2(A) = \lim_{q\to\infty} \frac{P^A(q)}{P^d(q)} \approx \frac{2}{A} \frac{\int_{\Delta q^{\rm high}} dq\, q^2 n_{\lambda}^A(q)}{\int_{\Delta q^{\rm high}} dq\, q^2 n_{\lambda}^d(q)}.
\end{align}
%
We apply the LDA to both the numerator and denominator, which may help to cancel systematic errors.
The ``error bars'' (which are not statistical uncertainty intervals) are established by using integration ranges $\Delta q^{\rm high} = 2$--$\infty$ \fmi and  $\Delta q^{\rm high} = 3.8$--$4.5$ \fmi~\cite{Ryckebusch:2019oya}.
The agreement with experiment is good.
In future work we will extend the comparison to more nuclei, explore the SRG $\lambda$ dependence in detail, and test the sensitivity to our assumptions~\cite{Tropiano:2021prep}.

\subsection{Low-resolution take on SRC physics}

Here we revisit the key features of high-resolution SRC phenomenology from Sec.~\ref{sec:introduction}, now understood from low resolution via Fig.~\ref{fig:schematic_SRC_physics} and through our explicit LDA calculations from Sec.~\ref{subsec:LDA}.
%
\begin{enumerate}
  %\renewcommand{\theenumi}{\Alph{enumi}}
   \item \textbf{Universal high-momentum nucleon distributions.}
  The entire sequence in Fig.~\ref{fig:schematic_SRC_physics} illustrates the outcome of taking ratios of inclusive cross sections.
  Figure~\ref{fig:schematic_SRC_physics}(h) in particular is the embodiment of universal distributions, with the dependence on the nucleus factorized from the dependence on the high momenta.
  Explicit calculations of the momentum densities manifest the factorization as seen in Fig.~\ref{fig:proton_momentum_distributions}, where each nucleus exhibits the same $q$ dependence.
  The kinematic thresholds selected for the inclusive experiments are those necessary for this clean factorization to hold.
  For SRG parameter $\lambda$ comparable to $\kF$, this corresponds to the conditions for factorization as well as complete dominance of the two-body current.
  In taking ratios, the high-momentum part cancels out, so the leading dependence of the plateau heights in the cross-section ratio, namely $a_2$, is a mean-field quantity, which is well reproduced in our approximations (see Fig.~\ref{fig:src_scaling_factors_a2}).
  The conditions here hold for any high-momentum current.

   \item \textbf{Kinematics of the knocked-out nucleons.}

   If we look at Fig.~\ref{fig:schematic_SRC_physics}(e), we see that the external high-momentum current operator is connected to the soft, evolved low-energy wave function by the operator $\Uhat^\dagger$.
   That wave function has mostly Fermi sea nucleons and nearby admixtures.
   When $\Uhat^\dagger$ acts, we can read off from Eq.~\eqref{eq:Uschematic} that connecting to a high-momentum nucleon must come from the $\delta U_\lambda^\dagger$ part.
   Since this part starts with a two-body piece with the same pair center-of-mass momentum $\Kvec$ as for the states annihilated from the Fermi sea or near the Fermi surface, the high-momentum states must be a pair with center-of-mass momentum distribution the same as the Fermi sea.
   Furthermore, the contributions are dominated by relative s-waves (see Table~\ref{tab:partial_wave_contributions}).
   Thus this basic part of SRC phenomenology~\cite{Cohen:2018gzh} follows immediately.

   We can address the role of the omitted three-body terms either through direct evolution, which is nontrivial but well-established technology for SRG evolution~\cite{Jurgenson:2009qs}, or indirectly by considering the dependence on the SRG flow parameter $\lambda$. Weak dependence indicates small effects of three-body (and higher-body) operators.
   The work of Neff, Feldmeier, and Horiuchi~\cite{Neff:2015xda} used the indirect method for the SRG-evolved nucleon pair distributions for $A=3$ and $A=4$. 
   For example, they look at pair densities with SRG two-body-only unitary transformations in helium-4 and identify where there is $\lambda$ dependence. 
    There is almost no dependence for $K=0$ pairs, but with larger center-of-mass momentum it is significant, meaning that three-body contributions cannot be neglected.
    When integrated over $K$ there is slight $\lambda$ dependence near $2\,\fmi$ in the dominant $S=1,\,T=0$ channel and strong dependence in the other channels. 
    In all cases the $\lambda$ dependence is small above $3\,\fmi$.
   The $\lambda$ dependence for the calculations presented here will be explored in detail in future work~\cite{Tropiano:2021prep}.

  \item \textbf{Ratio of $np$ to $pp$ knocked-out pairs for intermediate relative momentum (300--500 MeV).}

    Tensor dominance follows directly from calculations of the unitary transformation operator in the two-body subspace.
    Figure~\ref{fig:ratio_1p35_kvnn_6_222} shows the ratio of unitary transformations in the dominant s-waves. 
    The ratio of triplet to singlet shows the peak near $q = 2\,\fmi$ for both potentials, associated with a zero in the \singletS\ channel and the enhanced tensor contribution in the \tripletS\ channel.
    Figures~\ref{fig:barcharts_AV18} and \ref{fig:barcharts_Gezerlis} show that despite the tensor dominance, at low-RG resolution the coupling to the wave function is through the s-waves, not tensor correlations in the wave functions.
    The consequences for experimental ratios are illustrated in Figs.~\ref{fig:pp_plus_pn_ratios} and \ref{fig:pp_to_pn_ratios}, which are consistent with SRC phenomenology.

   \item \textbf{Ratio of knock-out cross sections from neutron-rich nuclei compared to $N=Z$ nuclei.}

    In the region of $np$ dominance, the pairs coupled from the Fermi sea are almost all $np$ pairs, so the high-momentum proton and neutron distributions are the same, independent of the $N/Z$ ratio in the mean-field part.
    This is seen in Fig.~\ref{fig:pp_plus_pn_ratios} and is an immediate consequence of the $\delta U$ part being dominated by the $\tripletS$ channel and this term in $\Uhat$ creating pairs. 
    So whatever low-energy wave function it hits, it will always ``kick above the Fermi sea'' an equal number of neutrons and protons.

  \item \textbf{Transition from $np$ dominance of SRC pairs to ratios expected from scalar counting.}
   This transition is manifested in Figs.~\ref{fig:ratio_1p35_kvnn_6_222} and \ref{fig:pp_to_pn_ratios}.
   In the low-RG resolution formalism, it is simply a consequence of the two-body physics that is encapsulated in the two-body unitary transformations by the SRG evolution.
   This physics is well-known from NN scattering.

\end{enumerate}

\textbf{The generalized contact formalism.}
%
As already noted, the GCF phenomenology is built on
a factorization ansatz for the many-body wave function  when a pair of nucleons has small relative distance or high relative momenta.
This leads to the pair distributions in coordinate and momentum space taking the forms in Eqs.~\eqref{eq:GCF_coordinate} and \eqref{eq:GCF_momentum}, respectively.

The parallel formulation at low-RG resolution is that the dependence on $r$ or $q$ in the wave function becomes the corresponding part of the facotrized unitary transformation.
As such, it is the leading term in an operator product expansion~\cite{Anderson:2010aq,Bogner:2012zm,Tropiano:2020zwb}.
A key advantage of the RG formulation is that systematic corrections are well defined.

\textbf{The low-order correlation operator approximation (LCA)}.
The LCA methodology can be used to compute observables for nucleon knockout reactions that are dominated by SRCs.
The high-resolution ground-state wave function $|\Psi_A\rangle$ or nucleus $A$  is related to a simple wave function $|\Phi_A\rangle$ (a Slater determinant in practice) through a correlation operator
$\calG$:
%
\begin{align}
    |\Psi_A\rangle = \frac{1}{\sqrt{\langle \Phi_A | \calG^\dagger \calG | \Phi_A\rangle}}
    \calG | \Phi_A \rangle
    \;.
\end{align}
%
The LCA consists in approximating $\calG$ by central (Jastrow), tensor, and spin-isospin SRC correlations with terms corresponding to two-body operators.
The dominant contribution to the SRC part of the nuclear momentum distribution takes the form~\cite{Ryckebusch:2019oya}
%
\begin{align} \label{eq:LCA}
    n^A_{\rm\scriptscriptstyle SRC}(\qvec) &\sim 
    \sum_{NN'\in\{p,n\}} \sum_{\alpha\beta} \sum_{\Kvec,\kvec,\kvec'}
    \calG^\dagger_{12}(\frac{\Kvec}{2}+\kvec-\qvec) \notag \\
    & \qquad\qquad\qquad\qquad\qquad \null \times
    \calG_{12}(\frac{\Kvec}{2}+\kvec'-\qvec) \notag \\
    & \null \times \langle N\alpha, N'\beta |
    \akdag_{\frac{\Kvec}{2}+\kvec}
    \akdag_{\frac{\Kvec}{2}-\kvec}
    a^{\phantom{\dagger}}_{\frac{\Kvec}{2}+\kvec'}
    a^{\phantom{\dagger}}_{\frac{\Kvec}{2}-\kvec'}
    | N\alpha, N'\beta \rangle
    ,
\end{align}
%
where the $\alpha,\beta$ sum runs over  occupied single-particle states
in the Slater determinant $|\Phi_A\rangle$.
The parallels to our low-RG resolution formulation are apparent, both using a simple many-body wave function and with the correlation function taking the place of our two-body unitary transformations.
Note that these functions 
%have explicit dependence on the center-of-mass momentum $\Kvec$, they 
are not unitary and they are constructed by matching to ab initio results rather than being constructed directly.
It will be interesting to make more detailed comparisons.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion: Takeaway points} \label{sec:implications}

%\subsection{Questions and answers}

In this section we summarize some of the takeaway points from an RG-based perspective on SRC physics in the form of answers to frequently asked questions.

\begin{itemize}
    \item \textbf{What is short-range-correlation (SRC) physics?}
    SRC physics is short-distance physics manifesting at high RG resolution as high-relative-momentum nucleon pairs, while such pairs are suppressed at low RG resolution.
    The SRC momentum scale starts where the tensor force dominates the NN interaction (around $2\,\fmi = 400$\,MeV or a bit lower).
    The SRC pairs have center-of-mass momentum distributions with a width comparable to the Fermi momentum.

    \item \textbf{Where does the short-range physics of SRC pairs appear at low RG resolution?}
    With decreasing RG resolution, this physics will shift from wave functions (structure) to interaction operators (potential/reactions) with smooth momentum dependence. 
    This was demonstrated explicitly and quantitatively for deuteron electrodisintegration~\cite{More:2015tpa,More:2017syr}.
    The characteristics of this SRC physics can be identified from the unitary transformation operator evaluated in a few-body space (it is dominantly two-body).

   \item\textbf{Which is the correct picture of nuclei, with hard or soft potentials?}
   The RG explains that both hard and soft pictures are correct descriptions of nature (actually there is a continuum of pictures!), if one treats structure and reactions consistently (i.e., at the same RG resolution).

   \item\textbf{What is the best choice of RG resolution scale?} 
   Weinberg’s 3rd Law of Progress in Theoretical Physics~\cite{Weinberg:1981qq} states ``You can use any degrees of freedom you like to describe a physical system, but if you choose the wrong ones you’ll be sorry!'' 
   For applications to hard scattering in QCD, the resolution scale is chosen to be of order the characteristic four-momentum transfer so that the reaction mechanism can be calculated in perturbation theory and factorization is well established.
   But the best choice of scale may not be so clear for analyzing SRC experiments because of the trade-offs.

   \item\textbf{Is SRC physics missing from low-RG resolution descriptions of nuclei?}
   It is not missing. The Hamiltonians at low resolution are constructed to match energies or scattering observables for low-energy bound states. 
   This can be seen  explicitly through RG evolution (e.g., with the SRG), where short-distance modification of wave functions in coordinate space due to repulsive core or tensor interactions, or the related high-momentum tail of momentum-space wave functions, is smoothly suppressed with the lowering of the RG scale and the potential shifts by weakly momentum-dependent pieces.
   If appropriate (i.e., consistent) operators are omitted, then SRC physics \emph{will} be missed, but it can always be accommodated in a consistent calculation.

   \item\textbf{What are the advantages of a high-RG-resolution description of nuclei?}
   A high-RG description enables models of short-distance physics that use resolved degrees of freedom. 
   This can mean that the dominant reaction mechanism is particularly simple (e.g., one-body currents). 
  The high-RG-resolution GCF phenomenology provides a reasonable, if not yet high-precision, description of SRC experiments to date.
   It is also the starting point for evolution to low resolution.

   \item\textbf{What are the advantages of a low-RG-resolution description of nuclei?}
   The nuclear structure is increasingly perturbative at low resolution. 
   Many ab initio methods only work at lower resolutions and many-body perturbation theory becomes usable. 
   Scale separations and factorization are better exploited. 
   Universal behavior is more apparent. 
   Final-state interactions have been shown to be suppressed for deuteron electrodisintegration and this is expected to be a general phenomena based on local decoupling.

   \item\textbf{What does it mean for structure and reaction models to be \emph{consistent}?}
   There are several aspects to consistency. 
   One aspect is the scale and scheme. 
   If one uses a low-resolution wave function with high-resolution reaction operators, this is inconsistent and can lead to apparent quenching. 
   To maintain consistency at different scales, one can start with a consistent Hamiltonian and current operators and evolve them together with an RG approach like SRG.

   \item\textbf{How do you connect the pictures at two resolutions?}
   Using the (similarity) renormalization group! The consistent low-RG resolution operators can be evolved from high resolution (even many-body operators).   Unitary evolution is an important aspect if we want to describe high-experimental-resolution probes of low-RG-resolution nuclei.
   Or consistent operators can be fit! (The latter possibility will be explored in future work~\cite{Tropiano:2021prep}.)

  \item\textbf{How does RG resolution relate to experimental resolution?}
  RG resolution is set by the decoupling scale, which dictates what momenta are part of a low-energy wave function. 
  Note that for unitary RG evolution, like the SRG, this is a separation scale; the high-momentum components are not eliminated but appear only in wave functions of high-energy states.
  Experimental resolution is set by the kinematics of the experiment. 
  These are independent!
  The RG resolution is not a measurable quantity but rather a choice of the analysis.

  \item\textbf{Can high-momentum nuclear distributions be measured experimentally?}
  They can be extracted from experiment in a scale/scheme dependent manner. This is the same situation as with QCD parton distributions.
  Note that this means that high-momentum distributions using different Hamiltonians (which will manifest scale and scheme dependence) will not agree.

  \item\textbf{When you soften a Hamiltonian, do you “harden” the interaction operators?}
  No. SRG makes unitary transformations, so no physics is lost, but it is nonperturbatively “reshuffled”.
  (Note that this means that an SRG-evolved Hamiltonian will have the same limitations or virtues as the original Hamiltonian!)
  Low-energy states filter operators so only low-momentum components of the operator contribute to matrix elements. 
  This leads to numerous simplifications.
  Purely high-momentum operators (meaning operators connecting to only high-momentum physics) factorize and the dependence on high momentum is state independent.
  This is the manifestation of an operator product expansion.
  Where the tensor interaction plays a role, there is a de-emphasis of D-wave physics compared to S-wave contributions.
  Reduced final-state interactions are observed.
  The complication is from higher many-body operators, but these can be evolved in few-body spaces.

  \item\textbf{What can SRC experiments tell us about high-density nuclear matter?}
  In the high-SRG-resolution picture, the basic intuition is that in SRC pairs nucleons are at short distances so they probe high densities.
  But to be quantitatively useful at high densities in this picture one would at least need to extend the description to three-body forces.
  The GCF phenomenology is an implementation of leading-order Brueckner theory, which provides a \emph{low-density} expansion.
  Three-body correlations are known from calculations to be important for neutron star physics.
  %[\emph{Also more mixing with near-$\kF$ states will increase three-body correlations.}]

  \item\textbf{What is the relevance of EMC physics for low-energy nuclei? How should we understand the observed SRC-EMC correlation?} 
  This physics should be automatically included in an EFT expansion because of the completeness of the operator basis. 
  The EMC effect is from short-distance physics that manifests first as two-body contact operators. 
  If mean-field estimate plus chiral naturalness is valid, then the expected EMC slope is consistent with experiment. The treatment (from Chen and Detmold originally~\cite{Chen:2004zx,Chen:2016bde,Lynn:2019vwp}) starts with an operator product expansion applied at the level of QCD matrix elements, which is then matched to an EFT for matrix elements; 2-body operators must be there! 
  The dominance of the leading two-body contact then accounts for EMC-SRC correlations.

  \item\textbf{What are the implications for other knock-out reactions?}
  Analyses of exclusive intermediate energy nucleon knock-out experiments have shown systematic discrepancies between measured cross sections and theoretical predictions~\cite{Tostevin:2014usa,Aumann:2020tcq}.
  But these analyses mix a high-resolution reaction mechanism (e.g., eikonal model) with a low-resolution structure description (e.g., shell model).
  Such a mismatch applied to the electron-scattering SRC experiments considered here would lead to essentially zero cross section predicted theoretically because the contribution from the two-body current at low RG resolution would be entirely omitted and the one-body current has no support at high momentum.
  This implies that RG evolution of the reaction operators may be essential for resolving the discrepancies.
  The situation is not nearly as clean as the present case, however.
  For exclusive scattering to low-lying single-particle states, the theory would be \emph{larger} than experiment because a missing induced current (two-body, if electron scattering) would not exclude flux (cf.\ SRCs depleting the orbitals).

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary} \label{sec:summary}

We have demonstrated that high-RG-resolution SRC physics is faithfully incorporated at low resolution by unitary RG evolution, with weakly correlated wave functions and simple evolved operators.
We have also confirmed that at low-resolution the consequences of SRC experiments follow directly from basic and well-established nuclear physics: the density dependence of nuclei and  characterisitcs of the nucleon-nucleon interactions, in particular the tensor force and short-distance repulsion.
Furthermore, the basic features of the SRC phenomenologies, in particular the GCF and the LCA, emerge naturally by consideration of low resolution. 
The systematic SRG framework points to how to improve them.

The value so far  of the SRC knock-out experiments is not new insight into the internucleon interactions or features of the many-body wavefunctions.
Indeed, we have seen that all that is needed to explain the observations are familiar features of the NN interaction from phenomenological or chiral EFT potentials well understood from pion exchange and fitting to NN scattering data.
Rather, it is the demonstration that this physics can be isolated and controlled that opens the possibilities to understand more complicated reactions.
A better understanding of how to analyze reactions is critical for rare isotope nuclear physics and extensions of the SRC experiments can be a gateway.
%Experiments that probe SRC physics can isolate short-distance reaction mechanisms.
Combined with RG analyses, such experiments can help calibrate and test reactions cleanly and set the stage for extensions to more complicated knock-out reactions.

Planned extensions of the present investigations include~\cite{Tropiano:2021prep}:
\begin{itemize}
    \item \textbf{Examining SRG resolution ($\lambda$) dependence.} How robust are the approximations and results presented here to changes in $\lambda$? What are the relative importance of three-body and tensor correlations in the wave functions, three-body forces in the Hamiltonian, induced three-body contributions to the operators?

    \item \textbf{Improving the treatment of ground-state wave function.} 
    One approach is to use the DME to improve the LDA and establish the uncertainties. 
    We can also explore the use of many-body perturbation theory and ab initio methods directly.

    \item \textbf{Improving the operators.} The truncation to two-body operators will be relaxed systematically, quantifying the corrections and seeking tractable approximations.

    \item \textbf{Fitting the operators.}
    An alternative to evolving high-resolution operators is to fit them at low-resolution. 
    This will first be explored for cases where evolution is also available.

    \item \textbf{Extensions to other reactions.}
    One of the first steps will be to re-examine the exclusive $(e,e'p)$ knock-out reactions (e.g., those studied at NIKHEF and other electron scattering facilities)~\cite{Dieperink:1990uk,Kelly:1996hd}.

\end{itemize}
%
Work on all of these areas is in progress.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{acknowledgments}
We thank Nathan Parzuchowski for contributions to an earlier version of this work, and Wim Cosyn and Jan Ryckebusch for helpful comments on the manuscript. We thank our colleagues for many useful discussions on SRC physics over the years.
The work of AJT and RJF was supported by the National Science Foundation under Grant No.~PHY--1913069, and the NUCLEI SciDAC Collaboration under US Department of Energy MSU subcontract RC107839-OSU\@.
The work of SKB was supported by the National Science Foundation under Grant Nos. PHY-1713901 and PHY-2013047, and the U.S. Department of Energy, Office of Science, Office of Nuclear Physics under Grant No. de-sc0018083 (NUCLEI SciDAC Collaboration).
\end{acknowledgments}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\appendix

\section{LDA formulas} \label{sec:formulas}

In this appendix we summarize the LDA formulas applied in Sec.~\ref{subsec:LDA}.
The single-nucleon momentum distribution is:
%
\begin{widetext}
\begin{align}
    \label{eq:snmd_partial_waves}
    & n_{\lambda}^{\tau}(q) =  \int d^3R\, \Bigl\{ 2 \theta(\kF^{\tau}-q) \notag \\
    & \quad \null + 32  \sum_{L,S,T}\!\!{\vphantom{\sum}}'\, \sum_{J}  (2J+1)
    \frac{2}{\pi}\int_0^{\infty}\! dk\, k^2  
    \melr{k (L S) J T}{\delta U}{k (L S) J T}  
%    \notag \\
%    & \qquad\qquad\null\times
        \sum_{\tau'} |\braket{\tau \tau'}{T \, \tau+\tau'}|^2
\theta(\kF^{\tau}-q) \int_{-1}^1 \frac{dx}{2}\theta(\kF^{\tau'}-\abs{\mathbf{q}-2\mathbf{k}}) \notag \\
    & \quad \null + 2  \sum_{L,L',S,T}\!\!\!\!\!{\vphantom{\sum}}'\,\,  \sum_{J}  (2J+1)  
    \Bigl(\frac{2}{\pi}\Bigr)^2 \int_0^{\infty} dk\, k^2 \int_0^{\infty} dK\, K^2 \int_{-1}^1 \frac{dy}{2} \int_{-1}^1 \frac{dz}{2}  
    \melr{k (L S) J T}{\delta U}{\abs{\mathbf{q}-\mathbf{K}/2}  (L' S) J T} 
    \notag \\
    & \qquad\qquad\qquad \null\times   
     \melr{\abs{\mathbf{q}-\mathbf{K}/2} (L' S) J T}{\delta U^{\dagger}}{k (L S) J T}  
%     \notag \\ 
%     & \qquad\qquad \null\times 
    \sum_{\tau'} |\braket{\tau \tau'}{T \,\tau+\tau'}|^2
     \,\theta(\kF^{\tau}-\abs{\mathbf{K}/2 + \mathbf{k}}) \,\theta(\kF^{\tau'}-\abs{\mathbf{K}/2 - \mathbf{k}})
     \Bigr\},
 \end{align}
%\end{widetext}
%
where the local Fermi momentum is $\kF^\tau(R) = (3\pi^2\rho^\tau(R))^{1/3}$ with $\rho^\tau$ the proton or neutron number density normalized to $Z$ or $N$.
For the angle averaging we have defined 
\begin{align}
  \abs{\mathbf{q}-2\mathbf{k}} = \sqrt{q^2+4k^2-4qkx}, 
  \qquad \abs{\mathbf{q}-\mathbf{K}/2} = \sqrt{q^2+K^2/4-qKy}, 
  \qquad
 \abs{\mathbf{K}/2 \pm \mathbf{k}} = \sqrt{K^2/4 + k^2 \pm Kkz}.
\end{align}
%
A primed summation means a restriction to $L + S + T$ odd and $L+L'$ even.
Integration over $\int d^3q/(2\pi)^3$ yields the full normalization of $n_{\lambda}^{\tau}(q)$ from the first line in Eq.~\eqref{eq:snmd_partial_waves} while the unitary condition from Eq.~\eqref{eq:UdaggerU} expanded in partial waves enforces cancellation of the second and third terms after changing variables appropriately.

%
The pair momentum distribution in the LDA assuming spherical symmetry is (with explicit $R$ or $R'$ dependence):
%
%\begin{widetext}
\begin{align}
    \label{eq:pmd_partial_waves}
    n_{\lambda}^{\tau \tau'}(\qvec,\mathbf{Q}) &= \frac{1}{2} 
    \int d^3R\, 2 \theta(\kF^{\tau}(R)-\abs{\mathbf{Q}/2 + \mathbf{q}}) 
    \int d^3R'\, 2\theta(\kF^{\tau'}(R') -\abs{\mathbf{Q}/2 - \mathbf{q}}) 
    \notag \\
    & \quad \null - \frac{1}{32}(2\pi)^3\delta^3(\qvec) \delta_{\tau,\tau'}
    \int d^3R\, 2 \theta(\kF^{\tau}(R)-\abs{\mathbf{Q}/2}) 
    \notag \\
    & \quad\null + 2\frac{(2\pi)^3}{4\pi} \int d^3R\,\sum_{L,S,T}\!\!{\vphantom{\sum}}'\, \sum_{J}  (2J+1) \frac{2}{\pi}  
    %\notag \\
    %& \qquad\qquad\null \times 
    \melr{q (L S) J T}{\delta U}{q (L S) J T}
    |\braket{\tau \tau'}{T\, \tau+\tau'}|^2
    \notag \\
    & \qquad\qquad \null \times
    \theta(\kF^{\tau}(R)-\abs{\mathbf{Q}/2 + \mathbf{q}}) \theta(\kF^{\tau'}(R)-\abs{\mathbf{Q}/2 - \mathbf{q}})  \notag \\
    & \quad \null +  \frac{(2\pi)^3}{4\pi} \int d^3R\, \sum_{L,L',S,T}\!\!\!\!\!{\vphantom{\sum}}'\,\,  \sum_{J} (2J+1) (\frac{2}{\pi})^2 \int_0^{\infty} dk\, k^2  
    %\notag \\
    %&  \qquad\qquad \null\times
    \melr{k (L S) J T}{\delta U}{q (L' S) J T} \melr{q (L' S) J T}{\delta U^{\dagger}}{k (L S) J T}   \notag \\  
  %  & \qquad\qquad \null\times  \theta(\kF^{\tau''}-\abs{\mathbf{Q}/2 + \mathbf{k}}) \theta(\kF^{\tau'''}-\abs{\mathbf{Q}/2 - \mathbf{k}}).
     & \qquad\qquad \null\times 
     %\sum_{\tau'', \tau'''}|\braket{\tau'' \tau'''}{T M_T}|^2 \,
    |\braket{\tau \tau'}{T \,\tau+\tau'}|^2
     \,\theta(\kF^{\tau}(R)-\abs{\mathbf{Q}/2 + \mathbf{k}}) \,\theta(\kF^{\tau'}(R)-\abs{\mathbf{Q}/2 - \mathbf{k}}),
\end{align}
%
\end{widetext}
%
where for $|\Qvec| \neq 0$, we average over the angle between $\Qvec$ and $\kvec$ to evaluate the $\theta$ functions in the last term.
The first two lines carry the full normalization of the momentum distribution. 
It is easily verified that an integration over $\int d^3q/(2\pi)^3 \int d^3Q/(2\pi)^3$ of these terms in the LDA followed by integrations over $\Rvec$ and $\Rvec'$  yield $Z(Z-1)/2$ if $\tau=\tau' = 1/2$, $N(N-1)/2$ if $\tau=\tau'=-1/2$, and $NZ/2$ if $\tau=\pm 1/2$ while $\tau'=\mp 1/2$.
The unitary condition from Eq.~\eqref{eq:UdaggerU} expanded in partial waves enforces cancellation of the third and fourth terms after integrating over $\qvec$, for any $\Qvec$. 
This is manifest after switching labels for $\kvec$ and $\qvec$ in the last term.

The angle average of the $\theta$ function in the second term of Eq.~\eqref{eq:snmd_partial_waves} is
%
\begin{align}
    F_1^{\tau\tau'}(q,k) &= \int_{-1}^1 \frac{dx}{2}\,\theta(\kF^{\tau'}-\abs{\mathbf{q}-2\mathbf{k}}) \notag \\
    &=
  \begin{cases} 
   1 & \text{if } q < \kF^{\tau'} \text{and\ } 2k < \kF^{\tau'} - q\\[8pt]
   \frac{{\kF^{\tau'}}^2 - (q-2k)^2}{8kq}  &  \text{if } q < \kF^{\tau'}\ \text{and\ } \\
   & \quad\kF^{\tau'} - q < 2k < \kF^{\tau'} + q \\[8pt]
   \frac{{\kF^{\tau'}}^2 - (q-2k)^2}{8kq} & \text{if }  \kF^{\tau'} < q < \kF^{\tau}\  \text{and\ } \\
   & \quad q - \kF^{\tau'}  < 2k < q + \kF^{\tau'} \\[8pt]
   0 & \text{otherwise}
  \end{cases}
\end{align}
%
% The angle average of pairs of theta functions that appear several times in Eqs.~\eqref{eq:snmd_partial_waves} and \eqref{eq:pmd_partial_waves} when the $\kF$s are equal 
% is given  by
% %
% \begin{align}
%     F_2(Q,k) &= \int_{-1}^{1}\frac{dz}{2}\,
%     \theta(\kF-\abs{\Qvec/2+\kvec}) 
%                     \theta(\kF - \abs{\Qvec/2-\kvec})
%                     \notag \\
%   &= 
%   \begin{cases} 
%   1 & \text{if } k < \kF - \frac{Q}{2}\\
%   \frac{\kF^2 - k^2 - Q^2/4}{kQ}  &  \text{if } \kF - \frac{Q}{2} < k < \sqrt{\kF^2 - \frac{Q^2}{4}} \\
%   0 & \text{if } k > \sqrt{\kF^2 - \frac{Q^2}{4}} 
%   \end{cases}
% \end{align}
% The generalization to $\kF^{\tau} \neq \kF^{\tau'}$ is straightforward although the expression is unwieldy~\cite{Tropiano:2021prep}.
%
The angle average of pairs of theta functions that appear several times in Eqs.~\eqref{eq:snmd_partial_waves} and \eqref{eq:pmd_partial_waves} 
is given  by
%
\begin{align}
    F_2(Q,k) &= \int_{-1}^{1}\frac{dz}{2}\,
    \theta(\kF^{\tau}-\abs{\Qvec/2+\kvec}) 
                    \theta(\kF^{\tau'} - \abs{\Qvec/2-\kvec})
                    \notag \\
  &= 
  \begin{cases} 
  1 & \text{if } k < \kFmin - \frac{Q}{2}\\[8pt]
  \frac{(\kFmin)^2 - (k - Q/2)^2}{2kQ}  &  \text{if } k < \kFmin + \frac{Q}{2} \text{\ and\ } \\
  & \hspace*{-13pt}\kFmin - \frac{Q}{2} < k < \kFmax - \frac{Q}{2} \\[8pt]
  \frac{(\kFavg)^2 - k^2 - Q^2/4}{kQ}  &  \text{if } \kFmax - \frac{Q}{2} < k  \text{\ and\ } \\
  & \quad k < \sqrt{(\kFavg)^2 - \frac{Q^2}{4}} \\[8pt]
  0 & \text{otherwise} 
  \end{cases}
\end{align}
%
where
%
\begin{align}
    \kFmin &\equiv \min(\kF^{\tau}, \kF^{\tau'}) ,\\
    \kFmax &\equiv \max(\kF^{\tau}, \kF^{\tau'}) ,\\
    \kFavg &\equiv \sqrt{\frac{1}{2}\Bigl({\kF^{\tau}}^2 +  {\kF^{\tau'}}^2\Bigr)} .
\end{align}
Extensions of the local density approximation applied here are discussed in Ref.~\cite{Tropiano:2021prep}.

\bibliography{tropiano_bib}

\end{document}

### 2021-09-10 notes/src_physics/src_low_res.tex
Updating notes/src_physics files after updating arXiv submission
Updated figures and corrected typos after iteration with PRC.

@@
 Our demonstration has implications for the analysis of knock-out reactions for which SRC physics is not cleanly isolated.
-
 \end{abstract}
@@
 Short-range correlations (SRCs) in atomic nuclei are usually identified as components of the nuclear wave function with nucleon pair momenta well above the Fermi momentum~\cite{Hen:2016kwk}. 
-There has long been an apparent need for such SRCs to account for measured cross sections~\cite{Brueckner:1955zzd}, but direct evidence has been nebulous until recent experiments succeeded in cleanly isolating this physics~\cite{Hen:2016kwk,Korover:2014dma,Hen:2014nza,Duer:2018sby,Duer:2018sxh,Schmookler:2019nvf,Cruz-Torres:2020uke,Schmidt:2020kcl,Korover:2020lqf}.
+There has long been an apparent need for such SRCs to account for measured cross sections~\cite{Brueckner:1955zzd}, but direct evidence has been nebulous until recent experiments succeeded in cleanly isolating this physics~\cite{Hen:2016kwk,Korover:2014dma,Hen:2014nza,Duer:2018sby,Duer:2018sxh,Schmookler:2019nvf,Cruz-Torres:2020uke,Schmidt:2020kcl,CLAS:2020rue}.
 SRC phenomenologies have been developed that account for the observations, but they seem to be at odds with successful descriptions of nuclear structure such as the shell model that do not feature explicit short-range structure in the nuclear wave function.
 The application of the renormalization group (RG) can make sense of this conflict. 
-RG methods are used to analyze critical phenomena in condensed matter and evolve the strong coupling and parton distributions in high-energy quantum chromodynamics (QCD).
+RG methods are used to analyze critical phenomena in condensed matter~\cite{Amit:2005} and evolve the strong coupling and parton distributions in high-energy quantum chromodynamics (QCD)~\cite{RevModPhys.67.157,peskin1995introduction}.
 Applied to nuclei, the RG shows how SRC physics is manifested differently at varying resolution scales. 
@@
     \centering
-    (a)\includegraphics[width=0.44\columnwidth]{low_rg_resolution_cartoon_1.pdf}~~%
-    (b)\includegraphics[width=0.44\columnwidth]{high_rg_resolution_cartoon_1.pdf}
+    (a)\includegraphics[width=0.43\columnwidth]{low_RG_resolution_cartoon_1_new.pdf}~~%
+    (b)\includegraphics[width=0.44\columnwidth]{high_RG_resolution_cartoon_1_new2.pdf}
     \caption{Cartoon snapshots of a nucleus at (a) low-RG  and (b) high-RG resolutions. 
@@
     \centering
-    \includegraphics[width=0.9\columnwidth]{Cartoon_momentum_distribution.pdf}
+    \includegraphics[width=0.9\columnwidth]{Cartoon_momentum_distribution_v2.pdf}
     \caption{Cartoon of a nuclear single-particle momentum distribution at high RG resolution.
@@
 In Fig.~\ref{fig:cartoon_nuclei} we visualize configurations that might be sampled at different RG resolutions. Only at high-RG resolution do we find a high-momentum pair.
-In practice we associate the high-resolution picture with local phenomenological Hamiltonians, in particular the Argonne V18 (AV18) potential~\cite{Wiringa:1994wb} and its associated three-body forces, which have been featured in most of the recent analyses of SRC experiments.
+In practice we associate the high-resolution picture with local phenomenological Hamiltonians, in particular the Argonne V18 (AV18) potential~\cite{Wiringa:1994wb} and its associated three-body forces~\cite{Carlson:1983kq,Pieper:2001ap}, which have been featured in most of the recent analyses of SRC experiments~\cite{Hen:2016kwk}.
 AV18 describes nucleon-nucleon observables within experimental accuracy up to the inelastic threshold and the elastic part of the cross section reasonably well up to much higher energies.
 The AV18 momentum distributions in nuclei extend well above 4\,fm$^{-1}$ or 800\,MeV (in units where $\hbar = c = 1$), as caricatured in Fig.~\ref{fig:cartoon_mom_dist} (see also the figures in Sec.~\ref{sec:low_resolution}).
-For concreteness we associate the low-resolution picture with the shell model (configuration interaction), either in its phenomenological form or derived from ab initio methods such as coupled cluster or the in-medium similarity RG.
+For concreteness we associate the low-resolution picture with the shell model (configuration interaction), either in its phenomenological form~\cite{Heyde:2004zz,Ring:2005} or derived from ab initio methods such as coupled cluster or the in-medium similarity RG~\cite{Hergert:2020bxy}.
 In this picture, nucleon momentum distributions die off rapidly above $\kF$.
@@
 These effects are all consistent with two phenomenological approaches. 
-The Generalized Contact Formalism (GCF) model uses a factorization ansatz for the nuclear many-body wavefunction applied to these high-momentum transfer processes~\cite{Weiss:2015mba,Weiss:2016obx,Weiss:2018tbu,Weiss:2021zyb}.
+The Generalized Contact Formalism (GCF) model uses a factorization ansatz for the nuclear many-body wavefunction applied to these high-momentum transfer processes~\cite{Weiss:2015mba,Alvioli:2016wwp,Weiss:2016obx,Weiss:2018tbu,Weiss:2021zyb}.
 The low-order correlation operator approximation (LCA)~\cite{Vanhalst:2014cqa,Ryckebusch:2018rct,Ryckebusch:2019oya} is used to compute how SRCs affect nuclear momentum distributions; it does so by shifting the SRC physics from the wave function to a correlation operator, which is in turn parametrized
@@
 Here $A$ is the nucleon number (protons plus neutrons) and $\alpha$ is a spin index.
-The common coefficient is called a ``contact'' in analogy to the quantity defined in cold atom physics.
-The two-body functions are extracted from the short-distance (high-momentum) dependence of the zero-energy solutions to the Sch\"odinger equation for a given NN interaction.%
+The common coefficient is called a ``contact'' in analogy to the quantity defined in cold atom physics~\cite{Tan2008contact1,Tan2008contact2}.
+The two-body functions are extracted from the short-distance (high-momentum) dependence of the zero-energy solutions to the Schr\"odinger equation for a given NN interaction.%
 \footnote{It would be misleading to call them wave functions, as pointed out originally in Ref.~\cite{Brueckner:1955zzd}.}
@@
   \centering
-  \includegraphics[width=0.9\columnwidth]{AV18_percentages_deuteron_band.png}
+  \includegraphics[width=0.9\columnwidth]{AV18_Gezerlis_percentages_deuteron_band.png}
   \caption{Percentage contributions from each channel to the matrix element
-  of the momentum distribution in the deuteron with $q=2$, $3$, and $4\,\fmi$ for AV18.
+  of the momentum distribution in the deuteron with $q=2$, $3$, and $4\,\fmi$ for AV18 (left bar at each $\lambda$ value) and Gezerlis \NNLO\ (right bar) potentials.
 We compare unevolved and SRG-evolved (both wave function and operator, so the net matrix element is unchanged) results where $\lambda=1.35\,\fmi$.}
-  \label{fig:barcharts_AV18}
+  \label{fig:barchart_deuteron}
 \end{figure}
 
-\begin{figure}[tbh]
-  \centering
-  \includegraphics[width=0.9\columnwidth]{Gezerlis_percentages_deuteron_band.png}
-  \caption{Same as Fig.~\ref{fig:barcharts_AV18} but for the Gezerlis \NNLO\ potential.}
-  \label{fig:barcharts_Gezerlis}
-\end{figure}
+% \begin{figure}[tbh]
+%   \centering
+%   \includegraphics[width=0.9\columnwidth]{Gezerlis_percentages_deuteron_band.png}
+%   \caption{Same as Fig.~\ref{fig:barcharts_AV18} but for the Gezerlis \NNLO\ potential.}
+%   \label{fig:barcharts_Gezerlis}
+% \end{figure}
 
 One might have expected that the dominance of the tensor means that the operator will be sensitive to $^3\mbox{D}_1$ admixtures in the ground state even when evolved.
-This is not the case, as illustrated in Figs.~\ref{fig:barcharts_AV18} and \ref{fig:barcharts_Gezerlis}. 
+This is not the case, as illustrated in Fig.~\ref{fig:barchart_deuteron}. 
 The high-resolution results ($\lambda = \infty$) do come dominantly from the $\tripletD$--$\tripletD$ part for momenta $q$ where the tensor force dominates while it is more evenly split with $\tripletS$--$\tripletS$ (in a scheme/scale dependent way) at higher momenta.
 But the low-resolution results ($\lambda = 1.35\,\fmi$ here) are always heavily dominated by the $\tripletS$--$\tripletS$ part.
-This implies that simple ground-state wave functions with local density approximations (LDAs) will work quite well at low RG resolution, as illustrated in the next section.
+Note that the same pattern holds for both the phenomenological AV18 potential and the Gezerlis \NNLO\ chiral EFT potential.
+This S-wave dominance implies that simple ground-state wave functions with local density approximations (LDAs) will work quite well at low RG resolution, as verified in the next section.
 
@@
 The results presented here are only a sampling of what is possible, using the crudest approximation.
-Nevertheless, they suffice to show that low-RG resolution calculations can reproduce all the features of SRG phenomenology listed in Sec.~\ref{sec:introduction}.
+Nevertheless, they suffice to show that low-RG resolution calculations can reproduce all the features of SRC phenomenology listed in Sec.~\ref{sec:introduction}.
 In future work we will explore more accurate approximations and calibrate the theoretical uncertainties~\cite{Tropiano:2021prep}.
@@
 Indeed, the physics is focused on short distances, which suggests that an LDA should work well, particularly as the unitary transformations in the factorization region ($\delUtilde^{(2)}_\lambda(\kvec,\kvec')$ with $|\kvec| < \lambda$ and $|\kvec'|\gg \lambda$) are weakly dependent on the low momentum~\cite{Tropiano:2020zwb}.
+Figures included as Supplemental Material [URL will be inserted by publisher] illustrate the factorization of the $\delUtilde\delUtilde^{\dagger}$ term in Eq.~\eqref{eq:pair_mom_dist_op}.
 
@@
 We demonstrate the LDA for proton momentum distributions using the AV18 potential in Fig.~\ref{fig:proton_momentum_distributions}, for which we can compare to quantum Monte Carlo calculations~\cite{Wiringa:2013ala,Lonardoni:2017egu,Wiringa:single_distributions}.
-We use proton and neutron densities generated from the SLy4 Skyrme interaction using the HFBRAD code~\cite{Bennaceur:2005mx}.
+We use proton and neutron densities generated from the SLy4 Skyrme functional~\cite{Chabanat:1997un} using the HFBRAD code~\cite{Bennaceur:2005mx}.
 We expect the approximations to be valid at least for momenta above the gray-shaded regions and indeed the agreement is quite reasonable, particularly at the highest momenta.
@@
 It is evident that the high momentum tails are very similar across the nuclei; this is the manifestation of the universal behavior of these distributions.
+There is a clear signature of the sharp cutoff caused by the $\theta$ functions in Eq.~\eqref{eq:snmd_partial_waves} at momenta near the Fermi momentum $\kF$.
+We expect a smoother distribution with higher-order contributions to the DME as well as from long-range correlations.
 From Table~\ref{tab:partial_wave_contributions} we see evidence that the s-waves dominate the contributions to these momentum distributions.
@@
 	\caption{Percentage contributions from s-waves and selected p-waves to proton momentum distributions for $q>2\,\fmi$.
-We show $N_X/N$ with $N \sim \int_2^{\infty} dq\, q^2 n_{\lambda}^A(q)$, where $n_{\lambda}^A(q)$ is the distribution for nucleus $A$ with evolved operator at $\lambda = 1.35\,\fmi$ and $X$ denotes using only one partial wave.}
+We show $N_X/N$ with $N \sim \int_2^{\infty} dq\, q^2 n_{\lambda}^A(q)$, where $n_{\lambda}^A(q)$ is the proton distribution for nucleus $A$ with evolved operator at $\lambda = 1.35\,\fmi$ and $X$ denotes using only one partial wave.}
 	\label{tab:partial_wave_contributions}
@@
 The high-momentum tail of any momentum distribution will be scale- and scheme-dependent, i.e., dependent on the potential used. 
-We can reproduce results at low-RG resolution for any initial potential, but the reaction operators must consistently evolved.
+We can reproduce results at low-RG resolution for any initial potential, but the reaction operators must be consistently evolved.
 As evident from Fig.~\ref{fig:schematic_SRC_physics}, we can cancel out the scale and scheme dependence in many cases by taking ratios.
@@
 The ratio is equal to one for $N=Z$ nuclei at all $q$, as expected from factorization as illustrated in Fig.~\ref{fig:schematic_SRC_physics} if the nucleus in numerator and denominator are the same.
-Even though there are no high-momentum nucleons in the low-resolution wave function, the result is consistent with phenomenology that the proton and neutron high-momentum distributions should be about the same.
+Even though there are no high-momentum nucleons in the low-resolution wave function, the result is consistent with phenomenology that the proton and neutron high-momentum distributions should be about the same~\cite{Hen:2016kwk}.
 In the region of np dominance near $q=2\,\fmi$ (400\,MeV), this ratio should be unity independent of $N/Z$, while there is $N/Z$ dependence away from this region because there are more nn than pp pairs.
@@
 The ratio dips down to essentially zero just before 2\,\fmi and then rises to about 0.15 at 4\,\fmi.
-This trend is also observed in the GCF calculations~\cite{Cruz-Torres:2019fum,Korover:2020lqf} and reflects the transition from the dominant effect of the tensor force toward the scalar limit.
+This trend is also observed in the GCF calculations~\cite{Cruz-Torres:2019fum,CLAS:2020rue} and reflects the transition from the dominant effect of the tensor force toward the scalar limit.
 In the low-resolution calculations here, this dependence on $q$ is purely from the high-momentum part of the factorized unitary transformations.
@@
     \centering
-\includegraphics[width=0.82\columnwidth]{figures_low_res/a2_errorbars_C12_O16_Ca40_Ca48_Fe56_Pb208_channels_1S0_3S1_kvnn_6_lamb_1p35.png}
+\includegraphics[width=0.82\columnwidth]{figures_low_res/a2_errorbars.png}
     \caption{SRC scaling factors $a_2$ calculated using AV18 according to Eq.~\eqref{eq:a2}. See text for further details.}
@@
 
-Finally, in Fig.~\ref{fig:src_scaling_factors_a2} we compare calculated SRC scaling factors $a_2$ using AV18 to values for even-even nuclei extracted from inclusive cross section ratios.
-Following the prescription of Ref.~\cite{Ryckebusch:2019oya}, we estimate $a_2$ by integrating single-nucleon probability distributions (phase-space weighted $n_{\lambda}^A(q)$) over a high-momentum range:
+Finally, in Fig.~\ref{fig:src_scaling_factors_a2} we compare calculated SRC scaling factors $a_2$ using AV18 to values for nuclei extracted from inclusive cross section ratios~\cite{Fomin:2011ng,Schmookler:2019nvf}.
+Following the prescription of Ref.~\cite{Ryckebusch:2019oya}, we estimate $a_2$ by integrating single-nucleon probability distributions (phase-space weighted $n_{\lambda}^A(q)$, summing proton and neutron distributions) over a high-momentum range:
 %
@@
 We apply the LDA to both the numerator and denominator, which may help to cancel systematic errors.
+Results using densities from the SLy4 Skyrme functional~\cite{Chabanat:1997un} are shown in red and results using densities from the Gogny functional~\cite{Decharge:1979fa} in blue.
 The ``error bars'' (which are not statistical uncertainty intervals) are established by using integration ranges $\Delta q^{\rm high} = 2$--$\infty$ \fmi and  $\Delta q^{\rm high} = 3.8$--$4.5$ \fmi~\cite{Ryckebusch:2019oya}.
-The agreement with experiment is good.
-In future work we will extend the comparison to more nuclei, explore the SRG $\lambda$ dependence in detail, and test the sensitivity to our assumptions~\cite{Tropiano:2021prep}.
+The agreement with experiment is consistent with these error bars.
+
+The magnitude of $a_2$ and the trend with $A$ can be roughly understood at low-RG resolution from a mean-field treatment of the leading operator product expansion for the integrands in \eqref{eq:a2}~\cite{Anderson:2010aq,Chen:2016bde,Lynn:2019vwp}.
+This means a factorization approximation to $\delta U(k,q)$ (including constant $k$ dependence) and the dominance of the $\tripletS$ contribution.
+When applied to the third term of Eq.~\eqref{eq:snmd_partial_waves}, which is the only contribution to the $a_2$ integrals,
+the short-distance $q$ dependence cancels in the $a_2$ ratio and we are left with integrals of the $\theta$ functions over total momentum $K$ and relative momentum $k$. 
+The integrals decouple after switching to single-particle momenta,  yielding a product of the proton and neutron densities at $R$.
+Thus $a_2$ is simply given by the ratio of $(1/A)\int d^3R\, \rho_p(R)\rho_n(R)$ factors, as would be expected from the schematic treatment in Fig.~\ref{fig:schematic_SRC_physics}.
+This ratio accounts for about 80\% of $a_2$ and the variation of the integral with $A$ tracks the $A$ dependence from $^4$He to $^{208}$Pb quite closely.
+The remaining 20\% comes primarily from the $\singletS$ contribution, with the relative weighting of $\singletS$ and $\tripletS$ dependent on the relative $q$ dependence in the $\delta U$ matrix elements seen in Fig.~\ref{fig:ratio_1p35_kvnn_6_222}.
+
+%In future work we will extend the comparison to more nuclei, explore the SRG $\lambda$ dependence in detail, and test the sensitivity to our assumptions~\cite{Tropiano:2021prep}.
 
@@
   For SRG parameter $\lambda$ comparable to $\kF$, this corresponds to the conditions for factorization as well as complete dominance of the two-body current.
-  In taking ratios, the high-momentum part cancels out, so the leading dependence of the plateau heights in the cross-section ratio, namely $a_2$, is a mean-field quantity, which is well reproduced in our approximations (see Fig.~\ref{fig:src_scaling_factors_a2}).
+  In taking ratios, the high-momentum part cancels out, so the leading dependence of the plateau heights in the cross-section ratio, namely $a_2$, is a mean-field quantity~\cite{Anderson:2010aq,Cruz-Torres:2019fum}, which is well reproduced in our approximations (see Fig.~\ref{fig:src_scaling_factors_a2}).
   The conditions here hold for any high-momentum current.
@@
     The ratio of triplet to singlet shows the peak near $q = 2\,\fmi$ for both potentials, associated with a zero in the \singletS\ channel and the enhanced tensor contribution in the \tripletS\ channel.
-    Figures~\ref{fig:barcharts_AV18} and \ref{fig:barcharts_Gezerlis} show that despite the tensor dominance, at low-RG resolution the coupling to the wave function is through the s-waves, not tensor correlations in the wave functions.
+    Figure~\ref{fig:barchart_deuteron}  show that despite the tensor dominance, at low-RG resolution the coupling to the wave function is through the s-waves, not tensor correlations in the wave functions.
     The consequences for experimental ratios are illustrated in Figs.~\ref{fig:pp_plus_pn_ratios} and \ref{fig:pp_to_pn_ratios}, which are consistent with SRC phenomenology.
@@
 
-The parallel formulation at low-RG resolution is that the dependence on $r$ or $q$ in the wave function becomes the corresponding part of the facotrized unitary transformation.
-As such, it is the leading term in an operator product expansion~\cite{Anderson:2010aq,Bogner:2012zm,Tropiano:2020zwb}.
+The parallel formulation at low-RG resolution is that the dependence on $r$ or $q$ in the wave function becomes the corresponding part of the factorized unitary transformation.
+As such, it is the leading term in an operator product expansion~\cite{Anderson:2010aq,Bogner:2012zm,Chen:2016bde,Tropiano:2020zwb}.
 A key advantage of the RG formulation is that systematic corrections are well defined.
@@
 
-  \item\textbf{What can SRC experiments tell us about high-density nuclear matter?}
-  In the high-SRG-resolution picture, the basic intuition is that in SRC pairs nucleons are at short distances so they probe high densities.
-  But to be quantitatively useful at high densities in this picture one would at least need to extend the description to three-body forces.
-  The GCF phenomenology is an implementation of leading-order Brueckner theory, which provides a \emph{low-density} expansion.
-  Three-body correlations are known from calculations to be important for neutron star physics.
+%   \item\textbf{What can SRC experiments tell us about high-density nuclear matter?}
+%   In the high-SRG-resolution picture, the basic intuition is that in SRC pairs nucleons are at short distances so they probe high densities.
+%   But to be quantitatively useful at high densities in this picture one would at least need to extend the description to three-body forces.
+%   The GCF phenomenology is an implementation of leading-order Brueckner theory, which provides a \emph{low-density} expansion.
+%   Three-body correlations are known from calculations to be important for neutron star physics.
   %[\emph{Also more mixing with near-$\kF$ states will increase three-body correlations.}]
 
-  \item\textbf{What is the relevance of EMC physics for low-energy nuclei? How should we understand the observed SRC-EMC correlation?} 
-  This physics should be automatically included in an EFT expansion because of the completeness of the operator basis. 
-  The EMC effect is from short-distance physics that manifests first as two-body contact operators. 
-  If mean-field estimate plus chiral naturalness is valid, then the expected EMC slope is consistent with experiment.
+%   \item\textbf{What is the relevance of EMC physics for low-energy nuclei? How should we understand the observed SRC-EMC correlation?} 
+%   This physics should be automatically included in an EFT expansion because of the completeness of the operator basis. 
+%   The EMC effect is from short-distance physics that manifests first as two-body contact operators. 
+%   If mean-field estimate plus chiral naturalness is valid, then the expected EMC slope is consistent with experiment.
 The treatment (from Chen and Detmold originally~\cite{Chen:2004zx,Chen:2016bde,Lynn:2019vwp}) starts with an operator product expansion applied at the level of QCD matrix elements, which is then matched to an EFT for matrix elements; 2-body operators must be there!
-  The dominance of the leading two-body contact then accounts for EMC-SRC correlations.
+%   The dominance of the leading two-body contact then accounts for EMC-SRC correlations.
 
   \item\textbf{What are the implications for other knock-out reactions?}
-  Analyses of exclusive intermediate energy nucleon knock-out experiments have shown systematic discrepancies between measured cross sections and theoretical predictions~\cite{Tostevin:2014usa,Aumann:2020tcq}.
-  But these analyses mix a high-resolution reaction mechanism (e.g., eikonal model) with a low-resolution structure description (e.g., shell model).
+  Analyses of intermediate energy nucleon knock-out experiments often
+ mix a high-resolution reaction mechanism (e.g., eikonal model) with a low-resolution structure description (e.g., shell model)~\cite{Tostevin:2014usa,Aumann:2020tcq}.
   Such a mismatch applied to the electron-scattering SRC experiments considered here would lead to essentially zero cross section predicted theoretically because the contribution from the two-body current at low RG resolution would be entirely omitted and the one-body current has no support at high momentum.
-  This implies that RG evolution of the reaction operators may be essential for resolving the discrepancies.
-  The situation is not nearly as clean as the present case, however.
-  For exclusive scattering to low-lying single-particle states, the theory would be \emph{larger} than experiment because a missing induced current (two-body, if electron scattering) would not exclude flux (cf.\ SRCs depleting the orbitals).
+  This implies that RG evolution of the reaction operators may be relevant for resolving systematic discrepancies between measured cross sections and theoretical predictions~\cite{Tostevin:2014usa,Aumann:2020tcq} (see also Ref.~\cite{Wylie:2021uot}).
+%   The situation is not nearly as clean as the present case, however.
+%   For exclusive scattering to low-lying single-particle states, the theory would be \emph{larger} than experiment because a missing induced current (two-body, if electron scattering) would not exclude flux (cf.\ SRCs depleting the orbitals).
 
@@
 
-Planned extensions of the present investigations include~\cite{Tropiano:2021prep}:
-\begin{itemize}
-    \item \textbf{Examining SRG resolution ($\lambda$) dependence.} How robust are the approximations and results presented here to changes in $\lambda$?
+% Planned extensions of the present investigations include~\cite{Tropiano:2021prep}:
+% \begin{itemize}
+%     \item \textbf{Examining SRG resolution ($\lambda$) dependence.} How robust are the approximations and results presented here to changes in $\lambda$?
 What are the relative importance of three-body and tensor correlations in the wave functions, three-body forces in the Hamiltonian, induced three-body contributions to the operators?
 
-    \item \textbf{Improving the treatment of ground-state wave function.} 
-    One approach is to use the DME to improve the LDA and establish the uncertainties. 
-    We can also explore the use of many-body perturbation theory and ab initio methods directly.
-
-    \item \textbf{Improving the operators.} The truncation to two-body operators will be relaxed systematically, quantifying the corrections and seeking tractable approximations.
-
-    \item \textbf{Fitting the operators.}
-    An alternative to evolving high-resolution operators is to fit them at low-resolution. 
-    This will first be explored for cases where evolution is also available.
-
-    \item \textbf{Extensions to other reactions.}
-    One of the first steps will be to re-examine the exclusive $(e,e'p)$ knock-out reactions (e.g., those studied at NIKHEF and other electron scattering facilities)~\cite{Dieperink:1990uk,Kelly:1996hd}.
-
-\end{itemize}
-%
+%     \item \textbf{Improving the treatment of ground-state wave function.} 
+%     One approach is to use the DME to improve the LDA and establish the uncertainties. 
+%     We can also explore the use of many-body perturbation theory and ab initio methods directly.
+
+%     \item \textbf{Improving the operators.} The truncation to two-body operators will be relaxed systematically, quantifying the corrections and seeking tractable approximations.
+
+%     \item \textbf{Fitting the operators.}
+%     An alternative to evolving high-resolution operators is to fit them at low-resolution. 
+%     This will first be explored for cases where evolution is also available.
+
+%     \item \textbf{Extensions to other reactions.}
+%     One of the first steps will be to re-examine the exclusive $(e,e'p)$ knock-out reactions (e.g., those studied at NIKHEF and other electron scattering facilities)~\cite{Dieperink:1990uk,Kelly:1996hd}.
+
+% \end{itemize}
+% %
+% Work on all of these areas is in progress.
+
+Planned extensions of the present investigations in the short term include~\cite{Tropiano:2021prep}:
+further examining the SRG resolution ($\lambda$) dependence; improving the treatment of the ground-state wave function with DME corrections; relaxing the truncation to two-body operating, quantifying the corrections and seeking tractable approximations; and re-examining $(e,e'p)$ knock-out reactions  studied at NIKHEF and other electron scattering facilities~\cite{Dieperink:1990uk,Kelly:1996hd}.
 Work on all of these areas is in progress.
@@
 \begin{acknowledgments}
-We thank Nathan Parzuchowski for contributions to an earlier version of this work, and Wim Cosyn and Jan Ryckebusch for helpful comments on the manuscript.
+We thank Nathan Parzuchowski for contributions to an earlier version of this work, Nicolas Schunck for sharing a code to calculate Gogny nucleon densities, and Wim Cosyn and Jan Ryckebusch for helpful comments on the manuscript.
 We thank our colleagues for many useful discussions on SRC physics over the years.
